### 2022-01-31 src/ms.tex
added brief summary

% Define document class
\documentclass[twocolumn]{aastex631}

% Filler text
\usepackage{blindtext}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author[0000-0000-0000-0000]{First Author}

% Abstract with filler text
\begin{abstract}
    \blindtext
\end{abstract}

% Main body with filler text
\section{Introduction}
\Blindtext[4]

\section{Methods}

\subsection{Accuracy of astroNN}

For $19784$ stars, or $\sim3.5\%$ of the sample, the astroNN [Fe/H] abundance estimate is $\gtrsim0.5$ dex lower than the value provided by ASPCAP. The vast majority of these stars are on the lower-main sequence according to \textit{Gaia} photometry, so we exclude stars with $\log(g) > 4$ in ASPCAP. In addition, 197 or $\sim3\%$ of stars with APOKASC-2 asteroseismic ages are reported to be $>5$ Gyr younger by astroNN. The APOKASC-2 age is unphysically high for many of these stars, often exceeding 15 Gyr. We identify prior mass loss as the cause of this discrepancy, so the astroNN ages are likely closer to the truth.

\end{document}

### 2022-06-06 src/ms.tex
update manuscript

@@
 \usepackage{blindtext}
+
+% Units in equations
+% \usepackage{siunitx}
 
@@
 
+\subsection{Measurements of the Type Ia Supernova Delay Time Distribution}
+
+\citet{Schonrich2009-RadialMixing} take their DTD to be an exponential with a 1.5 Gyr timescale, though this isn't strictly observationally motivated.
+
+\citet{Maoz2017-CosmicDTD} compare volumetric SN Ia rates to the cosmic star formation history.
+They get a power law with a slope of $-1.13\pm 0.06$ for field galaxies, and a slope of $-1.39^{+0.32}_{-0.05}$ for galaxy clusters.
+
+\citet{Heringer2019-FieldGalaxyDTD} study the distribution of SNe Ia in field galaxies and get a power-law index of $-1.34^{+0.19}_{-0.17}$ which is closer to Maoz's cluster DTD.
+
+\citet{Stolger2020-ExponentialDTD} perform maximum likelihood estimations based on the cosmic star formation history and the star formation histories of individual galaxies.
+In both cases their best fit functions were approximately exponential, though they started with a skew-normal function so could not have ended up with a power law even if they wanted to.
+They don't actually report the timescale of this exponential, but based on the plots I'd say it's about 1.5 - 2 (1.7?) Gyr.
+Their best fit parameters make no sense to me as they don't report their units.
+
+\citet{Wiseman2021-DESRates} measure the SN Ia rate in the redshift range $0.2 < z < 0.6$ and get a similar power law to \citet{Maoz2017-CosmicDTD} with a slope of $-1.13 \pm 0.05$.
+They also find that slower-declining SNe have a steeper DTD slope.
+
+\begin{deluxetable}{lCl}
+\tablecaption{Sources of the various forms of delay time distribution.}
+\tablehead{
+\colhead{Name} & \colhead{Form} & \colhead{Source}
+}
+\startdata
+Field Galaxy Power-Law      & t^{-1.1}              & \citet{Maoz2017-CosmicDTD} \\   
+Galaxy Cluster Power-Law    & t^{-1.4}              & \citet{Maoz2017-CosmicDTD} \\
+Short Exponential           & e^{-t/1.5\,\rm{Gyr}}  & \citet{Schonrich2009-RadialMixing} \\
+\enddata
+\end{deluxetable}
+
+\bibliography{bib}
+
 \end{document}

### 2022-06-28 migration/figures.py
remove simulation code (now at lodubay/galactic-dtd-migration)

@@ -1,195 +1,0 @@
-r"""
-This script produces the figures in Johnson et al. (2021).
-
-Run ``python figures.py --help`` for more info.
-"""
-
-import argparse
-import src
-import os
-
-
-# The functions that must be called to produce each figure
-_FUNCTIONS_ = {
-	"fig1": 	src.plots.h277_decomposition,
-	"fig2": 	src.plots.migration,
-	"fig3": 	src.plots.eta_tau_sfh,
-	"fig4": 	src.plots.evol,
-	"fig5": 	src.plots.sfe,
-	"fig6": 	src.plots.surface_density_gradient,
-	"fig7": 	src.plots.ofe_feh_densitymap,
-	"fig8": 	src.plots.tracks,
-	"fig9": 	src.plots.metallicity_gradient,
-	"fig10": 	src.plots.mdf_3panel,
-	"fig11": 	src.plots.mdf_3panel,
-	"fig12": 	src.plots.ofe_mdfs,
-	"fig13a": 	src.plots.age_ofe,
-	"fig13b": 	src.plots.age_ofe,
-	"fig14": 	src.plots.amr.galactic_regions,
-	"fig15": 	src.plots.amr.comparison,
-	"fig16": 	src.plots.amr.solar_annulus,
-	"fig17": 	src.plots.amr.comparison,
-	"fig18": 	src.plots.amr.comparison
-}
-
-
-# The arguments that must be passed to each function.
-_ARGS_ = {
-	"fig1": 	["./figures/fig1"],
-	"fig2": 	["./figures/fig2"],
-	"fig3": 	["./figures/fig3"],
-	"fig4": 	["./outputs/diffusion/static",
-					"./outputs/diffusion/insideout",
-					"./outputs/diffusion/lateburst",
-					"./outputs/diffusion/outerburst",
-					"./figures/fig4"],
-	"fig5": 	[["./outputs/diffusion/insideout"],
-					"./figures/fig5"],
-	"fig6": 	["./outputs/diffusion/insideout",
-					"./figures/fig6"],
-	"fig7": 	["./outputs/diffusion/insideout",
-					"./outputs/post-process/insideout",
-					"./figures/fig7"],
-	"fig8": 	["./outputs/diffusion/insideout",
-					"./outputs/post-process/insideout",
-					"./figures/fig8"],
-	"fig9": 	["./outputs/diffusion/static",
-					"./outputs/diffusion/insideout",
-					"./outputs/diffusion/lateburst",
-					"./outputs/diffusion/outerburst",
[…]

### 2022-06-28 migration/simulations.py

@@ -1,118 +1,0 @@
-r"""
-This script runs the models in Johnson et al. (2021).
-
-Run ``python simulations.py --help`` for more info.
-"""
-
-import argparse
-import src
-from vice import milkyway
-import sys
-
-_MIGRATION_MODELS_ = ["diffusion", "linear", "post-process", "sudden"]
-_EVOLUTION_MODELS_ = ["static", "insideout", "lateburst", "outerburst", "conroy22"]
-_DELAY_MODELS_ = ["powerlaw", "powerlaw_steep", "exponential", "bimodal"]
-
-def parse():
-	r"""
-	Parse the command line arguments using argparse.ArgumentParser
-	"""
-	parser = argparse.ArgumentParser(
-		description = "The parameters of the Milky Way models to run.")
-
-	parser.add_argument("-f", "--force",
-		help = "Force overwrite existing VICE outputs of the same name.",
-		action = "store_true")
-
-	parser.add_argument("--migration",
-		help = "The migration model to assume. (Default: diffusion)",
-		type = str,
-		default = "diffusion")
-
-	parser.add_argument("--evolution",
-		help = "The evolutionary history to assume (Default: insideout)",
-		type = str,
-		default = "insideout")
-
-	parser.add_argument("--RIa",
-		help = "The SN Ia delay-time distribution to assume (Default: powerlaw)",
-		type = str,
-		default = "powerlaw")
-
-	parser.add_argument("--minimum-delay",
-		 help = "The minimum SN Ia delay time in Gyr (Default: 0.04)",
-		 type = float,
-		 default = 0.04)
-
-	parser.add_argument("--dt",
-		help = "Timestep size in Gyr. (Default: 0.01)",
-		type = float,
-		default = 0.01)
-
-	parser.add_argument("--nstars",
-		help = """Number of stellar populations per zone per timestep. \
-(Default: 2)""",
-		type = int,
-		default = 2)
-
-	parser.add_argument("--name",
-		help = "The name of the output simulations (Default: 'milkway')",
-		type = str,
-		default = 'milkyway')
-
-	parser.add_argument("--elements",
-		help = """Elements to simulation the enrichment for separated by \
-underscores. (Default: \"fe_o\")""",
-		type = str,
-		default = "fe_o")
-
-	parser.add_argument("--zonewidth",
-		help = "The width of each annulus in kpc. (Default: 0.1)",
-		type = float,
-		default = 0.1)
-
[…]

### 2022-06-28 migration/src/__init__.py

@@ -1,4 +1,0 @@
-
-__all__ = ["plots", "simulations"]
-from . import plots
-from . import simulations

### 2022-06-28 migration/src/_globals.py

@@ -1,17 +1,0 @@
-r"""
-Global variables to the migration simulations and plot analysis.
-"""
-
-END_TIME = 13.2 # total simulation time in Gyr
-
-# Width of each annulus in kpc
-# This needs modified *only* if running the plotting scripts.
-ZONE_WIDTH = 0.1
-
-MAX_SF_RADIUS = 15.5 # Radius in kpc beyond which the SFR = 0
-
-# Stellar mass of Milky Way (Licquia & Newman 2015, ApJ, 806, 96)
-M_STAR_MW = 5.17e10
-
-COLORMAP = "winter"
-

### 2022-06-28 migration/src/plots/env.py

@@ -1,63 +1,0 @@
-r"""
-Ensures runtime dependencies are satisfied for producing figures in Johnson et
-al. (2021).
-
-Dependencies:
-
-	- matplotlib >= 2.0.0
-	- NumPy >= 1.17.0
-"""
-
-try:
-	ModuleNotFoundError
-except NameError:
-	ModuleNotFoundError = ImportError
-
-# Enforce matplotlib >= 2.0.0 or else RuntimeError
-try:
-	import matplotlib as mpl
-except (ModuleNotFoundError, ImportError):
-	raise ModuleNotFoundError("Matplotlib not found.")
-if tuple([int(i) for i in mpl.__version__.split('.')])[:2] < (2, 0):
-	raise RuntimeError("""Matplotlib version >= 2.0.0 required for producing \
-Johnson et al. (2021) figures. Current: %s""" % (mpl.__version__))
-else: pass
-
-# Enforce NumPy >= 1.17.0 or else RuntimeError
-try:
-	import numpy as np
-except (ModuleNotFoundError, ImportError):
-	raise ModuleNotFoundError("NumPy not found.")
-if tuple([int(i) for i in np.__version__.split('.')])[:2] < (1, 17):
-	raise RuntimeError("""NumPy version >= 1.17.0 required for producing \
-Johnson et al. (2021) figures. Current: %s""" % (np.__version__))
-else: pass
-
-
-# by setting matplotlib rcParams here, all plots will be automatically
-# formatted since this file will be imported everywhere to ensure dependencies
-# are met anyway.
-mpl.rcParams["font.family"] = "serif"
-mpl.rcParams["text.usetex"] = True
-mpl.rcParams["text.latex.preamble"] = [r"\usepackage{amsmath}"]
-mpl.rcParams["errorbar.capsize"] = 5
-mpl.rcParams["axes.linewidth"] = 2
-mpl.rcParams["xtick.major.size"] = 16
-mpl.rcParams["xtick.major.width"] = 2
-mpl.rcParams["xtick.minor.size"] = 8
-mpl.rcParams["xtick.minor.width"] = 1
-mpl.rcParams["ytick.major.size"] = 16
-mpl.rcParams["ytick.major.width"] = 2
-mpl.rcParams["ytick.minor.size"] = 8
-mpl.rcParams["ytick.minor.width"] = 1
-mpl.rcParams["axes.labelsize"] = 30
[…]

### 2022-06-28 migration/src/plots/plots/__init__.py

@@ -1,10 +1,0 @@
-
-__modules__ = ["amr"]
-__files__ = ["age_ofe", "evol", "eta_tau_sfh", "h277_decomposition",
-	"mdf_3panel", "metallicity_gradient", "migration", "ofe_feh_densitymap",
-	"ofe_mdfs", "sfe", "surface_density_gradient", "tracks"]
-__all__ = __modules__ + __files__
-
-for i in __modules__: exec("from . import %s" % (i))
-for i in __files__: exec("from .%s import main as %s" % (i, i))
-

### 2022-06-28 migration/src/plots/plots/amr/__init__.py

@@ -1,4 +1,0 @@
-
-__all__ = ["comparison", "galactic_regions", "solar_annulus"]
-for i in __all__: exec("from .%s import main as %s" % (i, i))
-

### 2022-06-28 migration/src/plots/plots/amr/solar_annulus.py

@@ -1,142 +1,0 @@
-r"""
-This script produces a plot of the age-[O/H] and age-[Fe/H] relations in the
-solar annulus predicted by the simulations and in comparison to the
-Feuillet et al. (2019) data.
-"""
-
-from ... import env
-from ...utils import zheights, weighted_median, feuillet2019_data
-from ..utils import named_colors, mpl_loc, markers, xticklabel_formatter
-from .galactic_regions import plot_amr, median_ages, feuillet2019_amr
-import matplotlib.patheffects as pe
-import matplotlib.pyplot as plt
-import numpy as np
-import vice
-
-
-def main(output, stem):
-	r"""
-	Produce a figure comparing the model-predicted age-[O/H] and age-[Fe/H]
-	relations in the solar annulus as predicted by VICE in comparison to the
-	relations reported by Feuillet et al. (2018, 2019) [1]_ [2]_.
-
-	Parameters
-	----------
-	output : ``str``
-		The relative or absolute path to the VICE output containing the
-		model predicted data.
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-
-	.. [1] Feuillet et al. (2018), MNRAS, 477, 2326
-	.. [2] Feuillet et al. (2019), MNRAS, 489, 1742
-	"""
-	ax1, ax2 = setup_axes()
-	output = vice.output(output)
-	output.stars["abszfinal"] = [abs(_) for _ in zheights(
-		output.name)[:output.stars.size[0]]]
-	min_radius = 7
-	max_radius = 9
-	min_z = 0
-	max_z = 0.5
-
-	# majority of plotting and calculations done by these functions in
-	# galactic_regions.py
-	plot_amr(ax1, "O", "H", output, min_radius, max_radius, min_z, max_z)
-	sc = plot_amr(ax2, "Fe", "H", output, min_radius, max_radius, min_z, max_z)
-	median_ages(ax1, "O", "H", output, min_radius, max_radius, min_z, max_z,
-		zorder = 2)
[…]

### 2022-06-28 migration/src/plots/plots/evol.py

@@ -1,135 +1,0 @@
-r"""
-Produces a plot of the densities of infall, star formation, and gas as a
-function of simulation time for all models.
-"""
-
-from .. import env
-from .utils import (named_colors, mpl_loc, yticklabel_formatter,
-	dummy_background_axes)
-from ..._globals import ZONE_WIDTH
-import matplotlib.pyplot as plt
-import math as m
-import vice
-
-# y-axis limits for SFR in Msun yr^-1 kpc^-2
-SFR_LIM = [1.1e-4, 0.3]
-
-# y-axis limit for infall rate in Msun yr^-1 kpc^-2
-IFR_LIM = [2.e-3, 0.3]
-
-# y-axis limit for gas surface density in Msun kpc^-2
-GAS_LIM = [3.e6, 3.e8]
-
-# x-axis limits for time in Gyr
-TIME_LIM = [-1, 13]
-
-# Galactocentric radii in kpc to plot the three quantities for.
-RADII = [3, 5, 7, 9, 11, 13, 15]
-
-# Colors to show each annulus's evolution in.
-COLORS = ["grey", "black", "red", "gold", "green", "blue", "darkviolet"]
-
-# Model names
-MODELS = ["Constant SFR", "Inside-Out", "Late-Burst", "Outer-Burst"]
-
-
-def main(static, insideout, lateburst, outerburst, stem):
-	r"""
-	Plot the surface densities of star formation, infall, and gas as functions
-	of time for the four SFH models described in Johnson et al. (2021).
-
-	Parameters
-	----------
-	static : ``str``
-		The relative path to the VICE output with a constant SFH.
-	insideout : ``str``
-		The relative path to the VICE output with an inside-out SFH.
-	lateburst : ``str``
-		The relative path to the VICE output with a late-burst SFH.
-	outerburst : ``str``
-		The relative path to the VICE output with an outer-burst SFH.
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-	"""
-	axes = setup_axes()
-	plot_evolution([row[0] for row in axes], vice.output(static), label = True)
[…]

### 2022-06-28 migration/src/plots/plots/mdf_3panel.py

@@ -1,298 +1,0 @@
-r"""
-This script produces 3-panel figures showing either the [Fe/H] or [O/H]
-distributions in 3 bins in z for different galactocentric radii. Can be shown
-in comparison to APOGEE DR16.
-"""
-
-
-from ..._globals import ZONE_WIDTH
-from .. import env
-from ..utils import zheights, filter_multioutput_stars
-from .utils import named_colors, mpl_loc, markers, dummy_background_axes
-from .metallicity_gradient import target_mode_abundance
-import matplotlib.pyplot as plt
-import numpy as np
-import vice
-
-
-def main(element, outputs, stem, radial_bins = [3, 5, 7, 9, 11, 13, 15],
-	z_bins = [0.0, 0.5, 1.0, 2.0],
-	labels = ["Inside-Out", "Late-Burst", "Outer-Burst"],
-	# apogee = False,
-	colors = ["black", "red", "gold", "green", "blue", "darkviolet"]):
-	r"""
-	For some element X, plot the metallicity distribution functions (MDFs) in
-	[X/H] in different galactic regions as predicted by a given VICE model,
-	with or without a comparison to the APOGEE data.
-
-	Parameters
-	----------
-	element : ``str``
-		The element X to plot the distributions in [X/H] for. Must be included
-		in the model output.
-	outputs : ``list`` [elements of type ``str``]
-		A list of relative or absolute or absolute paths to the VICE outputs to
-		predictions of.
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-	radial_bins : ``list`` [default : [3, 5, 7, 9, 11, 13, 15]]
-		The bin-edges in galactocentric radius in kpc in which to compute the
-		MDFs. Must be in ascending order.
-	z_bins : ``list`` [default : [0.0, 0.5, 1.0, 2.0]]
-		The bin-edges in height above/below the disk midplane in kpc in which
-		to compute the MDFs. Must be in ascending order. Sign is neglected.
-	labels : ``list`` [elements of type ``str``]
-		[default : ["Inside-Out", "Late-Burst", "Outer-Burst"]]
-		A descriptor to attach to each of the ``outputs`` to distinguish which
-		panel belongs to which model visually.
[…]

### 2022-06-28 migration/src/plots/plots/migration.py

@@ -1,311 +1,0 @@
-r"""
-Produces a plot of the migration schema implemented in Johnson et al. (2021).
-This is an artistic diagram which doesn't represent physical quantities, only
-qualitative trends.
-"""
-
-from ..._globals import END_TIME
-from .. import env
-import matplotlib.pyplot as plt
-from .utils import named_colors, mpl_loc
-import math as m
-import numbers
-import random
-
-
-def main(stem):
-	r"""
-	Produces a plot of the migration scheme implemented in Johnson et al.
-	(2021), illustrated in their Fig. 2. This is an artistic diagram which
-	doesn't represent physical quantities, only the qualitative trends of their
-	models.
-
-	Parameters
-	----------
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-	"""
-	ax = setup_axis()
-	initial = [1, 14] # birth radii in kpc
-	final = [9, 10] # final radii in kpc
-	birth = [3, 5] # birth times in Gyr
-	sudden = [9.1, 6.8] # times for sudden migration
-	for i in range(len(initial)):
-		for j in scheme.recognized_modes:
-			plot_scheme(ax, initial[i], final[i], birth[i], label = not i,
-				mode = j, sudden_migration_time = sudden[i])
-	leg = ax.legend(loc = mpl_loc("upper left"), ncol = 1, frameon = False,
-		bbox_to_anchor = (0.02, 0.98), fontsize = 20)
-	plt.tight_layout()
-	plt.savefig("%s.pdf" % (stem))
-	plt.savefig("%s.png" % (stem))
-	plt.close()
-
-
-def plot_scheme(ax, initial, final, birth, mode = "diffusion", label = False,
-	sudden_migration_time = 10):
-	r"""
-	Plot a migration scheme as a function of simulation time.
-
-	Parameters
-	----------
-	ax : ``axes``
-		The matplotlib subplot to plot on.
-	initial : ``float``
-		Galactocentric radius of birth in kpc.
-	final : ``float``
-		Present-day galactocentric radius in kpc.
-	birth : ``float``
-		Simulation time of birth in Gyr.
-	mode : ``str`` [case-insensitive] [default : "diffusion"]
-		A keyword denoting the time-dependence of migration from birth to
-		present-day radii.
-	label : ``bool`` [default : False]
[…]

### 2022-06-28 migration/src/plots/plots/ofe_feh_densitymap.py

@@ -1,186 +1,0 @@
-r"""
-Produces a scatterplot of 10,000 randomly selected model-predicted stellar
-populations in [O/Fe]-[Fe/H] space for 15 galactic regions color-coded by
-galactocentric radius of birth.
-
-This script produces Fig. 7 of Johnson et al. (2021).
-"""
-
-from ..._globals import ZONE_WIDTH, COLORMAP
-from .. import env
-from ..utils import zheights, filter_multioutput_stars
-from .utils import named_colors, dummy_background_axes
-import matplotlib.pyplot as plt
-import numpy as np
-import vice
-
-# The bin edges in radius in kpc defining galactic regions
-RADII = [3, 5, 7, 9, 11, 13, 15]
-
-# The bin edges in height above/below the midplane in kpc defining
-# galactic regions
-HEIGHTS = [0.0, 0.5, 1.0, 2.0]
-
-# x-axis limits for [Fe/H]
-FEH_LIM = [-1.3, 0.8]
-
-# y-axis limits for [O/Fe]
-OFE_LIM = [-0.1, 0.5]
-
-# positions of ticks on the x-axis for [Fe/H]
-FEH_TICKS = [-1, -0.5, 0, 0.5]
-
-
-def main(output, comparison, stem, colormap = "winter", N = 10000):
-	r"""
-	Produce a 15-panel figure showing a scatter plot of randomly sampled
-	stellar populations in [O/Fe]-[Fe/H] space color-coded by birth radius for
-	different present-day galactic regions.
-
-	Parameters
-	----------
-	output : ``str``
-		The relative or absolute path to the VICE output whose predicted
-		[O/Fe]-[Fe/H] distribution is to be visualized.
-	comparison : ``str``
-		The relative or absolute path to the VICE output whose predicted
-		gas-phase track for the solar circle (R = 8 kpc) will be plotted as a
-		reference in all panels.
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-	colormap : ``str`` [default : "winter"]
-		The colormap to use in color-coding stellar populations by their
-		birth radius.
-	N : ``int`` [default : 10,000]
[…]

### 2022-06-28 migration/src/plots/plots/sfe.py

@@ -1,139 +1,0 @@
-r"""
-Produces a plot of the SFE timescale as a function of galactocentric radius at
-various timestamps for a set of VICE models.
-
-This script produces Fig. 5 of Johnson et al. (2021).
-"""
-
-from ..._globals import END_TIME, ZONE_WIDTH, MAX_SF_RADIUS
-from .. import env
-from .utils import (named_colors, mpl_loc, dummy_background_axes,
-	yticklabel_formatter)
-import matplotlib.pyplot as plt
-import vice
-
-# x-axis limits for galactocentric radius in kpc.
-RGAL_LIM = [-2, 17]
-
-
-def main(outputs, stem,
-	labels = ["Constant SFR", "Inside-Out", "Late-Burst", "Outer-Burst"],
-	times = [2, 4, 6, 8, 10, END_TIME],
-	colors = ["red", "gold", "green", "blue", "darkviolet", "black"],
-	ylim = [0.5, 20], yticks = [1, 10]):
-
-	r"""
-	Produce a plot of the SFE timescale :math:`\tau_\star` as a function of
-	galactocentric radius at various timestamps for a set of VICE models.
-
-	Parameters
-	----------
-	outputs : ``list`` [elements of type ``str``]
-		The relative or absolute paths to the VICE outputs whose predicted SFE
-		timescales are to be visualized here. They will be plotted in the
-		order they appear in this list.
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-	labels : array-like [elements of type ``str``] or ``None``
-		[default : ["Constant SFR", "Inside-Out", "Late-Burst", "Outer-Burst"]]
-		Short descriptors for each of the models to be plotted. Must contain
-		at least as many elements as ``outputs``. If ``None``, no labels will
-		be included.
-	times : array-like [elements of type ``float``]
-		[default : [2, 4, 6, 8, 10, 13.2]]
-		The time-stamps at which to plot the SFE timescale as a function of
-		radius.
-	colors : array-like [elements of type ``str``]
-		[default : ["red", "gold", "green", "blue", "darkviolet", "black"]]
-		The colors in which to plot the SFE timescales. Must contain at least
[…]

### 2022-06-28 migration/src/plots/plots/surface_density_gradient.py

@@ -1,216 +1,0 @@
-r"""
-Plots the surface density gradient as a function of galactocentric radius for a
-given VICE output.
-
-This script produces Fig. 6 of Johnson et al. (2021).
-"""
-
-from ..._globals import ZONE_WIDTH
-from .. import env
-import matplotlib.pyplot as plt
-from .utils import named_colors, mpl_loc, markers
-import math as m
-import vice
-
-
-def main(output, stem):
-	r"""
-	Plot the surface density of gas and stars as a function of galactocentric
-	radius as predicted by a VICE model in comparison to that reported for the
-	Milky Way by Bland-Hawthorn & Gerhard (2016) [1]_.
-
-	Parameters
-	----------
-	output : ``str``
-		The relative or absolute path to the VICE output whose gradient is to
-		be visualized here.
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-
-	Notes
-	-----
-	This figure will assume a normalization to the Bland-Hawthorn & Gerhard
-	(2016) consistent with a total stellar mass of ~6.08e+10 solar masses,
-	consistent with the value reported by Licquia & Newman (2015) [2]_ for the
-	total stellar mass of the Milky Way.
-
-	Galactocentric radii will be plotted in units of kiloparces, and surface
-	densities will be plotted in units of solar masses per square kiloparsec.
-
-	.. [1] Bland-Hawthorn & Gerhard (2016), ARA&A, 54, 529
-	.. [2] Licquia & Newman (2015), ApJ, 806, 96
-	"""
-	ax = setup_axis()
-	surface_densities(ax, vice.multioutput(output))
-	plt.tight_layout()
-	plt.subplots_adjust(right = 0.99)
-	plt.savefig("%s.pdf" % (stem))
-	plt.savefig("%s.png" % (stem))
-
-
-def surface_densities(ax, output):
-	r"""
-	Calculate and plot the surface densities as a function of radius for the
-	given output.
-
-	Parameters
-	----------
-	ax : ``axes``
-		The matplotlib subplot to plot on.
-	output : ``vice.multioutput``
-		The model-predicted data from the VICE output.
[…]

### 2022-06-28 migration/src/plots/plots/tracks.py

@@ -1,210 +1,0 @@
-r"""
-This file produces plots of single-panel [O/Fe]-[Fe/H] track comparisons
-between two models.
-"""
-
-from ..._globals import ZONE_WIDTH, END_TIME
-from .. import env
-from .utils import named_colors, mpl_loc, markers, yticklabel_formatter
-import matplotlib.pyplot as plt
-import vice
-
-RADII = [3, 5, 7, 9, 11, 13, 15]
-COLORS = ["grey", "black", "red", "gold", "green", "blue", "darkviolet"]
-PREFACTORS = [55, 25, 10, 5, 3, 2.0, 1.0]
-
-
-def main(output1, output2, stem, times = [2, 4, 6, 8, 10, END_TIME]):
-	r"""
-	Produce a two-panel figure comparing the gas-phase [O/Fe]-[Fe/H] tracks
-	of two models in the left-hand panel and a comparison of their SN Ia rates
-	in the right-hand panel.
-
-	Parameters
-	----------
-	output1 : ``str``
-		The relative or absolute path to the first of the two VICE outputs.
-		This one will be illustrated using solid lines.
-	output2 : ``str``
-		The relative or absolute path to the second of the two VICE outputs.
-		This one will be illustrated using dotted lines.
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-	times : ``list`` [elements of type ``float``]
-		[default : [2, 4, 6, 8, 10, 13.2]]
-		The times in Gyr at which to mark the positions of the [O/Fe]-[Fe/H]
-		tracks of the two models.
-	"""
-	axes = setup_axis()
-	out1 = vice.output(output1)
-	out2 = vice.output(output2)
-	plot_tracks(axes[0], out1, label = True)
-	plot_tracks(axes[0], out2, linestyle = ':')
-	plot_ticks(axes[0], out1, times, marker = markers()['x'])
-	plot_ticks(axes[0], out2, times, marker = markers()["point"])
-	plot_ia_rate_proxies(axes[1], out1)
-	plot_ia_rate_proxies(axes[1], out2, linestyle = ':')
-	leg = axes[0].legend(loc = mpl_loc("lower left"), ncol = 1, frameon = False,
[…]

### 2022-06-28 migration/src/plots/plots/utils.py

@@ -1,208 +1,0 @@
-
-import matplotlib as mpl
-from matplotlib.ticker import FormatStrFormatter as fsf
-import matplotlib.pyplot as plt
-
-
-def xticklabel_formatter(ax):
-	r"""
-	Format the x-tick labels to '%g'
-
-	Parameters
-	----------
-	ax : subplot
-		The subplot to apply the formatting to.
-	"""
-	ax.xaxis.set_major_formatter(fsf("%g"))
-
-
-def yticklabel_formatter(ax):
-	r"""
-	Format the y-tick labels to '%g'
-
-	Parameters
-	----------
-	ax : subplot
-		The subplot to apply the formatting to.
-	"""
-	ax.yaxis.set_major_formatter(fsf("%g"))
-
-
-def named_colors():
-	r"""
-	Returns
-	-------
-	colors : dict
-		A dictionary of color names to matplotlib colors
-
-	Notes
-	-----
-	This function simply wraps matplotlib.colors.get_named_colors_mapping()
-	"""
-	return mpl.colors.get_named_colors_mapping()
-
-
-def mpl_loc(label):
-	r"""
-	Parameters
-	----------
-	label : str
-		A descriptive location of a point in box
-
-		Recognized inputs:
-
-			- "best"
-			- "upper right"
-			- "upper left"
-			- "lower left"
-			- "lower right"
-			- "right"
-			- "center left"
-			- "center right"
-			- "lower center"
-			- "upper center"
-			- "center"
-
-	Returns
-	-------
-	index : int
-		The matplotlib integer index denoting the location within the box
-	"""
-	indeces = {
-		"best": 0,
-		"upper right": 1,
-		"upper left": 2,
-		"lower left": 3,
-		"lower right": 4,
-		"right": 5,
-		"center left": 6,
-		"center right": 7,
-		"lower center": 8,
-		"upper center": 9,
-		"center": 10
-	}
-
-	if label.lower() in indeces.keys():
-		return indeces[label.lower()]
-	else:
-		raise ValueError("Unrecognized location string: %s" % (label))
-
-
-def markers():
-	r"""
-	Returns a dictionary of terms to matplotlib marker characters.
-
-	Recognized markers:
-		
-		* point
-		* pixel
-		* circle
-		* triangle_down
-		* triangle_up
-		* triangle_left
-		* triangle_right
-		* tri_down
[…]

### 2022-06-28 migration/src/simulations/__init__.py

@@ -1,4 +1,0 @@
-
-__all__ = ["config", "diskmodel"]
-from .config import config
-from .disks import diskmodel

### 2022-06-28 migration/src/simulations/config.py

@@ -1,162 +1,0 @@
-r"""
-This file implements the config object, which is used to store the user's
-model parameters before creating a ``diskmodel`` object from them.
-"""
-
-from vice import ScienceWarning
-from vice import milkyway
-import warnings
-import numbers
-
-class config:
-
-	r"""
-	Stores model parameters before creation of a ``diskmodel`` object.
-
-	Parameters
-	----------
-	kwargs : varying types
-		Attributes can be initialized via keyword arguments. See below.
-
-	Attributes
-	----------
-	timestep_size : float [default : 0.01]
-		The timestep size of the model in Gyr.
-	star_particle_density : int [default : 2]
-		The number of stellar populations per zone per timestep in the model.
-	zone_width : float [default : 0.1]
-		The width of each annulus in kpc in the model. Must be positive.
-	elements : list [default : ["fe", "o"]]
-		The elements to calculate the enrichment for. Components must be of
-		type ``str`` and correspond to elements recognized by VICE.
-	bins : list [default : [-3, -2.99, -2.98, ... , 2.98, 2.99, 3.00]]
-		The bins within which to sort the dN/d[X/Y] abundance distributions
-		into.
-	"""
-
-	def __init__(self, **kwargs):
-		defaults = {
-			"timestep_size": 			0.01,
-			"star_particle_density":	2,
-			"zone_width": 				0.1,
-			"elements": 				["fe", "o"],
-			"bins": 					[-3 + 0.01 * i for i in range(601)],
-		}
-		for i in kwargs.keys(): defaults[i] = kwargs[i]
-		self.timestep_size = 			defaults["timestep_size"]
-		self.star_particle_density = 	defaults["star_particle_density"]
-		self.zone_width = 				defaults["zone_width"]
-		self.elements = 				defaults["elements"]
-		self.bins = 					defaults["bins"]
-
-	@property
-	def timestep_size(self):
-		r"""
-		Type : float
-
-		The timestep size of the simulations in Gyr.
-		"""
-		return self._timestep_size
-
-	@timestep_size.setter
-	def timestep_size(self, value):
-		if isinstance(value, numbers.Number):
-			if value > 0.05: warnings.warn("""\
-Large timestep size: %g. This may cause numerical artifacts.\
-""" % (value), ScienceWarning)
-			if value > 0:
-				self._timestep_size = value
-			else:
-				raise ValueError("Timestep size must be positive.")
-		else:
[…]

### 2022-06-28 migration/src/simulations/disks.py

@@ -1,235 +1,0 @@
-r"""
-The diskmodel objects employed in the Johnson et al. (2021) study.
-"""
-
-try:
-	ModuleNotFoundError
-except NameError:
-	ModuleNotFoundError = ImportError
-try:
-	import vice
-except (ModuleNotFoundError, ImportError):
-	raise ModuleNotFoundError("Could not import VICE.")
-if vice.version[:2] < (1, 2):
-	raise RuntimeError("""VICE version >= 1.2.0 is required to produce \
-Johnson et al. (2021) figures. Current: %s""" % (vice.__version__))
-else: pass
-from vice.toolkit import hydrodisk, J21_sf_law
-from .._globals import END_TIME, MAX_SF_RADIUS, ZONE_WIDTH
-from . import migration
-from . import models
-from .dtd import PowerLaw, BrokenPowerLaw, Exponential, Bimodal
-from .models.utils import get_bin_number, interpolate
-from .models.gradient import gradient
-import math as m
-import sys
-
-
-class diskmodel(vice.milkyway):
-
-	r"""
-	A milkyway object tuned to the Johnson et al. (2021) models specifically.
-
-	Parameters
-	----------
-	zone_width : ``float`` [default : 0.1]
-		The width of each annulus in kpc.
-	name : ``str`` [default : "diskmodel"]
-		The name of the model; the output will be stored in a directory under
-		this name with a ".vice" extension.
-	spec : ``str`` [default : "static"]
-		A keyword denoting the time-dependence of the star formation history.
-		Allowed values:
-
-		- "static"
-		- "insideout"
-		- "lateburst"
-		- "outerburst"
-		- "conroy22"
-
-	verbose : ``bool`` [default : True]
-		Whether or not the run the models with verbose output.
-	migration_mode : ``str`` [default : "diffusion"]
-		A keyword denoting the time-dependence of stellar migration.
-		Allowed values:
-
-		- "diffusion"
-		- "linear"
-		- "sudden"
-		- "post-process"
-
-	delay : ``float`` [default : 0.04]
-		Minimum SN Ia delay time in Gyr.
-	RIa : ``str`` [default : "powerlaw"]
-		A keyword denoting the time-dependence of the SN Ia rate.
-		Allowed values:
-
-		- "powerlaw"
-		- "powerlaw_steep"
-		- "exponential"
-		- "bimodal"
-
-	kwargs : varying types
[…]

### 2022-06-28 migration/src/simulations/dtd.py

@@ -1,268 +1,0 @@
-"""
-This file contains the Type Ia supernova delay time distributions and related
-functions.
-"""
-
-import math as m
-from .._globals import END_TIME
-
-class Bimodal:
-    """
-    The bimodal delay-time distribution of SNe Ia. This assumes ~50% of SNe Ia
-    belong to a prompt (<0.1 Gyr) component with the form of a narrow Gaussian,
-    and the remaining ~50% form an exponential DTD.
-
-    Attributes
-    ----------
-    prompt : <function>
-        Prompt component as a function of time.
-    tardy : <function>
-        Tardy component as a function of time.
-    norm : float
-        Normalization coefficient scaled so the total integral is unity.
-    """
-
-    def __init__(self, center=0.05, stdev=0.01, timescale=3,
-                 tmin=0.04, tsplit=0.1, tmax=END_TIME):
-        """
-        Initialize the bimodal model.
-
-        Parameters
-        ----------
-        center : float [default: 0.05]
-            Center of the prompt Gaussian component in Gyr.
-        stdev : float [default: 0.01]
-            Standard deviation of the prompt Gaussian component in Gyr.
-        timescale : float [default: 3]
-            Exponential timescale of the tardy component in Gyr.
-        tmin : float [default: 0.04]
-            Minimum delay time in Gyr for integration purposes.
-        tsplit : float [default: 0.1]
-            Time in Gyr to switch from prompt to tardy component.
-        tmax : float [default: 13.2]
-            Maximum delay time in Gyr for integration purposes.
-
-        """
-        self.prompt = Gaussian(center=center, stdev=stdev, coeff=0.5)
-        self.tardy = Exponential(timescale=timescale, coeff=0.5)
-        self.norm = 1
-        # Normalize over full time range
-        self.norm *= 1e-9 * self.normalize(tmin, tmax)
-
-    def __call__(self, time):
-        """
-        Calculate the normalized SN Ia rate at the given time.
-
-        Parameters
-        ----------
-        time : float
-            Time in Gyr since the starburst.
-
-        Returns
-        -------
-        RIa : float
-            Normalized SN Ia rate per solar mass per year.
-
-        """
-        return self.norm * (self.prompt(time) + self.tardy(time))
-
-    def normalize(self, tmin, tmax, dt=1e-3):
-        """
-        Calculate the normalization coefficient over the whole distribution.
-
-        Parameters
-        ----------
-        tmin : float
[…]

### 2022-06-28 migration/src/simulations/migration.py

@@ -1,94 +1,0 @@
-
-from vice.toolkit import hydrodisk
-
-
-class diskmigration(hydrodisk.hydrodiskstars):
-
-	r"""
-	A ``hydrodiskstars`` object which writes extra analog star particle data to
-	an output file.
-
-	Parameters
-	----------
-	radbins : array-like
-		The bins in galactocentric radius in kpc corresponding to each annulus.
-	mode : ``str`` [default : "linear"]
-		A keyword denoting the time-dependence of stellar migration.
-		Allowed values:
-
-		- "diffusion"
-		- "linear"
-		- "sudden"
-		- "post-process"
-
-	filename : ``str`` [default : "stars.out"]
-		The name of the file to write the extra star particle data to.
-
-	Attributes
-	----------
-	write : ``bool`` [default : False] 	
-		A boolean describing whether or not to write to an output file when
-		the object is called. The ``multizone`` object, and by extension the
-		``milkyway`` object, automatically switch this attribute to True at the
-		correct time to record extra data.
-	"""
-
-	def __init__(self, radbins, mode = "diffusion", filename = "stars.out",
-		**kwargs):
-		super().__init__(radbins, mode = mode, **kwargs)
-		if isinstance(filename, str):
-			self._file = open(filename, 'w')
-			self._file.write("# zone_origin\ttime_origin\tanalog_id\tzfinal\n")
-		else:
-			raise TypeError("Filename must be a string. Got: %s" % (
-				type(filename)))
-
-		# use only disk stars in these simulations
-		self.decomp_filter([1, 2])
-
-		# Multizone object automatically swaps this to True in setting up
-		# its stellar population zone histories
-		self.write = False
-
-	def __call__(self, zone, tform, time):
-		if tform == time:
-			super().__call__(zone, tform, time) # reset analog star particle
-			if self.write:
-				if self.analog_index == -1:
-					# finalz = 100
-					finalz = 0
-					analog_id = -1
-				else:
-					finalz = self.analog_data["zfinal"][self.analog_index]
-					analog_id = self.analog_data["id"][self.analog_index]
-				self._file.write("%d\t%.2f\t%d\t%.2f\n" % (zone, tform,
-					analog_id, finalz))
-			else: pass
-			return zone
-		else:
-			return super().__call__(zone, tform, time)
-
-	def close_file(self):
-		r"""
-		Closes the output file - should be called after the multizone model
-		simulation runs.
-		"""
-		self._file.close()
-
[…]

### 2022-06-28 migration/src/simulations/models/__init__.py

@@ -1,8 +1,0 @@
-
-__all__ = ["insideout", "lateburst", "outerburst", "static",
-		   "conroy22_tau_star", "insideout_conroy22"]
-from .insideout import insideout
-from .lateburst import lateburst
-from .outerburst import outerburst
-from .static import static
-from .conroy22 import conroy22_tau_star, insideout_conroy22

### 2022-06-28 migration/src/simulations/models/conroy22.py

@@ -1,80 +1,0 @@
-r"""
-This file declares the time-dependence of the star formation efficiency
-timescale from Conroy et al. (2022)
-"""
-
-from ..._globals import END_TIME
-from .normalize import normalize
-from .utils import constant, exponential
-from .gradient import gradient
-from .insideout import insideout
-import vice
-import math as m
-
-class conroy22_tau_star:
-	r"""
-	The piecewise time-dependent star formation efficiency (SFE) timescale model
-	from Conroy et al. (2022).
-
-	Parameters
-	----------
-	t1 : float, optional
-		Start time in Gyr of the gradual increase in SFE. The default is 2.5 Gyr.
-	t2 : float, optional
-		End time in Gyr of the gradual increase in SFE. The default is 3.7 Gyr.
-	slope : float, optional
-		The steepness of the increase in SFE. The default is 3.
-	tau_star_init : float, optional
-		The initial SFE timescale in Gyr. The default is 50 Gyr.
-	tau_star_final : float, optional
-		The final SFE timescale in Gyr. The default is 2.36 Gyr.
-
-	Calling
-	-------
-	- Parameters
-
-		time : float
-			Simulation time in Gyr.
-	"""
-	def __init__(self, t1 = 2.5, t2 = 3.7, slope = 3, tau_star_init = 50,
-			  tau_star_final = 2.36):
-		self.t1 = t1
-		self.t2 = t2
-		self.slope = slope
-		self.tau_star_init = tau_star_init
-		self.tau_star_final = tau_star_final
-
-	def __call__(self, time, arg2):
-		if time < self.t1:
-			return self.tau_star_init
-		elif time >= self.t1 and time <= self.t2:
-			return self.tau_star_init / ((1 + self.slope * (time - self.t1))**2)
-		else:
-			return self.tau_star_final
-
-
-class insideout_conroy22(insideout):
-	def __init__(self, radius, dt = 0.01, dr = 0.01):
-		super().__init__(radius, dt = dt, dr = dr)
-		self.norm = normalize_conroy22(self, gradient, radius, dt = dt, dr = dr)
-
-
-def normalize_conroy22(time_dependence, radial_gradient, radius, dt = 0.01,
-	dr = 0.1, recycling = 0.4):
-	"""A modified version of normalize.normalize_ifrmode()."""
-	tau_star = conroy22_tau_star()
[…]

### 2022-06-28 migration/src/simulations/models/gradient.py

@@ -1,44 +1,0 @@
-r"""
-This file declares the radial dependence of the stellar surface density at
-late times in the Johnson et al. (2021) models.
-"""
-
-import math as m
-
-_THIN_DISK_SCALE_RADIUS_ = 2.5 # kpc
-_THICK_DISK_SCALE_RADIUS_ = 2.0 # kpc
-_THICK_TO_THIN_RATIO_ = 0.27 # at r = 0
-
-
-def gradient(radius):
-	r"""
-	The gradient in stellar surface density defined in Bland-Hawthorn &
-	Gerhard (2016) [1]_.
-
-	Parameters
-	----------
-	radius : real number
-		Galactocentric radius in kpc.
-
-	Returns
-	-------
-	sigma : real number
-		The radial surface density at that radius defined by the following
-		double-exponential profile:
-
-		.. math:: \Sigma_\star(r) = e^{-r/r_t} + Ae^{-r/r_T}
-
-		where :math:`r_t` = 2.5 kpc is the scale radius of the thin disk,
-		:math:`r_T` = 2.0 kpc is the scale radius of the thick disk, and
-		:math:`A = \Sigma_T / \Sigma_t \approx` 0.27 is the ratio of thick to
-		thin disks at :math:`r = 0`.
-
-		.. note:: This gradient is un-normalized.
-
-	.. [1] Bland-Hawthorn & Gerhard (2016), ARA&A, 54, 529
-	"""
-	return (
-		m.exp(-radius / _THIN_DISK_SCALE_RADIUS_) +
-		_THICK_TO_THIN_RATIO_ * m.exp(-radius / _THICK_DISK_SCALE_RADIUS_)
-	)
-

### 2022-06-28 migration/src/simulations/models/insideout.py

@@ -1,118 +1,0 @@
-r"""
-This file declares the time-dependence of the star formation history at a
-given radius in the fiducial inside-out model from Johnson et al. (2021).
-"""
-
-from .utils import modified_exponential, get_bin_number, interpolate
-from .normalize import normalize
-from .gradient import gradient
-import math as m
-import os
-
-_TAU_RISE_ = 2.0 # Gyr
-
-
-class insideout(modified_exponential):
-
-	r"""
-	The inside-out SFH model from Johnson et al. (2021).
-
-	Parameters
-	----------
-	radius : float
-		The galactocentric radius in kpc of a given annulus in the model.
-	dt : float [default : 0.01]
-		The timestep size of the model in Gyr.
-	dr : float [default : 0.1]
-		The width of the annulus in kpc.
-
-	Functions
-	---------
-	- timescale [staticmethod]
-
-	Other atributes and functionality are inherited from
-	``modified_exponential`` declared in ``src/simulations/models/utils.py``.
-	"""
-
-	def __init__(self, radius, dt = 0.01, dr = 0.1):
-		super().__init__(timescale = insideout.timescale(radius),
-			rise = _TAU_RISE_)
-		self.norm *= normalize(self, gradient, radius, dt = dt, dr = dr)
-
-	@staticmethod
-	def timescale(radius, Re = 5):
-		r"""
-		Determine the timescale of star formation at a given radius reported
-		by Sanchez (2020) [1]_.
-
-		Parameters
-		----------
-		radius : real number
-			Galactocentric radius in kpc.
-		Re : real number [default : 5]
-			The effective radius (i.e. half-mass radius) of the galaxy in kpc.
-
-		Returns
-		-------
-		tau_sfh : real number
-			The e-folding timescale of the star formation history at that
-			radius. The detailed time-dependence on the star formation history
-			has the following form:
-
-			.. math:: \dot{M}_\star \sim
-				(1 - e^{-t / \tau_\text{rise}})e^{-t / \tau_\text{sfh}}
-
-			where :math:`\tau_\text{rise}` = 2 Gyr and :math:`\tau_\text{sfh}`
-			is the value returned by this function.
-
-		.. [1] Sanchez (2020), ARA&A, 58, 99
-		"""
-		radius /= Re # convert to units of Re
-		radii, timescales = _read_sanchez_data()
-		idx = get_bin_number(radii, radius)
-		if idx != -1:
[…]

### 2022-06-28 migration/src/simulations/models/lateburst.py

@@ -1,46 +1,0 @@
-r"""
-This file declares the time-dependence of the star formation history at a
-given radius in the lateburst model from Johnson et al. (2021).
-"""
-
-from ..._globals import END_TIME
-from .utils import modified_exponential, gaussian
-from .insideout import _TAU_RISE_, insideout
-from .normalize import normalize, normalize_ifrmode
-from .gradient import gradient
-import math as m
-import os
-
-_BURST_TIME_ = END_TIME - 2 # Gyr
-
-
-class lateburst(modified_exponential, gaussian):
-
-	r"""
-	The late-burst SFH model from Johnson et al. (2021).
-
-	Parameters
-	----------
-	radius : float
-		The galactocentric radius in kpc of a given annulus in the model.
-	dt : float [default : 0.01]
-		The timestep size of the model in Gyr.
-	dr : float [default : 0.1]
-		The width of the annulus in kpc.
-
-	All attributes and functionality are inherited from ``modified_exponential``
-	and ``gaussian`` declared in ``src/simulations/models/utils.py``.
-	"""
-
-	def __init__(self, radius, dt = 0.01, dr = 0.1):
-		modified_exponential.__init__(self,
-			timescale = insideout.timescale(radius),
-			rise = _TAU_RISE_)
-		gaussian.__init__(self, mean = _BURST_TIME_, amplitude = 1.5)
-		self._prefactor = 1
-		self._prefactor = normalize(self, gradient, radius, dt = dt, dr = dr)
-
-	def __call__(self, time):
-		return self._prefactor * modified_exponential.__call__(self, time) * (
-			1 + gaussian.__call__(self, time)
-		)

### 2022-06-28 migration/src/simulations/models/normalize.py

@@ -1,86 +1,0 @@
-r"""
-This file implements the normalization calculation in Appendix A of
-Johnson et al. (2021).
-"""
-
-from ..._globals import MAX_SF_RADIUS, END_TIME, M_STAR_MW
-import vice
-from vice.toolkit import J21_sf_law
-import math as m
-
-
-def normalize(time_dependence, radial_gradient, radius, dt = 0.01, dr = 0.5,
-	recycling = 0.4):
-	r"""
-	Determine the prefactor on the surface density of star formation as a
-	function of time as described in Appendix A of Johnson et al. (2021).
-
-	Parameters
-	----------
-	time_dependence : <function>
-		A function accepting time in Gyr and galactocentric radius in kpc, in
-		that order, specifying the time-dependence of the star formation
-		history at that radius. Return value assumed to be unitless and
-		unnormalized.
-	radial_gradient : <function>
-		A function accepting galactocentric radius in kpc specifying the
-		desired stellar radial surface density gradient at the present day.
-		Return value assumed to be unitless and unnormalized.
-	radius : real number
-		The galactocentric radius to evaluate the normalization at.
-	dt : real number [default : 0.01]
-		The timestep size in Gyr.
-	dr : real number [default : 0.5]
-		The width of each annulus in kpc.
-	recycling : real number [default : 0.4]
-		The instantaneous recycling mass fraction for a single stellar
-		population. Default is calculated for the Kroupa IMF [1]_.
-
-	Returns
-	-------
-	A : real number
-		The prefactor on the surface density of star formation at that radius
-		such that when used in simulation, the correct total stellar mass with
-		the specified radial gradient is produced.
-
-	Notes
-	-----
-	This function automatically adopts the desired maximum radius of star
-	formation, end time of the model, and total stellar mass declared in
-	``src/_globals.py``.
-
-	.. [1] Kroupa (2001), MNRAS, 322, 231
-	"""
-
-	time_integral = 0
-	for i in range(int(END_TIME / dt)):
-		time_integral += time_dependence(i * dt) * dt * 1.e9 # yr to Gyr
-
-	radial_integral = 0
-	for i in range(int(MAX_SF_RADIUS / dr)):
[…]

### 2022-06-28 migration/src/simulations/models/outerburst.py

@@ -1,47 +1,0 @@
-r"""
-This file declares the time-dependence of the star formation history at a
-given radius in the outerburst model from Johnson et al. (2021).
-"""
-
-from .lateburst import _BURST_TIME_, lateburst
-from .insideout import _TAU_RISE_, insideout
-from .normalize import normalize
-from .gradient import gradient
-import math as m
-import os
-
-_RADIUS_ = 6 # radius in kpc beyond which there is a late starburst
-
-
-class outerburst(lateburst, insideout):
-
-	r"""
-	The outer-burst SFH model from Johnson et al. (2021).
-
-	Parameters
-	----------
-	radius : float
-		The galactocentric radius in kpc of a given annulus in the model.
-	dt : float [default : 0.01]
-		The timestep size of the model in Gyr.
-	dr : float [default : 0.1]
-		The width of the annulus in kpc.
-
-	All attributes and functionality are inherited from ``lateburst`` and
-	``insideout`` declared in ``src/simulations/models/lateburst.py`` and
-	``src/simulations/models/insideout.py``.
-	"""
-
-	def __init__(self, radius, dt = 0.01, dr = 0.1):
-		self._burst = radius > _RADIUS_ # whether or not there will be a burst
-		if self._burst:
-			lateburst.__init__(self, radius, dt = dt, dr = dr)
-		else:
-			insideout.__init__(self, radius, dt = dt, dr = dr)
-
-	def __call__(self, time):
-		if self._burst:
-			return lateburst.__call__(self, time)
-		else:
-			return insideout.__call__(self, time)
-

### 2022-06-28 migration/src/simulations/models/static.py

@@ -1,33 +1,0 @@
-r"""
-This file declares the time-dependence of the star formation history at a
-given radius in the constant SFH model from Johnson et al. (2021).
-"""
-
-from .utils import constant
-from .normalize import normalize
-from .gradient import gradient
-import math as m
-import os
-
-
-class static(constant):
-
-	r"""
-	The constant SFH model from Johnson et al. (2021).
-
-	Parameters
-	----------
-	radius : float
-		The galactocentric radius in kpc of a given annulus in the model.
-	dt : float [default : 0.01]
-		The timestep size of the model in Gyr.
-	dr : float [default : 0.1]
-		The width of the annulus in kpc.
-
-	All attributes and functionality are inherited from ``constant`` declared
-	in ``src/simulations/models/utils.py``.
-	"""
-
-	def __init__(self, radius, dt = 0.01, dr = 0.1):
-		super().__init__()
-		self.amplitude *= normalize(self, gradient, radius, dt = dt, dr = dr)

### 2022-06-28 migration/src/simulations/models/utils.py

@@ -1,358 +1,0 @@
-r"""
-Utilities for the Johnson et al. (2021) models.
-
-Contents
---------
-get_bin_number : <function>
-	Obtain the bin number for a given value in an array of bin edges.
-interpolate : <function>
-	Extrapolate the value of a y-coordinate given two points (x1, y1), (x2, y2)
-	and an x-coordinate.
-constant : object
-	A callable object which always returns a specified constant.
-exponential : object
-	Exponential growth/decay.
-modified_exponential : object
-	Exponential growth/decay with a limited exponential growth prefactor.
-gaussian : object
-	A Gaussian in an arbitrary x-coordinate.
-"""
-
-import math as m
-import numbers
-
-
-def get_bin_number(bins, value):
-	r"""
-	Obtain the bin number of a given value in an array-like object of bin
-	edges.
-
-	Parameters
-	----------
-	bins : array-like
-		The bin-edges themselves. Assumed to be sorted from least to greatest.
-	value : real number
-		The value to obtain the bin number for.
-
-	Returns
-	-------
-	x : int
-		The bin number of ``value`` in the array ``bins``. -1 if the value
-		lies outside the extent of the bins.
-	"""
-	for i in range(len(bins) - 1):
-		if bins[i] <= value <= bins[i + 1]: return i
-	return -1
-
-
-def interpolate(x1, y1, x2, y2, x):
-	r"""
-	Extrapolate a y-coordinate for a given x-coordinate from a line defined
-	by two points (x1, y1) and (x2, y2) in arbitrary units.
-
-	Parameters
-	----------
-	x1 : real number
-		The x-coordinate of the first point.
-	y1 : real number
-		The y-coordinate of the first point.
-	x2 : real number
-		The x-coordinate of the second point.
-	y2 : real number
-		The y-coordinate of the second point.
-	x : real number
-		The x-coordinate to extrapolate a y-coordinate for.
-
-	Returns
-	-------
-	y : real number
-		The y-coordinate such that the point (x, y) lies on the line defined
-		by the points (x1, y1) and (x2, y2).
-	"""
-	return (y2 - y1) / (x2 - x1) * (x - x1) + y1
-
-
-class constant:
-
-	r"""
-	Generic constant with a generic x-coordinate.
-
-	Parameters
-	----------
-	amplitude : real number [default : 1]
-		The attribute ``amplitude``, initialize via keyword argument. See
-		below.
-
-	Attributes
-	----------
-	amplitude : real number [default : 1]
[…]

### 2022-06-28 migration/src/simulations/yields/C22.py

@@ -1,9 +1,0 @@
-
-import vice
-
-vice.yields.ccsne.settings["o"] = 0.0207
-vice.yields.ccsne.settings["mg"] = 0.0026
-vice.yields.ccsne.settings["fe"] = 0.0012
-vice.yields.sneia.settings["o"] = 0
-vice.yields.sneia.settings["mg"] = 0
-vice.yields.sneia.settings["fe"] = 0.003

### 2022-07-12 src/scripts/track_and_mdf.py
update documentation

@@ -7,11 +7,9 @@ import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib.ticker import MultipleLocator
 
-def main():
-    pass
 
-
-def plot_vice_onezone(output, **kwargs):
+def plot_vice_onezone(output, fig=None, axs=[], style_kw={}, plot_kw={},
+                      hist_kw={'histtype': 'step'}):
     """
     Wrapper for plot_track_and_mdf given a VICE onezone output.
 
@@ -19,11 +17,26 @@ def plot_vice_onezone(output, **kwargs):
     ----------
     output : str
         Path to VICE output, not necessarily including the '.vice' extension
-    **kwargs passed to plot_track_and_mdf
+    fig : instance of matplotlib.figure.figure, optional
+        If no figure is provided, one is generated from setup_axes
+    axs : list of matplotlib.axes.Axes
+        There should be three axes: the first for the main [Fe/H] vs [O/Fe]
+        panel, the second for the MDF in [Fe/H], and the third for the MDF
+        in [O/Fe]
+    style_kw : dict, optional
+        Dict of style-related keyword arguments to pass to both
+        matplotlib.pyplot.plot and matplotlib.pyplot.hist
+    plot_kw : dict, optional
+        Dict of style-related keyword arguments to pass to
+        matplotlib.pyplot.plot
+    hist_kw : dict, optional
+        Dict of style-related keyword arguments to pass to
+        matplotlib.pyplot.plot
 
     Returns
     -------
-    fig, ax
+    fig : matplotlib.figure.Figure
+    axs : list of matplotlib.axes.Axes
     """
     import vice
     hist = vice.history(output)
@@ -32,7 +45,8 @@ def plot_vice_onezone(output, **kwargs):
     fig, axs = plot_track_and_mdf(hist['[fe/h]'], hist['[o/fe]'],
                                   dn_dfeh=mdf['dn/d[fe/h]'], feh_bins=mdf_bins,
                                   dn_dofe=mdf['dn/d[o/fe]'], ofe_bins=mdf_bins,
-                                  **kwargs)
+                                  fig=fig, axs=axs, style_kw=style_kw,
+                                  plot_kw=plot_kw, hist_kw=hist_kw)
     return fig, axs
 
 
[…]

### 2022-07-12 src/tex/ms.tex
migrate to showyourwork v0.3.0
line endings
[showyourwork] dummy change
[showyourwork] overleaf sync
Add missing \script{} command
Need to add \script{} now within figure environments for showyourwork to run the figure script.
[showyourwork] resolve overleaf conflict

--- 2022-06-06 src/ms.tex
@@
 
-% Filler text
-\usepackage{blindtext}
+% showyourwork!
+\usepackage{showyourwork}
 
@@
 % Author list
-\author[0000-0000-0000-0000]{First Author}
+\author[0000-0003-3781-0747]{Liam O. Dubay}
 
@@
 \begin{abstract}
-    \blindtext
+    Abstract.
 \end{abstract}
@@
 \section{Introduction}
-\Blindtext[4]
 
 \section{Methods}
+\label{sec:methods}
 
 \subsection{Accuracy of astroNN}
+\label{subsec:astronn-quality}
 
@@
 \subsection{Measurements of the Type Ia Supernova Delay Time Distribution}
+\label{subsec:dtd-measurements}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/delay_time_distributions.pdf}
+    \caption{Delay time distribution functions}
+    \label{fig:dtds}
+    \script{delay_time_distributions.py}
+\end{figure}
 
@@
 
+\section{Results}
+\label{sec:results}
+
+\subsection{One-Zone Models}
+\label{subsec:onezone-results}
+
+\subsubsection{The SN Ia Delay-Time Distribution}
+
+Adjusting the parameters of the DTD affects how steeply the abundance track in [Fe/H]-[O/Fe] space falls from its initial ``plateau'' and the location of the ``knee.'' Figure \ref{fig:onezone-slope-timescale} shows abundance tracks from one-zone models which assume different slopes of a power-law DTD or different timescales of an exponential DTD.
+A steeper power-law slope results in a steeper decline in [O/Fe] and a lower knee, as does a shorter exponential timescale.
+The consequence is that a very shallow power-law produces similar observable signatures to a very steep exponential, which suggests these models may be difficult to distinguish in this parameter space.
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_slope_timescale.pdf}
+    \caption{\textit{Center:} Abundance tracks in the [Fe/H]-[O/Fe] plane for one-zone models with various DTD parameters.
+Tracks from models which assume a power-law DTD are in black, with dotted, dashed, and solid curves representing power-law slopes ($\alpha$) of $-0.8$, $-1.1$, and $-1.4$, respectively.
+Tracks from models which assume an exponential DTD are in purple, with dotted, dashed, and solid curves representing exponential decay timescales ($\tau$) of 1.5 Gyr, 3 Gyr, and 6 Gyr, respectively.
+\textit{Top:} MDFs generated from by one-zone models.
+\textit{Right:} Distribution of [O/Fe] generated by the one-zone models.}
+    \label{fig:onezone-slope-timescale}
+    \script{onezone_slope_timescacle.py}
+\end{figure}
+
+\subsubsection{The Minimum SN Ia Delay Time}
+
+Figure \ref{fig:onezone-dtd-delay} shows that the minimum SN Ia delay time has a much stronger effect on the abundance track and MDFs of models which assume a power-law DTD than models which assume an exponential, due to the much higher SN Ia rate in the power-law models at early times (see Figure \ref{fig:dtds}).
+Moreover, a power-law DTD with a long minimum delay may be observationally hard to distinguish from an exponential.
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_dtd_delay.pdf}
+    \caption{Similar to Figure \ref{fig:onezone-slope-timescale} but with varying minimum SN Ia delay time ($t_D$).
+Dashed curves represent models with a minimum delay time of 40 Myr, while solid curves represent models with a minimum delay time of 150 Myr.
+The black curves represent a power-law DTD with a slope of $-1.1$, while the purple curves represent an exponential DTD with a timescale of 1.5 Gyr.}
+    \label{fig:onezone-dtd-delay}
+    \script{onezone_dtd_delay.py}
+\end{figure}
+
+\subsubsection{The Star Formation History}
+
+Figure \ref{fig:onezone-delay-taustar} shows results from one-zone models with a power-law DTD which differ in their assumed minimum SN Ia delay time ($t_D$) or star formation efficiency timescale ($\tau_*$).
+In [Fe/H]-[O/Fe] space, doubling or halving the minimum delay time produces similar results to doubling or halving the SFE timescale.
+A shorter minimum delay time means SNe Ia will start to explode sooner after the star formation burst, giving less time for CCSNe to explode at the plateau of the abundance track.
+Similarly, a longer SFE timescale means fewer massive stars will be produced by the initial star formation burst, resulting in fewer CCSNe before the first SNe Ia explode.
+
+These parameters have similar effects on the abundance tracks but very different effects on the MDFs.
+Altering the SFE timescale changes the stellar distribution of [Fe/H], especially at the low-metallicity end, as shown in the top panel of Figure \ref{fig:onezone-delay-taustar}.
+However, as a change in the SFE timescale affects both the number of high-mass and low-mass stars produced, it does not affect the distribution of [O/Fe], as shown in the right-hand panel of Figure \ref{fig:onezone-delay-taustar}.
+Meanwhile, a change in the minimum SN Ia delay time does not impact the total number of SNe which explode, so the distribution of [Fe/H] is largely unaffected, while it does result in a change in the number of high-$\alpha$ stars formed and therefore the distribution of [O/Fe].
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_delay_taustar.pdf}
+    \caption{Similar to Figure \ref{fig:onezone-slope-timescale} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\tau_*$).
+Tracks with $\tau_*=2$ Gyr are represented in black, while a track with a shorter $\tau_*=1$ Gyr is shown in red and a track with a longer $\tau_*=4$ Gyr is in yellow.
+The dotted, solid, and dashed black curves represent a minimum delay time of 40 Myr, 80 Myr, and 160 Myr, respectively.
+A power-law DTD is assumed in all models.}
+    \label{fig:onezone-delay-taustar}
+    \script{onezone_delay_taustar.py}
+\end{figure}
+
+\pagebreak
+
 \bibliography{bib}

### 2022-07-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Tracks from models which assume an exponential DTD are in purple, with dotted, dashed, and solid curves representing exponential decay timescales ($\tau$) of 1.5 Gyr, 3 Gyr, and 6 Gyr, respectively.
+In all cases a minimum delay time of 40 Myr is assumed.
 \textit{Top:} MDFs generated from by one-zone models.
@@
     \label{fig:onezone-slope-timescale}
-    \script{onezone_slope_timescacle.py}
+    \script{onezone_slope_timescale.py}
+\end{figure}
+
+Figure \ref{fig:onezone-dtd} compares the one-zone model outputs from the full range of DTDs we investigate in this paper.
+In general, the choice of DTD has the greatest effect on the location of the knee in [Fe/H]-[O/Fe] space (center panel) and the high-$\alpha$ end of the distribution of [O/Fe] (right panel).
+The DTD also has a smaller effect on the MDF in the range $-15.5\lesssim$ [Fe/H] $\lesssim-0.5$ (top panel).
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_dtd.pdf}
+    \caption{Similar to Figure \ref{fig:onezone-slope-timescale} but with a different selection of DTDs. In all cases a minimum delay time of 40 Myr is assumed.}
+    \label{fig:onezone-dtd}
+    \script{onezone_dtd.py}
 \end{figure}
@@
 
-These parameters have similar effects on the abundance tracks but very different effects on the MDFs.
+The minimum delay and SFE timescale have similar effects on the abundance tracks but very different effects on the MDFs.
 Altering the SFE timescale changes the stellar distribution of [Fe/H], especially at the low-metallicity end, as shown in the top panel of Figure \ref{fig:onezone-delay-taustar}.
@@
 
-\pagebreak
-
 \bibliography{bib}

### 2022-08-10 src/scripts/greggio05_dtd.py
minor edits

@@ -28,7 +28,7 @@ def main(dt=DT, nsamples=NSAMPLES, verbose=True):
     sd_arr = np.array([sd(t) for t in tarr])
     ax.plot(tarr * 1e9, sd_arr,
             color=paultol.muted.colors[0], linestyle='-', linewidth=1,
-            label='Single Degenerate' )
+            label='Single Degenerate Chandrasekhar' )
     if verbose:
         print('Done!')
         
@@ -82,7 +82,7 @@ def main(dt=DT, nsamples=NSAMPLES, verbose=True):
     ax.set_ylim((2e-12, 2e-9))
     ax.legend(loc='lower center', fontsize=7, handlelength=1.2, frameon=False)
 
-    fig.savefig(paths.figures / 'greggio05.pdf', dpi=300)
+    fig.savefig(paths.figures / 'greggio05_dtd.pdf', dpi=300)
 
 if __name__ == '__main__':
     main()

### 2022-08-10 src/scripts/onezone_greggio05.py

@@ -29,14 +29,14 @@ STANDARD_PARAMS = dict(
     delay=0.04,
     tau_star=2.,
 )
+LOG_MDF = False
 
 def main(overwrite=False):
     output_dir = paths.data / 'onezone' / 'greggio05'
     if not output_dir.exists():
         output_dir.mkdir(parents=True)
 
-    fig, axs = setup_axes()
-
+    fig, axs = setup_axes(logmdf=LOG_MDF)
 
     simtime = np.arange(0, END_TIME + DT, DT)
 
@@ -53,6 +53,7 @@ def main(overwrite=False):
                            'linestyle': '-',
                            'linewidth': 1,
                            'zorder': 10},
+                      logmdf=LOG_MDF
                       )
     
     # Double-degenerate CLOSE model
@@ -67,6 +68,7 @@ def main(overwrite=False):
                            'linestyle': '-',
                            'linewidth': 1,
                            'zorder': 9},
+                      logmdf=LOG_MDF
                       )
 
     # Single-degenerate
@@ -77,37 +79,70 @@ def main(overwrite=False):
     plot_vice_onezone(str(output_dir / dtd.name), fig=fig, axs=axs,
                       label='Single Degenerate',
                       color=paultol.muted.colors[0],
-                       style_kw={
-                           'linestyle': '-',
-                           'linewidth': 1,
-                           'zorder': 8},
+                      style_kw={
+                          'linestyle': '-',
+                          'linewidth': 1,
+                          'zorder': 8},
+                      logmdf=LOG_MDF
                       )
 
-    dtd = dtds.exponential(timescale=3)
+    # dtd = dtds.exponential(timescale=3)
+    # sz = vice.singlezone(name=str(output_dir / dtd.name), 
+    #                      RIa=dtd, **STANDARD_PARAMS)
+    # sz.run(simtime, overwrite=True)
+    # plot_vice_onezone(str(output_dir / dtd.name), fig=fig, axs=axs,
+    #                   label=r'Exponential ($\tau=3$ Gyr)',
+    #                   color=paultol.muted.colors[7],
+    #                   style_kw={
+    #                         'linestyle': '--',
+    #                         'linewidth': 1,
+    #                         'zorder': 1,
+    #                   },
+    #                   logmdf=False)
+    
+    dtd = dtds.plateau(width=1, slope=-1.1)
     sz = vice.singlezone(name=str(output_dir / dtd.name), 
                          RIa=dtd, **STANDARD_PARAMS)
[…]

### 2022-08-10 src/scripts/onezone_plateau.py

@@ -36,6 +36,7 @@ STANDARD_PARAMS = dict(
 
 # Plot settings
 LINE_STYLE = [':', '-.', '--', '-']
+LOG_MDF = True
 
 def main(overwrite=False):
     output_dir = paths.data / 'onezone' / 'plateau'
@@ -44,7 +45,7 @@ def main(overwrite=False):
 
     simtime = np.arange(0, END_TIME + DT, DT)
 
-    fig, axs = setup_axes()
+    fig, axs = setup_axes(logmdf=LOG_MDF)
 
     # Plot standard power-law for reference
     dist = dtds.powerlaw(slope=SLOPE, tmin=DELAY)
@@ -56,6 +57,7 @@ def main(overwrite=False):
                       style_kw={'linestyle': '-',
                                 'linewidth': 1,
                                 'zorder': 1},
+                      logmdf=LOG_MDF
                       )
 
     for i, plateau in enumerate(PLATEAUS):
@@ -75,6 +77,7 @@ def main(overwrite=False):
                               'linestyle': LINE_STYLE[i],
                               'linewidth': 1,
                               'zorder': 10},
+                          logmdf=LOG_MDF
                           )
 
     # Plot exponentials for reference
@@ -91,6 +94,7 @@ def main(overwrite=False):
                                     'linewidth': 1.5,
                                     'zorder': 1},
                           marker_labels=(tau==3),
+                          logmdf=LOG_MDF
                           )
 
     # Adjust axis limits

### 2022-08-10 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-% showyourwork!
 \usepackage{showyourwork}
+\usepackage{amsmath}
+\usepackage{siunitx}
 
-% Units in equations
-% \usepackage{siunitx}
+% custom unit definitions
+\DeclareSIUnit\year{yr}
 
@@
 % Title
-\title{An open source scientific article}
+\title{The Galactic Delay-Time Distribution of Type Ia Supernovae:\\
+    A Chemical Evolution Perspective}
 
@@
 \author[0000-0003-3781-0747]{Liam O. Dubay}
+\author[0000-0001-7258-1834]{Jennifer A. Johnson}
+\author[0000-0002-6534-8783]{James W. Johnson}
+% \author[0000-0001-7775-7261]{David H. Weinberg}
 
@@
 Tracks from models which assume a power-law DTD are in black, with dotted, dashed, and solid curves representing power-law slopes ($\alpha$) of $-0.8$, $-1.1$, and $-1.4$, respectively.
-Tracks from models which assume an exponential DTD are in purple, with dotted, dashed, and solid curves representing exponential decay timescales ($\tau$) of 1.5 Gyr, 3 Gyr, and 6 Gyr, respectively.
+Tracks from models which assume an exponential DTD are in blue, with dotted, dashed, and solid curves representing exponential decay timescales ($\tau$) of 1.5 Gyr, 3 Gyr, and 6 Gyr, respectively.
 In all cases a minimum delay time of 40 Myr is assumed.
@@
 Dashed curves represent models with a minimum delay time of 40 Myr, while solid curves represent models with a minimum delay time of 150 Myr.
-The black curves represent a power-law DTD with a slope of $-1.1$, while the purple curves represent an exponential DTD with a timescale of 1.5 Gyr.}
+The black curves represent a power-law DTD with a slope of $-1.1$, while the blue curves represent an exponential DTD with a timescale of 1.5 Gyr.}
     \label{fig:onezone-dtd-delay}
@@
 
+\subsubsection{Analytical Formulations}
+
+\citet{Greggio2005-AnalyticalRates} derives analytical DTDs for SD and DD progenitor systems from assumptions about binary stellar evolution and outcomes of mass exchange.
+They find that the parameters which have a large effect on the shape of the DTD are the distribution and range of stellar masses in progenitor systems; the efficiency of accretion in the SD scenario; and the distribution of separations at birth in the DD scenario.
+Figure \ref{fig:greggio05-dtd} shows the analytical DTDs for SD progenitors and two different prescriptions for DD progenitors (``WIDE'' and ``CLOSE'').
+In the ``WIDE'' scheme, it is assumed that there is a wide distribution of ratios $A/A_0$ of the separation of the DD system to the initial separation of the binary, and that the distributions of $A$ and total mass of the system $m_{\rm{DD}}$ are independent, so one cannot necessarily predict the total merge time of a system based on its initial parameters.
+In the ``CLOSE'' scheme, there is assumed to be a narrow distribution of $A/A_0$ and a correlation between $A$ and $m_{\rm{DD}}$, so the most massive binaries tend to merge quickly and the least massive merge last.
+
+An implementation of these DTDs in a chemical evolution model requires numerical integration (see their Equations 14, 33, and 34, respectively, for the exact functional forms), so to save on computation time we approximate the DTD for the DD prescriptions as a broken power-law with an exponential rise and tail:
+
+\begin{equation}
+    f_{\rm{Ia}}^{\rm{DD}}(t) \propto
+    \begin{cases}
+        t^{\alpha_1} (1 - A_{\rm{rise}} e^{-t/\tau_{\rm{rise}}}) & t \le \SI{1}{\giga\year} \\
+        B t^{\alpha_2} (1 + A_{\rm{tail}} e^{-(t - \SI{1}{\giga\year})/\tau_{\rm{tail}}}) & t > \SI{1}{\giga\year}
+    \end{cases}
+    \label{eq:greggio05-approx}
+\end{equation}
+
+\noindent with the normalization $B$ of the second part set such that
+
+\begin{equation}
+    B = \frac{1}{1 + A_{\rm{tail}}} t^{(\alpha_1-\alpha_2)} (1 - A_{\rm{rise}} e^{-(\SI{1}{\giga\year})/\tau_{\rm{rise}}}).
+\end{equation}
+
+\noindent We use a non-linear least squares method to fit Equation \ref{eq:greggio05-approx} to the analytical DTDs for DD progenitors.
+We obtain best-fit parameters $\alpha_1=-0.19$, $A_{\rm{rise}}=1.7$, $\tau_{\rm{rise}}=0.084$ Gyr, $\alpha_2=-0.91$, $A_{\rm{tail}}=0.85$, and $\tau_{\rm{tail}}=0.088$ Gyr for the ``WIDE'' scheme, and $\alpha_1=-0.53$, $A_{\rm{rise}}=3.0$, $\tau_{\rm{rise}}=0.042$ Gyr, $\alpha_2=-1.1$, $A_{\rm{tail}}=0.62$, and $\tau_{\rm{tail}}=0.11$ Gyr for the ``CLOSE'' scheme.
+These best-fit approximations are represented by the dashed curves in Figure \ref{fig:greggio05-dtd}.
+The difference between the true analytical DTDs and our best-fit approximations is small enough as to be irrelevant for our purposes, so for the rest of this section we rely on the best-fit approximations for faster simulations.
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/greggio05_dtd.pdf}
+    \caption{Analytical DTDs computed by \citet{Greggio2005-AnalyticalRates}.}
+    \label{fig:greggio05-dtd}
+    \script{greggio05_dtd.py}
+\end{figure}
+
+Figure \ref{fig:onezone-greggio05} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs.
+We assume $\eta=2.5$, $\tau_*=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
+We compare the SD, DD WIDE, and DD CLOSE schemes to standard power-law and exponential DTDs.
+The SD and DD CLOSE DTDs follow nearly identical tracks in [O/Fe] vs [Fe/H] to an exponential DTD with a 1.5 Gyr timescale.
+The DD WIDE DTD likewise follows a similar track to a 3 Gyr exponential.
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_greggio05.pdf}
+    \caption{Caption}
+    \label{fig:onezone-greggio05}
+    \script{onezone_greggio05.py}
+\end{figure}
+
 \bibliography{bib}

### 2022-08-10 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{amsmath}
-\usepackage{siunitx}
+% \usepackage{siunitx}
 
 % custom unit definitions
-\DeclareSIUnit\year{yr}
+% \DeclareSIUnit\year{yr}
 
@@
 Galaxy Cluster Power-Law    & t^{-1.4}              & \citet{Maoz2017-CosmicDTD} \\
-Short Exponential           & e^{-t/1.5\,\rm{Gyr}}  & \citet{Schonrich2009-RadialMixing} \\
+Short Exponential           & e^{-t/1.5~\rm{Gyr}}  & \citet{Schonrich2009-RadialMixing} \\
 \enddata
@@
     \begin{cases}
-        t^{\alpha_1} (1 - A_{\rm{rise}} e^{-t/\tau_{\rm{rise}}}) & t \le \SI{1}{\giga\year} \\
-        B t^{\alpha_2} (1 + A_{\rm{tail}} e^{-(t - \SI{1}{\giga\year})/\tau_{\rm{tail}}}) & t > \SI{1}{\giga\year}
+        t^{\alpha_1} (1 - A_{\rm{rise}} e^{-t/\tau_{\rm{rise}}}) & t \le 1~\rm{Gyr} \\
+        B t^{\alpha_2} (1 + A_{\rm{tail}} e^{-(t - 1~\rm{Gyr})/\tau_{\rm{tail}}}) & t > 1~\rm{Gyr}
     \end{cases}
@@
 \begin{equation}
-    B = \frac{1}{1 + A_{\rm{tail}}} t^{(\alpha_1-\alpha_2)} (1 - A_{\rm{rise}} e^{-(\SI{1}{\giga\year})/\tau_{\rm{rise}}}).
+    B = \frac{1}{1 + A_{\rm{tail}}} t^{(\alpha_1-\alpha_2)} (1 - A_{\rm{rise}} e^{-(1~\rm{Gyr})/\tau_{\rm{rise}}}).
 \end{equation}

### 2022-08-15 migration/src/simulations/dtds/plateau.py
plot tweaks

@@ -12,7 +12,7 @@ class plateau(broken_powerlaw):
     followed by a declining power-law.
     """
     def __init__(self, width=0.2, slope=-1.1, tmin=0.04, tmax=END_TIME):
-        super().__init__(tsplit=width, slope1=0, slope2=slope, tmin=tmin,
+        super().__init__(tsplit=width+tmin, slope1=0, slope2=slope, tmin=tmin,
                          tmax=tmax)
         self._name = 'plateau_width{:03d}_slope{:02d}'.format(
             int(width * 1000), int(abs(slope) * 10))

### 2022-08-15 src/scripts/delay_time_distributions.py

@@ -10,52 +10,54 @@ from migration.src.simulations import dtds
 from colormaps import paultol
 plt.rcParams['axes.prop_cycle'] = plt.cycler('color', paultol.bright.colors)
 
+DELAY = 0.04 # minimum Ia delay timie in Gyr
+
 class styles:
     plaw = {
-        'name': 'powerlaw',
-        'func': dtds.powerlaw(),
+        'func': dtds.powerlaw(slope=-1.1, tmin=DELAY),
         'label': r'Power-Law ($\alpha=-1.1$)',
         'color': 'k',
         'line': '-',
     }
     plaw_steep = {
-        'name': 'powerlaw_steep',
-        'func': dtds.powerlaw(slope=-1.4),
+        'func': dtds.powerlaw(slope=-1.4, tmin=DELAY),
         'label': r'Power-Law ($\alpha=-1.4$)',
         'color': paultol.bright.colors[5],
         'line': '--',
     }
-    plaw_broken = {
-        'name': 'powerlaw_broken',
-        'func': dtds.powerlaw_broken(),
-        'label': 'Broken Power-Law',
+    plateau = {
+        'func': dtds.plateau(width=0.3, slope=-1.1, tmin=DELAY),
+        'label': r'Plateau ($W=300$ Myr)',
         'color': paultol.bright.colors[1],
+        'line': ':',
+    }
+    plateau_long = {
+        'func': dtds.plateau(width=1., slope=-1.1, tmin=DELAY),
+        'label': r'Plateau ($W=1$ Gyr)',
+        'color': paultol.bright.colors[3],
         'line': '-.',
     }
     exp = {
-        'name': 'exponential',
-        'func': dtds.exponential(),
+        'func': dtds.exponential(timescale=1.5, tmin=DELAY),
         'label': r'Exponential ($\tau=1.5$ Gyr)',
         'color': paultol.bright.colors[4],
         'line': '--',
     }
     exp_long = {
-        'name': 'exponential_long',
-        'func': dtds.exponential(timescale=3),
+        'func': dtds.exponential(timescale=3, tmin=DELAY),
         'label': r'Exponential ($\tau=3$ Gyr)',
         'color': paultol.bright.colors[0],
         'line': '-',
     }
-    bimodal = {
-        'name': 'bimodal',
-        'func': dtds.bimodal(),
-        'label': 'Bimodal',
+    prompt = {
[…]

### 2022-08-15 src/scripts/onezone_greggio05_double.py

@@ -86,12 +86,12 @@ def main(overwrite=False):
                       logmdf=LOG_MDF
                       )
     
-    dtd = dtds.plateau(width=0.35, slope=-1.1)
+    dtd = dtds.plateau(width=0.3, slope=-1.1)
     sz = vice.singlezone(name=str(output_dir / dtd.name), 
                           RIa=dtd, **STANDARD_PARAMS)
     sz.run(simtime, overwrite=True)
     plot_vice_onezone(str(output_dir / dtd.name), fig=fig, axs=axs,
-                      label=r'Plateau ($W=350$ Myr, $\alpha=-1.1$)',
+                      label=r'Plateau ($W=300$ Myr, $\alpha=-1.1$)',
                       color=paultol.muted.colors[7],
                       style_kw={
                             'linestyle': '--',

### 2022-08-15 src/scripts/onezone_plateau.py

@@ -19,7 +19,7 @@ from track_and_mdf import setup_axes, plot_vice_onezone
 from utils import run_singlezone
 
 # VICE one-zone model settings
-PLATEAUS = [0.1, 0.2, 0.5, 1.] # Gyr
+PLATEAUS = [0.1, 0.3, 1.] # Gyr
 DELAY = 0.04 # minimum delay time in Gyr
 DT = 0.01
 SLOPE = -1.1
@@ -35,8 +35,8 @@ STANDARD_PARAMS = dict(
 )
 
 # Plot settings
-LINE_STYLE = [':', '-.', '--', '-']
-LOG_MDF = True
+LINE_STYLE = [':', '-.', '-']
+LOG_MDF = False
 
 def main(overwrite=False):
     output_dir = paths.data / 'onezone' / 'plateau'

### 2022-08-15 src/scripts/onezone_prompt.py

@@ -25,7 +25,7 @@ plt.rcParams['axes.prop_cycle'] = plt.cycler('color', paultol.bright.colors)
 PEAKS = [0.5, 0.2, 0.1, 0.05]
 # PEAKS = [0.5, 0.5, 0.5, 0.5]
 # WIDTHS = [0.1, 0.04, 0.02, 0.01]
-WIDTHS = [0.01, 0.01, 0.01, 0.01]
+WIDTHS = [0.15, 0.06, 0.03, 0.015]
 TIMESCALE = 3 # Exponential timescale in Gyr
 DT = 0.01
 DELAY = 0.04

### 2022-08-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{amsmath}
+\usepackage{layouts}
 % \usepackage{siunitx}
@@
 \subsection{Accuracy of astroNN}
-\label{subsec:astronn-quality}
+\label{sec:astronn-quality}
 
@@
 \subsection{Measurements of the Type Ia Supernova Delay Time Distribution}
-\label{subsec:dtd-measurements}
+\label{sec:dtd-measurements}
 
@@
 \subsection{One-Zone Models}
-\label{subsec:onezone-results}
+\label{sec:onezone-results}
+
+All models are run for a duration of 13.2 Gyr with a simulation timestep of 0.01 Gyr.
 
@@
 A steeper power-law slope results in a steeper decline in [O/Fe] and a lower knee, as does a shorter exponential timescale.
-The consequence is that a very shallow power-law produces similar observable signatures to a very steep exponential, which suggests these models may be difficult to distinguish in this parameter space.
+The consequence is that a very shallow power-law produces a similar abundance track to a very steep exponential, which suggests these models may be difficult to distinguish in this parameter space.
+However, these cases can be distinguished by their MDFs and [O/Fe] distributions, where the power-law DTD produces a narrower, less skewed distribution while the exponential DTD produces a broader, more skewed distribution.
+In the [O/Fe] distribution especially, an exponential DTD with a 6 Gyr timescale produces a large number of high-$\alpha$ stars.
 
@@
 In all cases a minimum delay time of 40 Myr is assumed.
-\textit{Top:} MDFs generated from by one-zone models.
+\textit{Top:} MDFs generated by the one-zone models.
 \textit{Right:} Distribution of [O/Fe] generated by the one-zone models.}
@@
 \noindent We use a non-linear least squares method to fit Equation \ref{eq:greggio05-approx} to the analytical DTDs for DD progenitors.
-We obtain best-fit parameters $\alpha_1=-0.19$, $A_{\rm{rise}}=1.7$, $\tau_{\rm{rise}}=0.084$ Gyr, $\alpha_2=-0.91$, $A_{\rm{tail}}=0.85$, and $\tau_{\rm{tail}}=0.088$ Gyr for the ``WIDE'' scheme, and $\alpha_1=-0.53$, $A_{\rm{rise}}=3.0$, $\tau_{\rm{rise}}=0.042$ Gyr, $\alpha_2=-1.1$, $A_{\rm{tail}}=0.62$, and $\tau_{\rm{tail}}=0.11$ Gyr for the ``CLOSE'' scheme.
-These best-fit approximations are represented by the dashed curves in Figure \ref{fig:greggio05-dtd}.
+We obtain best-fit parameters $\alpha_1=-0.19$, $A_{\rm{rise}}=1.7$, $\tau_{\rm{rise}}=0.084$ Gyr, $\alpha_2=-0.91$, $A_{\rm{tail}}=0.85$, and $\tau_{\rm{tail}}=0.088$ Gyr for the ``WIDE'' scheme, and $\alpha_1=-0.53$, $A_{\rm{rise}}=3.0$, $\tau_{\rm{rise}}=0.042$ Gyr, $\alpha_2=-1.1$, $A_{\rm{tail}}=0.62$, and $\tau_{\rm{tail}}=0.11$ Gyr for the ``CLOSE'' scheme.\footnote{
+Our implementation of these best-fit approximations, as well as the original SD and DD formulations, is available in the GitHub repository for this paper.
+} These best-fit approximations are represented by the dashed curves in Figure \ref{fig:greggio05-dtd} \citep[see also Figure 8 in][]{Greggio2005-AnalyticalRates}.
 The difference between the true analytical DTDs and our best-fit approximations is small enough as to be irrelevant for our purposes, so for the rest of this section we rely on the best-fit approximations for faster simulations.
@@
     \includegraphics{figures/greggio05_dtd.pdf}
-    \caption{Analytical DTDs computed by \citet{Greggio2005-AnalyticalRates}.}
+    \caption{Analytical DTDs computed by \citet{Greggio2005-AnalyticalRates}.
+The solid red curve represents the SD DTD for Chandrasekhar explosions, while the green and blue solid curves represent, respectively, the CLOSE and WIDE formulations of a DD DTD.
+The best-fit approximations for the DD DTDs (see Equation \ref{eq:greggio05-approx}) are represented by the dashed olive and cyan curves, respectively.
+All DTDs are normalized to unity.}
     \label{fig:greggio05-dtd}
@@
 We assume $\eta=2.5$, $\tau_*=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
-We compare the SD, DD WIDE, and DD CLOSE schemes to standard power-law and exponential DTDs.
-The SD and DD CLOSE DTDs follow nearly identical tracks in [O/Fe] vs [Fe/H] to an exponential DTD with a 1.5 Gyr timescale.
-The DD WIDE DTD likewise follows a similar track to a 3 Gyr exponential.
+We compare the SD, DD WIDE, and DD CLOSE schemes to standard power-law, broken power-law, and exponential DTDs.
+The SD and DD CLOSE DTDs follow nearly identical tracks in [O/Fe] vs [Fe/H]; however, their distributions on [O/Fe] differ at the low end.
+The SD DTD follows an exponential with a 1.5 Gyr timescale, whereas the DD CLOSE DTD is well-approximated by a broken power-law with an initial plateau of 350 Myr and a subsequent declining slope of -1.1.
+The WIDE prescription is likewise best approximated by a broken power-law, but with a longer plateau width of 1 Gyr.
+In all cases, the difference between the analytical DTD and the nearest broken power-law or exponential is likely too small to be observationally detectable, so in our multi-zone models we implement the more generic functions in lieu of the analytical DTDs.
 
-\begin{figure}
+A multi-zone with the \citet{Greggio2005-AnalyticalRates} SD DTD produced nearly identical results to an exponential DTD with a 1.5 Gyr timescale.
+
+\begin{figure*}
     \centering
-    \includegraphics{figures/onezone_greggio05.pdf}
-    \caption{Caption}
+    \includegraphics{figures/onezone_greggio05_single.pdf}
+    \includegraphics{figures/onezone_greggio05_double.pdf}
+    \caption{Abundance tracks and distributions from one-zone models with the analytical DTDs from \citet{Greggio2005-AnalyticalRates}.
+\textit{Left:} a comparison between the analytical SD DTD (solid curve), an exponential DTD with a 1.5 Gyr timescale (dashed curve), and a power-law DTD with a slope of -1.1 (dotted curve).
+\textit{Right:} a comparison between two different prescriptions for an analytical DD DTD (solid curves), power-law DTDs with an initial plateau of 1 Gyr and 350 Myr (dashed curves), and a power-law DTD with no plateau and a slope of -1.1 (dotted curve).}
     \label{fig:onezone-greggio05}
-    \script{onezone_greggio05.py}
-\end{figure}
+    \script{onezone_greggio05_single.py}
+    \script{onezone_greggio05_double.py}
+\end{figure*}
+
+\subsection{Multi-Zone Models}
+\label{sec:multizone-results}
 

### 2022-08-15 src/scripts/onezone_greggio05.py
switch to wrapper script

@@ -1,172 +1,11 @@
+r"""
+This script generates plots for both the single degenerate and double
+degenerate cases from Grettio 2005. Reference this script in the `\script{}`
+command when plotting both figures side-by-side in the LaTeX document.
 """
-This script plots abundance tracks for one-zone models with varying minimum
-Type Ia delay times and star formation efficiency timescales.
-"""
 
-import sys
-from pathlib import Path
-import numpy as np
-import matplotlib.pyplot as plt
-import vice
-from vice.yields.presets import JW20
-vice.yields.sneia.settings['fe'] *= 10**0.1
-import paths
-sys.path.append(str(paths.root))
-from migration.src.simulations import models, dtds
-from migration.src._globals import END_TIME
-from colormaps import paultol
-from track_and_mdf import setup_axes, plot_vice_onezone
+from .onezone_greggio05_single import main as main_single
+from .onezone_greggio05_double import main as main_double
 
-# One-zone model settings
-DT = 0.01
-STANDARD_PARAMS = dict(
-    func=models.insideout(8, dt=DT),
-    mode='sfr',
-    elements=('fe', 'o'),
-    dt=DT,
-    recycling='continuous',
-    eta=2.5,
-    delay=0.04,
-    tau_star=2.,
-)
-LOG_MDF = False
-
-def main(overwrite=False):
-    output_dir = paths.data / 'onezone' / 'greggio05'
-    if not output_dir.exists():
-        output_dir.mkdir(parents=True)
-
-    fig, axs = setup_axes(logmdf=LOG_MDF)
-
-    simtime = np.arange(0, END_TIME + DT, DT)
-
-    # Double-degenerate WIDE model
-    dtd = dtds.greggio05_approximate.from_defaults('wide')
-    sz = vice.singlezone(name=str(output_dir / dtd.name),
-                         RIa=dtd, **STANDARD_PARAMS)
-    sz.run(simtime, overwrite=True)
-    plot_vice_onezone(str(output_dir / dtd.name), fig=fig, axs=axs,
-                      label='Double Degenerate WIDE',
-                      color=paultol.muted.colors[1],
-                      marker_labels=True,
-                      style_kw={
-                           'linestyle': '-',
-                           'linewidth': 1,
-                           'zorder': 10},
-                      logmdf=LOG_MDF
-                      )
-    
-    # Double-degenerate CLOSE model
-    dtd = dtds.greggio05_approximate.from_defaults('close')
[…]

### 2022-08-15 src/scripts/onezone_greggio05.py
Update onezone_greggio05.py

@@ -4,8 +4,8 @@ degenerate cases from Grettio 2005. Reference this script in the `\script{}`
 command when plotting both figures side-by-side in the LaTeX document.
 """
 
-from .onezone_greggio05_single import main as main_single
-from .onezone_greggio05_double import main as main_double
+from onezone_greggio05_single import main as main_single
+from onezone_greggio05_double import main as main_double
 
 main_single()
 main_double()

### 2022-08-15 src/scripts/onezone_greggio05_single.py
fixed yields

@@ -9,7 +9,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 import vice
 from vice.yields.presets import JW20
-vice.yields.sneia.settings['fe'] *= 10**0.1
+vice.yields.sneia.settings['fe'] = 0.0021
 import paths
 sys.path.append(str(paths.root))
 from migration.src.simulations import models, dtds

### 2023-02-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{layouts}
+\usepackage{xcolor}
 % \usepackage{siunitx}
@@
 % \DeclareSIUnit\year{yr}
+
+% user-defined commands
+\newcommand{\yes}{\textcolor{green}{\checkmark}}
+\newcommand{\meh}{\textcolor{black}{$\sim$}}
+\newcommand{\no}{\textcolor{red}{$\times$}}
 
@@
 
-\subsection{Accuracy of astroNN}
-\label{sec:astronn-quality}
-
-For $19784$ stars, or $\sim3.5\%$ of the sample, the astroNN [Fe/H] abundance estimate is $\gtrsim0.5$ dex lower than the value provided by ASPCAP.
-The vast majority of these stars are on the lower-main sequence according to \textit{Gaia} photometry, so we exclude stars with $\log(g) > 4$ in ASPCAP.
-In addition, 197 or $\sim3\%$ of stars with APOKASC-2 asteroseismic ages are reported to be $>5$ Gyr younger by astroNN.
-The APOKASC-2 age is unphysically high for many of these stars, often exceeding 15 Gyr.
-We identify prior mass loss as the cause of this discrepancy, so the astroNN ages are likely closer to the truth.
-
-\subsection{Measurements of the Type Ia Supernova Delay Time Distribution}
-\label{sec:dtd-measurements}
+\subsection{DTD Models}
+\label{sec:dtd-models}
 
@@
 
-\citet{Schonrich2009-RadialMixing} take their DTD to be an exponential with a 1.5 Gyr timescale, though this isn't strictly observationally motivated.
+\subsubsection{From Observations}
 
+\citet{Maoz2014-Review}
+
+A typical form for the DTD is a power-law $t^\alpha$ where $\alpha\sim-1$.
 \citet{Maoz2017-CosmicDTD} compare volumetric SN Ia rates to the cosmic star formation history.
@@
 \citet{Heringer2019-FieldGalaxyDTD} study the distribution of SNe Ia in field galaxies and get a power-law index of $-1.34^{+0.19}_{-0.17}$ which is closer to Maoz's cluster DTD.
+
+\citet{Wiseman2021-DESRates} measure the SN Ia rate in the redshift range $0.2 < z < 0.6$ and get a similar power law to \citet{Maoz2017-CosmicDTD} with a slope of $-1.13 \pm 0.05$.
+They also find that slower-declining SNe have a steeper DTD slope.
+
+Another commonly assumed functional form is an exponential.
+\citet{Schonrich2009-RadialMixing} take their DTD to be an exponential with a 1.5 Gyr timescale, though this isn't strictly observationally motivated.
 
@@
 
-\citet{Wiseman2021-DESRates} measure the SN Ia rate in the redshift range $0.2 < z < 0.6$ and get a similar power law to \citet{Maoz2017-CosmicDTD} with a slope of $-1.13 \pm 0.05$.
-They also find that slower-declining SNe have a steeper DTD slope.
+% \begin{deluxetable}{lCl}
+% \tablecaption{Sources of the various forms of delay time distribution.}
+% \tablehead{
+% \colhead{Name} & \colhead{Form} & \colhead{Source}
+% }
+% \startdata
+% Field Galaxy Power-Law      & t^{-1.1}              & \citet{Maoz2017-CosmicDTD} \\   
+% Galaxy Cluster Power-Law    & t^{-1.4}              & \citet{Maoz2017-CosmicDTD} \\
+% Short Exponential           & e^{-t/1.5~\rm{Gyr}}  & \citet{Schonrich2009-RadialMixing} \\
+% \enddata
+% \end{deluxetable}
 
-\begin{deluxetable}{lCl}
-\tablecaption{Sources of the various forms of delay time distribution.}
-\tablehead{
-\colhead{Name} & \colhead{Form} & \colhead{Source}
-}
-\startdata
-Field Galaxy Power-Law      & t^{-1.1}              & \citet{Maoz2017-CosmicDTD} \\   
-Galaxy Cluster Power-Law    & t^{-1.4}              & \citet{Maoz2017-CosmicDTD} \\
-Short Exponential           & e^{-t/1.5~\rm{Gyr}}  & \citet{Schonrich2009-RadialMixing} \\
-\enddata
-\end{deluxetable}
+\subsubsection{Theoretical Models}
 
-\section{Results}
-\label{sec:results}
+\citet{Matteucci1986-SupernovaEnrichment}
 
-\subsection{One-Zone Models}
+\citet{Greggio2005-AnalyticalRates}
+
+\citet{Rajamuthukumar2022-TripleEvolution}
+
+\citet{Schonrich2009-RadialMixing,Weinberg2017-ChemicalEquilibrium} assume an exponential with $\tau=1.5$ Gyr
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/dtd_greggio05.pdf}
+    \caption{Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and close approximation simple functions (dashed curves).}
+    \label{fig:dtd-greggio05}
+\end{figure}
+
+\subsubsection{Our Models}
+
+We explore four different classes of DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, and an exponential with a prompt Gaussian component, with one or two different parameterizations for each.
+Figure \ref{fig:dtds} presents these DTDs as a function of time since star formation.
+
+The power-law DTD is motivated by studies of the cosmic Ia rate \citep{Maoz2017-CosmicDTD,Wiseman2021-DESRates}, and we explore slopes of $\alpha=-1.1$ and $\alpha=-1.4$ which correspond to the field galaxy and galaxy cluster DTDs of \citet{Maoz2017-CosmicDTD}, respectively.
+We explore the broken power-law with plateau widths of 300 Myr and 1 Gyr \textemdash the first as a proxy for both
+
+\subsection{APOGEE Data}
+\label{sec:apogee-data}
+
+\subsubsection{Accuracy of astroNN}
+\label{sec:astronn-quality}
+
+For $19784$ stars, or $\sim3.5\%$ of the sample, the astroNN [Fe/H] abundance estimate is $\gtrsim0.5$ dex lower than the value provided by ASPCAP.
+The vast majority of these stars are on the lower-main sequence according to \textit{Gaia} photometry, so we exclude stars with $\log(g) > 4$ in ASPCAP.
+In addition, 197 or $\sim3\%$ of stars with APOKASC-2 asteroseismic ages are reported to be $>5$ Gyr younger by astroNN.
+The APOKASC-2 age is unphysically high for many of these stars, often exceeding 15 Gyr.
+We identify prior mass loss as the cause of this discrepancy, so the astroNN ages are likely closer to the truth.
+
+\subsection{Chemical Evolution Models}
+\label{sec:vice-models}
+
+\section{Results from Single-Zone Models}
 \label{sec:onezone-results}
@@
 
-\subsubsection{The SN Ia Delay-Time Distribution}
+\subsection{The SN Ia Delay-Time Distribution}
 
@@
 
-\subsubsection{The Minimum SN Ia Delay Time}
+\subsection{The Minimum SN Ia Delay Time}
 
@@
 
-\subsubsection{The Star Formation History}
+\subsection{The Star Formation History}
 
@@
 
-\subsubsection{Analytical Formulations}
+\subsection{Analytical Formulations}
 
@@
     \label{fig:onezone-greggio05}
-    \script{onezone_greggio05_single.py}
-    \script{onezone_greggio05_double.py}
+    \script{onezone_greggio05.py}
 \end{figure*}
 
-\subsection{Multi-Zone Models}
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_prompt.pdf}
+    \caption{Caption}
+    \label{fig:onezone-prompt}
+    \script{onezone_prompt.py}
+\end{figure}
+
+\section{Results from Multi-Zone Models}
 \label{sec:multizone-results}
+
+\section{Discussion}
+\label{sec:discussion}
+
+Picking the team.
+
+\begin{deluxetable*}{ll|cccc}
+\label{tab:results}
+\tablehead{
+\colhead{DTD} & \colhead{SFH} & \colhead{MDF} & \colhead{ODF} & \colhead{[Fe/H]--[O/Fe]} & \colhead{Age--[O/Fe]}
+}
+\startdata
+Power law               & Inside-out    & \meh  & \no   & \meh  & \no     \\
+($\alpha=-1.1$)         & Late burst    & \meh  & \no   & \meh  & \no     \\
+                        & Early burst   & \no   & \yes  & \meh  & \meh    \\
+                        & Two-infall    & \no   & \no   & \meh  & \no     \\
+\hline
+Power law               & Inside-out    & \meh  & \no   & \no   & \no     \\
+($\alpha=-1.4$)         & Late burst    & \meh  & \no   & \no   & \no     \\
+                        & Early burst   & \no   & \yes  & \no   & \meh    \\
+                        & Two-infall    & \no   & \no   & \no   & \no     \\
+\hline
+Exponential             & Inside-out    & \yes  & \no   & \yes  & \no     \\
+($\tau=1.5$ Gyr)        & Late burst    & \yes  & \no   & \yes  & \no     \\
+                        & Early burst   & \no   & \yes  & \meh  & \yes    \\
+                        & Two-infall    & \yes  & \meh  & \meh  & \meh    \\
+\hline
+Exponential             & Inside-out    & \yes  & \meh  & \yes  & \meh    \\
+($\tau=3$ Gyr)          & Late burst    & \yes  & \meh  & \yes  & \meh    \\
+                        & Early burst   & \no   & \yes  & \no   & \yes    \\
+                        & Two-infall    & \meh  & \meh  & \meh  & \meh    \\
+\hline
+Plateau                 & Inside-out    & \yes  & \meh  & \yes  & \no     \\
+($W=0.3$ Gyr)           & Late burst    & \yes  & \no   & \yes  & \no     \\
+                        & Early burst   & \no   & \yes  & \meh  & \yes    \\
+                        & Two-infall    & \yes  & \meh  & \yes  & \meh    \\
+\hline
+Plateau                 & Inside-out    & \meh  & \meh  & \yes  & \meh    \\
+($W=1.0$ Gyr)           & Late burst    & \meh  & \meh  & \yes  & \meh    \\
+                        & Early burst   & \no   & \yes  & \no   & \yes    \\
+                        & Two-infall    & \meh  & \meh  & \meh  & \meh    \\
+\hline
+Prompt                  & Inside-out    & \meh  & \no   & \no   & \no     \\
+($t_{50}=0.1$ Gyr)      & Late burst    & \meh  & \no   & \no   & \no     \\
+                        & Early burst   & \no   & \yes  & \no   & \yes    \\
+                        & Two-infall    & \yes  & \no   & \no   & \no     \\
+\hline
+Triple system           & Inside-out    & \yes  & \meh  & \meh  & \yes    \\
+($t_{\rm{max}}=1$ Gyr)  & Late burst    & \yes  & \yes  & \meh  & \meh    \\
+                        & Early burst   & \no   & \meh  & \no   & \yes    \\
+                        & Two-infall    & \meh  & \meh  & \meh  & \meh    \\
+\enddata
+\end{deluxetable*}
+
+\section{Conclusions}
+\label{sec:conclusions}
+
+\appendix
 

### 2023-02-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/greggio05_dtd.pdf}
-    \caption{Analytical DTDs computed by \citet{Greggio2005-AnalyticalRates}.
+% \begin{figure}
+%     \centering
+%     \includegraphics{figures/greggio05_dtd.pdf}
+%     \caption{Analytical DTDs computed by \citet{Greggio2005-AnalyticalRates}.
 The solid red curve represents the SD DTD for Chandrasekhar explosions, while the green and blue solid curves represent, respectively, the CLOSE and WIDE formulations of a DD DTD.
@@
 All DTDs are normalized to unity.}
-    \label{fig:greggio05-dtd}
-    \script{greggio05_dtd.py}
-\end{figure}
+%     \label{fig:greggio05-dtd}
+%     \script{greggio05_dtd.py}
+% \end{figure}
 

### 2023-06-14 migration/src/plots/__init__.py
clean old files

@@ -1,4 +1,0 @@
-
-__all__ = []
-from .plots import *
-__all__.extend(plots.__all__)

### 2023-06-14 migration/src/plots/env.py

@@ -1,63 +1,0 @@
-r"""
-Ensures runtime dependencies are satisfied for producing figures in Johnson et
-al. (2021).
-
-Dependencies:
-
-	- matplotlib >= 2.0.0
-	- NumPy >= 1.17.0
-"""
-
-try:
-	ModuleNotFoundError
-except NameError:
-	ModuleNotFoundError = ImportError
-
-# Enforce matplotlib >= 2.0.0 or else RuntimeError
-try:
-	import matplotlib as mpl
-except (ModuleNotFoundError, ImportError):
-	raise ModuleNotFoundError("Matplotlib not found.")
-if tuple([int(i) for i in mpl.__version__.split('.')])[:2] < (2, 0):
-	raise RuntimeError("""Matplotlib version >= 2.0.0 required for producing \
-Johnson et al. (2021) figures. Current: %s""" % (mpl.__version__))
-else: pass
-
-# Enforce NumPy >= 1.17.0 or else RuntimeError
-try:
-	import numpy as np
-except (ModuleNotFoundError, ImportError):
-	raise ModuleNotFoundError("NumPy not found.")
-if tuple([int(i) for i in np.__version__.split('.')])[:2] < (1, 17):
-	raise RuntimeError("""NumPy version >= 1.17.0 required for producing \
-Johnson et al. (2021) figures. Current: %s""" % (np.__version__))
-else: pass
-
-
-# by setting matplotlib rcParams here, all plots will be automatically
-# formatted since this file will be imported everywhere to ensure dependencies
-# are met anyway.
-# mpl.rcParams["font.family"] = "serif"
-# mpl.rcParams["text.usetex"] = True
-# mpl.rcParams["text.latex.preamble"] = [r"\usepackage{amsmath}"]
-# mpl.rcParams["errorbar.capsize"] = 5
-# mpl.rcParams["axes.linewidth"] = 2
-# mpl.rcParams["xtick.major.size"] = 16
-# mpl.rcParams["xtick.major.width"] = 2
-# mpl.rcParams["xtick.minor.size"] = 8
-# mpl.rcParams["xtick.minor.width"] = 1
-# mpl.rcParams["ytick.major.size"] = 16
-# mpl.rcParams["ytick.major.width"] = 2
-# mpl.rcParams["ytick.minor.size"] = 8
-# mpl.rcParams["ytick.minor.width"] = 1
[…]

### 2023-06-14 migration/src/plots/plots/age_ofe.py

@@ -1,194 +1,0 @@
-r"""
-This script produces a 2x2 panel figures compairing four Age-[O/Fe] relations
-in a given galactic regions predicted by different models.
-
-In Johnson et al. (2021), this script produces Figs. 13a and 13b.
-"""
-
-from ..._globals import ZONE_WIDTH, COLORMAP
-from .. import env
-from ..utils import (zheights, weighted_median, filter_multioutput_stars,
-	feuillet2019_data)
-from .utils import (named_colors, mpl_loc, markers, xticklabel_formatter,
-	dummy_background_axes)
-from .amr.galactic_regions import feuillet2019_amr
-from astropy.io import fits
-import matplotlib.pyplot as plt
-import vice
-
-# y-axis limits for [O/Fe]
-OFE_LIM = [-0.2, 0.5]
-
-# x-axis limits for age in Gyr (note: log-scaled x-axis)
-TIME_LIM = [0.4, 18]
-
-# bins in [O/Fe] in which to measure mass-weighted median age
-BINS = [-1. + 0.02 * i for i in range(101)]
-
-
-def main(upperleft, upperright, lowerleft, lowerright, stem,
-	min_rgal = 7, max_rgal = 9, min_absz = 0, max_absz = 0.5,
-	names = [["Constant SFR", "Inside-Out"], ["Late-Burst", "Outer-Burst"]]):
-	r"""
-	Plot a 2x2 panel figure showing comparing the model-predicted age-[O/Fe]
-	relations to the Feuillet et al. (2019) [1]_ measurements in a given
-	galactic region.
-
-	Parameters
-	----------
-	upperleft : ``str``
-		The relative or absolute path to the VICE output whose predicted
-		age-[O/Fe] relation is to go in the upper-left panel.
-	upperright: ``str``
-		The relative or absolute path to the VICE output whose predicted
-		age-[O/Fe] relation is to go in the upper-right panel.
-	lowerleft : ``str``
-		The relative or absolute  path to the VICE output whose predicted
-		age-[O/Fe] relation is to go in the lower-left panel.
-	lowerright : ``str``
-		The relative or absolute path to the VICE output whose predicted
[…]

### 2023-06-14 migration/src/plots/plots/amr/comparison.py

@@ -1,141 +1,0 @@
-r"""
-Plots the age-metallicity relation (AMR) within the disk in for a set of
-four models.
-"""
-
-from ... import env
-from ...utils import zheights, weighted_median, feuillet2019_data
-from ..utils import (named_colors, mpl_loc, markers, xticklabel_formatter,
-	dummy_background_axes)
-from .galactic_regions import (plot_amr, median_ages, feuillet2019_amr, OH_LIM,
-	FEH_LIM, TIME_LIM)
-import matplotlib.pyplot as plt
-import vice
-
-
-def main(element, outputs, stem, radii = [[5, 7], [7, 9], [9, 11], [11, 13]],
-	feuillet2019 = True,
-	labels = ["Constant SFR", "Inside-Out", "Late-Burst", "Outer-Burst"],
-	**subplots_adjust_kwargs):
-
-	r"""
-	Produce a plot comparing the age-[X/H] relation predicted by a set of
-	models in various galactic regions.
-
-	Parameters
-	----------
-	element : ``str``
-		The element X in age-[X/H] relation.
-	outputs : array-like [elements of type ``str``]
-		The relative or absolute paths to the VICE outputs whose predicted
-		age-[X/H] relations are to be visualized.
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-	radii : ``list`` [elements are two-component ``list``s storing ``float``s]
-		[default : [[5, 7], [7, 9], [9, 11], [11, 13]]]
-		The ranges in radius defining the galactic regions to visualize the
-		age-[X/H] relation within.
-	feuillet2019 : ``bool`` [default : True]
-		Whether or not to include the measurements of Feuillet et al. (2019)
-		[1]_ as a comparison.
-	labels : ``list`` [elements of type ``str``]
-		Short descriptors distinguishing which model is which in the
-		visualization. Models will be plotted in the order in which they appear
-		in the ``outputs`` array.
-	subplots_adjust_kwargs : varying types
-		Additional keywords to pass to ``pyplot.subplots_adjust``.
-
-
[…]

### 2023-06-14 migration/src/plots/plots/amr/galactic_regions.py

@@ -1,346 +1,0 @@
-r"""
-Plots the age-[X/Y] relation for a given model in various regions of the
-galaxy.
-
-This script produces Fig. 14 of Johnson et al. (2021).
-"""
-
-from ...._globals import ZONE_WIDTH, COLORMAP
-from ... import env
-from ...utils import (zheights, weighted_median, feuillet2019_data,
-	filter_multioutput_stars)
-from ..utils import (named_colors, mpl_loc, markers, xticklabel_formatter,
-	dummy_background_axes)
-import matplotlib.pyplot as plt
-import vice
-
-# x-axis limits for age in Gyr (note: log-scaled)
-TIME_LIM = [0.2, 20]
-
-# y-axis limits for [O/H]
-OH_LIM = [-0.9, 0.7]
-
-# y-axis limits for [Fe/H]
-FEH_LIM = [-1.2, 0.7]
-
-# bins in [O/Fe] for computing median ages
-OFE_BINS = [-0.5 + 0.02 * i for i in range(51)]
-
-# bins in [X/H] for computing median ages.
-ONH_BINS = [-1. + 0.05 * i for i in range(41)]
-
-# The bin-edges in radius defining the galactic regions the data will be
-# presented in
-RADII = [5, 7, 9, 11, 13]
-
-# The bin-edges in disk midplane distance |z| defining the regions the data
-# will be presented in, in reverse order.
-HEIGHTS = [2.0, 1.0, 0.5, 0.0]
-
-
-def main(element_x, element_y, output, stem):
-	r"""
-	Illustrate the age-[X/Y] relation in 12 galactic regions as predicted by a
-	given VICE model in comparison to the measurements of Feuillet et al.
-	(2019) [1]_.
-
-	Parameters
-	----------
-	element_x : ``str``
-		The element X in age-[X/Y] relation.
-	element_y : ``str``
-		The element Y in age-[X/Y] relation.
-	output : ``str``
-		The relative or absolute path to the VICE output whose predicted
-		age-[X/Y] relation is to be visualized here.
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-
-	.. [1] Feuillet et al. (2019), MNRAS, 489, 1742
-	"""
[…]

### 2023-06-14 migration/src/plots/plots/eta_tau_sfh.py

@@ -1,93 +1,0 @@
-r"""
-This script creates a plot of the mass-loading factor eta and the star
-formation e-folding timescale as functions of Galactocentric radius in the
-forms adopted by Johnson et al. (2021).
-"""
-
-from .. import env
-from ...simulations.models.insideout import insideout
-from .utils import named_colors
-import matplotlib.pyplot as plt
-import math as m
-import vice
-
-
-def main(stem):
-	r"""
-	Plot a 1x2 panel figure, showing the mass-loading factor :math:`\eta` and
-	the e-folding timescales of the star formation history as functions of
-	galactocentric radius in kpc as adopted by Johnson et al. (2021).
-
-	Parameters
-	----------
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-	"""
-	ax1, ax2 = setup_axes()
-	plot_eta(ax1)
-	plot_tau_sfh(ax2)
-	plt.tight_layout()
-	plt.subplots_adjust(hspace = 0)
-	plt.savefig("%s.png" % (stem))
-	plt.savefig("%s.pdf" % (stem))
-	plt.close()
-
-
-def plot_eta(ax):
-	r"""
-	Plot the mass-loading factor :math:`\eta` as a function of Galactocentric
-	radius in kpc as adopted by Johnson et al. (2021).
-
-	Parameters
-	----------
-	ax : ``axes``
-		The matplotlib subplot to plot on.
-	"""
-	rgal = [0.01 * _ for _ in range(1551)]
-	eta = [vice.milkyway.default_mass_loading(_) for _ in rgal]
-	ax.plot(rgal, eta, c = named_colors()["black"])
-	ax.plot(2 * [8.], ax.get_ylim(), c = named_colors()["crimson"],
-		linestyle = ':')
-	ax.plot(ax.get_xlim(), 2 * [vice.milkyway.default_mass_loading(8.)],
-		c = named_colors()["crimson"], linestyle = ':')
-
-
-def plot_tau_sfh(ax):
-	r"""
-	Plot the e-folding timescales of the star formation history as a function
-	of Galactocentric radius as adopted by Johnson et al. (2021).
-
-	Parameters
[…]

### 2023-06-14 migration/src/plots/plots/h277_decomposition.py

@@ -1,218 +1,0 @@
-r"""
-This script produces a plot of the birth/final radii distributions of h277
-star particles in bins of their birth/final radii and age.
-"""
-
-from .. import env
-from .utils import named_colors, mpl_loc, dummy_background_axes
-from vice.toolkit.hydrodisk import hydrodiskstars
-from ..._globals import END_TIME
-import matplotlib.pyplot as plt
-import numpy as np
-
-
-def main(stem, age_bins = [[0, 2], [2, 4], [4, 6], [6, 8], [8, 10]],
-	radial_bins = [[5, 7], [7, 9], [9, 11], [11, 13]],
-	colors = ["darkviolet", "blue", "green", "gold", "red"]):
-	r"""
-	Create a figure showing the distributions of birth and final radii in
-	bins of age for ``h277`` star particles (see Johnson et al. 2021 paper).
-
-	Parameters
-	----------
-	stem : ``str``
-		The full or relative path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-	age_bins : ``list`` [elements are 2-element ``list``s storing ``float``s]
-		[default : [[0, 2], [2, 4], [4, 6], [6, 8], [8, 10]]]
-		The bin-edges in star particle ages in Gyr.
-	radial_bins : ``list`` [elements are 2-element ``list``s storing ``float``s]
-		[default : [[5, 7], [7, 9], [9, 11], [11, 13]]]
-		The bin-edges in birth or final radius in kpc. This is required because
-		distribution will be plotted for final radius in bins of birth radius,
-		and vice versa. Must contain at least as many elements as ``age_bins``.
-	colors : ``list`` [elements of type ``str``]
-		The colors to plot these distributions in. Must contain at least as
-		many elements as ``age_bins``.
-	"""
-	axes = setup_axes(n_columns = len(radial_bins))
-	h277 = hydrodiskstars([0.1 * _ for _ in range(201)], N = 3102519)
-	h277.decomp_filter([1, 2])
-	h277.analog_data["age"] = [END_TIME - _ for _ in h277.analog_data["tform"]]
-	for i in range(len(axes[0])):
-		# note the radial bin both in text and vertical black dotted lines
-		if radial_bins[i][1] >= 11:
[…]

### 2023-06-14 migration/src/plots/plots/metallicity_gradient.py

@@ -1,364 +1,0 @@
-r"""
-This script produces a 4x2 panel figure comparing the model-predicted radial
-abundance gradients of four models in [O/H], [Fe/H], and [O/Fe].
-
-In Johnson et al. (2021), this script produces Fig. 9.
-"""
-
-from ..._globals import ZONE_WIDTH
-from .. import env
-from ..utils import zheights
-from .utils import named_colors, mpl_loc, markers, dummy_background_axes
-import matplotlib.pyplot as plt
-import vice
-
-# The maximum radius of the VICE models in kpc
-MAX_RADIUS = 20.0
-
-# The maximum radius of star formation in the VICE models in kpc
-# gas gradients will be plotted only to this radius.
-MAX_SF_RADIUS = 15.5
-
-# y-axis limits for [O/H] and [Fe/H]
-XH_YLIM = [-0.9, 1.2]
-
-# y-axis limits for [O/Fe]
-OFE_YLIM = [-0.2, 0.5]
-
-# x-axis limits for galactocentric radius in kpc
-XLIM = [-2, 22]
-
-
-def main(farleft, midleft, midright, farright, stem,
-	labels = ["Constant SFR", "Inside-Out", "Late-Burst", "Outer-Burst"]):
-	r"""
-	Produce a 4x2 panel figure showing the radial metallicity gradients in
-	both stars and gas predicted by four VICE models.
-
-	Parameters
-	----------
-	static : ``str``
-		The relative or absolute path to the VICE output whose predicted
-		gradient is to be plotted in the far-left panels.
-	midleft : ``str``
-		The relative or absolute path to the VICE output whose predicted
-		gradient is to be plotted in the middle-left panels.
-	midright : ``str``
-		The relative or absolute path to the VICE output whose predicted
-		gradient is to be plotted in the middle-right panels.
-	farright: ``str``
-		The relative or absolute path to the VICE output whose predicted
-		gradient is to be plotted in the far-right panels.
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-	labels : ``list`` [elements of type ``str``]
[…]

### 2023-06-14 migration/src/plots/plots/ofe_mdfs.py

@@ -1,250 +1,0 @@
-r"""
-Plots the distribution of [O/Fe] in bins of [Fe/H] within 15 different galactic
-regions.
-
-This script produces Fig. 12 of Johnson et al. (2021).
-"""
-
-from ..._globals import ZONE_WIDTH
-from .. import env
-import matplotlib.pyplot as plt
-from ..utils import analogdata, filter_multioutput_stars
-from .utils import named_colors, mpl_loc
-import numpy as np
-import vice
-
-# x-axis limits for [O/Fe]
-XLIM = [-0.05, 0.35]
-
-# y-axis limits for PDF
-YLIM = [0, 20]
-
-# The bins in [Fe/H] to calculate the distribution within
-FEH_BINS = [
-	[-0.4, -0.2],
-	[0.0, 0.2]
-]
-
-# The colors to plot the distributions in bins of [Fe/H] with
-COLORS = [
-	"blue",
-	"crimson"
-]
-
-# The edges of the radial bins defining galactic region in kpc
-RADII = [3, 5, 7, 9, 11, 13]
-
-# the edges of the midplane distance bins defining galactic region in kpc.
-Z = [2.0, 1.0, 0.5, 0.0]
-
-
-def main(name, stem):
-	r"""
-	Plot the distributions of [O/Fe] in bins of [Fe/H] in 15 different galactic
-	regions.
-
-	Parameters
-	----------
-	name : ``str``
-		The relative or absolute path to the VICE output whose predicted
-		[O/Fe] distributions are to be visualized here.
-	stem : ``str``
-		The relative or absolute path to the output image, with no extension.
-		This function will save the figure in both PDF and PNG formats.
-
-	.. note:: The 15 regions are defined by bins in radius whose edges are
-		3, 5, 7, 9, 11, and 13 kpc, and bins in height above/below the disk
-		midplane whose edges are 0, 0.5, 1, and 2 kpc. In each panel, the
-		distribution will be shown for [Fe/H] = -0.4 - -0.2 and 0 - 0.2.
-	"""
-	axes = setup_axes()
-	out = vice.multioutput(name)
-	analog_data = analogdata("%s_analogdata.out" % (name))
-	out.stars["abszfinal"] = [abs(row[-1]) for row in
-		analog_data[:out.stars.size[0]]]
-	for i in range(3):
[…]

### 2023-06-14 migration/src/plots/utils.py

@@ -1,183 +1,0 @@
-r"""
-Utility functions for producing plots
-"""
-
-import numpy as np
-from astropy.io import fits
-
-
-def analogdata(filename):
-	r"""
-	Read a data file containing the extra stellar population data.
-
-	Parameters
-	----------
-	filename : str
-		The name of the file containing the star particle data.
-
-	Returns
-	-------
-	data : list
-		The 2-D list containing the data, sorted by rows.
-
-		- data[i][0] : zone of the formation of the i'th stellar population
-		- data[i][1] : time of formation in Gyr of the i'th stellar population
-		- data[i][2] : height z above/below the disk midplane at the present day
-	"""
-	data = []
-	with open(filename, 'r') as f:
-		line = f.readline()
-		while line[0] == '#':
-			line = f.readline()
-		while line != '':
-			line = line.split()
-			data.append([int(line[0]), float(line[1]), float(line[-1])])
-			line = f.readline()
-		f.close()
-	return data
-
-
-def zheights(name):
-	r"""
-	Obtain the heights above/below the disk midplane in kpc for each stellar
-	population in the simulation.
-
-	Parameters
-	----------
-	name : str
-		The name of the output.
-
-	Returns
-	-------
-	z : list
-		Height above/below disk midplane in kpc for each stellar population,
-		as they appear in the stars attribute of the multioutput object.
-
-	Notes
-	-----
-	The simulations ran by this program produce an extra output file under
-	the name "<output_name>_analogdata.out" which stores each analog star
-	particle's z-heights.
-	"""
-	return [row[-1] for row in analogdata("%s_analogdata.out" % (name))]
-
-
-def weighted_median(values, weights, stop = 0.5):
-	r"""
-	Compute the n'th percentile of a weighted distribution. Despite the name,
-	this function can compute any percentile, but by default it will be the
-	50th (i.e. the median).
-
-	Parameters
-	----------
-	values : ``list``
-		The values for which the n'th percentile given some weightes is to be
-		calculated.
-	weights : ``list``
-		The weights themselves. Must be the same length as ``values``.
-	stop : ``float`` [default : 0.5]
-		In decimal representation, the percentile at which to stop the
[…]

### 2023-06-14 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Define document class
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn,linenumbers,twocolappendix]{aastex631}
 
@@
 \author[0000-0002-6534-8783]{James W. Johnson}
-% \author[0000-0001-7775-7261]{David H. Weinberg}
+\author[0000-0001-7775-7261]{David H. Weinberg}
 
@@
     \includegraphics{figures/dtd_greggio05.pdf}
-    \caption{Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and close approximation simple functions (dashed curves).}
+    \caption{Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and close approximation simple functions (dashed curves).
+Some functions are presented with a constant multiplicative factor for visual clarity.}
     \label{fig:dtd-greggio05}
+    \script{dtd_greggio05.py}
 \end{figure}
@@
 
+\begin{enumerate}
+    \item A simple power law with slope $\alpha$:
+    \begin{equation}
+        R(t) = A_\alpha (t/1\,\rm{Gyr})^\alpha
+        \label{eq:powerlaw-dtd}
+    \end{equation}
+    where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
+    We investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$, following the field galaxy and galaxy cluster DTDs of \citet{Maoz2017-CosmicDTD}, respectively.
+
+    \item A ``plateau'' model consisting of a flat slope of width $W$ followed by a power law decline with normalization $B_W$:
+    \begin{equation}
+        R(t) = 
+        \begin{cases}
+            B_W, & t < W \\
+            B_W (t/W)^\alpha, & t \ge W
+        \end{cases}
+        \label{eq:plateau-dtd}
+    \end{equation}
+    where $B_W=[(W-t_{\rm min}) + \frac{t_{\rm max}^{\alpha+1} - W^{\alpha+1}}{(\alpha+1)W^\alpha}]^{-1}$ is the normalization coefficient.
+    We investigate the cases $W=0.3$ Gyr and $W=1$ Gyr, taking $\alpha=-1.1$ for all plateau models.
+Figure \ref{fig:dtd-greggio05} illustrates the similarity between these models and two different treatments of the analytical double-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
+
+    \item An exponentially declining DTD with timescale $\tau$ and normalization $C_\tau$:
+    \begin{equation}
+        R(t) = 1/\tau \exp(-t/\tau)
+        \label{eq:exponential-dtd}
+    \end{equation}
+    We investigate the case where $\tau=1.5$ Gyr, which has been used in previous studies \citep[e.g.,][]{Schonrich2009-RadialMixing,Weinberg2017-ChemicalEquilibrium} and is similar to the analytical single-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
+We also investigate a longer timescale of $\tau=3$ Gyr.
+
+    \item A DTD in which 50\% of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the other 50\% form an exponential tail at large $t$, normalized by $D_{t_p,\sigma,\tau}$:
+    \begin{equation}
+        R(t) = D_{t_p,\sigma,\tau} \Big[\exp\Big(-\frac{(t-t_p)^2}{2\sigma^2}\Big) + \exp(-t/\tau)\Big]
+        \label{eq:prompt-dtd}
+    \end{equation}
+    Following the two-population model from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in roughly 50\% of SNe Ia exploding within $t<100$ Myr.
+
+    \item A DTD based on simulations of triple-system evolution by \citet{Rajamuthukumar2022-TripleEvolution}.
+We approximate their DTD as a special case of the plateau model (Equation \ref{eq:plateau-dtd}) where the initial rate is quite low until an instantaneous rise to the plateau value at time $t_{\rm rise}$:
+    \begin{equation}
+        R(t) = 
+        \begin{cases}
+            \epsilon B_W, & t < t_{\rm rise} \\
+            B_W, & t_{\rm rise} \leq t < W \\
+            B_W (t / W) ^ \alpha, & t \geq W
+        \end{cases}
+        \label{eq:triple-dtd}
+    \end{equation}
+    We take $t_{\rm rise}=0.5$ Gyr, $W=0.5$ Gyr, $\alpha=-1.1$, and $\epsilon=0.05$ so the initial rate is 5\% of the peak rate.
+\end{enumerate}
+
 \subsection{APOGEE Data}
@@
 
-\subsubsection{Accuracy of astroNN}
-\label{sec:astronn-quality}
+We use APOGEE DR17 \citep{Abdurro'uf2022-SDSSIV-DR17}. Our selection criteria are presented in Table \ref{tab:sample-selection}, producing a final sample of 192,926 stars.
 
-For $19784$ stars, or $\sim3.5\%$ of the sample, the astroNN [Fe/H] abundance estimate is $\gtrsim0.5$ dex lower than the value provided by ASPCAP.
+\begin{deluxetable*}{lll}
+    \tablecaption{Sample Selection\label{tab:sample-selection}}
+    \tablehead{
+        \colhead{Parameter} & \colhead{Range} & \colhead{Notes}
+    }
+    \startdata
+        $\log g$            & $1.0 < \log g < 3.8$          & Select giants only \\
+        $T_{\rm eff}$       & $3500 < T_{\rm eff} < 5500$ K & Reliable temperature range \\
+        $S/N$               & $S/N > 80$                    & Required for accurate stellar parameters \\
+        ASPCAPFLAG Bits     & $\notin$ 23                   & Remove stars flagged as bad \\
+        EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
+    \enddata
+\end{deluxetable*}
+
+\subsubsection{Stellar Ages}
+\label{sec:stellar-ages}
+
+191,179 stars in our sample have astroNN ages and 71,684 have ages from \citet{Leung2023-Ages}.
+
+% For $19784$ stars, or $\sim3.5\%$ of the sample, the astroNN [Fe/H] abundance estimate is $\gtrsim0.5$ dex lower than the value provided by ASPCAP.
 The vast majority of these stars are on the lower-main sequence according to \textit{Gaia} photometry, so we exclude stars with $\log(g) > 4$ in ASPCAP.
@@
 \label{sec:vice-models}
+
+\subsubsection{Stellar Migration}
+\label{sec:migration}
+
+\citet{Johnson2021-Migration}
+
+We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm initial}$ from the \texttt{h277} output in bins of $R_{\rm initial}$ and age.
+Each Gaussian is centered at 0 and we find that the scale $\sigma_{\Delta R}$ is best described by the function
+
+\begin{equation}
+    \sigma_{\Delta R} = 1.35\,{\rm kpc}(R_{\rm form}/8\,{\rm kpc})^{0.61} (\tau/1\,{\rm Gyr})^{0.33}
+    \label{eq:radial-migration}
+\end{equation}
+
+\noindent where $\tau$ is the age of the star particle.
+
+We fit a sech$^2$ function \citep{Spitzer1942} to the distribution of midplane distances $z_{\rm final}$.
+Vertical migration away from the midplane does not affect the chemical evolution simulation, but we do use $z_{\rm final}$ in our analysis.
+The probability density function (PDF) of $z_{\rm final}$ given some scale height $h_z$ is
+
+\begin{equation}
+    {\rm PDF}(z_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z_{\rm final}}{2 h_z}\Big)
+    \label{eq:sech-pdf}
+\end{equation}
+
+\noindent and the corresponding cumulative distribution function (CDF) is
+
+\begin{equation}
+    {\rm CDF}(z_{\rm final}) = \frac{1}{1 + \exp(-z_{\rm final} / h_z)}.
+    \label{eq:sech-cdf}
+\end{equation}
+
+\noindent We fit the above function to the distributions of $z_{\rm final}$ in h277 in varying bins of $\tau$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
+
+\begin{equation}
+    h_z = (0.25\,{\rm kpc}) 
+    \exp\Big(\frac{\tau-5\,{\rm Gyr}}{7.0\,{\rm Gyr}}\Big)
+    \exp\Big(\frac{R_{\rm final}-8\,{\rm kpc}}{6.0\,{\rm kpc}}\Big)
+    \label{eq:scale-height}
+\end{equation}
 
@@
 \end{figure}
+
+A 150 Myr minimum delay time is incompatible with the prompt DTD model, which has $\sim 50$ of SNe Ia explode in the first 100 Myr.
 
@@
 
+\begin{deluxetable}{lll}
+    \tablecaption{Median Parameter Uncertainties\label{tab:uncertainties}}
+    \tablehead{
+        \colhead{Parameter} & \colhead{Median Uncertainty} & \colhead{Source}
+    }
+    \startdata
+        [Fe/H] & $9.2\times10^{-3}$ & APOGEE \\
+        $\rm [O/Fe]$ & $1.8\times10^{-2}$ & APOGEE \\
+        log(Age/Gyr) & $0.12$ & \citet{Leung2023-Ages}
+        % Age/Gyr & 29\% & astroNN
+    \enddata
+\end{deluxetable}
+
+\subsection{Comparison to APOGEE MDFs}
+
+To quantify the similarity between the MDFs generated by VICE and the observed APOGEE MDF, we compute the Kullback-Leibler (KL) divergence \citep{KullbackLeibler1951}, defined as
+
+\begin{equation}
+\label{eq:kl-divergence}
+D_{\rm{KL}}(P \parallel Q) = \int_{-\infty}^{\infty} p(x) \log\Big(\frac{p(x)}{q(x)}\Big) dx
+\end{equation}
+
+\noindent for distributions $P$ and $Q$ with probability density functions $p(x)$ and $q(x)$.
+In this case, $P$ is the APOGEE MDF, $Q$ is the model MDF, and $x$ is [Fe/H].
+For each model SFH and DTD, we compute $D_{\rm{KL}}$ in 18 different galactocentric zones defined by radial bins $3-5$ kpc, $5-7$ kpc, $7-9$ kpc, $9-11$ kpc, $11-13$ kpc, and $13-15$ kpc and absolute $z$-height bins $0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
+The KL divergence for the entire model is taken to be the average of $D_{\rm{KL}}$ for each zone, weighted by the number of APOGEE stars in each zone.
+
+\subsection{Comparison to APOGEE ODFs}
+
 \section{Discussion}
@@
 Prompt                  & Inside-out    & \meh  & \no   & \no   & \no     \\
-($t_{50}=0.1$ Gyr)      & Late burst    & \meh  & \no   & \no   & \no     \\
+($t_{\rm max}=0.05$ Gyr)& Late burst    & \meh  & \no   & \no   & \no     \\
                         & Early burst   & \no   & \yes  & \no   & \yes    \\
@@
 
+Blah
+
+\begin{acknowledgments}
+Funding for the Sloan Digital Sky 
+Survey IV has been provided by the 
+Alfred P. Sloan Foundation, the U.S. 
+Department of Energy Office of 
+Science, and the Participating 
+Institutions.
+
+SDSS-IV acknowledges support and 
+resources from the Center for High 
+Performance Computing  at the 
+University of Utah. The SDSS 
+website is www.sdss4.org.
+
+SDSS-IV is managed by the 
+Astrophysical Research Consortium 
+for the Participating Institutions 
+of the SDSS Collaboration including 
+the Brazilian Participation Group, 
+the Carnegie Institution for Science, 
+Carnegie Mellon University, Center for 
+Astrophysics | Harvard \& 
+Smithsonian, the Chilean Participation 
+Group, the French Participation Group, 
+Instituto de Astrof\'isica de 
+Canarias, The Johns Hopkins 
+University, Kavli Institute for the 
+Physics and Mathematics of the 
+Universe (IPMU) / University of 
+Tokyo, the Korean Participation Group, 
+Lawrence Berkeley National Laboratory, 
+Leibniz Institut f\"ur Astrophysik 
+Potsdam (AIP),  Max-Planck-Institut 
+f\"ur Astronomie (MPIA Heidelberg), 
+Max-Planck-Institut f\"ur 
+Astrophysik (MPA Garching), 
+Max-Planck-Institut f\"ur 
+Extraterrestrische Physik (MPE), 
+National Astronomical Observatories of 
+China, New Mexico State University, 
+New York University, University of 
+Notre Dame, Observat\'ario 
+Nacional / MCTI, The Ohio State 
+University, Pennsylvania State 
+University, Shanghai 
+Astronomical Observatory, United 
+Kingdom Participation Group, 
+Universidad Nacional Aut\'onoma 
+de M\'exico, University of Arizona, 
+University of Colorado Boulder, 
+University of Oxford, University of 
+Portsmouth, University of Utah, 
+University of Virginia, University 
+of Washington, University of 
+Wisconsin, Vanderbilt University, 
+and Yale University.
+\end{acknowledgments}
+
 \appendix

### 2023-06-14 migration/src/__init__.py
remove old plot imports

@@ -1,4 +1,3 @@
 
-__all__ = ["plots", "simulations"]
-from . import plots
+__all__ = ["simulations"]
 from . import simulations

### 2023-06-15 src/scripts/star_formation_histories.py
combine all sfhs to one plot

@@ -3,46 +3,40 @@ This script plots various quantities relating to star formation history as a
 function of time for multiple VICE simulation outputs.
 """
 
-import sys
 from pathlib import Path
 import numpy as np
 import matplotlib.pyplot as plt
+from matplotlib.ticker import MultipleLocator
 import vice
 import paths
-from utils import discrete_colormap, get_color_list, setup_discrete_colorbar, \
-    get_bin_centers
-from _globals import END_TIME, GALR_BINS, ZONE_WIDTH
+from utils import get_color_list
+from _globals import END_TIME, ZONE_WIDTH, TWO_COLUMN_WIDTH
+from colormaps import paultol
+plt.rcParams['axes.prop_cycle'] = plt.cycler('color', paultol.vibrant.colors)
 
-def main(evolution, RIa='powerlaw_slope11', cmap_name='plasma_r'):
-    output = paths.data / 'migration' / 'post-process' / evolution / RIa
-    fname = 'sfh_%s.png' % evolution
-    plot_by_zone(output, fname=fname, zone_width=ZONE_WIDTH, cmap_name=cmap_name)
-    # fig, axs = setup_axes()
-    # plot_history(axs, paths.data / 'migration/diffusion/twoinfall/powerlaw_slope11_delay040', 80, color='b')
-    # plot_history(axs, paths.data / 'migration/diffusion/insideout_conroy22/powerlaw_slope11_delay040', 80, color='orange')
-    # plt.savefig(paths.figures / 'star_formation_histories.png', dpi=300)
-    
+MIGRATION = 'post-process'
+EVOLUTION_LIST = ['insideout', 'lateburst', 'conroy22_JW20yields', 'twoinfall']
+DTD = 'powerlaw_slope11'
+GALR_LIST = [3, 5, 7, 9, 11, 13, 15]
+CMAP_NAME = 'plasma_r'
 
-def plot_by_zone(output, galr_bins=GALR_BINS, zone_width=ZONE_WIDTH, 
-                 cmap_name='plasma_r', fname='star_formation_histories.png'):
-    # Determine zones to plot
-    galr_centers = get_bin_centers(galr_bins)
-    zones = [int(galr / zone_width) for galr in galr_centers]
-    # Set up plot
+def main():
     fig, axs = setup_axes()
-    cmap, norm = discrete_colormap(cmap_name, galr_bins)
[…]

### 2023-06-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-% Begin!
 \begin{document}
@@
 
-% Abstract with filler text
+% Abstract from AAS 241
 \begin{abstract}
-    Abstract.
+    Type Ia supernovae (SNe Ia) produce most of Fe-peak elements in the Universe and therefore are a crucial ingredient in galactic chemical evolution models.
+SNe Ia do not explode immediately after star formation and the delay-time distribution (DTD) has not been definitively determined by supernova surveys or theoretical models.
+Because the DTD also affects the relationship among age, [Fe/H], and [$\alpha$/Fe] in chemical evolution models, comparison with observations of stars in the Milky Way is an important consistency check for any proposed DTD.
+We implement several popular forms of the DTD in combination with multiple star formation histories for the Milky Way in one-zone and multi-zone chemical evolution models using the Versatile Integrator for Chemical Evolution (VICE).
+VICE includes a prescription for radial stellar migration in multi-zone models.
+We compare our predicted interstellar medium abundance tracks, stellar abundance distributions, and stellar age distributions to the 17th data release of the Apache Point Observatory Galactic Evolution Experiment (APOGEE).
+We find that the SN Ia DTD has the largest effect on the [$\alpha$/Fe] distribution: a DTD with more prompt SNe Ia produces a stellar abundance distribution that is skewed toward a lower [$\alpha$/Fe] ratio, whereas a DTD with more delayed SNe Ia produces a distribution that is skewed toward higher [$\alpha$/Fe].
+While the DTD alone cannot explain the observed bimodality in the [$\alpha$/Fe] distribution, in combination with an appropriate star formation history it affects the goodness of fit between the simulated and observed high-$\alpha$ sequence.
 \end{abstract}
@@
 
-We explore four different classes of DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, and an exponential with a prompt Gaussian component, with one or two different parameterizations for each.
+We explore five different classes of DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, an exponential with a prompt Gaussian component, with one or two different parameterizations for each.
 Figure \ref{fig:dtds} presents these DTDs as a function of time since star formation.
 
-The power-law DTD is motivated by studies of the cosmic Ia rate \citep{Maoz2017-CosmicDTD,Wiseman2021-DESRates}, and we explore slopes of $\alpha=-1.1$ and $\alpha=-1.4$ which correspond to the field galaxy and galaxy cluster DTDs of \citet{Maoz2017-CosmicDTD}, respectively.
-We explore the broken power-law with plateau widths of 300 Myr and 1 Gyr \textemdash the first as a proxy for both
-
-\begin{enumerate}
-    \item A simple power law with slope $\alpha$:
+\paragraph{Power-law} A simple power law with slope $\alpha$:
 \begin{equation}
@@
 where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
-    We investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$, following the field galaxy and galaxy cluster DTDs of \citet{Maoz2017-CosmicDTD}, respectively.
+We investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$, which correspond to the field galaxy and galaxy cluster DTDs of \citet{Maoz2017-CosmicDTD}, respectively.
 
-    \item A ``plateau'' model consisting of a flat slope of width $W$ followed by a power law decline with normalization $B_W$:
+\paragraph{Plateau} A ``plateau'' model consisting of a flat slope of width $W$ followed by a power law decline with normalization $B_W$:
 \begin{equation}
@@
 
-    \item An exponentially declining DTD with timescale $\tau$ and normalization $C_\tau$:
+\paragraph{Exponential} An exponentially declining DTD with timescale $\tau$ and normalization $C_\tau$:
 \begin{equation}
-        R(t) = 1/\tau \exp(-t/\tau)
+    R(t) = \frac{1}{\tau} e^{-t/\tau}
     \label{eq:exponential-dtd}
@@
 
-    \item A DTD in which 50\% of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the other 50\% form an exponential tail at large $t$, normalized by $D_{t_p,\sigma,\tau}$:
+\paragraph{Prompt} A DTD in which 50\% of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the other 50\% form an exponential tail at large $t$, normalized by $D_{t_p,\sigma,\tau}$:
 \begin{equation}
-        R(t) = D_{t_p,\sigma,\tau} \Big[\exp\Big(-\frac{(t-t_p)^2}{2\sigma^2}\Big) + \exp(-t/\tau)\Big]
+    R(t) = D_{t_p,\sigma,\tau} \Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
     \label{eq:prompt-dtd}
@@
 
-    \item A DTD based on simulations of triple-system evolution by \citet{Rajamuthukumar2022-TripleEvolution}.
+\paragraph{Triple} A DTD based on simulations of triple-system evolution by \citet{Rajamuthukumar2022-TripleEvolution}.
 We approximate their DTD as a special case of the plateau model (Equation \ref{eq:plateau-dtd}) where the initial rate is quite low until an instantaneous rise to the plateau value at time $t_{\rm rise}$:
@@
 We take $t_{\rm rise}=0.5$ Gyr, $W=0.5$ Gyr, $\alpha=-1.1$, and $\epsilon=0.05$ so the initial rate is 5\% of the peak rate.
-\end{enumerate}
+
+\subsection{Star Formation Histories}
+\label{sec:sfh}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/star_formation_histories.pdf}
+    \caption{Caption}
+    \label{fig:sfhs}
+    \script{star_formation_histories.py}
+\end{figure*}
+
+\paragraph{Inside-out}
+\begin{equation}
+    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm SFH}}
+    \label{eq:insideout-sfh}
+\end{equation}
+
+\paragraph{Late-burst}
+\begin{equation}
+    f_{\rm LB}(t|R_{\rm gal}) = f_{\rm IO}(t|R_{\rm gal}) \Big(1 + A_b e^{-(t-t_b)^2/2\sigma_b^2} \Big)
+\end{equation}
+
+\paragraph{Early-burst} The infall rate at a given radius declines exponentially with time:
+\begin{equation}
+    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm IFR}}
+    \label{eq:earlyburst-ifr}
+\end{equation}
+We take $\tau_{\rm IFR} = \tau_{\rm SFH}$ at all radii.
+The time-dependence of the SFE timescale $\tau_*$ comes from \citet{Conroy2022-ThickDisk}:
+\begin{equation}
+    \frac{\tau_*}{1\,\rm{Gyr}} =
+    \begin{cases}
+        50 & t < 2.5\,\rm{Gyr} \\
+        50/[1+3(t-2.5)]^2 & 2.5\leq t \leq 3.7\,\rm{Gyr} \\
+        2.36 & t > 3.7\,\rm{Gyr}
+    \end{cases}
+    \label{eq:earlyburst-taustar}
+\end{equation}
+
+\paragraph{Two-infall}
+
+\subsection{Stellar Migration}
+\label{sec:migration}
+
+\citet{Johnson2021-Migration}
+
+We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm initial}$ from the \texttt{h277} output in bins of $R_{\rm initial}$ and age.
+Each Gaussian is centered at 0 and we find that the scale $\sigma_{\Delta R}$ is best described by the function
+
+\begin{equation}
+    \sigma_{\Delta R} = 1.35\,{\rm kpc} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61} \Big(\frac{\tau}{1\,{\rm Gyr}}\Big)^{0.33}
+    \label{eq:radial-migration}
+\end{equation}
+
+\noindent where $\tau$ is the age of the star particle.
+
+We fit a sech$^2$ function \citep{Spitzer1942} to the distribution of midplane distances $z_{\rm final}$.
+Vertical migration away from the midplane does not affect the chemical evolution simulation, but we do use $z_{\rm final}$ in our analysis.
+The probability density function (PDF) of $z_{\rm final}$ given some scale height $h_z$ is
+
+\begin{equation}
+    {\rm PDF}(z_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z_{\rm final}}{2 h_z}\Big)
+    \label{eq:sech-pdf}
+\end{equation}
+
+\noindent and the corresponding cumulative distribution function (CDF) is
+
+\begin{equation}
+    {\rm CDF}(z_{\rm final}) = \frac{1}{1 + e^{-z_{\rm final} / h_z}}.
+    \label{eq:sech-cdf}
+\end{equation}
+
+\noindent We fit the above function to the distributions of $z_{\rm final}$ in h277 in varying bins of $\tau$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
+
+\begin{equation}
+    h_z = (0.25\,{\rm kpc}) 
+    e^{\frac{\tau-5\,{\rm Gyr}}{7.0\,{\rm Gyr}}}
+    e^{\frac{R_{\rm final}-8\,{\rm kpc}}{6.0\,{\rm kpc}}}
+    \label{eq:scale-height}
+\end{equation}
 
@@
 We identify prior mass loss as the cause of this discrepancy, so the astroNN ages are likely closer to the truth.
-
-\subsection{Chemical Evolution Models}
-\label{sec:vice-models}
-
-\subsubsection{Stellar Migration}
-\label{sec:migration}
-
-\citet{Johnson2021-Migration}
-
-We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm initial}$ from the \texttt{h277} output in bins of $R_{\rm initial}$ and age.
-Each Gaussian is centered at 0 and we find that the scale $\sigma_{\Delta R}$ is best described by the function
-
-\begin{equation}
-    \sigma_{\Delta R} = 1.35\,{\rm kpc}(R_{\rm form}/8\,{\rm kpc})^{0.61} (\tau/1\,{\rm Gyr})^{0.33}
-    \label{eq:radial-migration}
-\end{equation}
-
-\noindent where $\tau$ is the age of the star particle.
-
-We fit a sech$^2$ function \citep{Spitzer1942} to the distribution of midplane distances $z_{\rm final}$.
-Vertical migration away from the midplane does not affect the chemical evolution simulation, but we do use $z_{\rm final}$ in our analysis.
-The probability density function (PDF) of $z_{\rm final}$ given some scale height $h_z$ is
-
-\begin{equation}
-    {\rm PDF}(z_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z_{\rm final}}{2 h_z}\Big)
-    \label{eq:sech-pdf}
-\end{equation}
-
-\noindent and the corresponding cumulative distribution function (CDF) is
-
-\begin{equation}
-    {\rm CDF}(z_{\rm final}) = \frac{1}{1 + \exp(-z_{\rm final} / h_z)}.
-    \label{eq:sech-cdf}
-\end{equation}
-
-\noindent We fit the above function to the distributions of $z_{\rm final}$ in h277 in varying bins of $\tau$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
-
-\begin{equation}
-    h_z = (0.25\,{\rm kpc}) 
-    \exp\Big(\frac{\tau-5\,{\rm Gyr}}{7.0\,{\rm Gyr}}\Big)
-    \exp\Big(\frac{R_{\rm final}-8\,{\rm kpc}}{6.0\,{\rm kpc}}\Big)
-    \label{eq:scale-height}
-\end{equation}
 

### 2023-06-20 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \includegraphics{figures/star_formation_histories.pdf}
-    \caption{Caption}
+    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equations \ref{eq:twoinfall-ifr} and \ref{eq:twoinfall-taustar}).
+In each panel, we plot curves for the zones which have inner radii of 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
     \label{fig:sfhs}
@@
     f_{\rm LB}(t|R_{\rm gal}) = f_{\rm IO}(t|R_{\rm gal}) \Big(1 + A_b e^{-(t-t_b)^2/2\sigma_b^2} \Big)
+    \label{eq:lateburst-sfh}
 \end{equation}
@@
 \begin{equation}
-    \frac{\tau_*}{1\,\rm{Gyr}} =
+    \frac{\tau_*(t|\Sigma_g)}{1\,\rm{Gyr}} =
     \begin{cases}
-        50 & t < 2.5\,\rm{Gyr} \\
-        50/[1+3(t-2.5)]^2 & 2.5\leq t \leq 3.7\,\rm{Gyr} \\
-        2.36 & t > 3.7\,\rm{Gyr}
+        50, & t < 2.5\,\rm{Gyr} \\
+        \frac{50}{[1+3(t-2.5)]^2}, & 2.5\leq t \leq 3.7\,\rm{Gyr} \\
+        2.36, & t > 3.7\,\rm{Gyr}
     \end{cases}
+    \label{eq:earlyburst-conroy22}
+\end{equation}
+We combine this with the Kennicutt-Schmidt relation used by \citet{Johnson2021-Migration}, minus the dependence on the molecular timescale $\tau_{\rm mol}$:
+\begin{equation}
+    \dot \Sigma_* = 
+    \begin{cases}
+        \Sigma_g, & \Sigma_g \geq \Sigma_{g,2} \\
+        \Sigma_g \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
+        \Sigma_g \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1}
+    \end{cases}
+    \label{eq:kennicutt-schmidt}
+\end{equation}
+Which leads to an overall SFE timescale of
+\begin{equation}
+    \tau_*(t,\Sigma_g) = \tau_*(t|\Sigma_g) \frac{\Sigma_g}{\dot \Sigma_*}
     \label{eq:earlyburst-taustar}
@@
 \paragraph{Two-infall} 
+We parameterize the infall rate as two successive, exponentially declining bursts as in \citet{Chiappini2001-AbundanceGradients}:
+\begin{equation}
+    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2}
+\end{equation}
+with normalization coefficients
+\begin{equation}
+    N_1(R_{\rm gal}) = \frac{\Sigma_{1,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_1}}{\tau_1 (1-e^{-t_{\rm max}/\tau_1})}
+\end{equation}
+and
+\begin{equation}
+    N_2(R_{\rm gal}) = \frac{\Sigma_{2,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_2}}{\tau_2 (1-e^{-(t_{\rm max}-t_{\rm on})/\tau_2})}
+\end{equation}
+Second infall onset time $t_{\rm on}=4$ Gyr, infall timescales $\tau_1=1$ Gyr and $\tau_2=4$ Gyr.
+We take the surface mass density ratio of the thin disk to the thick disk at the Sun to be $(\frac{\Sigma_2}{\Sigma_1})_\odot=5.6$ \citep{Spitoni2021-TwoInfall}.
 

### 2023-06-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-We use APOGEE DR17 \citep{Abdurro'uf2022-SDSSIV-DR17}. Our selection criteria are presented in Table \ref{tab:sample-selection}, producing a final sample of 192,926 stars.
+We use APOGEE DR17 \citep{Abdurro'uf2022-SDSSIV-DR17}.
+Our selection criteria are presented in Table \ref{tab:sample-selection}, producing a final sample of \variable{output/sample_size.txt} stars.
+We limit to stars with a reported measurement of both [Fe/H] and [O/Fe].
+APOGEE survey \citep{Majewski2017-APOGEE}, spectrographs \citep{Wilson2019-APOGEE-Spectrographs}, ASPCAP \citep{Holtzmann2015-ASPCAP,GarciaPerez2016-ASPCAP}, 2.5-meter Sloan Foundation Telescope \citep{Gunn2006-SloanTelescope} at Apache Point Observatory, New Mexico.
+Ir{\'e}n{\'e}e DuPont Telescope \citep{BowenVaughan1973-DuPontTelescope} at Las Campanas Observatory, Chile for Southern Hemisphere observations.
+Data reduction pipeline \citep{Nidever2015-APOGEE-DataReduction}, model grids and interpolation method \citep{Jonsson2020-APOGEE-DR16}.
 
@@
 They find that the parameters which have a large effect on the shape of the DTD are the distribution and range of stellar masses in progenitor systems; the efficiency of accretion in the SD scenario; and the distribution of separations at birth in the DD scenario.
-Figure \ref{fig:greggio05-dtd} shows the analytical DTDs for SD progenitors and two different prescriptions for DD progenitors (``WIDE'' and ``CLOSE'').
+Figure \ref{fig:dtd-greggio05} shows the analytical DTDs for SD progenitors and two different prescriptions for DD progenitors (``WIDE'' and ``CLOSE'').
 In the ``WIDE'' scheme, it is assumed that there is a wide distribution of ratios $A/A_0$ of the separation of the DD system to the initial separation of the binary, and that the distributions of $A$ and total mass of the system $m_{\rm{DD}}$ are independent, so one cannot necessarily predict the total merge time of a system based on its initial parameters.
@@
 We obtain best-fit parameters $\alpha_1=-0.19$, $A_{\rm{rise}}=1.7$, $\tau_{\rm{rise}}=0.084$ Gyr, $\alpha_2=-0.91$, $A_{\rm{tail}}=0.85$, and $\tau_{\rm{tail}}=0.088$ Gyr for the ``WIDE'' scheme, and $\alpha_1=-0.53$, $A_{\rm{rise}}=3.0$, $\tau_{\rm{rise}}=0.042$ Gyr, $\alpha_2=-1.1$, $A_{\rm{tail}}=0.62$, and $\tau_{\rm{tail}}=0.11$ Gyr for the ``CLOSE'' scheme.\footnote{
-Our implementation of these best-fit approximations, as well as the original SD and DD formulations, is available in the GitHub repository for this paper.
-} These best-fit approximations are represented by the dashed curves in Figure \ref{fig:greggio05-dtd} \citep[see also Figure 8 in][]{Greggio2005-AnalyticalRates}.
+Our implementation of these best-fit approximations, as well as the original SD and DD formulations, is available in the GitHub repository for this paper: \GitHubURL
+} These best-fit approximations are represented by the dashed curves in Figure \ref{fig:dtd-greggio05} \citep[see also Figure 8 in][]{Greggio2005-AnalyticalRates}.
 The difference between the true analytical DTDs and our best-fit approximations is small enough as to be irrelevant for our purposes, so for the rest of this section we rely on the best-fit approximations for faster simulations.
@@
 
-\begin{deluxetable*}{ll|cccc}
+\begin{deluxetable*}{ll|ccccc}
 \label{tab:results}
 \tablehead{
-\colhead{DTD} & \colhead{SFH} & \colhead{MDF} & \colhead{ODF} & \colhead{[Fe/H]--[O/Fe]} & \colhead{Age--[O/Fe]}
+    \colhead{DTD} & \colhead{SFH} & \colhead{[Fe/H] DF} & \colhead{[O/Fe] DF} & 
+    \colhead{[Fe/H]--[O/Fe]} & \colhead{Age--[O/Fe]} & \colhead{Bimodality}
 }
 \startdata
-Power law               & Inside-out    & \meh  & \no   & \meh  & \no     \\
-($\alpha=-1.1$)         & Late burst    & \meh  & \no   & \meh  & \no     \\
-                        & Early burst   & \no   & \yes  & \meh  & \meh    \\
-                        & Two-infall    & \no   & \no   & \meh  & \no     \\
+Power law & Inside-out & \no & \meh & \meh & \no & \no \\
+($\alpha=-1.1$) & Late-burst & \no & \no & \meh & \no & \no \\
+ & Early-burst & \yes & \no & \no & \meh & \yes \\
+ & Two-infall & \yes & \meh & \meh & \no & \no \\ 
 \hline
-Power law               & Inside-out    & \meh  & \no   & \no   & \no     \\
-($\alpha=-1.4$)         & Late burst    & \meh  & \no   & \no   & \no     \\
-                        & Early burst   & \no   & \yes  & \no   & \meh    \\
-                        & Two-infall    & \no   & \no   & \no   & \no     \\
+Power law & Inside-out & \no & \no & \no & \no & \no \\
+($\alpha=-1.4$) & Late-burst & \no & \no & \no & \no & \no \\
+ & Early-burst & \meh & \no & \no & \no & \yes \\
+ & Two-infall & \no & \no & \no & \no & \no \\ 
 \hline
-Exponential             & Inside-out    & \yes  & \no   & \yes  & \no     \\
-($\tau=1.5$ Gyr)        & Late burst    & \yes  & \no   & \yes  & \no     \\
-                        & Early burst   & \no   & \yes  & \meh  & \yes    \\
-                        & Two-infall    & \yes  & \meh  & \meh  & \meh    \\
+Exponential & Inside-out & \meh & \meh & \meh & \no & \no \\
+($\tau=1.5$ Gyr) & Late-burst & \meh & \yes & \meh & \meh & \yes \\
+ & Early-burst & \no & \no & \no & \meh & \yes \\
+ & Two-infall & \yes & \meh & \meh & \meh & \yes \\ 
 \hline
-Exponential             & Inside-out    & \yes  & \meh  & \yes  & \meh    \\
-($\tau=3$ Gyr)          & Late burst    & \yes  & \meh  & \yes  & \meh    \\
-                        & Early burst   & \no   & \yes  & \no   & \yes    \\
-                        & Two-infall    & \meh  & \meh  & \meh  & \meh    \\
+Exponential & Inside-out & \yes & \yes & \yes & \meh & \no \\
+($\tau=3.0$ Gyr) & Late-burst & \meh & \yes & \yes & \yes & \yes \\
+ & Early-burst & \meh & \no & \meh & \yes & \yes \\
+ & Two-infall & \yes & \meh & \meh & \yes & \yes \\ 
 \hline
-Plateau                 & Inside-out    & \yes  & \meh  & \yes  & \no     \\
-($W=0.3$ Gyr)           & Late burst    & \yes  & \no   & \yes  & \no     \\
-                        & Early burst   & \no   & \yes  & \meh  & \yes    \\
-                        & Two-infall    & \yes  & \meh  & \yes  & \meh    \\
+Plateau & Inside-out & \meh & \yes & \yes & \meh & \no \\
+($W=0.3$ Gyr) & Late-burst & \no & \yes & \yes & \meh & \yes \\
+ & Early-burst & \meh & \meh & \no & \yes & \yes \\
+ & Two-infall & \yes & \yes & \yes & \meh & \yes \\ 
 \hline
-Plateau                 & Inside-out    & \meh  & \meh  & \yes  & \meh    \\
-($W=1.0$ Gyr)           & Late burst    & \meh  & \meh  & \yes  & \meh    \\
-                        & Early burst   & \no   & \yes  & \no   & \yes    \\
-                        & Two-infall    & \meh  & \meh  & \meh  & \meh    \\
+Plateau & Inside-out & \yes & \yes & \yes & \meh & \no \\
+($W=1.0$ Gyr) & Late-burst & \no & \yes & \yes & \yes & \yes \\
+ & Early-burst & \meh & \meh & \meh & \yes & \yes \\
+ & Two-infall & \yes & \yes & \yes & \yes & \yes \\ 
 \hline
-Prompt                  & Inside-out    & \meh  & \no   & \no   & \no     \\
-($t_{\rm max}=0.05$ Gyr)& Late burst    & \meh  & \no   & \no   & \no     \\
-                        & Early burst   & \no   & \yes  & \no   & \yes    \\
-                        & Two-infall    & \yes  & \no   & \no   & \no     \\
+Prompt & Inside-out & \no & \no & \no & \no & \no \\
+($t_{\rm max}=0.05$ Gyr) & Late-burst & \no & \no & \no & \no & \yes \\
+ & Early-burst & \yes & \no & \no & \meh & \yes \\
+ & Two-infall & \meh & \meh & \no & \no & \no \\ 
 \hline
-Triple system           & Inside-out    & \yes  & \meh  & \meh  & \yes    \\
-($t_{\rm{max}}=1$ Gyr)  & Late burst    & \yes  & \yes  & \meh  & \meh    \\
-                        & Early burst   & \no   & \meh  & \no   & \yes    \\
-                        & Two-infall    & \meh  & \meh  & \meh  & \meh    \\
+Triple system & Inside-out & \yes & \yes & \yes & \yes & \no \\
+($t_{\rm max}=1.0$ Gyr) & Late-burst & \no & \yes & \yes & \yes & \yes \\
+ & Early-burst & \meh & \meh & \meh & \yes & \yes \\
+ & Two-infall & \yes & \meh & \yes & \yes & \yes \\
 \enddata
 \end{deluxetable*}
+
+\subsection{Radial Migration \& Bimodality}
+
+Something about \citet{Johnson2021-Migration} and \citet{Schonrich2009-RadialMixing}.
 
@@
 
-Blah
+\begin{itemize}
+
+    \item Our diagnostics consistently favor a DTD with a large fraction of delayed SNe Ia, such as the 3 Gyr exponential, 1 Gyr plateau, or triple system evolution models, over a DTD with a high number of prompt SNe Ia, such as the $t^{-1.4}$ power law or prompt models.
+[Discuss the disconnect and/or complement with \citet{Maoz2017-CosmicDTD}, etc.; something about different timescales probed by volumetric surveys vs.
+us]
+
+    \item While the choice of DTD cannot produce a bimodal distribution of [O/Fe], it can affect the shape of the distribution, the ratio of high-$\alpha$ to low-$\alpha$ stars, and the location of the high-$\alpha$ sequence if it exists.
+The SFH is the critical determining factor in bimodality.
+
+    \item The distribution of [Fe/H] depends strongly on the chosen SFH, but there is only a weak effect from the DTD.
+
+    \item The early-burst SFH model is the only one which produced a bimodal distribution of [O/Fe] across the disk resembling APOGEE, from the models we investigate.
+[Add: summary of why everything else fails.]
+
+    \item [Something about how radial migration can't produce bimodality on its own]
+
+\end{itemize}
 
 \begin{acknowledgments}
+
 Funding for the Sloan Digital Sky 
@@
 and Yale University.
+
 \end{acknowledgments}
@@
 
+\section{Reproducibility}
+\label{app:reproducibility}
+
+This study was carried out using the reproducibility software
+\href{https://github.com/showyourwork/showyourwork}{\showyourwork}
+\citep{Luger2021-showyourwork}, which leverages continuous integration to
+programmatically download the data from
+\href{https://zenodo.org/}{zenodo.org}, create the figures, and
+compile the manuscript. Each figure caption contains two links: one
+to the dataset stored on zenodo used in the corresponding figure,
+and the other to the script used to make the figure (at the commit
+corresponding to the current build of the manuscript). The git
+repository associated to this study is publicly available at
+\GitHubURL, and the release v.X.X allows anyone to re-build the entire 
+manuscript. The datasets are stored at [URL].
+
 \bibliography{bib}

### 2023-06-30 src/scripts/simulations.py
add simulations rule + zenodo cache

@@ -11,30 +11,30 @@ DTD_LIST = [
     {'name': 'powerlaw_slope11',
      'model': 'powerlaw',
      'params': {'slope': -1.1}},
-    {'name': 'powerlaw_slope14',
-     'model': 'powerlaw',
-     'params': {'slope': -1.4}},
-    {'name': 'exponential_timescale15',
-     'model': 'exponential',
-     'params': {'timescale': 1.5}},
-    {'name': 'exponential_timescale30',
-     'model': 'exponential',
-     'params': {'timescale': 3.}},
-    {'name': 'plateau_width300_slope11',
-     'model': 'plateau',
-     'params': {'width': 0.3, 'slope': -1.1}},
-    {'name': 'plateau_width1000_slope11',
-     'model': 'plateau',
-     'params': {'width': 0.3, 'slope': -1.1}},
-    {'name': 'prompt_peak050_stdev015_timescale30',
-     'model': 'prompt',
-     'params': {'peak': 0.05, 'stdev': 0.015, 'timescale': 3.}},
-    {'name': 'triple_rise500_width500_slope11',
-     'model': 'triple',
-     'params': {'rise_time': 0.5, 'width': 0.5, 'slope': -1.1}},
+    # {'name': 'powerlaw_slope14',
+    #  'model': 'powerlaw',
+    #  'params': {'slope': -1.4}},
+    # {'name': 'exponential_timescale15',
+    #  'model': 'exponential',
+    #  'params': {'timescale': 1.5}},
+    # {'name': 'exponential_timescale30',
+    #  'model': 'exponential',
+    #  'params': {'timescale': 3.}},
+    # {'name': 'plateau_width300_slope11',
+    #  'model': 'plateau',
+    #  'params': {'width': 0.3, 'slope': -1.1}},
+    # {'name': 'plateau_width1000_slope11',
+    #  'model': 'plateau',
+    #  'params': {'width': 0.3, 'slope': -1.1}},
+    # {'name': 'prompt_peak050_stdev015_timescale30',
+    #  'model': 'prompt',
+    #  'params': {'peak': 0.05, 'stdev': 0.015, 'timescale': 3.}},
+    # {'name': 'triple_rise500_width500_slope11',
+    #  'model': 'triple',
+    #  'params': {'rise_time': 0.5, 'width': 0.5, 'slope': -1.1}},
 ]
 # Star formation history models
[…]

### 2023-06-30 src/scripts/snakesim.py

@@ -1,0 +1,51 @@
+"""
+This script runs a VICE multizone simulation from snakemake parameters.
+"""
+
+import multizone
+import paths
+import _globals
+
+def main():
+    r"""
+    Runs the script.
+    """
+    fullpath = paths.root / snakemake.output / 'diskmodel'
+    model_ = model(str(fullpath), snakemake.params)
+    model_.run([_ * model_.dt for _ in range(round(
+        _globals.END_TIME / model_.dt) + 1)],
+        overwrite = True, pickle = False)
+
+
+def model(name, params):
+    r"""
+    Get the milkyway object corresponding to the desired simulation.
+
+    Parameters
+    ----------
+    args : argparse.Namespace
+        The command line arguments parsed via argparse.
+    """
+    config = multizone.src.config(
+        timestep_size = _globals.DT,
+        star_particle_density = _globals.NSTARS,
+        zone_width = _globals.ZONE_WIDTH,
+        elements = _globals.ELEMENTS
+    )
+    kwargs = dict(
+        name = name,
+        spec = params.evolution,
+        RIa = params.RIa,
+        RIa_kwargs = params.RIa_params,
+        delay = params.minimum_delay,
+        yields = params.yields
+    )
+    if params.migration == "post-process":
+        kwargs["simple"] = True
+    else:
+        kwargs["migration_mode"] = params.migration
+    return multizone.src.diskmodel.from_config(config, **kwargs)
+
+
+if __name__ == '__main__':
+    main()

### 2023-06-30 src/scripts/star_formation_histories.py

@@ -15,7 +15,8 @@ from colormaps import paultol
 plt.rcParams['axes.prop_cycle'] = plt.cycler('color', paultol.vibrant.colors)
 
 MIGRATION = 'gaussian'
-EVOLUTION_LIST = ['insideout', 'lateburst', 'earlyburst', 'twoinfall']
+# EVOLUTION_LIST = ['insideout', 'lateburst', 'earlyburst', 'twoinfall']
+EVOLUTION_LIST = ['insideout', 'insideout', 'insideout', 'insideout']
 DTD = 'powerlaw_slope11'
 CMAP_NAME = 'plasma_r'
 

### 2023-06-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \author[0000-0002-6534-8783]{James W. Johnson}
-\author[0000-0001-7775-7261]{David H. Weinberg}
+% \author[0000-0001-7775-7261]{David H. Weinberg}
 
@@
 \begin{equation}
+    \label{eq:twoinfall-ifr}
     f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2}
 \end{equation}
-with normalization coefficients
+% with normalization coefficients
+% \begin{equation}
+%     N_1(R_{\rm gal}) = \frac{\Sigma_{1,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_1}}{\tau_1 (1-e^{-t_{\rm max}/\tau_1})}
+% \end{equation}
+% and
+% \begin{equation}
+%     N_2(R_{\rm gal}) = \frac{\Sigma_{2,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_2}}{\tau_2 (1-e^{-(t_{\rm max}-t_{\rm on})/\tau_2})}
+% \end{equation}
+% Second infall onset time $t_{\rm on}=4$ Gyr, infall timescales $\tau_1=1$ Gyr and $\tau_2=4$ Gyr.
+We take the surface mass density ratio of the thin disk to the thick disk at the Sun to be $(\frac{\Sigma_2}{\Sigma_1})_\odot=5.6$ \citep{Spitoni2021-TwoInfall}.
+The normalization ratio $N_2/N_1$ is calculated so that the ratio of stellar surface mass density produced by the second infall relative to the first follows
 \begin{equation}
-    N_1(R_{\rm gal}) = \frac{\Sigma_{1,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_1}}{\tau_1 (1-e^{-t_{\rm max}/\tau_1})}
+    \frac{\Sigma_2}{\Sigma_1} = \Big(\frac{\Sigma_2}{\Sigma_1}\Big)_{R_0} e^{(R-R_0)(1/h{R,2} - 1/h_{R,1})}
 \end{equation}
-and
-\begin{equation}
-    N_2(R_{\rm gal}) = \frac{\Sigma_{2,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_2}}{\tau_2 (1-e^{-(t_{\rm max}-t_{\rm on})/\tau_2})}
-\end{equation}
-Second infall onset time $t_{\rm on}=4$ Gyr, infall timescales $\tau_1=1$ Gyr and $\tau_2=4$ Gyr.
-We take the surface mass density ratio of the thin disk to the thick disk at the Sun to be $(\frac{\Sigma_2}{\Sigma_1})_\odot=5.6$ \citep{Spitoni2021-TwoInfall}.
+where $h_{R,1}=2.0$ kpc and $h_{R,2}=3.5$ kpc are the thick- and thin-disk scale radii, respectively, found by \citet{Bovy2012-SubPopulationStructure}.
+We take the local thick- to thin-disk surface density ratio $(\Sigma_1/\Sigma_2)_{R_0}=0.05$ for [reasons].
 

### 2023-07-05 src/tex/ms.tex
[showyourwork] overleaf sync

--- 2023-06-30 src/tex/ms.tex
@@
 
+Figure \ref{fig:sfhs} presents an overview of our model star formation histories.
+
 \begin{figure*}
@@
     \includegraphics{figures/star_formation_histories.pdf}
-    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equations \ref{eq:twoinfall-ifr} and \ref{eq:twoinfall-taustar}).
+    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
 In each panel, we plot curves for the zones which have inner radii of 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
@@
 \begin{equation}
+    \label{eq:twoinfall-ifr}
     f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2}
 \end{equation}
-with normalization coefficients
+In this model, the first infall produces the thick disk and the second infall produces the thin disk.
+The normalization ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
 \begin{equation}
-    N_1(R_{\rm gal}) = \frac{\Sigma_{1,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_1}}{\tau_1 (1-e^{-t_{\rm max}/\tau_1})}
+    f_\Sigma(R) = f_\Sigma(0) e^{R(1/R_2 - 1/R_1)}
 \end{equation}
-and
-\begin{equation}
-    N_2(R_{\rm gal}) = \frac{\Sigma_{2,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_2}}{\tau_2 (1-e^{-(t_{\rm max}-t_{\rm on})/\tau_2})}
-\end{equation}
-Second infall onset time $t_{\rm on}=4$ Gyr, infall timescales $\tau_1=1$ Gyr and $\tau_2=4$ Gyr.
-We take the surface mass density ratio of the thin disk to the thick disk at the Sun to be $(\frac{\Sigma_2}{\Sigma_1})_\odot=5.6$ \citep{Spitoni2021-TwoInfall}.
+where we take the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$ following \citet{BlandHawthornGerhard2016-MilkyWayReview}.
 
@@
 
-\citet{Johnson2021-Migration}
+For each star particle in VICE, \citet{Johnson2021-Migration} randomly assign an analogue star particle from \texttt{h277} and adopt its radial migration distance $\Delta R$ and final midplane distance $z$.
+This allows VICE to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
+However, in regions where the number of h277 star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single h277 star particle can be assigned as an analogue to multiple VICE stellar populations.
+These populations will have similar formation and migration histories and consequently similar abundances, which produces unphysical ``clumps'' of stars in the abundance distributions at high  latitudes and large radii.
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/radial_migration.pdf}
+    \caption{Caption.}
+    \label{fig:radial-migration}
+    \script{radial_migration.py}
+\end{figure*}
 
@@
 
+% TODO make table with numerical scores (KL divergences, etc) for supplementary material
+% TODO explain that precise statistical understanding of these scores is outside the scope of the paper
+
 \begin{deluxetable*}{ll|ccccc}

### 2023-07-06 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \includegraphics{figures/radial_migration.pdf}
-    \caption{Caption.}
+    \caption{The distribution of final radius as a function of formation radius and age for the h277 analogue (top row) and Gaussian sampling scheme (bottom row).
+From left to right, star particles are binned by formation annulus, from the inner disk (far left column) to the Solar annulus (center column) to the outer disk (far right column).
+Within each panel, colored curves represent the different age bins, ranging from the youngest stars (dark blue) to the oldest (dark red).
+The vertical dotted black lines indicate the bounds of each bin in formation radius; stars within that region of the distribution have not migrated outside their birth annulus over their lifetime.}
     \label{fig:radial-migration}
     \script{radial_migration.py}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/midplane_distance.pdf}
+    \caption{Similar to Figure \ref{fig:radial-migration} but for the distribution of final midplane distance $z_{\rm final}$ as a function of final radius and age.
+From left to right, star particles are binned by \textit{final} annulus.}
+    \label{fig:midplane-distance}
+    \script{midplane_distance.py}
 \end{figure*}
@@
     \caption{Abundance tracks and distributions from one-zone models with the analytical DTDs from \citet{Greggio2005-AnalyticalRates}.
-\textit{Left:} a comparison between the analytical SD DTD (solid curve), an exponential DTD with a 1.5 Gyr timescale (dashed curve), and a power-law DTD with a slope of -1.1 (dotted curve).
-\textit{Right:} a comparison between two different prescriptions for an analytical DD DTD (solid curves), power-law DTDs with an initial plateau of 1 Gyr and 350 Myr (dashed curves), and a power-law DTD with no plateau and a slope of -1.1 (dotted curve).}
+\textit{Left:} a comparison between the analytical SD DTD (solid magenta curve), an exponential DTD with a 1.5 Gyr timescale (dashed pink curve), and a power-law DTD with a slope of -1.1 (dotted black curve).
+\textit{Right:} a comparison between WIDE and CLOSE prescriptions for an analytical DD DTD (solid blue and green curves, respectively), power-law DTDs with an initial plateau of 1 Gyr and 300 Myr (dashed cyan and yellow curves, respectively), and a power-law DTD with no plateau and a slope of -1.1 (dotted black curve).}
     \label{fig:onezone-greggio05}

### 2023-07-07 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\begin{deluxetable*}{ll|ccccc}
-\label{tab:results}
-\tablehead{
-    \colhead{DTD} & \colhead{SFH} & \colhead{[Fe/H] DF} & \colhead{[O/Fe] DF} & 
-    \colhead{[Fe/H]--[O/Fe]} & \colhead{Age--[O/Fe]} & \colhead{Bimodality}
-}
-\startdata
-Power law & Inside-out & \no & \meh & \meh & \no & \no \\
-($\alpha=-1.1$) & Late-burst & \no & \no & \meh & \no & \no \\
- & Early-burst & \yes & \no & \no & \meh & \yes \\
- & Two-infall & \yes & \meh & \meh & \no & \no \\ 
-\hline
-Power law & Inside-out & \no & \no & \no & \no & \no \\
-($\alpha=-1.4$) & Late-burst & \no & \no & \no & \no & \no \\
- & Early-burst & \meh & \no & \no & \no & \yes \\
- & Two-infall & \no & \no & \no & \no & \no \\ 
-\hline
-Exponential & Inside-out & \meh & \meh & \meh & \no & \no \\
-($\tau=1.5$ Gyr) & Late-burst & \meh & \yes & \meh & \meh & \yes \\
- & Early-burst & \no & \no & \no & \meh & \yes \\
- & Two-infall & \yes & \meh & \meh & \meh & \yes \\ 
-\hline
-Exponential & Inside-out & \yes & \yes & \yes & \meh & \no \\
-($\tau=3.0$ Gyr) & Late-burst & \meh & \yes & \yes & \yes & \yes \\
- & Early-burst & \meh & \no & \meh & \yes & \yes \\
- & Two-infall & \yes & \meh & \meh & \yes & \yes \\ 
-\hline
-Plateau & Inside-out & \meh & \yes & \yes & \meh & \no \\
-($W=0.3$ Gyr) & Late-burst & \no & \yes & \yes & \meh & \yes \\
- & Early-burst & \meh & \meh & \no & \yes & \yes \\
- & Two-infall & \yes & \yes & \yes & \meh & \yes \\ 
-\hline
-Plateau & Inside-out & \yes & \yes & \yes & \meh & \no \\
-($W=1.0$ Gyr) & Late-burst & \no & \yes & \yes & \yes & \yes \\
- & Early-burst & \meh & \meh & \meh & \yes & \yes \\
- & Two-infall & \yes & \yes & \yes & \yes & \yes \\ 
-\hline
-Prompt & Inside-out & \no & \no & \no & \no & \no \\
-($t_{\rm max}=0.05$ Gyr) & Late-burst & \no & \no & \no & \no & \yes \\
- & Early-burst & \yes & \no & \no & \meh & \yes \\
- & Two-infall & \meh & \meh & \no & \no & \no \\ 
-\hline
-Triple system & Inside-out & \yes & \yes & \yes & \yes & \no \\
-($t_{\rm max}=1.0$ Gyr) & Late-burst & \no & \yes & \yes & \yes & \yes \\
- & Early-burst & \meh & \meh & \meh & \yes & \yes \\
- & Two-infall & \yes & \meh & \yes & \yes & \yes \\
-\enddata
-\end{deluxetable*}
+\variable{output/summary_table.tex}
 

### 2023-07-10 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{amssymb}
-\usepackage{layouts}
+% \usepackage{layouts}
 \usepackage{xcolor}
@@
     \includegraphics{figures/delay_time_distributions.pdf}
-    \caption{Delay time distribution functions}
+    \caption{Models of the SN Ia delay time distribution used in this paper. All functions are normalized to $f_{\rm Ia}=1$ at $\tau=1$ Gyr.}
     \label{fig:dtds}
@@
     \includegraphics{figures/radial_migration.pdf}
-    \caption{The distribution of final radius as a function of formation radius and age for the h277 analogue (top row) and Gaussian sampling scheme (bottom row).
+    \caption{The distribution of final radius $R_{\rm final}$ as a function of formation radius and age for the h277 analogue (top row) and Gaussian sampling scheme (bottom row).
 From left to right, star particles are binned by formation annulus, from the inner disk (far left column) to the Solar annulus (center column) to the outer disk (far right column).
@@
 Figure \ref{fig:dtd-greggio05} shows the analytical DTDs for SD progenitors and two different prescriptions for DD progenitors (``WIDE'' and ``CLOSE'').
-In the ``WIDE'' scheme, it is assumed that there is a wide distribution of ratios $A/A_0$ of the separation of the DD system to the initial separation of the binary, and that the distributions of $A$ and total mass of the system $m_{\rm{DD}}$ are independent, so one cannot necessarily predict the total merge time of a system based on its initial parameters.
-In the ``CLOSE'' scheme, there is assumed to be a narrow distribution of $A/A_0$ and a correlation between $A$ and $m_{\rm{DD}}$, so the most massive binaries tend to merge quickly and the least massive merge last.
+In the ``WIDE'' scheme, it is assumed that there is a wide distribution of ratios $A/A_0$ of the separation of the DD system to the initial separation of the binary, and that the distributions of $A$ and total mass of the system $m_{\rm DD}$ are independent, so one cannot necessarily predict the total merge time of a system based on its initial parameters.
+In the ``CLOSE'' scheme, there is assumed to be a narrow distribution of $A/A_0$ and a correlation between $A$ and $m_{\rm DD}$, so the most massive binaries tend to merge quickly and the least massive merge last.
 
@@
 
-    \item [Something about how radial migration can't produce bimodality on its own]
+    \item Something about how radial migration can't produce bimodality on its own.
 
@@
 repository associated to this study is publicly available at
-\GitHubURL, and the release v.X.X allows anyone to re-build the entire 
+\url{\GitHubURL}, and the release v.X.X allows anyone to re-build the entire 
 manuscript. The datasets are stored at [URL].

### 2023-07-10 src/scripts/summary_table.py
fix output names

@@ -53,7 +53,7 @@ def gen_summary_table():
     with tqdm(total=len(SFH_LIST) * len(DTD_LIST)) as t:
         for dtd in DTD_LIST:
             for sfh in SFH_LIST:
-                output_name = '/'.join([MIGRATION, sfh, dtd])
+                output_name = '/'.join([MIGRATION, sfh, dtd, 'diskmodel'])
                 mzs = MultizoneStars.from_output(output_name)
                 mzs.model_uncertainty(apogee_data, inplace=True)
                 # Set up lists to track scores by region

### 2023-07-10 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+We explore five different functional forms for the SN Ia DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, an exponential with a prompt Gaussian component, with one or two different parameterizations for each.
+Figure \ref{fig:dtds} presents these DTDs as a function of time since star formation.
+
 \begin{figure}
@@
 
-\subsubsection{From Observations}
+% \citet{Stolger2020-ExponentialDTD} perform maximum likelihood estimations based on the cosmic star formation history and the star formation histories of individual galaxies.
+In both cases their best fit functions were approximately exponential, though they started with a skew-normal function so could not have ended up with a power law even if they wanted to.
+They don't actually report the timescale of this exponential, but based on the plots I'd say it's about 1.5 - 2 (1.7?) Gyr.
+Their best fit parameters make no sense to me as they don't report their units.
 
-\citet{Maoz2014-Review}
+\begin{deluxetable*}{lll}
+\tablecaption{Summary of SN Ia DTD models explored in this paper.}
+\tablehead{
+\colhead{Model} & \colhead{Parameters} & \colhead{Similar to}
+}
+\startdata
+Power-law   & $\alpha=-1.1$     & \citet[][field]{Maoz2017-CosmicDTD}; 
+                                  \citet{Wiseman2021-DESRates}              \\
+            & $\alpha=-1.4$     & \citet[][cluster]{Maoz2017-CosmicDTD}; 
+                                  \citet{Heringer2019-FieldGalaxyDTD}       \\
+Exponential & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
+                                  \citet{Schonrich2009-RadialMixing,
+                                         Weinberg2017-ChemicalEquilibrium}  \\
+            & $\tau=3.0$ Gyr    & \\
+Plateau     & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
+            & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
+Prompt      & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, $\tau=3.0$ Gyr & \citet{Mannucci2006-TwoPopulations} \\
+Triple      & & \citet{Rajamuthukumar2022-TripleEvolution}
+\enddata
+\end{deluxetable*}
+
+\paragraph{Power-law} A simple power law with slope $\alpha$:
+\begin{equation}
+    R(t) = A_\alpha (t/1\,\rm{Gyr})^\alpha
+    \label{eq:powerlaw-dtd}
+\end{equation}
+where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
+We investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$, which correspond to the field galaxy and galaxy cluster DTDs of \citet{Maoz2017-CosmicDTD}, respectively.
 
@@
 They also find that slower-declining SNe have a steeper DTD slope.
-
-Another commonly assumed functional form is an exponential.
-\citet{Schonrich2009-RadialMixing} take their DTD to be an exponential with a 1.5 Gyr timescale, though this isn't strictly observationally motivated.
-
-\citet{Stolger2020-ExponentialDTD} perform maximum likelihood estimations based on the cosmic star formation history and the star formation histories of individual galaxies.
-In both cases their best fit functions were approximately exponential, though they started with a skew-normal function so could not have ended up with a power law even if they wanted to.
-They don't actually report the timescale of this exponential, but based on the plots I'd say it's about 1.5 - 2 (1.7?) Gyr.
-Their best fit parameters make no sense to me as they don't report their units.
-
-% \begin{deluxetable}{lCl}
-% \tablecaption{Sources of the various forms of delay time distribution.}
-% \tablehead{
-% \colhead{Name} & \colhead{Form} & \colhead{Source}
-% }
-% \startdata
-% Field Galaxy Power-Law      & t^{-1.1}              & \citet{Maoz2017-CosmicDTD} \\   
-% Galaxy Cluster Power-Law    & t^{-1.4}              & \citet{Maoz2017-CosmicDTD} \\
-% Short Exponential           & e^{-t/1.5~\rm{Gyr}}  & \citet{Schonrich2009-RadialMixing} \\
-% \enddata
-% \end{deluxetable}
-
-\subsubsection{Theoretical Models}
-
-\citet{Matteucci1986-SupernovaEnrichment}
-
-\citet{Greggio2005-AnalyticalRates}
-
-\citet{Rajamuthukumar2022-TripleEvolution}
-
-\citet{Schonrich2009-RadialMixing,Weinberg2017-ChemicalEquilibrium} assume an exponential with $\tau=1.5$ Gyr
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/dtd_greggio05.pdf}
-    \caption{Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and close approximation simple functions (dashed curves).
-Some functions are presented with a constant multiplicative factor for visual clarity.}
-    \label{fig:dtd-greggio05}
-    \script{dtd_greggio05.py}
-\end{figure}
-
-\subsubsection{Our Models}
-
-We explore five different classes of DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, an exponential with a prompt Gaussian component, with one or two different parameterizations for each.
-Figure \ref{fig:dtds} presents these DTDs as a function of time since star formation.
-
-\paragraph{Power-law} A simple power law with slope $\alpha$:
-\begin{equation}
-    R(t) = A_\alpha (t/1\,\rm{Gyr})^\alpha
-    \label{eq:powerlaw-dtd}
-\end{equation}
-where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
-We investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$, which correspond to the field galaxy and galaxy cluster DTDs of \citet{Maoz2017-CosmicDTD}, respectively.
 
@@
 
+\begin{figure}
+    \centering
+    \includegraphics{figures/dtd_greggio05.pdf}
+    \caption{Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and close approximation simple functions (dashed curves).
+Some functions are presented with a constant multiplicative factor for visual clarity.}
+    \label{fig:dtd-greggio05}
+    \script{dtd_greggio05.py}
+\end{figure}
+
 \paragraph{Exponential} An exponentially declining DTD with timescale $\tau$ and normalization $C_\tau$:
@@
 We also investigate a longer timescale of $\tau=3$ Gyr.
+\citet{Matteucci1986-SupernovaEnrichment}, \citet{Stolger2020-ExponentialDTD}
 
@@
 
-An implementation of these DTDs in a chemical evolution model requires numerical integration (see their Equations 14, 33, and 34, respectively, for the exact functional forms), so to save on computation time we approximate the DTD for the DD prescriptions as a broken power-law with an exponential rise and tail:
-
-\begin{equation}
-    f_{\rm{Ia}}^{\rm{DD}}(t) \propto
-    \begin{cases}
-        t^{\alpha_1} (1 - A_{\rm{rise}} e^{-t/\tau_{\rm{rise}}}) & t \le 1~\rm{Gyr} \\
-        B t^{\alpha_2} (1 + A_{\rm{tail}} e^{-(t - 1~\rm{Gyr})/\tau_{\rm{tail}}}) & t > 1~\rm{Gyr}
-    \end{cases}
-    \label{eq:greggio05-approx}
-\end{equation}
-
-\noindent with the normalization $B$ of the second part set such that
-
-\begin{equation}
-    B = \frac{1}{1 + A_{\rm{tail}}} t^{(\alpha_1-\alpha_2)} (1 - A_{\rm{rise}} e^{-(1~\rm{Gyr})/\tau_{\rm{rise}}}).
-\end{equation}
-
-\noindent We use a non-linear least squares method to fit Equation \ref{eq:greggio05-approx} to the analytical DTDs for DD progenitors.
-We obtain best-fit parameters $\alpha_1=-0.19$, $A_{\rm{rise}}=1.7$, $\tau_{\rm{rise}}=0.084$ Gyr, $\alpha_2=-0.91$, $A_{\rm{tail}}=0.85$, and $\tau_{\rm{tail}}=0.088$ Gyr for the ``WIDE'' scheme, and $\alpha_1=-0.53$, $A_{\rm{rise}}=3.0$, $\tau_{\rm{rise}}=0.042$ Gyr, $\alpha_2=-1.1$, $A_{\rm{tail}}=0.62$, and $\tau_{\rm{tail}}=0.11$ Gyr for the ``CLOSE'' scheme.\footnote{
-Our implementation of these best-fit approximations, as well as the original SD and DD formulations, is available in the GitHub repository for this paper: \GitHubURL
-} These best-fit approximations are represented by the dashed curves in Figure \ref{fig:dtd-greggio05} \citep[see also Figure 8 in][]{Greggio2005-AnalyticalRates}.
-The difference between the true analytical DTDs and our best-fit approximations is small enough as to be irrelevant for our purposes, so for the rest of this section we rely on the best-fit approximations for faster simulations.
-
 % \begin{figure}

### 2023-07-10 src/tex/ms.tex
[showyourwork] overleaf sync

@@
                                   \citet{Wiseman2021-DESRates}              \\
-            & $\alpha=-1.4$     & \citet[][cluster]{Maoz2017-CosmicDTD}; 
+Power-law   & $\alpha=-1.4$     & \citet[][cluster]{Maoz2017-CosmicDTD}; 
                                   \citet{Heringer2019-FieldGalaxyDTD}       \\
 Exponential & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
-                                  \citet{Schonrich2009-RadialMixing,
-                                         Weinberg2017-ChemicalEquilibrium}  \\
+                                  \citet{Schonrich2009-RadialMixing};       \\
+            &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
+Exponential & $\tau=3.0$ Gyr    & \\
+Plateau     & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
+Plateau     & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
+Prompt      & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
             & $\tau=3.0$ Gyr & \\
-Plateau     & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
-            & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
-Prompt      & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, $\tau=3.0$ Gyr & \citet{Mannucci2006-TwoPopulations} \\
-Triple      & & \citet{Rajamuthukumar2022-TripleEvolution}
+Triple      & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2022-TripleEvolution} \\
+            & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
 \enddata

### 2023-07-11 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-We explore five different functional forms for the SN Ia DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, an exponential with a prompt Gaussian component, with one or two different parameterizations for each.
+We explore four different functional forms for the SN Ia DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, and an exponential with a prompt Gaussian component, with a few different parameterizations for each.
 Figure \ref{fig:dtds} presents these DTDs as a function of time since star formation.
@@
 
-\begin{deluxetable*}{lll}
-\tablecaption{Summary of SN Ia DTD models explored in this paper.}
-\tablehead{
-\colhead{Model} & \colhead{Parameters} & \colhead{Similar to}
-}
-\startdata
-Power-law   & $\alpha=-1.1$     & \citet[][field]{Maoz2017-CosmicDTD}; 
-                                  \citet{Wiseman2021-DESRates}              \\
-Power-law   & $\alpha=-1.4$     & \citet[][cluster]{Maoz2017-CosmicDTD}; 
-                                  \citet{Heringer2019-FieldGalaxyDTD}       \\
-Exponential & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
-                                  \citet{Schonrich2009-RadialMixing};       \\
-            &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
-Exponential & $\tau=3.0$ Gyr    & \\
-Plateau     & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
-Plateau     & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
-Prompt      & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
-            & $\tau=3.0$ Gyr & \\
-Triple      & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2022-TripleEvolution} \\
-            & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
-\enddata
-\end{deluxetable*}
-
 \paragraph{Power-law} A simple power law with slope $\alpha$:
@@
 where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
-We investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$, which correspond to the field galaxy and galaxy cluster DTDs of \citet{Maoz2017-CosmicDTD}, respectively.
-
-A typical form for the DTD is a power-law $t^\alpha$ where $\alpha\sim-1$.
-\citet{Maoz2017-CosmicDTD} compare volumetric SN Ia rates to the cosmic star formation history.
-They get a power law with a slope of $-1.13\pm 0.06$ for field galaxies, and a slope of $-1.39^{+0.32}_{-0.05}$ for galaxy clusters.
-
-\citet{Heringer2019-FieldGalaxyDTD} study the distribution of SNe Ia in field galaxies and get a power-law index of $-1.34^{+0.19}_{-0.17}$ which is closer to Maoz's cluster DTD.
-
-\citet{Wiseman2021-DESRates} measure the SN Ia rate in the redshift range $0.2 < z < 0.6$ and get a similar power law to \citet{Maoz2017-CosmicDTD} with a slope of $-1.13 \pm 0.05$.
-They also find that slower-declining SNe have a steeper DTD slope.
+A declining power-law with $\alpha\sim-1$ is a standard assumption in many observational studies of the DTD as well as GCE studies.
+\citet{Maoz2017-CosmicDTD} obtain a DTD with $\alpha=-1.07\pm0.09$ based on volumetric rates and an assumed cosmic SFH for field galaxies in redshift range $0\leq z\leq 2.25$.
+\citet{Wiseman2021-DESRates} obtain a similar slope of $\alpha=-1.13\pm0.05$ for field galaxies in the redshift range $0.2<z<0.6$.
+For galaxy clusters, \citet{Maoz2017-CosmicDTD} find a steeper DTD slope of $\alpha=-1.39^{+0.32}_{-0.05}$.
+\citet{Heringer2019-FieldGalaxyDTD} use a SFH-independent method to constrain the DTD for field galaxies within $0.01<z<0.2$ and find a steeper slope of $\alpha=-1.34^{+0.19}_{-0.17}$.
+In this paper, we investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$.
 
@@
 We take $t_{\rm rise}=0.5$ Gyr, $W=0.5$ Gyr, $\alpha=-1.1$, and $\epsilon=0.05$ so the initial rate is 5\% of the peak rate.
+
+Table \ref{tab:dtds} summarizes the model DTDs we investigate in this paper.
+
+\begin{deluxetable*}{lll}
+\tablecaption{Summary of SN Ia DTD models explored in this paper.\label{tab:dtds}}
+\tablehead{
+\colhead{Model} & \colhead{Parameters} & \colhead{Similar to}
+}
+\startdata
+Power-law   & $\alpha=-1.1$                 & \citet[][field]{Maoz2017-CosmicDTD}; 
+                                              \citet{Wiseman2021-DESRates}              \\
+Power-law   & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
+                                              \citet{Heringer2019-FieldGalaxyDTD}       \\
+Plateau     & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
+Plateau     & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
+Triple-system   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2022-TripleEvolution} \\
+            & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
+Exponential & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
+                                  \citet{Schonrich2009-RadialMixing};       \\
+            &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
+Exponential & $\tau=3.0$ Gyr    & \\
+Prompt      & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
+            & $\tau=3.0$ Gyr & \\
+\enddata
+\end{deluxetable*}
 
@@
 Within each panel, colored curves represent the different age bins, ranging from the youngest stars (dark blue) to the oldest (dark red).
-The vertical dotted black lines indicate the bounds of each bin in formation radius; stars within that region of the distribution have not migrated outside their birth annulus over their lifetime.}
+The vertical dotted black lines indicate the bounds of each bin in formation radius; stars within that region of the distribution have not migrated outside their birth annulus over their lifetime.
+All distributions are normalized so that the area under the curve is 1.}
     \label{fig:radial-migration}
@@
 The probability density function (PDF) of $z_{\rm final}$ given some scale height $h_z$ is
-
 \begin{equation}
@@
 \end{equation}
-
-\noindent and the corresponding cumulative distribution function (CDF) is
-
+and the corresponding cumulative distribution function (CDF) is
 \begin{equation}
@@
 \end{equation}
-
-\noindent We fit the above function to the distributions of $z_{\rm final}$ in h277 in varying bins of $\tau$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
-
+We fit the above function to the distributions of $z_{\rm final}$ in h277 in varying bins of $\tau$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
 \begin{equation}
@@
     e^{\frac{\tau-5\,{\rm Gyr}}{7.0\,{\rm Gyr}}}
-    e^{\frac{R_{\rm final}-8\,{\rm kpc}}{6.0\,{\rm kpc}}}
+    e^{\frac{R_{\rm final}-8\,{\rm kpc}}{6.0\,{\rm kpc}}}.
     \label{eq:scale-height}
@@
 
-\subsection{APOGEE Data}
-\label{sec:apogee-data}
+When a star particle is created by VICE at initial radius $R_{\rm form}$, we sample its total radial migration distance $\Delta R$ from a Gaussian with a width described by Equation \ref{eq:radial-migration}, and we sample its final midplane distance $z_{\rm final}$ from the distribution described by Equation \ref{eq:sech-pdf} with a width given by Equation \ref{eq:scale-height}.
+The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citet{Johnson2021-Migration}, but with a time dependence $\propto t^{1/3}$.
+This produces distributions of $R_{\rm final}$ and $z_{\rm final}$ which are similar to the analogue migration case for all but the oldest stars
 
-We use APOGEE DR17 \citep{Abdurro'uf2022-SDSSIV-DR17}.
-Our selection criteria are presented in Table \ref{tab:sample-selection}, producing a final sample of \variable{output/sample_size.txt} stars.
-We limit to stars with a reported measurement of both [Fe/H] and [O/Fe].
-APOGEE survey \citep{Majewski2017-APOGEE}, spectrographs \citep{Wilson2019-APOGEE-Spectrographs}, ASPCAP \citep{Holtzmann2015-ASPCAP,GarciaPerez2016-ASPCAP}, 2.5-meter Sloan Foundation Telescope \citep{Gunn2006-SloanTelescope} at Apache Point Observatory, New Mexico.
-Ir{\'e}n{\'e}e DuPont Telescope \citep{BowenVaughan1973-DuPontTelescope} at Las Campanas Observatory, Chile for Southern Hemisphere observations.
-Data reduction pipeline \citep{Nidever2015-APOGEE-DataReduction}, model grids and interpolation method \citep{Jonsson2020-APOGEE-DR16}.
+\subsection{Observational Sample}
+\label{sec:observational-sample}
+
+We compare our simulation results to abundance measurements from the 17th data release \citep[DR17;][]{Abdurro'uf2022-SDSSIV-DR17} of the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE}.
+APOGEE uses infrared spectrographs \citep{Wilson2019-APOGEE-Spectrographs} mounted on two telescopes: the 2.5-meter Sloan Foundation Telescope \citep{Gunn2006-SloanTelescope} at Apache Point Observatory, United States in the Northern Hemisphere, and the Ir{\'e}n{\'e}e DuPont Telescope \citep{BowenVaughan1973-DuPontTelescope} at Las Campanas Observatory, Chile in the Southern Hemisphere.
+After the spectra are passed through the data reduction pipeline \citep{Nidever2015-APOGEE-DataReduction}, the APOGEE Stellar Parameter and Chemical Abundance Pipeline \citep[ASPCAP;][]{Holtzmann2015-ASPCAP,GarciaPerez2016-ASPCAP} extracts chemical abundances using the model grids and interpolation method described by \citet{Jonsson2020-APOGEE-DR16}.
+
+We limit our sample to red giant branch and red clump stars with high-quality spectra; Table \ref{tab:sample-selection} lists our selection criteria, which produce a final sample of \variable{output/sample_size.txt}stars.
 

### 2023-07-11 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
-A declining power-law with $\alpha\sim-1$ is a standard assumption in many observational studies of the DTD as well as GCE studies.
+A declining power-law with $\alpha\sim-1$ is a standard assumption in many observational studies of the DTD as well as GCE simulations.
 \citet{Maoz2017-CosmicDTD} obtain a DTD with $\alpha=-1.07\pm0.09$ based on volumetric rates and an assumed cosmic SFH for field galaxies in redshift range $0\leq z\leq 2.25$.
@@
     \includegraphics{figures/onezone_prompt.pdf}
-    \caption{Caption}
+    \caption{One-zone model abundance tracks and distributions for variants of the prompt DTD.}
     \label{fig:onezone-prompt}

### 2023-07-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\begin{figure*}
-    \centering
-    \includegraphics{figures/radial_migration.pdf}
-    \caption{The distribution of final radius $R_{\rm final}$ as a function of formation radius and age for the h277 analogue (top row) and Gaussian sampling scheme (bottom row).
-From left to right, star particles are binned by formation annulus, from the inner disk (far left column) to the Solar annulus (center column) to the outer disk (far right column).
-Within each panel, colored curves represent the different age bins, ranging from the youngest stars (dark blue) to the oldest (dark red).
-The vertical dotted black lines indicate the bounds of each bin in formation radius; stars within that region of the distribution have not migrated outside their birth annulus over their lifetime.
-All distributions are normalized so that the area under the curve is 1.}
-    \label{fig:radial-migration}
-    \script{radial_migration.py}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \includegraphics{figures/midplane_distance.pdf}
-    \caption{Similar to Figure \ref{fig:radial-migration} but for the distribution of final midplane distance $z_{\rm final}$ as a function of final radius and age.
-From left to right, star particles are binned by \textit{final} annulus.}
-    \label{fig:midplane-distance}
-    \script{midplane_distance.py}
-\end{figure*}
-
 We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm initial}$ from the \texttt{h277} output in bins of $R_{\rm initial}$ and age.
@@
 The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citet{Johnson2021-Migration}, but with a time dependence $\propto t^{1/3}$.
-This produces distributions of $R_{\rm final}$ and $z_{\rm final}$ which are similar to the analogue migration case for all but the oldest stars
+This produces distributions of $R_{\rm final}$ and $z_{\rm final}$ which are similar to the analogue migration case for all but the oldest stars.
+
+Figure \ref{fig:radial-migration} compares the distributions of $R_{\rm final}$ in bins of $R_{\rm form}$ and age between the analogue and Gaussian migration schema. The
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/radial_migration.pdf}
+    \caption{The distribution of final radius $R_{\rm final}$ as a function of formation radius $R_{\rm form}$ and age for the h277 analogue (top row) and Gaussian sampling scheme (bottom row).
+From left to right, star particles are binned by formation annulus, from the inner disk (far left column) to the Solar annulus (center column) to the outer disk (far right column).
+Within each panel, colored curves represent the different age bins, ranging from the youngest stars (dark blue) to the oldest (dark red).
+All distributions are normalized so that the area under the curve is 1, and have been smoothed by a boxcar function of width 0.5 kpc.
+The vertical dotted black lines indicate the bounds of each bin in $R_{\rm form}$; stars within that region of the distribution have not migrated outside their birth annulus over their lifetime.}
+    \label{fig:radial-migration}
+    \script{radial_migration.py}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/midplane_distance.pdf}
+    \caption{Similar to Figure \ref{fig:radial-migration} but for the distribution of final midplane distance $z_{\rm final}$ as a function of final radius and age.
+From left to right, star particles are binned by \textit{final} annulus.
+All distributions have been smoothed by a boxcar function of width 0.1 kpc.}
+    \label{fig:midplane-distance}
+    \script{midplane_distance.py}
+\end{figure*}
 
@@
 To quantify the similarity between the MDFs generated by VICE and the observed APOGEE MDF, we compute the Kullback-Leibler (KL) divergence \citep{KullbackLeibler1951}, defined as
-
 \begin{equation}
@@
 \end{equation}
-
-\noindent for distributions $P$ and $Q$ with probability density functions $p(x)$ and $q(x)$.
+for distributions $P$ and $Q$ with probability density functions $p(x)$ and $q(x)$.
 In this case, $P$ is the APOGEE MDF, $Q$ is the model MDF, and $x$ is [Fe/H].

### 2023-07-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+\subsection{Nucleosynthetic Yields}
+\label{sec:yields}
+
+We use the same yields as in \citet{Johnson2021-Migration}.
+
+\begin{deluxetable}{lll}
+    \tablecaption{Nucleosynthetic yields assumed in our simulations.\label{tab:yields}}
+    \tablehead{
+        \colhead{Source} & \colhead{Element} & \colhead{Yield}
+    }
+    \startdata
+    CCSN    & O     & 0.015     \\
+    CCSN    & Fe    & 0.0012    \\
+    \hline
+    SN Ia   & O     & 0         \\
+    SN Ia   & Fe    & 0.00214   \\
+    \enddata
+\end{deluxetable}
+
 \subsection{Observational Sample}
@@
     \centering
-    \includegraphics{figures/onezone_slope_timescale.pdf}
-    \caption{\textit{Center:} Abundance tracks in the [Fe/H]-[O/Fe] plane for one-zone models with various DTD parameters.
-Tracks from models which assume a power-law DTD are in black, with dotted, dashed, and solid curves representing power-law slopes ($\alpha$) of $-0.8$, $-1.1$, and $-1.4$, respectively.
-Tracks from models which assume an exponential DTD are in blue, with dotted, dashed, and solid curves representing exponential decay timescales ($\tau$) of 1.5 Gyr, 3 Gyr, and 6 Gyr, respectively.
-In all cases a minimum delay time of 40 Myr is assumed.
-\textit{Top:} MDFs generated by the one-zone models.
-\textit{Right:} Distribution of [O/Fe] generated by the one-zone models.}
-    \label{fig:onezone-slope-timescale}
-    \script{onezone_slope_timescale.py}
+    \includegraphics{figures/onezone_powerlaw_slope.pdf}
+    \caption{\textit{Center:} Abundance tracks in the [Fe/H]-[O/Fe] plane for one-zone models with a power-law DTD.
+The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively.
+In all cases a minimum SN Ia delay time of 40 Myr is assumed.
+\textit{Top:} Metalliticy distribution functions (MDFs) generated by the one-zone models.
+\textit{Right:} Distributions of [O/Fe] generated by the one-zone models.}
+    \label{fig:onezone-powerlaw-slope}
+    \script{onezone_powerlaw_slope.py}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_exponential_timescale.pdf}
+    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with an exponential DTD.
+The dotted, dashed, and solid curves represent exponential decay timescales $\tau=1.5$ Gyr, 3 Gyr, and 6 Gyr, respectively.}
+    \label{fig:onezone-exponential-timescale}
+    \script{onezone_exponential_timescale.py}
 \end{figure}

### 2023-07-17 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_plateau_width.pdf}
+    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with a plateau DTD.
+The solid, dashed, and dot-dashed pink curves represent plateau widths $W=1.0$, 0.3, and 0.1 Gyr, respectively.
+All plateau DTDs assume a power-law slope of $\alpha=-1.1$.
+For comparison, the blue dotted curve represents an exponential DTD with a timescale $\tau=3$ Gyr, and the black dotted curve represents a power-law DTD with the same slope but no plateau.}
+    \label{fig:onezone-plateau-width}
+    \script{onezone_plateau_width.py}
+\end{figure}
+
 Figure \ref{fig:onezone-dtd} compares the one-zone model outputs from the full range of DTDs we investigate in this paper.
@@
     \includegraphics{figures/onezone_dtd.pdf}
-    \caption{Similar to Figure \ref{fig:onezone-slope-timescale} but with a different selection of DTDs. In all cases a minimum delay time of 40 Myr is assumed.}
+    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with a different selection of DTDs. In all cases a minimum delay time of 40 Myr is assumed.}
     \label{fig:onezone-dtd}
@@
     \includegraphics{figures/onezone_delay_taustar.pdf}
-    \caption{Similar to Figure \ref{fig:onezone-slope-timescale} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\tau_*$).
+    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\tau_*$).
 Tracks with $\tau_*=2$ Gyr are represented in black, while a track with a shorter $\tau_*=1$ Gyr is shown in red and a track with a longer $\tau_*=4$ Gyr is in yellow.
@@
     \script{onezone_delay_taustar.py}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_sfh.pdf}
+    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying star formation history (SFH). An exponential DTD with $\tau=1.5$ Gyr is assumed in all models.}
+    \label{fig:onezone-sfh}
+    \script{onezone_sfh.py}
 \end{figure}

### 2023-07-18 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-A 150 Myr minimum delay time is incompatible with the prompt DTD model, which has $\sim 50$ of SNe Ia explode in the first 100 Myr.
+A 150 Myr minimum delay time is incompatible with the prompt DTD model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr.
 
@@
 
+\begin{figure*}
+    \centering
+    \includegraphics{figures/feh_df_sfh.pdf}
+    \caption{Distributions of [Fe/H] for multi-zone simulations with different SFHs.
+Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}).
+Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue).
+}
+    \label{fig:feh-df-sfh}
+    \script{feh_df_sfh.py}
+\end{figure*}
+
 \subsection{Comparison to APOGEE ODFs}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/ofe_df_dtd.pdf}
+    \caption{Caption.}
+    \label{fig:ofe-df-dtd}
+    \script{ofe_df_dtd.py}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/ofe_df_sfh.pdf}
+    \caption{Caption.}
+    \label{fig:ofe-df-sfh}
+    \script{ofe_df_sfh.py}
+\end{figure*}
 

### 2023-07-20 src/scripts/age_ofe.py
update age-ofe plots

@@ -11,14 +11,12 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 from matplotlib.ticker import MultipleLocator, FormatStrFormatter
-import vice
-from scatter_plot_grid import setup_axes, setup_colorbar, plot_vice_sample
-from utils import multioutput_to_pandas, filter_multioutput_stars, \
-    weighted_quantile, \
-    group_by_bins, model_uncertainty, feuillet2019_data
+# import vice
+from scatter_plot_grid import setup_axes, setup_colorbar
+from utils import weighted_quantile, group_by_bins, feuillet2019_data
 from multizone_stars import MultizoneStars
 from apogee_tools import import_apogee, apogee_region
-from _globals import GALR_BINS, ABSZ_BINS, ZONE_WIDTH
+from _globals import GALR_BINS, ABSZ_BINS
 import paths
 
 GALR_BINS = GALR_BINS[:-1]
@@ -33,26 +31,18 @@ AGE_LABELS = {'F19': 'Feuillet et al. (2019)',
               'M19': 'Mackereth et al. (2019)',
               'L23': 'Leung et al. (2023)'}
 
-def main(evolution, RIa, migration='diffusion', ages='L23', verbose=False, 
-         uncertainties=False, **kwargs):
+def main(evolution, RIa, migration='gaussian', verbose=False, **kwargs):
     # Import VICE multi-zone output data
-    output_name = '/'.join([migration, evolution, RIa])
+    output_name = '/'.join([migration, evolution, RIa, 'diskmodel'])
     # Import APOGEE and astroNN data
     apogee_data = import_apogee(verbose=verbose)
     # Main plot function
-    if uncertainties:
-        fname = '%s_%s_errors.png' % (RIa, ages)
-    else:
-        fname = '%s_%s.png' % (RIa, ages)
-    save_dir = paths.debug / 'age_ofe' / migration / evolution
-    plot_age_ofe(output_name, apogee_data, fname=fname, ages=ages, 
-                 verbose=verbose, save_dir=save_dir, 
-                 uncertainties=uncertainties, **kwargs)
+    plot_age_ofe(output_name, apogee_data, verbose=verbose, **kwargs)
 
 
 def plot_age_ofe(output_name, apogee_data, fname='age_ofe.png', ages='L23', 
-                 cmap='winter', log=False, score=False, uncertainties=False, 
-                 verbose=False, save_dir=paths.debug/'age_ofe'):
[…]

### 2023-07-20 src/scripts/age_ofe_sfh.py

@@ -1,5 +1,6 @@
 """
-Compare plots of [O/Fe] vs age in a single Galactic region for various DTDs.
+Compare [O/Fe]-Age plots for the Solar annulus for VICE outputs with
+different star formation histories.
 """
 
 from utils import multioutput_to_pandas, filter_multioutput_stars, model_uncertainty
@@ -8,14 +9,14 @@ import matplotlib.pyplot as plt
 from matplotlib.ticker import MultipleLocator, FormatStrFormatter
 from age_ofe import plot_vice_medians, plot_astroNN_medians
 from scatter_plot_grid import setup_colorbar, plot_vice_sample
-from _globals import ZONE_WIDTH, ONE_COLUMN_WIDTH
+from _globals import ZONE_WIDTH, ONE_COLUMN_WIDTH, MAX_SF_RADIUS
 import paths
 
 SFH_LIST = ['insideout', 'lateburst', 'conroy22_JW20yields', 'twoinfall']
 DTD = 'powerlaw_slope11'
 LABEL_LIST = ['Inside-Out', 'Late-Burst', 'Early-Burst', 'Two-Infall']
 AGE_COL = 'LATENT_AGE'
-AGE_LABEL = 'Leung et al. 2023'
+AGE_LABEL = 'Leung et al. (2023)'
 AGE_LIM = (0.3, 20)
 OFE_LIM = (-0.15, 0.55)
 CMAP = 'winter'
@@ -30,8 +31,9 @@ def main():
                             sharex=True, sharey=True)
     plt.subplots_adjust(right=0.94, left=0.1, bottom=0.1, top=0.98,
                         wspace=0, hspace=0)
-    cbar = setup_colorbar(fig, cmap=CMAP, vmin=0, vmax=15.5, 
+    cbar = setup_colorbar(fig, cmap=CMAP, vmin=0, vmax=MAX_SF_RADIUS, 
                           label=r'Birth $R_{\rm{Gal}}$ [kpc]', pad=0.02, width=0.04)
+    cbar.ax.yaxis.set_major_locator(MultipleLocator(2))
     cbar.ax.yaxis.set_minor_locator(MultipleLocator(0.5))
     
     for ax, sfh, label in zip(axs.flatten(), SFH_LIST, LABEL_LIST):

### 2023-07-20 src/scripts/ofe_feh_sfh.py

@@ -6,8 +6,6 @@ different star formation histories.
 from pathlib import Path
 import matplotlib.pyplot as plt
 from matplotlib.ticker import MultipleLocator
-# from matplotlib.colors import Normalize
-# from matplotlib.cm import ScalarMappable
 import vice
 from multizone_stars import MultizoneStars
 from scatter_plot_grid import setup_colorbar

### 2023-07-20 src/scripts/scatter_plot_grid.py

@@ -141,7 +141,7 @@ def setup_axes(galr_bins=GALR_BINS[:-1], absz_bins=ABSZ_BINS,
     cols = len(galr_bins) - 1
     fig, axs = plt.subplots(rows, cols, figsize=(width, (width/cols)*rows),
                             sharex=True, sharey=True)
-    plt.subplots_adjust(right=0.98, left=0.06, bottom=0.07, top=0.95,
+    plt.subplots_adjust(right=0.98, left=0.06, bottom=0.08, top=0.95,
                         wspace=spacing, hspace=spacing)
     # Figure title
     if len(title) > 0:

### 2023-07-20 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-% Main body with filler text
 \section{Introduction}
@@
             &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
-Exponential & $\tau=3.0$ Gyr    & \\
+Exponential & $\tau=3.0$ Gyr    & --- \\
 Prompt      & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
@@
 
-Figure \ref{fig:sfhs} presents an overview of our model star formation histories.
+In this paper, we consider four models for the SFH: inside-out, late-burst, early-burst, and two-infall.
+The first two models are run in VICE's ``star formation mode,'' where the surface density of star formation rate $\dot\Sigma_*$ is prescribed along with the star formation efficiency timescale $\tau_*$, and the infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_{\rm gas}$ are calculated from the specified quantities.
+The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$  and $\tau_*$ and the other two quantities follow.
 
-\begin{figure*}
-    \centering
-    \includegraphics{figures/star_formation_histories.pdf}
-    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
-In each panel, we plot curves for the zones which have inner radii of 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
-    \label{fig:sfhs}
-    \script{star_formation_histories.py}
-\end{figure*}
+The functions presented below are dimensionless.
+For a detailed look at the normalization of the star formation rate with $R_{\rm gal}$, we refer the reader to Appendix B of \citet{Johnson2021-Migration}.
 
-\paragraph{Inside-out}
+\paragraph{Inside-out} Following \citet{Johnson2021-Migration}, this is our fiducial SFH:
 \begin{equation}
-    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm SFH}}
+    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm sfh}}
     \label{eq:insideout-sfh}
 \end{equation}
+where we assume $\tau_{\rm rise}=2$ Gyr for all radii.
+The SFH timescale $\tau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\tau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the Solar annulus and longer timescales in the outer galaxy.
+The $\tau_{\rm sfh} - R_{\rm gal}$ relation is determined from the data of \citet{Sanchez2020-StarFormationTimescales}; see Section 2.5 of \citet{Johnson2021-Migration} for the details.
 
-\paragraph{Late-burst}
+\paragraph{Late-burst} A variation on the inside-out SFH with a Gaussian burst in the star formation rate:
 \begin{equation}
@@
 \end{equation}
+where $A_b$ is the dimensionless amplitude of the starburst, $t_b$ is the time of the peak of the burst, and $\sigma_b$ is the width of the Gaussian.
+Following \citet{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr.
+The determination of $\tau_{\rm sfh}$ and the normalization of the SFR as a function of $R_{\rm gal}$ are the same as in the inside-out case.
 
@@
 \begin{equation}
-    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm IFR}}
+    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}}
     \label{eq:earlyburst-ifr}
 \end{equation}
-We take $\tau_{\rm IFR} = \tau_{\rm SFH}$ at all radii.
 The time-dependence of the SFE timescale $\tau_*$ comes from \citet{Conroy2022-ThickDisk}:
@@
 where we take the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$ following \citet{BlandHawthornGerhard2016-MilkyWayReview}.
+
+Figure \ref{fig:sfhs} presents an overview of these model star formation histories.
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/star_formation_histories.pdf}
+    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
+In each panel, we plot curves for the zones which have inner radii of 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
+    \label{fig:sfhs}
+    \script{star_formation_histories.py}
+\end{figure*}
 
@@
 
-We use the same yields as in \citet{Johnson2021-Migration}.
+Table \ref{tab:yields} summarizes the nucleosynthetic yields assumed in this paper, which we adopt from \citet{Johnson2021-Migration}.
 
@@
 \begin{deluxetable*}{lll}
-    \tablecaption{Sample Selection\label{tab:sample-selection}}
+    \tablecaption{Sample selection parameters from APOGEE DR17\label{tab:sample-selection}}
     \tablehead{
@@
 
-\section{Results from Single-Zone Models}
+\section{Results from One-Zone Models}
 \label{sec:onezone-results}
 
-All models are run for a duration of 13.2 Gyr with a simulation timestep of 0.01 Gyr.
+All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=0.01$ Gyr.
+We adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citep[see Equation 8 from][]{Johnson2021-Migration} and a star formation efficiency timescale $\tau_*\equiv M_{\rm gas}/\dot M_*=2$ Gyr.
+We adopt a continuous recycling prescription \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
+Unless otherwise specified, we adopt the inside-out star formation rate (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc, with timescales $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr, and our models have an initial gas mass $M_{\rm gas,0}=0$.
+Unless otherwise specified, we assume a minimum SN Ia delay time of 40 Myr.
+A summary of these one-zone fiducial parameters is presented in Table \ref{tab:onezone-parameters}.
+
+\begin{deluxetable}{Ccl}
+    \tablecaption{A summary of parameters and their fiducial values for our one-zone chemical evolution models.\label{tab:onezone-parameters}}
+    \tablehead{
+        \colhead{Parameter} & \colhead{Value} & \colhead{Description}
+    }
+    \startdata
+    \Delta t        & 10 Myr    & Time-step size \\
+    t_{\rm max}     & 13.2 Gyr  & Maximum simulation time \\
+    \eta            & 2.15      & Outflow mass-loading factor \\
+    \tau_*          & 2.0 Gyr   & Star formation efficiency timescale \\
+    \dot M_r        & continuous    & Recycling rate \\
+    t_D             & 40 Myr    & Minimum SN Ia delay time \\
+    M_{\rm gas,0}   & 0         & Initial gas mass \\
+    \dot M_*(t)     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
+    \tau_{\rm rise} & 2 Gyr     & SFR rise timescale \\
+    \tau_{\rm sfh}  & 15.1 Gyr  & SFR exponential timescale
+    \enddata
+\end{deluxetable}
 
@@
 In general, the choice of DTD has the greatest effect on the location of the knee in [Fe/H]-[O/Fe] space (center panel) and the high-$\alpha$ end of the distribution of [O/Fe] (right panel).
-The DTD also has a smaller effect on the MDF in the range $-15.5\lesssim$ [Fe/H] $\lesssim-0.5$ (top panel).
+The DTD also has a smaller effect on the MDF in the range $-1.5\lesssim$ [Fe/H] $\lesssim-0.5$ (top panel).
 
@@
 
-Figure \ref{fig:onezone-dtd-delay} shows that the minimum SN Ia delay time has a much stronger effect on the abundance track and MDFs of models which assume a power-law DTD than models which assume an exponential, due to the much higher SN Ia rate in the power-law models at early times (see Figure \ref{fig:dtds}).
-Moreover, a power-law DTD with a long minimum delay may be observationally hard to distinguish from an exponential.
+Figure \ref{fig:onezone-minimum-delay} shows that the minimum SN Ia delay time has a much stronger effect on the abundance track and MDFs of models which assume a power-law DTD than models which assume a plateau or exponential DTD, due to the much higher SN Ia rate in the power-law models at early times (see Figure \ref{fig:dtds}).
+Moreover, a power-law DTD with a long minimum delay may be observationally hard to distinguish from a plateau model.
+In Figure \ref{fig:onezone-minimum-delay}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (red dashed line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (blue solid line), and the [O/Fe] distributions are virtually identical.
 
@@
     \centering
-    \includegraphics{figures/onezone_dtd_delay.pdf}
-    \caption{Similar to Figure \ref{fig:onezone-slope-timescale} but with varying minimum SN Ia delay time ($t_D$).
-Dashed curves represent models with a minimum delay time of 40 Myr, while solid curves represent models with a minimum delay time of 150 Myr.
-The black curves represent a power-law DTD with a slope of $-1.1$, while the blue curves represent an exponential DTD with a timescale of 1.5 Gyr.}
-    \label{fig:onezone-dtd-delay}
-    \script{onezone_dtd_delay.py}
+    \includegraphics{figures/onezone_minimum_delay.pdf}
+    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying DTD models and minimum SN Ia delay time ($t_D$).
+Solid curves represent models with a minimum delay time of 40 Myr, while dashed curves represent models with a minimum delay time of 150 Myr.
+The red curves represent a power-law DTD with slope $\alpha=-1.1$; blue curves represent an plateau DTD with width $W=0.3$ Gyr and slope $\alpha=-1.1$; and orange curves represent an exponential DTD with timescale $\tau=3$ Gyr.
+In all cases an exponential rise-fall SFR is assumed.}
+    \label{fig:onezone-minimum-delay}
+    \script{onezone_minimum_delay.py}
 \end{figure}
 
-A 150 Myr minimum delay time is incompatible with the prompt DTD model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr.
+A 150 Myr minimum delay time is incompatible with the prompt DTD model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD as its relative SN Ia rate is so low at early times.
 
@@
 The dotted, solid, and dashed black curves represent a minimum delay time of 40 Myr, 80 Myr, and 160 Myr, respectively.
-A power-law DTD is assumed in all models.}
+A power-law DTD with $\alpha=-1.1$ is assumed in all models.}
     \label{fig:onezone-delay-taustar}
@@
     \startdata
-        [Fe/H] & $9.2\times10^{-3}$ & APOGEE \\
-        $\rm [O/Fe]$ & $1.8\times10^{-2}$ & APOGEE \\
+        [Fe/H] & $9.2\times10^{-3}$ & APOGEE DR17 \\
+        $\rm [O/Fe]$ & $1.8\times10^{-2}$ & APOGEE DR17 \\
         log(Age/Gyr) & $0.12$ & \citet{Leung2023-Ages}
@@
 
-\subsection{Comparison to APOGEE MDFs}
+\subsection{The distribution of [Fe/H]}
 
@@
 
+Figure \ref{fig:feh-df-sfh} plots the distribution of [Fe/H] in multiple regions across the disk for the four SFHs in this paper.
+
 \begin{figure*}
@@
 Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue).
-}
+Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row.
+All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex.
+In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.
+Distributions from APOGEE DR17, binned similarly, are presented in the right-most column for reference.}
     \label{fig:feh-df-sfh}
@@
 
-\subsection{Comparison to APOGEE ODFs}
+Holding the SFH fixed, varying the DTD has only a minor effect on the MDF.
+Figure \ref{fig:feh-df-dtd} plots the [Fe/H] distributions for two multi-zone simulations which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
+The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of SNe Ia exploding within 1 Gyr in the former model but only $\sim 30\%$ in the latter.
+Nevertheless, the effect of the DTD on the MDF is second-order compared to the effect of the SFH as seen in Figure \ref{fig:feh-df-sfh}.
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/feh_df_dtd.pdf}
+    \caption{Distributions of [Fe/H] for multi-zone simulations with different DTDs: a power-law with slope $\alpha=-1.4$ (\textit{left}), and an exponential with timescale $\tau=3$ Gyr (\textit{right}).
+In both cases an inside-out SFH is assumed.
+The plot format is similar to Figure \ref{fig:feh-df-sfh}.}
+    \label{fig:feh-df-dtd}
+    \script{feh_df_dtd.py}
+\end{figure}
+
+\subsection{The distribution of [O/Fe]}
 
@@
     \includegraphics{figures/ofe_df_dtd.pdf}
-    \caption{Caption.}
+    \caption{Distributions of [O/Fe] for multi-zone simulations with different DTDs.
+In all cases an inside-out SFH is assumed.
+The plot format is similar to Figure \ref{fig:feh-df-sfh}.
+All distributions are smoothed with a box-car width of 0.05 dex.}
     \label{fig:ofe-df-dtd}
@@
     \includegraphics{figures/ofe_df_sfh.pdf}
-    \caption{Caption.}
+    \caption{Distributions of [O/Fe] for multi-zone simulations with different SFHs.
+The plot format is similar to Figure \ref{fig:feh-df-sfh}.
+In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.}
     \label{fig:ofe-df-sfh}
     \script{ofe_df_sfh.py}
+\end{figure*}
+
+\subsection{The [O/Fe]--[Fe/H] Plane}
+\label{sec:ofe-feh}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/ofe_feh_sfh.pdf}
+    \caption{Caption}
+    \label{fig:ofe-feh-sfh}
+    \script{ofe-feh-sfh.py}
+\end{figure}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/ofe_feh_dtd.pdf}
+    \caption{Caption}
+    \label{fig:ofe-feh-dtd}
+    \script{ofe-feh-dtd.py}
 \end{figure*}

### 2023-07-21 src/scripts/age_ofe_dtd.py
update age-ofe and ofe-feh plots

@@ -2,58 +2,65 @@
 Compare plots of [O/Fe] vs age in a single Galactic region for various DTDs.
 """
 
-from utils import multioutput_to_pandas, \
-    filter_multioutput_stars, model_uncertainty
 from apogee_tools import import_apogee, apogee_region
 import matplotlib.pyplot as plt
 from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+from multizone_stars import MultizoneStars
 from age_ofe import plot_vice_medians, plot_astroNN_medians
-from scatter_plot_grid import setup_colorbar, plot_vice_sample
-from _globals import ZONE_WIDTH, ONE_COLUMN_WIDTH
+from scatter_plot_grid import setup_colorbar
+from _globals import ZONE_WIDTH, TWO_COLUMN_WIDTH, MAX_SF_RADIUS, ABSZ_BINS
 import paths
 
-SFH = 'insideout'
-DTD_LIST = ['powerlaw_slope11', 'exponential_timescale15', 
-            'plateau_width1000_slope11', 'triple_delay040']
-LABEL_LIST = [r'Power law ($\alpha=-1.1$)', r'Exponential ($\tau=1.5$ Gyr)',
-              r'Plateau ($W=1.0$ Gyr)', 'Triple system evolution']
-AGE_LABELS = {'ASTRONN_AGE': 'Mackereth et al. 2019',
-              'LATENT_AGE': 'Leung et al. 2023'}
+SFH_MODEL = 'insideout'
+DTD_LIST = ['prompt', 
+            'powerlaw_slope11', 
+            'exponential_timescale15', 
+            'plateau_width10', 
+            'triple']
+LABEL_LIST = ['Two-population', 
+              'Power law\n($\\alpha=-1.1$)', 
+              'Exponential\n($\\tau=1.5$ Gyr)',
+              'Plateau\n($W=1.0$ Gyr)', 
+              'Triple-system']
+AGE_SOURCE = 'L23'
+AGE_COL = 'LATENT_AGE'
+AGE_LABEL = 'Leung et al.\n(2023)'
 AGE_LIM = (0.3, 20)
 OFE_LIM = (-0.15, 0.55)
+GALR_LIM = (7, 9)
+CMAP_NAME = 'winter'
 
-def main(cmap='winter', galr_lim=(7, 9), absz_lim=(0, 0.5), age_col='LATENT_AGE'):
-    apogee_data = import_apogee()
[…]

### 2023-07-21 src/scripts/age_ofe_sfh.py

@@ -19,10 +19,10 @@ AGE_SOURCE = 'L23'
 AGE_COL = 'LATENT_AGE'
 AGE_LABEL = 'Leung et al.\n(2023)'
 AGE_LIM = (0.3, 20)
-OFE_LIM = (-0.15, 0.55)
+OFE_LIM = (-0.15, 0.5)
 CMAP_NAME = 'winter'
 GALR_LIM = (7, 9)
-ABSZ_LIM = (0, 2)
+ABSZ_LIM = (0, 0.5)
 
 def main():
     plt.style.use(paths.styles / 'paper.mplstyle')
@@ -73,7 +73,7 @@ def main():
         ax.set_ylabel('[O/Fe]', labelpad=2)
         
     # Legend
-    axs[0,1].legend(loc='upper left', frameon=False, 
+    axs[0,0].legend(loc='upper left', frameon=False, 
                     bbox_to_anchor=(0.02, 0.89), handlelength=0.7)
     
     fig.savefig(paths.figures / 'age_ofe_sfh.pdf', dpi=300)

### 2023-07-21 src/scripts/multizone_stars.py

@@ -258,7 +258,7 @@ class MultizoneStars:
                             (self.stars[galr_col]       <  galr_max) &
                             (self.stars['zfinal'].abs() >= absz_min) &
                             (self.stars['zfinal'].abs() <  absz_max) &
-                            (self.stars['mass']         >= min_mass)]
+                            (self.stars['mstar']        >= min_mass)]
         subset.reset_index(inplace=True, drop=True)
         if inplace:
             self.stars = subset
@@ -347,7 +347,7 @@ class MultizoneStars:
         pandas.DataFrame
             N samples of full DataFrame.
         """
-        sample_weights = self.stars['mass'] / self.stars['mass'].sum()
+        sample_weights = self.stars['mstar'] / self.stars['mstar'].sum()
         sample = sample_dataframe(self.stars.copy(), N, weights=sample_weights)
         return sample
     
@@ -451,13 +451,13 @@ class MultizoneStars:
         # Create dummy entries to count at least 0 mass at every age
         temp_df = pd.DataFrame({
             'age': bin_centers, 
-            'mass': np.zeros(bin_centers.shape)
+            'mstar': np.zeros(bin_centers.shape)
         })
         stars = pd.concat([self.stars, temp_df])
         # stars['age'] = np.round(stars['age'], decimals=2)
         # Sum stellar mass in each bin
         mass_total, _ = np.histogram(stars['age'], bins=bin_edges, 
-                                     weights=stars['mass'])
+                                     weights=stars['mstar'])
         # Calculate remaining stellar mass today
         mass_remaining = mass_total * (1 - np.array(
             [vice.cumulative_return_fraction(age) for age in bin_centers]))

### 2023-07-21 src/scripts/ofe_feh_dtd.py

@@ -18,7 +18,7 @@ from _globals import ZONE_WIDTH, TWO_COLUMN_WIDTH, MAX_SF_RADIUS, ABSZ_BINS
 import paths
 
 FEH_LIM = (-1.3, 0.6)
-OFE_LIM = (-0.1, 0.55)
+OFE_LIM = (-0.15, 0.55)
 GALR_LIM = (7, 9)
 
 SFH_MODEL = 'insideout'
@@ -27,7 +27,7 @@ DTD_LIST = ['prompt',
             'exponential_timescale15', 
             'plateau_width10', 
             'triple']
-DTD_LABELS = ['Prompt', 
+DTD_LABELS = ['Two-population', 
               'Power-law\n($\\alpha=-1.1$)', 
               'Exponential\n($\\tau=1.5$ Gyr)',
               'Plateau\n($W=1$ Gyr)',
@@ -50,21 +50,18 @@ def main():
     
     apogee_data = import_apogee()
     
-    for i, row in enumerate(axs):
-        absz_lim = (ABSZ_BINS[-(i+2)], ABSZ_BINS[-(i+1)])
-        # Axis row labels
-        axs[i,0].text(0.93, 0.93, r'$%s\leq |z| < %s$ kpc' % absz_lim, 
-                      va='top', ha='right', transform=axs[i,0].transAxes)
-        for j, ax in enumerate(row):
-            dtd = DTD_LIST[j]
-            output_name = '/'.join(['gaussian', SFH_MODEL, dtd, 'diskmodel'])
-            # Import multioutput stars data
-            mzs = MultizoneStars.from_output(output_name)
-            mzs.model_uncertainty(inplace=True)
-            mzs.region(GALR_LIM, absz_lim, inplace=True)
+    for j, dtd in enumerate(DTD_LIST):
+        output_name = '/'.join(['gaussian', SFH_MODEL, dtd, 'diskmodel'])
+        # Import multioutput stars data
+        mzs = MultizoneStars.from_output(output_name)
+        mzs.model_uncertainty(inplace=True)
+        for i in range(len(ABSZ_BINS) - 1):
+            absz_lim = (ABSZ_BINS[-(i+2)], ABSZ_BINS[-(i+1)])
+            vice_subset = mzs.region(GALR_LIM, absz_lim)
             # Plot sample of star particle abundances
-            mzs.scatter_plot(axs[i,j], '[fe/h]', '[o/fe]', color='galr_origin',
[…]

### 2023-07-21 src/scripts/ofe_feh_sfh.py

@@ -9,15 +9,15 @@ from matplotlib.ticker import MultipleLocator
 import vice
 from multizone_stars import MultizoneStars
 from scatter_plot_grid import setup_colorbar
-from _globals import ZONE_WIDTH, ONE_COLUMN_WIDTH
+from _globals import ZONE_WIDTH, ONE_COLUMN_WIDTH, MAX_SF_RADIUS
 import paths
 from ofe_feh_dtd import apogee_contours
 from apogee_tools import import_apogee
 
 FEH_LIM = (-1.3, 0.6)
-OFE_LIM = (-0.1, 0.55)
+OFE_LIM = (-0.15, 0.55)
 GALR_LIM = (7, 9)
-ABSZ_LIM = (0, 2)
+ABSZ_LIM = (0, 0.5)
 
 SFH_LABELS = ['Inside-out', 'Late-burst', 'Early-burst', 'Two-infall']
 DTD_MODEL = 'exponential_timescale15'
@@ -29,9 +29,9 @@ def main():
     fig, axs = plt.subplots(2, 2, sharex=True, sharey=True,
                             figsize=(ONE_COLUMN_WIDTH, 0.9*ONE_COLUMN_WIDTH))
     plt.subplots_adjust(top=0.98, right=0.93, wspace=0., hspace=0.)
-    cbar = setup_colorbar(fig, cmap=CMAP_NAME, vmin=0, vmax=15.5, width=0.04,
+    cbar = setup_colorbar(fig, cmap=CMAP_NAME, vmin=0, vmax=MAX_SF_RADIUS,
                           label=r'Birth $R_{\rm{gal}}$ [kpc]', pad=0.02,
-                          labelpad=2)
+                          labelpad=2, width=0.04)
     cbar.ax.yaxis.set_major_locator(MultipleLocator(2))
     cbar.ax.yaxis.set_minor_locator(MultipleLocator(0.5))
     

### 2023-07-21 src/scripts/delay_time_distributions.py
rename 'prompt' model to 'two-population'

@@ -31,7 +31,7 @@ class styles:
     """Plot styling for different DTD models."""
     plaw = {
         'func': dtds.powerlaw(slope=-1.1, tmin=DELAY),
-        'label': r'Power law ($\alpha=-1.1$)',
+        'label': r'Power-law ($\alpha=-1.1$)',
         'color': paultol.bright.colors[0],
         'line': '-',
     }
@@ -49,15 +49,13 @@ class styles:
     }
     prompt = {
         'func': dtds.prompt(peak=0.05, stdev=0.015, timescale=3, tmin=DELAY),
-        'label': r'Prompt ($t_{\rm{max}}=50$ Myr)'
-                 '\n'
-                 r'+ exponential ($\tau=3$ Gyr)',
+        'label': 'Two-population',
         'color': paultol.bright.colors[1],
         'line': ':',
     }
     triple = {
         'func': dtds.triple(tmin=DELAY),
-        'label': r'Triple-system evolution',
+        'label': r'Triple-system',
         'color': paultol.bright.colors[2],
         'line': '-.'
     }
@@ -76,7 +74,7 @@ class styles:
     }
     plaw_steep = {
         'func': dtds.powerlaw(slope=-1.4, tmin=DELAY),
-        'label': r'Power law ($\alpha=-1.4$)',
+        'label': r'Power-law ($\alpha=-1.4$)',
         'color': paultol.muted.colors[1],
         'line': '--',
     }

### 2023-07-21 src/scripts/ofe_df_dtd.py

@@ -20,7 +20,7 @@ DTD_LIST = ['prompt',
             'exponential_timescale15', 
             'plateau_width10', 
             'triple']
-DTD_LABELS = ['Prompt', 
+DTD_LABELS = ['Two-population', 
               'Power-law\n($\\alpha=-1.1$)', 
               'Exponential\n($\\tau=1.5$ Gyr)',
               'Plateau\n($W=1$ Gyr)',

### 2023-07-21 src/scripts/ofe_feh_summary.py

@@ -29,7 +29,7 @@ DTD_LIST = ['prompt',
             'exponential_timescale15', 
             'plateau_width10', 
             'triple']
-DTD_LABELS = ['Prompt', 
+DTD_LABELS = ['Two-population', 
               'Power-law\n($\\alpha=-1.1$)', 
               'Exponential\n($\\tau=1.5$ Gyr)',
               'Plateau\n($W=1$ Gyr)',

### 2023-07-21 src/scripts/onezone_dtd.py

@@ -36,7 +36,7 @@ def main():
               r'Plateau ($W=1$ Gyr)',
               r'Exponential ($\tau=1.5$ Gyr)',
               r'Power-law ($\alpha=-1.1$)',
-              r'Prompt',]
+              r'Two-population',]
     colors = [paultol.vibrant.colors[i] for i in [5, 0, 1, 4, 2]]
     line_styles = ['-', '-.', '--', ':', ':']
 

### 2023-07-21 src/scripts/onezone_twopopulation.py

@@ -77,7 +77,7 @@ def main():
     axs[0].set_ylim((-0.1, 0.52))
 
     axs[0].legend(frameon=False, loc='lower left', handlelength=1.2)
-    fig.savefig(paths.figures / 'onezone_prompt.pdf', dpi=300)
+    fig.savefig(paths.figures / 'onezone_twopopulation.pdf', dpi=300)
     plt.close()
 
 

### 2023-07-21 src/scripts/summary_table.py

@@ -265,14 +265,14 @@ def to_latex(df):
                                              ~df['bimodality'].astype('bool'),
                                         other='\\no')
     # Fancy row labels
-    dtd_labels = ['Power law', '($\\alpha=-1.1$)', '', '',
-                  'Power law', '($\\alpha=-1.4$)', '', '',
+    dtd_labels = ['Power-law', '($\\alpha=-1.1$)', '', '',
+                  'Power-law', '($\\alpha=-1.4$)', '', '',
                   'Exponential', '($\\tau=1.5$ Gyr)', '', '',
                   'Exponential', '($\\tau=3.0$ Gyr)', '', '',
                   'Plateau', '($W=0.3$ Gyr)', '', '',
                   'Plateau', '($W=1.0$ Gyr)', '', '',
-                  'Prompt', '($t_{\\rm max}=0.05$ Gyr)', '', '',
-                  'Triple system', '($t_d=0.5$ Gyr)', '', '']
+                  'Two-population', '($t_{\\rm max}=0.05$ Gyr)', '', '',
+                  'Triple-system', '($t_d=0.5$ Gyr)', '', '']
     sfh_labels = ['Inside-out', 'Late-burst', 'Early-burst', 'Two-infall']
     df.reset_index(drop=False, inplace=True)
     df['DTD'] = dtd_labels

### 2023-07-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \includegraphics{figures/ofe_feh_sfh.pdf}
-    \caption{Caption}
+    \caption{A comparison of the [O/Fe]--[Fe/H] plane between the four SFH models in our multi-zone simulations.
+All assume an exponential DTD with $\tau=1.5$ Gyr.
+Each point plots the abundances of a single star particle and is color-coded according to its Galactocentric radius at birth.
+Each panel plots a random sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) weighted by their mass.
+A Gaussian scatter has been applied to all points based on the median abundance errors in APOGEE DR17.
+The black curves represent the ISM abundance tracks in the 8 kpc zone.
+The red contours represent the APOGEE abundance distribution, with the solid and dashed contours enclosing 68\% and 95\% of stars, respectively.}
     \label{fig:ofe-feh-sfh}
@@
     \includegraphics{figures/ofe_feh_dtd.pdf}
-    \caption{Caption}
+    \caption{Similar to Figure \ref{fig:ofe-feh-sfh} but comparing multi-zone simulations with different DTD models. All assume an inside-out SFH.}
     \label{fig:ofe-feh-dtd}
@@
 \end{figure*}
+
+\subsection{The Age--[O/Fe] Plane}
+\label{sec:age-ofe}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/age_ofe_sfh.pdf}
+    \caption{Caption}
+    \label{fig:age-ofe-sfh}
+    \script{age_ofe_sfh.py}
+\end{figure}
 

### 2023-07-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \centering
-    \includegraphics{figures/onezone_prompt.pdf}
+    \includegraphics{figures/onezone_twopopulation.pdf}
     \caption{One-zone model abundance tracks and distributions for variants of the prompt DTD.}
     \label{fig:onezone-prompt}
-    \script{onezone_prompt.py}
+    \script{onezone_twopopulation.py}
 \end{figure}
@@
     \includegraphics{figures/ofe_feh_dtd.pdf}
-    \caption{Similar to Figure \ref{fig:ofe-feh-sfh} but comparing multi-zone simulations with different DTD models. All assume an inside-out SFH.}
+    \caption{Similar to Figure \ref{fig:ofe-feh-sfh} but comparing multi-zone simulations with different DTD models.
+All assume an inside-out SFH.
+Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
+All panels present stars within the Solar annulus ($7\leq R_{\rm gal}<9$ kpc).}
     \label{fig:ofe-feh-dtd}

### 2023-07-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-We explore four different functional forms for the SN Ia DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, and an exponential with a prompt Gaussian component, with a few different parameterizations for each.
+We explore five different functional forms for the SN Ia DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, a two-population model, and a model based on triple-system dynamics, with a one or two different parameterizations for each.
 Figure \ref{fig:dtds} presents these DTDs as a function of time since star formation.
@@
 
-\paragraph{Prompt} A DTD in which 50\% of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the other 50\% form an exponential tail at large $t$, normalized by $D_{t_p,\sigma,\tau}$:
+\paragraph{Two-population} A DTD in which 50\% of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the other 50\% form an exponential tail at large $t$, normalized by $D_{t_p,\sigma,\tau}$:
 \begin{equation}
@@
 Exponential & $\tau=3.0$ Gyr    & --- \\
-Prompt      & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
+Two-population  & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
             & $\tau=3.0$ Gyr & \\
@@
     \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
-In each panel, we plot curves for the zones which have inner radii of 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
+In each panel, we plot curves for the zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
     \label{fig:sfhs}
@@
 All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=0.01$ Gyr.
-We adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citep[see Equation 8 from][]{Johnson2021-Migration} and a star formation efficiency timescale $\tau_*\equiv M_{\rm gas}/\dot M_*=2$ Gyr.
+We adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citep[see Equation 8 from][]{Johnson2021-Migration}, a star formation efficiency timescale $\tau_*\equiv M_{\rm gas}/\dot M_*=2$ Gyr, and an initial gas mass $M_{\rm gas,0}=0$.
 We adopt a continuous recycling prescription \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
-Unless otherwise specified, we adopt the inside-out star formation rate (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc, with timescales $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr, and our models have an initial gas mass $M_{\rm gas,0}=0$.
-Unless otherwise specified, we assume a minimum SN Ia delay time of 40 Myr.
+Unless otherwise specified, we adopt the inside-out star formation rate (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr), and a minimum SN Ia delay time of 40 Myr.
 A summary of these one-zone fiducial parameters is presented in Table \ref{tab:onezone-parameters}.
@@
 \subsection{The SN Ia Delay-Time Distribution}
+\label{sec:onezone-dtd}
 
-Adjusting the parameters of the DTD affects how steeply the abundance track in [Fe/H]-[O/Fe] space falls from its initial ``plateau'' and the location of the ``knee.'' Figure \ref{fig:onezone-slope-timescale} shows abundance tracks from one-zone models which assume different slopes of a power-law DTD or different timescales of an exponential DTD.
+% Adjusting the parameters of the DTD affects how steeply the abundance track in [Fe/H]-[O/Fe] space falls from its initial ``plateau'' and the location of the ``knee.'' Figure \ref{fig:onezone-slope-timescale} shows abundance tracks from one-zone models which assume different slopes of a power-law DTD or different timescales of an exponential DTD.
 A steeper power-law slope results in a steeper decline in [O/Fe] and a lower knee, as does a shorter exponential timescale.
@@
 
+Figure \ref{fig:onezone-powerlaw-slope} compares the results of three one-zone models which are identical except for the slope of the power-law DTD.
+A steeper slope produces a sharper ``knee'' and a faster decline in [O/Fe], resulting in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
+Conversely, a shallower slope produces a gentler knee and slower decline in [O/Fe], resulting in a broader [O/Fe] distribution and a greater number of high-$\alpha$ stars.
+In all cases the [O/Fe] distribution is distinctly unimodal.
+The distribution of [Fe/H] is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
+
 \begin{figure}
@@
     \includegraphics{figures/onezone_powerlaw_slope.pdf}
-    \caption{\textit{Center:} Abundance tracks in the [Fe/H]-[O/Fe] plane for one-zone models with a power-law DTD.
+    \caption{\textit{Center:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone models with a power-law DTD.
 The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively.
+The open symbols located along each curve mark logarithmic steps in simulation time.
 In all cases a minimum SN Ia delay time of 40 Myr is assumed.
@@
 \end{figure}
+
+Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in Figure \ref{fig:onezone-exponential-timescale}.
+Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around 1 Gyr.
+A short exponential timescale shifts this knee down to lower [O/Fe] values, while a longer timescale raises it.
+The effect on the [O/Fe] distribution is similar to the power-law slope: a short timescale produces more low-$\alpha$ stars, while a long timescale produces more high-$\alpha$ stars (but still a unimodal distribution).
+The effect on the [Fe/H] distribution is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values.
+A doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
 
@@
     \script{onezone_plateau_width.py}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_twopopulation.pdf}
+    \caption{One-zone model abundance tracks and distributions for variants of the two-population DTD.}
+    \label{fig:onezone-prompt}
+    \script{onezone_twopopulation.py}
 \end{figure}
@@
 
-A 150 Myr minimum delay time is incompatible with the prompt DTD model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD as its relative SN Ia rate is so low at early times.
+A 150 Myr minimum delay time is incompatible with the two-population DTD model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD as its relative SN Ia rate is so low at early times.
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/onezone_sfh.pdf}
-    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying star formation history (SFH). An exponential DTD with $\tau=1.5$ Gyr is assumed in all models.}
-    \label{fig:onezone-sfh}
-    \script{onezone_sfh.py}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics{figures/onezone_sfh.pdf}
+%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying star formation history (SFH). An exponential DTD with $\tau=1.5$ Gyr is assumed in all models.}
+%     \label{fig:onezone-sfh}
+%     \script{onezone_sfh.py}
+% \end{figure}
 
@@
 In the ``CLOSE'' scheme, there is assumed to be a narrow distribution of $A/A_0$ and a correlation between $A$ and $m_{\rm DD}$, so the most massive binaries tend to merge quickly and the least massive merge last.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics{figures/greggio05_dtd.pdf}
-%     \caption{Analytical DTDs computed by \citet{Greggio2005-AnalyticalRates}.
-The solid red curve represents the SD DTD for Chandrasekhar explosions, while the green and blue solid curves represent, respectively, the CLOSE and WIDE formulations of a DD DTD.
-The best-fit approximations for the DD DTDs (see Equation \ref{eq:greggio05-approx}) are represented by the dashed olive and cyan curves, respectively.
-All DTDs are normalized to unity.}
-%     \label{fig:greggio05-dtd}
-%     \script{greggio05_dtd.py}
-% \end{figure}
 
@@
 \end{figure*}
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/onezone_twopopulation.pdf}
-    \caption{One-zone model abundance tracks and distributions for variants of the prompt DTD.}
-    \label{fig:onezone-prompt}
-    \script{onezone_twopopulation.py}
-\end{figure}
 
@@
 In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.
-Distributions from APOGEE DR17, binned similarly, are presented in the right-most column for reference.}
+Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
     \label{fig:feh-df-sfh}
@@
 
-Holding the SFH fixed, varying the DTD has only a minor effect on the MDF.
+Holding the SFH fixed, varying the DTD has only a minor effect on the MDF across the disk.
 Figure \ref{fig:feh-df-dtd} plots the [Fe/H] distributions for two multi-zone simulations which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
@@
 All assume an exponential DTD with $\tau=1.5$ Gyr.
-Each point plots the abundances of a single star particle and is color-coded according to its Galactocentric radius at birth.
-Each panel plots a random sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) weighted by their mass.
+Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
 A Gaussian scatter has been applied to all points based on the median abundance errors in APOGEE DR17.
@@
 
+\begin{figure*}
+    \centering
+    \includegraphics{figures/age_ofe_dtd.pdf}
+    \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different DTD models.
+All assume an inside-out SFH.
+Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
+Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar annulus ($7\leq R_{\rm gal}<9$ kpc) color-coded by the Galactocentric radius at birth.
+A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citet{Leung2023-Ages}.
+Black squares represent the mass-weighted median age of star particles within bins of [O/Fe] with a width of 0.05 dex, and the horizontal black error bars encompass the 16th and 84th percentiles.
+Red triangles represent the median age from \citet{Leung2023-Ages} in bins of [O/Fe], and the horizontal red error bars encompass the 16th and 84th percentiles.
+For clarity, bins which contain less than 1\% of the total mass (in the simulations) or total number of stars (in the data) are not plotted.}
+    \label{fig:age-ofe-dtd}
+    \script{age_ofe_dtd.py}
+\end{figure*}
+
 \begin{figure}
@@
     \includegraphics{figures/age_ofe_sfh.pdf}
-    \caption{Caption}
+    \caption{Similar to Figure \ref{fig:age-ofe-dtd} but for simulations with different SFH models.
+All assume an exponential DTD with $\tau=1.5$ Gyr.
+In all panels, stars are limited to the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc)}
     \label{fig:age-ofe-sfh}
@@
 
-    \item Our diagnostics consistently favor a DTD with a large fraction of delayed SNe Ia, such as the 3 Gyr exponential, 1 Gyr plateau, or triple system evolution models, over a DTD with a high number of prompt SNe Ia, such as the $t^{-1.4}$ power law or prompt models.
+    \item Our diagnostics consistently favor a DTD with a large fraction of delayed SNe Ia, such as the 3 Gyr exponential, 1 Gyr plateau, or triple system evolution models, over a DTD with a high number of prompt SNe Ia, such as the $t^{-1.4}$ power-law or two-population models.
 [Discuss the disconnect and/or complement with \citet{Maoz2017-CosmicDTD}, etc.; something about different timescales probed by volumetric surveys vs.
@@
 
+\section{Analytical DTDs}
+\label{app:analytical-dtds}
+
+Discuss \citet{Greggio2005-AnalyticalRates} vs our simple function approximations here?
+
 \bibliography{bib}

### 2023-07-25 src/scripts/delay_time_distributions.py
add multipanel onezone figure

@@ -7,9 +7,8 @@ from matplotlib.ticker import FuncFormatter
 import paths
 from multizone.src import dtds
 from colormaps import paultol
+from _globals import MIN_RIA_DELAY
 plt.rcParams['axes.prop_cycle'] = plt.cycler('color', paultol.bright.colors)
-
-DELAY = 0.04 # minimum Ia delay time in Gyr
 
 def main():
     plt.style.use(paths.styles / 'paper.mplstyle')
@@ -30,52 +29,52 @@ def main():
 class styles:
     """Plot styling for different DTD models."""
     plaw = {
-        'func': dtds.powerlaw(slope=-1.1, tmin=DELAY),
+        'func': dtds.powerlaw(slope=-1.1, tmin=MIN_RIA_DELAY),
         'label': r'Power-law ($\alpha=-1.1$)',
         'color': paultol.bright.colors[0],
         'line': '-',
     }
     plateau = {
-        'func': dtds.plateau(width=0.3, slope=-1.1, tmin=DELAY),
+        'func': dtds.plateau(width=0.3, slope=-1.1, tmin=MIN_RIA_DELAY),
         'label': r'Plateau ($W=0.3$ Gyr)',
         'color': paultol.bright.colors[4],
         'line': '--',
     }
     exp = {
-        'func': dtds.exponential(timescale=1.5, tmin=DELAY),
+        'func': dtds.exponential(timescale=1.5, tmin=MIN_RIA_DELAY),
         'label': r'Exponential ($\tau=1.5$ Gyr)',
         'color': paultol.bright.colors[5],
         'line': '-',
     }
     prompt = {
-        'func': dtds.prompt(peak=0.05, stdev=0.015, timescale=3, tmin=DELAY),
+        'func': dtds.prompt(peak=0.05, stdev=0.015, timescale=3, tmin=MIN_RIA_DELAY),
         'label': 'Two-population',
         'color': paultol.bright.colors[1],
         'line': ':',
     }
     triple = {
-        'func': dtds.triple(tmin=DELAY),
+        'func': dtds.triple(tmin=MIN_RIA_DELAY),
         'label': r'Triple-system',
         'color': paultol.bright.colors[2],
         'line': '-.'
     }
     # Additional DTDs
     exp_long = {
-        'func': dtds.exponential(timescale=3, tmin=DELAY),
+        'func': dtds.exponential(timescale=3, tmin=MIN_RIA_DELAY),
[…]

### 2023-07-25 src/scripts/onezone_multipanel.py

@@ -1,0 +1,230 @@
+"""
+This script generates plots for a multi-panel figure comparing the results
+of several one-zone chemical evolution models with various DTD parameters.
+"""
+
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.lines import Line2D
+import vice
+import paths
+from multizone.src.yields import J21
+from multizone.src import models, dtds
+from _globals import END_TIME, ONEZONE_DEFAULTS
+from colormaps import paultol
+from track_and_mdf import setup_axes, plot_vice_onezone
+from delay_time_distributions import styles
+
+def main():
+    plt.style.use(paths.styles / 'paper.mplstyle')
+    plt.rcParams['axes.prop_cycle'] = plt.cycler('color', paultol.bright.colors)
+    plot_powerlaw_slope()
+    plot_exponential_timescale()
+    plot_plateau_width()
+    plot_minimum_delay()
+    plot_all()
+
+
+def plot_powerlaw_slope():
+    slopes = [-0.8, -1.1,-1.4]
+    line_styles = ['-', '--', ':']
+    
+    output_dir = paths.data / 'onezone' / 'powerlaw_slope'
+    if not output_dir.exists():
+        output_dir.mkdir(parents=True)
+    
+    fig, axs = setup_axes(title='Power-law DTD')
+    
+    for i, slope in enumerate(slopes):
+        dtd = dtds.powerlaw(slope=slope, tmin=ONEZONE_DEFAULTS['delay'])
+        run_onezone(dtd, output_dir=output_dir)
+        plot_vice_onezone(str(output_dir / dtd.name), 
+                          fig=fig, axs=axs, 
+                          linestyle=line_styles[i], 
+                          color=styles.plaw['color'], 
+                          label=rf'$\alpha={slope:.1f}$', 
+                          marker_labels=(i==0))
+    
+    # Re-scale marginal axis limits
+    axs[1].set_ylim(bottom=0)
+    axs[2].set_xlim(left=0)
+    axs[0].legend(frameon=False, loc='lower left')
+    fig.savefig(paths.figures / 'onezone_powerlaw_slope.pdf', dpi=300)
+    plt.close()
+    
+    
+def plot_exponential_timescale():
+    timescales = [6, 3, 1.5]
+    line_styles = ['-', '--', ':']
+    
+    output_dir = paths.data / 'onezone' / 'exponential_timescale'
+    if not output_dir.exists():
[…]

### 2023-07-25 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \section{Introduction}
+
+Studies of galactic chemical evolution typically assume a single form for the SN Ia DTD.
+This is the first comprehensive look at the DTD in a model for GCE which includes the effects of radial migration.
+
+Why radial migration is important for SNe Ia.
+
+Summary of observational studies of the DTD.
+These studies all assume a particular form for the DTD and fit for the specific parameters.
+They do not quantitatively favor one form over another (e.g., power-law over exponential).
 
@@
 Figure \ref{fig:dtd-greggio05} illustrates the similarity between these models and two different treatments of the analytical double-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/dtd_greggio05.pdf}
-    \caption{Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and close approximation simple functions (dashed curves).
-Some functions are presented with a constant multiplicative factor for visual clarity.}
-    \label{fig:dtd-greggio05}
-    \script{dtd_greggio05.py}
-\end{figure}
 
@@
 
-\subsection{Stellar Migration}
-\label{sec:migration}
-
-For each star particle in VICE, \citet{Johnson2021-Migration} randomly assign an analogue star particle from \texttt{h277} and adopt its radial migration distance $\Delta R$ and final midplane distance $z$.
-This allows VICE to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
-However, in regions where the number of h277 star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single h277 star particle can be assigned as an analogue to multiple VICE stellar populations.
-These populations will have similar formation and migration histories and consequently similar abundances, which produces unphysical ``clumps'' of stars in the abundance distributions at high latitudes and large radii.
-
-We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm initial}$ from the \texttt{h277} output in bins of $R_{\rm initial}$ and age.
-Each Gaussian is centered at 0 and we find that the scale $\sigma_{\Delta R}$ is best described by the function
-
-\begin{equation}
-    \sigma_{\Delta R} = 1.35\,{\rm kpc} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61} \Big(\frac{\tau}{1\,{\rm Gyr}}\Big)^{0.33}
-    \label{eq:radial-migration}
-\end{equation}
-
-\noindent where $\tau$ is the age of the star particle.
-
-We fit a sech$^2$ function \citep{Spitzer1942} to the distribution of midplane distances $z_{\rm final}$.
-Vertical migration away from the midplane does not affect the chemical evolution simulation, but we do use $z_{\rm final}$ in our analysis.
-The probability density function (PDF) of $z_{\rm final}$ given some scale height $h_z$ is
-\begin{equation}
-    {\rm PDF}(z_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z_{\rm final}}{2 h_z}\Big)
-    \label{eq:sech-pdf}
-\end{equation}
-and the corresponding cumulative distribution function (CDF) is
-\begin{equation}
-    {\rm CDF}(z_{\rm final}) = \frac{1}{1 + e^{-z_{\rm final} / h_z}}.
-    \label{eq:sech-cdf}
-\end{equation}
-We fit the above function to the distributions of $z_{\rm final}$ in h277 in varying bins of $\tau$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
-\begin{equation}
-    h_z = (0.25\,{\rm kpc}) 
-    e^{\frac{\tau-5\,{\rm Gyr}}{7.0\,{\rm Gyr}}}
-    e^{\frac{R_{\rm final}-8\,{\rm kpc}}{6.0\,{\rm kpc}}}.
-    \label{eq:scale-height}
-\end{equation}
-
-When a star particle is created by VICE at initial radius $R_{\rm form}$, we sample its total radial migration distance $\Delta R$ from a Gaussian with a width described by Equation \ref{eq:radial-migration}, and we sample its final midplane distance $z_{\rm final}$ from the distribution described by Equation \ref{eq:sech-pdf} with a width given by Equation \ref{eq:scale-height}.
-The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citet{Johnson2021-Migration}, but with a time dependence $\propto t^{1/3}$.
-This produces distributions of $R_{\rm final}$ and $z_{\rm final}$ which are similar to the analogue migration case for all but the oldest stars.
-
-Figure \ref{fig:radial-migration} compares the distributions of $R_{\rm final}$ in bins of $R_{\rm form}$ and age between the analogue and Gaussian migration schema. The
-
-\begin{figure*}
-    \centering
-    \includegraphics{figures/radial_migration.pdf}
-    \caption{The distribution of final radius $R_{\rm final}$ as a function of formation radius $R_{\rm form}$ and age for the h277 analogue (top row) and Gaussian sampling scheme (bottom row).
-From left to right, star particles are binned by formation annulus, from the inner disk (far left column) to the Solar annulus (center column) to the outer disk (far right column).
-Within each panel, colored curves represent the different age bins, ranging from the youngest stars (dark blue) to the oldest (dark red).
-All distributions are normalized so that the area under the curve is 1, and have been smoothed by a boxcar function of width 0.5 kpc.
-The vertical dotted black lines indicate the bounds of each bin in $R_{\rm form}$; stars within that region of the distribution have not migrated outside their birth annulus over their lifetime.}
-    \label{fig:radial-migration}
-    \script{radial_migration.py}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \includegraphics{figures/midplane_distance.pdf}
-    \caption{Similar to Figure \ref{fig:radial-migration} but for the distribution of final midplane distance $z_{\rm final}$ as a function of final radius and age.
-From left to right, star particles are binned by \textit{final} annulus.
-All distributions have been smoothed by a boxcar function of width 0.1 kpc.}
-    \label{fig:midplane-distance}
-    \script{midplane_distance.py}
-\end{figure*}
-
 \subsection{Nucleosynthetic Yields}
@@
 \label{sec:onezone-dtd}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.32\linewidth]{figures/onezone_powerlaw_slope.pdf}
+    \includegraphics[width=0.32\linewidth]{figures/onezone_exponential_timescale.pdf}
+    \includegraphics[width=0.32\linewidth]{figures/onezone_plateau_width.pdf}
+    \\
+    \includegraphics[width=0.49\linewidth]{figures/onezone_minimum_delay.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/onezone_dtd.pdf}
+    \caption{}
+    \label{fig:onezone-multipanel}
+    \script{onezone_multipanel.py}
+\end{figure*}
 
@@
 
-\subsection{The Star Formation History}
+% \subsection{The Star Formation History}
 
-Figure \ref{fig:onezone-delay-taustar} shows results from one-zone models with a power-law DTD which differ in their assumed minimum SN Ia delay time ($t_D$) or star formation efficiency timescale ($\tau_*$).
+% Figure \ref{fig:onezone-delay-taustar} shows results from one-zone models with a power-law DTD which differ in their assumed minimum SN Ia delay time ($t_D$) or star formation efficiency timescale ($\tau_*$).
 In [Fe/H]-[O/Fe] space, doubling or halving the minimum delay time produces similar results to doubling or halving the SFE timescale.
@@
 
-The minimum delay and SFE timescale have similar effects on the abundance tracks but very different effects on the MDFs.
+% The minimum delay and SFE timescale have similar effects on the abundance tracks but very different effects on the MDFs.
 Altering the SFE timescale changes the stellar distribution of [Fe/H], especially at the low-metallicity end, as shown in the top panel of Figure \ref{fig:onezone-delay-taustar}.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/onezone_delay_taustar.pdf}
-    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\tau_*$).
+% \begin{figure}
+%     \centering
+%     \includegraphics{figures/onezone_delay_taustar.pdf}
+%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\tau_*$).
 Tracks with $\tau_*=2$ Gyr are represented in black, while a track with a shorter $\tau_*=1$ Gyr is shown in red and a track with a longer $\tau_*=4$ Gyr is in yellow.
@@
 A power-law DTD with $\alpha=-1.1$ is assumed in all models.}
-    \label{fig:onezone-delay-taustar}
-    \script{onezone_delay_taustar.py}
-\end{figure}
+%     \label{fig:onezone-delay-taustar}
+%     \script{onezone_delay_taustar.py}
+% \end{figure}
 
@@
 A multi-zone with the \citet{Greggio2005-AnalyticalRates} SD DTD produced nearly identical results to an exponential DTD with a 1.5 Gyr timescale.
-
-\begin{figure*}
-    \centering
-    \includegraphics{figures/onezone_greggio05_single.pdf}
-    \includegraphics{figures/onezone_greggio05_double.pdf}
-    \caption{Abundance tracks and distributions from one-zone models with the analytical DTDs from \citet{Greggio2005-AnalyticalRates}.
-\textit{Left:} a comparison between the analytical SD DTD (solid magenta curve), an exponential DTD with a 1.5 Gyr timescale (dashed pink curve), and a power-law DTD with a slope of -1.1 (dotted black curve).
-\textit{Right:} a comparison between WIDE and CLOSE prescriptions for an analytical DD DTD (solid blue and green curves, respectively), power-law DTDs with an initial plateau of 1 Gyr and 300 Myr (dashed cyan and yellow curves, respectively), and a power-law DTD with no plateau and a slope of -1.1 (dotted black curve).}
-    \label{fig:onezone-greggio05}
-    \script{onezone_greggio05.py}
-\end{figure*}
 
@@
 
+\begin{figure*}
+    \centering
+    \includegraphics{figures/dtd_analytical.pdf}
+    \includegraphics{figures/onezone_analytical_dtd.pdf}
+    \caption{\textit{Left:} Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and close approximation simple functions (dashed curves).
+Some functions are presented with a constant multiplicative factor for visual clarity.
+\textit{Right:} Abundance tracks and distributions from one-zone models with the analytical DTDs from \citet{Greggio2005-AnalyticalRates}.
+\textit{Left:} a comparison between the analytical SD DTD (solid magenta curve), an exponential DTD with a 1.5 Gyr timescale (dashed pink curve), and a power-law DTD with a slope of -1.1 (dotted black curve).
+\textit{Right:} a comparison between WIDE and CLOSE prescriptions for an analytical DD DTD (solid blue and green curves, respectively), power-law DTDs with an initial plateau of 1 Gyr and 300 Myr (dashed cyan and yellow curves, respectively), and a power-law DTD with no plateau and a slope of -1.1 (dotted black curve).}
+    \label{fig:analytical-dtd}
+    \script{analytical_dtd_twopanel.py}
+\end{figure*}
+
+\section{Stellar Migration}
+\label{app:migration}
+
+For each star particle in VICE, \citet{Johnson2021-Migration} randomly assign an analogue star particle from \texttt{h277} and adopt its radial migration distance $\Delta R$ and final midplane distance $z$.
+This allows VICE to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
+However, in regions where the number of h277 star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single h277 star particle can be assigned as an analogue to multiple VICE stellar populations.
+These populations will have similar formation and migration histories and consequently similar abundances, which produces unphysical ``clumps'' of stars in the abundance distributions at high latitudes and large radii.
+
+We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm initial}$ from the \texttt{h277} output in bins of $R_{\rm initial}$ and age.
+Each Gaussian is centered at 0 and we find that the scale $\sigma_{\Delta R}$ is best described by the function
+\begin{equation}
+    \sigma_{\Delta R} = 1.35\,{\rm kpc} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61} \Big(\frac{\tau}{1\,{\rm Gyr}}\Big)^{0.33}
+    \label{eq:radial-migration}
+\end{equation}
+where $\tau$ is the age of the star particle.
+
+We fit a sech$^2$ function \citep{Spitzer1942} to the distribution of midplane distances $z_{\rm final}$.
+Vertical migration away from the midplane does not affect the chemical evolution simulation, but we do use $z_{\rm final}$ in our analysis.
+The probability density function (PDF) of $z_{\rm final}$ given some scale height $h_z$ is
+\begin{equation}
+    {\rm PDF}(z_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z_{\rm final}}{2 h_z}\Big)
+    \label{eq:sech-pdf}
+\end{equation}
+and the corresponding cumulative distribution function (CDF) is
+\begin{equation}
+    {\rm CDF}(z_{\rm final}) = \frac{1}{1 + e^{-z_{\rm final} / h_z}}.
+    \label{eq:sech-cdf}
+\end{equation}
+We fit the above function to the distributions of $z_{\rm final}$ in h277 in varying bins of $\tau$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
+\begin{equation}
+    h_z = (0.25\,{\rm kpc}) 
+    e^{\frac{\tau-5\,{\rm Gyr}}{7.0\,{\rm Gyr}}}
+    e^{\frac{R_{\rm final}-8\,{\rm kpc}}{6.0\,{\rm kpc}}}.
+    \label{eq:scale-height}
+\end{equation}
+
+When a star particle is created by VICE at initial radius $R_{\rm form}$, we sample its total radial migration distance $\Delta R$ from a Gaussian with a width described by Equation \ref{eq:radial-migration}, and we sample its final midplane distance $z_{\rm final}$ from the distribution described by Equation \ref{eq:sech-pdf} with a width given by Equation \ref{eq:scale-height}.
+The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citet{Johnson2021-Migration}, but with a time dependence $\propto t^{1/3}$.
+This produces distributions of $R_{\rm final}$ and $z_{\rm final}$ which are similar to the analogue migration case for all but the oldest stars.
+
+Figure \ref{fig:radial-migration} compares the distributions of $R_{\rm final}$ in bins of $R_{\rm form}$ and age between the analogue and Gaussian migration schema. The
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/radial_migration.pdf}
+    \caption{The distribution of final radius $R_{\rm final}$ as a function of formation radius $R_{\rm form}$ and age for the h277 analogue (top row) and Gaussian sampling scheme (bottom row).
+From left to right, star particles are binned by formation annulus, from the inner disk (far left column) to the Solar annulus (center column) to the outer disk (far right column).
+Within each panel, colored curves represent the different age bins, ranging from the youngest stars (dark blue) to the oldest (dark red).
+All distributions are normalized so that the area under the curve is 1, and have been smoothed by a boxcar function of width 0.5 kpc.
+The vertical dotted black lines indicate the bounds of each bin in $R_{\rm form}$; stars within that region of the distribution have not migrated outside their birth annulus over their lifetime.}
+    \label{fig:radial-migration}
+    \script{radial_migration.py}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/midplane_distance.pdf}
+    \caption{Similar to Figure \ref{fig:radial-migration} but for the distribution of final midplane distance $z_{\rm final}$ as a function of final radius and age.
+From left to right, star particles are binned by \textit{final} annulus.
+All distributions have been smoothed by a boxcar function of width 0.1 kpc.}
+    \label{fig:midplane-distance}
+    \script{midplane_distance.py}
+\end{figure*}
+
 \bibliography{bib}

### 2023-07-26 src/scripts/feh_df_comparison.py
add single mdf comparison plot

@@ -1,0 +1,66 @@
+"""
+This script plots [Fe/H] distribution functions from VICE runs with the same
+DTD but different SFHs.
+"""
+
+import argparse
+from pathlib import Path
+import matplotlib.pyplot as plt
+import distribution_functions as dfs
+from multizone_stars import MultizoneStars
+from apogee_tools import import_apogee
+from utils import get_color_list
+import paths
+import _globals
+
+# Multizone outputs
+SFH_LIST = ['insideout', 'twoinfall']
+SFH_LABELS = ['Inside-out', 'Two-infall']
+DTD_MODEL = 'exponential_timescale15' # hold constant while varying SFH
+DTD_LIST = ['powerlaw_slope14',
+            'exponential_timescale30']
+DTD_LABELS = ['Power-law\n($\\alpha=-1.4$)',
+              'Exponential\n($\\tau=3$ Gyr)']
+SFH_MODEL = 'insideout' # hold constant while varying DTD
+# Plot settings
+NBINS = 100
+FEH_LIM = (-1.1, 0.6)
+SMOOTH_WIDTH = 0.2
+CMAP = 'plasma_r'
+
+def main():
+    plt.style.use(paths.styles / 'paper.mplstyle')
+    apogee_data = import_apogee()
+    # Set up plot
+    fig, axs = dfs.setup_axes(ncols=len(SFH_LIST)+len(DTD_LIST)+1, 
+                              figure_width=_globals.TWO_COLUMN_WIDTH, 
+                              cmap_name=CMAP, xlabel='[Fe/H]', xlim=FEH_LIM, 
+                              major_tick_spacing=0.5, cbar_width=0.4)
+    fig.subplots_adjust(top=0.9, left=0.07, right=0.98)
+    colors = get_color_list(plt.get_cmap(CMAP), _globals.GALR_BINS)
+    # plot varying SFH, constant DTD
+    mdf_kwargs = {'bins': NBINS, 'range': FEH_LIM, 'smoothing': SMOOTH_WIDTH}
+    for i, sfh in enumerate(SFH_LIST):
+        output_name = '/'.join(['gaussian', sfh, DTD_MODEL, 'diskmodel'])
+        mzs = MultizoneStars.from_output(output_name)
+        mzs.model_uncertainty(apogee_data, inplace=True)
+        dfs.plot_multizone_mdfs(mzs, axs[:,i], '[fe/h]', colors, 
[…]

### 2023-07-26 src/scripts/onezone_multipanel.py

@@ -98,7 +98,7 @@ def plot_plateau_width():
     plot_vice_onezone(str(output_dir / dtd.name), 
                       fig=fig, axs=axs,
                       linestyle=':', 
-                      color=styles.plateau['color'], 
+                      color=styles.exp['color'], 
                       label=rf'Exponential ($\tau=3$ Gyr)', 
                       marker_labels=True, 
                       linewidth=1.5)
@@ -110,7 +110,7 @@ def plot_plateau_width():
         plot_vice_onezone(str(output_dir / dtd.name), 
                           fig=fig, axs=axs,
                           linestyle=line_styles[i], 
-                          color=styles.exp['color'], 
+                          color=styles.plateau['color'], 
                           label=r'$W={:1.1f}$ Gyr'.format(width))
     
     # Power law for comparison

### 2023-07-26 src/scripts/delay_time_distributions.py
update colors

@@ -31,19 +31,19 @@ class styles:
     plaw = {
         'func': dtds.powerlaw(slope=-1.1, tmin=MIN_RIA_DELAY),
         'label': r'Power-law ($\alpha=-1.1$)',
-        'color': paultol.bright.colors[0],
+        'color': paultol.bright.colors[5],
         'line': '-',
     }
     plateau = {
         'func': dtds.plateau(width=0.3, slope=-1.1, tmin=MIN_RIA_DELAY),
         'label': r'Plateau ($W=0.3$ Gyr)',
-        'color': paultol.bright.colors[4],
+        'color': paultol.bright.colors[2],
         'line': '--',
     }
     exp = {
         'func': dtds.exponential(timescale=1.5, tmin=MIN_RIA_DELAY),
         'label': r'Exponential ($\tau=1.5$ Gyr)',
-        'color': paultol.bright.colors[5],
+        'color': paultol.bright.colors[0],
         'line': '-',
     }
     prompt = {
@@ -55,26 +55,26 @@ class styles:
     triple = {
         'func': dtds.triple(tmin=MIN_RIA_DELAY),
         'label': r'Triple-system',
-        'color': paultol.bright.colors[2],
+        'color': paultol.bright.colors[3],
         'line': '-.'
     }
     # Additional DTDs
     exp_long = {
         'func': dtds.exponential(timescale=3, tmin=MIN_RIA_DELAY),
         'label': r'Exponential ($\tau=3$ Gyr)',
-        'color': paultol.bright.colors[5],
+        'color': paultol.bright.colors[0],
         'line': '--',
     }
     plateau_long = {
         'func': dtds.plateau(width=1., slope=-1.1, tmin=MIN_RIA_DELAY),
         'label': r'Plateau ($W=1$ Gyr)',
-        'color': paultol.bright.colors[4],
+        'color': paultol.bright.colors[2],
         'line': ':',
     }
     plaw_steep = {
         'func': dtds.powerlaw(slope=-1.4, tmin=MIN_RIA_DELAY),
         'label': r'Power-law ($\alpha=-1.4$)',
-        'color': paultol.bright.colors[0],
+        'color': paultol.bright.colors[5],
         'line': '--',
     }
 

### 2023-07-26 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     SN Ia   & O     & 0         \\
-    SN Ia   & Fe    & 0.00214   \\
+    SN Ia   & Fe    & 0.00214
     \enddata
@@
     \includegraphics[width=0.32\linewidth]{figures/onezone_plateau_width.pdf}
-    \\
     \includegraphics[width=0.49\linewidth]{figures/onezone_minimum_delay.pdf}
     \includegraphics[width=0.49\linewidth]{figures/onezone_dtd.pdf}
-    \caption{}
+    \caption{\textit{Top left:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone models with a power-law DTD.
+The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively.
+The open symbols located along each curve mark logarithmic steps in simulation time.
+In all cases a minimum SN Ia delay time of 40 Myr is assumed.
+The marginal panels above and to the right present the distributions of [Fe/H] and [O/Fe], respectively, convolved with a Gaussian with a standard deviation of 0.02 dex for display purposes.
+    \textit{Top middle:} A similar plot comparing exponential DTDs with varying timescales. The solid, dashed, and dotted curves represent timescales $\tau=6$, 3, and 1.5 Gyr, respectively.
+    \textit{Top right:} Similar, comparing plateau DTDs with varying plateau widths.
+The solid, dashed, and dotted curves represent widths $W=1$, 0.3, and 0.1 Gyr, respectively.
+All plateau DTD models assume a post-plateau power-law slope of $\alpha=-1.1$.
+For reference, the dotted purple curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted blue curve represents a power-law DTD $\alpha=-1.1$ and no plateau.
+    \textit{Bottom left:} A similar plot comparing minimum SN Ia delay times of 40 Myr (solid) and 150 Myr (dashed) for two DTDs: a power-law with $\alpha=-1.1$ (blue), and an exponential with $\tau=1.5$ Gyr (purple).
+    \textit{Bottom right:} A similar plot comparing all five functional forms for the DTD in this paper: triple-system (green), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
+In all cases a minimum SN Ia delay time of 40 Myr is assumed.}
     \label{fig:onezone-multipanel}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/onezone_powerlaw_slope.pdf}
-    \caption{\textit{Center:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone models with a power-law DTD.
+% \begin{figure}
+%     \centering
+%     \includegraphics{figures/onezone_powerlaw_slope.pdf}
+%     \caption{\textit{Center:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone models with a power-law DTD.
 The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively.
@@
 \textit{Right:} Distributions of [O/Fe] generated by the one-zone models.}
-    \label{fig:onezone-powerlaw-slope}
-    \script{onezone_powerlaw_slope.py}
-\end{figure}
+%     \label{fig:onezone-powerlaw-slope}
+%     \script{onezone_powerlaw_slope.py}
+% \end{figure}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/onezone_exponential_timescale.pdf}
-    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with an exponential DTD.
+% \begin{figure}
+%     \centering
+%     \includegraphics{figures/onezone_exponential_timescale.pdf}
+%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with an exponential DTD.
 The dotted, dashed, and solid curves represent exponential decay timescales $\tau=1.5$ Gyr, 3 Gyr, and 6 Gyr, respectively.}
-    \label{fig:onezone-exponential-timescale}
-    \script{onezone_exponential_timescale.py}
-\end{figure}
+%     \label{fig:onezone-exponential-timescale}
+%     \script{onezone_exponential_timescale.py}
+% \end{figure}
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/onezone_plateau_width.pdf}
-    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with a plateau DTD.
+% \begin{figure}
+%     \centering
+%     \includegraphics{figures/onezone_plateau_width.pdf}
+%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with a plateau DTD.
 The solid, dashed, and dot-dashed pink curves represent plateau widths $W=1.0$, 0.3, and 0.1 Gyr, respectively.
@@
 For comparison, the blue dotted curve represents an exponential DTD with a timescale $\tau=3$ Gyr, and the black dotted curve represents a power-law DTD with the same slope but no plateau.}
-    \label{fig:onezone-plateau-width}
-    \script{onezone_plateau_width.py}
-\end{figure}
+%     \label{fig:onezone-plateau-width}
+%     \script{onezone_plateau_width.py}
+% \end{figure}
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/onezone_twopopulation.pdf}
-    \caption{One-zone model abundance tracks and distributions for variants of the two-population DTD.}
-    \label{fig:onezone-prompt}
-    \script{onezone_twopopulation.py}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics{figures/onezone_twopopulation.pdf}
+%     \caption{One-zone model abundance tracks and distributions for variants of the two-population DTD.}
+%     \label{fig:onezone-prompt}
+%     \script{onezone_twopopulation.py}
+% \end{figure}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/onezone_dtd.pdf}
-    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with a different selection of DTDs. In all cases a minimum delay time of 40 Myr is assumed.}
-    \label{fig:onezone-dtd}
-    \script{onezone_dtd.py}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics{figures/onezone_dtd.pdf}
+%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with a different selection of DTDs. In all cases a minimum delay time of 40 Myr is assumed.}
+%     \label{fig:onezone-dtd}
+%     \script{onezone_dtd.py}
+% \end{figure}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/onezone_minimum_delay.pdf}
-    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying DTD models and minimum SN Ia delay time ($t_D$).
+% \begin{figure}
+%     \centering
+%     \includegraphics{figures/onezone_minimum_delay.pdf}
+%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying DTD models and minimum SN Ia delay time ($t_D$).
 Solid curves represent models with a minimum delay time of 40 Myr, while dashed curves represent models with a minimum delay time of 150 Myr.
@@
 In all cases an exponential rise-fall SFR is assumed.}
-    \label{fig:onezone-minimum-delay}
-    \script{onezone_minimum_delay.py}
-\end{figure}
+%     \label{fig:onezone-minimum-delay}
+%     \script{onezone_minimum_delay.py}
+% \end{figure}
 
@@
 
-\subsection{Analytical Formulations}
-
-\citet{Greggio2005-AnalyticalRates} derives analytical DTDs for SD and DD progenitor systems from assumptions about binary stellar evolution and outcomes of mass exchange.
-They find that the parameters which have a large effect on the shape of the DTD are the distribution and range of stellar masses in progenitor systems; the efficiency of accretion in the SD scenario; and the distribution of separations at birth in the DD scenario.
-Figure \ref{fig:dtd-greggio05} shows the analytical DTDs for SD progenitors and two different prescriptions for DD progenitors (``WIDE'' and ``CLOSE'').
-In the ``WIDE'' scheme, it is assumed that there is a wide distribution of ratios $A/A_0$ of the separation of the DD system to the initial separation of the binary, and that the distributions of $A$ and total mass of the system $m_{\rm DD}$ are independent, so one cannot necessarily predict the total merge time of a system based on its initial parameters.
-In the ``CLOSE'' scheme, there is assumed to be a narrow distribution of $A/A_0$ and a correlation between $A$ and $m_{\rm DD}$, so the most massive binaries tend to merge quickly and the least massive merge last.
-
-Figure \ref{fig:onezone-greggio05} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs.
-We assume $\eta=2.5$, $\tau_*=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
-We compare the SD, DD WIDE, and DD CLOSE schemes to standard power-law, broken power-law, and exponential DTDs.
-The SD and DD CLOSE DTDs follow nearly identical tracks in [O/Fe] vs [Fe/H]; however, their distributions on [O/Fe] differ at the low end.
-The SD DTD follows an exponential with a 1.5 Gyr timescale, whereas the DD CLOSE DTD is well-approximated by a broken power-law with an initial plateau of 350 Myr and a subsequent declining slope of -1.1.
-The WIDE prescription is likewise best approximated by a broken power-law, but with a longer plateau width of 1 Gyr.
-In all cases, the difference between the analytical DTD and the nearest broken power-law or exponential is likely too small to be observationally detectable, so in our multi-zone models we implement the more generic functions in lieu of the analytical DTDs.
-
-A multi-zone with the \citet{Greggio2005-AnalyticalRates} SD DTD produced nearly identical results to an exponential DTD with a 1.5 Gyr timescale.
-
 \section{Results from Multi-Zone Models}
@@
 
+Holding the SFH fixed, varying the DTD has only a minor effect on the MDF across the disk.
+Figure \ref{fig:feh-df-dtd} plots the [Fe/H] distributions for two multi-zone simulations which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
+The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of SNe Ia exploding within 1 Gyr in the former model but only $\sim 30\%$ in the latter.
+Nevertheless, the effect of the DTD on the MDF is second-order compared to the effect of the SFH as seen in Figure \ref{fig:feh-df-sfh}.
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/feh_df_dtd.pdf}
+    \caption{Distributions of [Fe/H] for multi-zone simulations with different DTDs: a power-law with slope $\alpha=-1.4$ (\textit{left}), and an exponential with timescale $\tau=3$ Gyr (\textit{right}).
+In both cases an inside-out SFH is assumed.
+The plot format is similar to Figure \ref{fig:feh-df-sfh}.}
+    \label{fig:feh-df-dtd}
+    \script{feh_df_dtd.py}
+\end{figure}
+
 Figure \ref{fig:feh-df-sfh} plots the distribution of [Fe/H] in multiple regions across the disk for the four SFHs in this paper.
@@
 \end{figure*}
-
-Holding the SFH fixed, varying the DTD has only a minor effect on the MDF across the disk.
-Figure \ref{fig:feh-df-dtd} plots the [Fe/H] distributions for two multi-zone simulations which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
-The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of SNe Ia exploding within 1 Gyr in the former model but only $\sim 30\%$ in the latter.
-Nevertheless, the effect of the DTD on the MDF is second-order compared to the effect of the SFH as seen in Figure \ref{fig:feh-df-sfh}.
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/feh_df_dtd.pdf}
-    \caption{Distributions of [Fe/H] for multi-zone simulations with different DTDs: a power-law with slope $\alpha=-1.4$ (\textit{left}), and an exponential with timescale $\tau=3$ Gyr (\textit{right}).
-In both cases an inside-out SFH is assumed.
-The plot format is similar to Figure \ref{fig:feh-df-sfh}.}
-    \label{fig:feh-df-dtd}
-    \script{feh_df_dtd.py}
-\end{figure}
-
 \subsection{The distribution of [O/Fe]}
@@
 
+\citet{Greggio2005-AnalyticalRates} derives analytical DTDs for SD and DD progenitor systems from assumptions about binary stellar evolution and outcomes of mass exchange.
+They find that the parameters which have a large effect on the shape of the DTD are the distribution and range of stellar masses in progenitor systems; the efficiency of accretion in the SD scenario; and the distribution of separations at birth in the DD scenario.
+Figure \ref{fig:dtd-greggio05} shows the analytical DTDs for SD progenitors and two different prescriptions for DD progenitors (``WIDE'' and ``CLOSE'').
+In the ``WIDE'' scheme, it is assumed that there is a wide distribution of ratios $A/A_0$ of the separation of the DD system to the initial separation of the binary, and that the distributions of $A$ and total mass of the system $m_{\rm DD}$ are independent, so one cannot necessarily predict the total merge time of a system based on its initial parameters.
+In the ``CLOSE'' scheme, there is assumed to be a narrow distribution of $A/A_0$ and a correlation between $A$ and $m_{\rm DD}$, so the most massive binaries tend to merge quickly and the least massive merge last.
+
+Figure \ref{fig:onezone-greggio05} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs.
+We assume $\eta=2.5$, $\tau_*=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
+We compare the SD, DD WIDE, and DD CLOSE schemes to standard power-law, broken power-law, and exponential DTDs.
+The SD and DD CLOSE DTDs follow nearly identical tracks in [O/Fe] vs [Fe/H]; however, their distributions on [O/Fe] differ at the low end.
+The SD DTD follows an exponential with a 1.5 Gyr timescale, whereas the DD CLOSE DTD is well-approximated by a broken power-law with an initial plateau of 350 Myr and a subsequent declining slope of -1.1.
+The WIDE prescription is likewise best approximated by a broken power-law, but with a longer plateau width of 1 Gyr.
+In all cases, the difference between the analytical DTD and the nearest broken power-law or exponential is likely too small to be observationally detectable, so in our multi-zone models we implement the more generic functions in lieu of the analytical DTDs.
+
+A multi-zone with the \citet{Greggio2005-AnalyticalRates} SD DTD produced nearly identical results to an exponential DTD with a 1.5 Gyr timescale.
+
 \begin{figure*}

### 2023-07-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \includegraphics[width=0.32\linewidth]{figures/onezone_plateau_width.pdf}
-    \includegraphics[width=0.49\linewidth]{figures/onezone_minimum_delay.pdf}
-    \includegraphics[width=0.49\linewidth]{figures/onezone_dtd.pdf}
-    \caption{\textit{Top left:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone models with a power-law DTD.
+    \caption{\textit{Left:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone models with a power-law DTD.
 The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively.
@@
 The marginal panels above and to the right present the distributions of [Fe/H] and [O/Fe], respectively, convolved with a Gaussian with a standard deviation of 0.02 dex for display purposes.
-    \textit{Top middle:} A similar plot comparing exponential DTDs with varying timescales. The solid, dashed, and dotted curves represent timescales $\tau=6$, 3, and 1.5 Gyr, respectively.
-    \textit{Top right:} Similar, comparing plateau DTDs with varying plateau widths.
+    \textit{Middle:} A similar plot comparing exponential DTDs with varying timescales. The solid, dashed, and dotted curves represent timescales $\tau=6$, 3, and 1.5 Gyr, respectively.
+    \textit{Right:} Similar, comparing plateau DTDs with varying plateau widths.
 The solid, dashed, and dotted curves represent widths $W=1$, 0.3, and 0.1 Gyr, respectively.
 All plateau DTD models assume a post-plateau power-law slope of $\alpha=-1.1$.
-For reference, the dotted purple curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted blue curve represents a power-law DTD $\alpha=-1.1$ and no plateau.
-    \textit{Bottom left:} A similar plot comparing minimum SN Ia delay times of 40 Myr (solid) and 150 Myr (dashed) for two DTDs: a power-law with $\alpha=-1.1$ (blue), and an exponential with $\tau=1.5$ Gyr (purple).
-    \textit{Bottom right:} A similar plot comparing all five functional forms for the DTD in this paper: triple-system (green), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
+For reference, the dotted purple curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted blue curve represents a power-law DTD $\alpha=-1.1$ and no plateau.}
+    \label{fig:onezone-threepanel}
+    \script{onezone_threepanel.py}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.49\linewidth]{figures/onezone_minimum_delay.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/onezone_dtd.pdf}
+    \caption{\textit{Left:} A similar plot comparing minimum SN Ia delay times of 40 Myr (solid) and 150 Myr (dashed) for two DTDs: a power-law with $\alpha=-1.1$ (blue), and an exponential with $\tau=1.5$ Gyr (purple).
+    \textit{Right:} A similar plot comparing all five functional forms for the DTD in this paper: triple-system (green), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
 In all cases a minimum SN Ia delay time of 40 Myr is assumed.}
-    \label{fig:onezone-multipanel}
-    \script{onezone_multipanel.py}
+    \label{fig:onezone-twopanel}
+    \script{onezone_twopanel.py}
 \end{figure*}
@@
     \centering
+    \includegraphics{figures/ofe_df_sfh.pdf}
+    \caption{Distributions of [O/Fe] for multi-zone simulations with different SFHs.
+The plot format is similar to Figure \ref{fig:feh-df-sfh}.
+In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.}
+    \label{fig:ofe-df-sfh}
+    \script{ofe_df_sfh.py}
+\end{figure*}
+
+\begin{figure*}
+    \centering
     \includegraphics{figures/ofe_df_dtd.pdf}
@@
     \script{ofe_df_dtd.py}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \includegraphics{figures/ofe_df_sfh.pdf}
-    \caption{Distributions of [O/Fe] for multi-zone simulations with different SFHs.
-The plot format is similar to Figure \ref{fig:feh-df-sfh}.
-In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.}
-    \label{fig:ofe-df-sfh}
-    \script{ofe_df_sfh.py}
 \end{figure*}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics{figures/age_ofe_sfh.pdf}
+    \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different SFH models.
+All assume an inside-out SFH.
+Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
+Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar annulus ($7\leq R_{\rm gal}<9$ kpc) color-coded by the Galactocentric radius at birth.
+A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citet{Leung2023-Ages}.
+Black squares represent the mass-weighted median age of star particles within bins of [O/Fe] with a width of 0.05 dex, and the horizontal black error bars encompass the 16th and 84th percentiles.
+Red triangles represent the median age from \citet{Leung2023-Ages} in bins of [O/Fe], and the horizontal red error bars encompass the 16th and 84th percentiles.
+For clarity, bins which contain less than 1\% of the total mass (in the simulations) or total number of stars (in the data) are not plotted.
+Similar to Figure \ref{fig:age-ofe-dtd} but for simulations with different SFH models.
+All assume an exponential DTD with $\tau=1.5$ Gyr.
+In all panels, stars are limited to the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc)}
+    \label{fig:age-ofe-sfh}
+    \script{age_ofe_sfh.py}
+\end{figure}
+
 \begin{figure*}
@@
 \end{figure*}
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/age_ofe_sfh.pdf}
-    \caption{Similar to Figure \ref{fig:age-ofe-dtd} but for simulations with different SFH models.
-All assume an exponential DTD with $\tau=1.5$ Gyr.
-In all panels, stars are limited to the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc)}
-    \label{fig:age-ofe-sfh}
-    \script{age_ofe_sfh.py}
-\end{figure}
 
@@
 \textit{Right:} Abundance tracks and distributions from one-zone models with the analytical DTDs from \citet{Greggio2005-AnalyticalRates}.
-\textit{Left:} a comparison between the analytical SD DTD (solid magenta curve), an exponential DTD with a 1.5 Gyr timescale (dashed pink curve), and a power-law DTD with a slope of -1.1 (dotted black curve).
-\textit{Right:} a comparison between WIDE and CLOSE prescriptions for an analytical DD DTD (solid blue and green curves, respectively), power-law DTDs with an initial plateau of 1 Gyr and 300 Myr (dashed cyan and yellow curves, respectively), and a power-law DTD with no plateau and a slope of -1.1 (dotted black curve).}
+For clarity}
     \label{fig:analytical-dtd}

### 2023-07-27 src/scripts/score_multizone_outputs.py
split summary table to 2 scripts

@@ -1,0 +1,242 @@
+"""
+This script compares the results of multi-zone simulations to APOGEE data.
+Various statistical tests are used to assign a score for each diagnostic plot:
+[Fe/H] distribution functions, [O/Fe] distribution functions, the [Fe/H] -
+[O/Fe] plane, the age - [O/Fe] plane, and bimodality of the [O/Fe] distribution.
+"""
+
+from tqdm import tqdm
+import numpy as np
+import pandas as pd
+from scipy.signal import find_peaks
+from apogee_tools import import_apogee, apogee_region, apogee_mdf
+from multizone_stars import MultizoneStars
+from utils import kl_divergence, kl_div_2D, group_by_bins, weighted_quantile
+import paths
+from _globals import ABSZ_BINS, GALR_BINS
+
+MIGRATION = 'gaussian'
+SFH_LIST = ['insideout', 'lateburst', 'earlyburst', 'twoinfall']
+DTD_LIST = ['powerlaw_slope11', 
+            'powerlaw_slope14', 
+            'exponential_timescale15',
+            'exponential_timescale30',
+            'plateau_width03',
+            'plateau_width10',
+            'prompt',
+            'triple']
+AGE_SOURCE = 'L23' # Use Leung et al (2023) "latent-space" ages
+
+def main():    
+    apogee_data = import_apogee()
+    
+    summary_table = pd.DataFrame([], 
+        index=pd.MultiIndex.from_product([DTD_LIST, SFH_LIST], 
+                                         names=['DTD', 'SFH']),
+        # temporary column names
+        columns=['feh_df', 'ofe_df', 'ofe_feh', 'age_ofe', 'bimodality'],
+    )
+    
+    age_col = {'L23': 'LATENT_AGE', 'M19': 'ASTRONN_AGE'}[AGE_SOURCE]
+    
+    with tqdm(total=len(SFH_LIST) * len(DTD_LIST)) as t:
+        for dtd in DTD_LIST:
+            for sfh in SFH_LIST:
+                output_name = '/'.join([MIGRATION, sfh, dtd, 'diskmodel'])
+                mzs = MultizoneStars.from_output(output_name)
+                mzs.model_uncertainty(apogee_data, inplace=True)
+                # Set up lists to track scores by region
+                scores = {col: [] for col in summary_table.columns[:-1]}
+                weights = []
+                for i in range(len(ABSZ_BINS) - 1):
[…]

### 2023-07-27 src/scripts/summary_table.py

@@ -3,253 +3,18 @@ This script generates a LaTeX table which summarizes the results of the
 multizone simulations across multiple parameter spaces.
 """
 
-from tqdm import tqdm
-import numpy as np
 import pandas as pd
-from scipy.signal import find_peaks
-from apogee_tools import import_apogee, apogee_region, apogee_mdf
-from multizone_stars import MultizoneStars
-from utils import kl_divergence, kl_div_2D, group_by_bins, weighted_quantile
 import paths
-from _globals import ABSZ_BINS, GALR_BINS
+from score_multizone_outputs import main as gen_scores
+from score_multizone_outputs import DTD_LIST
 
-MIGRATION = 'gaussian'
-SFH_LIST = ['insideout', 'lateburst', 'earlyburst', 'twoinfall']
-DTD_LIST = ['powerlaw_slope11', 
-            'powerlaw_slope14', 
-            'exponential_timescale15',
-            'exponential_timescale30',
-            'plateau_width03',
-            'plateau_width10',
-            'prompt',
-            'triple']
-AGE_SOURCE = 'L23' # Use Leung et al (2023) "latent-space" ages
-
-def main(overwrite=False):
-    csv_file = paths.output / 'summary_table.csv'
-    if csv_file.exists() and not overwrite:
-        summary_table = pd.read_csv(csv_file, index_col=[0, 1])
-    else:
-        summary_table = gen_summary_table()
-        summary_table.to_csv(csv_file)
+def main():
+    # Import numerical scores of multi-zone outputs, or generate if missing
+    csv_file = paths.data / 'multizone' / 'scores.csv'
+    if not csv_file.exists():
+        gen_scores()
+    df = pd.read_csv(csv_file, index_col=[0, 1])
     # Convert to LaTeX format and write to output file
-    latex_table = to_latex(summary_table)
-    with open(paths.output / 'summary_table.tex', 'w') as f:
-        f.write(latex_table)
-
-
-def gen_summary_table():
-    apogee_data = import_apogee()
-    
-    summary_table = pd.DataFrame([], 
-        index=pd.MultiIndex.from_product([DTD_LIST, SFH_LIST], 
-                                         names=['DTD', 'SFH']),
-        # temporary column names
-        columns=['feh_df', 'ofe_df', 'ofe_feh', 'age_ofe', 'bimodality'],
-    )
-    
[…]

### 2023-07-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 We explore five different functional forms for the SN Ia DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, a two-population model, and a model based on triple-system dynamics, with a one or two different parameterizations for each.
-Figure \ref{fig:dtds} presents these DTDs as a function of time since star formation.
+Figure \ref{fig:dtds} presents these DTDs as a function of time after star formation.
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.32\linewidth]{figures/onezone_powerlaw_slope.pdf}
-    \includegraphics[width=0.32\linewidth]{figures/onezone_exponential_timescale.pdf}
-    \includegraphics[width=0.32\linewidth]{figures/onezone_plateau_width.pdf}
-    \caption{\textit{Left:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone models with a power-law DTD.
-The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively.
-The open symbols located along each curve mark logarithmic steps in simulation time.
-In all cases a minimum SN Ia delay time of 40 Myr is assumed.
-The marginal panels above and to the right present the distributions of [Fe/H] and [O/Fe], respectively, convolved with a Gaussian with a standard deviation of 0.02 dex for display purposes.
-    \textit{Middle:} A similar plot comparing exponential DTDs with varying timescales. The solid, dashed, and dotted curves represent timescales $\tau=6$, 3, and 1.5 Gyr, respectively.
-    \textit{Right:} Similar, comparing plateau DTDs with varying plateau widths.
-The solid, dashed, and dotted curves represent widths $W=1$, 0.3, and 0.1 Gyr, respectively.
-All plateau DTD models assume a post-plateau power-law slope of $\alpha=-1.1$.
-For reference, the dotted purple curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted blue curve represents a power-law DTD $\alpha=-1.1$ and no plateau.}
-    \label{fig:onezone-threepanel}
-    \script{onezone_threepanel.py}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.49\linewidth]{figures/onezone_minimum_delay.pdf}
-    \includegraphics[width=0.49\linewidth]{figures/onezone_dtd.pdf}
-    \caption{\textit{Left:} A similar plot comparing minimum SN Ia delay times of 40 Myr (solid) and 150 Myr (dashed) for two DTDs: a power-law with $\alpha=-1.1$ (blue), and an exponential with $\tau=1.5$ Gyr (purple).
-    \textit{Right:} A similar plot comparing all five functional forms for the DTD in this paper: triple-system (green), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
-In all cases a minimum SN Ia delay time of 40 Myr is assumed.}
-    \label{fig:onezone-twopanel}
-    \script{onezone_twopanel.py}
-\end{figure*}
-
-% Adjusting the parameters of the DTD affects how steeply the abundance track in [Fe/H]-[O/Fe] space falls from its initial ``plateau'' and the location of the ``knee.'' Figure \ref{fig:onezone-slope-timescale} shows abundance tracks from one-zone models which assume different slopes of a power-law DTD or different timescales of an exponential DTD.
-A steeper power-law slope results in a steeper decline in [O/Fe] and a lower knee, as does a shorter exponential timescale.
-The consequence is that a very shallow power-law produces a similar abundance track to a very steep exponential, which suggests these models may be difficult to distinguish in this parameter space.
-However, these cases can be distinguished by their MDFs and [O/Fe] distributions, where the power-law DTD produces a narrower, less skewed distribution while the exponential DTD produces a broader, more skewed distribution.
-In the [O/Fe] distribution especially, an exponential DTD with a 6 Gyr timescale produces a large number of high-$\alpha$ stars.
-
-Figure \ref{fig:onezone-powerlaw-slope} compares the results of three one-zone models which are identical except for the slope of the power-law DTD.
+The left-hand panel of Figure \ref{fig:onezone-threepanel} compares the results of three one-zone models which are identical except for the slope of the power-law DTD.
 A steeper slope produces a sharper ``knee'' and a faster decline in [O/Fe], resulting in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics{figures/onezone_powerlaw_slope.pdf}
-%     \caption{\textit{Center:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone models with a power-law DTD.
-The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively.
-The open symbols located along each curve mark logarithmic steps in simulation time.
-In all cases a minimum SN Ia delay time of 40 Myr is assumed.
-\textit{Top:} Metalliticy distribution functions (MDFs) generated by the one-zone models.
-\textit{Right:} Distributions of [O/Fe] generated by the one-zone models.}
-%     \label{fig:onezone-powerlaw-slope}
-%     \script{onezone_powerlaw_slope.py}
-% \end{figure}
-
-Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in Figure \ref{fig:onezone-exponential-timescale}.
+Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in the middle panel of Figure \ref{fig:onezone-threepanel}.
 Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around 1 Gyr.
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics{figures/onezone_exponential_timescale.pdf}
-%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with an exponential DTD.
-The dotted, dashed, and solid curves represent exponential decay timescales $\tau=1.5$ Gyr, 3 Gyr, and 6 Gyr, respectively.}
-%     \label{fig:onezone-exponential-timescale}
-%     \script{onezone_exponential_timescale.py}
-% \end{figure}
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.32\linewidth]{figures/onezone_powerlaw_slope.pdf}
+    \includegraphics[width=0.32\linewidth]{figures/onezone_exponential_timescale.pdf}
+    \includegraphics[width=0.32\linewidth]{figures/onezone_plateau_width.pdf}
+    \caption{\textit{Left:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone chemical evolution models models which assume a power-law DTD.
+The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively.
+In all cases a minimum SN Ia delay time of 40 Myr is assumed.
+The open symbols located along each curve mark logarithmic steps in simulation time.
+The marginal panels above and to the right of the central panel present the distributions of [Fe/H] and [O/Fe], respectively.
+For display purposes these distributions are convolved with a Gaussian with a standard deviation of 0.02 dex.
+    \textit{Middle:} A similar plot comparing exponential DTDs with varying timescales. The solid, dashed, and dotted curves represent timescales $\tau=6$, 3, and 1.5 Gyr, respectively.
+    \textit{Right:} Similar, comparing plateau DTDs with varying plateau widths.
+The solid, dashed, and dotted green curves represent widths $W=1$, 0.3, and 0.1 Gyr, respectively.
+All plateau DTD models assume a post-plateau power-law slope of $\alpha=-1.1$.
+For reference, the dotted blue curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted purple curve represents a power-law DTD $\alpha=-1.1$ and no plateau.}
+    \label{fig:onezone-threepanel}
+    \script{onezone_threepanel.py}
+\end{figure*}
 
-% \begin{figure}
-%     \centering
-%     \includegraphics{figures/onezone_plateau_width.pdf}
-%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with a plateau DTD.
-The solid, dashed, and dot-dashed pink curves represent plateau widths $W=1.0$, 0.3, and 0.1 Gyr, respectively.
-All plateau DTDs assume a power-law slope of $\alpha=-1.1$.
-For comparison, the blue dotted curve represents an exponential DTD with a timescale $\tau=3$ Gyr, and the black dotted curve represents a power-law DTD with the same slope but no plateau.}
-%     \label{fig:onezone-plateau-width}
-%     \script{onezone_plateau_width.py}
-% \end{figure}
+The left-hand panel of Figure \ref{fig:onezone-twopanel} shows that the minimum SN Ia delay time has a much stronger effect on the abundance track and MDFs of models which assume a power-law DTD than models which assume a plateau or exponential DTD, due to the much higher SN Ia rate in the power-law models at early times (see Figure \ref{fig:dtds}).
+Moreover, a power-law DTD with a long minimum delay may be observationally hard to distinguish from a plateau model.
+In Figure \ref{fig:onezone-twopanel}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (red dashed line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (blue solid line), and the [O/Fe] distributions are virtually identical.
 
-% \begin{figure}
-%     \centering
-%     \includegraphics{figures/onezone_twopopulation.pdf}
-%     \caption{One-zone model abundance tracks and distributions for variants of the two-population DTD.}
-%     \label{fig:onezone-prompt}
-%     \script{onezone_twopopulation.py}
-% \end{figure}
+A 150 Myr minimum delay time is incompatible with the two-population DTD model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD as its relative SN Ia rate is so low at early times.
 
-Figure \ref{fig:onezone-dtd} compares the one-zone model outputs from the full range of DTDs we investigate in this paper.
+The right-hand panel of Figure \ref{fig:onezone-twopanel} compares the one-zone model outputs from the full range of DTDs we investigate in this paper.
 In general, the choice of DTD has the greatest effect on the location of the knee in [Fe/H]-[O/Fe] space (center panel) and the high-$\alpha$ end of the distribution of [O/Fe] (right panel).
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics{figures/onezone_dtd.pdf}
-%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with a different selection of DTDs. In all cases a minimum delay time of 40 Myr is assumed.}
-%     \label{fig:onezone-dtd}
-%     \script{onezone_dtd.py}
-% \end{figure}
-
-\subsection{The Minimum SN Ia Delay Time}
-
-Figure \ref{fig:onezone-minimum-delay} shows that the minimum SN Ia delay time has a much stronger effect on the abundance track and MDFs of models which assume a power-law DTD than models which assume a plateau or exponential DTD, due to the much higher SN Ia rate in the power-law models at early times (see Figure \ref{fig:dtds}).
-Moreover, a power-law DTD with a long minimum delay may be observationally hard to distinguish from a plateau model.
-In Figure \ref{fig:onezone-minimum-delay}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (red dashed line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (blue solid line), and the [O/Fe] distributions are virtually identical.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics{figures/onezone_minimum_delay.pdf}
-%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying DTD models and minimum SN Ia delay time ($t_D$).
-Solid curves represent models with a minimum delay time of 40 Myr, while dashed curves represent models with a minimum delay time of 150 Myr.
-The red curves represent a power-law DTD with slope $\alpha=-1.1$; blue curves represent an plateau DTD with width $W=0.3$ Gyr and slope $\alpha=-1.1$; and orange curves represent an exponential DTD with timescale $\tau=3$ Gyr.
-In all cases an exponential rise-fall SFR is assumed.}
-%     \label{fig:onezone-minimum-delay}
-%     \script{onezone_minimum_delay.py}
-% \end{figure}
-
-A 150 Myr minimum delay time is incompatible with the two-population DTD model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD as its relative SN Ia rate is so low at early times.
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.49\linewidth]{figures/onezone_minimum_delay.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/onezone_dtd.pdf}
+    \caption{\textit{Left:} Comparison of one-zone models with minimum SN Ia delay times of 40 Myr (solid) and 150 Myr (dashed curves) for two DTDs: a power-law with $\alpha=-1.1$ (blue), and an exponential with $\tau=1.5$ Gyr (purple curves).
+The layout is similar to the plots in Figure \ref{fig:onezone-threepanel}.
+    \textit{Right:} Comparison of one-zone models which assume all five functional forms for the DTD in this paper: triple-system (green), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
+In all cases a minimum SN Ia delay time of 40 Myr is assumed.}
+    \label{fig:onezone-twopanel}
+    \script{onezone_twopanel.py}
+\end{figure*}
 
@@
 %     \script{onezone_delay_taustar.py}
-% \end{figure}
-
-% \begin{figure}
-%     \centering
-%     \includegraphics{figures/onezone_sfh.pdf}
-%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying star formation history (SFH). An exponential DTD with $\tau=1.5$ Gyr is assumed in all models.}
-%     \label{fig:onezone-sfh}
-%     \script{onezone_sfh.py}
 % \end{figure}
@@
     \includegraphics{figures/feh_df_dtd.pdf}
-    \caption{Distributions of [Fe/H] for multi-zone simulations with different DTDs: a power-law with slope $\alpha=-1.4$ (\textit{left}), and an exponential with timescale $\tau=3$ Gyr (\textit{right}).
-In both cases an inside-out SFH is assumed.
-The plot format is similar to Figure \ref{fig:feh-df-sfh}.}
+    \caption{Distributions of [Fe/H] from multi-zone simulations with different DTDs: a power-law with slope $\alpha=-1.4$ (\textit{left}), and an exponential with timescale $\tau=3$ Gyr (\textit{right}).
+Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}).
+Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue).
+Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row.
+All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex.
+In both cases an inside-out SFH is assumed.}
     \label{fig:feh-df-dtd}
@@
     \includegraphics{figures/feh_df_sfh.pdf}
-    \caption{Distributions of [Fe/H] for multi-zone simulations with different SFHs.
-Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}).
-Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue).
-Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row.
-All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex.
+    \caption{Distributions of [Fe/H] from multi-zone simulations with different SFHs.
+The plot format is similar to Figure \ref{fig:feh-df-dtd}.
 In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.
@@
     \includegraphics{figures/ofe_df_sfh.pdf}
-    \caption{Distributions of [O/Fe] for multi-zone simulations with different SFHs.
-The plot format is similar to Figure \ref{fig:feh-df-sfh}.
-In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.}
+    \caption{Distributions of [O/Fe] from multi-zone simulations with different SFHs.
+The format of each panel is similar to Figure \ref{fig:feh-df-dtd}.
+In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.
+Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
     \label{fig:ofe-df-sfh}
@@
     \includegraphics{figures/ofe_df_dtd.pdf}
-    \caption{Distributions of [O/Fe] for multi-zone simulations with different DTDs.
+    \caption{Distributions of [O/Fe] from multi-zone simulations with different DTDs.
 In all cases an inside-out SFH is assumed.

### 2023-07-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \includegraphics{figures/delay_time_distributions.pdf}
-    \caption{Models of the SN Ia delay time distribution used in this paper. All functions are normalized to $f_{\rm Ia}=1$ at $\tau=1$ Gyr.}
+    \caption{Models of the SN Ia delay time distribution used in this paper.
+All functions are normalized to $f_{\rm Ia}=1$ at $\tau=1$ Gyr.
+The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD}.
+The horizontal error bars indicate the time range of each DTD measurement, and the vertical error bars represent the 1$\sigma$ uncertainties.}
     \label{fig:dtds}
@@
 \end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/feh_df_comparison.pdf}
+    \caption{Distributions of [Fe/H] from multi-zone simulations with different SFHs.
+The plot format is similar to Figure \ref{fig:feh-df-dtd}.
+In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.
+Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
+    \label{fig:feh-df-comparison}
+    \script{feh_df_comparison.py}
+\end{figure*}
+
 \subsection{The distribution of [O/Fe]}

### 2023-07-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/feh_df_dtd.pdf}
-    \caption{Distributions of [Fe/H] from multi-zone simulations with different DTDs: a power-law with slope $\alpha=-1.4$ (\textit{left}), and an exponential with timescale $\tau=3$ Gyr (\textit{right}).
+% \begin{figure}
+%     \centering
+%     \includegraphics{figures/feh_df_dtd.pdf}
+%     \caption{Distributions of [Fe/H] from multi-zone simulations with different DTDs: a power-law with slope $\alpha=-1.4$ (\textit{left}), and an exponential with timescale $\tau=3$ Gyr (\textit{right}).
 Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}).
@@
 In both cases an inside-out SFH is assumed.}
-    \label{fig:feh-df-dtd}
-    \script{feh_df_dtd.py}
-\end{figure}
+%     \label{fig:feh-df-dtd}
+%     \script{feh_df_dtd.py}
+% \end{figure}
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics{figures/feh_df_sfh.pdf}
-    \caption{Distributions of [Fe/H] from multi-zone simulations with different SFHs.
+% \begin{figure*}
+%     \centering
+%     \includegraphics{figures/feh_df_sfh.pdf}
+%     \caption{Distributions of [Fe/H] from multi-zone simulations with different SFHs.
 The plot format is similar to Figure \ref{fig:feh-df-dtd}.
@@
 Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
-    \label{fig:feh-df-sfh}
-    \script{feh_df_sfh.py}
-\end{figure*}
+%     \label{fig:feh-df-sfh}
+%     \script{feh_df_sfh.py}
+% \end{figure*}
 
@@
     \includegraphics{figures/feh_df_comparison.pdf}
-    \caption{Distributions of [Fe/H] from multi-zone simulations with different SFHs.
-The plot format is similar to Figure \ref{fig:feh-df-dtd}.
-In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.
-Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
+    \caption{Distributions of [Fe/H] from multi-zone simulations with various models for the SFH and DTD.
+Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}).
+Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue).
+Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row.
+All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex.
+    \textit{Left columns:} comparison between the inside-out and two-infall SFH models. In both cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed. 
+    \textit{Center column:} the distributions from APOGEE DR17 for reference, binned and smoothed similarly.
+    \textit{Right columns:} comparison between the power-law ($\alpha=-1.4$) and exponential ($\tau=3$ Gyr) DTD models. In both cases the inside-out SFH is assumed.}
     \label{fig:feh-df-comparison}
@@
     \caption{Distributions of [O/Fe] from multi-zone simulations with different SFHs.
-The format of each panel is similar to Figure \ref{fig:feh-df-dtd}.
 In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.
+The format of each panel is the same as in Figure \ref{fig:feh-df-comparison}, except that all distributions are smoothed with a box-car width of 0.05 dex.
 Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
@@
     \includegraphics{figures/ofe_df_dtd.pdf}
-    \caption{Distributions of [O/Fe] from multi-zone simulations with different DTDs.
-In all cases an inside-out SFH is assumed.
-The plot format is similar to Figure \ref{fig:feh-df-sfh}.
-All distributions are smoothed with a box-car width of 0.05 dex.}
+    \caption{Distributions of [O/Fe] from multi-zone simulations with different DTDs. In all cases an inside-out SFH is assumed. The plot format is similar to Figure \ref{fig:ofe-df-sfh}.}
     \label{fig:ofe-df-dtd}
@@
 Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
-A Gaussian scatter has been applied to all points based on the median abundance errors in APOGEE DR17.
+A Gaussian scatter has been applied to all points based on the median abundance errors in APOGEE DR17 (ses Table \ref{tab:uncertainties}).
 The black curves represent the ISM abundance tracks in the 8 kpc zone.
-The red contours represent the APOGEE abundance distribution, with the solid and dashed contours enclosing 68\% and 95\% of stars, respectively.}
+The red contours represent the APOGEE abundance distribution, with the solid and dashed contours enclosing 68\% and 95\% of stars in the sample, respectively.}
     \label{fig:ofe-feh-sfh}
@@
     \includegraphics{figures/ofe_feh_dtd.pdf}
-    \caption{Similar to Figure \ref{fig:ofe-feh-sfh} but comparing multi-zone simulations with different DTD models.
-All assume an inside-out SFH.
-Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
+    \caption{The [O/Fe]--[Fe/H] plane from multi-zone simulations with different DTD models.
+All assume the inside-out SFH.
+Each panel is similar to those in Figure \ref{fig:ofe-feh-sfh}, except each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
 All panels present stars within the Solar annulus ($7\leq R_{\rm gal}<9$ kpc).}
@@
     \includegraphics{figures/onezone_analytical_dtd.pdf}
-    \caption{\textit{Left:} Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and close approximation simple functions (dashed curves).
+    \caption{\textit{Left:} Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and simple DTD functions (dashed curves).
 Some functions are presented with a constant multiplicative factor for visual clarity.
-\textit{Right:} Abundance tracks and distributions from one-zone models with the analytical DTDs from \citet{Greggio2005-AnalyticalRates}.
-For clarity}
+\textit{Right:} Abundance tracks and distributions from one-zone models with the analytical and simple DTDs (same color scheme).
+For clarity, we vary the mass-loading factor to be $\eta=4$, $\eta=2$, and $\eta=1$ for the red, green, and blue curves, respectively.}
     \label{fig:analytical-dtd}

### 2023-07-27 src/scripts/onezone_plateau_width.py
add gray reference curve

@@ -32,9 +32,8 @@ def main(overwrite=False):
 
     fig, axs = setup_axes(width=0.4*TWO_COLUMN_WIDTH, title='Plateau DTD')
 
-    # Plot exponentials for referenc
-    tau = 3
-    dtd = dtds.exponential(timescale=tau, tmin=delay)
+    # Plot exponentials for reference
+    dtd = dtds.exponential(timescale=3, tmin=delay)
     sz = vice.singlezone(name=str(output_dir / dtd.name),
                          RIa=dtd,
                          func=models.insideout(8, dt=dt), 
@@ -43,18 +42,14 @@ def main(overwrite=False):
     sz.run(simtime, overwrite=True)
     plot_vice_onezone(str(output_dir / dtd.name), 
                       fig=fig, axs=axs,
-                      linestyle=':', 
-                      color=styles.exp['color'], 
-                      label=rf'Exponential ($\tau=3$ Gyr)', 
+                      linestyle='-', 
+                      linewidth=2,
+                      color='#bbbbbb', 
+                      label=r'Exponential ($\tau=3$ Gyr)', 
                       marker_labels=True, 
-                      linewidth=1.5)
+                      zorder=1)
 
     for i, width in enumerate(PLATEAU_WIDTHS):
-        if width >= 1:
-            label = f'{width:.01f} Gyr plateau'
-        else:
-            label = f'{int(width*1000)} Myr plateau'
-
         dtd = dtds.plateau(width=width, slope=SLOPE, tmin=delay)
         sz = vice.singlezone(name=str(output_dir / dtd.name),
                              RIa=dtd,

### 2023-07-27 src/scripts/onezone_powerlaw_slope.py

@@ -28,6 +28,23 @@ def main():
 
     dt = ONEZONE_DEFAULTS['dt']
     simtime = np.arange(0, END_TIME + dt, dt)
+    
+    # Exponential DTD for reference
+    dtd = dtds.exponential(timescale=3, tmin=ONEZONE_DEFAULTS['delay'])
+    sz = vice.singlezone(name=str(output_dir / dtd.name),
+                         RIa=dtd,
+                         func=models.insideout(8, dt=dt), 
+                         mode='sfr',
+                         **ONEZONE_DEFAULTS)
+    sz.run(simtime, overwrite=True)
+    plot_vice_onezone(str(output_dir / dtd.name), 
+                      fig=fig, axs=axs, 
+                      linestyle='-', 
+                      linewidth=2,
+                      color='#bbbbbb', 
+                      label=r'Exponential ($\tau=3$ Gyr)', 
+                      marker_labels=True,
+                      zorder=1)
 
     for i, slope in enumerate(SLOPES):
         dtd = dtds.powerlaw(slope=slope, tmin=ONEZONE_DEFAULTS['delay'])
@@ -43,7 +60,7 @@ def main():
                           linestyle=LINE_STYLES[i], 
                           color=styles.plaw['color'], 
                           label=rf'$\alpha={slope:.1f}$', 
-                          marker_labels=(i==0))
+                          marker_labels=False)
 
     # Adjust axis limits
     axs[1].set_ylim(bottom=0)

### 2023-07-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different SFH models.
-All assume an inside-out SFH.
-Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
-Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar annulus ($7\leq R_{\rm gal}<9$ kpc) color-coded by the Galactocentric radius at birth.
-A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citet{Leung2023-Ages}.
+All assume an exponential DTD with $\tau=1.5$ Gyr.
+Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
+A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citet{Leung2023-Ages} (see Table \ref{tab:uncertainties}).
 Black squares represent the mass-weighted median age of star particles within bins of [O/Fe] with a width of 0.05 dex, and the horizontal black error bars encompass the 16th and 84th percentiles.
 Red triangles represent the median age from \citet{Leung2023-Ages} in bins of [O/Fe], and the horizontal red error bars encompass the 16th and 84th percentiles.
-For clarity, bins which contain less than 1\% of the total mass (in the simulations) or total number of stars (in the data) are not plotted.
-Similar to Figure \ref{fig:age-ofe-dtd} but for simulations with different SFH models.
-All assume an exponential DTD with $\tau=1.5$ Gyr.
-In all panels, stars are limited to the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc)}
+For clarity, bins which contain less than 1\% of the total mass (in the simulations) or total number of stars (in the data) are not plotted.}
     \label{fig:age-ofe-sfh}
@@
 Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
-Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar annulus ($7\leq R_{\rm gal}<9$ kpc) color-coded by the Galactocentric radius at birth.
-A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citet{Leung2023-Ages}.
-Black squares represent the mass-weighted median age of star particles within bins of [O/Fe] with a width of 0.05 dex, and the horizontal black error bars encompass the 16th and 84th percentiles.
-Red triangles represent the median age from \citet{Leung2023-Ages} in bins of [O/Fe], and the horizontal red error bars encompass the 16th and 84th percentiles.
-For clarity, bins which contain less than 1\% of the total mass (in the simulations) or total number of stars (in the data) are not plotted.}
+In all panels stars are limited to the Solar annulus ($7\leq R_{\rm gal}<9$ kpc), and the layout of each panel is as in Figure \ref{fig:age-ofe-sfh}.}
     \label{fig:age-ofe-dtd}
@@
 \textit{Right:} Abundance tracks and distributions from one-zone models with the analytical and simple DTDs (same color scheme).
-For clarity, we vary the mass-loading factor to be $\eta=4$, $\eta=2$, and $\eta=1$ for the red, green, and blue curves, respectively.}
+For clarity, we vary the mass-loading factor to be $\eta=4$, $\eta=2$, and $\eta=1$ for the red, green, and blue curves, respectively.
+All simulation parameters between the similarly-colored solid and dashed curves are identical.}
     \label{fig:analytical-dtd}

### 2023-08-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{xcolor}
+\usepackage{upgreek}
 % \usepackage{siunitx}
@@
         EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
+        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citet{Leung2023-Ages}
     \enddata
@@
     \tablehead{
-        \colhead{Parameter} & \colhead{Value} & \colhead{Description}
+        \colhead{Quantity} & \colhead{Value} & \colhead{Description}
     }
@@
 \end{deluxetable}
-
-\subsection{The SN Ia Delay-Time Distribution}
-\label{sec:onezone-dtd}
 
@@
 
+\begin{deluxetable*}{Ccl}
+    \tablecaption{A summary of parameters and their fiducial values for our multi-zone chemical evolution models.
+We omit parameters which have been left unchanged from \citet{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
+    \tablehead{
+        \colhead{Quantity} & \colhead{Value} & \colhead{Description}
+    }
+    \startdata
+        t_D                 & 40 Myr                                & Minimum SN Ia delay time \\
+        \Delta R_{\rm gal}  & Equation \ref{eq:radial-migration}    & Change in radius due to stellar migration (see Appendix \ref{app:migration}) \\
+        z                   & Equation \ref{eq:sech-pdf}            & Distance from Galactic midplane at present day (see Appendix \ref{app:migration}) \\
+        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & Time-dependence of the infall rate in the early-burst model \\
+        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & Time-dependence of the infall rate in the two-infall model \\
+        \uptau_{*,\rm EB}(t|R_{\rm gal})  & Equation \ref{eq:earlyburst-conroy22} & Time-dependence of the SFE timescale in the early-burst model \\
+    \enddata
+\end{deluxetable*}
+
 \begin{deluxetable}{lll}
@@
         $\rm [O/Fe]$ & $1.8\times10^{-2}$ & APOGEE DR17 \\
-        log(Age/Gyr) & $0.12$ & \citet{Leung2023-Ages}
+        log(Age/Gyr) & $0.10$ & \citet{Leung2023-Ages}
         % Age/Gyr & 29\% & astroNN
@@
 \subsection{The distribution of [Fe/H]}
-
-To quantify the similarity between the MDFs generated by VICE and the observed APOGEE MDF, we compute the Kullback-Leibler (KL) divergence \citep{KullbackLeibler1951}, defined as
-\begin{equation}
-\label{eq:kl-divergence}
-D_{\rm{KL}}(P \parallel Q) = \int_{-\infty}^{\infty} p(x) \log\Big(\frac{p(x)}{q(x)}\Big) dx
-\end{equation}
-for distributions $P$ and $Q$ with probability density functions $p(x)$ and $q(x)$.
-In this case, $P$ is the APOGEE MDF, $Q$ is the model MDF, and $x$ is [Fe/H].
-For each model SFH and DTD, we compute $D_{\rm{KL}}$ in 18 different galactocentric zones defined by radial bins $3-5$ kpc, $5-7$ kpc, $7-9$ kpc, $9-11$ kpc, $11-13$ kpc, and $13-15$ kpc and absolute $z$-height bins $0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
-The KL divergence for the entire model is taken to be the average of $D_{\rm{KL}}$ for each zone, weighted by the number of APOGEE stars in each zone.
 
@@
 
-Picking the team.
+We've run a lot of models and need some semi-quantitative way to say that some models do better than others.
+We compare our multi-zone outputs to APOGEE across five diagnostics: the [Fe/H] DF, [O/Fe] DF, [Fe/H]--[O/Fe] plane, age--[O/Fe] plane, and bimodality in the [O/Fe] DF.
+We perform statistical tests between APOGEE and simulation outputs in each region of the galaxy, then average the scores together (weighted by the number of APOGEE targets in each galactic region) to obtain a single numerical score for each simulation.
+Note that we are not trying to use these scores to fit our models to the data, nor are we trying to rule out any SFH in general.
+We use these scores to get a handle on which combinations of SFH and DTD are favorable or disfavorable in certain regimes.
 
-% TODO make table with numerical scores (KL divergences, etc) for supplementary material
-% TODO explain that precise statistical understanding of these scores is outside the scope of the paper
+To quantify the difference between the abundance distributions generated by VICE and those observed in APOGEE, we compute the Kullback-Leibler (KL) divergence \citep{KullbackLeibler1951}, defined as
+\begin{equation}
+    D_{\rm{KL}}(P \parallel Q) \equiv \int_{-\infty}^{\infty} p(x) \log\Big(\frac{p(x)}{q(x)}\Big) dx
+    \label{eq:kl-divergence}
+\end{equation}
+for distributions $P$ and $Q$ with probability density functions $p(x)$ and $q(x)$.
+A KL divergence of 0 indicates that the two distributions contain equal amounts of information.
+In this case, $P$ is the APOGEE DF, $Q$ is the model DF, and $x$ is either [Fe/H] or [O/Fe].
+For each model SFH and DTD, we compute $D_{\rm{KL}}$ in 18 different Galactocentric regions: bins in $R_{\rm gal}$ of $3-5$ kpc, $5-7$ kpc, $7-9$ kpc, $9-11$ kpc, $11-13$ kpc, and $13-15$ kpc, and bins in $|z|$ of $0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
+The KL divergence for the entire model is taken to be the average of $D_{\rm{KL}}$ for each region weighted by the number of APOGEE stars in that region.
+
+\citet{PerezCruz2008-KLTest2D} present a method for estimating the KL divergence between two continuous, multivariate samples using a $k$-nearest neighbor estimate.
+We implement this method to calculate the divergence between the multi-zone models and APOGEE data in [Fe/H]---[O/Fe] space.\footnote{We got the implementation from \url{https://mail.python.org/pipermail/scipy-user/2011-May/029521.html}.}
+
+We employ a different test in the age---[O/Fe] plane.
+[motivated by the large age uncertainties?] As shown in Figures \ref{fig:age-ofe-sfh} and \ref{fig:age-ofe-dtd}, in each Galactic region we bin the model outputs and data into bins of [O/Fe] with a width of 0.05 dex.
+We define the RMS median age difference for the region as
+\begin{equation}
+    \Delta\tau_{\rm RMS} \equiv \sqrt{\frac{\sum_k \Delta\tau_k^2 n_{{\rm L23},k}}{n_{\rm L23,tot}}}
+    \label{eq:age-ofe-score}
+\end{equation}
+where $\Delta\tau_k=\rm{med}(\tau_{\rm VICE})-\rm{med}(\tau_{\rm L23})$ is the difference between the mass-weighted median star particle age in VICE and the median stellar age from \citet{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citet{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
+As before, the score for the model as a whole is the average of $\Delta \tau_{\rm RMS}$ across all regions, weighted by the number of stars in the age sample in each region.
+
+The results of these tests are presented in Table \ref{tab:results}.
+Instead of reporting the numerical scores for each simulation output, in the column corresponding to a particular diagnostic we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom third out of all of our simulations, respectively.
+A \yes indicates that particular combination of model SFH and DTD performed better than most when compared to the APOGEE sample for that diagnostic.
 
@@
 The SD and DD CLOSE DTDs follow nearly identical tracks in [O/Fe] vs [Fe/H]; however, their distributions on [O/Fe] differ at the low end.
-The SD DTD follows an exponential with a 1.5 Gyr timescale, whereas the DD CLOSE DTD is well-approximated by a broken power-law with an initial plateau of 350 Myr and a subsequent declining slope of -1.1.
+The SD DTD follows an exponential with a 1.5 Gyr timescale, whereas the DD CLOSE DTD is well-approximated by a broken power-law with an initial plateau of 300 Myr and a subsequent declining slope of -1.1.
 The WIDE prescription is likewise best approximated by a broken power-law, but with a longer plateau width of 1 Gyr.
@@
 
-We fit a sech$^2$ function \citep{Spitzer1942} to the distribution of midplane distances $z_{\rm final}$.
-Vertical migration away from the midplane does not affect the chemical evolution simulation, but we do use $z_{\rm final}$ in our analysis.
-The probability density function (PDF) of $z_{\rm final}$ given some scale height $h_z$ is
+We fit a sech$^2$ function \citep{Spitzer1942} to the distribution of midplane distances $z$.
+Vertical migration away from the midplane does not affect the chemical evolution simulation, but we do use $z$ in our analysis.
+The probability density function (PDF) of $z$ given some scale height $h_z$ is
 \begin{equation}
-    {\rm PDF}(z_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z_{\rm final}}{2 h_z}\Big)
+    {\rm PDF}(z) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z}{2 h_z}\Big)
     \label{eq:sech-pdf}
@@
 \begin{equation}
-    {\rm CDF}(z_{\rm final}) = \frac{1}{1 + e^{-z_{\rm final} / h_z}}.
+    {\rm CDF}(z) = \frac{1}{1 + e^{-z / h_z}}.
     \label{eq:sech-cdf}
 \end{equation}
-We fit the above function to the distributions of $z_{\rm final}$ in h277 in varying bins of $\tau$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
+We fit the above function to the distributions of $z$ in h277 in varying bins of $\tau$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
 \begin{equation}
@@
 Within each panel, colored curves represent the different age bins, ranging from the youngest stars (dark blue) to the oldest (dark red).
+In the top row, we exclude bins with fewer than 100 unique analogue IDs for clarity.
 All distributions are normalized so that the area under the curve is 1, and have been smoothed by a boxcar function of width 0.5 kpc.
@@
 From left to right, star particles are binned by \textit{final} annulus.
+In the top row, we exclude bins with fewer than 500 unique analogue IDs for clarity.
 All distributions have been smoothed by a boxcar function of width 0.1 kpc.}

### 2023-08-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Within each panel, colored curves represent the different age bins, ranging from the youngest stars (dark blue) to the oldest (dark red).
-In the top row, we exclude bins with fewer than 100 unique analogue IDs for clarity.
+In the top row, we exclude age bins with fewer than 100 unique analogue IDs for clarity.
 All distributions are normalized so that the area under the curve is 1, and have been smoothed by a boxcar function of width 0.5 kpc.
@@
 From left to right, star particles are binned by \textit{final} annulus.
-In the top row, we exclude bins with fewer than 500 unique analogue IDs for clarity.
+In the top row, we exclude age bins with fewer than 500 unique analogue IDs for clarity.
 All distributions have been smoothed by a boxcar function of width 0.1 kpc.}

### 2023-08-30 src/scripts/ofe_bimodality_summary.py
add [o/fe] bimodality plot

@@ -1,0 +1,121 @@
+"""
+This script plots a comparison of the [O/Fe] bimodality for several DTDs.
+It takes the [O/Fe] distribution within a narrow slice of [Fe/H]
+for each VICE multi-zone output, and runs a peak-finding algorithm to determine
+whether the output exhibits alpha-element bimodality.
+"""
+from tqdm import tqdm
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MultipleLocator
+from multizone_stars import MultizoneStars
+import paths
+from utils import get_bin_centers
+from apogee_tools import import_apogee, apogee_region, apogee_mdf
+from colormaps import paultol
+from _globals import TWO_COLUMN_WIDTH
+
+OFE_LIM = (-0.15, 0.55)
+PROMINENCE = 0.1
+FEH_BINS = [(-0.6, -0.4), (-0.4, -0.2)]
+COLORS = [paultol.highcontrast.colors[0], paultol.highcontrast.colors[2]]
+LINESTYLES = ['--', '-']
+GALR_LIM = (7, 9)
+ABSZ_LIM = (0, 2)
+SMOOTH_WIDTH = 0.05
+
+SFH_LIST = ['insideout', 'lateburst', 'earlyburst', 'twoinfall']
+SFH_LABELS = ['Inside-out', 'Late-burst', 'Early-burst', 'Two-infall']
+DTD_LIST = ['prompt', 
+            'powerlaw_slope11', 
+            'exponential_timescale15', 
+            'plateau_width10', 
+            'triple']
+DTD_LABELS = ['Two-population', 
+              'Power law\n($\\alpha=-1.1$)', 
+              'Exponential\n($\\tau=1.5$ Gyr)',
+              'Plateau\n($W=1.0$ Gyr)', 
+              'Triple-system']
+
+def main():
+    plt.style.use(paths.styles / 'paper.mplstyle')
+    figwidth = TWO_COLUMN_WIDTH
+    fig, axs = plt.subplots(2, 5, figsize=(figwidth, figwidth*0.4), 
+                            sharex=True, sharey='row')
+    fig.subplots_adjust(left=0.06, top=0.89, right=0.98, bottom=0.13,
+                        wspace=0.07, hspace=0.3)
+    # Remove spines and y-axis labels
+    for ax in axs.flatten():
+        ax.spines['right'].set_visible(False)
[…]

### 2023-08-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{upgreek}
-% \usepackage{siunitx}
-
-% custom unit definitions
-% \DeclareSIUnit\year{yr}
 
@@
 
+Summary of DTDs used in simulations and theoretical studies.
+The Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations implement the DTD from \citet{Mannucci2006-TwoPopulations} (explain previously).
+Following \citet{Schonrich2009-RadialMixing}, \citet{Weinberg2017-ChemicalEquilibrium} assume an exponential DTD for the purposes of producing an analytical solution to the equations of chemical equilibrium, but they show that it can be extended to a double-exponential DTD which closely approximates a power-law.
+
+A few chemical evolution studies have compared DTDs with different functional forms.
+\citet{Poulhazan2018-PrecisionPollution} investigate six different DTDs in a smoothed-particle hydrodynamics simulation.
+\citet{Palicio2023-AnalyticDTD} derive analytic solutions to one-zone chemical evolution equations for seven DTDs (three theoretical and four empirical), approximating the more complicated DTD functions as a linear combination of exponential, Gaussian, and power-law components.
+
+The origin of the [$\alpha$/Fe] bimodality is debated.
+\citet{Schonrich2009-RadialMixing} argue that it arises due to radial migration (churning) even with a smooth star formation rate.
+\citet{Johnson2021-Migration} use a smooth SFR and a prescription for radial migration but are unable to reproduce the bimodality.
+\citet{Spitoni2021-TwoInfall} (definitely earlier papers too) argue that two distinct infall episodes can explain the bimodality.
+
 \section{Methods}
@@
     \includegraphics{figures/delay_time_distributions.pdf}
-    \caption{Models of the SN Ia delay time distribution used in this paper.
+    \caption{Models of the SN Ia delay time distribution (DTD) used in this paper.
 All functions are normalized to $f_{\rm Ia}=1$ at $\tau=1$ Gyr.
-The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD}.
+The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD}, to the same scale as the DTD models.
 The horizontal error bars indicate the time range of each DTD measurement, and the vertical error bars represent the 1$\sigma$ uncertainties.}
@@
 We investigate the cases $W=0.3$ Gyr and $W=1$ Gyr, taking $\alpha=-1.1$ for all plateau models.
-Figure \ref{fig:dtd-greggio05} illustrates the similarity between these models and two different treatments of the analytical double-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
+Figure \ref{fig:analytical-dtd} illustrates the similarity between these models and two different treatments of the analytical double-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
+For more discussion on this, see Appendix \ref{app:analytical-dtds}.
 
@@
 Following the two-population model from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in roughly 50\% of SNe Ia exploding within $t<100$ Myr.
+\citet{Poulhazan2018-PrecisionPollution} refer to this as the ``bimodal'' model.
 
@@
     \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
-In each panel, we plot curves for the zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
+In each panel, we plot curves for the simulation zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
     \label{fig:sfhs}
@@
 The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively.
+For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr.
 In all cases a minimum SN Ia delay time of 40 Myr is assumed.
@@
 The marginal panels above and to the right of the central panel present the distributions of [Fe/H] and [O/Fe], respectively.
-For display purposes these distributions are convolved with a Gaussian with a standard deviation of 0.02 dex.
-    \textit{Middle:} A similar plot comparing exponential DTDs with varying timescales. The solid, dashed, and dotted curves represent timescales $\tau=6$, 3, and 1.5 Gyr, respectively.
+For display purposes, these distributions are convolved with a Gaussian with a standard deviation of 0.02 dex.
+    \textit{Middle:} Similar, comparing exponential DTDs with varying timescales. The solid, dashed, and dotted curves represent timescales $\tau=6$, 3, and 1.5 Gyr, respectively.
     \textit{Right:} Similar, comparing plateau DTDs with varying plateau widths.
@@
 All plateau DTD models assume a post-plateau power-law slope of $\alpha=-1.1$.
-For reference, the dotted blue curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted purple curve represents a power-law DTD $\alpha=-1.1$ and no plateau.}
+For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted purple curve represents a power-law DTD $\alpha=-1.1$ and no plateau.}
     \label{fig:onezone-threepanel}
@@
     \includegraphics[width=0.49\linewidth]{figures/onezone_dtd.pdf}
-    \caption{\textit{Left:} Comparison of one-zone models with minimum SN Ia delay times of 40 Myr (solid) and 150 Myr (dashed curves) for two DTDs: a power-law with $\alpha=-1.1$ (blue), and an exponential with $\tau=1.5$ Gyr (purple curves).
+    \caption{\textit{Left:} Comparison of one-zone models with minimum SN Ia delay times of 40 Myr (solid curves) and 150 Myr (dashed curves) for two DTDs: a power-law with $\alpha=-1.1$ (blue curves), and an exponential with $\tau=1.5$ Gyr (purple curves).
 The layout is similar to the plots in Figure \ref{fig:onezone-threepanel}.
     \textit{Right:} Comparison of one-zone models which assume all five functional forms for the DTD in this paper: triple-system (green), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
-In all cases a minimum SN Ia delay time of 40 Myr is assumed.}
+A minimum SN Ia delay time of 40 Myr is assumed for all models.}
     \label{fig:onezone-twopanel}
@@
 
-Holding the SFH fixed, varying the DTD has only a minor effect on the MDF across the disk.
-Figure \ref{fig:feh-df-dtd} plots the [Fe/H] distributions for two multi-zone simulations which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
+Figure \ref{fig:feh-df-comparison} shows MDFs across the Galaxy for a selection of models and APOGEE data.
+The two left-hand columns show MDFs from our simulations which assume the same DTD (exponential with $\tau=1.5$ Gyr) but different model SFHs.
+For comparison, the APOGEE MDFs are binned similarly and presented in the center column of Figure \ref{fig:feh-df-comparison}.
+
+Holding the SFH fixed, varying the DTD has a very minor effect on the MDF across the disk.
+The two right-hand columns of Figure \ref{fig:feh-df-comparison} plot the MDFs for two multi-zone simulations which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
 The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of SNe Ia exploding within 1 Gyr in the former model but only $\sim 30\%$ in the latter.
-Nevertheless, the effect of the DTD on the MDF is second-order compared to the effect of the SFH as seen in Figure \ref{fig:feh-df-sfh}.
 
-% \begin{figure}
-%     \centering
-%     \includegraphics{figures/feh_df_dtd.pdf}
-%     \caption{Distributions of [Fe/H] from multi-zone simulations with different DTDs: a power-law with slope $\alpha=-1.4$ (\textit{left}), and an exponential with timescale $\tau=3$ Gyr (\textit{right}).
-Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}).
-Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue).
-Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row.
-All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex.
-In both cases an inside-out SFH is assumed.}
-%     \label{fig:feh-df-dtd}
-%     \script{feh_df_dtd.py}
-% \end{figure}
+The choice of DTD and SFH has a larger effect on the inner regions of the galaxy than the outer.
+Inner regions have a higher SFR and more stars are formed at early times than late, so differences in the SN Ia rate have a more pronounced effect on the MDF.
+For all SFH models except two-infall, the outer galaxy has a longer SFR timescale than the inner galaxy, so the MDF in the outer galaxy is relatively unaffected by the fraction of prompt SNe Ia.
 
-Figure \ref{fig:feh-df-sfh} plots the distribution of [Fe/H] in multiple regions across the disk for the four SFHs in this paper.
-
-% \begin{figure*}
-%     \centering
-%     \includegraphics{figures/feh_df_sfh.pdf}
-%     \caption{Distributions of [Fe/H] from multi-zone simulations with different SFHs.
-The plot format is similar to Figure \ref{fig:feh-df-dtd}.
-In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.
-Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
-%     \label{fig:feh-df-sfh}
-%     \script{feh_df_sfh.py}
-% \end{figure*}
+While there are some quantitative differences in how the shape of the MDF varies with Galactic region, the qualitative trends are unaffected by the choice of model SFH or DTD.
+These trends are primarily driven by chemical equilibrium, abundance gradients, and radial migration \citep[][see their Section 3.2 for further discussion]{Johnson2021-Migration}.
 
@@
 
+% \begin{figure}
+%     \centering
+%     \includegraphics{figures/feh_df_dtd.pdf}
+%     \caption{Distributions of [Fe/H] from multi-zone simulations with different DTDs: a power-law with slope $\alpha=-1.4$ (\textit{left}), and an exponential with timescale $\tau=3$ Gyr (\textit{right}).
+Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}).
+Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue).
+Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row.
+All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex.
+In both cases an inside-out SFH is assumed.}
+%     \label{fig:feh-df-dtd}
+%     \script{feh_df_dtd.py}
+% \end{figure}
+
+% \begin{figure*}
+%     \centering
+%     \includegraphics{figures/feh_df_sfh.pdf}
+%     \caption{Distributions of [Fe/H] from multi-zone simulations with different SFHs.
+The plot format is similar to Figure \ref{fig:feh-df-dtd}.
+In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.
+Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
+%     \label{fig:feh-df-sfh}
+%     \script{feh_df_sfh.py}
+% \end{figure*}
+
 \subsection{The distribution of [O/Fe]}
+
+The early-burst model produces a bimodal distribution of [O/Fe] even out to large radii and close to the midplane, whereas the APOGEE distribution does not show a prominent high-$\alpha$ peak beyond $R_{\rm{Gal}}\sim11$ kpc.
 
@@
 
+Figure \ref{fig:ofe-df-dtd} shows [O/Fe] distributions from simulations with the same SFH but a variety of different DTDs.
+We choose the early-burst SFH because it produces distinct high- and low-$\alpha$ sequences, which makes the effect of the DTD on the former more apparent.
+The most apparent effect of the DTD is to shift the mode of the high-$\alpha$ sequence.
+The two-population DTD, which has the most prompt SNe Ia of any model in this paper, places the high-$\alpha$ sequence at [O/Fe]$\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places $\sim0.2$ dex higher at [O/Fe]$\approx0.4$.
+
 \begin{figure*}
@@
 
+\subsection{Bimodality in [O/Fe]}
+\label{sec:bimodality}
+
 \subsection{The [O/Fe]--[Fe/H] Plane}
 \label{sec:ofe-feh}
+
+Figure \ref{fig:ofe-feh-sfh} compares the [O/Fe]--[Fe/H] plane in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) between our four model SFHs.
 
@@
 \variable{output/summary_table.tex}
+
+Compare to previous studies: \citet{Poulhazan2018-PrecisionPollution,Palicio2023-AnalyticDTD}.
+
+\citet{Poulhazan2018-PrecisionPollution} found that DTD models with a significant prompt component (power-law and two-population) produced the highest average stellar abundance of [O/Fe].
+They also found that these models produced the narrowest [O/Fe] distributions and suppressed the long tail to low [O/Fe] ratios.
+Conversely, their models with essentially 0 prompt SNe Ia produced a lower average stellar [O/Fe] ratio at late times and a broader distribution of [O/Fe].
+Their isolated galaxy simulations have an SFR which features an early ($<1$ Gyr) burst followed by a roughly exponential decline, qualitatively similar to our early-burst model but with the peak of star formation occuring $\sim3$ Gyr earlier.
+We note that their simulations were not designed to reproduce a Milky Way-like galaxy; as such, their [O/Fe] distributions peak around $\sim0.45$ which is higher than the APOGEE high-$\alpha$ sequence.
+Nevertheless, our study reproduces their finding that a DTD with more prompt SNe Ia will produce a narrower distribution of [O/Fe].
+One exception to this is the exponential DTD, which has a marginally narrower distribution than the power-law DTD close to the midplane [numbers here] but a more prominent hith-$\alpha$ tail.
+This is likely a consequence of the fact that the exponential DTD has a much lower SN Ia rate at late times ($\sim10$ Gyr) than other models [expand on this].
 
@@
 They find that the parameters which have a large effect on the shape of the DTD are the distribution and range of stellar masses in progenitor systems; the efficiency of accretion in the SD scenario; and the distribution of separations at birth in the DD scenario.
-Figure \ref{fig:dtd-greggio05} shows the analytical DTDs for SD progenitors and two different prescriptions for DD progenitors (``WIDE'' and ``CLOSE'').
+The left-hand panel of Figure \ref{fig:analytical-dtd} shows the analytical DTDs for SD progenitors and two different prescriptions for DD progenitors (``WIDE'' and ``CLOSE'').
 In the ``WIDE'' scheme, it is assumed that there is a wide distribution of ratios $A/A_0$ of the separation of the DD system to the initial separation of the binary, and that the distributions of $A$ and total mass of the system $m_{\rm DD}$ are independent, so one cannot necessarily predict the total merge time of a system based on its initial parameters.
@@
 
-Figure \ref{fig:onezone-greggio05} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs.
+The right-hand panel of Figure \ref{fig:analytical-dtd} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs.
 We assume $\eta=2.5$, $\tau_*=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.

### 2023-08-30 src/scripts/snakesim.py
remove multizone pickling

@@ -27,7 +27,7 @@ def main():
     model_ = model(str(fullpath), dict(snakemake.params))
     model_.run([_ * model_.dt for _ in range(round(
         _globals.END_TIME / model_.dt) + 1)],
-        overwrite = True, pickle = True)
+        overwrite = True, pickle = False)
 
 
 def model(name, params):

### 2023-08-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+\begin{figure*}
+    \centering
+    \includegraphics{figures/ofe_bimodality_summary.pdf}
+    \caption{The distributions of [O/Fe] along two slices of [Fe/H]: $-0.6\leq$[Fe/H]$<-0.4$ (blue dashed) and $-0.4\leq$[Fe/H]$<-0.2$ (red solid).
+\textit{Top row:} results from five multi-zone simulations which assume the late-bust SFH but different DTD models.
+\textit{Bottom row}: the first four panels compare the four SFH models, all assuming an exponential DTD with $\tau=1.5$ Gyr.
+The bottom-right panel plots data from APOGEE DR17 for reference.
+All panels contain stars within the Galactic region defined by $7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc.
+The maximum of each distribution is normalized to 1.}
+    \label{fig:ofe-bimodality}
+    \script{ofe_bimodality_summary.py}
+\end{figure*}
+
 \subsection{The [O/Fe]--[Fe/H] Plane}
@@
     \label{fig:ofe-feh-sfh}
-    \script{ofe-feh-sfh.py}
+    \script{ofe_feh_sfh.py}
 \end{figure}
@@
     \label{fig:ofe-feh-dtd}
-    \script{ofe-feh-dtd.py}
+    \script{ofe_feh_dtd.py}
 \end{figure*}

### 2023-09-19 src/scripts/feh_df_comparison.py
add panel highlighting function

@@ -8,7 +8,7 @@ import matplotlib.pyplot as plt
 import distribution_functions as dfs
 from multizone_stars import MultizoneStars
 from apogee_tools import import_apogee
-from utils import get_color_list
+from utils import get_color_list, highlight_panels
 import paths
 import _globals
 
@@ -53,14 +53,13 @@ def main():
         mzs = MultizoneStars.from_output(output_name)
         mzs.model_uncertainty(apogee_data, inplace=True)
         dfs.plot_multizone_mdfs(mzs, axs[:,3+i], '[fe/h]', colors, 
-                                label=DTD_LABELS[i], bins=NBINS,
-                                range=FEH_LIM, smoothing=SMOOTH_WIDTH)
+                                label=DTD_LABELS[i], **mdf_kwargs)
     # Add vertical lines for visual separation
-    for x in get_subplot_edges(fig, axs)[1:-1]:
-        line = plt.Line2D([x,x], [0.13,0.98], transform=fig.transFigure, 
-                          color='k', linewidth=0.5)
-        fig.add_artist(line)
-    
+    # for x in get_subplot_edges(fig, axs)[1:-1]:
+    #     line = plt.Line2D([x,x], [0.13,0.98], transform=fig.transFigure, 
+    #                       color='k', linewidth=0.5)
+    #     fig.add_artist(line)
+    highlight_panels(fig, axs, [(0,2),(1,2),(2,2)])
     
     for ax in axs[:,0]:
         ax.set_ylim((0, None))

### 2023-09-19 src/scripts/ofe_bimodality_summary.py

@@ -10,7 +10,7 @@ import matplotlib.pyplot as plt
 from matplotlib.ticker import MultipleLocator
 from multizone_stars import MultizoneStars
 import paths
-from utils import get_bin_centers
+from utils import get_bin_centers, highlight_panels
 from apogee_tools import import_apogee, apogee_region, apogee_mdf
 from colormaps import paultol
 from _globals import TWO_COLUMN_WIDTH
@@ -100,19 +100,7 @@ def main():
                     title='[Fe/H] bin')
     
     # Add gray box underneath APOGEE subpanel for visual separation
-    # Note: bbox coordinates converted from display to figure
-    bbox00 = axs[0,0].get_window_extent().transformed(fig.transFigure.inverted())
-    bbox01 = axs[0,1].get_window_extent().transformed(fig.transFigure.inverted())
-    bbox10 = axs[1,0].get_window_extent().transformed(fig.transFigure.inverted())
-    pad_h = bbox01.x0 - bbox00.x0 - bbox00.width
-    pad_v = bbox00.y0 - bbox10.y0 - bbox10.height
-    bg_color = '#cccccc'
-    bbox = axs[1,-1].get_tightbbox().transformed(fig.transFigure.inverted())
-    fig.patches.extend([plt.Rectangle((bbox.x0 - pad_h/2, bbox.y0 - pad_v/4),
-                                      bbox.x1 - bbox.x0 + pad_h, # width
-                                      bbox.y1 - bbox.y0 + pad_v/2, # height
-                                      fill=True, color=bg_color, zorder=-1,
-                                      transform=fig.transFigure, figure=fig)])
+    highlight_panels(fig, axs, (1,-1))
     
     # Save
     plt.savefig(paths.figures / 'ofe_bimodality_summary.pdf', dpi=300)

### 2023-09-19 src/scripts/ofe_df_dtd.py

@@ -9,7 +9,7 @@ import matplotlib.pyplot as plt
 import distribution_functions as dfs
 from multizone_stars import MultizoneStars
 from apogee_tools import import_apogee
-from utils import get_color_list
+from utils import get_color_list, highlight_panels
 import paths
 import _globals
 
@@ -51,6 +51,7 @@ def main():
         dfs.plot_multizone_mdfs(mzs, axs[:,i], '[o/fe]', colors, 
                                 label=DTD_LABELS[i], **mdf_kwargs)
     dfs.plot_apogee_mdfs(apogee_data, axs[:,-1], 'O_FE', colors, **mdf_kwargs)
+    highlight_panels(fig, axs, [(0,-1),(1,-1),(2,-1)])
     for ax in axs[:,0]:
         ax.set_ylim((0, None))
     plt.savefig(paths.figures / 'ofe_df_dtd.pdf', dpi=300)

### 2023-09-19 src/scripts/ofe_df_sfh.py

@@ -3,13 +3,12 @@ This script plots [O/Fe] distribution functions from VICE runs with the same
 DTD but different SFHs.
 """
 
-import argparse
 from pathlib import Path
 import matplotlib.pyplot as plt
 import distribution_functions as dfs
 from multizone_stars import MultizoneStars
 from apogee_tools import import_apogee
-from utils import get_color_list
+from utils import get_color_list, highlight_panels
 import paths
 import _globals
 
@@ -43,6 +42,7 @@ def main():
         dfs.plot_multizone_mdfs(mzs, axs[:,i], '[o/fe]', colors, 
                                 label=SFH_LABELS[i], **mdf_kwargs)
     dfs.plot_apogee_mdfs(apogee_data, axs[:,-1], 'O_FE', colors, **mdf_kwargs)
+    highlight_panels(fig, axs, [(0,-1),(1,-1),(2,-1)])
     for ax in axs[:,0]:
         ax.set_ylim((0, None))
     plt.savefig(paths.figures / 'ofe_df_sfh.pdf', dpi=300)

### 2023-09-19 src/scripts/midplane_distance.py
add semi-transparent label bbox

@@ -37,7 +37,14 @@ def main():
         output_name = '/'.join((mig, 'insideout/powerlaw_slope11/diskmodel'))
         mzs = MultizoneStars.from_output(output_name)
         row[2].text(0.5, 0.85, ROW_LABELS[m], 
-                    ha='center', transform=row[2].transAxes)
+                    ha='center', transform=row[2].transAxes,
+                    bbox={
+                        'facecolor': 'w',
+                        'edgecolor': 'none',
+                        'boxstyle': 'round',
+                        'pad': 0.15,
+                        'alpha': 1.,
+                    })
         for i, ax in enumerate(row):
             rfinal_lim = tuple(RFINAL_BINS[i:i+2])
             if m == 0:

### 2023-09-19 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Studies of galactic chemical evolution typically assume a single form for the SN Ia DTD.
-This is the first comprehensive look at the DTD in a model for GCE which includes the effects of radial migration.
+This is the first comprehensive look at the DTD in a multi-zone GCE model which includes the effects of radial migration.
 
@@
 
+Studies which have noted the [$\alpha$/Fe] bimodality: \citet{Furhmann1998-NearbyStars,Hayden2015-ChemicalCartography}.
 The origin of the [$\alpha$/Fe] bimodality is debated.
@@
 \label{sec:methods}
+
+\begin{deluxetable*}{Cccl}
+    \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models.
+We omit parameters which have been left unchanged from \citet{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
+    \tablehead{
+        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Section} & \colhead{Description}
+    }
+    \startdata
+        % Multi-zone simulation parameters
+        R_{\rm gal}     & [0, 20] kpc   & & Galactocentric radius \\
+        \delta R_{\rm gal}  & 100 pc    & & Width of each concentric ring \\
+        \Delta R_{\rm gal}  & N/A       & \ref{app:migration} & Change in orbital radius due to stellar migration \\
+        p(\Delta R_{\rm gal}|\tau,R_{\rm form}) & Equation \ref{eq:radial-migration}    & \ref{app:migration} & Probability density function of radial migration \\
+        z                   & [-3, 3] kpc                & \ref{app:migration} & Distance from Galactic midplane at present day \\
+        p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
+        \Delta t        & 10 Myr    & & Time-step size \\
+        t_{\rm max}     & 13.2 Gyr  & & Maximum simulation time \\
+        n               & 8         & & Number of stellar populations formed per ring per time-step \\
+        R_{\rm Ia}(t)   & Equations \ref{eq:powerlaw-dtd}--\ref{eq:triple-dtd}  & \ref{sec:dtd-models}  & Delay time distribution of Type Ia supernovae \\
+        t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
+        M_{\rm gas,0}   & 0         & & Initial gas mass \\
+        % Nucleosynthetic yields
+        y_{\rm O}^{\rm CC}  & 0.015     & & CCSN yield of O    \\
+        y_{\rm Fe}^{\rm CC} & 0.0012    & & CCSN yield of Fe   \\
+        y_{\rm O}^{\rm Ia}  & 0         & & SN Ia yield of O       \\
+        y_{\rm Fe}^{\rm Ia} & 0.00214   & & SN Ia yield of Fe \\
+        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & & Time-dependence of the star formation rate in the inside-out model \\
+        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & & Time-dependence of the star formation rate in the late-burst model \\
+        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & & Time-dependence of the infall rate in the early-burst model \\
+        \uptau_{*,\rm EB}(t|R_{\rm gal})  & Equation \ref{eq:earlyburst-conroy22} & & Time-dependence of the SFE timescale in the early-burst model \\
+        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & & Time-dependence of the infall rate in the two-infall model \\
+    \enddata
+\end{deluxetable*}
 
@@
 
-We limit our sample to red giant branch and red clump stars with high-quality spectra; Table \ref{tab:sample-selection} lists our selection criteria, which produce a final sample of \variable{output/sample_size.txt}stars.
+We limit our sample to red giant branch and red clump stars with high-quality spectra.
+Table \ref{tab:sample-selection} lists our selection criteria, which largely follow from \citet{Hayden2015-ChemicalCartography}.
+This produces a final sample of \variable{output/sample_size.txt}stars.
 
@@
 
-191,179 stars in our sample have astroNN ages and 71,684 have ages from \citet{Leung2023-Ages}.
+\citet{Leung2023-Ages} use a variational encoder-decoder network to estimate the age of APOGEE giants without contamination from age-abundance correlations.
+Their sample does not experience the $\sim10$ Gyr plateau that affects ages from astroNN \citep{Mackereth2019-astroNN-Ages}.
+We use an age uncertainty cut of 40\% per the recommendations of \citet{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt}APOGEE stars with age estimates.
+
+% 191,179 stars in our sample have astroNN ages and 71,684 have ages from \citet{Leung2023-Ages}.
 
@@
 
-\begin{deluxetable*}{Ccl}
-    \tablecaption{A summary of parameters and their fiducial values for our multi-zone chemical evolution models.
-We omit parameters which have been left unchanged from \citet{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
-    \tablehead{
-        \colhead{Quantity} & \colhead{Value} & \colhead{Description}
-    }
-    \startdata
-        t_D                 & 40 Myr                                & Minimum SN Ia delay time \\
-        \Delta R_{\rm gal}  & Equation \ref{eq:radial-migration}    & Change in radius due to stellar migration (see Appendix \ref{app:migration}) \\
-        z                   & Equation \ref{eq:sech-pdf}            & Distance from Galactic midplane at present day (see Appendix \ref{app:migration}) \\
-        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & Time-dependence of the infall rate in the early-burst model \\
-        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & Time-dependence of the infall rate in the two-infall model \\
-        \uptau_{*,\rm EB}(t|R_{\rm gal})  & Equation \ref{eq:earlyburst-conroy22} & Time-dependence of the SFE timescale in the early-burst model \\
-    \enddata
-\end{deluxetable*}
-
 \begin{deluxetable}{lll}
@@
 
+Away from the midplane, there is a clear trend of a higher average stellar [O/Fe] at small $R_{\rm gal}$ and lower [O/Fe] at large $R_{\rm gal}$.
+However, the APOGEE data show a clear dichotomy between inner-galaxy, high-$\alpha$ stars and outer-galaxy, low-$\alpha$ stars, with few in between.
+In the inside-out and late-burst SFHs, the shift from high-$\alpha$ to low-$\alpha$ is much more gradual and the trough at [O/Fe]$\approx0.2$ does not appear.
+The two-infall SFH appears to produce \textit{three} modes, at [O/Fe]$\approx 0.0$, $0.2$, and $0.4$, with the first and last showing the most variation with $R_{\rm gal}$ at high latitudes.
+The early-burst SFH produces the closest match to the data by far: the low-$\alpha$ sequence away from the midplane shows increasing contribution with larger radii, with the innermost radii containing very few low-$\alpha$ stars.
+However, the high-$\alpha$ sequence contains substantial contribution from stars at large radii, which is not seen in the data.
+
 \begin{figure*}
@@
 
+A striking feature of the [O/Fe] distribution in the Milky Way is the distinct separation into two components, the high- and low-$\alpha$ sequences.
+
 \begin{figure*}
@@
 All panels contain stars within the Galactic region defined by $7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc.
-The maximum of each distribution is normalized to 1.}
+The distributions of stars in $|z|$ The maximum of each distribution is normalized to 1 and the vertical scale is consistent across all panels.}
     \label{fig:ofe-bimodality}
@@
     \centering
-    \includegraphics{figures/age_ofe_sfh.pdf}
+    \includegraphics{figures/age_ofe_sfh_alt.pdf}
     \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different SFH models.
@@
     \label{fig:age-ofe-sfh}
-    \script{age_ofe_sfh.py}
+    \script{age_ofe_sfh_alt.py}
 \end{figure}
@@
     \centering
-    \includegraphics{figures/age_ofe_dtd.pdf}
+    \includegraphics{figures/age_ofe_dtd_alt.pdf}
     \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different DTD models.
@@
     \label{fig:age-ofe-dtd}
-    \script{age_ofe_dtd.py}
+    \script{age_ofe_dtd_alt.py}
 \end{figure*}
@@
 This is likely a consequence of the fact that the exponential DTD has a much lower SN Ia rate at late times ($\sim10$ Gyr) than other models [expand on this].
+
+\citet{Palicio2023-AnalyticDTD} compare seven different DTDs, including the analytical SD, DD-WIDE, and DD-CLOSE, as well as the empirical two-population and $t^{-1}$ power-law DTDs, in a one-zone model with a two-infall SFH.
+[Note that they use some different parameters for the analytical models than we do).
+Critically for our purposes, and in contrast to previous studies of the two-infall model \citep[e.g.,][others]{Chiappini1997-TwoInfall,Spitoni2021-TwoInfall}, the authors include the effects of outflows, although they explore mass-loading values of $\eta=0.2-0.8$ which is significantly lower than in our simulations.
 
@@
 When a star particle is created by VICE at initial radius $R_{\rm form}$, we sample its total radial migration distance $\Delta R$ from a Gaussian with a width described by Equation \ref{eq:radial-migration}, and we sample its final midplane distance $z_{\rm final}$ from the distribution described by Equation \ref{eq:sech-pdf} with a width given by Equation \ref{eq:scale-height}.
-The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citet{Johnson2021-Migration}, but with a time dependence $\propto t^{1/3}$.
+The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citet{Johnson2021-Migration}, but with a time dependence $\propto \Delta t^{1/3}$.
 This produces distributions of $R_{\rm final}$ and $z_{\rm final}$ which are similar to the analogue migration case for all but the oldest stars.
 
-Figure \ref{fig:radial-migration} compares the distributions of $R_{\rm final}$ in bins of $R_{\rm form}$ and age between the analogue and Gaussian migration schema. The
+\citet{Okalidis2022-AurigaMigration} studied the stellar migration in the Auriga simulations and found that the migration strength had both a dependence on age and formation radius.
+They also found that in strongly-barred galaxies, the migration is stronger overall but has a slower timestep evolution than diffusion ($\Delta t^{0.5}$).
+
+Figure \ref{fig:radial-migration} compares the distributions of $R_{\rm final}$ in bins of $R_{\rm form}$ and age between the analogue and Gaussian migration schema.
 

### 2023-09-19 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{upgreek}
+\let\tablenum\relax
+\usepackage{siunitx}
 
@@
 
-\subsection{Nucleosynthetic Yields}
-\label{sec:yields}
+We adopt the same nucleosynthetic yields as \citet{Johnson2021-Migration}; the values are presented in Table \ref{tab:multizone-parameters}.
 
-Table \ref{tab:yields} summarizes the nucleosynthetic yields assumed in this paper, which we adopt from \citet{Johnson2021-Migration}.
-
-\begin{deluxetable}{lll}
-    \tablecaption{Nucleosynthetic yields assumed in our simulations.\label{tab:yields}}
-    \tablehead{
-        \colhead{Source} & \colhead{Element} & \colhead{Yield}
-    }
-    \startdata
-    CCSN    & O     & 0.015     \\
-    CCSN    & Fe    & 0.0012    \\
-    \hline
-    SN Ia   & O     & 0         \\
-    SN Ia   & Fe    & 0.00214
-    \enddata
-\end{deluxetable}
+% \subsection{Nucleosynthetic Yields}
+% \label{sec:yields}
+% 
+% Table \ref{tab:yields} summarizes the nucleosynthetic yields assumed in this paper, which we adopt from \citet{Johnson2021-Migration}.
+% 
+% \begin{deluxetable}{lll}
+%     \tablecaption{Nucleosynthetic yields assumed in our simulations.\label{tab:yields}}
+%     \tablehead{
+%         \colhead{Source} & \colhead{Element} & \colhead{Yield}
+%     }
+%     \startdata
+%     CCSN    & O     & 0.015     \\
+%     CCSN    & Fe    & 0.0012    \\
+%     \hline
+%     SN Ia   & O     & 0         \\
+%     SN Ia   & Fe    & 0.00214
+%     \enddata
+% \end{deluxetable}
 
@@
 We compare our simulation results to abundance measurements from the 17th data release \citep[DR17;][]{Abdurro'uf2022-SDSSIV-DR17} of the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE}.
-APOGEE uses infrared spectrographs \citep{Wilson2019-APOGEE-Spectrographs} mounted on two telescopes: the 2.5-meter Sloan Foundation Telescope \citep{Gunn2006-SloanTelescope} at Apache Point Observatory, United States in the Northern Hemisphere, and the Ir{\'e}n{\'e}e DuPont Telescope \citep{BowenVaughan1973-DuPontTelescope} at Las Campanas Observatory, Chile in the Southern Hemisphere.
-After the spectra are passed through the data reduction pipeline \citep{Nidever2015-APOGEE-DataReduction}, the APOGEE Stellar Parameter and Chemical Abundance Pipeline \citep[ASPCAP;][]{Holtzmann2015-ASPCAP,GarciaPerez2016-ASPCAP} extracts chemical abundances using the model grids and interpolation method described by \citet{Jonsson2020-APOGEE-DR16}.
+APOGEE used infrared spectrographs \citep{Wilson2019-APOGEE-Spectrographs} mounted on two telescopes: the 2.5-meter Sloan Foundation Telescope \citep{Gunn2006-SloanTelescope} at Apache Point Observatory, United States in the Northern Hemisphere, and the Ir{\'e}n{\'e}e DuPont Telescope \citep{BowenVaughan1973-DuPontTelescope} at Las Campanas Observatory, Chile in the Southern Hemisphere.
+After the spectra were passed through the data reduction pipeline \citep{Nidever2015-APOGEE-DataReduction}, the APOGEE Stellar Parameter and Chemical Abundance Pipeline \citep[ASPCAP;][]{Holtzmann2015-ASPCAP,GarciaPerez2016-ASPCAP} extracted chemical abundances using the model grids and interpolation method described by \citet{Jonsson2020-APOGEE-DR16}.
 
-We limit our sample to red giant branch and red clump stars with high-quality spectra.
+We restrict our sample to red giant branch and red clump stars with high-quality spectra.
 Table \ref{tab:sample-selection} lists our selection criteria, which largely follow from \citet{Hayden2015-ChemicalCartography}.
 This produces a final sample of \variable{output/sample_size.txt}stars.
+APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
+We adopt estimated ages from \citet{Leung2023-Ages}, who use a variational encoder-decoder network to estimate the age of APOGEE giants without contamination from age-abundance correlations.
+Their sample does not experience the $\sim10$ Gyr plateau that affects ages from astroNN \citep{Mackereth2019-astroNN-Ages}.
+We use an age uncertainty cut of 40\% per the recommendations of \citet{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt}APOGEE stars with age estimates.
+The median uncertainty in log-age space is $\sim 0.1$.
 
@@
 \end{deluxetable*}
-
-\subsubsection{Stellar Ages}
-\label{sec:stellar-ages}
-
-\citet{Leung2023-Ages} use a variational encoder-decoder network to estimate the age of APOGEE giants without contamination from age-abundance correlations.
-Their sample does not experience the $\sim10$ Gyr plateau that affects ages from astroNN \citep{Mackereth2019-astroNN-Ages}.
-We use an age uncertainty cut of 40\% per the recommendations of \citet{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt}APOGEE stars with age estimates.
-
-% 191,179 stars in our sample have astroNN ages and 71,684 have ages from \citet{Leung2023-Ages}.
-
-% For $19784$ stars, or $\sim3.5\%$ of the sample, the astroNN [Fe/H] abundance estimate is $\gtrsim0.5$ dex lower than the value provided by ASPCAP.
-The vast majority of these stars are on the lower-main sequence according to \textit{Gaia} photometry, so we exclude stars with $\log(g) > 4$ in ASPCAP.
-In addition, 197 or $\sim3\%$ of stars with APOKASC-2 asteroseismic ages are reported to be $>5$ Gyr younger by astroNN.
-The APOKASC-2 age is unphysically high for many of these stars, often exceeding 15 Gyr.
-We identify prior mass loss as the cause of this discrepancy, so the astroNN ages are likely closer to the truth.
 
@@
 
+This work has made use of data from the European Space Agency (ESA) mission
+{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
+Data Processing and Analysis Consortium (DPAC,
+\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
+has been provided by national institutions, in particular the institutions
+participating in the {\it Gaia} Multilateral Agreement.
+
 \end{acknowledgments}
@@
 In the top row, we exclude age bins with fewer than 100 unique analogue IDs for clarity.
-All distributions are normalized so that the area under the curve is 1, and have been smoothed by a boxcar function of width 0.5 kpc.
+All distributions are normalized so that the area under the curve is 1, and have been smoothed by a boxcar function with a width of 0.5 kpc.
 The vertical dotted black lines indicate the bounds of each bin in $R_{\rm form}$; stars within that region of the distribution have not migrated outside their birth annulus over their lifetime.}
@@
 In the top row, we exclude age bins with fewer than 500 unique analogue IDs for clarity.
-All distributions have been smoothed by a boxcar function of width 0.1 kpc.}
+All distributions have been smoothed by a boxcar function with a width of 0.1 kpc.}
     \label{fig:midplane-distance}

### 2023-09-27 src/scripts/ofe_feh_sfh.py
add legend

@@ -6,6 +6,7 @@ different star formation histories.
 from pathlib import Path
 import matplotlib.pyplot as plt
 from matplotlib.ticker import MultipleLocator
+from matplotlib.lines import Line2D
 import vice
 from multizone_stars import MultizoneStars
 from scatter_plot_grid import setup_colorbar
@@ -28,7 +29,7 @@ def main():
     plt.style.use(paths.styles / 'paper.mplstyle')
     fig, axs = plt.subplots(2, 2, sharex=True, sharey=True,
                             figsize=(ONE_COLUMN_WIDTH, 0.9*ONE_COLUMN_WIDTH))
-    plt.subplots_adjust(top=0.98, right=0.93, wspace=0., hspace=0.)
+    plt.subplots_adjust(top=0.95, right=0.93, wspace=0., hspace=0., left=0.11)
     cbar = setup_colorbar(fig, cmap=CMAP_NAME, vmin=0, vmax=MAX_SF_RADIUS,
                           label=r'Birth $R_{\rm{gal}}$ [kpc]', pad=0.02,
                           labelpad=2, width=0.04)
@@ -46,7 +47,7 @@ def main():
         mzs.region(GALR_LIM, ABSZ_LIM, inplace=True)
         # Plot sample of star particle abundances
         mzs.scatter_plot(ax, '[fe/h]', '[o/fe]', color='galr_origin',
-                         cmap=CMAP_NAME, norm=cbar.norm, markersize=0.1)
+                          cmap=CMAP_NAME, norm=cbar.norm, markersize=0.1)
         apogee_contours(ax, apogee_data, GALR_LIM, ABSZ_LIM)
         # Plot abundance tracks
         zone = int(0.5 * (GALR_LIM[0] + GALR_LIM[1]) / ZONE_WIDTH)
@@ -72,6 +73,18 @@ def main():
         ax.set_xlabel('[Fe/H]')
     for ax in axs[:,0]:
         ax.set_ylabel('[O/Fe]')
+    # Custom legend
+    custom_lines = [Line2D([0], [0], color='k', linestyle='-', linewidth=0.5),
+                    Line2D([0], [0], color='r', linestyle='-', linewidth=0.5),
+                    Line2D([0], [0], color='r', linestyle='--', linewidth=0.5)]
+    legend_labels = ['Gas abundance', 'APOGEE 30% contour', 'APOGEE 80% contour']
+    # axs[0,1].legend(custom_lines, legend_labels, frameon=False, 
[…]

### 2023-09-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Define document class
-\documentclass[twocolumn,linenumbers,twocolappendix]{aastex631}
+\documentclass[modern,linenumbers]{aastex631}
+%twocolappendix
 
@@
 \usepackage{amssymb}
+\usepackage{graphicx}
 % \usepackage{layouts}
@@
 \newcommand{\no}{\textcolor{red}{$\times$}}
+\newcommand{\osuaffil}{Department of Astronomy, The Ohio State University, 140 W. 18th Ave, Columbus OH 43210, USA}
+
+\shorttitle{Galactic SN Ia DTD}
+\shortauthors{Dubay, Johnson, \& Johnson}
 
@@
 \author[0000-0003-3781-0747]{Liam O. Dubay}
+\affiliation{\osuaffil}
 \author[0000-0001-7258-1834]{Jennifer A. Johnson}
+\affiliation{\osuaffil}
+\affiliation{Center for Cosmology and Astroparticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus OH 43210, USA}
 \author[0000-0002-6534-8783]{James W. Johnson}
+\affiliation{\osuaffil}
+\affiliation{Carnegie Observatories}
 % \author[0000-0001-7775-7261]{David H. Weinberg}
@@
         y_{\rm Fe}^{\rm Ia} & 0.00214   & & SN Ia yield of Fe \\
-        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & & Time-dependence of the star formation rate in the inside-out model \\
-        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & & Time-dependence of the star formation rate in the late-burst model \\
-        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & & Time-dependence of the infall rate in the early-burst model \\
+        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & & Time-dependence of the SFR in the inside-out model \\
+        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & & Time-dependence of the SFR in the late-burst model \\
+        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & & Time-dependence of the IFR in the early-burst model \\
         \uptau_{*,\rm EB}(t|R_{\rm gal})  & Equation \ref{eq:earlyburst-conroy22} & & Time-dependence of the SFE timescale in the early-burst model \\
-        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & & Time-dependence of the infall rate in the two-infall model \\
+        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & & Time-dependence of the IFR in the two-infall model \\
     \enddata
@@
 
-We explore five different functional forms for the SN Ia DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, a two-population model, and a model based on triple-system dynamics, with a one or two different parameterizations for each.
-Figure \ref{fig:dtds} presents these DTDs as a function of time after star formation.
+\begin{subequations}
+\begin{align}
+    \dot M_{\rm Fe}^{\rm Ia} &= y_{\rm Fe}^{\rm Ia} \langle \dot M_*\rangle_{\rm Ia} \\
+    &= y_{\rm Fe}^{\rm Ia} \frac{\int_0^t \dot M_*(t')R_{\rm Ia}(t-t')dt'}{\int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt'}
+\end{align}
+\end{subequations}
+
+The yield $y_{\rm Fe}^{\rm Ia}$ can be expressed in terms of the integral of the DTD:
+
+\begin{equation}
+    y_{\rm Fe}^{\rm Ia} = m_{\rm Fe}^{\rm Ia} \int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt' = m_{\rm Fe}^{\rm Ia} \frac{N_{\rm Ia}}{M_*}
+    \label{eq:dtd-integral}
+\end{equation}
+where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia.
+We take the average number of SNe Ia per mass of stars formed to be $N_{\rm Ia}/M_*=2.2\times10^{-3}\,{\rm M}_\odot^{-1}$ following \citet{MaozMannucci2012-SNeIaReview}, which gives $R_{\rm Ia}$ units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$.
+
+We explore five different functional forms for the SN Ia DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, a two-population model, and a model based on triple-system dynamics, with a one or two variants of each.
+We present the unnormalized functional forms for $R_{\rm Ia}(t)$ below; VICE automatically normalizes and scales the DTD to produce the correct number of SNe Ia over the lifetime of the Galaxy.
+Figure \ref{fig:dtds} presents these DTDs as a function of time after star formation, and Table \ref{tab:dtds} summarizes the DTD models and their parameters.
 
@@
     \includegraphics{figures/delay_time_distributions.pdf}
-    \caption{Models of the SN Ia delay time distribution (DTD) used in this paper.
-All functions are normalized to $f_{\rm Ia}=1$ at $\tau=1$ Gyr.
-The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD}, to the same scale as the DTD models.
-The horizontal error bars indicate the time range of each DTD measurement, and the vertical error bars represent the 1$\sigma$ uncertainties.}
+    \caption{Selection of models for the SN Ia delay time distribution (DTD) used in this paper.
+All functions are normalized such that $R_{\rm Ia}(t=1\,{\rm Gyr})=1$.
+The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD} at the same scale as the DTD models.
+The horizontal and vertical error bars indicate the time range and 1$\sigma$ uncertainties, respectively, of each DTD measurement.}
     \label{fig:dtds}
@@
 \end{figure}
-
-% \citet{Stolger2020-ExponentialDTD} perform maximum likelihood estimations based on the cosmic star formation history and the star formation histories of individual galaxies.
-In both cases their best fit functions were approximately exponential, though they started with a skew-normal function so could not have ended up with a power law even if they wanted to.
-They don't actually report the timescale of this exponential, but based on the plots I'd say it's about 1.5 - 2 (1.7?) Gyr.
-Their best fit parameters make no sense to me as they don't report their units.
-
-\paragraph{Power-law} A simple power law with slope $\alpha$:
-\begin{equation}
-    R(t) = A_\alpha (t/1\,\rm{Gyr})^\alpha
-    \label{eq:powerlaw-dtd}
-\end{equation}
-where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
-A declining power-law with $\alpha\sim-1$ is a standard assumption in many observational studies of the DTD as well as GCE simulations.
-\citet{Maoz2017-CosmicDTD} obtain a DTD with $\alpha=-1.07\pm0.09$ based on volumetric rates and an assumed cosmic SFH for field galaxies in redshift range $0\leq z\leq 2.25$.
-\citet{Wiseman2021-DESRates} obtain a similar slope of $\alpha=-1.13\pm0.05$ for field galaxies in the redshift range $0.2<z<0.6$.
-For galaxy clusters, \citet{Maoz2017-CosmicDTD} find a steeper DTD slope of $\alpha=-1.39^{+0.32}_{-0.05}$.
-\citet{Heringer2019-FieldGalaxyDTD} use a SFH-independent method to constrain the DTD for field galaxies within $0.01<z<0.2$ and find a steeper slope of $\alpha=-1.34^{+0.19}_{-0.17}$.
-In this paper, we investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$.
-
-\paragraph{Plateau} A ``plateau'' model consisting of a flat slope of width $W$ followed by a power law decline with normalization $B_W$:
-\begin{equation}
-    R(t) = 
-    \begin{cases}
-        B_W, & t < W \\
-        B_W (t/W)^\alpha, & t \ge W
-    \end{cases}
-    \label{eq:plateau-dtd}
-\end{equation}
-where $B_W=[(W-t_{\rm min}) + \frac{t_{\rm max}^{\alpha+1} - W^{\alpha+1}}{(\alpha+1)W^\alpha}]^{-1}$ is the normalization coefficient.
-We investigate the cases $W=0.3$ Gyr and $W=1$ Gyr, taking $\alpha=-1.1$ for all plateau models.
-Figure \ref{fig:analytical-dtd} illustrates the similarity between these models and two different treatments of the analytical double-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
-For more discussion on this, see Appendix \ref{app:analytical-dtds}.
-
-\paragraph{Exponential} An exponentially declining DTD with timescale $\tau$ and normalization $C_\tau$:
-\begin{equation}
-    R(t) = \frac{1}{\tau} e^{-t/\tau}
-    \label{eq:exponential-dtd}
-\end{equation}
-We investigate the case where $\tau=1.5$ Gyr, which has been used in previous studies \citep[e.g.,][]{Schonrich2009-RadialMixing,Weinberg2017-ChemicalEquilibrium} and is similar to the analytical single-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
-We also investigate a longer timescale of $\tau=3$ Gyr.
-\citet{Matteucci1986-SupernovaEnrichment}, \citet{Stolger2020-ExponentialDTD}
-
-\paragraph{Two-population} A DTD in which 50\% of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the other 50\% form an exponential tail at large $t$, normalized by $D_{t_p,\sigma,\tau}$:
-\begin{equation}
-    R(t) = D_{t_p,\sigma,\tau} \Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
-    \label{eq:prompt-dtd}
-\end{equation}
-Following the two-population model from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in roughly 50\% of SNe Ia exploding within $t<100$ Myr.
-\citet{Poulhazan2018-PrecisionPollution} refer to this as the ``bimodal'' model.
-
-\paragraph{Triple} A DTD based on simulations of triple-system evolution by \citet{Rajamuthukumar2022-TripleEvolution}.
-We approximate their DTD as a special case of the plateau model (Equation \ref{eq:plateau-dtd}) where the initial rate is quite low until an instantaneous rise to the plateau value at time $t_{\rm rise}$:
-\begin{equation}
-    R(t) = 
-    \begin{cases}
-        \epsilon B_W, & t < t_{\rm rise} \\
-        B_W, & t_{\rm rise} \leq t < W \\
-        B_W (t / W) ^ \alpha, & t \geq W
-    \end{cases}
-    \label{eq:triple-dtd}
-\end{equation}
-We take $t_{\rm rise}=0.5$ Gyr, $W=0.5$ Gyr, $\alpha=-1.1$, and $\epsilon=0.05$ so the initial rate is 5\% of the peak rate.
-
-Table \ref{tab:dtds} summarizes the model DTDs we investigate in this paper.
 
@@
 \end{deluxetable*}
+
+% \citet{Stolger2020-ExponentialDTD} perform maximum likelihood estimations based on the cosmic star formation history and the star formation histories of individual galaxies.
+In both cases their best fit functions were approximately exponential, though they started with a skew-normal function so could not have ended up with a power law even if they wanted to.
+They don't actually report the timescale of this exponential, but based on the plots I'd say it's about 1.5 - 2 (1.7?) Gyr.
+Their best fit parameters make no sense to me as they don't report their units.
+
+\paragraph{Power-law} A simple power law with slope $\alpha$:
+\begin{equation}
+    R_{\rm Ia}(t) \propto (t/1\,\rm{Gyr})^\alpha
+    \label{eq:powerlaw-dtd}
+\end{equation}
+% where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
+A declining power-law with $\alpha\sim-1$ is a standard assumption in many observational studies of the DTD as well as GCE simulations.
+\citet{Maoz2017-CosmicDTD} obtain a DTD with $\alpha=-1.07\pm0.09$ based on volumetric rates and an assumed cosmic SFH for field galaxies in redshift range $0\leq z\leq 2.25$.
+\citet{Wiseman2021-DESRates} obtain a similar slope of $\alpha=-1.13\pm0.05$ for field galaxies in the redshift range $0.2<z<0.6$.
+For galaxy clusters, \citet{Maoz2017-CosmicDTD} find a steeper DTD slope of $\alpha=-1.39^{+0.32}_{-0.05}$.
+\citet{Heringer2019-FieldGalaxyDTD} use a SFH-independent method to constrain the DTD for field galaxies within $0.01<z<0.2$ and find a steeper slope of $\alpha=-1.34^{+0.19}_{-0.17}$.
+In this paper, we investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$.
+
+\paragraph{Plateau} A ``plateau'' model consisting of a flat slope of width $W$ followed by a power law decline:
+\begin{equation}
+    R_{\rm Ia}(t) \propto
+    \begin{cases}
+        1, & t < W \\
+        (t/W)^\alpha, & t \ge W
+    \end{cases}
+    \label{eq:plateau-dtd}
+\end{equation}
+% where $B_W=[(W-t_{\rm min}) + \frac{t_{\rm max}^{\alpha+1} - W^{\alpha+1}}{(\alpha+1)W^\alpha}]^{-1}$ is the normalization coefficient.
+We investigate the cases $W=0.3$ Gyr and $W=1$ Gyr, taking $\alpha=-1.1$ for all plateau models.
+Figure \ref{fig:analytical-dtd} illustrates the similarity between these models and two different treatments of the analytical double-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
+For more discussion on this, see Appendix \ref{app:analytical-dtds}.
+
+\paragraph{Triple-system} A DTD based on simulations of triple-system evolution by \citet{Rajamuthukumar2022-TripleEvolution}.
+We approximate their DTD as a special case of the plateau model (Equation \ref{eq:plateau-dtd}) where the initial rate is quite low until an instantaneous rise to the plateau value at time $t_{\rm rise}$:
+\begin{equation}
+    R_{\rm Ia}(t) \propto
+    \begin{cases}
+        \epsilon, & t < t_{\rm rise} \\
+        1, & t_{\rm rise} \leq t < W \\
+        (t / W) ^ \alpha, & t \geq W
+    \end{cases}
+    \label{eq:triple-dtd}
+\end{equation}
+We take $t_{\rm rise}=0.5$ Gyr, $W=0.5$ Gyr, $\alpha=-1.1$, and $\epsilon=0.05$ so the initial rate is 5\% of the peak rate.
+
+\paragraph{Exponential} An exponentially declining DTD with timescale $\tau$:
+\begin{equation}
+    R_{\rm Ia}(t) \propto \frac{1}{\tau} e^{-t/\tau}
+    \label{eq:exponential-dtd}
+\end{equation}
+We investigate the case where $\tau=1.5$ Gyr, which has been used in previous GCE studies \citep[e.g.,][]{Schonrich2009-RadialMixing,Weinberg2017-ChemicalEquilibrium} and is similar to the analytical single-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
+We also investigate a longer timescale of $\tau=3$ Gyr.
+\citet{Matteucci1986-SupernovaEnrichment}, \citet{Stolger2020-ExponentialDTD}
+
+\paragraph{Two-population} A DTD in which 50\% of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the other 50\% form an exponential tail at large $t$:
+\begin{equation}
+    R_{\rm Ia}(t) \propto 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
+    \label{eq:prompt-dtd}
+\end{equation}
+Following the two-population model from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in roughly 50\% of SNe Ia exploding within $t<100$ Myr.
+\citet{Poulhazan2018-PrecisionPollution} refer to this as the ``bimodal'' model.
+
+% Minimum SN Ia delay time
+The minimum SN Ia delay time $t_D$, i.e.
+the lifetime of the most massive progenitor system, is also a parameter of the DTD which can have an effect on chemical evolution.
+\citet{Andrews2017-ChemicalEvolution} found that a longer minimum delay time produces a sharper high-$\alpha$ ``knee'' and shifts it to higher [Fe/H], although they only explored this for an exponential DTD.
+They adopt a fiducial value of $t_D=150$ Myr, as do \citet{Johnson2021-Migration}.
+\citet{Poulhazan2018-PrecisionPollution} adopt a much smaller value of $t_D=29$ Myr as the lifetime of their most massive progenitors.
+
+We take $t_D=40$ Myr to be our fiducial value as it is the approximate lifetime of an $8\,{\rm M}_\odot$ star [Larson 1974].
+We find that adopting a longer $t_D$ has only a minor effect on the chemical evolution for most DTD models except the power-law, but in that case the effect of a longer minimum delay time can be approximated by adding an initial plateau of $\sim100$ Myr to the DTD.
+See Section \ref{sec:onezone-results} and Figure \ref{fig:onezone-twopanel} for details.
 
@@
     \centering
-    \includegraphics{figures/star_formation_histories.pdf}
+    \includegraphics[width=\linewidth]{figures/star_formation_histories.pdf}
     \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
@@
     \centering
-    \includegraphics{figures/feh_df_comparison.pdf}
+    \includegraphics[width=\linewidth]{figures/feh_df_comparison.pdf}
     \caption{Distributions of [Fe/H] from multi-zone simulations with various models for the SFH and DTD.
@@
 %     \centering
-%     \includegraphics{figures/feh_df_sfh.pdf}
+%     \includegraphics[width=\linewidth]{figures/feh_df_sfh.pdf}
 %     \caption{Distributions of [Fe/H] from multi-zone simulations with different SFHs.
@@
     \centering
-    \includegraphics{figures/ofe_df_sfh.pdf}
+    \includegraphics[width=\linewidth]{figures/ofe_df_sfh.pdf}
     \caption{Distributions of [O/Fe] from multi-zone simulations with different SFHs.
@@
     \centering
-    \includegraphics{figures/ofe_df_dtd.pdf}
+    \includegraphics[width=\linewidth]{figures/ofe_df_dtd.pdf}
     \caption{Distributions of [O/Fe] from multi-zone simulations with different DTDs. In all cases an inside-out SFH is assumed. The plot format is similar to Figure \ref{fig:ofe-df-sfh}.}
@@
 
+Reference \citet{Vincenzo2021-AlphaDistribution} for how the bimodality is made stronger by the selection function, but it's not just due to selection effects.
+
 \begin{figure*}
     \centering
-    \includegraphics{figures/ofe_bimodality_summary.pdf}
+    \includegraphics[width=\linewidth]{figures/ofe_bimodality_summary.pdf}
     \caption{The distributions of [O/Fe] along two slices of [Fe/H]: $-0.6\leq$[Fe/H]$<-0.4$ (blue dashed) and $-0.4\leq$[Fe/H]$<-0.2$ (red solid).
@@
 \textit{Bottom row}: the first four panels compare the four SFH models, all assuming an exponential DTD with $\tau=1.5$ Gyr.
-The bottom-right panel plots data from APOGEE DR17 for reference.
+The bottom-right panel (highlighted) plots data from APOGEE DR17 for reference.
 All panels contain stars within the Galactic region defined by $7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc.
@@
 The black curves represent the ISM abundance tracks in the 8 kpc zone.
-The red contours represent the APOGEE abundance distribution, with the solid and dashed contours enclosing 68\% and 95\% of stars in the sample, respectively.}
+The red contours represent a 2-D kernel density estimate of the APOGEE abundance distribution in that Galactic region, with the solid and dashed contours enclosing 30\% and 80\% of stars in the sample, respectively.}
     \label{fig:ofe-feh-sfh}
@@
     \centering
-    \includegraphics{figures/ofe_feh_dtd.pdf}
+    \includegraphics[width=\linewidth]{figures/ofe_feh_dtd.pdf}
     \caption{The [O/Fe]--[Fe/H] plane from multi-zone simulations with different DTD models.
@@
     \centering
-    \includegraphics{figures/age_ofe_dtd_alt.pdf}
+    \includegraphics[width=\linewidth]{figures/age_ofe_dtd_alt.pdf}
     \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different DTD models.
@@
 The results of these tests are presented in Table \ref{tab:results}.
-Instead of reporting the numerical scores for each simulation output, in the column corresponding to a particular diagnostic we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom third out of all of our simulations, respectively.
+Instead of reporting the numerical scores for each simulation output, in the column corresponding to a particular diagnostic we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom tirtile out of all of our simulations, respectively.
 A \yes indicates that particular combination of model SFH and DTD performed better than most when compared to the APOGEE sample for that diagnostic.
@@
 
+We need to constrain DTD or galactic SFH better. With SDSS-V, the latter seems much more achievable.
+
 \section{Conclusions}
@@
 \begin{acknowledgments}
-
     Funding for the Sloan Digital Sky 
@@
 
+    % This work made use of Astropy:\footnote{http://www.astropy.org} a community-developed core Python package and an ecosystem of tools and resources for astronomy \citep{astropy:2013, astropy:2018, astropy:2022}.
 \end{acknowledgments}
+
+\software{VICE \citep{JohnsonWeinberg2020-Starbursts}, Astropy \citep{astropy2013,astropy2018,astropy2022}, scikit-learn \citep{Pedregosa2011-ScikitLearn}, SciPy \citep{2020SciPy-NMeth}, Matplotlib \citep{Hunter2007-Matplotlib}}
 
@@
     \centering
-    \includegraphics{figures/dtd_analytical.pdf}
-    \includegraphics{figures/onezone_analytical_dtd.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/dtd_analytical.pdf}
+    \includegraphics[width=0.49\linewidth]{figures/onezone_analytical_dtd.pdf}
     \caption{\textit{Left:} Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and simple DTD functions (dashed curves).
@@
     \centering
-    \includegraphics{figures/radial_migration.pdf}
+    \includegraphics[width=\linewidth]{figures/radial_migration.pdf}
     \caption{The distribution of final radius $R_{\rm final}$ as a function of formation radius $R_{\rm form}$ and age for the h277 analogue (top row) and Gaussian sampling scheme (bottom row).
@@
     \centering
-    \includegraphics{figures/midplane_distance.pdf}
+    \includegraphics[width=\linewidth]{figures/midplane_distance.pdf}
     \caption{Similar to Figure \ref{fig:radial-migration} but for the distribution of final midplane distance $z_{\rm final}$ as a function of final radius and age.

### 2023-10-05 src/scripts/delay_time_distributions.py
update poster font

@@ -17,8 +17,8 @@ def main(style='paper'):
     plt.rcParams['axes.prop_cycle'] = plt.cycler('color', paultol.bright.colors)
     fig, ax = setup_axes()
     times = [t*0.001 for t in range(40, 13200)]
-    distributions = [styles.prompt, styles.plaw, styles.plateau, 
-                     styles.exp, styles.triple]
+    distributions = [styles.prompt, styles.plaw, styles.exp, 
+                     styles.plateau_long, styles.triple]
     for dtd in distributions:
         func = dtd['func']
         ax.plot(times, [func(t) / func(1) for t in times], 

### 2023-10-05 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 The black curves represent the ISM abundance tracks in the 8 kpc zone.
-The red contours represent a 2-D kernel density estimate of the APOGEE abundance distribution in that Galactic region, with the solid and dashed contours enclosing 30\% and 80\% of stars in the sample, respectively.}
+The red contours represent a 2-D kernel density estimate with a bandwidth of 0.03 of the APOGEE abundance distribution in that Galactic region, with the solid and dashed contours enclosing 30\% and 80\% of stars in the sample, respectively.}
     \label{fig:ofe-feh-sfh}

### 2023-10-10 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \affiliation{\osuaffil}
-\affiliation{Carnegie Observatories}
+\affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
 % \author[0000-0001-7775-7261]{David H. Weinberg}
@@
 
+Galactic chemical evolution (GCE) studies seek to reproduce the observed distribution of metals throughout the Milky Way Galaxy.
+
+Type Ia supernovae (SNe Ia), the explosions of carbon-oxygen white dwarfs (WDs), are responsible for roughly half of the iron produced in the Galaxy.
+Despite their importance, the mechanism(s) for producing SNe Ia are not fully understood.
+Two general production channels have been proposed: in the single-degenerate (SD) case, the WD accretes mass from a close non-degenerate companion until it surpasses a mass of $\sim1.4$ M$_\odot$ and explodes.
+In the double-degenerate (DD) case, two WDs merge after a gravitational-wave inspiral or head-on collision.
+Recent observations have placed tight constraints on the SD channel, heavily disfavoring it as the main pathway for producing ``normal'' SNe Ia.
+Though it is now the preferred model, the DD channel faces issues of its own with matching observed SN Ia rates as well as the fact that not all WD mergers may lead to a thermonuclear explosion.
+
+The delay-time distribution (DTD) is the rate of SNe Ia which explode as a function of time after a hypothetical single star formation event.
+By convolving the DTD with the star formation rate (SFR) as a function of time, one can produce a function describing the time-variation in the SN Ia rate.
+
+Uncertainties in the progenitor channels of SNe Ia translate into uncertainties in the form of the DTD.
+
 Studies of galactic chemical evolution typically assume a single form for the SN Ia DTD.
@@
 
-Why radial migration is important for SNe Ia.
+% Why radial migration is important for SNe Ia.
+Core-collapse SNe explode on timescales of a few Myr, before the progenitor has a chance to migrate far from its birth location.
+On the other hand, SNe Ia have a broad distribution of delay times and their progenitors can migrate great distances between birth and explosion.
+The consequence is that SNe Ia can enrich regions of the Galaxy far removed from regions which have experienced a high rate of star formation.
 
@@
 They do not quantitatively favor one form over another (e.g., power-law over exponential).
+
+\citet{Greggio2005-AnalyticalRates} used analytical approximations of binary population synthesis to produce theoretical DTDs for the SD and DD channels.
 
@@
     \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different DTD models.
-All assume an inside-out SFH.
+All assume the early-burst SFH.
 Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.

### 2023-10-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+[Hook and intro paragraph]
 Galactic chemical evolution (GCE) studies seek to reproduce the observed distribution of metals throughout the Milky Way Galaxy.
 
+[Introduction to SNe Ia]
 Type Ia supernovae (SNe Ia), the explosions of carbon-oxygen white dwarfs (WDs), are responsible for roughly half of the iron produced in the Galaxy.
@@
 
+[What is the delay time distribution]
 The delay-time distribution (DTD) is the rate of SNe Ia which explode as a function of time after a hypothetical single star formation event.
@@
 
+[Analytical DTDs]
 Uncertainties in the progenitor channels of SNe Ia translate into uncertainties in the form of the DTD. 
+\citet{Greggio2005-AnalyticalRates} used analytical approximations of binary population synthesis to produce theoretical DTDs for the SD and DD channels.
+
+[Observational DTDs]
+\citet{Mannucci2005-SNRate} found that the SN Ia rate per unit mass has a strong dependence on host galaxy morphology and color.
+Using these results, \citet{Mannucci2006-TwoPopulations} obtain a best-fit model for the DTD which consists of both a prompt component ($<100$ Myr) and a long exponential tail.
+These studies all assume a particular form for the DTD and fit for the specific parameters.
+They do not quantitatively favor one form over another (e.g., power-law over exponential).
+
+[Why radial migration is important for SNe Ia]
+Core-collapse SNe explode on timescales of a few Myr, before the progenitor has a chance to migrate far from its birth location.
+On the other hand, SNe Ia have a broad distribution of delay times and their progenitors can migrate great distances between birth and explosion.
+The consequence is that SNe Ia can enrich regions of the Galaxy far removed from regions which have experienced a high rate of star formation.
+
+[Summary of DTDs used in simulations and theoretical studies].
+The Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations implement the DTD from \citet{Mannucci2006-TwoPopulations} (explain previously).
+Following \citet{Schonrich2009-RadialMixing}, \citet{Weinberg2017-ChemicalEquilibrium} assume an exponential DTD for the purposes of producing an analytical solution to the equations of chemical equilibrium, but they show that it can be extended to a double-exponential DTD which closely approximates a power-law.
 
@@
 
-% Why radial migration is important for SNe Ia.
-Core-collapse SNe explode on timescales of a few Myr, before the progenitor has a chance to migrate far from its birth location.
-On the other hand, SNe Ia have a broad distribution of delay times and their progenitors can migrate great distances between birth and explosion.
-The consequence is that SNe Ia can enrich regions of the Galaxy far removed from regions which have experienced a high rate of star formation.
+A few chemical evolution studies have compared DTDs with different functional forms.
+\citet{Palicio2023-AnalyticDTD} derive analytic solutions to one-zone chemical evolution equations for seven DTDs (three theoretical and four empirical), approximating the more complicated DTD functions as a linear combination of exponential, Gaussian, and power-law components.
+They predict observables such as abundance tracks and MDFs and compare to APOGEE, but comparisons are limited to the Solar neighborhood.
+\citet{Poulhazan2018-PrecisionPollution} investigate six different DTDs in a smoothed-particle hydrodynamics simulation, but they only present global results for the entire galaxy, they don't compare abundances throughout the disk, and they don't compare to observations.
 
-Summary of observational studies of the DTD.
-These studies all assume a particular form for the DTD and fit for the specific parameters.
-They do not quantitatively favor one form over another (e.g., power-law over exponential).
-
-\citet{Greggio2005-AnalyticalRates} used analytical approximations of binary population synthesis to produce theoretical DTDs for the SD and DD channels.
-
-Summary of DTDs used in simulations and theoretical studies.
-The Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations implement the DTD from \citet{Mannucci2006-TwoPopulations} (explain previously).
-Following \citet{Schonrich2009-RadialMixing}, \citet{Weinberg2017-ChemicalEquilibrium} assume an exponential DTD for the purposes of producing an analytical solution to the equations of chemical equilibrium, but they show that it can be extended to a double-exponential DTD which closely approximates a power-law.
-
-A few chemical evolution studies have compared DTDs with different functional forms.
-\citet{Poulhazan2018-PrecisionPollution} investigate six different DTDs in a smoothed-particle hydrodynamics simulation.
-\citet{Palicio2023-AnalyticDTD} derive analytic solutions to one-zone chemical evolution equations for seven DTDs (three theoretical and four empirical), approximating the more complicated DTD functions as a linear combination of exponential, Gaussian, and power-law components.
-
-Studies which have noted the [$\alpha$/Fe] bimodality: \citet{Furhmann1998-NearbyStars,Hayden2015-ChemicalCartography}.
+One curious chemical feature of the Milky Way disk is the existence of two populations separated by their [$\alpha$/Fe] abundance ratios.
+First noted by \citet{Furhmann1998-NearbyStars}, expanded by \citet{Hayden2015-ChemicalCartography}, definitely others too.
+The ``high-$\alpha$'' population is associated with the thick disk and contains stars with low enrichment from SNe Ia, so their abundance ratios reflect that of pure CCSN enrichment.
+The ``low-$\alpha$'' population is associated with the thin disk and contains stars with roughly solar $\alpha$-abundances.
 The origin of the [$\alpha$/Fe] bimodality is debated.
@@
 \citet{Spitoni2021-TwoInfall} (definitely earlier papers too) argue that two distinct infall episodes can explain the bimodality.
+What separates the two sequences is SN Ia enrichment, so the DTD ought to have some impact on the [$\alpha$/Fe] bimodality, perhaps even determining whether or not it exists.
+
+In this paper we comprehensively evaluate a selection of DTD models from the literature with multiple SFHs and a prescription for radial migration in the Versatile Integrator for Chemical Evolution (VICE).
+In Section \ref{sec:methods}, we present our models for the DTD and SFH, and we describe our chemical evolution simulations.
+In Section \ref{sec:onezone-results}, we present the results of our one-zone chemical evolution simulations.
+In Section \ref{sec:multizone-results}, we present the results of our multi-zone simulations and compare to observations.
+In Section \ref{sec:discussion}, we discuss the implications for the DTD and future surveys.
+In Section \ref{sec:conclusions}, we conclude.
 
@@
     \includegraphics[width=\linewidth]{figures/ofe_df_dtd.pdf}
-    \caption{Distributions of [O/Fe] from multi-zone simulations with different DTDs. In all cases an inside-out SFH is assumed. The plot format is similar to Figure \ref{fig:ofe-df-sfh}.}
+    \caption{Distributions of [O/Fe] from multi-zone simulations with different DTDs. In all cases an early-burst SFH is assumed. The plot format is similar to Figure \ref{fig:ofe-df-sfh}.}
     \label{fig:ofe-df-dtd}

### 2023-11-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \documentclass[modern,linenumbers]{aastex631}
+% \documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
 %twocolappendix
@@
 \usepackage{siunitx}
+\usepackage{xspace}
 
@@
 \newcommand{\osuaffil}{Department of Astronomy, The Ohio State University, 140 W. 18th Ave, Columbus OH 43210, USA}
+\newcommand{\aFe}{[$\alpha$/Fe]\xspace}
 
@@
 \begin{abstract}
-    Type Ia supernovae (SNe Ia) produce most of Fe-peak elements in the Universe and therefore are a crucial ingredient in galactic chemical evolution models.
+    Type Ia supernovae (SNe Ia) produce most of the Fe-peak elements in the Universe and therefore are a crucial ingredient in galactic chemical evolution models.
 SNe Ia do not explode immediately after star formation and the delay-time distribution (DTD) has not been definitively determined by supernova surveys or theoretical models.
-Because the DTD also affects the relationship among age, [Fe/H], and [$\alpha$/Fe] in chemical evolution models, comparison with observations of stars in the Milky Way is an important consistency check for any proposed DTD.
+Because the DTD also affects the relationship among age, [Fe/H], and \aFe in chemical evolution models, comparison with observations of stars in the Milky Way is an important consistency check for any proposed DTD.
 We implement several popular forms of the DTD in combination with multiple star formation histories for the Milky Way in one-zone and multi-zone chemical evolution models using the Versatile Integrator for Chemical Evolution (VICE).
@@
 We compare our predicted interstellar medium abundance tracks, stellar abundance distributions, and stellar age distributions to the 17th data release of the Apache Point Observatory Galactic Evolution Experiment (APOGEE).
-We find that the SN Ia DTD has the largest effect on the [$\alpha$/Fe] distribution: a DTD with more prompt SNe Ia produces a stellar abundance distribution that is skewed toward a lower [$\alpha$/Fe] ratio, whereas a DTD with more delayed SNe Ia produces a distribution that is skewed toward higher [$\alpha$/Fe].
-While the DTD alone cannot explain the observed bimodality in the [$\alpha$/Fe] distribution, in combination with an appropriate star formation history it affects the goodness of fit between the simulated and observed high-$\alpha$ sequence.
+We find that the SN Ia DTD has the largest effect on the \aFe distribution: a DTD with more prompt SNe Ia produces a stellar abundance distribution that is skewed toward a lower \aFe ratio, whereas a DTD with more delayed SNe Ia produces a distribution that is skewed toward higher \aFe.
+While the DTD alone cannot explain the observed bimodality in the \aFe distribution, in combination with an appropriate star formation history it affects the goodness of fit between the simulated and observed high-$\alpha$ sequence.
+Our model results favor a DTD with longer delay times and fewer prompt SNe Ia than the fiducial $t^{-1}$ power law.
 \end{abstract}
@@
 
-[Hook and intro paragraph]
-Galactic chemical evolution (GCE) studies seek to reproduce the observed distribution of metals throughout the Milky Way Galaxy.
+% [Hook and intro paragraph]
+Galactic chemical evolution studies seek to reproduce the observed distribution of metals as a function of age throughout the Milky Way Galaxy.
+\citet{Tinsley1979-StellarLifetimes} proposed that the non-Solar \aFe ratios seen by, e.g., \citet{Wallerstein1962-GDwarfAbundances} were caused by different stellar lifetimes for the contributors of the Fe-peak elements than the $\alpha$-elements.
+Type Ia supernovae (SNe Ia), the explosions of carbon-oxygen white dwarfs (WDs), are responsible for roughly half of the iron produced in the Galaxy [cite].
+SNe Ia have long been known to occur in elliptical galaxies, suggesting that their progenitors may have lifetimes of up to many Gyr.
+\citet{Tinsley1979-StellarLifetimes} assumed a range of $\sim 3\times 10^7 - 10^8$ years for the lifetimes of SN Ia progenitors, although they argued against the hypothesis that SNe Ia are exploding white dwarfs.
+\citet{Matteucci1986-SupernovaEnrichment} modeled SNe Ia as the end product of binary evolution and arrived at much longer lifetimes for the progenitors, finding that SNe Ia did not contribute substantially to chemical enrichment for $\sim 10^8$ years after the commencement of star formation.
+% [Concluding sentence about how understanding the DTD is important for chemical evolution and for understanding the progenitors of SNe Ia]
+The timescale for Fe enrichment in the Galaxy, a key component of chemical evolution models, is directly linked to the progenitor lifetimes of SNe Ia.
 
-[Introduction to SNe Ia]
-Type Ia supernovae (SNe Ia), the explosions of carbon-oxygen white dwarfs (WDs), are responsible for roughly half of the iron produced in the Galaxy.
-Despite their importance, the mechanism(s) for producing SNe Ia are not fully understood.
-Two general production channels have been proposed: in the single-degenerate (SD) case, the WD accretes mass from a close non-degenerate companion until it surpasses a mass of $\sim1.4$ M$_\odot$ and explodes.
-In the double-degenerate (DD) case, two WDs merge after a gravitational-wave inspiral or head-on collision.
-Recent observations have placed tight constraints on the SD channel, heavily disfavoring it as the main pathway for producing ``normal'' SNe Ia.
-Though it is now the preferred model, the DD channel faces issues of its own with matching observed SN Ia rates as well as the fact that not all WD mergers may lead to a thermonuclear explosion.
+% [What is the delay time distribution]
+The delay-time distribution (DTD) is the rate of SNe Ia which explode as a function of time after a hypothetical instantaneous star formation event.
+By convolving the DTD with the star formation rate (SFR) as a function of time, one can produce a function describing the time-variation in the SN Ia rate.
+Different models for the SN Ia progenitor have different DTDs.
 
-[What is the delay time distribution]
-The delay-time distribution (DTD) is the rate of SNe Ia which explode as a function of time after a hypothetical single star formation event.
-By convolving the DTD with the star formation rate (SFR) as a function of time, one can produce a function describing the time-variation in the SN Ia rate.
+% [Introduction to SNe Ia]
+% Type Ia supernovae (SNe Ia), the explosions of carbon-oxygen white dwarfs (WDs), are responsible for roughly half of the iron produced in the Galaxy [cite]. Despite their importance, 
+The mechanism(s) for producing SNe Ia are not fully understood \citep[for reviews, see][]{Maoz2014-Review,Livio2018-ProgenitorReview,Ruiter2020-ProgenitorReview}.
+Two general production channels have been proposed: in the single-degenerate (SD) case, the WD accretes mass from a close non-degenerate companion until it surpasses a mass of $\sim1.4$ M$_\odot$ and explodes \citep{Whelan1973-SDModel,Nomoto1982-SDModel,Yoon2003-SDModel}.
+In the double-degenerate (DD) case, two WDs merge after a gravitational-wave inspiral \citep{Iben1984-IaBinary,Webbink1984-DDModel,Pakmor2012-WDMerger} or head-on collision \citep{Benz1989-CollisionalDD,Thompson2011-CollisionalDD}.
+Recent observations have placed tight constraints on the SD channel, heavily disfavoring it as the main pathway for producing ``normal'' SNe Ia \citep[e.g.,][]{Panagia2006-RadioEmission,Schaefer2012-ExCompanionSNR,Chomiuk2016-RadioEmission,Fausnaugh2019-EarlyIaLightCurves,Tucker2020-SNeIaSpectra,Do2021-Progenitor1972E,Tucker2023-SN2011fe}.
+Though it is now the preferred model, the DD channel faces issues of its own with matching observed SN Ia rates because not all WD mergers may lead to a thermonuclear explosion \citep[e.g.,][]{Shen2012-DDMergers}.
 
@@
 Studies of galactic chemical evolution typically assume a single form for the SN Ia DTD.
-This is the first comprehensive look at the DTD in a multi-zone GCE model which includes the effects of radial migration.
+This is the first comprehensive look at the DTD in a multi-zone chemical evolution model which includes the effects of radial migration.
 
@@
 
-One curious chemical feature of the Milky Way disk is the existence of two populations separated by their [$\alpha$/Fe] abundance ratios.
+One curious chemical feature of the Milky Way disk is the existence of two populations separated by their \aFe abundance ratios at the same metallicity.
 First noted by \citet{Furhmann1998-NearbyStars}, expanded by \citet{Hayden2015-ChemicalCartography}, definitely others too.
-The ``high-$\alpha$'' population is associated with the thick disk and contains stars with low enrichment from SNe Ia, so their abundance ratios reflect that of pure CCSN enrichment.
+The ``high-$\alpha$'' population contains stars with low enrichment from SNe Ia, so their abundance ratios reflect that of pure CCSN enrichment; it is associated with the kinematically hot thick disk \citep{Bensby2003-AbundanceTrends}.
 The ``low-$\alpha$'' population is associated with the thin disk and contains stars with roughly solar $\alpha$-abundances.
-The origin of the [$\alpha$/Fe] bimodality is debated.
+The origin of the \aFe bimodality is debated.
 \citet{Schonrich2009-RadialMixing} argue that it arises due to radial migration (churning) even with a smooth star formation rate.
@@
 \citet{Spitoni2021-TwoInfall} (definitely earlier papers too) argue that two distinct infall episodes can explain the bimodality.
-What separates the two sequences is SN Ia enrichment, so the DTD ought to have some impact on the [$\alpha$/Fe] bimodality, perhaps even determining whether or not it exists.
+What separates the two sequences is the ratio of CCSN to SN Ia enrichment, so the DTD ought to have some impact on the \aFe bimodality, perhaps even determining whether or not it exists.
 
@@
 Plateau     & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
-Triple-system   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2022-TripleEvolution} \\
+Triple-system   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2023-TripleEvolution} \\
             & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
@@
 % where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
-A declining power-law with $\alpha\sim-1$ is a standard assumption in many observational studies of the DTD as well as GCE simulations.
+A declining power-law with $\alpha\sim-1$ is a standard assumption in many observational studies of the DTD as well as Galactic chemical evolution simulations.
 \citet{Maoz2017-CosmicDTD} obtain a DTD with $\alpha=-1.07\pm0.09$ based on volumetric rates and an assumed cosmic SFH for field galaxies in redshift range $0\leq z\leq 2.25$.
@@
 
-\paragraph{Triple-system} A DTD based on simulations of triple-system evolution by \citet{Rajamuthukumar2022-TripleEvolution}.
+\paragraph{Triple-system} A DTD based on simulations of triple-system evolution by \citet{Rajamuthukumar2023-TripleEvolution}.
 We approximate their DTD as a special case of the plateau model (Equation \ref{eq:plateau-dtd}) where the initial rate is quite low until an instantaneous rise to the plateau value at time $t_{\rm rise}$:
@@
 \end{equation}
-We investigate the case where $\tau=1.5$ Gyr, which has been used in previous GCE studies \citep[e.g.,][]{Schonrich2009-RadialMixing,Weinberg2017-ChemicalEquilibrium} and is similar to the analytical single-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
+We investigate the case where $\tau=1.5$ Gyr, which has been used in previous chemical evolution studies \citep[e.g.,][]{Schonrich2009-RadialMixing,Weinberg2017-ChemicalEquilibrium} and is similar to the analytical single-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
 We also investigate a longer timescale of $\tau=3$ Gyr.
@@
     \centering
-    \includegraphics[width=0.32\linewidth]{figures/onezone_powerlaw_slope.pdf}
-    \includegraphics[width=0.32\linewidth]{figures/onezone_exponential_timescale.pdf}
-    \includegraphics[width=0.32\linewidth]{figures/onezone_plateau_width.pdf}
+    \includegraphics[width=\linewidth]{figures/onezone_threepanel.pdf}
+    % \includegraphics[width=0.32\linewidth]{figures/onezone_powerlaw_slope.pdf}
+    % \includegraphics[width=0.32\linewidth]{figures/onezone_exponential_timescale.pdf}
+    % \includegraphics[width=0.32\linewidth]{figures/onezone_plateau_width.pdf}
     \caption{\textit{Left:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone chemical evolution models models which assume a power-law DTD.
@@
 
+One parameter of the DTD which we hold fixed in the multi-zone models is the minimum SN Ia delay time $t_D$.
+Typical choices for $t_D$ in the literature range from $\sim 40$ Myr to 150 Myr.
 The left-hand panel of Figure \ref{fig:onezone-twopanel} shows that the minimum SN Ia delay time has a much stronger effect on the abundance track and MDFs of models which assume a power-law DTD than models which assume a plateau or exponential DTD, due to the much higher SN Ia rate in the power-law models at early times (see Figure \ref{fig:dtds}).
 Moreover, a power-law DTD with a long minimum delay may be observationally hard to distinguish from a plateau model.
-In Figure \ref{fig:onezone-twopanel}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (red dashed line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (blue solid line), and the [O/Fe] distributions are virtually identical.
+In Figure \ref{fig:onezone-twopanel}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (dashed purple line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (solid green line), and the [O/Fe] distributions are virtually identical.
 
@@
     \centering
-    \includegraphics[width=0.49\linewidth]{figures/onezone_minimum_delay.pdf}
-    \includegraphics[width=0.49\linewidth]{figures/onezone_dtd.pdf}
+    \includegraphics[width=\linewidth]{figures/onezone_twopanel.pdf}
+    % \includegraphics[width=0.49\linewidth]{figures/onezone_minimum_delay.pdf}
+    % \includegraphics[width=0.49\linewidth]{figures/onezone_dtd.pdf}
     \caption{\textit{Left:} Comparison of one-zone models with minimum SN Ia delay times of 40 Myr (solid curves) and 150 Myr (dashed curves) for two DTDs: a power-law with $\alpha=-1.1$ (blue curves), and an exponential with $\tau=1.5$ Gyr (purple curves).
 The layout is similar to the plots in Figure \ref{fig:onezone-threepanel}.
+For clarity, we use a mass-loading factor $\eta=1$ for the exponential DTD run.
     \textit{Right:} Comparison of one-zone models which assume all five functional forms for the DTD in this paper: triple-system (green), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
@@
 
-The early-burst model produces a bimodal distribution of [O/Fe] even out to large radii and close to the midplane, whereas the APOGEE distribution does not show a prominent high-$\alpha$ peak beyond $R_{\rm{Gal}}\sim11$ kpc.
+The distribution of [O/Fe] serves as a record of the relative rates of SNe Ia and CCSNe.
+As such, the shape of the distribution is greatly affected by both the SFH and DTD.
+Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs, all assuming an exponential DTD with $\tau=1.5$ Gyr, compared to the distributions measured by APOGEE.
+We see similar trends with Galactic region across all four simulations.
+Near the midplane, the distributions at the innermost and outermost annuli are similar, but away from the midplane, there is a clear trend of a higher average stellar [O/Fe] at small $R_{\rm gal}$ and lower [O/Fe] at large $R_{\rm gal}$.
 
-Away from the midplane, there is a clear trend of a higher average stellar [O/Fe] at small $R_{\rm gal}$ and lower [O/Fe] at large $R_{\rm gal}$.
-However, the APOGEE data show a clear dichotomy between inner-galaxy, high-$\alpha$ stars and outer-galaxy, low-$\alpha$ stars, with few in between.
-In the inside-out and late-burst SFHs, the shift from high-$\alpha$ to low-$\alpha$ is much more gradual and the trough at [O/Fe]$\approx0.2$ does not appear.
-The two-infall SFH appears to produce \textit{three} modes, at [O/Fe]$\approx 0.0$, $0.2$, and $0.4$, with the first and last showing the most variation with $R_{\rm gal}$ at high latitudes.
+While trends with $R_{\rm gal}$ and $|z|$ are similar, the shape of the distribution varies greatly with the chosen SFH.
+The inside-out and late-burst models produce similar distributions because of the similarity of their underlying SFHs \textemdash both skew heavily toward near-Solar [O/Fe], although the late-burst model produces a slightly broader peak and a less-prominent high-[O/Fe] tail.
+The only region which shows any significant skew toward high [O/Fe] is $R_{\rm gal}=3-5$ kpc and $|z|=1-2$ kpc, but the shift to higher [O/Fe] at high latitudes is gradual and does not produce the notable trough at [O/Fe]$\approx0.2$ which is seen in the APOGEE data.
+
+On the other hand, the early-burst model produces a bimodal distribution of [O/Fe] even out to large radii and close to the midplane, whereas the APOGEE distribution does not show a prominent high-$\alpha$ peak beyond $R_{\rm{Gal}}\sim11$ kpc.
 The early-burst SFH produces the closest match to the data by far: the low-$\alpha$ sequence away from the midplane shows increasing contribution with larger radii, with the innermost radii containing very few low-$\alpha$ stars.
 However, the high-$\alpha$ sequence contains substantial contribution from stars at large radii, which is not seen in the data.
+
+The two-infall SFH model produces \textit{three} distinct modes at [O/Fe]$\approx 0.0$, $0.2$, and $0.4$.
+At small $R_{\rm gal}$ and with increasing $|z|$, the low-$\alpha$ peak decreases in prominence and the high-$\alpha$ peak increases, but the intermediate peak is a striking feature at all latitudes which is at odds with the APOGEE data.
 
@@
 
-Figure \ref{fig:ofe-df-dtd} shows [O/Fe] distributions from simulations with the same SFH but a variety of different DTDs.
+Figure \ref{fig:ofe-df-dtd} shows [O/Fe] distributions produced by simulations with the same SFH but a range of different DTDs.
 We choose the early-burst SFH because it produces distinct high- and low-$\alpha$ sequences, which makes the effect of the DTD on the former more apparent.
 The most apparent effect of the DTD is to shift the mode of the high-$\alpha$ sequence.
-The two-population DTD, which has the most prompt SNe Ia of any model in this paper, places the high-$\alpha$ sequence at [O/Fe]$\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places $\sim0.2$ dex higher at [O/Fe]$\approx0.4$.
+The two-population DTD, which has the most prompt SNe Ia of any model in this paper, places the high-$\alpha$ sequence at [O/Fe]$\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.2$ dex higher at [O/Fe]$\approx0.4$.
+This metric alone would seem to favor the exponential ($\tau=1.5$ Gyr) or plateau ($W=0.3$ Gyr; not shown) models; however,
 
@@
 \begin{acknowledgments}
+    [Personal acknowledgements]
+
     Funding for the Sloan Digital Sky 
@@
     participating in the {\it Gaia} Multilateral Agreement.
+
+    [Ohio State \& Carnegie land acknowledgements]
+
+    [David and Jennifer NSF grant]
 

### 2023-12-11 src/scripts/delay_time_distributions.py
add median delay time indicators

@@ -16,13 +16,19 @@ def main(style='paper'):
     plt.style.use(paths.styles / f'{style}.mplstyle')
     plt.rcParams['axes.prop_cycle'] = plt.cycler('color', paultol.bright.colors)
     fig, ax = setup_axes()
-    times = [t*0.001 for t in range(40, 13200)]
+    times = np.arange(0.04, 13.2, 0.001)
     distributions = [styles.prompt, styles.plaw, styles.exp, 
                      styles.plateau_long, styles.triple]
     for dtd in distributions:
         func = dtd['func']
-        ax.plot(times, [func(t) / func(1) for t in times], 
+        yvals = np.array([func(t) for t in times])
+        ax.plot(times, yvals / func(1.), 
                 label=dtd['label'], c=dtd['color'], ls=dtd['line'])
+        # indicate median delay times
+        cdf = np.cumsum(yvals / np.sum(yvals))
+        med_idx = np.where(cdf >= 0.5)[0][0]
+        med = times[med_idx]
+        ax.scatter(med, 5e-3, c=dtd['color'], s=10, marker='o')
     ax.set_ylim((3e-3, 3e2))
     # Plot the SDSS-II DTD recovered by Maoz et al. (2012), MNRAS 426, 3282
     # (see their Table 2)

### 2023-12-11 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Title
-\title{The Galactic Delay-Time Distribution of Type Ia Supernovae:\\
-       A Chemical Evolution Perspective}
+% \title{The Galactic Delay-Time Distribution of Type Ia Supernovae:\\
+%        A Chemical Evolution Perspective}
+\title{Galactic Chemical Evolution Simulations Favor Long Delay Times for Type Ia Supernovae}
 
@@
 \citet{Mannucci2005-SNRate} found that the SN Ia rate per unit mass has a strong dependence on host galaxy morphology and color.
-Using these results, \citet{Mannucci2006-TwoPopulations} obtain a best-fit model for the DTD which consists of both a prompt component ($<100$ Myr) and a long exponential tail.
+Using these results, \citet{Mannucci2006-TwoPopulations} obtained a best-fit model for the DTD which consists of both a prompt component ($<100$ Myr) and a long exponential tail.
 These studies all assume a particular form for the DTD and fit for the specific parameters.
@@
 The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD} at the same scale as the DTD models.
-The horizontal and vertical error bars indicate the time range and 1$\sigma$ uncertainties, respectively, of each DTD measurement.}
+The horizontal and vertical error bars indicate the time range and 1$\sigma$ uncertainties, respectively, of each DTD measurement.
+The colored circles along the horizontal axis indicate the median delay time for each model in the same order as the legend.}
     \label{fig:dtds}
@@
 Figure \ref{fig:ofe-feh-sfh} compares the [O/Fe]--[Fe/H] plane in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) between our four model SFHs.
+All simulations presented in this figure assume an exponential DTD model with $\tau=1.5$ Gyr, as it lies in the middle in terms of balance between prompt and delayed SNe Ia.
+The black curves represent the ISM abundance as a function of time in the central zone; in the absence of radial migration, all simulated stellar populations would lie along these lines.
+Stars to the left of the abundance tracks were born in the outer disk, while stars to the right of the tracks were born in the inner disk, as evidenced by the color-coding in the figure.
+
+The inside-out and late-burst models produce similar results, the main difference being a slightly broader core of the abundance distribution around [O/Fe]$\approx0.05$ dex.
+The Gaussian burst in SFH in the late-burst model introduces a loop in the ISM abundance track, where an uptick in star formation at $t\approx11$ Gyr raises the CCSN rate, leading to a slight increase in [O/Fe] before the subsequent increase in the SN Ia rate brings it back down.
+This same pattern is seen much more strongly in the abundance tracks for the two-infall model: here, the significant infall of pristine gas at $t=4$ Gyr leads to rapid dilution of the ISM, followed by a large burst in the SFR which raises [O/Fe] by $\sim 0.2$ dex.
+In this case the second infall produces a ``ridge line'' in the abundance distribution at [O/Fe]$\approx 0.2$.
+Finally, the early-burst model shows the clearest separation between a high-[O/Fe] track which follows the ISM abundance from low metallicities, and a low-[O/Fe] sequence composed of stars with a wide range of birth radii.
+The early-burst model sees a higher density of points which closely follow the ISM track at [Fe/H]$\lesssim 0.5$ which is likely the result of an increased SFR at early times relative to the other models.
 
@@
 \end{figure}
+
+Figure \ref{fig:ofe-feh-dtd} compares [O/Fe]--[Fe/H] distributions for five simulations with the same SFH (inside-out) but different DTD models.
+We choose the inside-out SFH model for this figure because it produces a monotonically-decreasing abundance track, making comparisons between the different DTD models relatively straightforward.
+We note that in this model, both the low- and high-$\alpha$ sequences are composed of stars with a wide range of birth $R_{\rm gal}$.
+The simulation results are arranged so that from left to right the fraction of prompt SNe Ia decreases and the mean delay time increases.
+Results for the two-population and power-law ($\alpha$=-1.1) DTD models, with a large fraction of prompt SNe Ia, are presented in the first and second columns, respectively.
+For these models, the simulated stellar abundances are reasonably well-aligned with the APOGEE contours at low $|z|$ (bottom panels), but they entirely miss the observed high-$\alpha$ sequence at high $|z|$ (top panels).
+In the center column, the exponential ($\tau=1.5$ Gyr) DTD produces a distribution which aligns quite well with the APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to large [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
+While it does better at populating the high-$\alpha$ sequence than the previous DTD models, the bulk of the simulated populations at large $|z|$ still fall below the APOGEE 30\% contour (top panel).
+The two right-hand columns present simulation results for the plateau ($W=1$ Gyr) and triple-system DTD models,
 

### 2023-12-11 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 We note that in this model, both the low- and high-$\alpha$ sequences are composed of stars with a wide range of birth $R_{\rm gal}$.
-The simulation results are arranged so that from left to right the fraction of prompt SNe Ia decreases and the mean delay time increases.
+The simulation results are arranged by increasing median delay time from left to right.
 Results for the two-population and power-law ($\alpha$=-1.1) DTD models, with a large fraction of prompt SNe Ia, are presented in the first and second columns, respectively.
@@
 While it does better at populating the high-$\alpha$ sequence than the previous DTD models, the bulk of the simulated populations at large $|z|$ still fall below the APOGEE 30\% contour (top panel).
-The two right-hand columns present simulation results for the plateau ($W=1$ Gyr) and triple-system DTD models,
+The two right-hand columns present simulation results for the plateau ($W=1$ Gyr) and triple-system DTD models, which have the longest median delay times.
+The high-$\alpha$ ``knee'' occurs at a much higher metallicity in these models and is visible in the gas abundance tracks in the upper-left corner of the panels.
+At high $|z|$, the simulated abundance align quite well with the APOGEE high-$\alpha$ sequence (top panels), but there is a significant ridge of high-$\alpha$ stars from the inner Galaxy at low $|z|$ (bottom panels).
 
@@
 \label{sec:age-ofe}
+
+Figure \ref{fig:age-ofe-sfh} compares the stellar age and [O/Fe] distributions in the Solar neighborhood between our four SFH models.
+Similar to Figure \ref{fig:ofe-feh-sfh}, all four panels assume an exponential DTD model with $\tau=1.5$ Gyr.
+We include age data from \citet{Leung2023-Ages} for qualitative comparison, though we caution against drawing strong conclusions because we don't correct for selection effects or systematics in the neural net ages.
+The inside-out and late-burst models show fair agreement with the data at high [O/Fe], although both show a $\sim2$ Gyr offset to older ages.
+One could shift the ramp-up in star formation to slightly later times or simply run the simulation for a shorter amount of time to close this gap.
+Like the data, the trend in the median age with decreasing [O/Fe] decreases monotonically in the inside-out model.
+The late-burst model, however, shows a bump in the distribution around a lookback time of $\sim2$ Gyr driven by the Gaussian SFR burst, which is not seen in the data, as noted by \citet{Johnson2021-Migration}.
+Neither model produces a significant amount of stars below Solar [O/Fe], in contrast to the data.
+
+For the early-burst SFH model, the simulated stellar ages are almost perfectly aligned with the data for [O/Fe]$\gtrsim 0.2$.
+The rapid rise in the SFE at early times delays the descent to lower [O/Fe] values and produces a clump of low-metallicity, high-[O/Fe] stars at an age of $\sim10$ Gyr.
+The early-burst model produces a sharp transition between a linear relationship between [O/Fe] and age for stars older than $\sim5$ Gyr and a flat relationship for the younger stars, and it too misses the lowest [O/Fe] bin in the data.
+Finally, the two-infall SFH model produces the closest overall agreement between the simulated and observed median ages.
+Stars with [O/Fe]$\gtrsim 0.25$ were produced in the first infall, while the second infall produces a clump of stars with similar metallicity, ages of $\sim8$ Gyr, and [O/Fe]$\approx0.2$.
+There is an interesting small population of very old, low-$\alpha$ stars which is not seen in any of the other models.
+The two-infall model is the only one which plateaus at sub-Solar [O/Fe] for the youngest stars, leading to a very good match to the observed data at low [O/Fe].
 

### 2024-01-16 src/scripts/distribution_functions.py
adjust |z| bin labels

@@ -12,7 +12,8 @@ from _globals import ABSZ_BINS, GALR_BINS
 
 
 def plot_multizone_mdfs(mzs, axs, col='[fe/h]', colors=[], label='VICE', 
-                        galr_bins=GALR_BINS, absz_bins=ABSZ_BINS, **kwargs):
+                        galr_bins=GALR_BINS, absz_bins=ABSZ_BINS, 
+                        titlepad=18, **kwargs):
     """
     Plot [Fe/H] MDFs from a VICE multizone run.
     
@@ -29,6 +30,8 @@ def plot_multizone_mdfs(mzs, axs, col='[fe/h]', colors=[], label='VICE',
         Title for this column of axes. The default is 'VICE'.
     galr_bins: list of floats, optional
     absz_bins: list of floats, optional
+    titlepad: int, optional
+        Vertical padding for axes title. The default is 18.
     **kwargs passed to MultizoneStars.mdf()
     """
     if len(colors) != len(galr_bins) - 1:
@@ -42,13 +45,14 @@ def plot_multizone_mdfs(mzs, axs, col='[fe/h]', colors=[], label='VICE',
                 mdf, bin_edges = subset.mdf(col, **kwargs)
                 ax.plot(get_bin_centers(bin_edges), mdf, 
                         color=colors[j], linewidth=1)
-        axs[0].set_title(label, va='top', pad=18)
+        axs[0].set_title(label, va='top', pad=titlepad)
     else:
         raise ValueError('Mismatch between number of axes and |z|-height bins.')
 
 
 def plot_apogee_mdfs(data, axs, col='FE_H', colors=[], label='APOGEE', 
-                     galr_bins=GALR_BINS, absz_bins=ABSZ_BINS, **kwargs):
+                     galr_bins=GALR_BINS, absz_bins=ABSZ_BINS, 
+                     titlepad=18, **kwargs):
     """
     Plot [Fe/H] MDFs from the APOGEE sample.
     
@@ -65,6 +69,8 @@ def plot_apogee_mdfs(data, axs, col='FE_H', colors=[], label='APOGEE',
         Title for this column of axes. The default is 'APOGEE'.
     galr_bins: list of floats, optional
     absz_bins: list of floats, optional
+    titlepad: int, optional
+        Vertical padding for axes title. The default is 18.
     **kwargs passed to apogee_mdf()
     """
     if len(colors) != len(galr_bins) - 1:
[…]

### 2024-01-16 src/scripts/feh_df_comparison.py

@@ -35,7 +35,7 @@ def main():
                               figure_width=_globals.TWO_COLUMN_WIDTH, 
                               cmap_name=CMAP, xlabel='[Fe/H]', xlim=FEH_LIM, 
                               major_tick_spacing=0.5, cbar_width=0.4)
-    fig.subplots_adjust(top=0.9, left=0.07, right=0.98)
+    fig.subplots_adjust(top=0.9, left=0.04, right=0.96)
     colors = get_color_list(plt.get_cmap(CMAP), _globals.GALR_BINS)
     # plot varying SFH, constant DTD
     mdf_kwargs = {'bins': NBINS, 'range': FEH_LIM, 'smoothing': SMOOTH_WIDTH}

### 2024-01-16 src/scripts/ofe_bimodality_summary.py

@@ -23,7 +23,6 @@ LINESTYLES = ['--', '-']
 GALR_LIM = (7, 9)
 ABSZ_LIM = (0, 2)
 SMOOTH_WIDTH = 0.05
-TITLE_SIZE = 11
 
 SFH_LIST = ['insideout', 'lateburst', 'earlyburst', 'twoinfall']
 SFH_LABELS = ['Inside-out', 'Late-burst', 'Early-burst', 'Two-infall']
@@ -41,6 +40,7 @@ DTD_LABELS = ['Two-population',
 def main():
     plt.style.use(paths.styles / 'paper.mplstyle')
     figwidth = TWO_COLUMN_WIDTH
+    title_size = plt.rcParams['figure.titlesize']
     # create subfigures for top and bottom rows
     # fig = plt.figure(layout='constrained', figsize=(figwidth, figwidth*0.4))
     # subfigs = fig.subfigures(2, 1, hspace=0.1)
@@ -72,7 +72,7 @@ def main():
         plot_bimodality(axs[0,i], output_name, apogee_subset, uncertainties=True)
     axs[0,0].set_ylabel('Normalized PDF')
     fig.text(0.51, 0.98, 'Late-burst SFH',
-             ha='center', va='top', size=TITLE_SIZE)
+             ha='center', va='top', size=title_size)
     # axs[0,0].set_ylabel('Late-burst SFH')
     
     print('Plotting SFHs...')
@@ -82,7 +82,7 @@ def main():
         plot_bimodality(axs[1,j], output_name, apogee_subset, uncertainties=True)
     axs[1,0].set_ylabel('Normalized PDF')
     fig.text(0.42, 0.5, 'Exponential DTD ($\\tau=1.5$ Gyr)',
-             ha='center', va='top', size=TITLE_SIZE)
+             ha='center', va='top', size=title_size)
     # axs[1,0].set_ylabel('Exponential DTD\n($\\tau=1.5$ Gyr)')
         
     # Plot APOGEE
@@ -96,7 +96,7 @@ def main():
         mdf /= mdf.max()
         bin_centers = get_bin_centers(bin_edges)
         axs[1,-1].plot(bin_centers, mdf, ls=LINESTYLES[i], label=feh_bin, c=COLORS[i])
-    axs[1,-1].set_title('APOGEE', pad=8, size=TITLE_SIZE)
+    axs[1,-1].set_title('APOGEE', pad=8, size=title_size)
     
     for ax in axs[-1]:
         ax.set_xlabel('[O/Fe]')

### 2024-01-16 src/scripts/ofe_df_dtd.py

@@ -51,7 +51,7 @@ def main(style='paper'):
                               cmap_name=CMAP, xlabel='[O/Fe]', xlim=OFE_LIM, 
                               major_tick_spacing=0.2, major_minor_tick_ratio=4.,
                               cbar_width=cbar_width)
-    fig.subplots_adjust(top=0.9, left=0.08, right=0.98, bottom=0.25)
+    fig.subplots_adjust(top=0.9, left=0.04, right=0.96, bottom=0.25)
     colors = get_color_list(plt.get_cmap(CMAP), _globals.GALR_BINS)
     # plot
     mdf_kwargs = {'bins': NBINS, 'range': OFE_LIM, 'smoothing': SMOOTH_WIDTH}

### 2024-01-16 src/scripts/ofe_df_sfh.py

@@ -31,7 +31,7 @@ def main():
                               cmap_name=CMAP, xlabel='[O/Fe]', xlim=OFE_LIM, 
                               major_tick_spacing=0.2, major_minor_tick_ratio=4.,
                               cbar_width=0.4)
-    fig.subplots_adjust(top=0.9, left=0.07, right=0.98)
+    fig.subplots_adjust(top=0.92, left=0.04, right=0.96, bottom=0.23)
     colors = get_color_list(plt.get_cmap(CMAP), _globals.GALR_BINS)
     # plot
     mdf_kwargs = {'bins': NBINS, 'range': OFE_LIM, 'smoothing': SMOOTH_WIDTH}

### 2024-01-16 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Define document class
-\documentclass[modern,linenumbers]{aastex631}
-% \documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
+% \documentclass[modern,linenumbers]{aastex631}
+\documentclass[twocolumn,twocolappendix,linenumbers,trackchanges]{aastex631}
 %twocolappendix
@@
 % [Hook and intro paragraph]
-Galactic chemical evolution studies seek to reproduce the observed distribution of metals as a function of age throughout the Milky Way Galaxy.
-\citet{Tinsley1979-StellarLifetimes} proposed that the non-Solar \aFe ratios seen by, e.g., \citet{Wallerstein1962-GDwarfAbundances} were caused by different stellar lifetimes for the contributors of the Fe-peak elements than the $\alpha$-elements.
-Type Ia supernovae (SNe Ia), the explosions of carbon-oxygen white dwarfs (WDs), are responsible for roughly half of the iron produced in the Galaxy [cite].
+Galactic chemical evolution studies seek to explain the observed distribution of metals %as a function of age 
+throughout the Milky Way Galaxy. \citet{Tinsley1979-StellarLifetimes} proposed that the non-Solar \aFe\footnote{
+    In standard bracket notation, $[X/Y]\equiv \log_{10}(X/Y) - \log_{10}(X/Y)_{\odot}$.
+In this work we will use \aFe and [O/Fe] interchangeably, although observational studies will often use a combination of $\alpha$-elements to calculate \aFe.
+} ratios seen by, e.g., \citet{Wallerstein1962-GDwarfAbundances} were caused by different stellar lifetimes for the contributors of the Fe-peak elements than the $\alpha$-elements.
+Type Ia supernovae (SNe Ia), the explosions of carbon-oxygen white dwarfs (WDs), are responsible for a majority of the Fe produced in the Galaxy \citep{Matteucci1986-SupernovaEnrichment}; meanwhile, core collapse supernovae (CCSNe), the explosions of massive stars, produce the $\alpha$-elements (e.g., O and Mg) in addition to a smaller fraction of Fe.
 SNe Ia have long been known to occur in elliptical galaxies, suggesting that their progenitors may have lifetimes of up to many Gyr.
-\citet{Tinsley1979-StellarLifetimes} assumed a range of $\sim 3\times 10^7 - 10^8$ years for the lifetimes of SN Ia progenitors, although they argued against the hypothesis that SNe Ia are exploding white dwarfs.
-\citet{Matteucci1986-SupernovaEnrichment} modeled SNe Ia as the end product of binary evolution and arrived at much longer lifetimes for the progenitors, finding that SNe Ia did not contribute substantially to chemical enrichment for $\sim 10^8$ years after the commencement of star formation.
-% [Concluding sentence about how understanding the DTD is important for chemical evolution and for understanding the progenitors of SNe Ia]
+% \citet{Tinsley1979-StellarLifetimes} assumed a range of $\sim 3\times 10^7 - 10^8$ years for the lifetimes of SN Ia progenitors, although they argued against the hypothesis that SNe Ia are exploding white dwarfs.
+\citet{Matteucci1986-SupernovaEnrichment} modeled SNe Ia as the end product of binary evolution and %arrived at much longer lifetimes for the progenitors, finding 
+concluded that SNe Ia did not contribute substantially to chemical enrichment for $\sim 10^8$ years after the commencement of star formation.
 The timescale for Fe enrichment in the Galaxy, a key component of chemical evolution models, is directly linked to the progenitor lifetimes of SNe Ia.
+Therefore, the balance of SN rates over time regulates the relative abundances of the $\alpha$-elements and Fe as a function of stellar age. [Better concluding sentence]
 
 % [What is the delay time distribution]
-The delay-time distribution (DTD) is the rate of SNe Ia which explode as a function of time after a hypothetical instantaneous star formation event.
-By convolving the DTD with the star formation rate (SFR) as a function of time, one can produce a function describing the time-variation in the SN Ia rate.
-Different models for the SN Ia progenitor have different DTDs.
+SNe Ia are delayed by $\sim10^8 - 10^{10}$ years after the formation of their progenitors as a result of their stellar and binary evolution.
+The delay-time distribution (DTD) is the rate of SNe Ia which explode as a function of time after the formation of a hypothetical unit-mass single stellar population.
+When the DTD is convolved with the Galactic star formation rate (SFR) as a function of time, it yields the SN Ia rate as a function of time.
+The DTD controls the delay between chemical enrichment from CCSNe, which explode on timescales of a few Myr (smaller than the timestep size of many chemical evolution simulations), and SNe Ia.
+As such, it is a key parameter in the chemical evolution of the Galaxy.
+The DTD reflects the evolution of the SNe Ia progenitor systems, so different models for the progenitors of SNe Ia will naturally predict different forms for the DTD.
 
 % [Introduction to SNe Ia]
-% Type Ia supernovae (SNe Ia), the explosions of carbon-oxygen white dwarfs (WDs), are responsible for roughly half of the iron produced in the Galaxy [cite]. Despite their importance, 
 The mechanism(s) for producing SNe Ia are not fully understood \citep[for reviews, see][]{Maoz2014-Review,Livio2018-ProgenitorReview,Ruiter2020-ProgenitorReview}.
@@
 
-[Analytical DTDs]
+% [Analytical DTDs]
 Uncertainties in the progenitor channels of SNe Ia translate into uncertainties in the form of the DTD.
-\citet{Greggio2005-AnalyticalRates} used analytical approximations of binary population synthesis to produce theoretical DTDs for the SD and DD channels.
+\citet{Greggio2005-AnalyticalRates} formulated analytical DTDs for several progenitor models; she found that the SD channel tends to produce a steeper DTD function than the DD channel, and the median delay time can vary by a factor of 10 depending on the chosen progenitor scenario and its particular parameters.
 
@@
 
-[Why radial migration is important for SNe Ia]
+% [Why radial migration is important for SNe Ia]
+A complicating factor in observing and modeling the effects of the DTD is the migration of stars throughout the disk.
+\citet{SellwoodBinney2002-RadialMixing} first demonstrated that a transient spiral perturbation (or other potential feature; see [citations]) can cause resonant interactions which adjust stars' guiding center radii without leading to kinematic heating of the disk.
 Core-collapse SNe explode on timescales of a few Myr, before the progenitor has a chance to migrate far from its birth location.
@@
 The consequence is that SNe Ia can enrich regions of the Galaxy far removed from regions which have experienced a high rate of star formation.
+The first GCE model to incorporate radial mixing was developed by \citet{Schonrich2009-RadialMixing}, and subsequent studies have incorporated more comprehensive numerical treatments of radial migration and the effect of a central bar \citep[e.g.,][]{Minchev2013-ChemodynamicalEvolution}.
+In this paper, we follow the treatment by \citet{Johnson2021-Migration}, who [describe treatment].
 
@@
 
-In this paper we comprehensively evaluate a selection of DTD models from the literature with multiple SFHs and a prescription for radial migration in the Versatile Integrator for Chemical Evolution (VICE).
+In this paper we comprehensively evaluate a selection of DTD models from the literature with multiple SFHs and a prescription for radial migration in the Versatile Integrator for Chemical Evolution \citep[VICE;][]{JohnsonWeinberg2020-Starbursts}.
 In Section \ref{sec:methods}, we present our models for the DTD and SFH, and we describe our chemical evolution simulations.
@@
 \label{sec:methods}
+
+We make use of the multi-zone simulation tools in VICE developed by \citet{Johnson2021-Migration}.
+The basic setup of our models follows theirs: the simulated Galaxy is a disk with a radius of 20 kpc and is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
+The gas in each ring is assumed to be instantaneously mixed, and no gas is exchanged between rings.
+We run our simulations with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
+Following \citet{Johnson2021-Migration}, we set VICE to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_*=0$ for $R_{\rm gal}>R_{\rm SF}$.
+
+Table \ref{tab:multizone-parameters} summarizes many of the parameters in our multi-zone models.
 
@@
         % Multi-zone simulation parameters
-        R_{\rm gal}     & [0, 20] kpc   & & Galactocentric radius \\
-        \delta R_{\rm gal}  & 100 pc    & & Width of each concentric ring \\
+        R_{\rm gal}     & [0, 20] kpc   & \ref{sec:methods} & Galactocentric radius \\
+        \delta R_{\rm gal}  & 100 pc    & \ref{sec:methods} & Width of each concentric ring \\
         \Delta R_{\rm gal}  & N/A       & \ref{app:migration} & Change in orbital radius due to stellar migration \\
@@
         p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
-        \Delta t        & 10 Myr    & & Time-step size \\
-        t_{\rm max}     & 13.2 Gyr  & & Maximum simulation time \\
-        n               & 8         & & Number of stellar populations formed per ring per time-step \\
-        R_{\rm Ia}(t)   & Equations \ref{eq:powerlaw-dtd}--\ref{eq:triple-dtd}  & \ref{sec:dtd-models}  & Delay time distribution of Type Ia supernovae \\
+        \Delta t        & 10 Myr    & \ref{sec:methods} & Time-step size \\
+        t_{\rm max}     & 13.2 Gyr  & \ref{sec:methods} & Maximum simulation time \\
+        n               & 8         & \ref{sec:methods} & Number of stellar populations formed per ring per time-step \\
+        R_{\rm SF}      & 15.5 kpc  & \ref{sec:methods} & Maximum radius of star formation \\
+        M_{\rm gas,0}   & 0         & \ref{sec:sfh}     & Initial gas mass \\
+        % DTD
+        R_{\rm Ia}(t)   & Equations \ref{eq:powerlaw-dtd}--\ref{eq:prompt-dtd}  & \ref{sec:dtd-models}  & Delay time distribution of Type Ia supernovae \\
         t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
-        M_{\rm gas,0}   & 0         & & Initial gas mass \\
+        N_{\rm Ia}/M_*  & $2.2\times10^{-3}$ M$_\odot^{-1}$ & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \citep{MaozMannucci2012-SNeIaReview} \\
         % Nucleosynthetic yields
-        y_{\rm O}^{\rm CC}  & 0.015     & & CCSN yield of O    \\
-        y_{\rm Fe}^{\rm CC} & 0.0012    & & CCSN yield of Fe   \\
-        y_{\rm O}^{\rm Ia}  & 0         & & SN Ia yield of O       \\
-        y_{\rm Fe}^{\rm Ia} & 0.00214   & & SN Ia yield of Fe \\
-        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & & Time-dependence of the SFR in the inside-out model \\
-        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & & Time-dependence of the SFR in the late-burst model \\
-        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & & Time-dependence of the IFR in the early-burst model \\
-        \uptau_{*,\rm EB}(t|R_{\rm gal})  & Equation \ref{eq:earlyburst-conroy22} & & Time-dependence of the SFE timescale in the early-burst model \\
-        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & & Time-dependence of the IFR in the two-infall model \\
+        y_{\rm O}^{\rm CC}  & 0.015     & \ref{sec:yields}  & CCSN yield of O    \\
+        y_{\rm Fe}^{\rm CC} & 0.0012    & \ref{sec:yields}  & CCSN yield of Fe   \\
+        y_{\rm O}^{\rm Ia}  & 0         & \ref{sec:yields}  & SN Ia yield of O       \\
+        y_{\rm Fe}^{\rm Ia} & 0.00214   & \ref{sec:yields}  & SN Ia yield of Fe \\
+        % Star formation histories
+        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & \ref{sec:sfh} & Time-dependence of the SFR in the inside-out model \\
+        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the SFR in the late-burst model \\
+        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the IFR in the early-burst model \\
+        \uptau_{*,\rm EB}(t|R_{\rm gal})  & Equation \ref{eq:earlyburst-conroy22} & \ref{sec:sfh}   & Time-dependence of the SFE timescale in the early-burst model \\
+        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the IFR in the two-infall model \\
     \enddata
@@
 
+\subsection{Nucleosynthetic Yields}
+\label{sec:yields}
+
+CCSN enrichment:
+\begin{equation}
+    \dot M_x^{\rm CC} = y_x^{\rm CC} \dot M_*
+    \label{eq:ccsn-enrichment}
+\end{equation}
+where $y_x^{\rm CC}$ is the CCSN yield of element $x$ per unit mass of star formation.
+Following \citet{Johnson2021-Migration}, who in turn adopt their yields from \citet{Weinberg2017-ChemicalEquilibrium}, we adopt $y_{\rm O}^{\rm CC}=0.015$ and $y_{\rm Fe}^{\rm CC}=0.0012$.
+
+We follow the formalism of \citet{Weinberg2017-ChemicalEquilibrium} when deriving the equations for Fe enrichment from SNe Ia.
+
+$R_{\rm Ia}(t)$ is the DTD in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$.
+
+The rate of Fe contribution to the ISM from SNe Ia is 
+\begin{equation}
+    \dot M_{\rm Fe}^{\rm Ia} = y_{\rm Fe}^{\rm Ia} \langle \dot M_*\rangle_{\rm Ia} \\
+\end{equation}
+where $\langle \dot M_*\rangle_{\rm Ia}$ is the time-averaged SFR weighted by the DTD and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia.
+\citet{Weinberg2017-ChemicalEquilibrium} show in their Appendix A that
+\begin{equation}
+    \langle \dot M_*\rangle_{\rm Ia} \equiv \frac{\int_0^t \dot M_*(t')R_{\rm Ia}(t-t')dt'}{\int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt'}
+    \label{eq:weighted-sfr}
+\end{equation}
+where $\dot M_*(t)$ is the SFR at time $t$, $R_{\rm Ia}(t) dt$ is the number of SNe Ia which explode in the time interval $(t, t+dt)$ per unit mass of stars formed at $t=0$, $t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the maximum simulation time.
+The denominator of Equation \ref{eq:weighted-sfr} is therefore the total number of SNe Ia per M$_{\odot}$ of stars formed.
+
+The yield $y_{\rm Fe}^{\rm Ia}$ measures the mass of Fe produced by SNe Ia per unit mass of star formation. It can be expressed in terms of the integral of the DTD:
+\begin{equation}
+    y_{\rm Fe}^{\rm Ia} = m_{\rm Fe}^{\rm Ia} \int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt' = m_{\rm Fe}^{\rm Ia} \frac{N_{\rm Ia}}{M_*}
+    \label{eq:dtd-integral}
+\end{equation}
+where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia.
+We take the average number of SNe Ia per mass of stars formed to be $N_{\rm Ia}/M_*=2.2\times10^{-3}\,{\rm M}_\odot^{-1}$ following \citet{MaozMannucci2012-SNeIaReview}, which gives $R_{\rm Ia}$ units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$.
+Following \citet{Johnson2021-Migration}, we take $y_{\rm Fe}^{\rm Ia}=0.00214$.
+SNe Ia do not contribute O so $y_{\rm O}^{\rm Ia}=0$.
+
 \subsection{DTD Models}
 \label{sec:dtd-models}
-
-\begin{subequations}
-\begin{align}
-    \dot M_{\rm Fe}^{\rm Ia} &= y_{\rm Fe}^{\rm Ia} \langle \dot M_*\rangle_{\rm Ia} \\
-    &= y_{\rm Fe}^{\rm Ia} \frac{\int_0^t \dot M_*(t')R_{\rm Ia}(t-t')dt'}{\int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt'}
-\end{align}
-\end{subequations}
-
-The yield $y_{\rm Fe}^{\rm Ia}$ can be expressed in terms of the integral of the DTD:
-
-\begin{equation}
-    y_{\rm Fe}^{\rm Ia} = m_{\rm Fe}^{\rm Ia} \int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt' = m_{\rm Fe}^{\rm Ia} \frac{N_{\rm Ia}}{M_*}
-    \label{eq:dtd-integral}
-\end{equation}
-where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia.
-We take the average number of SNe Ia per mass of stars formed to be $N_{\rm Ia}/M_*=2.2\times10^{-3}\,{\rm M}_\odot^{-1}$ following \citet{MaozMannucci2012-SNeIaReview}, which gives $R_{\rm Ia}$ units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$.
 
@@
 The horizontal and vertical error bars indicate the time range and 1$\sigma$ uncertainties, respectively, of each DTD measurement.
-The colored circles along the horizontal axis indicate the median delay time for each model in the same order as the legend.}
+The colored circles along the horizontal axis indicate the median delay time for each model.}
     \label{fig:dtds}
@@
 
-\begin{deluxetable*}{lll}
+\begin{deluxetable*}{lcll}
 \tablecaption{Summary of SN Ia DTD models explored in this paper.\label{tab:dtds}}
 \tablehead{
-\colhead{Model} & \colhead{Parameters} & \colhead{Similar to}
+\colhead{Model} & \colhead{Eq.} & \colhead{Parameters} & \colhead{Similar to}
 }
 \startdata
-Power-law   & $\alpha=-1.1$                 & \citet[][field]{Maoz2017-CosmicDTD}; 
+Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.1$                 & \citet[][field]{Maoz2017-CosmicDTD}; 
                                               \citet{Wiseman2021-DESRates}              \\
-Power-law   & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
+Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
                                               \citet{Heringer2019-FieldGalaxyDTD}       \\
-Plateau     & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
-Plateau     & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
-Triple-system   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2023-TripleEvolution} \\
-            & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
-Exponential & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
+Plateau     & \ref{eq:plateau-dtd}  & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
+Plateau     & \ref{eq:plateau-dtd}  & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
+Triple-system   & \ref{eq:triple-dtd}   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2023-TripleEvolution} \\
+                &                       & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
+Exponential & \ref{eq:exponential-dtd}  & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
                                                               \citet{Schonrich2009-RadialMixing};       \\
-            &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
-Exponential & $\tau=3.0$ Gyr    & --- \\
-Two-population  & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
-            & $\tau=3.0$ Gyr & \\
+            &                           &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
+Exponential & \ref{eq:exponential-dtd}   & $\tau=3.0$ Gyr    & --- \\
+Two-population  & \ref{eq:prompt-dtd}   & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
+                &                       & $\tau=3.0$ Gyr & \\
 \enddata
@@
 The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$  and $\tau_*$ and the other two quantities follow.
+All models have an initial gas mass $M_{\rm gas,0} = M_{\rm gas}(t=0) = 0$ in all zones.
 
@@
 
+% [Intro paragraph, motivation for running one-zone models]
+Before running the full multi-zone simulations, it will be useful to observe the effects of the DTD in more idealized conditions.
+A one-zone model assumes the entire gas reservoir is instantaneously mixed, so there is no spacial dependence for the distribution of metal abundances.
+In this section
+
 All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=0.01$ Gyr.
-We adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citep[see Equation 8 from][]{Johnson2021-Migration}, a star formation efficiency timescale $\tau_*\equiv M_{\rm gas}/\dot M_*=2$ Gyr, and an initial gas mass $M_{\rm gas,0}=0$.
+We adopt the inside-out star formation rate (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr), a star formation efficiency timescale $\tau_*\equiv M_{\rm gas}/\dot M_*=2$ Gyr, and an initial gas mass $M_{\rm gas,0}=0$.
 We adopt a continuous recycling prescription \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
-Unless otherwise specified, we adopt the inside-out star formation rate (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr), and a minimum SN Ia delay time of 40 Myr.
+Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citep[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time of 40 Myr.
 A summary of these one-zone fiducial parameters is presented in Table \ref{tab:onezone-parameters}.
-
 \begin{deluxetable}{Ccl}
@@
     \dot M_*(t)     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
-    \tau_{\rm rise} & 2 Gyr     & SFR rise timescale \\
+    \tau_{\rm rise} & 2.0 Gyr     & SFR rise timescale \\
     \tau_{\rm sfh}  & 15.1 Gyr  & SFR exponential timescale
@@
 
-Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in the middle panel of Figure \ref{fig:onezone-threepanel}.
-Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around 1 Gyr.
-A short exponential timescale shifts this knee down to lower [O/Fe] values, while a longer timescale raises it.
-The effect on the [O/Fe] distribution is similar to the power-law slope: a short timescale produces more low-$\alpha$ stars, while a long timescale produces more high-$\alpha$ stars (but still a unimodal distribution).
-The effect on the [Fe/H] distribution is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values.
-A doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
-
 \begin{figure*}
@@
     \includegraphics[width=\linewidth]{figures/onezone_threepanel.pdf}
-    % \includegraphics[width=0.32\linewidth]{figures/onezone_powerlaw_slope.pdf}
-    % \includegraphics[width=0.32\linewidth]{figures/onezone_exponential_timescale.pdf}
-    % \includegraphics[width=0.32\linewidth]{figures/onezone_plateau_width.pdf}
     \caption{\textit{Left:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone chemical evolution models models which assume a power-law DTD.
@@
 
+Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in the middle panel of Figure \ref{fig:onezone-threepanel}.
+Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around a simulation time of 1 Gyr.
+A short exponential timescale shifts this knee down to lower [O/Fe] values, while a longer timescale raises it.
+The effect on the [O/Fe] distribution is similar to the power-law slope: a short timescale produces more low-$\alpha$ stars, while a long timescale produces more high-$\alpha$ stars (but still a unimodal distribution).
+The effect on the [Fe/H] distribution is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values.
+A doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
+For all exponential models, the low-$\alpha$ peak sits approximately 0.02 dex lower than for the power-law models.
+
+Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of the plateau DTD model width on abundance tracks and distributions.
+The effect on the [O/Fe] distribution is similar to the previous two models: a longer plateau raises the median delay time, resulting in a smaller low-$\alpha$ peak and a more prominent high-$\alpha$ tail.
+The abundance tracks from several different plateau widths fill the space in between the exponential ($\tau=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
+The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\tau=3$ Gyr), although the [O/Fe] distributions are somewhat more distinct.
+
 One parameter of the DTD which we hold fixed in the multi-zone models is the minimum SN Ia delay time $t_D$.
@@
 In Figure \ref{fig:onezone-twopanel}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (dashed purple line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (solid green line), and the [O/Fe] distributions are virtually identical.
-
-A 150 Myr minimum delay time is incompatible with the two-population DTD model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD as its relative SN Ia rate is so low at early times.
-
-The right-hand panel of Figure \ref{fig:onezone-twopanel} compares the one-zone model outputs from the full range of DTDs we investigate in this paper.
-In general, the choice of DTD has the greatest effect on the location of the knee in [Fe/H]-[O/Fe] space (center panel) and the high-$\alpha$ end of the distribution of [O/Fe] (right panel).
-The DTD also has a smaller effect on the MDF in the range $-1.5\lesssim$ [Fe/H] $\lesssim-0.5$ (top panel).
+The difference between the two values of $t_D$ for the exponential ($\tau=3$ Gyr) DTD in both the abundance tracks and distributions is nearly indistinguishable.
+We do not consider the effect on the other DTD models because a 150 Myr minimum delay time is incompatible with the two-population model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD due to its low SN Ia rate at short delay times.
 
@@
     \includegraphics[width=\linewidth]{figures/onezone_twopanel.pdf}
-    % \includegraphics[width=0.49\linewidth]{figures/onezone_minimum_delay.pdf}
-    % \includegraphics[width=0.49\linewidth]{figures/onezone_dtd.pdf}
     \caption{\textit{Left:} Comparison of one-zone models with minimum SN Ia delay times of 40 Myr (solid curves) and 150 Myr (dashed curves) for two DTDs: a power-law with $\alpha=-1.1$ (blue curves), and an exponential with $\tau=1.5$ Gyr (purple curves).
@@
 \end{figure*}
+
+The right-hand panel of Figure \ref{fig:onezone-twopanel} compares the one-zone model outputs from the full range of DTD models we investigate in this work.
+The choice of DTD primarily affects the location of the high-$\alpha$ ``knee'' in the [Fe/H]--[O/Fe] abundance tracks.
+At one extreme is the triple-system model, which sees the CC SN plateau extend up to [Fe/H]$\approx0.8$ followed by a sharp downward turn as the SN Ia rate suddenly increases at a delay time of 500 Myr.
+Star formation proceeds for such a long time before the knee that the [O/Fe] distribution shows a slight second peak around the CC SN value; this model is the only one which produces any amount of bimodality in the one-zone simulations.
+At the other extreme are the two-population and power-law ($\alpha=-1.1$) models which peak immediately after the minimum delay time of 40 Myr, placing the knee at [Fe/H]$\approx-1.8$.
+The two-population model has a unique second knee at [Fe/H]$\sim-0.2$ and [O/Fe]$\sim0.1$, which is a result of the delayed exponential component.
+The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models lie in the intermediate space between these extremes.
+On the other hand, the [O/Fe] distribution from the exponential model is the most strongly peaked at the Solar value, while the plateau ($W=1$ Gyr) and triple-system models produce nearly identical distributions in the low-$\alpha$ regime.
+The exponential ($\tau=3$ Gyr) and plateau ($W=0.3$ Gyr) models, while not shown, produce similar abundance tracks to the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models, respectively.
+
+[Summary and conclusions from one-zone models]
 
@@
 
+[Subsection introduction]
+Section \ref{sec:onezone-results} and specifically Figures \ref{fig:onezone-threepanel} and \ref{fig:onezone-twopanel} illustrated the effect of the DTD models and parameters on [O/Fe]--[Fe/H] tracks in idealized one-zone models.
+
 Figure \ref{fig:ofe-feh-sfh} compares the [O/Fe]--[Fe/H] plane in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) between our four model SFHs.
@@
 
+[Subsection introduction]
+
 Figure \ref{fig:age-ofe-sfh} compares the stellar age and [O/Fe] distributions in the Solar neighborhood between our four SFH models.
@@
 Neither model produces a significant amount of stars below Solar [O/Fe], in contrast to the data.
-
-For the early-burst SFH model, the simulated stellar ages are almost perfectly aligned with the data for [O/Fe]$\gtrsim 0.2$.
-The rapid rise in the SFE at early times delays the descent to lower [O/Fe] values and produces a clump of low-metallicity, high-[O/Fe] stars at an age of $\sim10$ Gyr.
-The early-burst model produces a sharp transition between a linear relationship between [O/Fe] and age for stars older than $\sim5$ Gyr and a flat relationship for the younger stars, and it too misses the lowest [O/Fe] bin in the data.
-Finally, the two-infall SFH model produces the closest overall agreement between the simulated and observed median ages.
-Stars with [O/Fe]$\gtrsim 0.25$ were produced in the first infall, while the second infall produces a clump of stars with similar metallicity, ages of $\sim8$ Gyr, and [O/Fe]$\approx0.2$.
-There is an interesting small population of very old, low-$\alpha$ stars which is not seen in any of the other models.
-The two-infall model is the only one which plateaus at sub-Solar [O/Fe] for the youngest stars, leading to a very good match to the observed data at low [O/Fe].
 
@@
 
+For the early-burst SFH model, the simulated stellar ages are almost perfectly aligned with the data for [O/Fe]$\gtrsim 0.2$.
+The rapid rise in the SFE at early times delays the descent to lower [O/Fe] values and produces a clump of low-metallicity, high-[O/Fe] stars at an age of $\sim10$ Gyr.
+The early-burst model produces a sharp transition between a linear relationship between [O/Fe] and age for stars older than $\sim5$ Gyr and a flat relationship for the younger stars, and it too misses the lowest [O/Fe] bin in the data.
+Finally, the two-infall SFH model produces the closest overall agreement between the simulated and observed median ages.
+Stars with [O/Fe]$\gtrsim 0.25$ were produced in the first infall, while the second infall produces a clump of stars with similar metallicity, ages of $\sim8$ Gyr, and [O/Fe]$\approx0.2$.
+There is an interesting small population of very old, low-$\alpha$ stars which is not seen in any of the other models.
+The two-infall model is the only one which plateaus at sub-Solar [O/Fe] for the youngest stars, leading to a very good match to the observed data at low [O/Fe].
+
+Figure \ref{fig:age-ofe-dtd} similarly plots the simulated distributions in age--[O/Fe] space for five of our DTD models.
+All simulations were run with the early-burst SFH model because the high-$\alpha$ sequence was distinct in metallicity space in Figure \ref{fig:age-ofe-sfh}.
+Similar to Figure \ref{fig:ofe-feh-dtd}, simulations are arranged from left to right by increasing median SN Ia delay time.
+Moving from left to right, the high-$\alpha$ sequence moves to higher [O/Fe] with increasing median delay time, from $\sim0.4$ for the two-population model to $\sim0.4$ for the triple-system DTD.
+As we have seen in previous figures, the range in [O/Fe] produced by the models on the left is much smaller than for the models on the right.
+At high $|z|$ (top row), the observed range of [O/Fe] is larger than produced by any of our simulations, although the plateau ($W=1$ Gyr) and triple-system models come close.
+While the other three fall short of the observed range in [O/Fe], they more closely match the median age--[O/Fe] relation.
+There is a slight reversal in the observed trend for the stars with the highest [O/Fe]: the $0.45\leq{\rm [O/Fe]}<0.5$ bin has a slightly \textit{lower} median age than the $0.3\leq{\rm [O/Fe]}<0.35$ bin at high $|z|$ in the \citet{Leung2023-Ages} sample, a small effect but one which is not observed in any of our simulation results.
+
 \begin{figure*}
@@
 
+Moving to stars at low $|z|$, our plateau ($W=1$ Gyr) and triple-system DTDs over-produce stars at the old, high-$\alpha$ end of the distribution, while also diverging significantly from the observed sequence near solar [O/Fe].
+The exponential ($\tau=1.5$ Gyr) DTD comes closest to reproducing the observed range in [O/Fe], while the two DTDs with the shortest median delay time once again produce a smaller range of [O/Fe] than observed.
+We note that the break between the linear and flat parts of the relation is sharpest for the exponential DTD, and a more gradual transition is observed for the other four DTD models.
+This could be because the exponential DTD is most dominant at intermediate delay times ($\tau\sim 1-3$ Gyr) but falls off much faster than the other models at long delay times, so the evolution of [O/Fe] is quite slow for lookback times $\lesssim 5$ Gyr.
+Overall, the exponential ($\tau=1.5$ Gyr) DTD most closely matches the data for stars with $0\leq|z|<1$ kpc.
+
 \section{Discussion}
@@
 In this case, $P$ is the APOGEE DF, $Q$ is the model DF, and $x$ is either [Fe/H] or [O/Fe].
-For each model SFH and DTD, we compute $D_{\rm{KL}}$ in 18 different Galactocentric regions: bins in $R_{\rm gal}$ of $3-5$ kpc, $5-7$ kpc, $7-9$ kpc, $9-11$ kpc, $11-13$ kpc, and $13-15$ kpc, and bins in $|z|$ of $0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
+For each model SFH and DTD, we compute $D_{\rm{KL}}$ in 18 different Galactocentric regions: 2 kpc-wide bins in $R_{\rm gal}$ between 3 and 15 kpc, and bins in $|z|$ of $0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
 The KL divergence for the entire model is taken to be the average of $D_{\rm{KL}}$ for each region weighted by the number of APOGEE stars in that region.

### 2024-01-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \documentclass[twocolumn,twocolappendix,linenumbers,trackchanges]{aastex631}
-%twocolappendix
 
@@
 
-\shorttitle{Galactic SN Ia DTD}
+\shorttitle{SN Ia DTD in GCE Simulations}
 \shortauthors{Dubay, Johnson, \& Johnson}
+% \linespread{1.8}
 
@@
 %        A Chemical Evolution Perspective}
-\title{Galactic Chemical Evolution Simulations Favor Long Delay Times for Type Ia Supernovae}
+\title{Galactic Chemical Evolution Models Favor Extended Type Ia Supernova Delay-Time Distributions}
 
@@
 \author[0000-0002-6534-8783]{James W. Johnson}
-\affiliation{\osuaffil}
+% \affiliation{\osuaffil}
 \affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
@@
 VICE includes a prescription for radial stellar migration in multi-zone models.
-We compare our predicted interstellar medium abundance tracks, stellar abundance distributions, and stellar age distributions to the 17th data release of the Apache Point Observatory Galactic Evolution Experiment (APOGEE).
+We compare our predicted interstellar medium abundance tracks, stellar abundance distributions, and stellar age distributions to the final data release of the Apache Point Observatory Galactic Evolution Experiment (APOGEE).
 We find that the SN Ia DTD has the largest effect on the \aFe distribution: a DTD with more prompt SNe Ia produces a stellar abundance distribution that is skewed toward a lower \aFe ratio, whereas a DTD with more delayed SNe Ia produces a distribution that is skewed toward higher \aFe.
@@
 % [Hook and intro paragraph]
-Galactic chemical evolution studies seek to explain the observed distribution of metals %as a function of age 
-throughout the Milky Way Galaxy. \citet{Tinsley1979-StellarLifetimes} proposed that the non-Solar \aFe\footnote{
+Galactic chemical evolution (GCE) studies seek to explain the observed distribution of metals throughout the Milky Way Galaxy.
+One curious chemical feature of the Milky Way disk is the existence of two populations separated by their \aFe\footnote{
     In standard bracket notation, $[X/Y]\equiv \log_{10}(X/Y) - \log_{10}(X/Y)_{\odot}$.
 In this work we will use \aFe and [O/Fe] interchangeably, although observational studies will often use a combination of $\alpha$-elements to calculate \aFe.
-} ratios seen by, e.g., \citet{Wallerstein1962-GDwarfAbundances} were caused by different stellar lifetimes for the contributors of the Fe-peak elements than the $\alpha$-elements.
-Type Ia supernovae (SNe Ia), the explosions of carbon-oxygen white dwarfs (WDs), are responsible for a majority of the Fe produced in the Galaxy \citep{Matteucci1986-SupernovaEnrichment}; meanwhile, core collapse supernovae (CCSNe), the explosions of massive stars, produce the $\alpha$-elements (e.g., O and Mg) in addition to a smaller fraction of Fe.
-SNe Ia have long been known to occur in elliptical galaxies, suggesting that their progenitors may have lifetimes of up to many Gyr.
-% \citet{Tinsley1979-StellarLifetimes} assumed a range of $\sim 3\times 10^7 - 10^8$ years for the lifetimes of SN Ia progenitors, although they argued against the hypothesis that SNe Ia are exploding white dwarfs.
-\citet{Matteucci1986-SupernovaEnrichment} modeled SNe Ia as the end product of binary evolution and %arrived at much longer lifetimes for the progenitors, finding 
-concluded that SNe Ia did not contribute substantially to chemical enrichment for $\sim 10^8$ years after the commencement of star formation.
-The timescale for Fe enrichment in the Galaxy, a key component of chemical evolution models, is directly linked to the progenitor lifetimes of SNe Ia.
-Therefore, the balance of SN rates over time regulates the relative abundances of the $\alpha$-elements and Fe as a function of stellar age. [Better concluding sentence]
+} abundance ratios at similar metallicity. 
+\citet{Tinsley1979-StellarLifetimes} first[?] proposed that the non-Solar \aFe ratios seen by, e.g., \citet{Wallerstein1962-GDwarfAbundances} were caused by different stellar lifetimes for the contributors of the Fe-peak elements than the $\alpha$-elements.
+Type Ia supernovae (SNe Ia), the thermonuclear explosions of carbon-oxygen white dwarfs (WDs), are responsible for most of the Fe produced in the Galaxy \citep{Matteucci1986-SupernovaEnrichment}; meanwhile, core collapse supernovae (CCSNe), the explosions of massive stars, produce the $\alpha$-elements (e.g., O and Mg) in addition to a smaller fraction of Fe.
+SNe Ia are delayed by $\sim10^8 - 10^{10}$ years after star formation events, as evidenced by observations at large distances from star forming regions and in elliptical galaxies \citep[e.g.,][]{Maza1976-SNStatistics}.
+This delayed enrichment leads to a decrease in \aFe with increasing [Fe/H] \citep{Matteucci1986-SupernovaEnrichment}.
+% The decrease in \aFe with [Fe/H] has long been understood to be a consequence of the delayed nature of SNe Ia, which do not contribute substantially to chemical enrichment for $\sim 10^8$ years after the commencement of star formation \citep{Tinsley1979-StellarLifetimes,Matteucci1986-SupernovaEnrichment}.
+% As SNe Ia are a product of intermediate-mass stars which undergo binary evolution, they do not contribute substantially to chemical enrichment for $\sim 10^8$ years after the commencement of star formation \citep{Matteucci1986-SupernovaEnrichment}.
+% The timescale for Fe enrichment in the Galaxy, a key component of chemical evolution models, is directly linked to the progenitor lifetimes of SNe Ia. 
+Therefore, the relative abundances of the $\alpha$-elements and Fe as a function of stellar age trace the balance of SN rates over time.
 
 % [What is the delay time distribution]
-SNe Ia are delayed by $\sim10^8 - 10^{10}$ years after the formation of their progenitors as a result of their stellar and binary evolution.
-The delay-time distribution (DTD) is the rate of SNe Ia which explode as a function of time after the formation of a hypothetical unit-mass single stellar population.
+The rate of SNe Ia which explode as a function of time after the formation of a hypothetical unit-mass single stellar population is known as the delay-time distribution (DTD).
 When the DTD is convolved with the Galactic star formation rate (SFR) as a function of time, it yields the SN Ia rate as a function of time. 
-The DTD controls the delay between chemical enrichment from CCSNe, which explode on timescales of a few Myr (smaller than the timestep size of many chemical evolution simulations), and SNe Ia.
-As such, it is a key parameter in the chemical evolution of the Galaxy.
-The DTD reflects the evolution of the SNe Ia progenitor systems, so different models for the progenitors of SNe Ia will naturally predict different forms for the DTD.
+The quantitative details of the relationship between \aFe and [Fe/H] are set by the DTD, and as such it is a key parameter in GCE models.
+The DTD remains poorly constrained, however, because it reflects the detailed evolution of the SNe Ia progenitor systems, so different models for the progenitors of SNe Ia will naturally predict different forms for the DTD.
 
@@
 The mechanism(s) for producing SNe Ia are not fully understood \citep[for reviews, see][]{Maoz2014-Review,Livio2018-ProgenitorReview,Ruiter2020-ProgenitorReview}. 
-Two general production channels have been proposed: in the single-degenerate (SD) case, the WD accretes mass from a close non-degenerate companion until it surpasses a mass of $\sim1.4$ M$_\odot$ and explodes \citep{Whelan1973-SDModel,Nomoto1982-SDModel,Yoon2003-SDModel}.
+Two general production channels have been proposed: in the single-degenerate (SD) case, the WD accretes mass from a close non-degenerate companion until it surpasses $\sim1.4$ M$_\odot$ and explodes \citep{Whelan1973-SDModel,Nomoto1982-SDModel,Yoon2003-SDModel}.
 In the double-degenerate (DD) case, two WDs merge after a gravitational-wave inspiral \citep{Iben1984-IaBinary,Webbink1984-DDModel,Pakmor2012-WDMerger} or head-on collision \citep{Benz1989-CollisionalDD,Thompson2011-CollisionalDD}.
-Recent observations have placed tight constraints on the SD channel, heavily disfavoring it as the main pathway for producing ``normal'' SNe Ia \citep[e.g.,][]{Panagia2006-RadioEmission,Schaefer2012-ExCompanionSNR,Chomiuk2016-RadioEmission,Fausnaugh2019-EarlyIaLightCurves,Tucker2020-SNeIaSpectra,Do2021-Progenitor1972E,Tucker2023-SN2011fe}.
-Though it is now the preferred model, the DD channel faces issues of its own with matching observed SN Ia rates because not all WD mergers may lead to a thermonuclear explosion \citep[e.g.,][]{Shen2012-DDMergers}.
-
-% [Analytical DTDs]
-Uncertainties in the progenitor channels of SNe Ia translate into uncertainties in the form of the DTD.
-\citet{Greggio2005-AnalyticalRates} formulated analytical DTDs for several progenitor models; she found that the SD channel tends to produce a steeper DTD function than the DD channel, and the median delay time can vary by a factor of 10 depending on the chosen progenitor scenario and its particular parameters.
-
-[Observational DTDs]
-\citet{Mannucci2005-SNRate} found that the SN Ia rate per unit mass has a strong dependence on host galaxy morphology and color.
+Searches for signs of interaction between the SN ejecta and a non-degenerate companion \citep[e.g.,][]{Panagia2006-RadioEmission,Chomiuk2016-RadioEmission,Fausnaugh2019-EarlyIaLightCurves,Tucker2020-SNeIaSpectra} or for a surviving non-degenerate companion \citep[e.g.,][]{Schaefer2012-ExCompanionSNR,Do2021-Progenitor1972E,Tucker2023-SN2011fe} have placed tight constraints on the SD channel, heavily disfavoring it as the main pathway for producing ``normal'' SNe Ia.
+The DD channel, now the preferred model, faces issues of its own with matching observed SN Ia rates because not all WD mergers may lead to a thermonuclear explosion \citep[e.g.,][]{NomotoIben1985-DDMergers,SaioNomoto1998-DDMergers,Shen2012-DDMergers}, and the progenitor systems are difficult to detect even within our own Galaxy \citep{RebassaMansergas2019-WhereAreDDProgenitors}.
+
+% [Theoretical DTDs]
+Uncertainties in the progenitor channels of SNe Ia translate into uncertainties in the shape of the DTD. 
+% By formulating analytical DTDs for several progenitor models, \citet{Greggio2005-AnalyticalRates} found that the SD channel tends to produce a steeper DTD function than the DD channel, and the median delay time (by which 50\% of SNe Ia have exploded) can vary by a factor of 10 depending on the chosen progenitor scenario and its particular parameters.
+For the DD channel, arguments about the distribution of post-common envelope separations and the rate of gravitational wave inspiral suggest a broad $\sim t^{-1}$ DTD at long delay times ($\gtrsim 1$ Gyr), but at short delays ($\lesssim 1$ Gyr) the rate is limited by the need to produce two WDs \citep[see Section 3.5 from][]{Maoz2014-Review}.
+Higher-order progenitor systems could also produce a $t^{-1}$ DTD \citep{Fang2018-QuadrupleSystems,Rajamuthukumar2023-TripleEvolution}.
+The DTD which would result from the SD channel depends greatly on the assumptions of binary population synthesis, but in general is expected to cover a narrower range of delay times and may feature a steep exponential cutoff at the long end \citep[e.g.,][]{Greggio2005-AnalyticalRates}.
+% More recently, \citet{Rajamuthukumar2023-TripleEvolution} computed a DTD from the evolution of triple system progenitors.
+[Expand, connect binary evolution to delay times, look for other theory papers]
+
+% [Observational DTDs]
+Surveys of SNe Ia have provided the primary observational constraints on the DTD.  
+This can be done by comparing the observed rate of SNe Ia to their host galaxy parameters \citep[e.g.,][]{Mannucci2005-SNRate,Heringer2019-FieldGalaxyDTD} or inferred star formation histories \citep[SFHs; e.g.,][]{Maoz2012-SloanIIDTD}, measuring SN Ia rates in galaxy clusters \citep[e.g.,][]{Maoz2010-ClusterDTD}, or comparing the volumetric SN Ia rate to the cosmic SFH as a whole \citep[e.g.,][]{Graur2014-VolumetricSNIaRates,Strolger2020-ExponentialDTD}.
+Early studies, which had limited sample sizes, produced unimodal \citep{Strolger2004-SNIaProgenitors} or bimodal \citep{Mannucci2006-TwoPopulations} DTDs where the majority of SNe Ia explode within a relatively narrow range of delay times.
+More recent studies have recovered broader DTD functions, with many converging on a declining power-law of $\sim t^{-1}$ \citep[e.g.,][]{Maoz2017-CosmicDTD,Castrillo2021-DTD,Wiseman2021-DESRates}, though there is some evidence for a steeper slope in galaxy clusters \citep{Maoz2017-CosmicDTD,FriedmannMaoz2018-ClusterDTD}.
+It is especially difficult to constrain the DTD for short delay times \citep{MaozMannucci2012-SNeIaReview} because of the need for SN Ia rates at long lookback times and uncertainties in the age estimates of stellar populations.
+
+% Notes on observational DTDs:
+% \citet{Strolger2004-SNIaProgenitors} analyzed 42 SNe Ia with redshifts $0.2<z<1.6$ and favored a delayed ($\gtrsim2$ Gyr) narrow Gaussian DTD while disfavoring exponentially declining models with a large fraction of prompt SNe Ia.
+% \citet{Mannucci2005-SNRate} found that the SN Ia rate per unit mass has a strong dependence on host galaxy morphology and color.
 Using these results, \citet{Mannucci2006-TwoPopulations} obtained a best-fit model for the DTD which consists of both a prompt component ($<100$ Myr) and a long exponential tail.
-These studies all assume a particular form for the DTD and fit for the specific parameters.
-They do not quantitatively favor one form over another (e.g., power-law over exponential).
-
-% [Why radial migration is important for SNe Ia]
-A complicating factor in observing and modeling the effects of the DTD is the migration of stars throughout the disk.
-\citet{SellwoodBinney2002-RadialMixing} first demonstrated that a transient spiral perturbation (or other potential feature; see [citations]) can cause resonant interactions which adjust stars' guiding center radii without leading to kinematic heating of the disk.
-Core-collapse SNe explode on timescales of a few Myr, before the progenitor has a chance to migrate far from its birth location.
-On the other hand, SNe Ia have a broad distribution of delay times and their progenitors can migrate great distances between birth and explosion.
-The consequence is that SNe Ia can enrich regions of the Galaxy far removed from regions which have experienced a high rate of star formation.
-The first GCE model to incorporate radial mixing was developed by \citet{Schonrich2009-RadialMixing}, and subsequent studies have incorporated more comprehensive numerical treatments of radial migration and the effect of a central bar \citep[e.g.,][]{Minchev2013-ChemodynamicalEvolution}.
-In this paper, we follow the treatment by \citet{Johnson2021-Migration}, who [describe treatment].
-
-[Summary of DTDs used in simulations and theoretical studies].
-The Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations implement the DTD from \citet{Mannucci2006-TwoPopulations} (explain previously).
-Following \citet{Schonrich2009-RadialMixing}, \citet{Weinberg2017-ChemicalEquilibrium} assume an exponential DTD for the purposes of producing an analytical solution to the equations of chemical equilibrium, but they show that it can be extended to a double-exponential DTD which closely approximates a power-law.
-
-Studies of galactic chemical evolution typically assume a single form for the SN Ia DTD.
-This is the first comprehensive look at the DTD in a multi-zone chemical evolution model which includes the effects of radial migration.
-
-A few chemical evolution studies have compared DTDs with different functional forms.
-\citet{Palicio2023-AnalyticDTD} derive analytic solutions to one-zone chemical evolution equations for seven DTDs (three theoretical and four empirical), approximating the more complicated DTD functions as a linear combination of exponential, Gaussian, and power-law components.
-They predict observables such as abundance tracks and MDFs and compare to APOGEE, but comparisons are limited to the Solar neighborhood.
-\citet{Poulhazan2018-PrecisionPollution} investigate six different DTDs in a smoothed-particle hydrodynamics simulation, but they only present global results for the entire galaxy, they don't compare abundances throughout the disk, and they don't compare to observations.
-
-One curious chemical feature of the Milky Way disk is the existence of two populations separated by their \aFe abundance ratios at the same metallicity.
-First noted by \citet{Furhmann1998-NearbyStars}, expanded by \citet{Hayden2015-ChemicalCartography}, definitely others too.
-The ``high-$\alpha$'' population contains stars with low enrichment from SNe Ia, so their abundance ratios reflect that of pure CCSN enrichment; it is associated with the kinematically hot thick disk \citep{Bensby2003-AbundanceTrends}.
-The ``low-$\alpha$'' population is associated with the thin disk and contains stars with roughly solar $\alpha$-abundances.
-The origin of the \aFe bimodality is debated.
-\citet{Schonrich2009-RadialMixing} argue that it arises due to radial migration (churning) even with a smooth star formation rate.
-\citet{Johnson2021-Migration} use a smooth SFR and a prescription for radial migration but are unable to reproduce the bimodality.
-\citet{Spitoni2021-TwoInfall} (definitely earlier papers too) argue that two distinct infall episodes can explain the bimodality.
-What separates the two sequences is the ratio of CCSN to SN Ia enrichment, so the DTD ought to have some impact on the \aFe bimodality, perhaps even determining whether or not it exists.
-
-In this paper we comprehensively evaluate a selection of DTD models from the literature with multiple SFHs and a prescription for radial migration in the Versatile Integrator for Chemical Evolution \citep[VICE;][]{JohnsonWeinberg2020-Starbursts}.
-In Section \ref{sec:methods}, we present our models for the DTD and SFH, and we describe our chemical evolution simulations.
-In Section \ref{sec:onezone-results}, we present the results of our one-zone chemical evolution simulations.
+% The Maoz studies all assume a particular form for the DTD and fit for the specific parameters. They do not quantitatively favor one form over another (e.g., power-law over exponential). 
+% \citet{Castrillo2021-DTD} find a best fit power law slope of $\alpha\approx-1.1$ with a minimum delay time of $\sim50$ Myr, they also find a fairly high correlation between SN Ia rate and H$\alpha$ (a proxy for young stars) which is surprising.
+% \citet{Stolger2020-ExponentialDTD} perform maximum likelihood estimations based on the cosmic star formation history and the star formation histories of individual galaxies.
+In both cases their best fit functions were approximately exponential, though they started with a skew-normal function so could not have ended up with a power law even if they wanted to.
+They don't actually report the timescale of this exponential, but based on the plots I'd say it's about 1.5 - 2 (1.7?) Gyr.
+Their best fit parameters make no sense to me as they don't report their units.
+
+The uncertainties in the SN Ia DTD propagate into GCE models.
+In principle, then, the observed chemical abundance patterns should contain information about the DTD, and therefore the progenitors, of SNe Ia.
+A few studies have compared different DTDs in one-zone chemical evolution models, but the scope of their conclusions is limited by the assumption of instantaneous mixing \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
+\citet{Poulhazan2018-PrecisionPollution} compared six DTD models in a smoothed-particle hydrodynamics simulation in a cosmological context.
+They found that models with a prompt SN Ia component produced the highest abundance ratios and the narrowest \aFe distributions at late times, although their simulation was not tuned to reproduce the parameters of the Milky Way and they did not compare to observed chemical abundances.
+% The current era of large spectroscopic surveys such as the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE}
+
+% Notes on GCE studies
+% \citet{Andrews2017-ChemicalEvolution} predict abundance tracks and distributions using one-zone models for four different DTD models; they find that most are consistent with their abundance data.
+% \citet{Palicio2023-AnalyticDTD} derive analytic solutions to one-zone chemical evolution equations for seven DTD models, but their comparisons to data are limited to the Solar neighborhood. 
+% \citet{Poulhazan2018-PrecisionPollution} investigate six different DTD models in a smoothed-particle hydrodynamics simulation, but they only present global results for the entire galaxy, they don't compare abundances throughout the disk, and they don't compare to observations.
+
+This paper presents the first comprehensive look at the DTD in a multi-zone GCE model that can qualitatively reproduce the abundance structure of the Milky Way disk.
+We evaluate a selection of DTD models from the literature with multiple SFHs and a prescription for radial stellar migration in the Versatile Integrator for Chemical Evolution \citep[VICE;][]{JohnsonWeinberg2020-Starbursts}.
+In Section \ref{sec:methods}, we present our models for the DTD and SFH, and we describe our chemical evolution models.
+In Section \ref{sec:onezone-results}, we present the results of our one-zone chemical evolution models.
 In Section \ref{sec:multizone-results}, we present the results of our multi-zone simulations and compare to observations.
@@
 The basic setup of our models follows theirs: the simulated Galaxy is a disk with a radius of 20 kpc and is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
-The gas in each ring is assumed to be instantaneously mixed, and no gas is exchanged between rings.
+The gas in each ring is assumed to be instantaneously mixed; while star particles are allowed to migrate radially (see Appendix \ref{app:migration}), there is no exchange of gas between rings.
 We run our simulations with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
@@
 
-CCSN enrichment:
+Like \citet{Johnson2021-Migration}, we focus our analysis on O and Fe, representing the $\alpha$ and Fe-peak elements, respectively.
+Both elements are produced by CCSNe.
+VICE adopts the instantaneous recycling approximation for CCSNe, so the equation which governs CCSN enrichment as a function of star formation for some element $x$ is simply
 \begin{equation}
@@
 \end{equation}
-where $y_x^{\rm CC}$ is the CCSN yield of element $x$ per unit mass of star formation.
+where $y_x^{\rm CC}$ is the CCSN yield of element $x$ per unit mass of star formation, and $\dot M_*$ is the star formation rate.
 Following \citet{Johnson2021-Migration}, who in turn adopt their yields from \citet{Weinberg2017-ChemicalEquilibrium}, we adopt $y_{\rm O}^{\rm CC}=0.015$ and $y_{\rm Fe}^{\rm CC}=0.0012$.
-
-We follow the formalism of \citet{Weinberg2017-ChemicalEquilibrium} when deriving the equations for Fe enrichment from SNe Ia.
-
-$R_{\rm Ia}(t)$ is the DTD in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$.
-
-The rate of Fe contribution to the ISM from SNe Ia is 
+The primary effect of these yields is to set the ``plateau'' in [O/Fe] which represents pure CCSN enrichment.
+The chosen yields for this paper produce a plateau at [O/Fe]$=0.45$; see \citet{Weinberg2023-CCSNYield} for more discussion.
+
+Following the formalism of \citet{Weinberg2017-ChemicalEquilibrium}, the rate of Fe contribution to the ISM from SNe Ia is 
 \begin{equation}
@@
 \end{equation}
-where $\dot M_*(t)$ is the SFR at time $t$, $R_{\rm Ia}(t) dt$ is the number of SNe Ia which explode in the time interval $(t, t+dt)$ per unit mass of stars formed at $t=0$, $t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the maximum simulation time.
+where %$\dot M_*(t)$ is the SFR at time $t$, 
+%$R_{\rm Ia}(t) dt$ is the number of SNe Ia which explode in the time interval $(t, t+dt)$ per unit mass of stars formed at $t=0$, 
+$R_{\rm Ia}$ is the DTD in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$,
+$t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the maximum simulation time.
 The denominator of Equation \ref{eq:weighted-sfr} is therefore the total number of SNe Ia per M$_{\odot}$ of stars formed.
@@
 where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia.
-We take the average number of SNe Ia per mass of stars formed to be $N_{\rm Ia}/M_*=2.2\times10^{-3}\,{\rm M}_\odot^{-1}$ following \citet{MaozMannucci2012-SNeIaReview}, which gives $R_{\rm Ia}$ units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$.
+We take the average number of SNe Ia per mass of stars formed to be $N_{\rm Ia}/M_*=2.2\times10^{-3}\,{\rm M}_\odot^{-1}$ from \citet{MaozMannucci2012-SNeIaReview}.%, which gives $R_{\rm Ia}$ units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$.
 Following \citet{Johnson2021-Migration}, we take $y_{\rm Fe}^{\rm Ia}=0.00214$.
+This yield was selected so that the inside-out SFH model produces stars with [O/Fe]$\approx 0.0$ by the end of the simulation.
 SNe Ia do not contribute O so $y_{\rm O}^{\rm Ia}=0$.
@@
 Figure \ref{fig:dtds} presents these DTDs as a function of time after star formation, and Table \ref{tab:dtds} summarizes the DTD models and their parameters.
+
+[Say something about DTD normalization?]
 
@@
 
-% \citet{Stolger2020-ExponentialDTD} perform maximum likelihood estimations based on the cosmic star formation history and the star formation histories of individual galaxies.
-In both cases their best fit functions were approximately exponential, though they started with a skew-normal function so could not have ended up with a power law even if they wanted to.
-They don't actually report the timescale of this exponential, but based on the plots I'd say it's about 1.5 - 2 (1.7?) Gyr.
-Their best fit parameters make no sense to me as they don't report their units.
-
 \paragraph{Power-law} A simple power law with slope $\alpha$:
@@
 We also investigate a longer timescale of $\tau=3$ Gyr.
-\citet{Matteucci1986-SupernovaEnrichment}, \citet{Stolger2020-ExponentialDTD}
+\citet{Matteucci1986-SupernovaEnrichment}, \citet{Strolger2020-ExponentialDTD}.
+\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} assume for the DTD an declining exponential function with a timescale of 1.5 Gyr, which has the benefit of an analytic solution to the equations of chemical equilibrium.
 
@@
 \citet{Poulhazan2018-PrecisionPollution} refer to this as the ``bimodal'' model.
+This is the DTD which is adopted by the Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations.
 
@@
 The simulation results are arranged by increasing median delay time from left to right.
-Results for the two-population and power-law ($\alpha$=-1.1) DTD models, with a large fraction of prompt SNe Ia, are presented in the first and second columns, respectively.
+Results for the two-population and power-law ($\alpha=-1.1$) DTD models, with a large fraction of prompt SNe Ia, are presented in the first and second columns, respectively.
 For these models, the simulated stellar abundances are reasonably well-aligned with the APOGEE contours at low $|z|$ (bottom panels), but they entirely miss the observed high-$\alpha$ sequence at high $|z|$ (top panels).
@@
 
-Compare to previous studies: \citet{Poulhazan2018-PrecisionPollution,Palicio2023-AnalyticDTD}.
+[Compare to previous studies]
+Discuss \citet{Matteucci2006-BimodalDTDConsequences} findings of the \citet{Mannucci2006-TwoPopulations} DTD in the two-infall model.
 
@@
 
+[Metallicity dependent DTD]
+
+[Is the MW DTD the same as elsewhere?]
+\citet{Walcher2016-SelfSimilarity} argue that the similarity of the age--[$\alpha$/Fe] relation between Solar neighborhood stars and nearby elliptical galaxies is evidence for a universal DTD; between a bimodal, narrow Gaussian, and power-law DTD, they find the latter best explains their data.
+
 \subsection{Radial Migration \& Bimodality}
+
+% Taken from introduction
+The bimodal distribution of \aFe in stars with similar metallicities was first noted in the Solar neighborhood \citep[e.g.,][]{Furhmann1998-NearbyStars}, later extended to the whole of the Milky Way disk \citep{Nidever2014-ChemicalEvolutionAPOGEE,Hayden2015-ChemicalCartography}.
+The ``high-$\alpha$'' population contains stars with low enrichment from SNe Ia, so their abundance ratios reflect that of almost pure CCSN enrichment; it is associated with the kinematically hot thick disk \citep{Bensby2003-AbundanceTrends}.
+The ``low-$\alpha$'' population is associated with the thin disk and contains stars with roughly solar $\alpha$-abundances.
+Various explanations of the \aFe bimodality have been proposed, including radial stellar mixing \citep{Schonrich2009-RadialMixing} and a bursty gas infall history \citep[e.g.,][]{Spitoni2021-TwoInfall}.
+% The origin of the \aFe bimodality is debated.
+\citet{Schonrich2009-RadialMixing} argue that it arises due to radial migration (churning) even with a smooth star formation rate.
+\citet{Johnson2021-Migration} use a smooth SFR and a prescription for radial migration but are unable to reproduce the bimodality.
+\citet{Spitoni2021-TwoInfall} (definitely earlier papers too) argue that two distinct infall episodes can explain the bimodality.
+What separates the two sequences is the ratio of CCSN to SN Ia enrichment, so the DTD ought to have some impact on the \aFe bimodality, perhaps even determining whether or not it exists.
+
+% Taken from introduction
+A complicating factor in observing and modeling the effects of the DTD is the migration of stars throughout the disk.
+\citet{SellwoodBinney2002-RadialMixing} first demonstrated that a transient spiral perturbation (or other potential feature; see [citations]) can cause resonant interactions which adjust stars' guiding center radii without leading to kinematic heating of the disk.
+Core-collapse SNe explode on timescales of a few Myr, before the progenitor has a chance to migrate far from its birth location.
+On the other hand, SNe Ia have a broad distribution of delay times and their progenitors can migrate great distances between birth and explosion.
+The consequence is that SNe Ia can enrich regions of the Galaxy far removed from regions which have experienced a high rate of star formation.
+Talk about \citet{Scannapieco2005-ChemicalEnrichment}.
+The first GCE model to incorporate radial mixing was developed by \citet{Schonrich2009-RadialMixing}, and subsequent studies have incorporated more comprehensive numerical treatments of radial migration and the effect of a central bar \citep[e.g.,][]{Minchev2013-ChemodynamicalEvolution}.
+In this paper, we follow the treatment by \citet{Johnson2021-Migration}, who [describe treatment].
+Talk about \citet{Karapetyan2022-SNIaDistances}.
 

### 2024-02-05 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \newcommand{\osuaffil}{Department of Astronomy, The Ohio State University, 140 W. 18th Ave, Columbus OH 43210, USA}
+\newcommand{\ccappaffil}{Center for Cosmology and AstroParticle Physics, The Ohio State University, 191 W. Woodruff Ave., Columbus OH 43210, USA}
 \newcommand{\aFe}{[$\alpha$/Fe]\xspace}
@@
 %        A Chemical Evolution Perspective}
-\title{Galactic Chemical Evolution Models Favor Extended Type Ia Supernova Delay-Time Distributions}
+\title{Galactic Chemical Evolution Models Favor an Extended Type Ia Supernova Delay-Time Distribution}
 
@@
 \affiliation{\osuaffil}
+\affiliation{\ccappaffil}
 \author[0000-0001-7258-1834]{Jennifer A. Johnson}
 \affiliation{\osuaffil}
-\affiliation{Center for Cosmology and Astroparticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus OH 43210, USA}
+\affiliation{\ccappaffil}
 \author[0000-0002-6534-8783]{James W. Johnson}
-% \affiliation{\osuaffil}
 \affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
+\affiliation{\osuaffil}
+\affiliation{\ccappaffil}
 % \author[0000-0001-7775-7261]{David H. Weinberg}
@@
 Galactic chemical evolution (GCE) studies seek to explain the observed distribution of metals throughout the Milky Way Galaxy.
-One curious chemical feature of the Milky Way disk is the existence of two populations separated by their \aFe\footnote{
+\citet{Tinsley1979-StellarLifetimes} made a compelling case that the non-Solar \aFe\footnote{
     In standard bracket notation, $[X/Y]\equiv \log_{10}(X/Y) - \log_{10}(X/Y)_{\odot}$.
 In this work we will use \aFe and [O/Fe] interchangeably, although observational studies will often use a combination of $\alpha$-elements to calculate \aFe.
-} abundance ratios at similar metallicity. 
-\citet{Tinsley1979-StellarLifetimes} first[?] proposed that the non-Solar \aFe ratios seen by, e.g., \citet{Wallerstein1962-GDwarfAbundances} were caused by different stellar lifetimes for the contributors of the Fe-peak elements than the $\alpha$-elements.
-Type Ia supernovae (SNe Ia), the thermonuclear explosions of carbon-oxygen white dwarfs (WDs), are responsible for most of the Fe produced in the Galaxy \citep{Matteucci1986-SupernovaEnrichment}; meanwhile, core collapse supernovae (CCSNe), the explosions of massive stars, produce the $\alpha$-elements (e.g., O and Mg) in addition to a smaller fraction of Fe.
+} ratios seen by, e.g., \citet{Wallerstein1962-GDwarfAbundances} were caused by different stellar lifetimes for the contributors of the Fe-peak elements than the $\alpha$-elements. 
+Type Ia supernovae (SNe Ia), the thermonuclear explosions of carbon-oxygen white dwarfs (WDs), are responsible for a majority of the Fe produced in the Galaxy \citep{Matteucci1986-SupernovaEnrichment}; meanwhile, core collapse supernovae (CCSNe), the explosions of massive stars, produce the $\alpha$-elements (e.g., O and Mg) in addition to a smaller fraction of Fe.
 SNe Ia are delayed by $\sim10^8 - 10^{10}$ years after star formation events, as evidenced by observations at large distances from star forming regions and in elliptical galaxies \citep[e.g.,][]{Maza1976-SNStatistics}.
@@
 % [What is the delay time distribution]
-The rate of SNe Ia which explode as a function of time after the formation of a hypothetical unit-mass single stellar population is known as the delay-time distribution (DTD).
+The rate of SNe Ia which explode as a function of time after the formation of a hypothetical unit-mass single stellar population is known as the delay-time distribution \citep[DTD; for a review, see Section 3.5 of][]{Maoz2014-Review}.
 When the DTD is convolved with the Galactic star formation rate (SFR) as a function of time, it yields the SN Ia rate as a function of time. 
@@
 The mechanism(s) for producing SNe Ia are not fully understood \citep[for reviews, see][]{Maoz2014-Review,Livio2018-ProgenitorReview,Ruiter2020-ProgenitorReview}.
-Two general production channels have been proposed: in the single-degenerate (SD) case, the WD accretes mass from a close non-degenerate companion until it surpasses $\sim1.4$ M$_\odot$ and explodes \citep{Whelan1973-SDModel,Nomoto1982-SDModel,Yoon2003-SDModel}.
+Two general production channels have been proposed.
+In the single-degenerate (SD) case, the WD accretes mass from a close non-degenerate companion until it surpasses $\sim1.4$ M$_\odot$ and explodes \citep{Whelan1973-SDModel,Nomoto1982-SDModel,Yoon2003-SDModel}.
 In the double-degenerate (DD) case, two WDs merge after a gravitational-wave inspiral \citep{Iben1984-IaBinary,Webbink1984-DDModel,Pakmor2012-WDMerger} or head-on collision \citep{Benz1989-CollisionalDD,Thompson2011-CollisionalDD}.
@@
 % By formulating analytical DTDs for several progenitor models, \citet{Greggio2005-AnalyticalRates} found that the SD channel tends to produce a steeper DTD function than the DD channel, and the median delay time (by which 50\% of SNe Ia have exploded) can vary by a factor of 10 depending on the chosen progenitor scenario and its particular parameters.
-For the DD channel, arguments about the distribution of post-common envelope separations and the rate of gravitational wave inspiral suggest a broad $\sim t^{-1}$ DTD at long delay times ($\gtrsim 1$ Gyr), but at short delays ($\lesssim 1$ Gyr) the rate is limited by the need to produce two WDs \citep[see Section 3.5 from][]{Maoz2014-Review}.
+For the DD channel, assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral suggest a broad $\sim t^{-1}$ DTD at long delay times ($\gtrsim 1$ Gyr), but at short delays ($\lesssim 1$ Gyr) the rate is limited by the need to produce two WDs \citep[see Section 3.5 from][]{Maoz2014-Review}.
 Higher-order progenitor systems could also produce a $t^{-1}$ DTD \citep{Fang2018-QuadrupleSystems,Rajamuthukumar2023-TripleEvolution}.
@@
 In principle, then, the observed chemical abundance patterns should contain information about the DTD, and therefore the progenitors, of SNe Ia.
-A few studies have compared different DTDs in one-zone chemical evolution models, but the scope of their conclusions is limited by the assumption of instantaneous mixing \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
+A few studies have compared different DTDs in one-zone chemical evolution models, but their comparisons to abundance data are limited to the local Solar neighborhood \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
 \citet{Poulhazan2018-PrecisionPollution} compared six DTD models in a smoothed-particle hydrodynamics simulation in a cosmological context.
 They found that models with a prompt SN Ia component produced the highest abundance ratios and the narrowest \aFe distributions at late times, although their simulation was not tuned to reproduce the parameters of the Milky Way and they did not compare to observed chemical abundances.
-% The current era of large spectroscopic surveys such as the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE}
+The current era of large spectroscopic surveys such as the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE} and the forthcoming Milky Way Mapper [cite] has made abundances across the Milky Way disk available for comparison to more sophisticated GCE models.
 
@@
 
-This paper presents the first comprehensive look at the DTD in a multi-zone GCE model that can qualitatively reproduce the abundance structure of the Milky Way disk.
+This paper presents the first comprehensive look at the DTD in a multi-zone GCE model that can qualitatively reproduce the observed abundance structure of the Milky Way disk.
 We evaluate a selection of DTD models from the literature with multiple SFHs and a prescription for radial stellar migration in the Versatile Integrator for Chemical Evolution \citep[VICE;][]{JohnsonWeinberg2020-Starbursts}.
@@
 In Section \ref{sec:onezone-results}, we present the results of our one-zone chemical evolution models.
-In Section \ref{sec:multizone-results}, we present the results of our multi-zone simulations and compare to observations.
+In Section \ref{sec:multizone-results}, we present the results of our multi-zone models and compare to observations.
 In Section \ref{sec:discussion}, we discuss the implications for the DTD and future surveys.
-In Section \ref{sec:conclusions}, we conclude.
+In Section \ref{sec:conclusions}, we summarize our conclusions.
 
@@
     \centering
-    \includegraphics{figures/age_ofe_sfh_alt.pdf}
+    \includegraphics{figures/age_ofe_sfh.pdf}
     \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different SFH models.
@@
     \label{fig:age-ofe-sfh}
-    \script{age_ofe_sfh_alt.py}
+    \script{age_ofe_sfh.py}
 \end{figure}
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/age_ofe_dtd_alt.pdf}
+    \includegraphics[width=\linewidth]{figures/age_ofe_dtd.pdf}
     \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different DTD models.
@@
     \label{fig:age-ofe-dtd}
-    \script{age_ofe_dtd_alt.py}
+    \script{age_ofe_dtd.py}
 \end{figure*}
@@
 
-We've run a lot of models and need some semi-quantitative way to say that some models do better than others.
+\subsection{Scoring the Model Outputs}
+\label{sec:scores}
+
+The results presented in Section \ref{sec:multizone-results} represent a fraction of the total model outputs.
+We ran models for four different SFHs and eight different DTDs, for a combined total of 32 model runs.
+While we focused our attention on results in the Solar annulus (for which we still have the best data), we have model outputs which span the entire disk out to 20 kpc.
+In order to identify trends among our many models, it will be useful to have some semi-quantitative way to compare their outputs to APOGEE data across the disk.
+
 We compare our multi-zone outputs to APOGEE across five diagnostics: the [Fe/H] DF, [O/Fe] DF, [Fe/H]--[O/Fe] plane, age--[O/Fe] plane, and bimodality in the [O/Fe] DF.
@@
 
-To quantify the difference between the abundance distributions generated by VICE and those observed in APOGEE, we compute the Kullback-Leibler (KL) divergence \citep{KullbackLeibler1951}, defined as
+To quantify the difference between the abundance distributions (MDFs and [O/Fe] DFs) generated by VICE and those observed in APOGEE, we compute the Kullback-Leibler (KL) divergence \citep{KullbackLeibler1951}, defined as
 \begin{equation}
@@
 \subsection{Radial Migration \& Bimodality}
+
+One curious chemical feature of the Milky Way disk is the existence of two populations separated by their \aFe abundance ratios at similar metallicity \citep[e.g.,][]{Bensby2014-SolarNeighborhoodAbundances}.
 

### 2024-02-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \newcommand{\aFe}{[$\alpha$/Fe]\xspace}
+
+% Citation aliases
+\defcitealias{Johnson2021-Migration}{J21}
+\defcitealias{Leung2023-Ages}{L23}
 
@@
 
-We make use of the multi-zone simulation tools in VICE developed by \citet{Johnson2021-Migration}.
+We make use of the multi-zone simulation tools in VICE developed by \citet{Johnson2021-Migration} (hereafter \citetalias{Johnson2021-Migration}).
 The basic setup of our models follows theirs: the simulated Galaxy is a disk with a radius of 20 kpc and is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
@@
 We run our simulations with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
-Following \citet{Johnson2021-Migration}, we set VICE to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_*=0$ for $R_{\rm gal}>R_{\rm SF}$.
+Following \citetalias{Johnson2021-Migration}, we set VICE to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_*=0$ for $R_{\rm gal}>R_{\rm SF}$ (stars are allowed to migrate past $R_{\rm SF}$, they are just not born there).
 
@@
     \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models.
-We omit parameters which have been left unchanged from \citet{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
+We omit parameters which have been left unchanged from \citetalias{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
     \tablehead{
@@
         R_{\rm SF}      & 15.5 kpc  & \ref{sec:methods} & Maximum radius of star formation \\
-        M_{\rm gas,0}   & 0         & \ref{sec:sfh}     & Initial gas mass \\
+        M_{g,0}   & 0         & \ref{sec:sfh}     & Initial gas mass \\
         % DTD
@@
 
-Like \citet{Johnson2021-Migration}, we focus our analysis on O and Fe, representing the $\alpha$ and Fe-peak elements, respectively.
+Like \citetalias{Johnson2021-Migration}, we focus our analysis on O and Fe, representing the $\alpha$ and Fe-peak elements, respectively.
 Both elements are produced by CCSNe.
@@
 \end{equation}
-where $y_x^{\rm CC}$ is the CCSN yield of element $x$ per unit mass of star formation, and $\dot M_*$ is the star formation rate.
-Following \citet{Johnson2021-Migration}, who in turn adopt their yields from \citet{Weinberg2017-ChemicalEquilibrium}, we adopt $y_{\rm O}^{\rm CC}=0.015$ and $y_{\rm Fe}^{\rm CC}=0.0012$.
+where $y_x^{\rm CC}$ is the CCSN yield of element $x$ per unit mass of star formation, and $\dot M_*$ is the SFR.
+Following \citetalias{Johnson2021-Migration}, who in turn adopt their yields from \citet{Weinberg2017-ChemicalEquilibrium}, we adopt $y_{\rm O}^{\rm CC}=0.015$ and $y_{\rm Fe}^{\rm CC}=0.0012$.
 The primary effect of these yields is to set the ``plateau'' in [O/Fe] which represents pure CCSN enrichment.
@@
 We take the average number of SNe Ia per mass of stars formed to be $N_{\rm Ia}/M_*=2.2\times10^{-3}\,{\rm M}_\odot^{-1}$ from \citet{MaozMannucci2012-SNeIaReview}.%, which gives $R_{\rm Ia}$ units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$.
-Following \citet{Johnson2021-Migration}, we take $y_{\rm Fe}^{\rm Ia}=0.00214$.
+Following \citetalias{Johnson2021-Migration}, we take $y_{\rm Fe}^{\rm Ia}=0.00214$.
 This yield was selected so that the inside-out SFH model produces stars with [O/Fe]$\approx 0.0$ by the end of the simulation.
@@
 Figure \ref{fig:dtds} presents these DTDs as a function of time after star formation, and Table \ref{tab:dtds} summarizes the DTD models and their parameters.
-
-[Say something about DTD normalization?]
 
@@
 % where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
-A declining power-law with $\alpha\sim-1$ is a standard assumption in many observational studies of the DTD as well as Galactic chemical evolution simulations.
+A declining power-law with $\alpha\sim-1$ is expected to arise from typical assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral \citep[see Section 3.5 from][]{Maoz2014-Review}.
+It is therefore a commonly assumed DTD in GCE studies \citepalias[e.g.,][]{Johnson2021-Migration}.
+Additionally, the observational evidence for a power-law DTD is strong.
 \citet{Maoz2017-CosmicDTD} obtain a DTD with $\alpha=-1.07\pm0.09$ based on volumetric rates and an assumed cosmic SFH for field galaxies in redshift range $0\leq z\leq 2.25$.
@@
 
-\paragraph{Plateau} A ``plateau'' model consisting of a flat slope of width $W$ followed by a power law decline:
+\paragraph{Plateau} A modification of the simple power-law in which the DTD ``plateaus'' for a duration $W$ before declining:
 \begin{equation}
@@
 % where $B_W=[(W-t_{\rm min}) + \frac{t_{\rm max}^{\alpha+1} - W^{\alpha+1}}{(\alpha+1)W^\alpha}]^{-1}$ is the normalization coefficient.
+Our primary motivation is to consider a model which matches observations at delay times beyond a few Gyr, where the DTD is best constrained, but which has a much smaller fraction of prompt ($\lesssim 100$ Myr) SNe Ia.
+To our knowledge, this form of the DTD has not been considered in previous studies.
+However, we show in Appendix \ref{app:analytical-dtds} that this form can approximate the more complicated analytical DD DTDs from \citet{Greggio2005-AnalyticalRates}.
 We investigate the cases $W=0.3$ Gyr and $W=1$ Gyr, taking $\alpha=-1.1$ for all plateau models.
-Figure \ref{fig:analytical-dtd} illustrates the similarity between these models and two different treatments of the analytical double-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
-For more discussion on this, see Appendix \ref{app:analytical-dtds}.
 
 \paragraph{Triple-system} A DTD based on simulations of triple-system evolution by \citet{Rajamuthukumar2023-TripleEvolution}.
-We approximate their DTD as a special case of the plateau model (Equation \ref{eq:plateau-dtd}) where the initial rate is quite low until an instantaneous rise to the plateau value at time $t_{\rm rise}$:
+We approximate their numerically-generated DTD as a special case of the plateau model (Equation \ref{eq:plateau-dtd}) where the initial rate is quite low until an instantaneous rise to the plateau value at time $t_{\rm rise}$:
 \begin{equation}
@@
 \end{equation}
-We take $t_{\rm rise}=0.5$ Gyr, $W=0.5$ Gyr, $\alpha=-1.1$, and $\epsilon=0.05$ so the initial rate is 5\% of the peak rate.
+with $t_{\rm rise}=0.5$ Gyr, $W=0.5$ Gyr, $\alpha=-1.1$, and $\epsilon=0.05$ so the initial rate is 5\% of the peak rate.
 
@@
 \end{equation}
-We investigate the case where $\tau=1.5$ Gyr, which has been used in previous chemical evolution studies \citep[e.g.,][]{Schonrich2009-RadialMixing,Weinberg2017-ChemicalEquilibrium} and is similar to the analytical single-degenerate DTD from \citet{Greggio2005-AnalyticalRates}.
-We also investigate a longer timescale of $\tau=3$ Gyr.
-\citet{Matteucci1986-SupernovaEnrichment}, \citet{Strolger2020-ExponentialDTD}.
-\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} assume for the DTD an declining exponential function with a timescale of 1.5 Gyr, which has the benefit of an analytic solution to the equations of chemical equilibrium.
-
-\paragraph{Two-population} A DTD in which 50\% of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the other 50\% form an exponential tail at large $t$:
+This model can be used to calculate an analytic solution to the equations of chemical equilibrium, making it a popular choice among GCE studies.
+\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assume an exponential DTD with a timescale $\tau=1.5$ Gyr.
+We show in Appendix \ref{app:analytical-dtds} that a $\tau=1.5$ Gyr exponential is an adequate approximation for the analytical SD DTD from \citet{Greggio2005-AnalyticalRates}.
+There is less observational support for an exponential DTD.
+\citet{Strolger2020-ExponentialDTD}, fitting to the cosmic SFH and SFHs from field galaxies, find a range of exponential-like solutions with timescales $\sim 1.5 - 6$ Gyr.
+In this paper we investigate timescales $\tau=1.5$ and 3 Gyr.
+% I've looked at Matteucci & Greggio (1986) and I'm not sure what their DTD would be
+
+\paragraph{Two-population} A DTD in which $\sim50\%$ of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the remainder form an exponential tail at large $t$:
 \begin{equation}
@@
 \end{equation}
-Following the two-population model from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in roughly 50\% of SNe Ia exploding within $t<100$ Myr.
-\citet{Poulhazan2018-PrecisionPollution} refer to this as the ``bimodal'' model.
-This is the DTD which is adopted by the Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations.
-
-% Minimum SN Ia delay time
-The minimum SN Ia delay time $t_D$, i.e.
-the lifetime of the most massive progenitor system, is also a parameter of the DTD which can have an effect on chemical evolution.
-\citet{Andrews2017-ChemicalEvolution} found that a longer minimum delay time produces a sharper high-$\alpha$ ``knee'' and shifts it to higher [Fe/H], although they only explored this for an exponential DTD.
-They adopt a fiducial value of $t_D=150$ Myr, as do \citet{Johnson2021-Migration}.
-\citet{Poulhazan2018-PrecisionPollution} adopt a much smaller value of $t_D=29$ Myr as the lifetime of their most massive progenitors.
-
-We take $t_D=40$ Myr to be our fiducial value as it is the approximate lifetime of an $8\,{\rm M}_\odot$ star [Larson 1974].
-We find that adopting a longer $t_D$ has only a minor effect on the chemical evolution for most DTD models except the power-law, but in that case the effect of a longer minimum delay time can be approximated by adding an initial plateau of $\sim100$ Myr to the DTD.
-See Section \ref{sec:onezone-results} and Figure \ref{fig:onezone-twopanel} for details.
+To approximate the DTD from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in $\sim 50\%$ of SNe Ia exploding within $t<100$ Myr.
+This formulation is slightly different than the approximation used in other GCE studies \citep[e.g.,][]{Matteucci2006-BimodalDTDConsequences,Poulhazan2018-PrecisionPollution}, where it has a more distinctly bimodal shape.
+We have compared the two approximations to this DTD in a one-zone model and found that they produce very similar abundance tracks and MDFs.
+This DTD is adopted by the Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations.
+
+\subsubsection{The Minimum SN Ia Delay Time}
+
+In addition to the DTD shape, the minimum SN Ia delay time $t_D$ is another parameter which can have an effect on chemical evolution observables, such as the location of the high-$\alpha$ knee and the [O/Fe] DF \citep{Andrews2017-ChemicalEvolution}.
+The value of $t_D$ is set by the lifetime of the most massive SN Ia progenitor system.
+Previous GCE studies have adopted values ranging from $t_D\approx30$ Myr \citep[e.g.,][]{Poulhazan2018-PrecisionPollution} to $t_D=150$ Myr \citepalias[e.g.,][]{Johnson2021-Migration}.
+We take $t_D=40$ Myr to be our fiducial value as it is the approximate lifetime of an $8\,{\rm M}_\odot$ star.
+In Section \ref{sec:onezone-results} we find that adopting a longer $t_D$ has only a minor effect on the chemical evolution for most DTD models except the power-law, but in that case the effect of a longer $t_D$ can be approximated by adding an initial plateau of width $W=0.3$ Gyr to the DTD (see Figure \ref{fig:onezone-twopanel}).
 
@@
 
-In this paper, we consider four models for the SFH: inside-out, late-burst, early-burst, and two-infall.
-The first two models are run in VICE's ``star formation mode,'' where the surface density of star formation rate $\dot\Sigma_*$ is prescribed along with the star formation efficiency timescale $\tau_*$, and the infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_{\rm gas}$ are calculated from the specified quantities.
-The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$  and $\tau_*$ and the other two quantities follow.
-All models have an initial gas mass $M_{\rm gas,0} = M_{\rm gas}(t=0) = 0$ in all zones.
-
-The functions presented below are dimensionless.
-For a detailed look at the normalization of the star formation rate with $R_{\rm gal}$, we refer the reader to Appendix B of \citet{Johnson2021-Migration}.
-
-\paragraph{Inside-out} Following \citet{Johnson2021-Migration}, this is our fiducial SFH:
-\begin{equation}
-    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm sfh}}
-    \label{eq:insideout-sfh}
-\end{equation}
-where we assume $\tau_{\rm rise}=2$ Gyr for all radii.
-The SFH timescale $\tau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\tau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the Solar annulus and longer timescales in the outer galaxy.
-The $\tau_{\rm sfh} - R_{\rm gal}$ relation is determined from the data of \citet{Sanchez2020-StarFormationTimescales}; see Section 2.5 of \citet{Johnson2021-Migration} for the details.
-
-\paragraph{Late-burst} A variation on the inside-out SFH with a Gaussian burst in the star formation rate:
-\begin{equation}
-    f_{\rm LB}(t|R_{\rm gal}) = f_{\rm IO}(t|R_{\rm gal}) \Big(1 + A_b e^{-(t-t_b)^2/2\sigma_b^2} \Big)
-    \label{eq:lateburst-sfh}
-\end{equation}
-where $A_b$ is the dimensionless amplitude of the starburst, $t_b$ is the time of the peak of the burst, and $\sigma_b$ is the width of the Gaussian.
-Following \citet{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr.
-The determination of $\tau_{\rm sfh}$ and the normalization of the SFR as a function of $R_{\rm gal}$ are the same as in the inside-out case.
-
-\paragraph{Early-burst} The infall rate at a given radius declines exponentially with time:
-\begin{equation}
-    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}}
-    \label{eq:earlyburst-ifr}
-\end{equation}
-The time-dependence of the SFE timescale $\tau_*$ comes from \citet{Conroy2022-ThickDisk}:
-\begin{equation}
-    \frac{\tau_*(t|\Sigma_g)}{1\,\rm{Gyr}} =
-    \begin{cases}
-        50, & t < 2.5\,\rm{Gyr} \\
-        \frac{50}{[1+3(t-2.5)]^2}, & 2.5\leq t \leq 3.7\,\rm{Gyr} \\
-        2.36, & t > 3.7\,\rm{Gyr}
-    \end{cases}
-    \label{eq:earlyburst-conroy22}
-\end{equation}
-We combine this with the Kennicutt-Schmidt relation used by \citet{Johnson2021-Migration}, minus the dependence on the molecular timescale $\tau_{\rm mol}$:
-\begin{equation}
-    \dot \Sigma_* = 
-    \begin{cases}
-        \Sigma_g, & \Sigma_g \geq \Sigma_{g,2} \\
-        \Sigma_g \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
-        \Sigma_g \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1}
-    \end{cases}
-    \label{eq:kennicutt-schmidt}
-\end{equation}
-Which leads to an overall SFE timescale of
-\begin{equation}
-    \tau_*(t,\Sigma_g) = \tau_*(t|\Sigma_g) \frac{\Sigma_g}{\dot \Sigma_*}
-    \label{eq:earlyburst-taustar}
-\end{equation}
-
-\paragraph{Two-infall} 
-We parameterize the infall rate as two successive, exponentially declining bursts as in \citet{Chiappini2001-AbundanceGradients}:
-\begin{equation}
-    \label{eq:twoinfall-ifr}
-    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2}
-\end{equation}
-In this model, the first infall produces the thick disk and the second infall produces the thin disk.
-The normalization ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
-\begin{equation}
-    f_\Sigma(R) = f_\Sigma(0) e^{R(1/R_2 - 1/R_1)}
-\end{equation}
-where we take the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$ following \citet{BlandHawthornGerhard2016-MilkyWayReview}.
-
-Figure \ref{fig:sfhs} presents an overview of these model star formation histories.
+We consider four models for the SFH: inside-out, late-burst, early-burst, and two-infall.
+The first two models are taken from \citetalias{Johnson2021-Migration} and are run in VICE's ``star formation mode,'' where the SFR surface density $\dot\Sigma_*$ is prescribed along with the star formation efficiency (SFE) timescale $\tau_*\equiv \Sigma_g/\dot\Sigma_*$.
+The remaining quantities, infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
+The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$ and $\tau_*$.
+All models have zero initial gas mass in all zones.
+We present an overview of these models in Figure \ref{fig:sfhs}.
 
@@
     \includegraphics[width=\linewidth]{figures/star_formation_histories.pdf}
-    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
+    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
 In each panel, we plot curves for the simulation zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
@@
 
-We adopt the same nucleosynthetic yields as \citet{Johnson2021-Migration}; the values are presented in Table \ref{tab:multizone-parameters}.
-
-% \subsection{Nucleosynthetic Yields}
-% \label{sec:yields}
-% 
-% Table \ref{tab:yields} summarizes the nucleosynthetic yields assumed in this paper, which we adopt from \citet{Johnson2021-Migration}.
-% 
-% \begin{deluxetable}{lll}
-%     \tablecaption{Nucleosynthetic yields assumed in our simulations.\label{tab:yields}}
-%     \tablehead{
-%         \colhead{Source} & \colhead{Element} & \colhead{Yield}
-%     }
-%     \startdata
-%     CCSN    & O     & 0.015     \\
-%     CCSN    & Fe    & 0.0012    \\
-%     \hline
-%     SN Ia   & O     & 0         \\
-%     SN Ia   & Fe    & 0.00214
-%     \enddata
-% \end{deluxetable}
+\paragraph{Inside-out} As in \citetalias{Johnson2021-Migration}, this is our fiducial SFH. The dimensionless time-dependence of the SFR is given by
+\begin{equation}
+    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm sfh}}
+    \label{eq:insideout-sfh}
+\end{equation}
+where we assume $\tau_{\rm rise}=2$ Gyr for all radii.
+The SFH timescale $\tau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\tau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the Solar annulus and longer timescales in the outer galaxy.
+The $\tau_{\rm sfh} - R_{\rm gal}$ relation is determined from the data of \citet{Sanchez2020-StarFormationTimescales}; see Section 2.5 of \citetalias{Johnson2021-Migration} for the details.
+For a detailed look at the normalization of the SFR with $R_{\rm gal}$, we refer the reader to Appendix B of \citetalias{Johnson2021-Migration}.
+
+\paragraph{Late-burst} A variation on the inside-out SFH with a Gaussian burst in the SFR at late times:
+\begin{equation}
+    f_{\rm LB}(t|R_{\rm gal}) = f_{\rm IO}(t|R_{\rm gal}) \Big(1 + A_b e^{-(t-t_b)^2/2\sigma_b^2} \Big)
+    \label{eq:lateburst-sfh}
+\end{equation}
+where $A_b$ is the dimensionless amplitude of the starburst, $t_b$ is the time of the peak of the burst, and $\sigma_b$ is the width of the Gaussian.
+Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr.
+The determination of $\tau_{\rm sfh}$
+% and the normalization of the SFR as a function of $R_{\rm gal}$ 
+is the same as in the inside-out case.
+
+\paragraph{Early-burst} An extension of the model proposed by \citet{Conroy2022-ThickDisk} to explain the non-monotonic behavior of the high-$\alpha$ sequence down to ${\rm [Fe/H]}\approx-2.5$.
+An abrupt factor $\sim20$ rise in the SFE at early times drives an increase in the [O/Fe] abundance and populates the high-$\alpha$ sequence.
+We adopt the formula for the time-dependence of the SFE timescale from \citet{Conroy2022-ThickDisk}:
+\begin{equation}
+    \frac{\tau_{\rm EB}}{1\,\rm{Gyr}} =
+    \begin{cases}
+        50, & t < 2.5\,\rm{Gyr} \\
+        \frac{50}{[1+3(t-2.5)]^2}, & 2.5\leq t \leq 3.7\,\rm{Gyr} \\
+        2.36, & t > 3.7\,\rm{Gyr}.
+    \end{cases}
+    \label{eq:earlyburst-taustar}
+\end{equation}
+In contrast to the previous SFH models, we run the early-burst model in ``infall'' mode.
+While \citet{Conroy2022-ThickDisk} use a constant infall rate in their one-zone model, we adopt a radially-dependent infall rate which declines exponentially with time:
+\begin{equation}
+    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}}
+    \label{eq:earlyburst-ifr}
+\end{equation}
+where $\tau_{\rm sfh}$ is the same as in the inside-out case.
+To calculate $\dot \Sigma_*$ from the above quantities, we modify the fiducial star formation law adopted from \citetalias{Johnson2021-Migration}, substituting $\tau_{\rm EB}$ for the SFE timescale of molecular gas:
+\begin{equation}
+    \dot \Sigma_* = 
+    \begin{cases}
+        \Sigma_g \tau_{\rm EB}^{-1}, & \Sigma_g \geq \Sigma_{g,2} \\
+        \Sigma_g \tau_{\rm EB}^{-1} \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
+        \Sigma_g \tau_{\rm EB}^{-1} \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1},
+    \end{cases}
+    \label{eq:earlyburst-sfr}
+\end{equation}
+with $\Sigma_{g,1}=5\times 10^6\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\Sigma_{g,2}=2\times 10^7\,{\rm M}_\odot\,{\rm kpc}^{-2}$.
+
+\paragraph{Two-infall} 
+We parameterize the infall rate as two successive, exponentially declining bursts as in \citet{Chiappini2001-AbundanceGradients}:
+\begin{equation}
+    \label{eq:twoinfall-ifr}
+    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2}
+\end{equation}
+In this model, the first infall produces the thick disk and the second infall produces the thin disk.
+The normalization ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
+\begin{equation}
+    f_\Sigma(R) = f_\Sigma(0) e^{R(1/R_2 - 1/R_1)}.
+\end{equation}
+Following \citet{BlandHawthornGerhard2016-MilkyWayReview}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
 
@@
 
-We compare our simulation results to abundance measurements from the 17th data release \citep[DR17;][]{Abdurro'uf2022-SDSSIV-DR17} of the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE}.
+We compare our simulation results to abundance measurements from the final data release \citep[DR17;][]{Abdurro'uf2022-SDSSIV-DR17} of the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE}.
 APOGEE used infrared spectrographs \citep{Wilson2019-APOGEE-Spectrographs} mounted on two telescopes: the 2.5-meter Sloan Foundation Telescope \citep{Gunn2006-SloanTelescope} at Apache Point Observatory, United States in the Northern Hemisphere, and the Ir{\'e}n{\'e}e DuPont Telescope \citep{BowenVaughan1973-DuPontTelescope} at Las Campanas Observatory, Chile in the Southern Hemisphere.
@@
 APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
-We adopt estimated ages from \citet{Leung2023-Ages}, who use a variational encoder-decoder network to estimate the age of APOGEE giants without contamination from age-abundance correlations.
-Their sample does not experience the $\sim10$ Gyr plateau that affects ages from astroNN \citep{Mackereth2019-astroNN-Ages}.
-We use an age uncertainty cut of 40\% per the recommendations of \citet{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt}APOGEE stars with age estimates.
+We use estimated ages from \citet{Leung2023-Ages} (hereafter \citetalias{Leung2023-Ages}), who use a variational encoder-decoder network to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
+Importantly, the \citetalias{Leung2023-Ages} sample does not experience the $\sim10$ Gyr plateau that affects ages from astroNN \citep{Mackereth2019-astroNN-Ages}.
+We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt}APOGEE stars with age estimates.
 The median uncertainty in log-age space is $\sim 0.1$.
@@
         EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
-        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citet{Leung2023-Ages}
+        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{Leung2023-Ages}
     \enddata
@@
 Before running the full multi-zone simulations, it will be useful to observe the effects of the DTD in more idealized conditions.
-A one-zone model assumes the entire gas reservoir is instantaneously mixed, so there is no spacial dependence for the distribution of metal abundances.
+A one-zone model assumes the entire gas reservoir is instantaneously mixed, so there is no spatial dependence for the distribution of metal abundances.
 In this section
@@
 All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=0.01$ Gyr.
-We adopt the inside-out star formation rate (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr), a star formation efficiency timescale $\tau_*\equiv M_{\rm gas}/\dot M_*=2$ Gyr, and an initial gas mass $M_{\rm gas,0}=0$.
+We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr), an SFE timescale $\tau_*\equiv M_g/\dot M_*=2$ Gyr, and an initial gas mass $M_{g,0}=0$.
 We adopt a continuous recycling prescription \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
-Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citep[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time of 40 Myr.
+Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time of 40 Myr.
 A summary of these one-zone fiducial parameters is presented in Table \ref{tab:onezone-parameters}.
@@
     \eta            & 2.15      & Outflow mass-loading factor \\
-    \tau_*          & 2.0 Gyr   & Star formation efficiency timescale \\
+    \tau_*          & 2.0 Gyr   & SFE timescale \\
     \dot M_r        & continuous    & Recycling rate \\
     t_D             & 40 Myr    & Minimum SN Ia delay time \\
-    M_{\rm gas,0}   & 0         & Initial gas mass \\
+    M_{g,0}   & 0         & Initial gas mass \\
     \dot M_*(t)     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
@@
 The marginal panels above and to the right of the central panel present the distributions of [Fe/H] and [O/Fe], respectively.
-For display purposes, these distributions are convolved with a Gaussian with a standard deviation of 0.02 dex.
+For display purposes, these distributions are convolved with a Gaussian kernel with a standard deviation of 0.02 dex.
     \textit{Middle:} Similar, comparing exponential DTDs with varying timescales. The solid, dashed, and dotted curves represent timescales $\tau=6$, 3, and 1.5 Gyr, respectively.
@@
 All plateau DTD models assume a post-plateau power-law slope of $\alpha=-1.1$.
-For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted purple curve represents a power-law DTD $\alpha=-1.1$ and no plateau.}
+For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted purple curve represents a power-law DTD with $\alpha=-1.1$ and no plateau.}
     \label{fig:onezone-threepanel}
@@
 The layout is similar to the plots in Figure \ref{fig:onezone-threepanel}.
-For clarity, we use a mass-loading factor $\eta=1$ for the exponential DTD run.
+For clarity, we assume a mass-loading factor $\eta=1$ for the exponential DTD curves.
     \textit{Right:} Comparison of one-zone models which assume all five functional forms for the DTD in this paper: triple-system (green), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
-A minimum SN Ia delay time of 40 Myr is assumed for all models.}
+A minimum SN Ia delay time of 40 Myr is assumed for all models in the right panel.}
     \label{fig:onezone-twopanel}
@@
         $\rm [O/Fe]$ & $1.8\times10^{-2}$ & APOGEE DR17 \\
-        log(Age/Gyr) & $0.10$ & \citet{Leung2023-Ages}
+        log(Age/Gyr) & $0.10$ & \citetalias{Leung2023-Ages}
         % Age/Gyr & 29\% & astroNN
@@
 While there are some quantitative differences in how the shape of the MDF varies with Galactic region, the qualitative trends are unaffected by the choice of model SFH or DTD.
-These trends are primarily driven by chemical equilibrium, abundance gradients, and radial migration \citep[][see their Section 3.2 for further discussion]{Johnson2021-Migration}.
+These trends are primarily driven by chemical equilibrium, abundance gradients, and radial migration \citepalias[][see their Section 3.2 for further discussion]{Johnson2021-Migration}.
 
@@
 Similar to Figure \ref{fig:ofe-feh-sfh}, all four panels assume an exponential DTD model with $\tau=1.5$ Gyr.
-We include age data from \citet{Leung2023-Ages} for qualitative comparison, though we caution against drawing strong conclusions because we don't correct for selection effects or systematics in the neural net ages.
+We include age data from \citetalias{Leung2023-Ages} for qualitative comparison, though we caution against drawing strong conclusions because we don't correct for selection effects or systematics in the neural net ages.
 The inside-out and late-burst models show fair agreement with the data at high [O/Fe], although both show a $\sim2$ Gyr offset to older ages.
@@
 Like the data, the trend in the median age with decreasing [O/Fe] decreases monotonically in the inside-out model.
-The late-burst model, however, shows a bump in the distribution around a lookback time of $\sim2$ Gyr driven by the Gaussian SFR burst, which is not seen in the data, as noted by \citet{Johnson2021-Migration}.
+The late-burst model, however, shows a bump in the distribution around a lookback time of $\sim2$ Gyr driven by the Gaussian SFR burst, which is not seen in the data, as noted by \citetalias{Johnson2021-Migration}.
 Neither model produces a significant amount of stars below Solar [O/Fe], in contrast to the data.
@@
 Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
-A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citet{Leung2023-Ages} (see Table \ref{tab:uncertainties}).
+A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citetalias{Leung2023-Ages} (see Table \ref{tab:uncertainties}).
 Black squares represent the mass-weighted median age of star particles within bins of [O/Fe] with a width of 0.05 dex, and the horizontal black error bars encompass the 16th and 84th percentiles.
-Red triangles represent the median age from \citet{Leung2023-Ages} in bins of [O/Fe], and the horizontal red error bars encompass the 16th and 84th percentiles.
+Red triangles represent the median age from \citetalias{Leung2023-Ages} in bins of [O/Fe], and the horizontal red error bars encompass the 16th and 84th percentiles.
 For clarity, bins which contain less than 1\% of the total mass (in the simulations) or total number of stars (in the data) are not plotted.}
@@
 While the other three fall short of the observed range in [O/Fe], they more closely match the median age--[O/Fe] relation.
-There is a slight reversal in the observed trend for the stars with the highest [O/Fe]: the $0.45\leq{\rm [O/Fe]}<0.5$ bin has a slightly \textit{lower} median age than the $0.3\leq{\rm [O/Fe]}<0.35$ bin at high $|z|$ in the \citet{Leung2023-Ages} sample, a small effect but one which is not observed in any of our simulation results.
+There is a slight reversal in the observed trend for the stars with the highest [O/Fe]: the $0.45\leq{\rm [O/Fe]}<0.5$ bin has a slightly \textit{lower} median age than the $0.3\leq{\rm [O/Fe]}<0.35$ bin at high $|z|$ in the \citetalias{Leung2023-Ages} sample, a small effect but one which is not observed in any of our simulation results.
 
@@
 
-We compare our multi-zone outputs to APOGEE across five diagnostics: the [Fe/H] DF, [O/Fe] DF, [Fe/H]--[O/Fe] plane, age--[O/Fe] plane, and bimodality in the [O/Fe] DF.
+We compare our multi-zone outputs to APOGEE across five diagnostics: the [Fe/H] DF, [O/Fe] DF, [Fe/H]--[O/Fe] plane, age--[O/Fe] plane, and [O/Fe] bimodality.
 We perform statistical tests between APOGEE and simulation outputs in each region of the galaxy, then average the scores together (weighted by the number of APOGEE targets in each galactic region) to obtain a single numerical score for each simulation.
@@
 \end{equation}
-where $\Delta\tau_k=\rm{med}(\tau_{\rm VICE})-\rm{med}(\tau_{\rm L23})$ is the difference between the mass-weighted median star particle age in VICE and the median stellar age from \citet{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citet{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
+where $\Delta\tau_k=\rm{med}(\tau_{\rm VICE})-\rm{med}(\tau_{\rm L23})$ is the difference between the mass-weighted median star particle age in VICE and the median stellar age from \citetalias{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citetalias{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
 As before, the score for the model as a whole is the average of $\Delta \tau_{\rm RMS}$ across all regions, weighted by the number of stars in the age sample in each region.
@@
 \variable{output/summary_table.tex}
+
+\subsection{The Two-Infall SFH Model}
 
@@
 % The origin of the \aFe bimodality is debated.
-\citet{Schonrich2009-RadialMixing} argue that it arises due to radial migration (churning) even with a smooth star formation rate.
-\citet{Johnson2021-Migration} use a smooth SFR and a prescription for radial migration but are unable to reproduce the bimodality.
+\citet{Schonrich2009-RadialMixing} argue that it arises due to radial migration (churning) even with a smooth SFR.
+\citetalias{Johnson2021-Migration} use a smooth SFR and a prescription for radial migration but are unable to reproduce the bimodality.
 \citet{Spitoni2021-TwoInfall} (definitely earlier papers too) argue that two distinct infall episodes can explain the bimodality.
@@
 The first GCE model to incorporate radial mixing was developed by \citet{Schonrich2009-RadialMixing}, and subsequent studies have incorporated more comprehensive numerical treatments of radial migration and the effect of a central bar \citep[e.g.,][]{Minchev2013-ChemodynamicalEvolution}.
-In this paper, we follow the treatment by \citet{Johnson2021-Migration}, who [describe treatment].
-Talk about \citet{Karapetyan2022-SNIaDistances}.
-
-Something about \citet{Johnson2021-Migration} and \citet{Schonrich2009-RadialMixing}.
+In this paper, we follow the treatment by \citetalias{Johnson2021-Migration}, who [describe treatment].
+
+\citet{Karapetyan2022-SNIaDistances} find a correlation between the SN Ia light curve decline rate, $\Delta m_{15}$, and the distance between the SN and the star-forming shock front of spiral arms.
+As this distance is expected to be an indicator of the age of the SN progenitor, such a correlation would suggest that the less-luminous, faster-declining SNe Ia come from an older progenitor population, which would be expected from progenitor models with sub-Chandrasekhar mass explosions.
+A similar study on the {\it radial} migration distance is probably impossible due to the challenges in estimating birth radii even in the Milky Way.
+It could be interesting to incorporate a SN Ia yield which varies with progenitor age into a GCE model.
+[Are there analytic DTDs for a DD progenitor with sub-Chandra explosions?]
+
+Something about \citetalias{Johnson2021-Migration} and \citet{Schonrich2009-RadialMixing}.
 
@@
 
+\end{itemize}
+
+Future work
+\begin{itemize}
+    \item Metallicity-dependent DTD normalization and/or shape.
 \end{itemize}
@@
 
-For each star particle in VICE, \citet{Johnson2021-Migration} randomly assign an analogue star particle from \texttt{h277} and adopt its radial migration distance $\Delta R$ and final midplane distance $z$.
+For each star particle in VICE, \citetalias{Johnson2021-Migration} randomly assign an analogue star particle from \texttt{h277} and adopt its radial migration distance $\Delta R$ and final midplane distance $z$.
 This allows VICE to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
@@
 When a star particle is created by VICE at initial radius $R_{\rm form}$, we sample its total radial migration distance $\Delta R$ from a Gaussian with a width described by Equation \ref{eq:radial-migration}, and we sample its final midplane distance $z_{\rm final}$ from the distribution described by Equation \ref{eq:sech-pdf} with a width given by Equation \ref{eq:scale-height}.
-The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citet{Johnson2021-Migration}, but with a time dependence $\propto \Delta t^{1/3}$.
+The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citetalias{Johnson2021-Migration}, but with a time dependence $\propto \Delta t^{1/3}$.
 This produces distributions of $R_{\rm final}$ and $z_{\rm final}$ which are similar to the analogue migration case for all but the oldest stars.

### 2024-02-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\paragraph{Two-infall} 
+\paragraph{Two-infall} [Expand]
 We parameterize the infall rate as two successive, exponentially declining bursts as in \citet{Chiappini2001-AbundanceGradients}:
@@
 The choice of DTD primarily affects the location of the high-$\alpha$ ``knee'' in the [Fe/H]--[O/Fe] abundance tracks.
-At one extreme is the triple-system model, which sees the CC SN plateau extend up to [Fe/H]$\approx0.8$ followed by a sharp downward turn as the SN Ia rate suddenly increases at a delay time of 500 Myr.
+At one extreme is the triple-system model, which sees the CC SN plateau extend up to ${\rm [Fe/H]}\approx0.8$ followed by a sharp downward turn as the SN Ia rate suddenly increases at a delay time of 500 Myr.
 Star formation proceeds for such a long time before the knee that the [O/Fe] distribution shows a slight second peak around the CC SN value; this model is the only one which produces any amount of bimodality in the one-zone simulations.
-At the other extreme are the two-population and power-law ($\alpha=-1.1$) models which peak immediately after the minimum delay time of 40 Myr, placing the knee at [Fe/H]$\approx-1.8$.
-The two-population model has a unique second knee at [Fe/H]$\sim-0.2$ and [O/Fe]$\sim0.1$, which is a result of the delayed exponential component.
+At the other extreme are the two-population and power-law ($\alpha=-1.1$) models which peak immediately after the minimum delay time of 40 Myr, placing the knee at ${\rm [Fe/H]}\approx-1.8$.
+The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is a result of the delayed exponential component.
 The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models lie in the intermediate space between these extremes.
@@
 The inside-out and late-burst models produce similar distributions because of the similarity of their underlying SFHs \textemdash both skew heavily toward near-Solar [O/Fe], although the late-burst model produces a slightly broader peak and a less-prominent high-[O/Fe] tail.
-The only region which shows any significant skew toward high [O/Fe] is $R_{\rm gal}=3-5$ kpc and $|z|=1-2$ kpc, but the shift to higher [O/Fe] at high latitudes is gradual and does not produce the notable trough at [O/Fe]$\approx0.2$ which is seen in the APOGEE data.
+The only region which shows any significant skew toward high [O/Fe] is $R_{\rm gal}=3-5$ kpc and $|z|=1-2$ kpc, but the shift to higher [O/Fe] at high latitudes is gradual and does not produce the notable trough at ${\rm [O/Fe]}\approx0.2$ which is seen in the APOGEE data.
 
@@
 
-The two-infall SFH model produces \textit{three} distinct modes at [O/Fe]$\approx 0.0$, $0.2$, and $0.4$.
+The two-infall SFH model produces \textit{three} distinct modes at ${\rm [O/Fe]}\approx 0.0$, $0.2$, and $0.4$.
 At small $R_{\rm gal}$ and with increasing $|z|$, the low-$\alpha$ peak decreases in prominence and the high-$\alpha$ peak increases, but the intermediate peak is a striking feature at all latitudes which is at odds with the APOGEE data.
@@
 The most apparent effect of the DTD is to shift the mode of the high-$\alpha$ sequence.
-The two-population DTD, which has the most prompt SNe Ia of any model in this paper, places the high-$\alpha$ sequence at [O/Fe]$\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.2$ dex higher at [O/Fe]$\approx0.4$.
+The two-population DTD, which has the most prompt SNe Ia of any model in this paper, places the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.2$ dex higher at ${\rm [O/Fe]}\approx0.4$.
 This metric alone would seem to favor the exponential ($\tau=1.5$ Gyr) or plateau ($W=0.3$ Gyr; not shown) models; however,
@@
 
-The inside-out and late-burst models produce similar results, the main difference being a slightly broader core of the abundance distribution around [O/Fe]$\approx0.05$ dex.
+The inside-out and late-burst models produce similar results, the main difference being a slightly broader core of the abundance distribution around ${\rm [O/Fe]}\approx0.05$ dex.
 The Gaussian burst in SFH in the late-burst model introduces a loop in the ISM abundance track, where an uptick in star formation at $t\approx11$ Gyr raises the CCSN rate, leading to a slight increase in [O/Fe] before the subsequent increase in the SN Ia rate brings it back down.
 This same pattern is seen much more strongly in the abundance tracks for the two-infall model: here, the significant infall of pristine gas at $t=4$ Gyr leads to rapid dilution of the ISM, followed by a large burst in the SFR which raises [O/Fe] by $\sim 0.2$ dex.
-In this case the second infall produces a ``ridge line'' in the abundance distribution at [O/Fe]$\approx 0.2$.
+In this case the second infall produces a ``ridge line'' in the abundance distribution at ${\rm [O/Fe]}\approx 0.2$.
 Finally, the early-burst model shows the clearest separation between a high-[O/Fe] track which follows the ISM abundance from low metallicities, and a low-[O/Fe] sequence composed of stars with a wide range of birth radii.
-The early-burst model sees a higher density of points which closely follow the ISM track at [Fe/H]$\lesssim 0.5$ which is likely the result of an increased SFR at early times relative to the other models.
+The early-burst model sees a higher density of points which closely follow the ISM track at ${\rm [Fe/H]}\lesssim 0.5$ which is likely the result of an increased SFR at early times relative to the other models.
 
@@
 
-For the early-burst SFH model, the simulated stellar ages are almost perfectly aligned with the data for [O/Fe]$\gtrsim 0.2$.
+For the early-burst SFH model, the simulated stellar ages are almost perfectly aligned with the data for ${\rm [O/Fe]}\gtrsim 0.2$.
 The rapid rise in the SFE at early times delays the descent to lower [O/Fe] values and produces a clump of low-metallicity, high-[O/Fe] stars at an age of $\sim10$ Gyr.
@@
 Finally, the two-infall SFH model produces the closest overall agreement between the simulated and observed median ages.
-Stars with [O/Fe]$\gtrsim 0.25$ were produced in the first infall, while the second infall produces a clump of stars with similar metallicity, ages of $\sim8$ Gyr, and [O/Fe]$\approx0.2$.
+Stars with ${\rm [O/Fe]}\gtrsim 0.25$ were produced in the first infall, while the second infall produces a clump of stars with similar metallicity, ages of $\sim8$ Gyr, and ${\rm [O/Fe]}\approx0.2$.
 There is an interesting small population of very old, low-$\alpha$ stars which is not seen in any of the other models.

### 2024-02-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 In the double-degenerate (DD) case, two WDs merge after a gravitational-wave inspiral \citep{Iben1984-IaBinary,Webbink1984-DDModel,Pakmor2012-WDMerger} or head-on collision \citep{Benz1989-CollisionalDD,Thompson2011-CollisionalDD}.
-Searches for signs of interaction between the SN ejecta and a non-degenerate companion \citep[e.g.,][]{Panagia2006-RadioEmission,Chomiuk2016-RadioEmission,Fausnaugh2019-EarlyIaLightCurves,Tucker2020-SNeIaSpectra} or for a surviving non-degenerate companion \citep[e.g.,][]{Schaefer2012-ExCompanionSNR,Do2021-Progenitor1972E,Tucker2023-SN2011fe} have placed tight constraints on the SD channel, heavily disfavoring it as the main pathway for producing ``normal'' SNe Ia.
+Searches for signs of interaction between the SN ejecta and a non-degenerate companion \citep[e.g.,][]{Panagia2006-RadioEmission,Chomiuk2016-RadioEmission,Fausnaugh2019-EarlyIaLightCurves,Tucker2020-SNeIaSpectra,Dubay2022-SNeIaCSM} or for a surviving companion \citep[e.g.,][]{Schaefer2012-ExCompanionSNR,Do2021-Progenitor1972E,Tucker2023-SN2011fe} have placed tight constraints on the SD channel, heavily disfavoring it as the main pathway for producing ``normal'' SNe Ia.
 The DD channel, now the preferred model, faces issues of its own with matching observed SN Ia rates because not all WD mergers may lead to a thermonuclear explosion \citep[e.g.,][]{NomotoIben1985-DDMergers,SaioNomoto1998-DDMergers,Shen2012-DDMergers}, and the progenitor systems are difficult to detect even within our own Galaxy \citep{RebassaMansergas2019-WhereAreDDProgenitors}.
@@
         f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the SFR in the late-burst model \\
+        \uptau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the SFE timescale in the early-burst model \\
         f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the IFR in the early-burst model \\
-        \uptau_{*,\rm EB}(t|R_{\rm gal})  & Equation \ref{eq:earlyburst-conroy22} & \ref{sec:sfh}   & Time-dependence of the SFE timescale in the early-burst model \\
         f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the IFR in the two-infall model \\
@@
 
-In addition to the DTD shape, the minimum SN Ia delay time $t_D$ is another parameter which can have an effect on chemical evolution observables, such as the location of the high-$\alpha$ knee and the [O/Fe] DF \citep{Andrews2017-ChemicalEvolution}.
+In addition to the DTD shape, the minimum SN Ia delay time $t_D$ is another parameter which can have an effect on chemical evolution observables, such as the location of the high-$\alpha$ knee and the [O/Fe] distribution function (DF) \citep{Andrews2017-ChemicalEvolution}.
 The value of $t_D$ is set by the lifetime of the most massive SN Ia progenitor system.
@@
 We consider four models for the SFH: inside-out, late-burst, early-burst, and two-infall.
-The first two models are taken from \citetalias{Johnson2021-Migration} and are run in VICE's ``star formation mode,'' where the SFR surface density $\dot\Sigma_*$ is prescribed along with the star formation efficiency (SFE) timescale $\tau_*\equiv \Sigma_g/\dot\Sigma_*$.
+The first two models are taken from \citetalias{Johnson2021-Migration} and are run in VICE's ``star formation mode,'' where the SFR surface density $\dot\Sigma_*$ is prescribed along with the star formation efficiency (SFE) timescale $\uptau_*\equiv \Sigma_g/\dot\Sigma_*$.
 The remaining quantities, infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
-The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$ and $\tau_*$.
+The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$ and $\uptau_*$.
 All models have zero initial gas mass in all zones.
@@
     \includegraphics[width=\linewidth]{figures/star_formation_histories.pdf}
-    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
+    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\uptau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
 In each panel, we plot curves for the simulation zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
@@
 \begin{equation}
-    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm sfh}}
+    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm sfh}},
     \label{eq:insideout-sfh}
@@
 \begin{equation}
-    f_{\rm LB}(t|R_{\rm gal}) = f_{\rm IO}(t|R_{\rm gal}) \Big(1 + A_b e^{-(t-t_b)^2/2\sigma_b^2} \Big)
+    f_{\rm LB}(t|R_{\rm gal}) = f_{\rm IO}(t|R_{\rm gal}) \Big(1 + A_b e^{-(t-t_b)^2/2\sigma_b^2} \Big),
     \label{eq:lateburst-sfh}
@@
 \begin{equation}
-    \frac{\tau_{\rm EB}}{1\,\rm{Gyr}} =
+    \frac{\uptau_{\rm EB}}{1\,\rm{Gyr}} =
     \begin{cases}
@@
 \end{equation}
-In contrast to the previous SFH models, we run the early-burst model in ``infall'' mode.
+In contrast to the previous SFH models, we run the early-burst model in VICE's ``infall'' mode.
 While \citet{Conroy2022-ThickDisk} use a constant infall rate in their one-zone model, we adopt a radially-dependent infall rate which declines exponentially with time:
 \begin{equation}
-    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}}
+    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}},
     \label{eq:earlyburst-ifr}
@@
 where $\tau_{\rm sfh}$ is the same as in the inside-out case.
-To calculate $\dot \Sigma_*$ from the above quantities, we modify the fiducial star formation law adopted from \citetalias{Johnson2021-Migration}, substituting $\tau_{\rm EB}$ for the SFE timescale of molecular gas:
+To calculate $\dot \Sigma_*$ from the above quantities, we modify the fiducial star formation law adopted from \citetalias{Johnson2021-Migration}, substituting $\uptau_{\rm EB}$ for the SFE timescale of molecular gas:
 \begin{equation}
@@
     \begin{cases}
-        \Sigma_g \tau_{\rm EB}^{-1}, & \Sigma_g \geq \Sigma_{g,2} \\
-        \Sigma_g \tau_{\rm EB}^{-1} \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
-        \Sigma_g \tau_{\rm EB}^{-1} \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1},
+        \Sigma_g \uptau_{\rm EB}^{-1}, & \Sigma_g \geq \Sigma_{g,2} \\
+        \Sigma_g \uptau_{\rm EB}^{-1} \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
+        \Sigma_g \uptau_{\rm EB}^{-1} \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1},
     \end{cases}
@@
 
-\paragraph{Two-infall} [Expand]
-We parameterize the infall rate as two successive, exponentially declining bursts as in \citet{Chiappini2001-AbundanceGradients}:
+\paragraph{Two-infall} First proposed by \citet{Chiappini1997-TwoInfall}, this model parameterizes the infall rate as two successive, exponentially declining bursts to explain the origin of the thick and thin disks:
 \begin{equation}
     \label{eq:twoinfall-ifr}
-    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2}
-\end{equation}
-In this model, the first infall produces the thick disk and the second infall produces the thin disk.
+    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2},
+\end{equation}
+% In this model, the first infall produces the thick disk and the second infall produces the thin disk. 
+where $N_1$ and $N_2$ are the normalizations of the first and second infall, respectively, and $t_{\rm on}$ is the onset time of the second infall.
 The normalization ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
@@
 Following \citet{BlandHawthornGerhard2016-MilkyWayReview}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
+We note that some previous studies which use the two-infall model \citep[e.g.,][]{Spitoni2021-TwoInfall} do not consider gas outflows, and instead adjust the nucleosynthetic yields to reproduce the Solar abundance.
+We adopt radially-dependent outflows as in \citetalias{Johnson2021-Migration} (see their Section 2.4 for details) for all our SFH models, including two-infall.
+We discuss the implications of this difference in Section \ref{sec:two-infall-discussion}.
 
@@
 We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt}APOGEE stars with age estimates.
-The median uncertainty in log-age space is $\sim 0.1$.
+Table \ref{tab:uncertainties} presents the median uncertainties in the data for [Fe/H], [O/Fe], and age.
 
@@
 
+\begin{deluxetable}{lll}
+    \tablecaption{Median Parameter Uncertainties\label{tab:uncertainties}}
+    \tablehead{
+        \colhead{Parameter} & \colhead{Median Uncertainty} & \colhead{Source}
+    }
+    \startdata
+        ${\rm [Fe/H]}$ & $9.2\times10^{-3}$ & APOGEE DR17 \\
+        ${\rm [O/Fe]}$ & $1.8\times10^{-2}$ & APOGEE DR17 \\
+        log(Age/Gyr) & $0.10$ & \citetalias{Leung2023-Ages}
+        % Age/Gyr & 29\% & astroNN
+    \enddata
+\end{deluxetable}
+
 \section{Results from One-Zone Models}
@@
 A one-zone model assumes the entire gas reservoir is instantaneously mixed, so there is no spatial dependence for the distribution of metal abundances.
-In this section
+This limits the ability to compare to observations across the disk, but it allows the models to be run in a fraction of the time and eliminates the complicating factor of stellar migration.
+In this section, we compare the results from one-zone models which examine various parameters of the DTD while keeping other parameters fixed.
 
 All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=0.01$ Gyr.
-We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr), an SFE timescale $\tau_*\equiv M_g/\dot M_*=2$ Gyr, and an initial gas mass $M_{g,0}=0$.
+We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr), an SFE timescale $\uptau_*\equiv M_g/\dot M_*=2$ Gyr, and an initial gas mass $M_{g,0}=0$.
 We adopt a continuous recycling prescription \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
 Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time of 40 Myr.
-A summary of these one-zone fiducial parameters is presented in Table \ref{tab:onezone-parameters}.
+A summary of these fiducial parameters is presented in Table \ref{tab:onezone-parameters}.
 \begin{deluxetable}{Ccl}
@@
     \eta            & 2.15      & Outflow mass-loading factor \\
-    \tau_*          & 2.0 Gyr   & SFE timescale \\
+    \uptau_*        & 2.0 Gyr   & SFE timescale \\
     \dot M_r        & continuous    & Recycling rate \\
@@
 A steeper slope produces a sharper ``knee'' and a faster decline in [O/Fe], resulting in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
-Conversely, a shallower slope produces a gentler knee and slower decline in [O/Fe], resulting in a broader [O/Fe] distribution and a greater number of high-$\alpha$ stars.
-In all cases the [O/Fe] distribution is distinctly unimodal.
-The distribution of [Fe/H] is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
+Conversely, a shallower slope produces a gentler knee and slower decline in [O/Fe], resulting in a broader [O/Fe] DF and a greater number of high-$\alpha$ stars.
+In all cases the [O/Fe] DF is distinctly unimodal.
+The [Fe/H] DF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
+
+Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in the middle panel of Figure \ref{fig:onezone-threepanel}.
+Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around a simulation time of 1 Gyr.
+A short exponential timescale shifts this knee down to lower [O/Fe] values, while a longer timescale raises it.
+The effect on the [O/Fe] DF is similar to the power-law slope: a short timescale produces more low-$\alpha$ stars, while a long timescale produces more high-$\alpha$ stars (but still a unimodal distribution).
+The effect on the [Fe/H] DF is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values.
+A doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
+For all exponential models, the low-$\alpha$ peak sits approximately 0.02 dex lower than for the power-law models.
+
+Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of the plateau DTD model width on abundance tracks and distributions.
+The effect on the [O/Fe] DF is similar to the previous two models: a longer plateau raises the median delay time, resulting in a smaller low-$\alpha$ peak and a more prominent high-$\alpha$ tail.
+The abundance tracks from several different plateau widths fill the space in between the exponential ($\tau=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
+The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\tau=3$ Gyr), although the [O/Fe] DFs are somewhat more distinct, with the plateau model producing a peak closer to the power-law case.
 
@@
 The open symbols located along each curve mark logarithmic steps in simulation time.
-The marginal panels above and to the right of the central panel present the distributions of [Fe/H] and [O/Fe], respectively.
+The marginal panels above and to the right of the central panel present the distribution functions (DFs) of [Fe/H] and [O/Fe], respectively.
 For display purposes, these distributions are convolved with a Gaussian kernel with a standard deviation of 0.02 dex.
@@
 
-Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in the middle panel of Figure \ref{fig:onezone-threepanel}.
-Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around a simulation time of 1 Gyr.
-A short exponential timescale shifts this knee down to lower [O/Fe] values, while a longer timescale raises it.
-The effect on the [O/Fe] distribution is similar to the power-law slope: a short timescale produces more low-$\alpha$ stars, while a long timescale produces more high-$\alpha$ stars (but still a unimodal distribution).
-The effect on the [Fe/H] distribution is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values.
-A doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
-For all exponential models, the low-$\alpha$ peak sits approximately 0.02 dex lower than for the power-law models.
-
-Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of the plateau DTD model width on abundance tracks and distributions.
-The effect on the [O/Fe] distribution is similar to the previous two models: a longer plateau raises the median delay time, resulting in a smaller low-$\alpha$ peak and a more prominent high-$\alpha$ tail.
-The abundance tracks from several different plateau widths fill the space in between the exponential ($\tau=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
-The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\tau=3$ Gyr), although the [O/Fe] distributions are somewhat more distinct.
-
 One parameter of the DTD which we hold fixed in the multi-zone models is the minimum SN Ia delay time $t_D$.
-Typical choices for $t_D$ in the literature range from $\sim 40$ Myr to 150 Myr.
-The left-hand panel of Figure \ref{fig:onezone-twopanel} shows that the minimum SN Ia delay time has a much stronger effect on the abundance track and MDFs of models which assume a power-law DTD than models which assume a plateau or exponential DTD, due to the much higher SN Ia rate in the power-law models at early times (see Figure \ref{fig:dtds}).
-Moreover, a power-law DTD with a long minimum delay may be observationally hard to distinguish from a plateau model.
-In Figure \ref{fig:onezone-twopanel}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (dashed purple line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (solid green line), and the [O/Fe] distributions are virtually identical.
+Typical choices for $t_D$ in the literature range from $\sim 30$ Myr \citep[e.g.,][]{Poulhazan2018-PrecisionPollution} to 150 Myr \citepalias[e.g.,][]{Johnson2021-Migration}.
+The left-hand panel of Figure \ref{fig:onezone-twopanel} shows that $t_D$ has a much stronger effect on the abundance tracks and distributions of models which assume a power-law DTD than models which assume a plateau or exponential DTD.
+This is a consequence of the much higher number of prompt SNe Ia in the power-law models compared to the others (see Figure \ref{fig:dtds}).
+Moreover, a power-law DTD with a long $t_D$ may be observationally hard to distinguish from a plateau model.
+In Figure \ref{fig:onezone-twopanel}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (dashed purple line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (solid green line), and their [O/Fe] DFs are virtually identical.
 The difference between the two values of $t_D$ for the exponential ($\tau=3$ Gyr) DTD in both the abundance tracks and distributions is nearly indistinguishable.
 We do not consider the effect on the other DTD models because a 150 Myr minimum delay time is incompatible with the two-population model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD due to its low SN Ia rate at short delay times.
+
+The right-hand panel of Figure \ref{fig:onezone-twopanel} compares the one-zone model outputs from the full range of DTD models we investigate in this work.
+As with the individual DTD parameters, the choice of DTD primarily affects the location of the high-$\alpha$ ``knee'' in the [Fe/H]--[O/Fe] abundance tracks.
+At one extreme is the triple-system model, which sees the CC SN plateau extend up to ${\rm [Fe/H]}\approx0.8$ followed by a sharp downward turn as the SN Ia rate suddenly increases at a delay time of 500 Myr.
+Star formation proceeds for such a long time before the knee that the [O/Fe] DF shows a slight second peak around the CC SN value; this model is the only one which produces any amount of bimodality in the one-zone simulations.
+At the other extreme are the two-population and power-law ($\alpha=-1.1$) models which peak immediately after the minimum delay time of 40 Myr, placing the knee at ${\rm [Fe/H]}\approx-1.8$.
+The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is a result of the delayed exponential component.
+The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models lie in the intermediate space between these extremes.
+On the other hand, the [O/Fe] DF from the exponential model has the strongest peak, while the plateau ($W=1$ Gyr) and triple-system models produce nearly identical distributions in the low-$\alpha$ regime.
+The power-law ($\alpha=-1.1$) and two-population DTDs produce similar [O/Fe] DFs despite notably different abundance tracks.
+The exponential ($\tau=3$ Gyr) and plateau ($W=0.3$ Gyr) models, while not shown, produce similar abundance tracks to the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models, respectively.
 
@@
 
-The right-hand panel of Figure \ref{fig:onezone-twopanel} compares the one-zone model outputs from the full range of DTD models we investigate in this work.
-The choice of DTD primarily affects the location of the high-$\alpha$ ``knee'' in the [Fe/H]--[O/Fe] abundance tracks.
-At one extreme is the triple-system model, which sees the CC SN plateau extend up to ${\rm [Fe/H]}\approx0.8$ followed by a sharp downward turn as the SN Ia rate suddenly increases at a delay time of 500 Myr.
-Star formation proceeds for such a long time before the knee that the [O/Fe] distribution shows a slight second peak around the CC SN value; this model is the only one which produces any amount of bimodality in the one-zone simulations.
-At the other extreme are the two-population and power-law ($\alpha=-1.1$) models which peak immediately after the minimum delay time of 40 Myr, placing the knee at ${\rm [Fe/H]}\approx-1.8$.
-The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is a result of the delayed exponential component.
-The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models lie in the intermediate space between these extremes.
-On the other hand, the [O/Fe] distribution from the exponential model is the most strongly peaked at the Solar value, while the plateau ($W=1$ Gyr) and triple-system models produce nearly identical distributions in the low-$\alpha$ regime.
-The exponential ($\tau=3$ Gyr) and plateau ($W=0.3$ Gyr) models, while not shown, produce similar abundance tracks to the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models, respectively.
-
-[Summary and conclusions from one-zone models]
+% [Summary and conclusions from one-zone models]
+The results presented in this section indicate that the observables which should show the greatest effect from the choice of DTD are the [O/Fe]--[Fe/H] abundance tracks and the [O/Fe] DF.
+Degeneracies between models in one regime, such as the abundance tracks from the exponential ($\tau=3$ Gyr) and plateau ($W=1$ Gyr) DTDs, can be resolved in the other.
+Of course, both of these observables are also greatly affected by the parameters of the SFH.
+We direct the reader to \citet{Palicio2023-AnalyticDTD} for a similar comparison of DTD models with a two-infall SFH.
 
@@
 
-% Figure \ref{fig:onezone-delay-taustar} shows results from one-zone models with a power-law DTD which differ in their assumed minimum SN Ia delay time ($t_D$) or star formation efficiency timescale ($\tau_*$).
+% Figure \ref{fig:onezone-delay-taustar} shows results from one-zone models with a power-law DTD which differ in their assumed minimum SN Ia delay time ($t_D$) or star formation efficiency timescale ($\uptau_*$).
 In [Fe/H]-[O/Fe] space, doubling or halving the minimum delay time produces similar results to doubling or halving the SFE timescale.
@@
 %     \includegraphics{figures/onezone_delay_taustar.pdf}
-%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\tau_*$).
-Tracks with $\tau_*=2$ Gyr are represented in black, while a track with a shorter $\tau_*=1$ Gyr is shown in red and a track with a longer $\tau_*=4$ Gyr is in yellow.
+%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\uptau_*$).
+Tracks with $\uptau_*=2$ Gyr are represented in black, while a track with a shorter $\uptau_*=1$ Gyr is shown in red and a track with a longer $\uptau_*=4$ Gyr is in yellow.
 The dotted, solid, and dashed black curves represent a minimum delay time of 40 Myr, 80 Myr, and 160 Myr, respectively.
@@
 \label{sec:multizone-results}
-
-\begin{deluxetable}{lll}
-    \tablecaption{Median Parameter Uncertainties\label{tab:uncertainties}}
-    \tablehead{
-        \colhead{Parameter} & \colhead{Median Uncertainty} & \colhead{Source}
-    }
-    \startdata
-        [Fe/H] & $9.2\times10^{-3}$ & APOGEE DR17 \\
-        $\rm [O/Fe]$ & $1.8\times10^{-2}$ & APOGEE DR17 \\
-        log(Age/Gyr) & $0.10$ & \citetalias{Leung2023-Ages}
-        % Age/Gyr & 29\% & astroNN
-    \enddata
-\end{deluxetable}
 
@@
 \subsection{The Two-Infall SFH Model}
+\label{sec:two-infall-discussion}
 
@@
 The right-hand panel of Figure \ref{fig:analytical-dtd} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs.
-We assume $\eta=2.5$, $\tau_*=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
+We assume $\eta=2.5$, $\uptau_*=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
 We compare the SD, DD WIDE, and DD CLOSE schemes to standard power-law, broken power-law, and exponential DTDs.

### 2024-02-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \newcommand{\aFe}{[$\alpha$/Fe]\xspace}
+\newcommand{\vice}{{\tt VICE}\xspace}
 
@@
 Because the DTD also affects the relationship among age, [Fe/H], and \aFe in chemical evolution models, comparison with observations of stars in the Milky Way is an important consistency check for any proposed DTD.
-We implement several popular forms of the DTD in combination with multiple star formation histories for the Milky Way in one-zone and multi-zone chemical evolution models using the Versatile Integrator for Chemical Evolution (VICE).
-VICE includes a prescription for radial stellar migration in multi-zone models.
+We implement several popular forms of the DTD in combination with multiple star formation histories for the Milky Way in one-zone and multi-zone chemical evolution models using the Versatile Integrator for Chemical Evolution (\vice).
+\vice includes a prescription for radial stellar migration in multi-zone models.
 We compare our predicted interstellar medium abundance tracks, stellar abundance distributions, and stellar age distributions to the final data release of the Apache Point Observatory Galactic Evolution Experiment (APOGEE).
@@
 This paper presents the first comprehensive look at the DTD in a multi-zone GCE model that can qualitatively reproduce the observed abundance structure of the Milky Way disk.
-We evaluate a selection of DTD models from the literature with multiple SFHs and a prescription for radial stellar migration in the Versatile Integrator for Chemical Evolution \citep[VICE;][]{JohnsonWeinberg2020-Starbursts}.
+A multi-zone approach allows for a radially-dependent parameterization of the SFH, outflows, stellar migration, and abundance gradient which can better match observations across the Galactic disk.
+We evaluate a selection of DTD models from the literature with multiple SFHs and a prescription for radial stellar migration in the Versatile Integrator for Chemical Evolution \citep[\vice;][]{JohnsonWeinberg2020-Starbursts}.
 In Section \ref{sec:methods}, we present our models for the DTD and SFH, and we describe our chemical evolution models.
@@
 
-We make use of the multi-zone simulation tools in VICE developed by \citet{Johnson2021-Migration} (hereafter \citetalias{Johnson2021-Migration}).
+We make use of the multi-zone simulation tools in \vice developed by \citet{Johnson2021-Migration} (hereafter \citetalias{Johnson2021-Migration}).
 The basic setup of our models follows theirs: the simulated Galaxy is a disk with a radius of 20 kpc and is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
@@
 We run our simulations with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
-Following \citetalias{Johnson2021-Migration}, we set VICE to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_*=0$ for $R_{\rm gal}>R_{\rm SF}$ (stars are allowed to migrate past $R_{\rm SF}$, they are just not born there).
-
-Table \ref{tab:multizone-parameters} summarizes many of the parameters in our multi-zone models.
+Following \citetalias{Johnson2021-Migration}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_*=0$ for $R_{\rm gal}>R_{\rm SF}$ (stars are allowed to migrate past $R_{\rm SF}$, they are just not born there).
+We summarize the parameters for our multi-zone models in Table \ref{tab:multizone-parameters}.
 
@@
     \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models.
-We omit parameters which have been left unchanged from \citetalias{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
+We omit parameters that are unchanged from \citetalias{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
     \tablehead{
@@
         % DTD
-        R_{\rm Ia}(t)   & Equations \ref{eq:powerlaw-dtd}--\ref{eq:prompt-dtd}  & \ref{sec:dtd-models}  & Delay time distribution of Type Ia supernovae \\
+        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & Delay time distribution of Type Ia supernovae \\
         t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
@@
         % Star formation histories
-        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & \ref{sec:sfh} & Time-dependence of the SFR in the inside-out model \\
-        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the SFR in the late-burst model \\
-        \uptau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the SFE timescale in the early-burst model \\
-        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the IFR in the early-burst model \\
-        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the IFR in the two-infall model \\
+        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & \ref{sec:sfh} & Time-dependence of the inside-out SFR \\
+        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the late-burst SFR \\
+        \uptau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the early-burst SFE timescale \\
+        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the early-burst IFR \\
+        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the two-infall IFR \\
     \enddata
@@
 Both elements are produced by CCSNe.
-VICE adopts the instantaneous recycling approximation for CCSNe, so the equation which governs CCSN enrichment as a function of star formation for some element $x$ is simply
+\vice adopts the instantaneous recycling approximation for CCSNe, so the equation which governs CCSN enrichment as a function of star formation for some element $x$ is simply
 \begin{equation}
@@
 where $y_x^{\rm CC}$ is the CCSN yield of element $x$ per unit mass of star formation, and $\dot M_*$ is the SFR. 
-Following \citetalias{Johnson2021-Migration}, who in turn adopt their yields from \citet{Weinberg2017-ChemicalEquilibrium}, we adopt $y_{\rm O}^{\rm CC}=0.015$ and $y_{\rm Fe}^{\rm CC}=0.0012$.
-The primary effect of these yields is to set the ``plateau'' in [O/Fe] which represents pure CCSN enrichment.
-The chosen yields for this paper produce a plateau at [O/Fe]$=0.45$; see \citet{Weinberg2023-CCSNYield} for more discussion.
+Following \citetalias{Johnson2021-Migration}, who in turn adopt their CCSN yields from \citet{ChieffiLimongi2004-CCSNYields} and \citet{LimongiChieffi2006-CCSNYields}, we adopt $y_{\rm O}^{\rm CC}=0.015$ and $y_{\rm Fe}^{\rm CC}=0.0012$.
+The primary effect of these yields is to set the low-[Fe/H] ``plateau'' in [O/Fe] which represents pure CCSN enrichment.
+The chosen yields for this paper produce a plateau at ${\rm [O/Fe]}=0.45$; see \citet{Weinberg2023-CCSNYield} for more discussion on the effect of the CCSN yields on chemical evolution.
 
@@
 \begin{equation}
-    y_{\rm Fe}^{\rm Ia} = m_{\rm Fe}^{\rm Ia} \int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt' = m_{\rm Fe}^{\rm Ia} \frac{N_{\rm Ia}}{M_*}
+    y_{\rm Fe}^{\rm Ia} = m_{\rm Fe}^{\rm Ia} \int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt' = m_{\rm Fe}^{\rm Ia} \frac{N_{\rm Ia}}{M_*},
     \label{eq:dtd-integral}
 \end{equation}
-where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia.
-We take the average number of SNe Ia per mass of stars formed to be $N_{\rm Ia}/M_*=2.2\times10^{-3}\,{\rm M}_\odot^{-1}$ from \citet{MaozMannucci2012-SNeIaReview}.%, which gives $R_{\rm Ia}$ units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$.
-Following \citetalias{Johnson2021-Migration}, we take $y_{\rm Fe}^{\rm Ia}=0.00214$.
-This yield was selected so that the inside-out SFH model produces stars with [O/Fe]$\approx 0.0$ by the end of the simulation.
-SNe Ia do not contribute O so $y_{\rm O}^{\rm Ia}=0$.
+where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia, and $N_{\rm Ia}/M_*=2.2\times10^{-3}\,{\rm M}_\odot^{-1}$ is the average number of SNe Ia per mass of stars formed \citep{MaozMannucci2012-SNeIaReview}.
+Adjusting the value of $y_{\rm Fe}^{\rm Ia}$ primarily affects the end point of chemical evolution tracks in [O/Fe]--[Fe/H] space. 
+Following \citetalias{Johnson2021-Migration}, we adopt $y_{\rm Fe}^{\rm Ia}=0.00214$.
+This yield was originally adapted from the W70 model of \citet{Iwamoto1999-SNIaYields}, but was slightly modified so that the inside-out SFH model produces stars with ${\rm [O/Fe]}\approx 0.0$ by the end of the simulation.
+\citet{Palla2021-SNIaYield} studies the effect of different SN Ia yields on GCE models in detail.
 
@@
 We explore five different functional forms for the SN Ia DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, a two-population model, and a model based on triple-system dynamics, with a one or two variants of each.
-We present the unnormalized functional forms for $R_{\rm Ia}(t)$ below; VICE automatically normalizes and scales the DTD to produce the correct number of SNe Ia over the lifetime of the Galaxy.
 Figure \ref{fig:dtds} presents these DTDs as a function of time after star formation, and Table \ref{tab:dtds} summarizes the DTD models and their parameters.
+We use simple forms rather than simulated physical or analytical models of SNe Ia for the sake of decreased computational time.
+Additionally, physically-motivated models of the DTD must contend with many unknown or poorly-constrained parameters, so our simple forms allow us to reduce the number of free parameters.
+In Appendix \ref{app:analytical-dtds}, we show that a few of our simple forms adequately approximate the more complete analytical models of \citet{Greggio2005-AnalyticalRates}.
+
+In this subsection we present unnormalized functional forms $f_{\rm Ia}$ for each DTD model.
+The relationship between $f_{\rm Ia}$, which has units of ${\rm Gyr}^{-1}$, and $R_{\rm Ia}$, which has units of ${\rm M}_\odot^{-1}\,{\rm Gyr}^{-1}$, is:
+\begin{equation}
+    R_{\rm Ia}(t) = 
+    \begin{cases}
+        \frac{N_{\rm Ia}}{M_*}
+        \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
+        0 & t < t_D.
+    \end{cases}
+    \label{eq:dtd-function}
+\end{equation}
+\vice automatically normalizes the provided function for the DTD according to this equation.
 
@@
     \caption{Selection of models for the SN Ia delay time distribution (DTD) used in this paper.
-All functions are normalized such that $R_{\rm Ia}(t=1\,{\rm Gyr})=1$.
+All functions are normalized such that $f_{\rm Ia}(t=1\,{\rm Gyr})=1$.
 The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD} at the same scale as the DTD models.
@@
 \begin{equation}
-    R_{\rm Ia}(t) \propto (t/1\,\rm{Gyr})^\alpha
+    f_{\rm Ia}^{\rm plaw}(t) = (t/1\,\rm{Gyr})^\alpha
     \label{eq:powerlaw-dtd}
@@
 A declining power-law with $\alpha\sim-1$ is expected to arise from typical assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral \citep[see Section 3.5 from][]{Maoz2014-Review}.
-It is therefore a commonly assumed DTD in GCE studies \citepalias[e.g.,][]{Johnson2021-Migration}.
+It is therefore a commonly assumed DTD in GCE studies (e.g., \citealt{Rybizki2017-Chempy}; \citetalias{Johnson2021-Migration}).
 Additionally, the observational evidence for a power-law DTD is strong.
@@
 \begin{equation}
-    R_{\rm Ia}(t) \propto
+    f_{\rm Ia}^{\rm plat}(t) =
     \begin{cases}
@@
 % where $B_W=[(W-t_{\rm min}) + \frac{t_{\rm max}^{\alpha+1} - W^{\alpha+1}}{(\alpha+1)W^\alpha}]^{-1}$ is the normalization coefficient.
-Our primary motivation is to consider a model which matches observations at delay times beyond a few Gyr, where the DTD is best constrained, but which has a much smaller fraction of prompt ($\lesssim 100$ Myr) SNe Ia.
+Our primary motivation is to consider a model which matches observations at delay times beyond a few Gyr, where the DTD is best constrained, but which has a much smaller fraction of prompt ($\lesssim 100$ Myr) SNe Ia than the simple power law.
 To our knowledge, this form of the DTD has not been considered in previous studies.
@@
 \begin{equation}
-    R_{\rm Ia}(t) \propto
+    f_{\rm Ia}^{\rm triple}(t) =
     \begin{cases}
@@
 \begin{equation}
-    R_{\rm Ia}(t) \propto \frac{1}{\tau} e^{-t/\tau}
+    f_{\rm Ia}^{\rm exp}(t) = \frac{1}{\tau} e^{-t/\tau}
     \label{eq:exponential-dtd}
@@
 \begin{equation}
-    R_{\rm Ia}(t) \propto 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
+    f_{\rm Ia}^{\rm twopop}(t) = 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
     \label{eq:prompt-dtd}
@@
 We consider four models for the SFH: inside-out, late-burst, early-burst, and two-infall. 
-The first two models are taken from \citetalias{Johnson2021-Migration} and are run in VICE's ``star formation mode,'' where the SFR surface density $\dot\Sigma_*$ is prescribed along with the star formation efficiency (SFE) timescale $\uptau_*\equiv \Sigma_g/\dot\Sigma_*$.
-The remaining quantities, infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
+The former two models, which feature a smooth SFH, were investigated by \citetalias{Johnson2021-Migration} using a similar methodology to this work.
+The inside-out model produced a better agreement to the age--[O/Fe] relation observed by \citet{Feuillet2019-MilkyWayAges}, while the late-burst model better matched their observed age--metallicity relation.
+The latter two models (early-burst and two-infall) feature discontinuous or ``bursty'' SFHs, and were proposed by \citet{Conroy2022-ThickDisk} and \citet{Chiappini1997-TwoInfall}, respectively, to explain the distinct evolution of the high- and low-$\alpha$ sequences.
+Together, these four models cover a range of behavior including a smooth SFH and SFR-, SFE-, and infall-driven starbursts.
+
+The inside-out and late-burst models
+% The first two models are taken from \citetalias{Johnson2021-Migration} and 
+are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_*$ is prescribed along with the star formation efficiency (SFE) timescale $\uptau_*\equiv \Sigma_g/\dot\Sigma_*$.
+The remaining quantities, infall rate (IFR) surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
 The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$ and $\uptau_*$.
+The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four equations are specified.
+See Appendix B of \citetalias{Johnson2021-Migration} for details on the normalization of the SFH.
 All models have zero initial gas mass in all zones.
@@
 where we assume $\tau_{\rm rise}=2$ Gyr for all radii.
-The SFH timescale $\tau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\tau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the Solar annulus and longer timescales in the outer galaxy.
+The SFH timescale $\tau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\tau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the Solar annulus and longer timescales in the outer Galaxy.
 The $\tau_{\rm sfh} - R_{\rm gal}$ relation is determined from the data of \citet{Sanchez2020-StarFormationTimescales}; see Section 2.5 of \citetalias{Johnson2021-Migration} for the details.
-For a detailed look at the normalization of the SFR with $R_{\rm gal}$, we refer the reader to Appendix B of \citetalias{Johnson2021-Migration}.
+% For a detailed look at the normalization of the SFR with $R_{\rm gal}$, we refer the reader to Appendix B of \citetalias{Johnson2021-Migration}.
 
@@
 where $A_b$ is the dimensionless amplitude of the starburst, $t_b$ is the time of the peak of the burst, and $\sigma_b$ is the width of the Gaussian. 
-Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr.
-The determination of $\tau_{\rm sfh}$
+Evidence for a recent star formation burst $\sim 2-3$ Gyr ago has been found in {\it Gaia} \citep{Mor2019-Starburst} and in massive WDs in the Solar neighborhood \citep{Isern2019-Starburst}.
+Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr. The determination of $\tau_{\rm sfh}$ 
 % and the normalization of the SFR as a function of $R_{\rm gal}$ 
@@
 \end{equation}
-In contrast to the previous SFH models, we run the early-burst model in VICE's ``infall'' mode.
+In contrast to the previous SFH models, we run the early-burst model in \vice's ``infall'' mode.
 While \citet{Conroy2022-ThickDisk} use a constant infall rate in their one-zone model, we adopt a radially-dependent infall rate which declines exponentially with time:
@@
 
-\paragraph{Two-infall} First proposed by \citet{Chiappini1997-TwoInfall}, this model parameterizes the infall rate as two successive, exponentially declining bursts to explain the origin of the thick and thin disks:
+\paragraph{Two-infall} First proposed by \citet{Chiappini1997-TwoInfall}, this model parameterizes the infall rate as two successive, exponentially declining bursts to explain the origin of the high- and low-$\alpha$ disk populations:
 \begin{equation}
@@
 Following \citet{BlandHawthornGerhard2016-MilkyWayReview}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
-We note that some previous studies which use the two-infall model \citep[e.g.,][]{Spitoni2021-TwoInfall} do not consider gas outflows, and instead adjust the nucleosynthetic yields to reproduce the Solar abundance.
+We note that some previous studies which use the two-infall model \citep[e.g.,][]{Spitoni2021-TwoInfall} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the Solar abundance.
 We adopt radially-dependent outflows as in \citetalias{Johnson2021-Migration} (see their Section 2.4 for details) for all our SFH models, including two-infall.
@@
 Table \ref{tab:sample-selection} lists our selection criteria, which largely follow from \citet{Hayden2015-ChemicalCartography}.
-This produces a final sample of \variable{output/sample_size.txt}stars.
+This produces a final sample of \variable{output/sample_size.txt}stars with [O/Fe] and [Fe/H] abundance measurements.
 APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
@@
 We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt}APOGEE stars with age estimates.
+We note that we use the full sample of \variable{output/sample_size.txt}APOGEE stars unless we explicitly compare to age estimates.
 Table \ref{tab:uncertainties} presents the median uncertainties in the data for [Fe/H], [O/Fe], and age.
@@
 
-% [Intro paragraph, motivation for running one-zone models]
-Before running the full multi-zone simulations, it will be useful to observe the effects of the DTD in more idealized conditions.
-A one-zone model assumes the entire gas reservoir is instantaneously mixed, so there is no spatial dependence for the distribution of metal abundances.
-This limits the ability to compare to observations across the disk, but it allows the models to be run in a fraction of the time and eliminates the complicating factor of stellar migration.
-In this section, we compare the results from one-zone models which examine various parameters of the DTD while keeping other parameters fixed.
-
-All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=0.01$ Gyr.
-We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr), an SFE timescale $\uptau_*\equiv M_g/\dot M_*=2$ Gyr, and an initial gas mass $M_{g,0}=0$.
-We adopt a continuous recycling prescription \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
-Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time of 40 Myr.
-A summary of these fiducial parameters is presented in Table \ref{tab:onezone-parameters}.
 \begin{deluxetable}{Ccl}
@@
 
-The left-hand panel of Figure \ref{fig:onezone-threepanel} compares the results of three one-zone models which are identical except for the slope of the power-law DTD.
-A steeper slope produces a sharper ``knee'' and a faster decline in [O/Fe], resulting in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
-Conversely, a shallower slope produces a gentler knee and slower decline in [O/Fe], resulting in a broader [O/Fe] DF and a greater number of high-$\alpha$ stars.
-In all cases the [O/Fe] DF is distinctly unimodal.
-The [Fe/H] DF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
-
-Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in the middle panel of Figure \ref{fig:onezone-threepanel}.
-Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around a simulation time of 1 Gyr.
-A short exponential timescale shifts this knee down to lower [O/Fe] values, while a longer timescale raises it.
-The effect on the [O/Fe] DF is similar to the power-law slope: a short timescale produces more low-$\alpha$ stars, while a long timescale produces more high-$\alpha$ stars (but still a unimodal distribution).
-The effect on the [Fe/H] DF is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values.
-A doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
-For all exponential models, the low-$\alpha$ peak sits approximately 0.02 dex lower than for the power-law models.
-
-Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of the plateau DTD model width on abundance tracks and distributions.
-The effect on the [O/Fe] DF is similar to the previous two models: a longer plateau raises the median delay time, resulting in a smaller low-$\alpha$ peak and a more prominent high-$\alpha$ tail.
-The abundance tracks from several different plateau widths fill the space in between the exponential ($\tau=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
-The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\tau=3$ Gyr), although the [O/Fe] DFs are somewhat more distinct, with the plateau model producing a peak closer to the power-law case.
+% [Intro paragraph, motivation for running one-zone models]
+Before running the full multi-zone simulations, it will be useful to observe the effects of the DTD in more idealized conditions.
+A one-zone model assumes the entire gas reservoir is instantaneously mixed, so there is no spatial dependence for the distribution of metal abundances.
+This limits the ability to compare to observations across the disk, but it allows the models to be run in a fraction of the time and eliminates the complicating factor of stellar migration.
+In this section, we compare the results from one-zone models which examine various parameters of the DTD while keeping other parameters fixed.
+
+All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=0.01$ Gyr.
+We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr), an SFE timescale $\uptau_*\equiv M_g/\dot M_*=2$ Gyr, and an initial gas mass $M_{g,0}=0$.
+We adopt a continuous recycling prescription \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
+Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time of 40 Myr.
+A summary of these fiducial parameters is presented in Table \ref{tab:onezone-parameters}.
 
@@
 
+The left-hand panel of Figure \ref{fig:onezone-threepanel} compares the results of three one-zone models that are identical except for the slope of the power-law DTD.
+A steeper slope produces a sharper ``knee'' and a faster decline in [O/Fe], resulting in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
+Conversely, a shallower slope produces a gentler knee and slower decline in [O/Fe], resulting in a broader [O/Fe] DF and a greater number of high-$\alpha$ stars.
+In all cases the [O/Fe] DF is distinctly unimodal.
+The [Fe/H] DF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
+
+Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in the middle panel of Figure \ref{fig:onezone-threepanel}.
+Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around a simulation time of 1 Gyr.
+A short exponential timescale shifts this knee down to lower [O/Fe] values, while a longer timescale raises it.
+The effect on the [O/Fe] DF is similar to the power-law slope: a short timescale produces more low-$\alpha$ stars, while a long timescale produces more high-$\alpha$ stars (but still a unimodal distribution).
+The effect on the [Fe/H] DF is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values.
+A doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
+For all exponential models, the low-$\alpha$ peak sits approximately 0.02 dex lower than for the power-law models.
+
+Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of the plateau DTD model width on abundance tracks and distributions.
+The effect on the [O/Fe] DF is similar to the previous two models: a longer plateau raises the median delay time, resulting in a smaller low-$\alpha$ peak and a more prominent high-$\alpha$ tail.
+The abundance tracks from several different plateau widths fill the space in between the exponential ($\tau=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
+The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\tau=3$ Gyr), although the [O/Fe] DFs are somewhat more distinct, with the plateau model producing a peak closer to the power-law case.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figures/onezone_twopanel.pdf}
+    \caption{\textit{Left:} Comparison of one-zone models with minimum SN Ia delay times of 40 Myr (solid curves) and 150 Myr (dashed curves) for two DTDs: a power-law with $\alpha=-1.1$ (blue curves), and an exponential with $\tau=1.5$ Gyr (purple curves).
+The layout is similar to the plots in Figure \ref{fig:onezone-threepanel}.
+For clarity, we assume a mass-loading factor $\eta=1$ for the exponential DTD curves.
+    \textit{Right:} Comparison of one-zone models which assume all five functional forms for the DTD in this paper: triple-system (green), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
+A minimum SN Ia delay time of 40 Myr is assumed for all models in the right panel.}
+    \label{fig:onezone-twopanel}
+    \script{onezone_twopanel.py}
+\end{figure*}
+
 One parameter of the DTD which we hold fixed in the multi-zone models is the minimum SN Ia delay time $t_D$.
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=\linewidth]{figures/onezone_twopanel.pdf}
-    \caption{\textit{Left:} Comparison of one-zone models with minimum SN Ia delay times of 40 Myr (solid curves) and 150 Myr (dashed curves) for two DTDs: a power-law with $\alpha=-1.1$ (blue curves), and an exponential with $\tau=1.5$ Gyr (purple curves).
-The layout is similar to the plots in Figure \ref{fig:onezone-threepanel}.
-For clarity, we assume a mass-loading factor $\eta=1$ for the exponential DTD curves.
-    \textit{Right:} Comparison of one-zone models which assume all five functional forms for the DTD in this paper: triple-system (green), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
-A minimum SN Ia delay time of 40 Myr is assumed for all models in the right panel.}
-    \label{fig:onezone-twopanel}
-    \script{onezone_twopanel.py}
-\end{figure*}
-
 % [Summary and conclusions from one-zone models]
@@
 Of course, both of these observables are also greatly affected by the parameters of the SFH.
-We direct the reader to \citet{Palicio2023-AnalyticDTD} for a similar comparison of DTD models with a two-infall SFH.
+In this section we focused on the fiducial inside-out SFH model; for a similar comparison of DTD models with a two-infall SFH, we direct the reader to \citet{Palicio2023-AnalyticDTD}.
 
@@
 \subsection{The distribution of [Fe/H]}
-
-Figure \ref{fig:feh-df-comparison} shows MDFs across the Galaxy for a selection of models and APOGEE data.
-The two left-hand columns show MDFs from our simulations which assume the same DTD (exponential with $\tau=1.5$ Gyr) but different model SFHs.
-For comparison, the APOGEE MDFs are binned similarly and presented in the center column of Figure \ref{fig:feh-df-comparison}.
-
-Holding the SFH fixed, varying the DTD has a very minor effect on the MDF across the disk.
-The two right-hand columns of Figure \ref{fig:feh-df-comparison} plot the MDFs for two multi-zone simulations which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
-The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of SNe Ia exploding within 1 Gyr in the former model but only $\sim 30\%$ in the latter.
-
-The choice of DTD and SFH has a larger effect on the inner regions of the galaxy than the outer.
-Inner regions have a higher SFR and more stars are formed at early times than late, so differences in the SN Ia rate have a more pronounced effect on the MDF.
-For all SFH models except two-infall, the outer galaxy has a longer SFR timescale than the inner galaxy, so the MDF in the outer galaxy is relatively unaffected by the fraction of prompt SNe Ia.
-
-While there are some quantitative differences in how the shape of the MDF varies with Galactic region, the qualitative trends are unaffected by the choice of model SFH or DTD.
-These trends are primarily driven by chemical equilibrium, abundance gradients, and radial migration \citepalias[][see their Section 3.2 for further discussion]{Johnson2021-Migration}.
+\label{sec:feh-df}
 
@@
 
+Figure \ref{fig:feh-df-comparison} shows MDFs across the Galaxy for a selection of models and APOGEE data.
+The two left-hand columns show MDFs from our models which assume the same DTD (exponential with $\tau=1.5$ Gyr) but different SFHs.
+For comparison, the APOGEE MDFs are binned similarly and presented in the center column of Figure \ref{fig:feh-df-comparison}.
+The two right-hand columns
+
+Holding the SFH fixed, varying the DTD has a very minor effect on the MDF across the disk.
+The two right-hand columns of Figure \ref{fig:feh-df-comparison} plot the MDFs for two multi-zone simulations which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
+The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of SNe Ia exploding within 1 Gyr in the former model but only $\sim 30\%$ in the latter.
+Nevertheless, while the former DTD produces a slightly narrower MDF in the inner Galaxy than the latter, the magnitude of this difference is much smaller than other factors.
+
+The choice of DTD and SFH has a larger effect on the inner regions of the galaxy than the outer.
+Inner regions have a higher SFR and more stars are formed at early times than late, so differences in the SN Ia rate have a more pronounced effect on the MDF.
+For all SFH models except two-infall, the outer galaxy has a longer SFR timescale than the inner galaxy, so the MDF in the outer galaxy is relatively unaffected by the fraction of prompt SNe Ia.
+
+While there are some quantitative differences in how the shape of the MDF varies with Galactic region, the qualitative trends are unaffected by the choice of model SFH or DTD.
+These trends are primarily driven by chemical equilibrium, abundance gradients, and radial migration \citepalias[][see their Section 3.2 for further discussion]{Johnson2021-Migration}.
+
+To quantify the agreement between the [Fe/H] DFs generated by \vice and those observed in APOGEE, we compute the Kullback-Leibler (KL) divergence \citep{KullbackLeibler1951}, defined as
+\begin{equation}
+    D_{\rm{KL}}(P \parallel Q) \equiv \int_{-\infty}^{\infty} p(x) \log\Big(\frac{p(x)}{q(x)}\Big) dx
+    \label{eq:kl-divergence}
+\end{equation}
+for distributions $P$ and $Q$ with probability density functions $p(x)$ and $q(x)$.
+If $D_{\rm KL}=0$, the two distributions contain equal information.
+In this case, $P$ is the APOGEE DF, $Q$ is the model DF, and $x={\rm [Fe/H]}$.
+We bin the distributions with a width of 0.01 dex and apply observational uncertainties to our modeled DFs according to Table \ref{tab:uncertainties}.
+For each model SFH and DTD, we compute $D_{\rm{KL}}$ in the 18 different Galactocentric regions shown in Figure \ref{fig:feh-df-comparison}: bins in $R_{\rm gal}$ with a width of 2 kpc between 3 and 15 kpc, and bins in $|z|$ of $0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
+The score $S$ for the entire model is taken to be the average of $D_{\rm{KL}}$ for each region $R$ weighted by the number of APOGEE stars in that region $N_{*,R}$:
+\begin{equation}
+    S = \frac{\sum_R D_{{\rm KL},R} N_{*,R}}{\sum_R N_{*,R}}.
+    \label{eq:feh-df-score}
+\end{equation}
+
+The model combination with the best (lowest) score for the [Fe/H] DF is the two-infall SFH with the exponential ($\tau=3$ Gyr) DTD.
+The choice of SFH has a larger effect on the overall score than the DTD, and the best-performing SFH is the two-infall model, followed closely by the early-burst.
+However, the difference between the best-scoring model and the worst (late-burst SFH with triple-evolution DTD) is fairly small.
+The quantitative agreement between the predicted and observed [Fe/H] DFs is primarily affected by the assumption of chemical equilibrium, the abundance gradient, and radial migration.
+For further discussion, wee Section 3.2 of \citetalias{Johnson2021-Migration}.
+
 % \begin{figure}
@@
 \subsection{The distribution of [O/Fe]}
-
-The distribution of [O/Fe] serves as a record of the relative rates of SNe Ia and CCSNe.
-As such, the shape of the distribution is greatly affected by both the SFH and DTD.
-Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs, all assuming an exponential DTD with $\tau=1.5$ Gyr, compared to the distributions measured by APOGEE.
-We see similar trends with Galactic region across all four simulations.
-Near the midplane, the distributions at the innermost and outermost annuli are similar, but away from the midplane, there is a clear trend of a higher average stellar [O/Fe] at small $R_{\rm gal}$ and lower [O/Fe] at large $R_{\rm gal}$.
-
-While trends with $R_{\rm gal}$ and $|z|$ are similar, the shape of the distribution varies greatly with the chosen SFH.
-The inside-out and late-burst models produce similar distributions because of the similarity of their underlying SFHs \textemdash both skew heavily toward near-Solar [O/Fe], although the late-burst model produces a slightly broader peak and a less-prominent high-[O/Fe] tail.
-The only region which shows any significant skew toward high [O/Fe] is $R_{\rm gal}=3-5$ kpc and $|z|=1-2$ kpc, but the shift to higher [O/Fe] at high latitudes is gradual and does not produce the notable trough at ${\rm [O/Fe]}\approx0.2$ which is seen in the APOGEE data.
-
-On the other hand, the early-burst model produces a bimodal distribution of [O/Fe] even out to large radii and close to the midplane, whereas the APOGEE distribution does not show a prominent high-$\alpha$ peak beyond $R_{\rm{Gal}}\sim11$ kpc.
-The early-burst SFH produces the closest match to the data by far: the low-$\alpha$ sequence away from the midplane shows increasing contribution with larger radii, with the innermost radii containing very few low-$\alpha$ stars.
-However, the high-$\alpha$ sequence contains substantial contribution from stars at large radii, which is not seen in the data.
-
-The two-infall SFH model produces \textit{three} distinct modes at ${\rm [O/Fe]}\approx 0.0$, $0.2$, and $0.4$.
-At small $R_{\rm gal}$ and with increasing $|z|$, the low-$\alpha$ peak decreases in prominence and the high-$\alpha$ peak increases, but the intermediate peak is a striking feature at all latitudes which is at odds with the APOGEE data.
+\label{sec:ofe-df}
 
@@
 
-Figure \ref{fig:ofe-df-dtd} shows [O/Fe] distributions produced by simulations with the same SFH but a range of different DTDs.
-We choose the early-burst SFH because it produces distinct high- and low-$\alpha$ sequences, which makes the effect of the DTD on the former more apparent.
-The most apparent effect of the DTD is to shift the mode of the high-$\alpha$ sequence.
-The two-population DTD, which has the most prompt SNe Ia of any model in this paper, places the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.2$ dex higher at ${\rm [O/Fe]}\approx0.4$.
-This metric alone would seem to favor the exponential ($\tau=1.5$ Gyr) or plateau ($W=0.3$ Gyr; not shown) models; however,
+The distribution of [O/Fe] serves as a record of the relative rates of SNe Ia and CCSNe.
+As such, the shape of the distribution is greatly affected by both the SFH and DTD.
+Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs, all assuming an exponential DTD with $\tau=1.5$ Gyr, compared to the distributions measured by APOGEE.
+We see similar trends with Galactic region across all four simulations.
+Near the midplane, the distributions at the innermost and outermost annuli are similar, but away from the midplane, there is a clear trend of a higher average stellar [O/Fe] at small $R_{\rm gal}$ and lower [O/Fe] at large $R_{\rm gal}$.
+
+While trends with $R_{\rm gal}$ and $|z|$ are similar, the shape of the distribution varies greatly with the chosen SFH.
+The inside-out and late-burst models produce similar distributions because of the similarity of their underlying SFHs \textemdash both skew heavily toward near-Solar [O/Fe], although the late-burst model produces a slightly broader peak and a less-prominent high-[O/Fe] tail.
+The only region which shows any significant skew toward high [O/Fe] is $R_{\rm gal}=3-5$ kpc and $|z|=1-2$ kpc, but the shift to higher [O/Fe] at high latitudes is gradual and does not produce the notable trough at ${\rm [O/Fe]}\approx0.2$ which is seen in the APOGEE data.
+
+On the other hand, the early-burst model produces a bimodal distribution of [O/Fe] even out to large radii and close to the midplane, whereas the APOGEE distribution does not show a prominent high-$\alpha$ peak beyond $R_{\rm{Gal}}\sim11$ kpc.
+The early-burst SFH produces the closest match to the data by far: the low-$\alpha$ sequence away from the midplane shows increasing contribution with larger radii, with the innermost radii containing very few low-$\alpha$ stars.
+However, the high-$\alpha$ sequence contains substantial contribution from stars at large radii, which is not seen in the data.
+
+The two-infall SFH model produces \textit{three} distinct modes at ${\rm [O/Fe]}\approx 0.0$, $0.2$, and $0.4$.
+At small $R_{\rm gal}$ and with increasing $|z|$, the low-$\alpha$ peak decreases in prominence and the high-$\alpha$ peak increases, but the intermediate peak is a striking feature at all latitudes which is at odds with the APOGEE data.
 
@@
 
+Figure \ref{fig:ofe-df-dtd} shows [O/Fe] distributions produced by simulations with the same SFH but a range of different DTDs.
+We choose the early-burst SFH because it produces distinct high- and low-$\alpha$ sequences, which makes the effect of the DTD on the former more apparent.
+The most obvious effect of the DTD is to shift the mode of the high-$\alpha$ sequence.
+The two-population DTD, which has the most prompt SNe Ia of any model in this paper, places the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.2$ dex higher at ${\rm [O/Fe]}\approx0.4$.
+This metric alone would seem to favor the exponential ($\tau=1.5$ Gyr) or plateau ($W=0.3$ Gyr; not shown) models; however,
+
+[Talk about scores]
+
 \subsection{Bimodality in [O/Fe]}
 \label{sec:bimodality}
-
-A striking feature of the [O/Fe] distribution in the Milky Way is the distinct separation into two components, the high- and low-$\alpha$ sequences.
-
-Reference \citet{Vincenzo2021-AlphaDistribution} for how the bimodality is made stronger by the selection function, but it's not just due to selection effects.
 
@@
 All panels contain stars within the Galactic region defined by $7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc.
-The distributions of stars in $|z|$ The maximum of each distribution is normalized to 1 and the vertical scale is consistent across all panels.}
+The $|z|$-distributions of the model stellar populations are re-sampled to match the vertical distribution of the APOGEE sample, and \num{20000} stellar populations are drawn from the adjusted distribution in each panel.
+The maximum of each distribution is normalized to 1 and the vertical scale is consistent across all panels.}
     \label{fig:ofe-bimodality}
@@
 
+A striking feature of the [O/Fe] distribution in the Milky Way is the distinct separation into two components, the high- and low-$\alpha$ sequences.
+The relative prominence of the two peaks varies with $R_{\rm gal}$ and $|z|$, as shown by the right-hand panels of Figures \ref{fig:ofe-df-sfh} and \ref{fig:ofe-df-dtd}.
+A crucial feature of this bimodality which is not apparent in the previous figures is the coincidence of both sequences at the same [Fe/H].
+Figure \ref{fig:ofe-bimodality} compares the [O/Fe] distributions in the Solar annulus ($7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc) in two bins of [Fe/H] for select model outputs and APOGEE data.
+The APOGEE distributions in the bottom-right panel (j) show that the high-$\alpha$ mode is more prominent at lower [Fe/H] and \vice versa, but the distributions in both bins are clearly bimodal.
+Moreover, the ``trough'' at ${\rm [O/Fe]}\approx0.2$ is consistent in each bin.
+
+[Reference \citet{Vincenzo2021-AlphaDistribution} for how the bimodality is made stronger by the selection function, but it's not just due to selection effects.
+Describe the re-sampling we do to correct for this.] For most of our models, the low-$\alpha$ peak is the more prominent of the two, so by performing this resampling we enhance strength of the bimodality.
+However, for some models the high-$\alpha$ peak is the strongest, and the re-sampling process de-emphasizes the low-$\alpha$ peak below the prominence threshold (e.g., panel (f) of Figure \ref{fig:ofe-bimodality}).
+[Explain why this is ok]
+
+The top row of panels (a--e) in Figure \ref{fig:ofe-bimodality} shows the [O/Fe] bimodality (or lack thereof) across five different DTD models, all of which assume the late-burst SFH.
+To quantify the bimodality, we use the {\tt scipy}'s \citep{2020SciPy-NMeth} peak-finding algorithm with an arbitrary prominence threshold of 0.1.
+Five of the eight DTD models (four of the five shown, plus the exponential ($\tau=3$ Gyr) model) exceed this threshold, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
+Panel (b) illustrates that the power-law ($\alpha=-1.1$) DTD produces a marginal high-$\alpha$ peak, although it doesn't meet the prominence threshold because it is too close to the low-$\alpha$ peak.
+In general, as was the case with the [O/Fe] distributions in Section \ref{sec:ofe-df}, DTD models with fewer prompt SNe Ia produce a high-$\alpha$ peak which is more prominent and at a higher [O/Fe].
+One major discrepancy is that the APOGEE data show bimodality in both bins of [Fe/H], while the models run with the late-burst SFH only show a clear high-$\alpha$ peak at the low-metallicity ($-0.6<{\rm [Fe/H]}<-0.4$) bin.
+[Talk about why / if this matters]
+
+Panels (f)--(i) in the bottom row of Figure \ref{fig:ofe-bimodality} illustrate the effect of the SFH model on the [O/Fe] bimodality when the DTD is held constant.
+We show the results for the exponential ($\tau=1.5$ Gyr) DTD model because it produces a bimodal [O/Fe] distribution for all four SFH models.
+
 \subsection{The [O/Fe]--[Fe/H] Plane}
 \label{sec:ofe-feh}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/ofe_feh_sfh.pdf}
+    \caption{A comparison of the [O/Fe]--[Fe/H] plane between the four SFH models in our multi-zone simulations.
+All assume an exponential DTD with $\tau=1.5$ Gyr.
+Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
+A Gaussian scatter has been applied to all points based on the median abundance errors in APOGEE DR17 (see Table \ref{tab:uncertainties}).
+The black curves represent the ISM abundance tracks in the 8 kpc zone.
+The red contours represent a 2-D kernel density estimate with a bandwidth of 0.03 of the APOGEE abundance distribution in that Galactic region, with the solid and dashed contours enclosing 30\% and 80\% of stars in the sample, respectively.}
+    \label{fig:ofe-feh-sfh}
+    \script{ofe_feh_sfh.py}
+\end{figure}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/ofe_feh_sfh.pdf}
-    \caption{A comparison of the [O/Fe]--[Fe/H] plane between the four SFH models in our multi-zone simulations.
-All assume an exponential DTD with $\tau=1.5$ Gyr.
-Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
-A Gaussian scatter has been applied to all points based on the median abundance errors in APOGEE DR17 (ses Table \ref{tab:uncertainties}).
-The black curves represent the ISM abundance tracks in the 8 kpc zone.
-The red contours represent a 2-D kernel density estimate with a bandwidth of 0.03 of the APOGEE abundance distribution in that Galactic region, with the solid and dashed contours enclosing 30\% and 80\% of stars in the sample, respectively.}
-    \label{fig:ofe-feh-sfh}
-    \script{ofe_feh_sfh.py}
-\end{figure}
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figures/ofe_feh_dtd.pdf}
+    \caption{The [O/Fe]--[Fe/H] plane from multi-zone simulations with different DTD models.
+All assume the inside-out SFH.
+Each panel is similar to those in Figure \ref{fig:ofe-feh-sfh}, except each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
+All panels present stars within the Solar annulus ($7\leq R_{\rm gal}<9$ kpc).}
+    \label{fig:ofe-feh-dtd}
+    \script{ofe_feh_dtd.py}
+\end{figure*}
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=\linewidth]{figures/ofe_feh_dtd.pdf}
-    \caption{The [O/Fe]--[Fe/H] plane from multi-zone simulations with different DTD models.
-All assume the inside-out SFH.
-Each panel is similar to those in Figure \ref{fig:ofe-feh-sfh}, except each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
-All panels present stars within the Solar annulus ($7\leq R_{\rm gal}<9$ kpc).}
-    \label{fig:ofe-feh-dtd}
-    \script{ofe_feh_dtd.py}
-\end{figure*}
+[Discuss effect of radial migration]
+
+\citet{PerezCruz2008-KLTest2D} present a method for estimating the KL divergence between two continuous, multivariate samples using a $k$-nearest neighbor estimate.
+We implement this method to calculate the divergence between the multi-zone models and APOGEE data in [Fe/H]---[O/Fe] space.\footnote{We got the implementation from \url{https://mail.python.org/pipermail/scipy-user/2011-May/029521.html}.}
 
@@
 \label{sec:age-ofe}
-
-[Subsection introduction]
-
-Figure \ref{fig:age-ofe-sfh} compares the stellar age and [O/Fe] distributions in the Solar neighborhood between our four SFH models.
-Similar to Figure \ref{fig:ofe-feh-sfh}, all four panels assume an exponential DTD model with $\tau=1.5$ Gyr.
-We include age data from \citetalias{Leung2023-Ages} for qualitative comparison, though we caution against drawing strong conclusions because we don't correct for selection effects or systematics in the neural net ages.
-The inside-out and late-burst models show fair agreement with the data at high [O/Fe], although both show a $\sim2$ Gyr offset to older ages.
-One could shift the ramp-up in star formation to slightly later times or simply run the simulation for a shorter amount of time to close this gap.
-Like the data, the trend in the median age with decreasing [O/Fe] decreases monotonically in the inside-out model.
-The late-burst model, however, shows a bump in the distribution around a lookback time of $\sim2$ Gyr driven by the Gaussian SFR burst, which is not seen in the data, as noted by \citetalias{Johnson2021-Migration}.
-Neither model produces a significant amount of stars below Solar [O/Fe], in contrast to the data.
 
@@
 
+[Subsection introduction]
+
+Figure \ref{fig:age-ofe-sfh} compares the stellar age and [O/Fe] distributions in the Solar neighborhood between our four SFH models.
+Similar to Figure \ref{fig:ofe-feh-sfh}, all four panels assume an exponential DTD model with $\tau=1.5$ Gyr.
+We include age data from \citetalias{Leung2023-Ages} for qualitative comparison, though we caution against drawing strong conclusions because we don't correct for selection effects or systematics in the neural net ages.
+The inside-out and late-burst models show fair agreement with the data at high [O/Fe], although both show a $\sim2$ Gyr offset to older ages.
+One could shift the ramp-up in star formation to slightly later times or simply run the simulation for a shorter amount of time to close this gap.
+Like the data, the trend in the median age with decreasing [O/Fe] decreases monotonically in the inside-out model.
+The late-burst model, however, shows a bump in the distribution around a lookback time of $\sim2$ Gyr driven by the Gaussian SFR burst, which is not seen in the data, as noted by \citetalias{Johnson2021-Migration}.
+Neither model produces a significant amount of stars below Solar [O/Fe], in contrast to the data.
+
 For the early-burst SFH model, the simulated stellar ages are almost perfectly aligned with the data for ${\rm [O/Fe]}\gtrsim 0.2$.
@@
 The two-infall model is the only one which plateaus at sub-Solar [O/Fe] for the youngest stars, leading to a very good match to the observed data at low [O/Fe].
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figures/age_ofe_dtd.pdf}
+    \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different DTD models.
+All assume the early-burst SFH.
+Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
+In all panels stars are limited to the Solar annulus ($7\leq R_{\rm gal}<9$ kpc), and the layout of each panel is as in Figure \ref{fig:age-ofe-sfh}.}
+    \label{fig:age-ofe-dtd}
+    \script{age_ofe_dtd.py}
+\end{figure*}
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=\linewidth]{figures/age_ofe_dtd.pdf}
-    \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different DTD models.
-All assume the early-burst SFH.
-Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
-In all panels stars are limited to the Solar annulus ($7\leq R_{\rm gal}<9$ kpc), and the layout of each panel is as in Figure \ref{fig:age-ofe-sfh}.}
-    \label{fig:age-ofe-dtd}
-    \script{age_ofe_dtd.py}
-\end{figure*}
-
 Moving to stars at low $|z|$, our plateau ($W=1$ Gyr) and triple-system DTDs over-produce stars at the old, high-$\alpha$ end of the distribution, while also diverging significantly from the observed sequence near solar [O/Fe].
@@
 
+We use a different scoring system from previous sub-sections due to the much larger uncertainties in age than [O/Fe].
+As shown in Figures \ref{fig:age-ofe-sfh} and \ref{fig:age-ofe-dtd}, in each Galactic region we bin the model outputs and data into bins of [O/Fe] with a width of 0.05 dex.
+We define the RMS median age difference for the region as
+\begin{equation}
+    \Delta\tau_{\rm RMS} \equiv \sqrt{\frac{\sum_k \Delta\tau_k^2 n_{{\rm L23},k}}{n_{\rm L23,tot}}}
+    \label{eq:age-ofe-score}
+\end{equation}
+where $\Delta\tau_k=\rm{med}(\tau_{\rm \vice})-\rm{med}(\tau_{\rm L23})$ is the difference between the mass-weighted median star particle age in \vice and the median stellar age from \citetalias{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citetalias{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
+As before, the score for the model as a whole is the average of $\Delta \tau_{\rm RMS}$ across all regions, weighted by the number of stars in the age sample in each region.
+
+The best, lowest-scoring model in the age--[O/Fe] plane
+
 \section{Discussion}
 \label{sec:discussion}
+
+Extra-galactic observations of the DTD are more sensitive to the late-time DTD; GCE comparisons with the high-alpha sequence are more sensitive to the early-time DTD. 
+[Later on, make suggestions]
 
@@
 
-To quantify the difference between the abundance distributions (MDFs and [O/Fe] DFs) generated by VICE and those observed in APOGEE, we compute the Kullback-Leibler (KL) divergence \citep{KullbackLeibler1951}, defined as
-\begin{equation}
-    D_{\rm{KL}}(P \parallel Q) \equiv \int_{-\infty}^{\infty} p(x) \log\Big(\frac{p(x)}{q(x)}\Big) dx
-    \label{eq:kl-divergence}
-\end{equation}
-for distributions $P$ and $Q$ with probability density functions $p(x)$ and $q(x)$.
-A KL divergence of 0 indicates that the two distributions contain equal amounts of information.
-In this case, $P$ is the APOGEE DF, $Q$ is the model DF, and $x$ is either [Fe/H] or [O/Fe].
-For each model SFH and DTD, we compute $D_{\rm{KL}}$ in 18 different Galactocentric regions: 2 kpc-wide bins in $R_{\rm gal}$ between 3 and 15 kpc, and bins in $|z|$ of $0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
-The KL divergence for the entire model is taken to be the average of $D_{\rm{KL}}$ for each region weighted by the number of APOGEE stars in that region.
-
-\citet{PerezCruz2008-KLTest2D} present a method for estimating the KL divergence between two continuous, multivariate samples using a $k$-nearest neighbor estimate.
-We implement this method to calculate the divergence between the multi-zone models and APOGEE data in [Fe/H]---[O/Fe] space.\footnote{We got the implementation from \url{https://mail.python.org/pipermail/scipy-user/2011-May/029521.html}.}
-
-We employ a different test in the age---[O/Fe] plane.
-[motivated by the large age uncertainties?] As shown in Figures \ref{fig:age-ofe-sfh} and \ref{fig:age-ofe-dtd}, in each Galactic region we bin the model outputs and data into bins of [O/Fe] with a width of 0.05 dex.
-We define the RMS median age difference for the region as
-\begin{equation}
-    \Delta\tau_{\rm RMS} \equiv \sqrt{\frac{\sum_k \Delta\tau_k^2 n_{{\rm L23},k}}{n_{\rm L23,tot}}}
-    \label{eq:age-ofe-score}
-\end{equation}
-where $\Delta\tau_k=\rm{med}(\tau_{\rm VICE})-\rm{med}(\tau_{\rm L23})$ is the difference between the mass-weighted median star particle age in VICE and the median stellar age from \citetalias{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citetalias{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
-As before, the score for the model as a whole is the average of $\Delta \tau_{\rm RMS}$ across all regions, weighted by the number of stars in the age sample in each region.
+% We employ a different test in the age---[O/Fe] plane. [motivated by the large age uncertainties?]
 
@@
 \variable{output/summary_table.tex}
+
+[Why does two-infall do so well across the board, even in the [Fe/H] and [O/Fe] DFs where it seems worse by eye?]
 
@@
 
-\software{VICE \citep{JohnsonWeinberg2020-Starbursts}, Astropy \citep{astropy2013,astropy2018,astropy2022}, scikit-learn \citep{Pedregosa2011-ScikitLearn}, SciPy \citep{2020SciPy-NMeth}, Matplotlib \citep{Hunter2007-Matplotlib}}
+\software{\vice \citep{JohnsonWeinberg2020-Starbursts}, Astropy \citep{astropy2013,astropy2018,astropy2022}, scikit-learn \citep{Pedregosa2011-ScikitLearn}, SciPy \citep{2020SciPy-NMeth}, Matplotlib \citep{Hunter2007-Matplotlib}}
 
@@
 
-For each star particle in VICE, \citetalias{Johnson2021-Migration} randomly assign an analogue star particle from \texttt{h277} and adopt its radial migration distance $\Delta R$ and final midplane distance $z$.
-This allows VICE to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
-However, in regions where the number of h277 star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single h277 star particle can be assigned as an analogue to multiple VICE stellar populations.
+For each star particle in \vice, \citetalias{Johnson2021-Migration} randomly assign an analogue star particle from \texttt{h277} and adopt its radial migration distance $\Delta R$ and final midplane distance $z$.
+This allows \vice to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
+However, in regions where the number of h277 star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single h277 star particle can be assigned as an analogue to multiple \vice stellar populations.
 These populations will have similar formation and migration histories and consequently similar abundances, which produces unphysical ``clumps'' of stars in the abundance distributions at high latitudes and large radii.
@@
 
-When a star particle is created by VICE at initial radius $R_{\rm form}$, we sample its total radial migration distance $\Delta R$ from a Gaussian with a width described by Equation \ref{eq:radial-migration}, and we sample its final midplane distance $z_{\rm final}$ from the distribution described by Equation \ref{eq:sech-pdf} with a width given by Equation \ref{eq:scale-height}.
+When a star particle is created by \vice at initial radius $R_{\rm form}$, we sample its total radial migration distance $\Delta R$ from a Gaussian with a width described by Equation \ref{eq:radial-migration}, and we sample its final midplane distance $z_{\rm final}$ from the distribution described by Equation \ref{eq:sech-pdf} with a width given by Equation \ref{eq:scale-height}.
 The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citetalias{Johnson2021-Migration}, but with a time dependence $\propto \Delta t^{1/3}$.

### 2024-03-06 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % user-defined commands
-\newcommand{\yes}{\textcolor{green}{\checkmark}}
-\newcommand{\meh}{\textcolor{black}{$\sim$}}
-\newcommand{\no}{\textcolor{red}{$\times$}}
+\newcommand{\yes}{\textcolor{green}{\checkmark}\xspace}
+\newcommand{\meh}{\textcolor{black}{$\sim$}\xspace}
+\newcommand{\no}{\textcolor{red}{$\times$}\xspace}
 \newcommand{\osuaffil}{Department of Astronomy, The Ohio State University, 140 W. 18th Ave, Columbus OH 43210, USA}
@@
 A few studies have compared different DTDs in one-zone chemical evolution models, but their comparisons to abundance data are limited to the local Solar neighborhood \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
+[Talk about \citep{Matteucci2009-DTDModels} multi-zone models].
 \citet{Poulhazan2018-PrecisionPollution} compared six DTD models in a smoothed-particle hydrodynamics simulation in a cosmological context.
@@
 
-We make use of the multi-zone simulation tools in \vice developed by \citet{Johnson2021-Migration} (hereafter \citetalias{Johnson2021-Migration}).
-The basic setup of our models follows theirs: the simulated Galaxy is a disk with a radius of 20 kpc and is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
-The gas in each ring is assumed to be instantaneously mixed; while star particles are allowed to migrate radially (see Appendix \ref{app:migration}), there is no exchange of gas between rings.
-We run our simulations with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
-Following \citetalias{Johnson2021-Migration}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_*=0$ for $R_{\rm gal}>R_{\rm SF}$ (stars are allowed to migrate past $R_{\rm SF}$, they are just not born there).
-We summarize the parameters for our multi-zone models in Table \ref{tab:multizone-parameters}.
-
-\begin{deluxetable*}{Cccl}
-    \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models.
-We omit parameters that are unchanged from \citetalias{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
-    \tablehead{
-        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Section} & \colhead{Description}
-    }
-    \startdata
-        % Multi-zone simulation parameters
-        R_{\rm gal}     & [0, 20] kpc   & \ref{sec:methods} & Galactocentric radius \\
-        \delta R_{\rm gal}  & 100 pc    & \ref{sec:methods} & Width of each concentric ring \\
-        \Delta R_{\rm gal}  & N/A       & \ref{app:migration} & Change in orbital radius due to stellar migration \\
-        p(\Delta R_{\rm gal}|\tau,R_{\rm form}) & Equation \ref{eq:radial-migration}    & \ref{app:migration} & Probability density function of radial migration \\
-        z                   & [-3, 3] kpc                & \ref{app:migration} & Distance from Galactic midplane at present day \\
-        p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
-        \Delta t        & 10 Myr    & \ref{sec:methods} & Time-step size \\
-        t_{\rm max}     & 13.2 Gyr  & \ref{sec:methods} & Maximum simulation time \\
-        n               & 8         & \ref{sec:methods} & Number of stellar populations formed per ring per time-step \\
-        R_{\rm SF}      & 15.5 kpc  & \ref{sec:methods} & Maximum radius of star formation \\
-        M_{g,0}   & 0         & \ref{sec:sfh}     & Initial gas mass \\
-        % DTD
-        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & Delay time distribution of Type Ia supernovae \\
-        t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
-        N_{\rm Ia}/M_*  & $2.2\times10^{-3}$ M$_\odot^{-1}$ & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \citep{MaozMannucci2012-SNeIaReview} \\
-        % Nucleosynthetic yields
-        y_{\rm O}^{\rm CC}  & 0.015     & \ref{sec:yields}  & CCSN yield of O    \\
-        y_{\rm Fe}^{\rm CC} & 0.0012    & \ref{sec:yields}  & CCSN yield of Fe   \\
-        y_{\rm O}^{\rm Ia}  & 0         & \ref{sec:yields}  & SN Ia yield of O       \\
-        y_{\rm Fe}^{\rm Ia} & 0.00214   & \ref{sec:yields}  & SN Ia yield of Fe \\
-        % Star formation histories
-        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & \ref{sec:sfh} & Time-dependence of the inside-out SFR \\
-        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the late-burst SFR \\
-        \uptau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the early-burst SFE timescale \\
-        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the early-burst IFR \\
-        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the two-infall IFR \\
-    \enddata
-\end{deluxetable*}
+[Quick note about mass loading?]
 
@@
 A declining power-law with $\alpha\sim-1$ is expected to arise from typical assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral \citep[see Section 3.5 from][]{Maoz2014-Review}.
-It is therefore a commonly assumed DTD in GCE studies (e.g., \citealt{Rybizki2017-Chempy}; \citetalias{Johnson2021-Migration}).
+It is therefore a commonly assumed DTD in GCE studies (e.g., \citealt{Rybizki2017-Chempy}; \citetalias{Johnson2021-Migration}; \citealt{Weinberg2023-CCSNYield}).
 Additionally, the observational evidence for a power-law DTD is strong.
@@
 We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr), an SFE timescale $\uptau_*\equiv M_g/\dot M_*=2$ Gyr, and an initial gas mass $M_{g,0}=0$.
-We adopt a continuous recycling prescription \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
+We adopt continuous recycling, which accounts for the time-dependent return of mass from all previous generations of stars \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
 Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time of 40 Myr.
@@
 For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr.
-In all cases a minimum SN Ia delay time of 40 Myr is assumed.
 The open symbols located along each curve mark logarithmic steps in simulation time.
@@
 
-% \subsection{The Star Formation History}
-
-% Figure \ref{fig:onezone-delay-taustar} shows results from one-zone models with a power-law DTD which differ in their assumed minimum SN Ia delay time ($t_D$) or star formation efficiency timescale ($\uptau_*$).
-In [Fe/H]-[O/Fe] space, doubling or halving the minimum delay time produces similar results to doubling or halving the SFE timescale.
-A shorter minimum delay time means SNe Ia will start to explode sooner after the star formation burst, giving less time for CCSNe to explode at the plateau of the abundance track.
-Similarly, a longer SFE timescale means fewer massive stars will be produced by the initial star formation burst, resulting in fewer CCSNe before the first SNe Ia explode.
-
-% The minimum delay and SFE timescale have similar effects on the abundance tracks but very different effects on the MDFs.
-Altering the SFE timescale changes the stellar distribution of [Fe/H], especially at the low-metallicity end, as shown in the top panel of Figure \ref{fig:onezone-delay-taustar}.
-However, as a change in the SFE timescale affects both the number of high-mass and low-mass stars produced, it does not affect the distribution of [O/Fe], as shown in the right-hand panel of Figure \ref{fig:onezone-delay-taustar}.
-Meanwhile, a change in the minimum SN Ia delay time does not impact the total number of SNe which explode, so the distribution of [Fe/H] is largely unaffected, while it does result in a change in the number of high-$\alpha$ stars formed and therefore the distribution of [O/Fe].
-
-% \begin{figure}
-%     \centering
-%     \includegraphics{figures/onezone_delay_taustar.pdf}
-%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\uptau_*$).
-Tracks with $\uptau_*=2$ Gyr are represented in black, while a track with a shorter $\uptau_*=1$ Gyr is shown in red and a track with a longer $\uptau_*=4$ Gyr is in yellow.
-The dotted, solid, and dashed black curves represent a minimum delay time of 40 Myr, 80 Myr, and 160 Myr, respectively.
-A power-law DTD with $\alpha=-1.1$ is assumed in all models.}
-%     \label{fig:onezone-delay-taustar}
-%     \script{onezone_delay_taustar.py}
-% \end{figure}
-
 \section{Results from Multi-Zone Models}
 \label{sec:multizone-results}
+
+\begin{deluxetable*}{Cccl}
+    \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models.
+We omit parameters that are unchanged from \citetalias{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
+    \tablehead{
+        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Section} & \colhead{Description}
+    }
+    \startdata
+        % Multi-zone simulation parameters
+        R_{\rm gal}     & [0, 20] kpc   & \ref{sec:multizone-results} & Galactocentric radius \\
+        \delta R_{\rm gal}  & 100 pc    & \ref{sec:multizone-results} & Width of each concentric ring \\
+        \Delta R_{\rm gal}  & N/A       & \ref{app:migration} & Change in orbital radius due to stellar migration \\
+        p(\Delta R_{\rm gal}|\tau,R_{\rm form}) & Equation \ref{eq:radial-migration}    & \ref{app:migration} & Probability density function of radial migration distance \\
+        z                   & [-3, 3] kpc                & \ref{app:migration} & Distance from Galactic midplane at present day \\
+        p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
+        \Delta t        & 10 Myr    & \ref{sec:multizone-results} & Time-step size \\
+        t_{\rm max}     & 13.2 Gyr  & \ref{sec:multizone-results} & Maximum simulation time \\
+        n               & 8         & \ref{sec:multizone-results} & Number of stellar populations formed per ring per time-step \\
+        R_{\rm SF}      & 15.5 kpc  & \ref{sec:multizone-results} & Maximum radius of star formation \\
+        M_{g,0}   & 0         & \ref{sec:sfh}     & Initial gas mass \\
+        % DTD
+        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & Delay time distribution of Type Ia supernovae \\
+        t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
+        N_{\rm Ia}/M_*  & $2.2\times10^{-3}$ M$_\odot^{-1}$ & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \citep{MaozMannucci2012-SNeIaReview} \\
+        % Nucleosynthetic yields
+        y_{\rm O}^{\rm CC}  & 0.015     & \ref{sec:yields}  & CCSN yield of O    \\
+        y_{\rm Fe}^{\rm CC} & 0.0012    & \ref{sec:yields}  & CCSN yield of Fe   \\
+        y_{\rm O}^{\rm Ia}  & 0         & \ref{sec:yields}  & SN Ia yield of O       \\
+        y_{\rm Fe}^{\rm Ia} & 0.00214   & \ref{sec:yields}  & SN Ia yield of Fe \\
+        % Star formation histories
+        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & \ref{sec:sfh} & Time-dependence of the inside-out SFR \\
+        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the late-burst SFR \\
+        \uptau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the early-burst SFE timescale \\
+        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the early-burst IFR \\
+        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the two-infall IFR \\
+    \enddata
+\end{deluxetable*}
+
+We make use of the multi-zone simulation tools in \vice developed by \citet{Johnson2021-Migration} (hereafter \citetalias{Johnson2021-Migration}).
+The basic setup of our models follows theirs: the simulated Galaxy is a disk with a radius of 20 kpc and is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
+The gas in each ring is assumed to be instantaneously mixed; while star particles are allowed to migrate radially (see Appendix \ref{app:migration}), there is no exchange of gas between rings.
+We run our simulations with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
+Following \citetalias{Johnson2021-Migration}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_*=0$ for $R_{\rm gal}>R_{\rm SF}$ (stars are allowed to migrate past $R_{\rm SF}$, they are just not born there).
+We summarize the parameters for our multi-zone models in Table \ref{tab:multizone-parameters}.
 
@@
 
-Panels (f)--(i) in the bottom row of Figure \ref{fig:ofe-bimodality} illustrate the effect of the SFH model on the [O/Fe] bimodality when the DTD is held constant.
-We show the results for the exponential ($\tau=1.5$ Gyr) DTD model because it produces a bimodal [O/Fe] distribution for all four SFH models.
+Panels (f)--(i) in the bottom row of Figure \ref{fig:ofe-bimodality} illustrate the effect of the SFH model on the [O/Fe] bimodality with the exponential ($\tau=1.5$ Gyr) DTD.
+The inside-out SFH does not produce a bimodal distribution for any of our DTD models.
+On the other hand, the early-burst SFH {\it always} produces a bimodal distribution in the $-0.4\leq{\rm [Fe/H]}<-0.2$ bin regardless of the assumed DTD, although the lower-metallicity bin does not (the lower peak falls short of our prominence threshold of 0.1).
+For models with the late-burst and two-infall SFHs, bimodality is variable depending on the DTD: those with longer median delay times (e.g., exponential, plateau, or triple-system) generally produce a bimodal distribution in the $-0.6\leq{\rm [Fe/H]}<-0.4$ bin, while the power-law DTDs do not.
+None of our SFH+DTD combinations can produce an [O/Fe] distribution which is bimodal in {\it both} bins of [Fe/H], as we observe in APOGEE (j).
 
@@
 \citet{PerezCruz2008-KLTest2D} present a method for estimating the KL divergence between two continuous, multivariate samples using a $k$-nearest neighbor estimate.
-We implement this method to calculate the divergence between the multi-zone models and APOGEE data in [Fe/H]---[O/Fe] space.\footnote{We got the implementation from \url{https://mail.python.org/pipermail/scipy-user/2011-May/029521.html}.}
+We implement this method to calculate the divergence between the multi-zone models and APOGEE data in [Fe/H]--[O/Fe] space.\footnote{We got the implementation from \url{https://mail.python.org/pipermail/scipy-user/2011-May/029521.html}.}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/ofe_feh_twoinfall.pdf}
+    \caption{The [O/Fe]--[Fe/H] plane for multiple Galactocentric regions from the model with the inside-out SFH and plateau ($W=0.3$ Gyr) DTD.
+The two columns of panels contain stars in different bins of $R_{\rm gals}$, and each row contains stars from a different bin of $|z|$.
+The contents of each panel is as described in Figure \ref{fig:ofe-feh-sfh}.}
+    \label{fig:ofe-feh-twoinfall}
+    \script{ofe_feh_twoinfall.py}
+\end{figure}
 
@@
 
+\variable{output/summary_table.tex}
+
+The results presented in Section \ref{sec:multizone-results} represent a fraction of the 32 total multi-zone model outputs (four SFHs and eight DTDs) and focus on the even smaller fraction of outputs which lie in the Solar annulus.
+% While we focused our attention on results in the Solar annulus (for which we still have the best data), we have model outputs which span the entire disk out to 20 kpc.
+In order to identify trends among our many models, it will be useful to have some semi-quantitative way to compare their outputs to APOGEE data across the disk.
+In this Section, we compare all our model outputs to APOGEE across five diagnostics: the [Fe/H] DF, [O/Fe] DF, [Fe/H]--[O/Fe] plane, age--[O/Fe] plane, and [O/Fe] bimodality.
+We perform statistical tests between APOGEE and the model outputs in each region of the Galaxy (as described in corresponding subsections of Section \ref{sec:multizone-results}), then compute the average weighted by the size of the APOGEE sample in each region to obtain a single numerical score.
+
+The diagnostic scores for each model are presented in Table \ref{tab:results}.
+These scores are useful to indicate combinations of SFH and DTD which are favorable or disfavorable in certain regimes, but we emphasize that we do not use these scores to fit the models to the data.
+To avoid drawing strong conclusions from small numerical differences in scores, 
+% Instead of reporting the numerical scores for each simulation output, 
+in the column corresponding to a particular diagnostic we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom tirtile out of all of our simulations, respectively.
+A \yes indicates that particular combination of model SFH and DTD performed better than most when compared to the APOGEE sample for that diagnostic.
+
+Table \ref{tab:results} indicates combinations of SFH and DTD which are more or less favorable in certain regimes.
+However, we emphasize that we do not use these scores to fit the models to the data.
+Much of the variation between models can be explained by the choice of SFH: in general, the two-infall models rank the highest across all diagnostics, while the late-burst models generally compare poorly to the rest.
+
 Extra-galactic observations of the DTD are more sensitive to the late-time DTD; GCE comparisons with the high-alpha sequence are more sensitive to the early-time DTD. 
@@
 
-\subsection{Scoring the Model Outputs}
-\label{sec:scores}
-
-The results presented in Section \ref{sec:multizone-results} represent a fraction of the total model outputs.
-We ran models for four different SFHs and eight different DTDs, for a combined total of 32 model runs.
-While we focused our attention on results in the Solar annulus (for which we still have the best data), we have model outputs which span the entire disk out to 20 kpc.
-In order to identify trends among our many models, it will be useful to have some semi-quantitative way to compare their outputs to APOGEE data across the disk.
-
-We compare our multi-zone outputs to APOGEE across five diagnostics: the [Fe/H] DF, [O/Fe] DF, [Fe/H]--[O/Fe] plane, age--[O/Fe] plane, and [O/Fe] bimodality.
-We perform statistical tests between APOGEE and simulation outputs in each region of the galaxy, then average the scores together (weighted by the number of APOGEE targets in each galactic region) to obtain a single numerical score for each simulation.
-Note that we are not trying to use these scores to fit our models to the data, nor are we trying to rule out any SFH in general.
-We use these scores to get a handle on which combinations of SFH and DTD are favorable or disfavorable in certain regimes.
-
-% We employ a different test in the age---[O/Fe] plane. [motivated by the large age uncertainties?]
-
-The results of these tests are presented in Table \ref{tab:results}.
-Instead of reporting the numerical scores for each simulation output, in the column corresponding to a particular diagnostic we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom tirtile out of all of our simulations, respectively.
-A \yes indicates that particular combination of model SFH and DTD performed better than most when compared to the APOGEE sample for that diagnostic.
-
-\variable{output/summary_table.tex}
-
-[Why does two-infall do so well across the board, even in the [Fe/H] and [O/Fe] DFs where it seems worse by eye?]
-
 \subsection{The Two-Infall SFH Model}
@@
 
+Across every diagnostic in Table \ref{tab:results}, the two-infall models outperform every other SFH.
+
+[Why does two-infall do so well across the board, even in the [Fe/H] and [O/Fe] DFs where it seems worse by eye?]
+
 [Compare to previous studies]
 Discuss \citet{Matteucci2006-BimodalDTDConsequences} findings of the \citet{Mannucci2006-TwoPopulations} DTD in the two-infall model.
+
+[First exploration of two-infall with mass loading, radial migration. Further investigation coming in future paper.]
 

### 2024-03-06 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-Like \citetalias{Johnson2021-Migration}, we focus our analysis on O and Fe, representing the $\alpha$ and Fe-peak elements, respectively.
+For simplicity and easier comparison to the results of \citet{Johnson2021-Migration} (hereafter \citetalias{Johnson2021-Migration}), we focus our analysis on O and Fe, representing the $\alpha$ and Fe-peak elements, respectively.
 Both elements are produced by CCSNe.
@@
 
-We make use of the multi-zone simulation tools in \vice developed by \citet{Johnson2021-Migration} (hereafter \citetalias{Johnson2021-Migration}).
-The basic setup of our models follows theirs: the simulated Galaxy is a disk with a radius of 20 kpc and is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
+We make use of the multi-zone GCE model tools in \vice developed by \citetalias{Johnson2021-Migration}.
+The basic setup of our models follows theirs: the model Galaxy is a disk with a radius of 20 kpc and is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
 The gas in each ring is assumed to be instantaneously mixed; while star particles are allowed to migrate radially (see Appendix \ref{app:migration}), there is no exchange of gas between rings.
@@
 The quantitative agreement between the predicted and observed [Fe/H] DFs is primarily affected by the assumption of chemical equilibrium, the abundance gradient, and radial migration.
-For further discussion, wee Section 3.2 of \citetalias{Johnson2021-Migration}.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics{figures/feh_df_dtd.pdf}
-%     \caption{Distributions of [Fe/H] from multi-zone simulations with different DTDs: a power-law with slope $\alpha=-1.4$ (\textit{left}), and an exponential with timescale $\tau=3$ Gyr (\textit{right}).
-Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}).
-Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue).
-Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row.
-All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex.
-In both cases an inside-out SFH is assumed.}
-%     \label{fig:feh-df-dtd}
-%     \script{feh_df_dtd.py}
-% \end{figure}
-
-% \begin{figure*}
-%     \centering
-%     \includegraphics[width=\linewidth]{figures/feh_df_sfh.pdf}
-%     \caption{Distributions of [Fe/H] from multi-zone simulations with different SFHs.
-The plot format is similar to Figure \ref{fig:feh-df-dtd}.
-In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.
-Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
-%     \label{fig:feh-df-sfh}
-%     \script{feh_df_sfh.py}
-% \end{figure*}
+For further discussion, see Section 3.2 of \citetalias{Johnson2021-Migration}.
 
@@
 The two-population DTD, which has the most prompt SNe Ia of any model in this paper, places the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.2$ dex higher at ${\rm [O/Fe]}\approx0.4$.
-This metric alone would seem to favor the exponential ($\tau=1.5$ Gyr) or plateau ($W=0.3$ Gyr; not shown) models; however,
 
@@
 Much of the variation between models can be explained by the choice of SFH: in general, the two-infall models rank the highest across all diagnostics, while the late-burst models generally compare poorly to the rest.
+This is different for the bimodality test, where the early-burst SFH is able to produce a bimodal [O/Fe] distribution for all DTDs, as discussed in Section \ref{sec:bimodality}.
+The choice of DTD has a clear effect on the model scores, and this effect is similar across the diagnostics.
+The models which perform the best (most \yes's and fewest \no's) are those with the exponential and plateau DTDs.
+It is interesting that the best-performing model overall in our scoring system, the exponential DTD with $\tau=1.5$ Gyr, is intermediate among all our DTDs in terms of the number of prompt SNe Ia and median delay time, but has the {\it lowest} rate at very long delay times ($\sim10$ Gyr).
+Models with a large fraction of prompt SNe Ia, such as the power-law and two-population DTDs, fare quite poorly, with the steepest power-law ($\alpha=-1.4$) ending up in the bottom tirtile across the board for most of our SFHs.
+
+[Discuss \citet{Palicio2024-CosmicSNIaRate}]
 

### 2024-03-18 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\shorttitle{SN Ia DTD in GCE Simulations}
+\shorttitle{SN Ia DTD in GCE Models}
 \shortauthors{Dubay, Johnson, \& Johnson}
@@
 Because the DTD also affects the relationship among age, [Fe/H], and \aFe in chemical evolution models, comparison with observations of stars in the Milky Way is an important consistency check for any proposed DTD.
-We implement several popular forms of the DTD in combination with multiple star formation histories for the Milky Way in one-zone and multi-zone chemical evolution models using the Versatile Integrator for Chemical Evolution (\vice).
-\vice includes a prescription for radial stellar migration in multi-zone models.
+We implement several popular forms of the DTD in combination with multiple star formation histories for the Milky Way in %one-zone and
+    multi-zone chemical evolution models including a prescription for radial stellar migration.
+    % using the Versatile Integrator for Chemical Evolution (\vice). \vice includes a prescription for radial stellar migration in multi-zone models. 
     We compare our predicted interstellar medium abundance tracks, stellar abundance distributions, and stellar age distributions to the final data release of the Apache Point Observatory Galactic Evolution Experiment (APOGEE).
@@
 Galactic chemical evolution (GCE) studies seek to explain the observed distribution of metals throughout the Milky Way Galaxy.
-\citet{Tinsley1979-StellarLifetimes} made a compelling case that the non-Solar \aFe\footnote{
+\citet{Tinsley1979-StellarLifetimes} made a compelling case that the non-solar \aFe\footnote{
     In standard bracket notation, $[X/Y]\equiv \log_{10}(X/Y) - \log_{10}(X/Y)_{\odot}$.
@@
 Type Ia supernovae (SNe Ia), the thermonuclear explosions of carbon-oxygen white dwarfs (WDs), are responsible for a majority of the Fe produced in the Galaxy \citep{Matteucci1986-SupernovaEnrichment}; meanwhile, core collapse supernovae (CCSNe), the explosions of massive stars, produce the $\alpha$-elements (e.g., O and Mg) in addition to a smaller fraction of Fe.
-SNe Ia are delayed by $\sim10^8 - 10^{10}$ years after star formation events, as evidenced by observations at large distances from star forming regions and in elliptical galaxies \citep[e.g.,][]{Maza1976-SNStatistics}.
+SNe Ia are delayed by $\sim0.1-10$ Gyr after star formation events, as evidenced by observations at large distances from star forming regions and in elliptical galaxies \citep[e.g.,][]{Maza1976-SNStatistics}.
 This delayed enrichment leads to a decrease in \aFe with increasing [Fe/H] \citep{Matteucci1986-SupernovaEnrichment}.
@@
 % [What is the delay time distribution]
-The rate of SNe Ia which explode as a function of time after the formation of a hypothetical unit-mass single stellar population is known as the delay-time distribution \citep[DTD; for a review, see Section 3.5 of][]{Maoz2014-Review}.
-When the DTD is convolved with the Galactic star formation rate (SFR) as a function of time, it yields the SN Ia rate as a function of time. 
+The {\it delay time distribution} (DTD) refers to the rate of SN Ia events per unit mass of star formation as a function of stellar population age
+% The rate of SNe Ia which explode as a function of time after the formation of a hypothetical unit-mass single stellar population is known as the delay-time distribution 
+\citep[for a review, see Section 3.5 of][]{Maoz2014-Review}.
+When the DTD is convolved with the Galactic star formation rate (SFR), it yields the overall SN Ia rate. 
 The quantitative details of the relationship between \aFe and [Fe/H] are set by the DTD, and as such it is a key parameter in GCE models.
-The DTD remains poorly constrained, however, because it reflects the detailed evolution of the SNe Ia progenitor systems, so different models for the progenitors of SNe Ia will naturally predict different forms for the DTD.
+However, the DTD remains poorly constrained because it reflects the detailed evolution of the SN Ia progenitor systems, so different models for the progenitors of SNe Ia will naturally predict different forms for the DTD.
 
 % [Introduction to SNe Ia]
-The mechanism(s) for producing SNe Ia are not fully understood \citep[for reviews, see][]{Maoz2014-Review,Livio2018-ProgenitorReview,Ruiter2020-ProgenitorReview}.
+The explosion mechanism(s) of SNe Ia are not fully understood \citep[for reviews, see][]{Maoz2014-Review,Livio2018-ProgenitorReview,Ruiter2020-ProgenitorReview}.
 Two general production channels have been proposed.
@@
 % [Theoretical DTDs]
-Uncertainties in the progenitor channels of SNe Ia translate into uncertainties in the shape of the DTD. 
+% Uncertainties in the progenitor channels of SNe Ia translate into uncertainties in the shape of the DTD. 
 % By formulating analytical DTDs for several progenitor models, \citet{Greggio2005-AnalyticalRates} found that the SD channel tends to produce a steeper DTD function than the DD channel, and the median delay time (by which 50\% of SNe Ia have exploded) can vary by a factor of 10 depending on the chosen progenitor scenario and its particular parameters.
+Theoretical models have yet to converge on a single prediction for the DTD.
 For the DD channel, assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral suggest a broad $\sim t^{-1}$ DTD at long delay times ($\gtrsim 1$ Gyr), but at short delays ($\lesssim 1$ Gyr) the rate is limited by the need to produce two WDs \citep[see Section 3.5 from][]{Maoz2014-Review}.
@@
 % [Observational DTDs]
-Surveys of SNe Ia have provided the primary observational constraints on the DTD.  
-This can be done by comparing the observed rate of SNe Ia to their host galaxy parameters \citep[e.g.,][]{Mannucci2005-SNRate,Heringer2019-FieldGalaxyDTD} or inferred star formation histories \citep[SFHs; e.g.,][]{Maoz2012-SloanIIDTD}, measuring SN Ia rates in galaxy clusters \citep[e.g.,][]{Maoz2010-ClusterDTD}, or comparing the volumetric SN Ia rate to the cosmic SFH as a whole \citep[e.g.,][]{Graur2014-VolumetricSNIaRates,Strolger2020-ExponentialDTD}.
+Surveys of SNe Ia 
+% have provided the primary observational constraints on the DTD. This can be done 
+can constrain the DTD
+by comparing the observed rate of SNe Ia to their host galaxy parameters \citep[e.g.,][]{Mannucci2005-SNRate,Heringer2019-FieldGalaxyDTD} or inferred star formation histories \citep[SFHs; e.g.,][]{Maoz2012-SloanIIDTD}, measuring SN Ia rates in galaxy clusters \citep[e.g.,][]{Maoz2010-ClusterDTD}, or comparing the volumetric SN Ia rate to the cosmic SFH as a whole \citep[e.g.,][]{Graur2014-VolumetricSNIaRates,Strolger2020-ExponentialDTD}.
 Early studies, which had limited sample sizes, produced unimodal \citep{Strolger2004-SNIaProgenitors} or bimodal \citep{Mannucci2006-TwoPopulations} DTDs where the majority of SNe Ia explode within a relatively narrow range of delay times.
@@
 The uncertainties in the SN Ia DTD propagate into GCE models.
-In principle, then, the observed chemical abundance patterns should contain information about the DTD, and therefore the progenitors, of SNe Ia.
-A few studies have compared different DTDs in one-zone chemical evolution models, but their comparisons to abundance data are limited to the local Solar neighborhood \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
+In principle, the observed chemical abundance patterns should therefore contain information about the SN Ia DTD, and by extension their progenitors.
+A few studies have compared different DTDs in one-zone chemical evolution models, but their comparisons to abundance data are limited to the local solar neighborhood \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
 [Talk about \citep{Matteucci2009-DTDModels} multi-zone models].
-\citet{Poulhazan2018-PrecisionPollution} compared six DTD models in a smoothed-particle hydrodynamics simulation in a cosmological context.
-They found that models with a prompt SN Ia component produced the highest abundance ratios and the narrowest \aFe distributions at late times, although their simulation was not tuned to reproduce the parameters of the Milky Way and they did not compare to observed chemical abundances.
-The current era of large spectroscopic surveys such as the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE} and the forthcoming Milky Way Mapper [cite] has made abundances across the Milky Way disk available for comparison to more sophisticated GCE models.
+\citet{Poulhazan2018-PrecisionPollution} compared six DTDs in a cosmological smoothed-particle hydrodynamics simulation.
+They found that models with a prompt SN Ia component produced the highest abundance ratios and the narrowest \aFe distributions at late times, although their simulation was not tuned to reproduce the parameters of the Milky Way, and they did not compare to observed chemical abundances.
+The current era of large spectroscopic surveys such as the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE} and the forthcoming Milky Way Mapper \citep{Kollmeier2017-SDSS-V} has made abundances across the Milky Way disk available for comparison to more sophisticated GCE models.
 
 % Notes on GCE studies
-% \citet{Andrews2017-ChemicalEvolution} predict abundance tracks and distributions using one-zone models for four different DTD models; they find that most are consistent with their abundance data.
-% \citet{Palicio2023-AnalyticDTD} derive analytic solutions to one-zone chemical evolution equations for seven DTD models, but their comparisons to data are limited to the Solar neighborhood. 
-% \citet{Poulhazan2018-PrecisionPollution} investigate six different DTD models in a smoothed-particle hydrodynamics simulation, but they only present global results for the entire galaxy, they don't compare abundances throughout the disk, and they don't compare to observations.
+% \citet{Andrews2017-ChemicalEvolution} predict abundance tracks and distributions using one-zone models for four different DTDs; they find that most are consistent with their abundance data.
+% \citet{Palicio2023-AnalyticDTD} derive analytic solutions to one-zone chemical evolution equations for seven DTDs, but their comparisons to data are limited to the solar neighborhood. 
+% \citet{Poulhazan2018-PrecisionPollution} investigate six different DTDs in a smoothed-particle hydrodynamics simulation, but they only present global results for the entire galaxy, they don't compare abundances throughout the disk, and they don't compare to observations.
 
@@
 A multi-zone approach allows for a radially-dependent parameterization of the SFH, outflows, stellar migration, and abundance gradient which can better match observations across the Galactic disk.
-We evaluate a selection of DTD models from the literature with multiple SFHs and a prescription for radial stellar migration in the Versatile Integrator for Chemical Evolution \citep[\vice;][]{JohnsonWeinberg2020-Starbursts}.
-In Section \ref{sec:methods}, we present our models for the DTD and SFH, and we describe our chemical evolution models.
-In Section \ref{sec:onezone-results}, we present the results of our one-zone chemical evolution models.
+We evaluate a selection of DTDs from the literature with multiple SFHs and a prescription for radial stellar migration in the Versatile Integrator for Chemical Evolution \citep[\vice;][]{JohnsonWeinberg2020-Starbursts}.
+In Section \ref{sec:methods}, we present our models for the DTD and SFH.
+In Section \ref{sec:onezone-results}, we detail our one-zone chemical evolution models and present results.
 In Section \ref{sec:multizone-results}, we present the results of our multi-zone models and compare to observations.
@@
 
-[Quick note about mass loading?]
+We use \vice to run chemical evolution models which closely follow those of \citet{JohnsonWeinberg2020-Starbursts} and \citet[][hereafter \citetalias{Johnson2021-Migration}]{Johnson2021-Migration}.
+We refer the interested reader to the former for details about the \vice package and to the latter for details about the model Milky Way disk, including the star formation law, radial density gradient, and outflows.
+Similar to \citetalias{Johnson2021-Migration}, we adopt a prescription for radial migration based on the {\tt h277} hydrodynamical simulation \citep{Christensen2012-h277}.
+Appendix \ref{app:migration} describes our method for determining the migration distance $\Delta R_{\rm gal}$ for each model stellar population, which produces smoother distributions in chemical abundance space than the simulation-based approach.
 
@@
 
-For simplicity and easier comparison to the results of \citet{Johnson2021-Migration} (hereafter \citetalias{Johnson2021-Migration}), we focus our analysis on O and Fe, representing the $\alpha$ and Fe-peak elements, respectively.
+For simplicity and easier comparison to the results of \citetalias{Johnson2021-Migration}, we focus our analysis on O and Fe, representing the $\alpha$ and Fe-peak elements, respectively.
 Both elements are produced by CCSNe.
@@
 $t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the maximum simulation time.
-The denominator of Equation \ref{eq:weighted-sfr} is therefore the total number of SNe Ia per M$_{\odot}$ of stars formed.
-
-The yield $y_{\rm Fe}^{\rm Ia}$ measures the mass of Fe produced by SNe Ia per unit mass of star formation. It can be expressed in terms of the integral of the DTD:
+The denominator of Equation \ref{eq:weighted-sfr} is therefore the total number of SNe Ia per M$_{\odot}$ of stars formed $N_{\rm Ia}/M_*$.
+
+The yield $y_{\rm Fe}^{\rm Ia}$ measures the mass of Fe produced by SNe Ia over the full duration of the DTD, which can be expressed as:
 \begin{equation}
@@
 \end{equation}
-where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia, and $N_{\rm Ia}/M_*=2.2\times10^{-3}\,{\rm M}_\odot^{-1}$ is the average number of SNe Ia per mass of stars formed \citep{MaozMannucci2012-SNeIaReview}.
+where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia, and $N_{\rm Ia}/M_*=2.2\pm1\times10^{-3}\,{\rm M}_\odot^{-1}$ is the average number of SNe Ia per mass of stars formed \citep{MaozMannucci2012-SNeIaReview}.
 Adjusting the value of $y_{\rm Fe}^{\rm Ia}$ primarily affects the end point of chemical evolution tracks in [O/Fe]--[Fe/H] space. 
 Following \citetalias{Johnson2021-Migration}, we adopt $y_{\rm Fe}^{\rm Ia}=0.00214$.
-This yield was originally adapted from the W70 model of \citet{Iwamoto1999-SNIaYields}, but was slightly modified so that the inside-out SFH model produces stars with ${\rm [O/Fe]}\approx 0.0$ by the end of the simulation.
-\citet{Palla2021-SNIaYield} studies the effect of different SN Ia yields on GCE models in detail.
-
-\subsection{DTD Models}
+This yield is originally adapted from the W70 model of \citet{Iwamoto1999-SNIaYields}, but it is increased slightly so that the inside-out SFH produces stars with ${\rm [O/Fe]}\approx 0.0$ by the end of the model.
+\citet{Palla2021-SNIaYield} studied the effect of different SN Ia yields on GCE models in detail.
+
+\subsection{Delay Time Distributions}
 \label{sec:dtd-models}
 
-We explore five different functional forms for the SN Ia DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, a two-population model, and a model based on triple-system dynamics, with a one or two variants of each.
-Figure \ref{fig:dtds} presents these DTDs as a function of time after star formation, and Table \ref{tab:dtds} summarizes the DTD models and their parameters.
-We use simple forms rather than simulated physical or analytical models of SNe Ia for the sake of decreased computational time.
-Additionally, physically-motivated models of the DTD must contend with many unknown or poorly-constrained parameters, so our simple forms allow us to reduce the number of free parameters.
-In Appendix \ref{app:analytical-dtds}, we show that a few of our simple forms adequately approximate the more complete analytical models of \citet{Greggio2005-AnalyticalRates}.
-
-In this subsection we present unnormalized functional forms $f_{\rm Ia}$ for each DTD model.
-The relationship between $f_{\rm Ia}$, which has units of ${\rm Gyr}^{-1}$, and $R_{\rm Ia}$, which has units of ${\rm M}_\odot^{-1}\,{\rm Gyr}^{-1}$, is:
+We explore five different functional forms for the DTD: a single power-law, a broken power-law with an initially flat plateau, a simple exponential, a two-population model, and a model based on triple-system dynamics.
+We also investigate one or two useful variations of the input parameters for each functional form.
+Figure \ref{fig:dtds} presents a selection of these DTDs, and Table \ref{tab:dtds} summarizes all of our DTDs and their parameters.
+We use simple forms rather than simulated physical or analytical models of SNe Ia for the sake of decreased computational time and easier interpretation of the model predictions.
+Physically-motivated models of the DTD must contend with many unknown or poorly-constrained parameters, so our simplified forms have the advantage of reducing the number of free parameters.
+In Appendix \ref{app:analytical-dtds}, we show that a few of our simple forms adequately approximate the more complete analytic models of \citet{Greggio2005-AnalyticalRates}.
+
+In this subsection we present functional forms $f_{\rm Ia}$ describing the shape of each DTD.
+$f_{\rm Ia}$ does not include the normalization, so it has units of Gyr$^{-1}$ as opposed to M$_\odot^{-1}$ Gyr$^{-1}$ and ist related to $R_{\rm Ia}$ according to
+% The relationship between $f_{\rm Ia}$, which has units of ${\rm Gyr}^{-1}$, and $R_{\rm Ia}$, which has units of ${\rm M}_\odot^{-1}\,{\rm Gyr}^{-1}$, is: 
 \begin{equation}
@@
 \vice automatically normalizes the provided function for the DTD according to this equation.
+In the remainder of this subsection, we discuss each form of $f_{\rm Ia}$ individually.
 
@@
 All functions are normalized such that $f_{\rm Ia}(t=1\,{\rm Gyr})=1$.
-The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD} at the same scale as the DTD models.
+The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD} at the same scale as the DTDs.
 The horizontal and vertical error bars indicate the time range and 1$\sigma$ uncertainties, respectively, of each DTD measurement.
@@
 
-\begin{deluxetable*}{lcll}
-\tablecaption{Summary of SN Ia DTD models explored in this paper.\label{tab:dtds}}
-\tablehead{
-\colhead{Model} & \colhead{Eq.} & \colhead{Parameters} & \colhead{Similar to}
-}
-\startdata
+% \begin{deluxetable*}{lcll}
+% \tablecaption{Summary of SN Ia DTDs explored in this paper.\label{tab:dtds}}
+% \tablehead{
+% \colhead{Model} & \colhead{Eq.} & \colhead{Parameters} & \colhead{Similar to}
+% }
+% \startdata
+\begin{table*}
+    \centering
+    \caption{Summary of SN Ia delay time distributions (DTDs) explored in this paper.\label{tab:dtds}}
+    \begin{tabular}{lcll}
+        \hline\hline
+        Model & Eq. & Parameters & Similar to \\
+        \hline
+        Two-population  & \ref{eq:prompt-dtd}   & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
+                        &                       & $\tau=3.0$ Gyr & \\
+        Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
+                                                      \citet{Heringer2019-FieldGalaxyDTD}       \\
         Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.1$                 & \citet[][field]{Maoz2017-CosmicDTD}; 
                                                       \citet{Wiseman2021-DESRates}              \\
-Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
-                                              \citet{Heringer2019-FieldGalaxyDTD}       \\
+        Exponential & \ref{eq:exponential-dtd}  & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
+                                                                      \citet{Schonrich2009-RadialMixing};       \\
+                    &                           &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
+        Exponential & \ref{eq:exponential-dtd}   & $\tau=3.0$ Gyr    & --- \\
         Plateau     & \ref{eq:plateau-dtd}  & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
@@
                         &                       & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
-Exponential & \ref{eq:exponential-dtd}  & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
-                                                              \citet{Schonrich2009-RadialMixing};       \\
-            &                           &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
-Exponential & \ref{eq:exponential-dtd}   & $\tau=3.0$ Gyr    & --- \\
-Two-population  & \ref{eq:prompt-dtd}   & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
-                &                       & $\tau=3.0$ Gyr & \\
-\enddata
-\end{deluxetable*}
-
-\paragraph{Power-law} A simple power law with slope $\alpha$:
+        \hline
+    \end{tabular}
+\end{table*}
+% \enddata
+% \end{deluxetable*}
+
+\paragraph{Two-population} A DTD in which $\sim50\%$ of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the remainder form an exponential tail at large $t$:
+\begin{equation}
+    f_{\rm Ia}^{\rm twopop}(t) = 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
+    \label{eq:prompt-dtd}
+\end{equation}
+To approximate the DTD from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in $\sim 50\%$ of SNe Ia exploding within $t<100$ Myr.
+As Figure \ref{fig:dtds} illustrates, the two-population DTD has a shorter median delay time than most other models (except the power-law with $\alpha=-1.4$, not shown).
+This formulation is slightly different than the approximation used in other GCE studies \citep[e.g.,][]{Matteucci2006-BimodalDTDConsequences,Poulhazan2018-PrecisionPollution}, where it has a more distinctly bimodal shape.
+We have compared the two approximations to this DTD in a one-zone model and found that they produce very similar abundance tracks and MDFs.
+This DTD is adopted by the Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations.
+
+\paragraph{Power-law} A single power law with slope $\alpha$:
 \begin{equation}
@@
 
-\paragraph{Plateau} A modification of the simple power-law in which the DTD ``plateaus'' for a duration $W$ before declining:
+\paragraph{Exponential} An exponentially declining DTD with timescale $\tau$:
+\begin{equation}
+    f_{\rm Ia}^{\rm exp}(t) = e^{-t/\tau}
+    \label{eq:exponential-dtd}
+\end{equation}
+This model allows analytic solutions to the abundances as a function of time for some SFHs, making it a popular choice.
+\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assume an exponential DTD with a timescale $\tau=1.5$ Gyr.
+We show in Appendix \ref{app:analytical-dtds} that a $\tau=1.5$ Gyr exponential is an adequate approximation for the analytical SD DTD from \citet{Greggio2005-AnalyticalRates}.
+There is less observational support for an exponential DTD.
+\citet{Strolger2020-ExponentialDTD}, fitting to the cosmic SFH and SFHs from field galaxies, find a range of exponential-like solutions with timescales $\sim 1.5 - 6$ Gyr.
+In this paper, we investigate timescales $\tau=1.5$ and 3 Gyr.
+
+\paragraph{Plateau} A modification of the power-law in which the DTD ``plateaus'' for a duration $W$ before declining:
 \begin{equation}
@@
 % where $B_W=[(W-t_{\rm min}) + \frac{t_{\rm max}^{\alpha+1} - W^{\alpha+1}}{(\alpha+1)W^\alpha}]^{-1}$ is the normalization coefficient.
-Our primary motivation is to consider a model which matches observations at delay times beyond a few Gyr, where the DTD is best constrained, but which has a much smaller fraction of prompt ($\lesssim 100$ Myr) SNe Ia than the simple power law.
-To our knowledge, this form of the DTD has not been considered in previous studies.
-However, we show in Appendix \ref{app:analytical-dtds} that this form can approximate the more complicated analytical DD DTDs from \citet{Greggio2005-AnalyticalRates}.
+Our primary motivation is to consider a model which matches observations at delay times beyond a few Gyr, where the DTD is best constrained, but with a smaller fraction of prompt ($\lesssim 100$ Myr) SNe Ia than the single power law.
+To our knowledge, this form of the DTD has not been considered in previous GCE models.
+We show in Appendix \ref{app:analytical-dtds} that this form can approximate the more complicated analytical DD DTDs from \citet{Greggio2005-AnalyticalRates}.
 We investigate the cases $W=0.3$ Gyr and $W=1$ Gyr, taking $\alpha=-1.1$ for all plateau models.
@@
 \end{equation}
-with $t_{\rm rise}=0.5$ Gyr, $W=0.5$ Gyr, $\alpha=-1.1$, and $\epsilon=0.05$ so the initial rate is 5\% of the peak rate.
-
-\paragraph{Exponential} An exponentially declining DTD with timescale $\tau$:
-\begin{equation}
-    f_{\rm Ia}^{\rm exp}(t) = \frac{1}{\tau} e^{-t/\tau}
-    \label{eq:exponential-dtd}
-\end{equation}
-This model can be used to calculate an analytic solution to the equations of chemical equilibrium, making it a popular choice among GCE studies.
-\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assume an exponential DTD with a timescale $\tau=1.5$ Gyr.
-We show in Appendix \ref{app:analytical-dtds} that a $\tau=1.5$ Gyr exponential is an adequate approximation for the analytical SD DTD from \citet{Greggio2005-AnalyticalRates}.
-There is less observational support for an exponential DTD.
-\citet{Strolger2020-ExponentialDTD}, fitting to the cosmic SFH and SFHs from field galaxies, find a range of exponential-like solutions with timescales $\sim 1.5 - 6$ Gyr.
-In this paper we investigate timescales $\tau=1.5$ and 3 Gyr.
-% I've looked at Matteucci & Greggio (1986) and I'm not sure what their DTD would be
-
-\paragraph{Two-population} A DTD in which $\sim50\%$ of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the remainder form an exponential tail at large $t$:
-\begin{equation}
-    f_{\rm Ia}^{\rm twopop}(t) = 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
-    \label{eq:prompt-dtd}
-\end{equation}
-To approximate the DTD from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in $\sim 50\%$ of SNe Ia exploding within $t<100$ Myr.
-This formulation is slightly different than the approximation used in other GCE studies \citep[e.g.,][]{Matteucci2006-BimodalDTDConsequences,Poulhazan2018-PrecisionPollution}, where it has a more distinctly bimodal shape.
-We have compared the two approximations to this DTD in a one-zone model and found that they produce very similar abundance tracks and MDFs.
-This DTD is adopted by the Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations.
+with $t_{\rm rise}=0.5$ Gyr, $W=0.5$ Gyr, $\alpha=-1.1$, and $\epsilon=0.05$ (i.e., the initial rate is 5\% of the peak rate).
+As illustrated in Figure \ref{fig:dtds}, the triple-system DTD has the longest median delay time out of all the models we investigate.
 
@@
 
-In addition to the DTD shape, the minimum SN Ia delay time $t_D$ is another parameter which can have an effect on chemical evolution observables, such as the location of the high-$\alpha$ knee and the [O/Fe] distribution function (DF) \citep{Andrews2017-ChemicalEvolution}.
+In addition to the DTD shape, the minimum SN Ia delay time $t_D$ is another parameter that can have an effect on chemical evolution observables, such as the location of the high-$\alpha$ knee and the [O/Fe] distribution function \citep[DF;][]{Andrews2017-ChemicalEvolution}.
 The value of $t_D$ is set by the lifetime of the most massive SN Ia progenitor system.
 Previous GCE studies have adopted values ranging from $t_D\approx30$ Myr \citep[e.g.,][]{Poulhazan2018-PrecisionPollution} to $t_D=150$ Myr \citepalias[e.g.,][]{Johnson2021-Migration}.
-We take $t_D=40$ Myr to be our fiducial value as it is the approximate lifetime of an $8\,{\rm M}_\odot$ star.
-In Section \ref{sec:onezone-results} we find that adopting a longer $t_D$ has only a minor effect on the chemical evolution for most DTD models except the power-law, but in that case the effect of a longer $t_D$ can be approximated by adding an initial plateau of width $W=0.3$ Gyr to the DTD (see Figure \ref{fig:onezone-twopanel}).
+We take $t_D=40$ Myr as our fiducial value as it is the approximate lifetime of an $8\,{\rm M}_\odot$ star.
+In Section \ref{sec:onezone-results} we find that adopting a longer $t_D$ has only a minor effect on the chemical evolution for most DTDs except the power-law, but in that case the effect of a longer $t_D$ can be approximated by adding an initial plateau of width $W=0.3$ Gyr to the DTD (see Figure \ref{fig:onezone-twopanel}).
 
@@
 
-We consider four models for the SFH: inside-out, late-burst, early-burst, and two-infall. 
-The former two models, which feature a smooth SFH, were investigated by \citetalias{Johnson2021-Migration} using a similar methodology to this work.
+We consider four models for the SFH, which we refer to as inside-out, late-burst, early-burst, and two-infall. 
+The former two models, which feature a smooth SFH, were investigated by \citetalias{Johnson2021-Migration} using a similar methodology to this paper.
 The inside-out model produced a better agreement to the age--[O/Fe] relation observed by \citet{Feuillet2019-MilkyWayAges}, while the late-burst model better matched their observed age--metallicity relation.
-The latter two models (early-burst and two-infall) feature discontinuous or ``bursty'' SFHs, and were proposed by \citet{Conroy2022-ThickDisk} and \citet{Chiappini1997-TwoInfall}, respectively, to explain the distinct evolution of the high- and low-$\alpha$ sequences.
+% The latter two models (early-burst and two-infall) feature discontinuous or ``bursty'' SFHs, and were proposed by \citet{Conroy2022-ThickDisk} and \citet{Chiappini1997-TwoInfall}, respectively, to explain the distinct evolution of the high- and low-$\alpha$ sequences.
+The latter two models feature discontinuous or ``bursty'' SFHs.
+The early-burst model, proposed by \citet{Conroy2022-ThickDisk}, uses an efficiency-driven starburst to explain the break in the \aFe trend observed in the H3 survey \citep{Conroy2019-H3Survey}.
+% , and [cite] found that it can also produce a bimodal \aFe distribution.
+The two-infall model was proposed by \citet{Chiappini1997-TwoInfall} and features two distinct episodes of gas infall which produce the thick and thin disks.
 Together, these four models cover a range of behavior including a smooth SFH and SFR-, SFE-, and infall-driven starbursts.
@@
 The remaining quantities, infall rate (IFR) surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
-The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$ and $\uptau_*$.
-The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four equations are specified.
-See Appendix B of \citetalias{Johnson2021-Migration} for details on the normalization of the SFH.
-All models have zero initial gas mass in all zones.
-We present an overview of these models in Figure \ref{fig:sfhs}.
+The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\uptau_*$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in SFR mode).
+The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified.
+% See Appendix B of \citetalias{Johnson2021-Migration} for details on the normalization of the SFH. 
+The SFH is normalized such that the model predicts an accurate total stellar mass and surface density gradient (see Appendix B of \citetalias{Johnson2021-Migration}).
+We present an overview of the four SFHs in Figure \ref{fig:sfhs}, and we discuss them individually here.
 
@@
     \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\uptau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
-In each panel, we plot curves for the simulation zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
+In each panel, we plot curves for the model zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
     \label{fig:sfhs}
@@
 where we assume $\tau_{\rm rise}=2$ Gyr for all radii.
-The SFH timescale $\tau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\tau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the Solar annulus and longer timescales in the outer Galaxy.
-The $\tau_{\rm sfh} - R_{\rm gal}$ relation is determined from the data of \citet{Sanchez2020-StarFormationTimescales}; see Section 2.5 of \citetalias{Johnson2021-Migration} for the details.
-% For a detailed look at the normalization of the SFR with $R_{\rm gal}$, we refer the reader to Appendix B of \citetalias{Johnson2021-Migration}.
-
-\paragraph{Late-burst} A variation on the inside-out SFH with a Gaussian burst in the SFR at late times:
+The SFH timescale $\tau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\tau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the solar annulus and longer timescales in the outer Galaxy.
+The $\tau_{\rm sfh} - R_{\rm gal}$ relation is based on the radial gradients in stellar age in Milky Way-like spirals measured by \citet[][see Section 2.5 of \citetalias{Johnson2021-Migration} for details]{Sanchez2020-StarFormationTimescales}.
+
+\paragraph{Late-burst} A variation on the inside-out SFH with a burst in the SFR at late times which is described by a Gaussian according to
 \begin{equation}
@@
 where $A_b$ is the dimensionless amplitude of the starburst, $t_b$ is the time of the peak of the burst, and $\sigma_b$ is the width of the Gaussian. 
-Evidence for a recent star formation burst $\sim 2-3$ Gyr ago has been found in {\it Gaia} \citep{Mor2019-Starburst} and in massive WDs in the Solar neighborhood \citep{Isern2019-Starburst}.
+Evidence for a recent star formation burst $\sim 2-3$ Gyr ago has been found in {\it Gaia} \citep{Mor2019-Starburst} and in massive WDs in the solar neighborhood \citep{Isern2019-Starburst}.
 Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr. The determination of $\tau_{\rm sfh}$ 
@@
 \paragraph{Early-burst} An extension of the model proposed by \citet{Conroy2022-ThickDisk} to explain the non-monotonic behavior of the high-$\alpha$ sequence down to ${\rm [Fe/H]}\approx-2.5$.
-An abrupt factor $\sim20$ rise in the SFE at early times drives an increase in the [O/Fe] abundance and populates the high-$\alpha$ sequence.
-We adopt the formula for the time-dependence of the SFE timescale from \citet{Conroy2022-ThickDisk}:
+This model features an abrupt factor $\sim20$ rise in the SFE at early times, driving an increase in the [O/Fe] abundance at the transition between the epochs of halo and thick disk formation.
+\citet{Stahlholdt2022-StarFormationEpochs} find evidence for a burst $\sim10$ Gyr ago which marks the beginning of a second phase of star formation.
+[Something about $\alpha$-bimodality from another paper].
+We adopt the following formula for the time-dependence of the SFE timescale from \citet{Conroy2022-ThickDisk}:
 \begin{equation}
@@
 \end{equation}
-In contrast to the previous SFH models, we run the early-burst model in \vice's ``infall'' mode.
 While \citet{Conroy2022-ThickDisk} use a constant infall rate in their one-zone model, we adopt a radially-dependent infall rate which declines exponentially with time:
@@
 Following \citet{BlandHawthornGerhard2016-MilkyWayReview}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
-We note that some previous studies which use the two-infall model \citep[e.g.,][]{Spitoni2021-TwoInfall} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the Solar abundance.
-We adopt radially-dependent outflows as in \citetalias{Johnson2021-Migration} (see their Section 2.4 for details) for all our SFH models, including two-infall.
+We note that most previous studies which use the two-infall model \citep[e.g.,][]{Spitoni2021-TwoInfall} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance.
+We adopt radially-dependent outflows as in \citetalias{Johnson2021-Migration} (see their Section 2.4 for details) for all our SFHs, including two-infall.
 We discuss the implications of this difference in Section \ref{sec:two-infall-discussion}.
 
-\subsection{Observational Sample}
-\label{sec:observational-sample}
-
-We compare our simulation results to abundance measurements from the final data release \citep[DR17;][]{Abdurro'uf2022-SDSSIV-DR17} of the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE}.
-APOGEE used infrared spectrographs \citep{Wilson2019-APOGEE-Spectrographs} mounted on two telescopes: the 2.5-meter Sloan Foundation Telescope \citep{Gunn2006-SloanTelescope} at Apache Point Observatory, United States in the Northern Hemisphere, and the Ir{\'e}n{\'e}e DuPont Telescope \citep{BowenVaughan1973-DuPontTelescope} at Las Campanas Observatory, Chile in the Southern Hemisphere.
-After the spectra were passed through the data reduction pipeline \citep{Nidever2015-APOGEE-DataReduction}, the APOGEE Stellar Parameter and Chemical Abundance Pipeline \citep[ASPCAP;][]{Holtzmann2015-ASPCAP,GarciaPerez2016-ASPCAP} extracted chemical abundances using the model grids and interpolation method described by \citet{Jonsson2020-APOGEE-DR16}.
-
-We restrict our sample to red giant branch and red clump stars with high-quality spectra.
-Table \ref{tab:sample-selection} lists our selection criteria, which largely follow from \citet{Hayden2015-ChemicalCartography}.
-This produces a final sample of \variable{output/sample_size.txt}stars with [O/Fe] and [Fe/H] abundance measurements.
-APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
-We use estimated ages from \citet{Leung2023-Ages} (hereafter \citetalias{Leung2023-Ages}), who use a variational encoder-decoder network to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
-Importantly, the \citetalias{Leung2023-Ages} sample does not experience the $\sim10$ Gyr plateau that affects ages from astroNN \citep{Mackereth2019-astroNN-Ages}.
-We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt}APOGEE stars with age estimates.
-We note that we use the full sample of \variable{output/sample_size.txt}APOGEE stars unless we explicitly compare to age estimates.
-Table \ref{tab:uncertainties} presents the median uncertainties in the data for [Fe/H], [O/Fe], and age.
-
-\begin{deluxetable*}{lll}
-    \tablecaption{Sample selection parameters from APOGEE DR17\label{tab:sample-selection}}
-    \tablehead{
-        \colhead{Parameter} & \colhead{Range} & \colhead{Notes}
-    }
-    \startdata
-        $\log g$            & $1.0 < \log g < 3.8$          & Select giants only \\
-        $T_{\rm eff}$       & $3500 < T_{\rm eff} < 5500$ K & Reliable temperature range \\
-        $S/N$               & $S/N > 80$                    & Required for accurate stellar parameters \\
-        ASPCAPFLAG Bits     & $\notin$ 23                   & Remove stars flagged as bad \\
-        EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
-        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{Leung2023-Ages}
-    \enddata
-\end{deluxetable*}
-
-\begin{deluxetable}{lll}
-    \tablecaption{Median Parameter Uncertainties\label{tab:uncertainties}}
-    \tablehead{
-        \colhead{Parameter} & \colhead{Median Uncertainty} & \colhead{Source}
-    }
-    \startdata
-        ${\rm [Fe/H]}$ & $9.2\times10^{-3}$ & APOGEE DR17 \\
-        ${\rm [O/Fe]}$ & $1.8\times10^{-2}$ & APOGEE DR17 \\
-        log(Age/Gyr) & $0.10$ & \citetalias{Leung2023-Ages}
-        % Age/Gyr & 29\% & astroNN
-    \enddata
-\end{deluxetable}
-
-\section{Results from One-Zone Models}
-\label{sec:onezone-results}
-
-\begin{deluxetable}{Ccl}
-    \tablecaption{A summary of parameters and their fiducial values for our one-zone chemical evolution models.\label{tab:onezone-parameters}}
-    \tablehead{
-        \colhead{Quantity} & \colhead{Value} & \colhead{Description}
-    }
-    \startdata
-    \Delta t        & 10 Myr    & Time-step size \\
-    t_{\rm max}     & 13.2 Gyr  & Maximum simulation time \\
-    \eta            & 2.15      & Outflow mass-loading factor \\
-    \uptau_*        & 2.0 Gyr   & SFE timescale \\
-    \dot M_r        & continuous    & Recycling rate \\
-    t_D             & 40 Myr    & Minimum SN Ia delay time \\
-    M_{g,0}   & 0         & Initial gas mass \\
-    \dot M_*(t)     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
-    \tau_{\rm rise} & 2.0 Gyr     & SFR rise timescale \\
-    \tau_{\rm sfh}  & 15.1 Gyr  & SFR exponential timescale
-    \enddata
-\end{deluxetable}
-
-% [Intro paragraph, motivation for running one-zone models]
-Before running the full multi-zone simulations, it will be useful to observe the effects of the DTD in more idealized conditions.
-A one-zone model assumes the entire gas reservoir is instantaneously mixed, so there is no spatial dependence for the distribution of metal abundances.
-This limits the ability to compare to observations across the disk, but it allows the models to be run in a fraction of the time and eliminates the complicating factor of stellar migration.
-In this section, we compare the results from one-zone models which examine various parameters of the DTD while keeping other parameters fixed.
-
-All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=0.01$ Gyr.
-We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr), an SFE timescale $\uptau_*\equiv M_g/\dot M_*=2$ Gyr, and an initial gas mass $M_{g,0}=0$.
-We adopt continuous recycling, which accounts for the time-dependent return of mass from all previous generations of stars \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
-Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time of 40 Myr.
-A summary of these fiducial parameters is presented in Table \ref{tab:onezone-parameters}.
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=\linewidth]{figures/onezone_threepanel.pdf}
-    \caption{\textit{Left:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone chemical evolution models models which assume a power-law DTD.
-The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively.
-For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr.
-The open symbols located along each curve mark logarithmic steps in simulation time.
-The marginal panels above and to the right of the central panel present the distribution functions (DFs) of [Fe/H] and [O/Fe], respectively.
-For display purposes, these distributions are convolved with a Gaussian kernel with a standard deviation of 0.02 dex.
-    \textit{Middle:} Similar, comparing exponential DTDs with varying timescales. The solid, dashed, and dotted curves represent timescales $\tau=6$, 3, and 1.5 Gyr, respectively.
-    \textit{Right:} Similar, comparing plateau DTDs with varying plateau widths.
-The solid, dashed, and dotted green curves represent widths $W=1$, 0.3, and 0.1 Gyr, respectively.
-All plateau DTD models assume a post-plateau power-law slope of $\alpha=-1.1$.
-For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted purple curve represents a power-law DTD with $\alpha=-1.1$ and no plateau.}
-    \label{fig:onezone-threepanel}
-    \script{onezone_threepanel.py}
-\end{figure*}
-
-The left-hand panel of Figure \ref{fig:onezone-threepanel} compares the results of three one-zone models that are identical except for the slope of the power-law DTD.
-A steeper slope produces a sharper ``knee'' and a faster decline in [O/Fe], resulting in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
-Conversely, a shallower slope produces a gentler knee and slower decline in [O/Fe], resulting in a broader [O/Fe] DF and a greater number of high-$\alpha$ stars.
-In all cases the [O/Fe] DF is distinctly unimodal.
-The [Fe/H] DF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
-
-Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in the middle panel of Figure \ref{fig:onezone-threepanel}.
-Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around a simulation time of 1 Gyr.
-A short exponential timescale shifts this knee down to lower [O/Fe] values, while a longer timescale raises it.
-The effect on the [O/Fe] DF is similar to the power-law slope: a short timescale produces more low-$\alpha$ stars, while a long timescale produces more high-$\alpha$ stars (but still a unimodal distribution).
-The effect on the [Fe/H] DF is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values.
-A doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
-For all exponential models, the low-$\alpha$ peak sits approximately 0.02 dex lower than for the power-law models.
-
-Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of the plateau DTD model width on abundance tracks and distributions.
-The effect on the [O/Fe] DF is similar to the previous two models: a longer plateau raises the median delay time, resulting in a smaller low-$\alpha$ peak and a more prominent high-$\alpha$ tail.
-The abundance tracks from several different plateau widths fill the space in between the exponential ($\tau=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
-The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\tau=3$ Gyr), although the [O/Fe] DFs are somewhat more distinct, with the plateau model producing a peak closer to the power-law case.
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=\linewidth]{figures/onezone_twopanel.pdf}
-    \caption{\textit{Left:} Comparison of one-zone models with minimum SN Ia delay times of 40 Myr (solid curves) and 150 Myr (dashed curves) for two DTDs: a power-law with $\alpha=-1.1$ (blue curves), and an exponential with $\tau=1.5$ Gyr (purple curves).
-The layout is similar to the plots in Figure \ref{fig:onezone-threepanel}.
-For clarity, we assume a mass-loading factor $\eta=1$ for the exponential DTD curves.
-    \textit{Right:} Comparison of one-zone models which assume all five functional forms for the DTD in this paper: triple-system (green), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
-A minimum SN Ia delay time of 40 Myr is assumed for all models in the right panel.}
-    \label{fig:onezone-twopanel}
-    \script{onezone_twopanel.py}
-\end{figure*}
-
-One parameter of the DTD which we hold fixed in the multi-zone models is the minimum SN Ia delay time $t_D$.
-Typical choices for $t_D$ in the literature range from $\sim 30$ Myr \citep[e.g.,][]{Poulhazan2018-PrecisionPollution} to 150 Myr \citepalias[e.g.,][]{Johnson2021-Migration}.
-The left-hand panel of Figure \ref{fig:onezone-twopanel} shows that $t_D$ has a much stronger effect on the abundance tracks and distributions of models which assume a power-law DTD than models which assume a plateau or exponential DTD.
-This is a consequence of the much higher number of prompt SNe Ia in the power-law models compared to the others (see Figure \ref{fig:dtds}).
-Moreover, a power-law DTD with a long $t_D$ may be observationally hard to distinguish from a plateau model.
-In Figure \ref{fig:onezone-twopanel}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (dashed purple line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (solid green line), and their [O/Fe] DFs are virtually identical.
-The difference between the two values of $t_D$ for the exponential ($\tau=3$ Gyr) DTD in both the abundance tracks and distributions is nearly indistinguishable.
-We do not consider the effect on the other DTD models because a 150 Myr minimum delay time is incompatible with the two-population model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD due to its low SN Ia rate at short delay times.
-
-The right-hand panel of Figure \ref{fig:onezone-twopanel} compares the one-zone model outputs from the full range of DTD models we investigate in this work.
-As with the individual DTD parameters, the choice of DTD primarily affects the location of the high-$\alpha$ ``knee'' in the [Fe/H]--[O/Fe] abundance tracks.
-At one extreme is the triple-system model, which sees the CC SN plateau extend up to ${\rm [Fe/H]}\approx0.8$ followed by a sharp downward turn as the SN Ia rate suddenly increases at a delay time of 500 Myr.
-Star formation proceeds for such a long time before the knee that the [O/Fe] DF shows a slight second peak around the CC SN value; this model is the only one which produces any amount of bimodality in the one-zone simulations.
-At the other extreme are the two-population and power-law ($\alpha=-1.1$) models which peak immediately after the minimum delay time of 40 Myr, placing the knee at ${\rm [Fe/H]}\approx-1.8$.
-The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is a result of the delayed exponential component.
-The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models lie in the intermediate space between these extremes.
-On the other hand, the [O/Fe] DF from the exponential model has the strongest peak, while the plateau ($W=1$ Gyr) and triple-system models produce nearly identical distributions in the low-$\alpha$ regime.
-The power-law ($\alpha=-1.1$) and two-population DTDs produce similar [O/Fe] DFs despite notably different abundance tracks.
-The exponential ($\tau=3$ Gyr) and plateau ($W=0.3$ Gyr) models, while not shown, produce similar abundance tracks to the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models, respectively.
-
-% [Summary and conclusions from one-zone models]
-The results presented in this section indicate that the observables which should show the greatest effect from the choice of DTD are the [O/Fe]--[Fe/H] abundance tracks and the [O/Fe] DF.
-Degeneracies between models in one regime, such as the abundance tracks from the exponential ($\tau=3$ Gyr) and plateau ($W=1$ Gyr) DTDs, can be resolved in the other.
-Of course, both of these observables are also greatly affected by the parameters of the SFH.
-In this section we focused on the fiducial inside-out SFH model; for a similar comparison of DTD models with a two-infall SFH, we direct the reader to \citet{Palicio2023-AnalyticDTD}.
-
-\section{Results from Multi-Zone Models}
-\label{sec:multizone-results}
+\subsection{The Multi-Zone Disk Model}
+\label{sec:multizone-methods}
 
@@
     \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models.
-We omit parameters that are unchanged from \citetalias{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
+We omit some parameters that are unchanged from \citetalias{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
     \tablehead{
@@
     \startdata
-        % Multi-zone simulation parameters
-        R_{\rm gal}     & [0, 20] kpc   & \ref{sec:multizone-results} & Galactocentric radius \\
-        \delta R_{\rm gal}  & 100 pc    & \ref{sec:multizone-results} & Width of each concentric ring \\
+        % Multi-zone model parameters
+        R_{\rm gal}     & [0, 20] kpc   & \ref{sec:multizone-methods} & Galactocentric radius \\
+        \delta R_{\rm gal}  & 100 pc    & \ref{sec:multizone-methods} & Width of each concentric ring \\
         \Delta R_{\rm gal}  & N/A       & \ref{app:migration} & Change in orbital radius due to stellar migration \\
@@
         p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
-        \Delta t        & 10 Myr    & \ref{sec:multizone-results} & Time-step size \\
-        t_{\rm max}     & 13.2 Gyr  & \ref{sec:multizone-results} & Maximum simulation time \\
-        n               & 8         & \ref{sec:multizone-results} & Number of stellar populations formed per ring per time-step \\
-        R_{\rm SF}      & 15.5 kpc  & \ref{sec:multizone-results} & Maximum radius of star formation \\
+        \Delta t        & 10 Myr    & \ref{sec:multizone-methods} & Time-step size \\
+        t_{\rm max}     & 13.2 Gyr  & \ref{sec:multizone-methods} & Maximum simulation time \\
+        n               & 8         & \ref{sec:multizone-methods} & Number of stellar populations formed per ring per time-step \\
+        R_{\rm SF}      & 15.5 kpc  & \ref{sec:multizone-methods} & Maximum radius of star formation \\
         M_{g,0}   & 0         & \ref{sec:sfh}     & Initial gas mass \\
+        \dot M_r    & continuous    & \ref{sec:multizone-methods} & Recycling rate \citep[][Equation 2]{JohnsonWeinberg2020-Starbursts} \\
         % DTD
@@
         f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the late-burst SFR \\
+        \tau_{\rm rise}             & 2 Gyr     & \ref{sec:sfh} & SFR rise timescale for inside-out and early-burst models \\
         \uptau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the early-burst SFE timescale \\
@@
         f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the two-infall IFR \\
+        \hline
+        % One-zone parameters
+        \uptau_*                        & 2 Gyr & \ref{sec:onezone-results} & SFE timescale in one-zone models \\
+        \eta(R_{\rm gal}=8\,{\rm kpc})  & 2.15  & \ref{sec:onezone-results} & Outflow mass-loading factor at the solar annulus \\
+        \tau_{\rm sfh}(R_{\rm gal}=8\,{\rm kpc})    & 15.1 Gyr  & \ref{sec:sfh} & SFH timescale at the solar annulus \\
     \enddata
 \end{deluxetable*}
+\vspace{-24pt}
 
@@
 The gas in each ring is assumed to be instantaneously mixed; while star particles are allowed to migrate radially (see Appendix \ref{app:migration}), there is no exchange of gas between rings.
-We run our simulations with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
+We run our models with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
 Following \citetalias{Johnson2021-Migration}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_*=0$ for $R_{\rm gal}>R_{\rm SF}$ (stars are allowed to migrate past $R_{\rm SF}$, they are just not born there).
-We summarize the parameters for our multi-zone models in Table \ref{tab:multizone-parameters}.
+We adopt continuous recycling, which accounts for the time-dependent return of mass from all previous generations of stars \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
+We summarize these parameters, as well as those discussed in previous sub-sections, in Table \ref{tab:multizone-parameters}.
+
+\subsection{Observational Sample}
+\label{sec:observational-sample}
+
+\begin{table*}
+    \centering
+    \caption{Sample selection parameters and median uncertainties from APOGEE DR17.}
+    \label{tab:sample}
+    \begin{tabular}{lll}
+        \hline\hline
+        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Range or Value} & \multicolumn{1}{c}{Notes} \\
+        \hline
+        $\log g$            & $1.0 < \log g < 3.8$          & Select giants only \\
+        $T_{\rm eff}$       & $3500 < T_{\rm eff} < 5500$ K & Reliable temperature range \\
+        $S/N$               & $S/N > 80$                    & Required for accurate stellar parameters \\
+        ASPCAPFLAG Bits     & $\notin$ 23                   & Remove stars flagged as bad \\
+        EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
+        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{Leung2023-Ages} \\
+        \hline
+        $\sigma({\rm [Fe/H]})$ & $9.2\times10^{-3}$ & Median uncertainty in [Fe/H] \\
+        $\sigma({\rm [O/Fe]})$ & $1.8\times10^{-2}$ & Median uncertainty in [O/Fe] \\
+        $\sigma($log(Age/Gyr)) & $0.10$ & Median age uncertainty \citepalias{Leung2023-Ages} \\
+        \hline
+    \end{tabular}
+\end{table*}
+
+% \begin{table}
+%     \centering
+%     \caption{Median parameter uncertainties}
+%     \label{tab:uncertainties}
+%     \begin{tabular}{ccc}
+%         \hline\hline
+%         Parameter & Median Uncertainty & Source \\
+%         \hline
+%         ${\rm [Fe/H]}$ & $9.2\times10^{-3}$ & APOGEE DR17 \\
+%         ${\rm [O/Fe]}$ & $1.8\times10^{-2}$ & APOGEE DR17 \\
+%         log(Age/Gyr) & $0.10$ & \citetalias{Leung2023-Ages} \\
+%         \hline
+%     \end{tabular}
+% \end{table}
+
+We compare our model results to abundance measurements from the final data release \citep[DR17;][]{Abdurro'uf2022-SDSSIV-DR17} of the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE}.
+APOGEE used infrared spectrographs \citep{Wilson2019-APOGEE-Spectrographs} mounted on two telescopes: the 2.5-meter Sloan Foundation Telescope \citep{Gunn2006-SloanTelescope} at Apache Point Observatory in the Northern Hemisphere, and the Ir{\'e}n{\'e}e DuPont Telescope \citep{BowenVaughan1973-DuPontTelescope} at Las Campanas Observatory in the Southern Hemisphere.
+After the spectra were passed through the data reduction pipeline \citep{Nidever2015-APOGEE-DataReduction}, the APOGEE Stellar Parameter and Chemical Abundance Pipeline \citep[ASPCAP;][]{Holtzmann2015-ASPCAP,GarciaPerez2016-ASPCAP} extracted chemical abundances using the model grids and interpolation method described by \citet{Jonsson2020-APOGEE-DR16}.
+
+We restrict our sample to red giant branch and red clump stars with high-quality spectra.
+Table \ref{tab:sample} lists our selection criteria, which largely follow from \citet{Hayden2015-ChemicalCartography}.
+This produces a final sample of \variable{output/sample_size.txt}stars with [O/Fe] and [Fe/H] abundance measurements.
+APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
+We use estimated ages from \citet[][hereafter \citetalias{Leung2023-Ages}]{Leung2023-Ages}, who use a variational encoder-decoder network to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
+Importantly, the \citetalias{Leung2023-Ages} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{Mackereth2019-astroNN-Ages}.
+We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt}APOGEE stars with age estimates.
+We note that we use the full sample of \variable{output/sample_size.txt}APOGEE stars unless we explicitly compare to age estimates.
+Table \ref{tab:sample} also presents the median uncertainties in the data for [Fe/H], [O/Fe], and age.
+
+\section{Results from One-Zone Models}
+\label{sec:onezone-results}
+
+% \begin{table}
+%     \centering
+%     \caption{A summary of parameters and their fiducial values for our one-zone chemical evolution models.\label{tab:onezone-parameters}}
+%     \begin{tabular}{ccl}
+%         \hline\hline
+%         Quantity & Value & \multicolumn{1}{c}{Description} \\
+%         \hline
+%         % $\Delta t$        & 10 Myr    & Time-step size \\
+%         % $t_{\rm max}$     & 13.2 Gyr  & Maximum simulation time \\
+%         % $\eta$            & 2.15      & Outflow mass-loading factor \\
+%         % $\uptau_*$        & 2.0 Gyr   & SFE timescale \\
+%         $\dot M_r$        & continuous    & Recycling rate \\
+%         % $t_D$             & 40 Myr    & Minimum SN Ia delay time \\
+%         % $M_{g,0}$         & 0         & Initial gas mass \\
+%         % $\dot M_*(t)$     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
+%         % $\tau_{\rm rise}$ & 2.0 Gyr     & SFR rise timescale \\
+%         % $\tau_{\rm sfh}$  & 15.1 Gyr  & SFR exponential \\
+%         \hline
+%     \end{tabular}
+% \end{table}
+
+% [Intro paragraph, motivation for running one-zone models]
+Before running the full multi-zone models, it is useful to observe the effects of the DTD in more idealized conditions.
+A one-zone model assumes the entire gas reservoir is instantaneously mixed, removing all spatial dependence.
+This limits the ability to compare to observations across the disk, but it allows the models to be run in a fraction of the time and eliminates the complicating factor of stellar migration.
+In this section, we compare the results from one-zone models which examine various parameters of the DTD while keeping other parameters fixed.
+
+% All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=10$ Myr. 
+For consistency, we adopt most of the parameter values from Table \ref{tab:multizone-parameters} for our one-zone models.
+We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr) and an SFE timescale $\uptau_*\equiv M_g/\dot M_*=2$ Gyr.
+Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time $t_D=40$ Myr.
+% A summary of these fiducial parameters is presented in Table \ref{tab:onezone-parameters}.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figures/onezone_threepanel.pdf}
+    \caption{{\it Each panel:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone chemical evolution models which assume the same DTD.
+The open symbols along each curve mark logarithmic steps in time.
+The top and right-hand marginal panels present the distribution functions (DFs) of [Fe/H] and [O/Fe], respectively.
+For display purposes, these distributions are convolved with a Gaussian kernel with a standard deviation of 0.02 dex.
+    \textit{Left:} Three models which assume a power-law DTD with varying slope $\alpha$. 
+    % The dotted, dashed, and solid curves represent models with $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively. 
+    For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr. 
+    \textit{Center:} Three models which assume an exponential DTD with varying timescale $\tau$. 
+    % The solid, dashed, and dotted curves represent $\tau=6$, 3, and 1.5 Gyr, respectively.
+    \textit{Right:} Three models which assume a plateau DTD with varying plateau width $W$. 
+    % The solid, dashed, and dotted green curves represent $W=1$, 0.3, and 0.1 Gyr, respectively. 
+    All assume a post-plateau slope of $\alpha=-1.1$.
+For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted purple curve represents a power-law DTD with $\alpha=-1.1$ and no plateau.}
+    \label{fig:onezone-threepanel}
+    \script{onezone_threepanel.py}
+\end{figure*}
+
+The left-hand panel of Figure \ref{fig:onezone-threepanel} compares the results of three one-zone models that are identical except for the slope of the power-law DTD.
+A steeper slope produces a sharper ``knee'' and a faster decline in [O/Fe], resulting in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
+Conversely, a shallower slope produces a gentler knee and slower decline in [O/Fe], resulting in a broader [O/Fe] DF and a greater number of high-$\alpha$ stars.
+In all cases the [O/Fe] DF is distinctly unimodal.
+The [Fe/H] DF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
+
+Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in the middle panel of Figure \ref{fig:onezone-threepanel}.
+Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around a simulation time of 1 Gyr.
+A short exponential timescale shifts this knee down to lower [O/Fe] values, while a longer timescale raises it.
+The effect on the [O/Fe] DF is similar to the power-law slope: a short timescale produces more low-$\alpha$ stars, while a long timescale produces more high-$\alpha$ stars (but still a unimodal distribution).
+The effect on the [Fe/H] DF is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values.
+A doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
+For all exponential models, the low-$\alpha$ peak sits approximately 0.02 dex lower than for the power-law models.
+
+Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of the plateau DTD width on abundance tracks and distributions.
+The effect on the [O/Fe] DF is similar to the previous two models: a longer plateau raises the median delay time, resulting in a smaller low-$\alpha$ peak and a more prominent high-$\alpha$ tail.
+The abundance tracks from several different plateau widths fill the space in between the exponential ($\tau=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
+The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\tau=3$ Gyr), although the [O/Fe] DFs are somewhat more distinct, with the plateau model producing a peak closer to the power-law case.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figures/onezone_twopanel.pdf}
+    \caption{\textit{Left:} Comparison of one-zone models with different minimum delay times $t_D$ and DTDs.
+    % minimum SN Ia delay times $t_D=40$ Myr (solid) and 150 Myr (dashed curves) for three DTDs: power-law with $\alpha=-1.1$ (blue), plateau with $W=0.3$ Gyr (green), and exponential with $\tau=1.5$ Gyr (purple curves).
+    The layout is similar to Figure \ref{fig:onezone-threepanel}. For clarity, we assume a mass-loading factor $\eta=1$ for the exponential DTD curves, which places the end-point at higher [Fe/H].
+    \textit{Right:} Comparison of one-zone models with five different forms for the DTD.
+    % : triple-system (yellow), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
+    }
+    \label{fig:onezone-twopanel}
+    \script{onezone_twopanel.py}
+\end{figure*}
+
+One parameter of the DTD which we hold fixed in the multi-zone models is the minimum SN Ia delay time $t_D$.
+Typical choices for $t_D$ in the literature range from $\sim 30$ Myr \citep[e.g.,][]{Poulhazan2018-PrecisionPollution} to 150 Myr \citepalias[e.g.,][]{Johnson2021-Migration}.
+The left-hand panel of Figure \ref{fig:onezone-twopanel} shows that $t_D$ has a much stronger effect on the abundance tracks and distributions of models which assume a power-law DTD than models which assume a plateau or exponential DTD.
+This is a consequence of the much higher number of prompt SNe Ia in the power-law models compared to the others (see Figure \ref{fig:dtds}).
+Moreover, a power-law DTD with a long $t_D$ may be observationally hard to distinguish from a plateau model.
+In Figure \ref{fig:onezone-twopanel}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (dashed purple line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (solid green line), and their [O/Fe] DFs are virtually identical.
+The difference between the two values of $t_D$ for the exponential ($\tau=3$ Gyr) DTD in both the abundance tracks and distributions is nearly indistinguishable.
+We do not consider the effect on the other DTDs because a 150 Myr minimum delay time is incompatible with the two-population model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD due to its low SN Ia rate at short delay times.
+
+The right-hand panel of Figure \ref{fig:onezone-twopanel} compares the one-zone model outputs from the full range of DTDs we investigate in this work.
+As with the individual DTD parameters, the choice of DTD primarily affects the location of the high-$\alpha$ ``knee'' in the [Fe/H]--[O/Fe] abundance tracks.
+At one extreme is the triple-system model, which sees the CC SN plateau extend up to ${\rm [Fe/H]}\approx0.8$ followed by a sharp downward turn as the SN Ia rate suddenly increases at a delay time of 500 Myr.
+Star formation proceeds for such a long time before the knee that the [O/Fe] DF shows a slight second peak around the CC SN value; this model is the only one which produces any amount of bimodality in the one-zone models.
+At the other extreme are the two-population and power-law ($\alpha=-1.1$) models which peak immediately after the minimum delay time of 40 Myr, placing the knee at ${\rm [Fe/H]}\approx-1.8$.
+The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is a result of the delayed exponential component.
+The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models lie in the intermediate space between these extremes.
+On the other hand, the [O/Fe] DF from the exponential model has the strongest peak, while the plateau ($W=1$ Gyr) and triple-system models produce nearly identical distributions in the low-$\alpha$ regime.
+The power-law ($\alpha=-1.1$) and two-population DTDs produce similar [O/Fe] DFs despite notably different abundance tracks.
+The exponential ($\tau=3$ Gyr) and plateau ($W=0.3$ Gyr) models, while not shown, produce similar abundance tracks to the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models, respectively.
+
+% [Summary and conclusions from one-zone models]
+The results presented in this section indicate that the observables which should show the greatest effect from the choice of DTD are the [O/Fe]--[Fe/H] abundance tracks and the [O/Fe] DF.
+Degeneracies between models in one regime, such as the abundance tracks from the exponential ($\tau=3$ Gyr) and plateau ($W=1$ Gyr) DTDs, can be resolved in the other.
+Of course, both of these observables are also greatly affected by the parameters of the SFH.
+In this section we focused on the fiducial inside-out SFH; for a similar comparison of DTDs with a two-infall SFH, we direct the reader to \citet{Palicio2023-AnalyticDTD}.
+
+\section{Results from Multi-Zone Models}
+\label{sec:multizone-results}
 
@@
     \includegraphics[width=\linewidth]{figures/feh_df_comparison.pdf}
-    \caption{Distributions of [Fe/H] from multi-zone simulations with various models for the SFH and DTD.
+    \caption{Distributions of [Fe/H] from multi-zone models with various models for the SFH and DTD.
 Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}).
@@
 All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex.
-    \textit{Left columns:} comparison between the inside-out and two-infall SFH models. In both cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed. 
+    \textit{Left columns:} comparison between the inside-out and two-infall SFHs; both assume the exponential ($\tau=1.5$ Gyr) DTD. 
     \textit{Center column:} the distributions from APOGEE DR17 for reference, binned and smoothed similarly.
-    \textit{Right columns:} comparison between the power-law ($\alpha=-1.4$) and exponential ($\tau=3$ Gyr) DTD models. In both cases the inside-out SFH is assumed.}
+    \textit{Right columns:} comparison between the power-law ($\alpha=-1.4$) and exponential ($\tau=3$ Gyr) DTDs with the inside-out SFH.}
     \label{fig:feh-df-comparison}
@@
 Holding the SFH fixed, varying the DTD has a very minor effect on the MDF across the disk.
-The two right-hand columns of Figure \ref{fig:feh-df-comparison} plot the MDFs for two multi-zone simulations which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
+The two right-hand columns of Figure \ref{fig:feh-df-comparison} plot the MDFs for two multi-zone models which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
 The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of SNe Ia exploding within 1 Gyr in the former model but only $\sim 30\%$ in the latter.
@@
 Inner regions have a higher SFR and more stars are formed at early times than late, so differences in the SN Ia rate have a more pronounced effect on the MDF.
-For all SFH models except two-infall, the outer galaxy has a longer SFR timescale than the inner galaxy, so the MDF in the outer galaxy is relatively unaffected by the fraction of prompt SNe Ia.
+For all SFHs except two-infall, the outer galaxy has a longer SFR timescale than the inner galaxy, so the MDF in the outer galaxy is relatively unaffected by the fraction of prompt SNe Ia.
 
@@
     \includegraphics[width=\linewidth]{figures/ofe_df_sfh.pdf}
-    \caption{Distributions of [O/Fe] from multi-zone simulations with different SFHs.
-In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.
+    \caption{Distributions of [O/Fe] from multi-zone models with different SFHs.
+All assume the exponential ($\tau=1.5$ Gyr) DTD.
 The format of each panel is the same as in Figure \ref{fig:feh-df-comparison}, except that all distributions are smoothed with a box-car width of 0.05 dex.
@@
 Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs, all assuming an exponential DTD with $\tau=1.5$ Gyr, compared to the distributions measured by APOGEE.
-We see similar trends with Galactic region across all four simulations.
+We see similar trends with Galactic region across all four models.
 Near the midplane, the distributions at the innermost and outermost annuli are similar, but away from the midplane, there is a clear trend of a higher average stellar [O/Fe] at small $R_{\rm gal}$ and lower [O/Fe] at large $R_{\rm gal}$.
@@
 While trends with $R_{\rm gal}$ and $|z|$ are similar, the shape of the distribution varies greatly with the chosen SFH.
-The inside-out and late-burst models produce similar distributions because of the similarity of their underlying SFHs \textemdash both skew heavily toward near-Solar [O/Fe], although the late-burst model produces a slightly broader peak and a less-prominent high-[O/Fe] tail.
+The inside-out and late-burst models produce similar distributions because of the similarity of their underlying SFHs \textemdash both skew heavily toward near-solar [O/Fe], although the late-burst model produces a slightly broader peak and a less-prominent high-[O/Fe] tail.
 The only region which shows any significant skew toward high [O/Fe] is $R_{\rm gal}=3-5$ kpc and $|z|=1-2$ kpc, but the shift to higher [O/Fe] at high latitudes is gradual and does not produce the notable trough at ${\rm [O/Fe]}\approx0.2$ which is seen in the APOGEE data.
@@
 
-The two-infall SFH model produces \textit{three} distinct modes at ${\rm [O/Fe]}\approx 0.0$, $0.2$, and $0.4$.
+The two-infall SFH produces \textit{three} distinct modes at ${\rm [O/Fe]}\approx 0.0$, $0.2$, and $0.4$.
 At small $R_{\rm gal}$ and with increasing $|z|$, the low-$\alpha$ peak decreases in prominence and the high-$\alpha$ peak increases, but the intermediate peak is a striking feature at all latitudes which is at odds with the APOGEE data.
@@
     \includegraphics[width=\linewidth]{figures/ofe_df_dtd.pdf}
-    \caption{Distributions of [O/Fe] from multi-zone simulations with different DTDs. In all cases an early-burst SFH is assumed. The plot format is similar to Figure \ref{fig:ofe-df-sfh}.}
+    \caption{Distributions of [O/Fe] from multi-zone models with different DTDs. In all cases an early-burst SFH is assumed. The plot format is similar to Figure \ref{fig:ofe-df-sfh}.}
     \label{fig:ofe-df-dtd}
@@
 
-Figure \ref{fig:ofe-df-dtd} shows [O/Fe] distributions produced by simulations with the same SFH but a range of different DTDs.
-We choose the early-burst SFH because it produces distinct high- and low-$\alpha$ sequences, which makes the effect of the DTD on the former more apparent.
+Figure \ref{fig:ofe-df-dtd} shows [O/Fe] distributions produced by models with the same SFH but a range of different DTDs.
+We show the early-burst SFH because it produces distinct low- and high-$\alpha$ sequences.
 The most obvious effect of the DTD is to shift the mode of the high-$\alpha$ sequence.
-The two-population DTD, which has the most prompt SNe Ia of any model in this paper, places the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.2$ dex higher at ${\rm [O/Fe]}\approx0.4$.
-
-[Talk about scores]
+The two-population DTD, which has the most prompt SNe Ia, places the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.2$ dex higher at ${\rm [O/Fe]}\approx0.4$.
+In general, models fewer prompt SNe Ia also populate the high-$\alpha$ sequence with more stars, as the chemical evolution track spends more time in the high-$\alpha$ regime.
+The exception to this is the two-population DTD, which produces a very strong high-$\alpha$ peak at $|z|>0.5$ kpc, likely a result of its long exponential tail.
+
+% [Talk about scores]
+We again compute the KL divergence (Equation \ref{eq:kl-divergence}) to quantify the agreement between the [O/Fe] DFs of our models and APOGEE.
+We calculate a score for each model as described in Section \ref{sec:feh-df}.
+The best-scoring model uses the two-infall SFH with the plateau ($W=0.3$ Gyr) DTD, although both plateau and exponential DTDs as well as the triple-system DTD score well when combined with certain SFHs.
+The late-burst SFH in general produces [O/Fe] DFs which score poorly compared to other models.
 
@@
     \includegraphics[width=\linewidth]{figures/ofe_bimodality_summary.pdf}
-    \caption{The distributions of [O/Fe] along two slices of [Fe/H]: $-0.6\leq$[Fe/H]$<-0.4$ (blue dashed) and $-0.4\leq$[Fe/H]$<-0.2$ (red solid).
-\textit{Top row:} results from five multi-zone simulations which assume the late-bust SFH but different DTD models.
-\textit{Bottom row}: the first four panels compare the four SFH models, all assuming an exponential DTD with $\tau=1.5$ Gyr.
-The bottom-right panel (highlighted) plots data from APOGEE DR17 for reference.
+    \caption{The distributions of [O/Fe] along two different slices of [Fe/H]. 
+    % $-0.6\leq$[Fe/H]$<-0.4$ (blue dashed) and $-0.4\leq$[Fe/H]$<-0.2$ (red solid). 
     All panels contain stars within the Galactic region defined by $7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc.
 The $|z|$-distributions of the model stellar populations are re-sampled to match the vertical distribution of the APOGEE sample, and \num{20000} stellar populations are drawn from the adjusted distribution in each panel.
-The maximum of each distribution is normalized to 1 and the vertical scale is consistent across all panels.}
+The maximum of each distribution is normalized to 1 and the vertical scale is consistent across all panels.
+    \textit{Top row:} results from five multi-zone models which assume the late-bust SFH but different DTDs.
+\textit{Bottom row}: the first four panels compare the four SFHs, all assuming an exponential DTD with $\tau=1.5$ Gyr.
+The bottom-right panel (highlighted) plots data from APOGEE DR17 for reference.}
     \label{fig:ofe-bimodality}
@@
 A crucial feature of this bimodality which is not apparent in the previous figures is the coincidence of both sequences at the same [Fe/H].
-Figure \ref{fig:ofe-bimodality} compares the [O/Fe] distributions in the Solar annulus ($7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc) in two bins of [Fe/H] for select model outputs and APOGEE data.
+Figure \ref{fig:ofe-bimodality} compares the [O/Fe] distributions in the solar annulus ($7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc) in two bins of [Fe/H] for select model outputs and APOGEE data.
 The APOGEE distributions in the bottom-right panel (j) show that the high-$\alpha$ mode is more prominent at lower [Fe/H] and \vice versa, but the distributions in both bins are clearly bimodal.
@@
 
-The top row of panels (a--e) in Figure \ref{fig:ofe-bimodality} shows the [O/Fe] bimodality (or lack thereof) across five different DTD models, all of which assume the late-burst SFH.
+The top row of panels (a--e) in Figure \ref{fig:ofe-bimodality} shows the [O/Fe] bimodality (or lack thereof) across five different DTDs, all of which assume the late-burst SFH.
 To quantify the bimodality, we use the {\tt scipy}'s \citep{2020SciPy-NMeth} peak-finding algorithm with an arbitrary prominence threshold of 0.1.
-Five of the eight DTD models (four of the five shown, plus the exponential ($\tau=3$ Gyr) model) exceed this threshold, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
+Five of the eight DTDs (four of the five shown, plus the exponential ($\tau=3$ Gyr) model) exceed this threshold, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
 Panel (b) illustrates that the power-law ($\alpha=-1.1$) DTD produces a marginal high-$\alpha$ peak, although it doesn't meet the prominence threshold because it is too close to the low-$\alpha$ peak.
-In general, as was the case with the [O/Fe] distributions in Section \ref{sec:ofe-df}, DTD models with fewer prompt SNe Ia produce a high-$\alpha$ peak which is more prominent and at a higher [O/Fe].
+In general, as was the case with the [O/Fe] distributions in Section \ref{sec:ofe-df}, DTDs with fewer prompt SNe Ia produce a high-$\alpha$ peak which is more prominent and at a higher [O/Fe].
 One major discrepancy is that the APOGEE data show bimodality in both bins of [Fe/H], while the models run with the late-burst SFH only show a clear high-$\alpha$ peak at the low-metallicity ($-0.6<{\rm [Fe/H]}<-0.4$) bin.
@@
 
-Panels (f)--(i) in the bottom row of Figure \ref{fig:ofe-bimodality} illustrate the effect of the SFH model on the [O/Fe] bimodality with the exponential ($\tau=1.5$ Gyr) DTD.
-The inside-out SFH does not produce a bimodal distribution for any of our DTD models.
+Panels (f)--(i) in the bottom row of Figure \ref{fig:ofe-bimodality} illustrate the effect of the SFH on the [O/Fe] bimodality with the exponential ($\tau=1.5$ Gyr) DTD.
+The inside-out SFH does not produce a bimodal distribution for any of our DTDs.
 On the other hand, the early-burst SFH {\it always} produces a bimodal distribution in the $-0.4\leq{\rm [Fe/H]}<-0.2$ bin regardless of the assumed DTD, although the lower-metallicity bin does not (the lower peak falls short of our prominence threshold of 0.1).
@@
     \includegraphics{figures/ofe_feh_sfh.pdf}
-    \caption{A comparison of the [O/Fe]--[Fe/H] plane between the four SFH models in our multi-zone simulations.
-All assume an exponential DTD with $\tau=1.5$ Gyr.
-Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
+    \caption{A comparison of the [O/Fe]--[Fe/H] plane between the four SFHs in our multi-zone models.
+All assume the exponential ($\tau=1.5$ Gyr) DTD.
+Each panel plots a random mass-weighted sample of 10,000 star particles in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by $R_{\rm gal}$ at birth.
 A Gaussian scatter has been applied to all points based on the median abundance errors in APOGEE DR17 (see Table \ref{tab:uncertainties}).
@@
 [Subsection introduction]
-Section \ref{sec:onezone-results} and specifically Figures \ref{fig:onezone-threepanel} and \ref{fig:onezone-twopanel} illustrated the effect of the DTD models and parameters on [O/Fe]--[Fe/H] tracks in idealized one-zone models.
-
-Figure \ref{fig:ofe-feh-sfh} compares the [O/Fe]--[Fe/H] plane in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) between our four model SFHs.
-All simulations presented in this figure assume an exponential DTD model with $\tau=1.5$ Gyr, as it lies in the middle in terms of balance between prompt and delayed SNe Ia.
+Section \ref{sec:onezone-results} and specifically Figures \ref{fig:onezone-threepanel} and \ref{fig:onezone-twopanel} illustrated the effect of the DTDs and parameters on [O/Fe]--[Fe/H] tracks in idealized one-zone models.
+
+Figure \ref{fig:ofe-feh-sfh} compares the [O/Fe]--[Fe/H] plane in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) between our four model SFHs.
+All models presented in this figure assume an exponential DTD with $\tau=1.5$ Gyr, as it lies in the middle in terms of balance between prompt and delayed SNe Ia.
 The black curves represent the ISM abundance as a function of time in the central zone; in the absence of radial migration, all simulated stellar populations would lie along these lines.
@@
     \includegraphics[width=\linewidth]{figures/ofe_feh_dtd.pdf}
-    \caption{The [O/Fe]--[Fe/H] plane from multi-zone simulations with different DTD models.
+    \caption{The [O/Fe]--[Fe/H] plane from multi-zone models with different DTDs.
 All assume the inside-out SFH.
 Each panel is similar to those in Figure \ref{fig:ofe-feh-sfh}, except each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
-All panels present stars within the Solar annulus ($7\leq R_{\rm gal}<9$ kpc).}
+All panels contain stars within the solar annulus ($7\leq R_{\rm gal}<9$ kpc).}
     \label{fig:ofe-feh-dtd}
@@
 
-Figure \ref{fig:ofe-feh-dtd} compares [O/Fe]--[Fe/H] distributions for five simulations with the same SFH (inside-out) but different DTD models.
-We choose the inside-out SFH model for this figure because it produces a monotonically-decreasing abundance track, making comparisons between the different DTD models relatively straightforward.
+Figure \ref{fig:ofe-feh-dtd} compares [O/Fe]--[Fe/H] distributions for five models with the same SFH (inside-out) but different DTDs.
+We choose the inside-out SFH for this figure because it produces a monotonically-decreasing abundance track, making comparisons between the different DTDs relatively straightforward.
 We note that in this model, both the low- and high-$\alpha$ sequences are composed of stars with a wide range of birth $R_{\rm gal}$.
-The simulation results are arranged by increasing median delay time from left to right.
-Results for the two-population and power-law ($\alpha=-1.1$) DTD models, with a large fraction of prompt SNe Ia, are presented in the first and second columns, respectively.
+The model results are arranged by increasing median delay time from left to right.
+Results for the two-population and power-law ($\alpha=-1.1$) DTDs, with a large fraction of prompt SNe Ia, are presented in the first and second columns, respectively.
 For these models, the simulated stellar abundances are reasonably well-aligned with the APOGEE contours at low $|z|$ (bottom panels), but they entirely miss the observed high-$\alpha$ sequence at high $|z|$ (top panels).
 In the center column, the exponential ($\tau=1.5$ Gyr) DTD produces a distribution which aligns quite well with the APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to large [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
-While it does better at populating the high-$\alpha$ sequence than the previous DTD models, the bulk of the simulated populations at large $|z|$ still fall below the APOGEE 30\% contour (top panel).
-The two right-hand columns present simulation results for the plateau ($W=1$ Gyr) and triple-system DTD models, which have the longest median delay times.
+While it does better at populating the high-$\alpha$ sequence than the previous DTDs, the bulk of the simulated populations at large $|z|$ still fall below the APOGEE 30\% contour (top panel).
+The two right-hand columns present model results for the plateau ($W=1$ Gyr) and triple-system DTDs, which have the longest median delay times.
 The high-$\alpha$ ``knee'' occurs at a much higher metallicity in these models and is visible in the gas abundance tracks in the upper-left corner of the panels.
@@
 \citet{PerezCruz2008-KLTest2D} present a method for estimating the KL divergence between two continuous, multivariate samples using a $k$-nearest neighbor estimate.
-We implement this method to calculate the divergence between the multi-zone models and APOGEE data in [Fe/H]--[O/Fe] space.\footnote{We got the implementation from \url{https://mail.python.org/pipermail/scipy-user/2011-May/029521.html}.}
+We implement this method to calculate the divergence between the multi-zone models and APOGEE data in [Fe/H]--[O/Fe] space.
+% \footnote{We got the implementation from \url{https://mail.python.org/pipermail/scipy-user/2011-May/029521.html}.}
 
@@
     \caption{The [O/Fe]--[Fe/H] plane for multiple Galactocentric regions from the model with the inside-out SFH and plateau ($W=0.3$ Gyr) DTD.
-The two columns of panels contain stars in different bins of $R_{\rm gals}$, and each row contains stars from a different bin of $|z|$.
+The two columns of panels contain stars in different bins of $R_{\rm gal}$, and each row contains stars from a different bin of $|z|$.
 The contents of each panel is as described in Figure \ref{fig:ofe-feh-sfh}.}
@@
 
+The best-scoring model uses the two-infall SFH with the plateau ($W=0.3$ Gyr) DTD.
+Figure \ref{fig:ofe-feh-twoinfall} plots the stellar [O/Fe]--[Fe/H] abundances from this model in the inner and outer Galaxy.
+The model distributions in the outer Galaxy closely match the APOGEE distributions.
+Stellar populations at the high-[Fe/H] end of the distribution have migrated from inner regions.
+
 \subsection{The Age--[O/Fe] Plane}
@@
     \includegraphics{figures/age_ofe_sfh.pdf}
-    \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different SFH models.
-All assume an exponential DTD with $\tau=1.5$ Gyr.
-Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
+    \caption{A comparison of the age--[O/Fe] relation between multi-zone models with different SFHs.
+All assume the exponential ($\tau=1.5$ Gyr) DTD.
+Each panel plots a random mass-weighted sample of 10,000 star particles in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
 A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citetalias{Leung2023-Ages} (see Table \ref{tab:uncertainties}).
 Black squares represent the mass-weighted median age of star particles within bins of [O/Fe] with a width of 0.05 dex, and the horizontal black error bars encompass the 16th and 84th percentiles.
-Red triangles represent the median age from \citetalias{Leung2023-Ages} in bins of [O/Fe], and the horizontal red error bars encompass the 16th and 84th percentiles.
-For clarity, bins which contain less than 1\% of the total mass (in the simulations) or total number of stars (in the data) are not plotted.}
+Red triangles and horizontal error bars represent the median, 16th, and 84th percentiles of age from \citetalias{Leung2023-Ages}, respectively.
+For clarity, bins which contain less than 1\% of the total mass (in the models) or total number of stars (in the data) are not plotted.}
     \label{fig:age-ofe-sfh}
@@
 
-Figure \ref{fig:age-ofe-sfh} compares the stellar age and [O/Fe] distributions in the Solar neighborhood between our four SFH models.
-Similar to Figure \ref{fig:ofe-feh-sfh}, all four panels assume an exponential DTD model with $\tau=1.5$ Gyr.
+Figure \ref{fig:age-ofe-sfh} compares the stellar age and [O/Fe] distributions in the solar neighborhood between our four SFHs.
+Similar to Figure \ref{fig:ofe-feh-sfh}, all four panels assume an exponential DTD with $\tau=1.5$ Gyr.
 We include age data from \citetalias{Leung2023-Ages} for qualitative comparison, though we caution against drawing strong conclusions because we don't correct for selection effects or systematics in the neural net ages.
 The inside-out and late-burst models show fair agreement with the data at high [O/Fe], although both show a $\sim2$ Gyr offset to older ages.
-One could shift the ramp-up in star formation to slightly later times or simply run the simulation for a shorter amount of time to close this gap.
+One could shift the ramp-up in star formation to slightly later times or simply run the model for a shorter amount of time to close this gap.
 Like the data, the trend in the median age with decreasing [O/Fe] decreases monotonically in the inside-out model.
 The late-burst model, however, shows a bump in the distribution around a lookback time of $\sim2$ Gyr driven by the Gaussian SFR burst, which is not seen in the data, as noted by \citetalias{Johnson2021-Migration}.
-Neither model produces a significant amount of stars below Solar [O/Fe], in contrast to the data.
-
-For the early-burst SFH model, the simulated stellar ages are almost perfectly aligned with the data for ${\rm [O/Fe]}\gtrsim 0.2$.
+Neither model produces a significant amount of stars below solar [O/Fe], in contrast to the data.
+
+For the early-burst SFH, the simulated stellar ages are almost perfectly aligned with the data for ${\rm [O/Fe]}\gtrsim 0.2$.
 The rapid rise in the SFE at early times delays the descent to lower [O/Fe] values and produces a clump of low-metallicity, high-[O/Fe] stars at an age of $\sim10$ Gyr.
 The early-burst model produces a sharp transition between a linear relationship between [O/Fe] and age for stars older than $\sim5$ Gyr and a flat relationship for the younger stars, and it too misses the lowest [O/Fe] bin in the data.
-Finally, the two-infall SFH model produces the closest overall agreement between the simulated and observed median ages.
+Finally, the two-infall SFH produces the closest overall agreement between the simulated and observed median ages.
 Stars with ${\rm [O/Fe]}\gtrsim 0.25$ were produced in the first infall, while the second infall produces a clump of stars with similar metallicity, ages of $\sim8$ Gyr, and ${\rm [O/Fe]}\approx0.2$.
 There is an interesting small population of very old, low-$\alpha$ stars which is not seen in any of the other models.
-The two-infall model is the only one which plateaus at sub-Solar [O/Fe] for the youngest stars, leading to a very good match to the observed data at low [O/Fe].
+The two-infall model is the only one which plateaus at sub-solar [O/Fe] for the youngest stars, leading to a very good match to the observed data at low [O/Fe].
 
@@
     \includegraphics[width=\linewidth]{figures/age_ofe_dtd.pdf}
-    \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different DTD models.
+    \caption{A comparison of the age--[O/Fe] relation between multi-zone models with different DTDs.
 All assume the early-burst SFH.
 Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
-In all panels stars are limited to the Solar annulus ($7\leq R_{\rm gal}<9$ kpc), and the layout of each panel is as in Figure \ref{fig:age-ofe-sfh}.}
+In all panels stars are limited to the solar annulus ($7\leq R_{\rm gal}<9$ kpc), and the layout of each panel is as in Figure \ref{fig:age-ofe-sfh}.}
     \label{fig:age-ofe-dtd}
@@
 
-Figure \ref{fig:age-ofe-dtd} similarly plots the simulated distributions in age--[O/Fe] space for five of our DTD models.
-All simulations were run with the early-burst SFH model because the high-$\alpha$ sequence was distinct in metallicity space in Figure \ref{fig:age-ofe-sfh}.
-Similar to Figure \ref{fig:ofe-feh-dtd}, simulations are arranged from left to right by increasing median SN Ia delay time.
+Figure \ref{fig:age-ofe-dtd} similarly plots the simulated distributions in age--[O/Fe] space for five of our DTDs.
+All models were run with the early-burst SFH because the high-$\alpha$ sequence was distinct in metallicity space in Figure \ref{fig:age-ofe-sfh}.
+Similar to Figure \ref{fig:ofe-feh-dtd}, models are arranged from left to right by increasing median SN Ia delay time.
 Moving from left to right, the high-$\alpha$ sequence moves to higher [O/Fe] with increasing median delay time, from $\sim0.4$ for the two-population model to $\sim0.4$ for the triple-system DTD.
 As we have seen in previous figures, the range in [O/Fe] produced by the models on the left is much smaller than for the models on the right.
-At high $|z|$ (top row), the observed range of [O/Fe] is larger than produced by any of our simulations, although the plateau ($W=1$ Gyr) and triple-system models come close.
+At high $|z|$ (top row), the observed range of [O/Fe] is larger than produced by any of our models, although the plateau ($W=1$ Gyr) and triple-system models come close.
 While the other three fall short of the observed range in [O/Fe], they more closely match the median age--[O/Fe] relation.
-There is a slight reversal in the observed trend for the stars with the highest [O/Fe]: the $0.45\leq{\rm [O/Fe]}<0.5$ bin has a slightly \textit{lower} median age than the $0.3\leq{\rm [O/Fe]}<0.35$ bin at high $|z|$ in the \citetalias{Leung2023-Ages} sample, a small effect but one which is not observed in any of our simulation results.
+There is a slight reversal in the observed trend for the stars with the highest [O/Fe]: the $0.45\leq{\rm [O/Fe]}<0.5$ bin has a slightly \textit{lower} median age than the $0.3\leq{\rm [O/Fe]}<0.35$ bin at high $|z|$ in the \citetalias{Leung2023-Ages} sample, a small effect but one which is not observed in any of our model results.
 
@@
 The exponential ($\tau=1.5$ Gyr) DTD comes closest to reproducing the observed range in [O/Fe], while the two DTDs with the shortest median delay time once again produce a smaller range of [O/Fe] than observed.
-We note that the break between the linear and flat parts of the relation is sharpest for the exponential DTD, and a more gradual transition is observed for the other four DTD models.
+We note that the break between the linear and flat parts of the relation is sharpest for the exponential DTD, and a more gradual transition is observed for the other four DTDs.
 This could be because the exponential DTD is most dominant at intermediate delay times ($\tau\sim 1-3$ Gyr) but falls off much faster than the other models at long delay times, so the evolution of [O/Fe] is quite slow for lookback times $\lesssim 5$ Gyr.
@@
 
-The results presented in Section \ref{sec:multizone-results} represent a fraction of the 32 total multi-zone model outputs (four SFHs and eight DTDs) and focus on the even smaller fraction of outputs which lie in the Solar annulus.
-% While we focused our attention on results in the Solar annulus (for which we still have the best data), we have model outputs which span the entire disk out to 20 kpc.
+The results presented in Section \ref{sec:multizone-results} represent a fraction of the 32 total multi-zone model outputs (four SFHs and eight DTDs) and focus on the even smaller fraction of outputs which lie in the solar annulus.
+% While we focused our attention on results in the solar annulus (for which we still have the best data), we have model outputs which span the entire disk out to 20 kpc.
 In order to identify trends among our many models, it will be useful to have some semi-quantitative way to compare their outputs to APOGEE data across the disk.
@@
 To avoid drawing strong conclusions from small numerical differences in scores, 
-% Instead of reporting the numerical scores for each simulation output, 
-in the column corresponding to a particular diagnostic we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom tirtile out of all of our simulations, respectively.
+% Instead of reporting the numerical scores for each model output, 
+in the column corresponding to a particular diagnostic we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom tirtile out of all of our models, respectively.
 A \yes indicates that particular combination of model SFH and DTD performed better than most when compared to the APOGEE sample for that diagnostic.
@@
 The models which perform the best (most \yes's and fewest \no's) are those with the exponential and plateau DTDs.
-It is interesting that the best-performing model overall in our scoring system, the exponential DTD with $\tau=1.5$ Gyr, is intermediate among all our DTDs in terms of the number of prompt SNe Ia and median delay time, but has the {\it lowest} rate at very long delay times ($\sim10$ Gyr).
+It is interesting that the best-performing DTD overall in our scoring system, the exponential DTD with $\tau=1.5$ Gyr, is intermediate among all our DTDs in terms of the number of prompt SNe Ia and median delay time, but has the {\it lowest} rate at very long delay times ($\sim10$ Gyr).
 Models with a large fraction of prompt SNe Ia, such as the power-law and two-population DTDs, fare quite poorly, with the steepest power-law ($\alpha=-1.4$) ending up in the bottom tirtile across the board for most of our SFHs.
-
-[Discuss \citet{Palicio2024-CosmicSNIaRate}]
-
-Extra-galactic observations of the DTD are more sensitive to the late-time DTD; GCE comparisons with the high-alpha sequence are more sensitive to the early-time DTD. 
-[Later on, make suggestions]
-
-\subsection{The Two-Infall SFH Model}
-\label{sec:two-infall-discussion}
-
-Across every diagnostic in Table \ref{tab:results}, the two-infall models outperform every other SFH.
-
-[Why does two-infall do so well across the board, even in the [Fe/H] and [O/Fe] DFs where it seems worse by eye?]
-
-[Compare to previous studies]
-Discuss \citet{Matteucci2006-BimodalDTDConsequences} findings of the \citet{Mannucci2006-TwoPopulations} DTD in the two-infall model.
-
-[First exploration of two-infall with mass loading, radial migration. Further investigation coming in future paper.]
-
-\citet{Poulhazan2018-PrecisionPollution} found that DTD models with a significant prompt component (power-law and two-population) produced the highest average stellar abundance of [O/Fe].
+If we remove the two-infall models altogether due to their dominance in the scoring system, our results do not qualitatively change.
+
+% The best DTDs for each SFH
+The main takeaway from Table \ref{tab:results} is that while certain DTDs tend to score better than others, there is no single DTD which always produces optimal agreement with the data across all diagnostics.
+Depending on the choice of SFH, different DTDs will succeed at reproducing different observables.
+If an inside-out or late-burst SFH is chosen, the exponential DTDs with either timescale will produce optimal agreement with all observables.
+However, the picture gets less clear-cut when looking at the other SFHs.
+If the early-burst SFH is chosen, the DTDs with many prompt SNe Ia (power-law and two-population) produce the best agreement with the APOGEE [Fe/H] DFs but the {\it worst} agreement with the other observables.
+Finally, for the two-infall SFH, any DTD other than the power-law and two-population scores well, but the best-scoring DTD varies between diagnostics.
+In general, too many prompt SNe Ia worsens agreement with observations across all our SFHs, while too few prompt SNe Ia can also worsen agreement for some SFHs and observables.
+
+% [Discuss \citet{Palicio2024-CosmicSNIaRate}]
+\citet{Palicio2024-CosmicSNIaRate} predict the cosmic SN Ia rate from a variety of DTDs and cosmic star formation rates (CSFRs) and fit to observations.
+They find that, depending on the choice of CSFR, the DTDs of \citet{MatteucciRecchi2001-SNIaTimescale}, \citet{Mannucci2006-TwoPopulations}, \citet{Totani2008-DTD}, and the WIDE DD model of \citet{Greggio2005-AnalyticalRates} can all produce good fits to the observed cosmic SN Ia rate.
+This study provides a useful basis for comparison because the first and last of these DTDs are similar to our exponential ($\tau=1.5$ Gyr) and plateau ($W=1$ Gyr) DTDs, respectively (see Appendix \ref{app:analytical-dtds} for more discussion); the \citet{Mannucci2006-TwoPopulations} is our two-population DTD; and the \citet{Totani2008-DTD} is a $t^{-1}$ power-law with a minimum delay $t_D=100$ Myr.
+It is noteworthy that the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale} best fits the majority of CSFRs in \citet{Palicio2024-CosmicSNIaRate}, and our similar exponential ($\tau=1.5$ Gyr) DTD {\it also} performs best across all our SFHs.
+
+\citet{Poulhazan2018-PrecisionPollution} found that DTDs with a significant prompt component (power-law and two-population) produced the highest average stellar abundance of [O/Fe].
 They also found that these models produced the narrowest [O/Fe] distributions and suppressed the long tail to low [O/Fe] ratios.
@@
 
+Across most of the observables, the power-law ($\alpha=-1.1$) DTD, which has the strongest motivation from extra-galactic observations, poorly reproduces the observed Galactic chemical abundance distributions.
+This can be mitigated somewhat with a longer minimum delay time, which we show in Section \ref{sec:onezone-results} has a similar effect on chemical evolution tracks as the plateau DTD.
+Even so, it is clear that the high fraction of prompt SNe Ia in the DTD of, e.g., \citet{Maoz2017-CosmicDTD} is at odds with Galactic chemical abundance measurements.
+Measurements of the cosmic SN Ia rate become much more uncertain above $z\approx1$, and it is difficult to constrain the SFH of individual galaxies below [number] [cite], so constraints on the DTD from external galaxies should be more sensitive to the rates at long delay times.
+On the other hand, our results demonstrate that the high-$\alpha$ sequence in GCE models is highly sensitive to the DTD at short delay times.
+
+[Metallicity dependent DTD] \citet{Gandhi2022-MetallicityDependentRates,Johnson2023-Binaries}
+
+[Is the MW DTD the same as elsewhere?]
+\citet{Walcher2016-SelfSimilarity} argue that the similarity of the age--[$\alpha$/Fe] relation between solar neighborhood stars and nearby elliptical galaxies is evidence for a universal DTD; between a bimodal, narrow Gaussian, and power-law DTD, they find the latter best explains their data.
+
+\subsection{The Two-Infall SFH}
+\label{sec:two-infall-discussion}
+
+[Why does two-infall do so well across the board, even in the [Fe/H] and [O/Fe] DFs where it seems worse by eye?]
+Across every diagnostic in Table \ref{tab:results}, the two-infall models outperform every other SFH.
+It is somewhat surprising that the two-infall models score higher than the early-burst even for the [O/Fe] DFs, when the double-peaked distributions produced by the latter are qualitatively closer to the APOGEE data than the former's triple-peaked distributions.
+This is because the KL divergence test heavily penalizes models with a high density in a region where the observations have little, as is the case for the high-$\alpha$ sequence in the outer Galaxy and close to the midplane.
+
+[Compare to previous studies]
+Discuss \citet{Matteucci2006-BimodalDTDConsequences} findings of the \citet{Mannucci2006-TwoPopulations} DTD in the two-infall model.
+
 \citet{Palicio2023-AnalyticDTD} compare seven different DTDs, including the analytical SD, DD-WIDE, and DD-CLOSE, as well as the empirical two-population and $t^{-1}$ power-law DTDs, in a one-zone model with a two-infall SFH.
 [Note that they use some different parameters for the analytical models than we do).
-Critically for our purposes, and in contrast to previous studies of the two-infall model \citep[e.g.,][others]{Chiappini1997-TwoInfall,Spitoni2021-TwoInfall}, the authors include the effects of outflows, although they explore mass-loading values of $\eta=0.2-0.8$ which is significantly lower than in our simulations.
-
-[Metallicity dependent DTD]
-
-[Is the MW DTD the same as elsewhere?]
-\citet{Walcher2016-SelfSimilarity} argue that the similarity of the age--[$\alpha$/Fe] relation between Solar neighborhood stars and nearby elliptical galaxies is evidence for a universal DTD; between a bimodal, narrow Gaussian, and power-law DTD, they find the latter best explains their data.
+Critically for our purposes, and in contrast to previous studies of the two-infall model \citep[e.g.,][others]{Chiappini1997-TwoInfall,Spitoni2021-TwoInfall}, the authors include the effects of outflows, although they explore mass-loading values of $\eta=0.2-0.8$ which is significantly lower than in our models.
+
+[First exploration of two-infall with mass loading, radial migration. Further investigation coming in future paper.]
 
@@
 
-One curious chemical feature of the Milky Way disk is the existence of two populations separated by their \aFe abundance ratios at similar metallicity \citep[e.g.,][]{Bensby2014-SolarNeighborhoodAbundances}.
+One curious chemical feature of the Milky Way disk is the existence of two populations separated by their \aFe abundance ratios at similar metallicity \citep[e.g.,][]{Bensby2014-solarNeighborhoodAbundances}.
 
 % Taken from introduction
-The bimodal distribution of \aFe in stars with similar metallicities was first noted in the Solar neighborhood \citep[e.g.,][]{Furhmann1998-NearbyStars}, later extended to the whole of the Milky Way disk \citep{Nidever2014-ChemicalEvolutionAPOGEE,Hayden2015-ChemicalCartography}.
+The bimodal distribution of \aFe in stars with similar metallicities was first noted in the solar neighborhood \citep[e.g.,][]{Furhmann1998-NearbyStars}, later extended to the whole of the Milky Way disk \citep{Nidever2014-ChemicalEvolutionAPOGEE,Hayden2015-ChemicalCartography}.
 The ``high-$\alpha$'' population contains stars with low enrichment from SNe Ia, so their abundance ratios reflect that of almost pure CCSN enrichment; it is associated with the kinematically hot thick disk \citep{Bensby2003-AbundanceTrends}.
@@
 
-We need to constrain DTD or galactic SFH better. With SDSS-V, the latter seems much more achievable.
-
 \section{Conclusions}
@@
 
-    \item The early-burst SFH model is the only one which produced a bimodal distribution of [O/Fe] across the disk resembling APOGEE, from the models we investigate.
+    \item The early-burst SFH is the only one which produced a bimodal distribution of [O/Fe] across the disk resembling APOGEE, from the models we investigate.
 [Add: summary of why everything else fails.]
@@
 
+We need to constrain DTD or galactic SFH better. With SDSS-V, the latter seems much more achievable.
+
 \begin{acknowledgments}
+    LOD thanks Dr. David Weinberg and attendees of OSU's Galaxy Hour for many useful discussions over the course of this project.
     [Personal acknowledgements]
@@
     University of Utah. The SDSS 
-    website is www.sdss4.org.
+    website is \url{www.sdss4.org}.
 
@@
     [Ohio State \& Carnegie land acknowledgements]
+    % From the Center for Belonging and Social Change, https://cbsc.osu.edu/about-us/land-acknowledgement
+    We would like to acknowledge the land that The Ohio State University occupies is the ancestral and contemporary territory of the Shawnee, Potawatomi, Delaware, Miami, Peoria, Seneca, Wyandotte, Ojibwe and many other Indigenous peoples.
+Specifically, the university resides on land ceded in the 1795 Treaty of Greeneville and the forced removal of tribes through the Indian Removal Act of 1830.
+As a land grant institution, we want to honor the resiliency of these tribal nations and recognize the historical contexts that has and continues to affect the Indigenous peoples of this land.
 
     [David and Jennifer NSF grant]
-
+    % Software acknowledgements if not a AAS journal
     % This work made use of Astropy:\footnote{http://www.astropy.org} a community-developed core Python package and an ecosystem of tools and resources for astronomy \citep{astropy:2013, astropy:2018, astropy:2022}.
@@
 For clarity, we vary the mass-loading factor to be $\eta=4$, $\eta=2$, and $\eta=1$ for the red, green, and blue curves, respectively.
-All simulation parameters between the similarly-colored solid and dashed curves are identical.}
+All model parameters between the similarly-colored solid and dashed curves are identical.}
     \label{fig:analytical-dtd}
@@
 We fit a sech$^2$ function \citep{Spitzer1942} to the distribution of midplane distances $z$.
-Vertical migration away from the midplane does not affect the chemical evolution simulation, but we do use $z$ in our analysis.
+Vertical migration away from the midplane does not affect the chemical evolution model, but we do use $z$ in our analysis.
 The probability density function (PDF) of $z$ given some scale height $h_z$ is
@@
     \caption{The distribution of final radius $R_{\rm final}$ as a function of formation radius $R_{\rm form}$ and age for the h277 analogue (top row) and Gaussian sampling scheme (bottom row).
-From left to right, star particles are binned by formation annulus, from the inner disk (far left column) to the Solar annulus (center column) to the outer disk (far right column).
+From left to right, star particles are binned by formation annulus, from the inner disk (far left column) to the solar annulus (center column) to the outer disk (far right column).
 Within each panel, colored curves represent the different age bins, ranging from the youngest stars (dark blue) to the oldest (dark red).

### 2024-03-18 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         \dot M_r    & continuous    & \ref{sec:multizone-methods} & Recycling rate \citep[][Equation 2]{JohnsonWeinberg2020-Starbursts} \\
+        \hline
         % DTD
@@
         N_{\rm Ia}/M_*  & $2.2\times10^{-3}$ M$_\odot^{-1}$ & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \citep{MaozMannucci2012-SNeIaReview} \\
+        \hline
         % Nucleosynthetic yields
@@
         y_{\rm Fe}^{\rm Ia} & 0.00214   & \ref{sec:yields}  & SN Ia yield of Fe \\
+        \hline
         % Star formation histories
@@
 %     \caption{Median parameter uncertainties}
-%     \label{tab:uncertainties}
+%     \label{tab:sample}
 %     \begin{tabular}{ccc}
@@
 Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row.
-All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex.
+All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:sample}) and smoothed with a box-car width of 0.2 dex.
     \textit{Left columns:} comparison between the inside-out and two-infall SFHs; both assume the exponential ($\tau=1.5$ Gyr) DTD. 
@@
 In this case, $P$ is the APOGEE DF, $Q$ is the model DF, and $x={\rm [Fe/H]}$.
-We bin the distributions with a width of 0.01 dex and apply observational uncertainties to our modeled DFs according to Table \ref{tab:uncertainties}.
+We bin the distributions with a width of 0.01 dex and apply observational uncertainties to our modeled DFs according to Table \ref{tab:sample}.
 For each model SFH and DTD, we compute $D_{\rm{KL}}$ in the 18 different Galactocentric regions shown in Figure \ref{fig:feh-df-comparison}: bins in $R_{\rm gal}$ with a width of 2 kpc between 3 and 15 kpc, and bins in $|z|$ of $0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
@@
 Each panel plots a random mass-weighted sample of 10,000 star particles in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by $R_{\rm gal}$ at birth.
-A Gaussian scatter has been applied to all points based on the median abundance errors in APOGEE DR17 (see Table \ref{tab:uncertainties}).
+A Gaussian scatter has been applied to all points based on the median abundance errors in APOGEE DR17 (see Table \ref{tab:sample}).
 The black curves represent the ISM abundance tracks in the 8 kpc zone.
@@
 Each panel plots a random mass-weighted sample of 10,000 star particles in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
-A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citetalias{Leung2023-Ages} (see Table \ref{tab:uncertainties}).
+A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citetalias{Leung2023-Ages} (see Table \ref{tab:sample}).
 Black squares represent the mass-weighted median age of star particles within bins of [O/Fe] with a width of 0.05 dex, and the horizontal black error bars encompass the 16th and 84th percentiles.
@@
 
-The best, lowest-scoring model in the age--[O/Fe] plane
+% The best, lowest-scoring model in the age--[O/Fe] plane
 
@@
 \variable{output/summary_table.tex}
+\vspace{-24pt}
 
@@
 \begin{acknowledgments}
-    LOD thanks Dr. David Weinberg and attendees of OSU's Galaxy Hour for many useful discussions over the course of this project.
+    LOD thanks Dr.\ David Weinberg and attendees of OSU's Galaxy Hour for many useful discussions over the course of this project.
     [Personal acknowledgements]
@@
     Survey IV has been provided by the 
-    Alfred P. Sloan Foundation, the U.S. 
+    Alfred P.\ Sloan Foundation, the U.S.\ 
     Department of Energy Office of 

### 2024-03-19 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \begin{equation}
-    \dot M_x^{\rm CC} = y_x^{\rm CC} \dot M_*
+    \dot M_x^{\rm CC} = y_x^{\rm CC} \dot M_\star
     \label{eq:ccsn-enrichment}
 \end{equation}
-where $y_x^{\rm CC}$ is the CCSN yield of element $x$ per unit mass of star formation, and $\dot M_*$ is the SFR. 
+where $y_x^{\rm CC}$ is the CCSN yield of element $x$ per unit mass of star formation, and $\dot M_\star$ is the SFR. 
 Following \citetalias{Johnson2021-Migration}, who in turn adopt their CCSN yields from \citet{ChieffiLimongi2004-CCSNYields} and \citet{LimongiChieffi2006-CCSNYields}, we adopt $y_{\rm O}^{\rm CC}=0.015$ and $y_{\rm Fe}^{\rm CC}=0.0012$.
@@
 \begin{equation}
-    \dot M_{\rm Fe}^{\rm Ia} = y_{\rm Fe}^{\rm Ia} \langle \dot M_*\rangle_{\rm Ia} \\
-\end{equation}
-where $\langle \dot M_*\rangle_{\rm Ia}$ is the time-averaged SFR weighted by the DTD and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia.
+    \dot M_{\rm Fe}^{\rm Ia} = y_{\rm Fe}^{\rm Ia} \langle \dot M_\star\rangle_{\rm Ia} \\
+\end{equation}
+where $\langle \dot M_\star\rangle_{\rm Ia}$ is the time-averaged SFR weighted by the DTD and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia.
 \citet{Weinberg2017-ChemicalEquilibrium} show in their Appendix A that
 \begin{equation}
-    \langle \dot M_*\rangle_{\rm Ia} \equiv \frac{\int_0^t \dot M_*(t')R_{\rm Ia}(t-t')dt'}{\int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt'}
+    \langle \dot M_\star\rangle_{\rm Ia} \equiv \frac{\int_0^t \dot M_\star(t')R_{\rm Ia}(t-t')dt'}{\int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt'}
     \label{eq:weighted-sfr}
 \end{equation}
-where %$\dot M_*(t)$ is the SFR at time $t$, 
+where %$\dot M_\star(t)$ is the SFR at time $t$, 
 %$R_{\rm Ia}(t) dt$ is the number of SNe Ia which explode in the time interval $(t, t+dt)$ per unit mass of stars formed at $t=0$, 
@@
 $t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the maximum simulation time.
-The denominator of Equation \ref{eq:weighted-sfr} is therefore the total number of SNe Ia per M$_{\odot}$ of stars formed $N_{\rm Ia}/M_*$.
+The denominator of Equation \ref{eq:weighted-sfr} is therefore the total number of SNe Ia per M$_{\odot}$ of stars formed $N_{\rm Ia}/M_\star$.
 
@@
 \begin{equation}
-    y_{\rm Fe}^{\rm Ia} = m_{\rm Fe}^{\rm Ia} \int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt' = m_{\rm Fe}^{\rm Ia} \frac{N_{\rm Ia}}{M_*},
+    y_{\rm Fe}^{\rm Ia} = m_{\rm Fe}^{\rm Ia} \int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt' = m_{\rm Fe}^{\rm Ia} \frac{N_{\rm Ia}}{M_\star},
     \label{eq:dtd-integral}
 \end{equation}
-where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia, and $N_{\rm Ia}/M_*=2.2\pm1\times10^{-3}\,{\rm M}_\odot^{-1}$ is the average number of SNe Ia per mass of stars formed \citep{MaozMannucci2012-SNeIaReview}.
+where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia, and $N_{\rm Ia}/M_\star=2.2\pm1\times10^{-3}\,{\rm M}_\odot^{-1}$ is the average number of SNe Ia per mass of stars formed \citep{MaozMannucci2012-SNeIaReview}.
 Adjusting the value of $y_{\rm Fe}^{\rm Ia}$ primarily affects the end point of chemical evolution tracks in [O/Fe]--[Fe/H] space. 
@@
     \begin{cases}
-        \frac{N_{\rm Ia}}{M_*}
+        \frac{N_{\rm Ia}}{M_\star}
         \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
@@
 % The first two models are taken from \citetalias{Johnson2021-Migration} and 
-are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_*$ is prescribed along with the star formation efficiency (SFE) timescale $\uptau_*\equiv \Sigma_g/\dot\Sigma_*$.
+are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_\star$ is prescribed along with the star formation efficiency (SFE) timescale $\uptau_\star\equiv \Sigma_g/\dot\Sigma_\star$.
 The remaining quantities, infall rate (IFR) surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
-The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\uptau_*$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in SFR mode).
+The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\uptau_\star$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in SFR mode).
 The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified.
@@
     \includegraphics[width=\linewidth]{figures/star_formation_histories.pdf}
-    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\uptau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
+    \caption{The surface densities of star formation $\dot \Sigma_\star$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\uptau_\star$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
 In each panel, we plot curves for the model zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
@@
 where $\tau_{\rm sfh}$ is the same as in the inside-out case.
-To calculate $\dot \Sigma_*$ from the above quantities, we modify the fiducial star formation law adopted from \citetalias{Johnson2021-Migration}, substituting $\uptau_{\rm EB}$ for the SFE timescale of molecular gas:
-\begin{equation}
-    \dot \Sigma_* = 
+To calculate $\dot \Sigma_\star$ from the above quantities, we modify the fiducial star formation law adopted from \citetalias{Johnson2021-Migration}, substituting $\uptau_{\rm EB}$ for the SFE timescale of molecular gas:
+\begin{equation}
+    \dot \Sigma_\star = 
     \begin{cases}
@@
         t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
-        N_{\rm Ia}/M_*  & $2.2\times10^{-3}$ M$_\odot^{-1}$ & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \citep{MaozMannucci2012-SNeIaReview} \\
+        N_{\rm Ia}/M_\star  & $2.2\times10^{-3}$ M$_\odot^{-1}$ & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \citep{MaozMannucci2012-SNeIaReview} \\
         \hline
@@
         % One-zone parameters
-        \uptau_*                        & 2 Gyr & \ref{sec:onezone-results} & SFE timescale in one-zone models \\
+        \uptau_\star                    & 2 Gyr & \ref{sec:onezone-results} & SFE timescale in one-zone models \\
         \eta(R_{\rm gal}=8\,{\rm kpc})  & 2.15  & \ref{sec:onezone-results} & Outflow mass-loading factor at the solar annulus \\
@@
 
-We make use of the multi-zone GCE model tools in \vice developed by \citetalias{Johnson2021-Migration}.
-The basic setup of our models follows theirs: the model Galaxy is a disk with a radius of 20 kpc and is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
-The gas in each ring is assumed to be instantaneously mixed; while star particles are allowed to migrate radially (see Appendix \ref{app:migration}), there is no exchange of gas between rings.
+We use the multi-zone GCE model tools in \vice developed by \citetalias{Johnson2021-Migration}.
+The basic setup of our models follows theirs.
+The disk is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
+Stellar populations migrate radially under the prescription we describe in Appendix \ref{app:migration}, but each ring is otherwise described by a conventional one-zone GCE model with instantaneous mixing (see discussion in Section \ref{sec:onezone-results}).
+Following \citetalias{Johnson2021-Migration}, we do not implement radial gas flows \citep[e.g.,][]{LaceyFall1985-RadialGasFlows,BilitewskiSchonrich2012-RadialFlows}.
+
 We run our models with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
-Following \citetalias{Johnson2021-Migration}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_*=0$ for $R_{\rm gal}>R_{\rm SF}$ (stars are allowed to migrate past $R_{\rm SF}$, they are just not born there).
+Following \citetalias{Johnson2021-Migration}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_\star=0$ for $R_{\rm gal}>R_{\rm SF}$.
+The model has a full radial extent of 20 kpc, allowing a purely migrated population to arise in the outer 4.5 kpc.
 We adopt continuous recycling, which accounts for the time-dependent return of mass from all previous generations of stars \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
@@
 
-\section{Results from One-Zone Models}
+\section{One-Zone Models}
 \label{sec:onezone-results}
@@
 %         % $\eta$            & 2.15      & Outflow mass-loading factor \\
-%         % $\uptau_*$        & 2.0 Gyr   & SFE timescale \\
+%         % $\uptau_\star$        & 2.0 Gyr   & SFE timescale \\
 %         $\dot M_r$        & continuous    & Recycling rate \\
@@
 %         % $M_{g,0}$         & 0         & Initial gas mass \\
-%         % $\dot M_*(t)$     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
+%         % $\dot M_\star(t)$     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
 %         % $\tau_{\rm rise}$ & 2.0 Gyr     & SFR rise timescale \\
@@
 % [Intro paragraph, motivation for running one-zone models]
-Before running the full multi-zone models, it is useful to observe the effects of the DTD in more idealized conditions.
+Before running the full multi-zone models, it is useful to understand the effects of the DTD in more idealized conditions.
 A one-zone model assumes the entire gas reservoir is instantaneously mixed, removing all spatial dependence.
-This limits the ability to compare to observations across the disk, but it allows the models to be run in a fraction of the time and eliminates the complicating factor of stellar migration.
+This limits the ability to compare to observations across the disk, but it eliminates the complicating factor of stellar migration and better isolates the effects of the nucleosynthesis prescription.
 In this section, we compare the results from one-zone models which examine various parameters of the DTD while keeping other parameters fixed.
@@
 For consistency, we adopt most of the parameter values from Table \ref{tab:multizone-parameters} for our one-zone models.
-We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr) and an SFE timescale $\uptau_*\equiv M_g/\dot M_*=2$ Gyr.
-Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time $t_D=40$ Myr.
+We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr) and an SFE timescale $\uptau_\star\equiv M_g/\dot M_\star=2$ Gyr.
+Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_\star=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time $t_D=40$ Myr.
 % A summary of these fiducial parameters is presented in Table \ref{tab:onezone-parameters}.
@@
 In all cases the [O/Fe] DF is distinctly unimodal.
-The [Fe/H] DF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
+The MDF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
 
@@
 The effect on the [O/Fe] DF is similar to the power-law slope: a short timescale produces more low-$\alpha$ stars, while a long timescale produces more high-$\alpha$ stars (but still a unimodal distribution).
-The effect on the [Fe/H] DF is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values.
+The effect on the MDF is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values.
 A doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
@@
 
-Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of the plateau DTD width on abundance tracks and distributions.
+Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of varying the width of the plateau DTD on abundance tracks and distributions.
 The effect on the [O/Fe] DF is similar to the previous two models: a longer plateau raises the median delay time, resulting in a smaller low-$\alpha$ peak and a more prominent high-$\alpha$ tail.
@@
 As with the individual DTD parameters, the choice of DTD primarily affects the location of the high-$\alpha$ ``knee'' in the [Fe/H]--[O/Fe] abundance tracks.
-At one extreme is the triple-system model, which sees the CC SN plateau extend up to ${\rm [Fe/H]}\approx0.8$ followed by a sharp downward turn as the SN Ia rate suddenly increases at a delay time of 500 Myr.
-Star formation proceeds for such a long time before the knee that the [O/Fe] DF shows a slight second peak around the CC SN value; this model is the only one which produces any amount of bimodality in the one-zone models.
+At one extreme is the triple-system model, which sees the CC SN plateau extend up to ${\rm [Fe/H]}\approx-0.8$ followed by a sharp downward turn as the SN Ia rate suddenly increases at a delay time of 500 Myr.
+Star formation proceeds for such a long time before the knee that the [O/Fe] DF shows a slight second peak around the CC SN yield ratio.
+Out of all our one-zone models, this small bump is the only degree of bimodality in the [O/Fe] DF that arises.
+
 At the other extreme are the two-population and power-law ($\alpha=-1.1$) models which peak immediately after the minimum delay time of 40 Myr, placing the knee at ${\rm [Fe/H]}\approx-1.8$.
 The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is a result of the delayed exponential component.
-The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models lie in the intermediate space between these extremes.
+The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models occupy the intermediate space between these extremes.
 On the other hand, the [O/Fe] DF from the exponential model has the strongest peak, while the plateau ($W=1$ Gyr) and triple-system models produce nearly identical distributions in the low-$\alpha$ regime.
@@
 % [Summary and conclusions from one-zone models]
-The results presented in this section indicate that the observables which should show the greatest effect from the choice of DTD are the [O/Fe]--[Fe/H] abundance tracks and the [O/Fe] DF.
-Degeneracies between models in one regime, such as the abundance tracks from the exponential ($\tau=3$ Gyr) and plateau ($W=1$ Gyr) DTDs, can be resolved in the other.
+The results presented in this section indicate that the observables most sensitive to the choice of DTD are the [O/Fe]--[Fe/H] abundance tracks and the [O/Fe] DF.
+Degeneracies between models in one regime can be resolved in the other.
+For example, the exponential ($\tau=3$ Gyr) and plateau ($W=1$ Gyr) DTDs are indistinguishable in [O/Fe]--[Fe/H] space but predict different [O/Fe] DFs.
 Of course, both of these observables are also greatly affected by the parameters of the SFH.
@@
 
-\section{Results from Multi-Zone Models}
+\section{Multi-Zone Models}
 \label{sec:multizone-results}
@@
 
-Holding the SFH fixed, varying the DTD has a very minor effect on the MDF across the disk.
-The two right-hand columns of Figure \ref{fig:feh-df-comparison} plot the MDFs for two multi-zone models which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
-The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of SNe Ia exploding within 1 Gyr in the former model but only $\sim 30\%$ in the latter.
-Nevertheless, while the former DTD produces a slightly narrower MDF in the inner Galaxy than the latter, the magnitude of this difference is much smaller than other factors.
-
-The choice of DTD and SFH has a larger effect on the inner regions of the galaxy than the outer.
+Holding the SFH fixed, varying the DTD has minimal influence on these MDFs for fixed SFH.
+The two right-hand columns of Figure \ref{fig:feh-df-comparison} plot the MDFs for two multi-zone models, which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
+The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of explosions occurring within 1 Gyr in the former but only $\sim 30\%$ in the latter.
+% Nevertheless, while the former DTD produces a slightly narrower MDF in the inner Galaxy than the latter, the magnitude of this difference is much smaller than other factors.
+However, the effect on the MDF is interestingly small given this difference. The steep power-law leads to an MDF at small radii that is only slightly narrower than the extended exponential.
+
+% The choice of DTD and SFH has a larger effect on the inner regions of the Galaxy than the outer.
 Inner regions have a higher SFR and more stars are formed at early times than late, so differences in the SN Ia rate have a more pronounced effect on the MDF.
-For all SFHs except two-infall, the outer galaxy has a longer SFR timescale than the inner galaxy, so the MDF in the outer galaxy is relatively unaffected by the fraction of prompt SNe Ia.
-
-While there are some quantitative differences in how the shape of the MDF varies with Galactic region, the qualitative trends are unaffected by the choice of model SFH or DTD.
+For all SFHs except two-infall, the outer Galaxy has a longer SFR timescale than the inner Galaxy, so the MDF in the outer Galaxy is relatively unaffected by the fraction of prompt SNe Ia.
+The inner Galaxy is more sensitive to the choice of DTD than the outer Galaxy.
+The SFH peaks earlier and declines more sharply due to the inside-out formation of the disk.
+Consequently, SNe Ia often explode when the gas supply is significantly lower than when the progenitors formed.
+This so-called ``gas-starved ISM'' effect drives a faster increase in metallicity \citep[see analytic demonstration in][]{Weinberg2017-ChemicalEquilibrium}, which ultimately lowers the number of low-metallicity stars.
+The more extended the DTD< the stronger the effect.
+The outer disk is less affected by the choice of DTD, though, due to the more extended SFH.
+
+While there are some {\it quantitative} differences in how the shape of the MDF varies with Galactic region, the {\it qualitative} trends are unaffected by the choice of model SFH or DTD.
 These trends are primarily driven by chemical equilibrium, abundance gradients, and radial migration \citepalias[][see their Section 3.2 for further discussion]{Johnson2021-Migration}.
 
-To quantify the agreement between the [Fe/H] DFs generated by \vice and those observed in APOGEE, we compute the Kullback-Leibler (KL) divergence \citep{KullbackLeibler1951}, defined as
-\begin{equation}
-    D_{\rm{KL}}(P \parallel Q) \equiv \int_{-\infty}^{\infty} p(x) \log\Big(\frac{p(x)}{q(x)}\Big) dx
+To quantify the agreement between the MDFs generated by \vice and those observed in APOGEE, we compute the Kullback-Leibler (KL) divergence \citep{KullbackLeibler1951}, defined as
+\begin{equation}
+    D_{\rm{KL}}(P,Q) \equiv \int_{-\infty}^{\infty} p(x) \log\Big(\frac{p(x)}{q(x)}\Big) dx
     \label{eq:kl-divergence}
@@
 If $D_{\rm KL}=0$, the two distributions contain equal information.
-In this case, $P$ is the APOGEE DF, $Q$ is the model DF, and $x={\rm [Fe/H]}$.
-We bin the distributions with a width of 0.01 dex and apply observational uncertainties to our modeled DFs according to Table \ref{tab:sample}.
-For each model SFH and DTD, we compute $D_{\rm{KL}}$ in the 18 different Galactocentric regions shown in Figure \ref{fig:feh-df-comparison}: bins in $R_{\rm gal}$ with a width of 2 kpc between 3 and 15 kpc, and bins in $|z|$ of $0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
-The score $S$ for the entire model is taken to be the average of $D_{\rm{KL}}$ for each region $R$ weighted by the number of APOGEE stars in that region $N_{*,R}$:
-\begin{equation}
-    S = \frac{\sum_R D_{{\rm KL},R} N_{*,R}}{\sum_R N_{*,R}}.
+In this case, $P$ is the APOGEE MDF, $Q$ is the model MDF, and $x={\rm [Fe/H]}$.
+We bin the distributions with a width of 0.01 dex and apply observational uncertainties to our modeled MDFs according to Table \ref{tab:sample}.
+For each SFH and DTD, we compute $D_{\rm{KL}}$ in the 18 different Galactocentric regions shown in Figure \ref{fig:feh-df-comparison}.
+We use bins in $R_{\rm gal}$ with a width of 2 kpc between 3 and 15 kpc, and bins in midplane distance of $|z|=0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
+The score $S$ for the entire model is taken to be the average of $D_{\rm{KL}}$ for each region $R$ weighted by the number of APOGEE stars in that region $N_{\star,R}$:
+\begin{equation}
+    S = \frac{\sum_R D_{\rm KL}(P,Q|R) N_\star(R)}{\sum_R N_\star(R)}.
     \label{eq:feh-df-score}
@@
 
-The model combination with the best (lowest) score for the [Fe/H] DF is the two-infall SFH with the exponential ($\tau=3$ Gyr) DTD.
+The model combination with the best (lowest) score for the MDF is the two-infall SFH with the exponential ($\tau=3$ Gyr) DTD.
 The choice of SFH has a larger effect on the overall score than the DTD, and the best-performing SFH is the two-infall model, followed closely by the early-burst.
 However, the difference between the best-scoring model and the worst (late-burst SFH with triple-evolution DTD) is fairly small.
-The quantitative agreement between the predicted and observed [Fe/H] DFs is primarily affected by the assumption of chemical equilibrium, the abundance gradient, and radial migration.
-For further discussion, see Section 3.2 of \citetalias{Johnson2021-Migration}.
+The quantitative agreement between the predicted and observed MDFs is primarily affected by the assumption of chemical equilibrium, the abundance gradient, and radial migration (see discussion in section 3.2 of \citetalias{Johnson2021-Migration}).
 
@@
 The distribution of [O/Fe] serves as a record of the relative rates of SNe Ia and CCSNe.
-As such, the shape of the distribution is greatly affected by both the SFH and DTD.
-Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs, all assuming an exponential DTD with $\tau=1.5$ Gyr, compared to the distributions measured by APOGEE.
+As such, its shape is greatly affected by both the SFH and DTD.
+Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs compared to the distributions measured by APOGEE, all assuming an exponential DTD with $\tau=1.5$ Gyr.
 We see similar trends with Galactic region across all four models.
-Near the midplane, the distributions at the innermost and outermost annuli are similar, but away from the midplane, there is a clear trend of a higher average stellar [O/Fe] at small $R_{\rm gal}$ and lower [O/Fe] at large $R_{\rm gal}$.
-
-While trends with $R_{\rm gal}$ and $|z|$ are similar, the shape of the distribution varies greatly with the chosen SFH.
-The inside-out and late-burst models produce similar distributions because of the similarity of their underlying SFHs \textemdash both skew heavily toward near-solar [O/Fe], although the late-burst model produces a slightly broader peak and a less-prominent high-[O/Fe] tail.
+Near the midplane, the distributions depend minimally on radius, but away from the midplane, there is a clear trend toward higher [O/Fe] at small $R_{\rm gal}$.
+
+While trends with $R_{\rm gal}$ and $|z|$ are similar between DTD models, the shape of the distribution varies greatly with the chosen SFH.
+The inside-out and late-burst models produce similar distributions because of the similarity of their underlying SFHs \textemdash the burst is imposed upon the inside-out SFH (see Equation \ref{eq:lateburst-sfh}).
+Both skew heavily toward near-solar [O/Fe], although the late-burst model produces a slightly broader peak and a less-prominent high-[O/Fe] tail.
+This difference arises because the late-burst SFH shifts a portion of the stellar mass budget to late times when [O/Fe] is low.
 The only region which shows any significant skew toward high [O/Fe] is $R_{\rm gal}=3-5$ kpc and $|z|=1-2$ kpc, but the shift to higher [O/Fe] at high latitudes is gradual and does not produce the notable trough at ${\rm [O/Fe]}\approx0.2$ which is seen in the APOGEE data.
 
-On the other hand, the early-burst model produces a bimodal distribution of [O/Fe] even out to large radii and close to the midplane, whereas the APOGEE distribution does not show a prominent high-$\alpha$ peak beyond $R_{\rm{Gal}}\sim11$ kpc.
-The early-burst SFH produces the closest match to the data by far: the low-$\alpha$ sequence away from the midplane shows increasing contribution with larger radii, with the innermost radii containing very few low-$\alpha$ stars.
-However, the high-$\alpha$ sequence contains substantial contribution from stars at large radii, which is not seen in the data.
+On the other hand, the early-burst model produces a bimodal distribution in [O/Fe] at most radii and close to the midplane, whereas the APOGEE distribution does not show a prominent high-$\alpha$ peak beyond $R_{\rm gal}\sim11$ kpc ($\sim7$ kpc in the midplane).
+Although agreement is not perfect, the early-burst SFH produces the closest match to the data by far: the low-$\alpha$ sequence away from the midplane is dominated by stars in the solar annulus and outer disk.
+However, the high-$\alpha$ sequence has considerably more outer disk stars than the data.
 
 The two-infall SFH produces \textit{three} distinct modes at ${\rm [O/Fe]}\approx 0.0$, $0.2$, and $0.4$.
-At small $R_{\rm gal}$ and with increasing $|z|$, the low-$\alpha$ peak decreases in prominence and the high-$\alpha$ peak increases, but the intermediate peak is a striking feature at all latitudes which is at odds with the APOGEE data.
+At small $R_{\rm gal}$ and with increasing $|z|$, the low-$\alpha$ peak decreases in prominence as the high-$\alpha$ peak increases, but the intermediate peak is a striking feature at all latitudes that is not observed.
+In the APOGEE data, the high-$\alpha$ peak is at ${\rm [O/Fe]}\approx+0.3$, roughly halfway between the intermediate and high-$\alpha$ peaks this model predicts.
 
@@
 The two-population DTD, which has the most prompt SNe Ia, places the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.2$ dex higher at ${\rm [O/Fe]}\approx0.4$.
-In general, models fewer prompt SNe Ia also populate the high-$\alpha$ sequence with more stars, as the chemical evolution track spends more time in the high-$\alpha$ regime.
+In general, models with fewer prompt SNe Ia also populate the high-$\alpha$ sequence with more stars because the chemical evolution track spends more time in the high-$\alpha$ regime.
 The exception to this is the two-population DTD, which produces a very strong high-$\alpha$ peak at $|z|>0.5$ kpc, likely a result of its long exponential tail.
@@
 The best-scoring model uses the two-infall SFH with the plateau ($W=0.3$ Gyr) DTD, although both plateau and exponential DTDs as well as the triple-system DTD score well when combined with certain SFHs.
-The late-burst SFH in general produces [O/Fe] DFs which score poorly compared to other models.
+The late-burst SFH generally produces [O/Fe] DFs that score poorly compared to other models.
 
@@
 
-A striking feature of the [O/Fe] distribution in the Milky Way is the distinct separation into two components, the high- and low-$\alpha$ sequences.
+A striking feature of the [O/Fe] distribution in the Milky Way is the distinct separation into two components, the high- and low-$\alpha$ sequences [references].
 The relative prominence of the two peaks varies with $R_{\rm gal}$ and $|z|$, as shown by the right-hand panels of Figures \ref{fig:ofe-df-sfh} and \ref{fig:ofe-df-dtd}.
-A crucial feature of this bimodality which is not apparent in the previous figures is the coincidence of both sequences at the same [Fe/H].
+A crucial feature of this bimodality, which is not apparent in the previous figures, is the presence of both sequences at the same [Fe/H].
 Figure \ref{fig:ofe-bimodality} compares the [O/Fe] distributions in the solar annulus ($7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc) in two bins of [Fe/H] for select model outputs and APOGEE data.
-The APOGEE distributions in the bottom-right panel (j) show that the high-$\alpha$ mode is more prominent at lower [Fe/H] and \vice versa, but the distributions in both bins are clearly bimodal.
+The APOGEE distributions in the bottom-right panel (j) show that the high-$\alpha$ mode is more prominent at lower [Fe/H] and vice versa, but the distributions in both bins are clearly bimodal.
 Moreover, the ``trough'' at ${\rm [O/Fe]}\approx0.2$ is consistent in each bin.
@@
 [Reference \citet{Vincenzo2021-AlphaDistribution} for how the bimodality is made stronger by the selection function, but it's not just due to selection effects.
-Describe the re-sampling we do to correct for this.] For most of our models, the low-$\alpha$ peak is the more prominent of the two, so by performing this resampling we enhance strength of the bimodality.
-However, for some models the high-$\alpha$ peak is the strongest, and the re-sampling process de-emphasizes the low-$\alpha$ peak below the prominence threshold (e.g., panel (f) of Figure \ref{fig:ofe-bimodality}).
+Describe the re-sampling we do to correct for this.]
+% \citet{Vincenzo2021-AlphaDistribution} demonstrate that the APOGEE selection function makes the observed $\alpha$ bimodality {\it weaker} in that the high-$\alpha$ sequence is undersampled relative to low-$\alpha$ stars.
+For most of our models, the low-$\alpha$ peak is the more prominent of the two, so by performing this resampling we enhance strength of the bimodality.
+However, for some models the high-$\alpha$ peak is the strongest, and the re-sampling process de-emphasizes the low-$\alpha$ peak below the prominence threshold (e.g., panel f of Figure \ref{fig:ofe-bimodality}).
 [Explain why this is ok]
@@
 The top row of panels (a--e) in Figure \ref{fig:ofe-bimodality} shows the [O/Fe] bimodality (or lack thereof) across five different DTDs, all of which assume the late-burst SFH.
-To quantify the bimodality, we use the {\tt scipy}'s \citep{2020SciPy-NMeth} peak-finding algorithm with an arbitrary prominence threshold of 0.1.
-Five of the eight DTDs (four of the five shown, plus the exponential ($\tau=3$ Gyr) model) exceed this threshold, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
-Panel (b) illustrates that the power-law ($\alpha=-1.1$) DTD produces a marginal high-$\alpha$ peak, although it doesn't meet the prominence threshold because it is too close to the low-$\alpha$ peak.
-In general, as was the case with the [O/Fe] distributions in Section \ref{sec:ofe-df}, DTDs with fewer prompt SNe Ia produce a high-$\alpha$ peak which is more prominent and at a higher [O/Fe].
+To quantify the bimodality, we use the peak-finding algorithm {\tt scipy.signal.find\_peaks} \citep{2020SciPy-NMeth}.
+We calculate the prominence, or vertical distance between a peak and its highest neighboring trough, and adopt an arbitrary threshold of 0.1.
+Five of the eight DTDs (four of the five shown, plus the exponential form with $\tau=3$ Gyr) exceed this prominence threshold, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
+Panel (b) shows that the power-law ($\alpha=-1.1$) DTD produces a marginal high-$\alpha$ peak, although it doesn't meet the prominence threshold because it is too close to the low-$\alpha$ peak.
+
+In general, DTDs with fewer prompt SNe Ia produce a high-$\alpha$ peak which is more prominent and at a higher [O/Fe], as was the case with the [O/Fe] distributions in Section \ref{sec:ofe-df}.
 One major discrepancy is that the APOGEE data show bimodality in both bins of [Fe/H], while the models run with the late-burst SFH only show a clear high-$\alpha$ peak at the low-metallicity ($-0.6<{\rm [Fe/H]}<-0.4$) bin.
@@
 On the other hand, the early-burst SFH {\it always} produces a bimodal distribution in the $-0.4\leq{\rm [Fe/H]}<-0.2$ bin regardless of the assumed DTD, although the lower-metallicity bin does not (the lower peak falls short of our prominence threshold of 0.1).
+
 For models with the late-burst and two-infall SFHs, bimodality is variable depending on the DTD: those with longer median delay times (e.g., exponential, plateau, or triple-system) generally produce a bimodal distribution in the $-0.6\leq{\rm [Fe/H]}<-0.4$ bin, while the power-law DTDs do not.
@@
 In order to identify trends among our many models, it will be useful to have some semi-quantitative way to compare their outputs to APOGEE data across the disk.
-In this Section, we compare all our model outputs to APOGEE across five diagnostics: the [Fe/H] DF, [O/Fe] DF, [Fe/H]--[O/Fe] plane, age--[O/Fe] plane, and [O/Fe] bimodality.
+In this Section, we compare all our model outputs to APOGEE across five diagnostics: the MDF, [O/Fe] DF, [Fe/H]--[O/Fe] plane, age--[O/Fe] plane, and [O/Fe] bimodality.
 We perform statistical tests between APOGEE and the model outputs in each region of the Galaxy (as described in corresponding subsections of Section \ref{sec:multizone-results}), then compute the average weighted by the size of the APOGEE sample in each region to obtain a single numerical score.
@@
 However, the picture gets less clear-cut when looking at the other SFHs.
-If the early-burst SFH is chosen, the DTDs with many prompt SNe Ia (power-law and two-population) produce the best agreement with the APOGEE [Fe/H] DFs but the {\it worst} agreement with the other observables.
+If the early-burst SFH is chosen, the DTDs with many prompt SNe Ia (power-law and two-population) produce the best agreement with the APOGEE MDFs but the {\it worst} agreement with the other observables.
 Finally, for the two-infall SFH, any DTD other than the power-law and two-population scores well, but the best-scoring DTD varies between diagnostics.
@@
 The right-hand panel of Figure \ref{fig:analytical-dtd} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs.
-We assume $\eta=2.5$, $\uptau_*=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
+We assume $\eta=2.5$, $\uptau_\star=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
 We compare the SD, DD WIDE, and DD CLOSE schemes to standard power-law, broken power-law, and exponential DTDs.

### 2024-03-19 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Appendix \ref{app:migration} describes our method for determining the migration distance $\Delta R_{\rm gal}$ for each model stellar population, which produces smoother distributions in chemical abundance space than the simulation-based approach.
-
-\subsection{Nucleosynthetic Yields}
-\label{sec:yields}
-
-For simplicity and easier comparison to the results of \citetalias{Johnson2021-Migration}, we focus our analysis on O and Fe, representing the $\alpha$ and Fe-peak elements, respectively.
-Both elements are produced by CCSNe.
-\vice adopts the instantaneous recycling approximation for CCSNe, so the equation which governs CCSN enrichment as a function of star formation for some element $x$ is simply
-\begin{equation}
-    \dot M_x^{\rm CC} = y_x^{\rm CC} \dot M_\star
-    \label{eq:ccsn-enrichment}
-\end{equation}
-where $y_x^{\rm CC}$ is the CCSN yield of element $x$ per unit mass of star formation, and $\dot M_\star$ is the SFR. 
-Following \citetalias{Johnson2021-Migration}, who in turn adopt their CCSN yields from \citet{ChieffiLimongi2004-CCSNYields} and \citet{LimongiChieffi2006-CCSNYields}, we adopt $y_{\rm O}^{\rm CC}=0.015$ and $y_{\rm Fe}^{\rm CC}=0.0012$.
-The primary effect of these yields is to set the low-[Fe/H] ``plateau'' in [O/Fe] which represents pure CCSN enrichment.
-The chosen yields for this paper produce a plateau at ${\rm [O/Fe]}=0.45$; see \citet{Weinberg2023-CCSNYield} for more discussion on the effect of the CCSN yields on chemical evolution.
-
-Following the formalism of \citet{Weinberg2017-ChemicalEquilibrium}, the rate of Fe contribution to the ISM from SNe Ia is 
-\begin{equation}
-    \dot M_{\rm Fe}^{\rm Ia} = y_{\rm Fe}^{\rm Ia} \langle \dot M_\star\rangle_{\rm Ia} \\
-\end{equation}
-where $\langle \dot M_\star\rangle_{\rm Ia}$ is the time-averaged SFR weighted by the DTD and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia.
-\citet{Weinberg2017-ChemicalEquilibrium} show in their Appendix A that
-\begin{equation}
-    \langle \dot M_\star\rangle_{\rm Ia} \equiv \frac{\int_0^t \dot M_\star(t')R_{\rm Ia}(t-t')dt'}{\int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt'}
-    \label{eq:weighted-sfr}
-\end{equation}
-where %$\dot M_\star(t)$ is the SFR at time $t$, 
-%$R_{\rm Ia}(t) dt$ is the number of SNe Ia which explode in the time interval $(t, t+dt)$ per unit mass of stars formed at $t=0$, 
-$R_{\rm Ia}$ is the DTD in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$,
-$t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the maximum simulation time.
-The denominator of Equation \ref{eq:weighted-sfr} is therefore the total number of SNe Ia per M$_{\odot}$ of stars formed $N_{\rm Ia}/M_\star$.
-
-The yield $y_{\rm Fe}^{\rm Ia}$ measures the mass of Fe produced by SNe Ia over the full duration of the DTD, which can be expressed as:
-\begin{equation}
-    y_{\rm Fe}^{\rm Ia} = m_{\rm Fe}^{\rm Ia} \int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt' = m_{\rm Fe}^{\rm Ia} \frac{N_{\rm Ia}}{M_\star},
-    \label{eq:dtd-integral}
-\end{equation}
-where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia, and $N_{\rm Ia}/M_\star=2.2\pm1\times10^{-3}\,{\rm M}_\odot^{-1}$ is the average number of SNe Ia per mass of stars formed \citep{MaozMannucci2012-SNeIaReview}.
-Adjusting the value of $y_{\rm Fe}^{\rm Ia}$ primarily affects the end point of chemical evolution tracks in [O/Fe]--[Fe/H] space. 
-Following \citetalias{Johnson2021-Migration}, we adopt $y_{\rm Fe}^{\rm Ia}=0.00214$.
-This yield is originally adapted from the W70 model of \citet{Iwamoto1999-SNIaYields}, but it is increased slightly so that the inside-out SFH produces stars with ${\rm [O/Fe]}\approx 0.0$ by the end of the model.
-\citet{Palla2021-SNIaYield} studied the effect of different SN Ia yields on GCE models in detail.
-
-\subsection{Delay Time Distributions}
-\label{sec:dtd-models}
-
-We explore five different functional forms for the DTD: a single power-law, a broken power-law with an initially flat plateau, a simple exponential, a two-population model, and a model based on triple-system dynamics.
-We also investigate one or two useful variations of the input parameters for each functional form.
-Figure \ref{fig:dtds} presents a selection of these DTDs, and Table \ref{tab:dtds} summarizes all of our DTDs and their parameters.
-We use simple forms rather than simulated physical or analytical models of SNe Ia for the sake of decreased computational time and easier interpretation of the model predictions.
-Physically-motivated models of the DTD must contend with many unknown or poorly-constrained parameters, so our simplified forms have the advantage of reducing the number of free parameters.
-In Appendix \ref{app:analytical-dtds}, we show that a few of our simple forms adequately approximate the more complete analytic models of \citet{Greggio2005-AnalyticalRates}.
-
-In this subsection we present functional forms $f_{\rm Ia}$ describing the shape of each DTD.
-$f_{\rm Ia}$ does not include the normalization, so it has units of Gyr$^{-1}$ as opposed to M$_\odot^{-1}$ Gyr$^{-1}$ and ist related to $R_{\rm Ia}$ according to
-% The relationship between $f_{\rm Ia}$, which has units of ${\rm Gyr}^{-1}$, and $R_{\rm Ia}$, which has units of ${\rm M}_\odot^{-1}\,{\rm Gyr}^{-1}$, is: 
-\begin{equation}
-    R_{\rm Ia}(t) = 
-    \begin{cases}
-        \frac{N_{\rm Ia}}{M_\star}
-        \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
-        0 & t < t_D.
-    \end{cases}
-    \label{eq:dtd-function}
-\end{equation}
-\vice automatically normalizes the provided function for the DTD according to this equation.
-In the remainder of this subsection, we discuss each form of $f_{\rm Ia}$ individually.
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/delay_time_distributions.pdf}
-    \caption{Selection of models for the SN Ia delay time distribution (DTD) used in this paper.
-All functions are normalized such that $f_{\rm Ia}(t=1\,{\rm Gyr})=1$.
-The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD} at the same scale as the DTDs.
-The horizontal and vertical error bars indicate the time range and 1$\sigma$ uncertainties, respectively, of each DTD measurement.
-The colored circles along the horizontal axis indicate the median delay time for each model.}
-    \label{fig:dtds}
-    \script{delay_time_distributions.py}
-\end{figure}
-
-% \begin{deluxetable*}{lcll}
-% \tablecaption{Summary of SN Ia DTDs explored in this paper.\label{tab:dtds}}
-% \tablehead{
-% \colhead{Model} & \colhead{Eq.} & \colhead{Parameters} & \colhead{Similar to}
-% }
-% \startdata
-\begin{table*}
-    \centering
-    \caption{Summary of SN Ia delay time distributions (DTDs) explored in this paper.\label{tab:dtds}}
-    \begin{tabular}{lcll}
-        \hline\hline
-        Model & Eq. & Parameters & Similar to \\
-        \hline
-        Two-population  & \ref{eq:prompt-dtd}   & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
-                        &                       & $\tau=3.0$ Gyr & \\
-        Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
-                                                      \citet{Heringer2019-FieldGalaxyDTD}       \\
-        Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.1$                 & \citet[][field]{Maoz2017-CosmicDTD}; 
-                                                      \citet{Wiseman2021-DESRates}              \\
-        Exponential & \ref{eq:exponential-dtd}  & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
-                                                                      \citet{Schonrich2009-RadialMixing};       \\
-                    &                           &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
-        Exponential & \ref{eq:exponential-dtd}   & $\tau=3.0$ Gyr    & --- \\
-        Plateau     & \ref{eq:plateau-dtd}  & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
-        Plateau     & \ref{eq:plateau-dtd}  & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
-        Triple-system   & \ref{eq:triple-dtd}   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2023-TripleEvolution} \\
-                        &                       & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
-        \hline
-    \end{tabular}
-\end{table*}
-% \enddata
-% \end{deluxetable*}
-
-\paragraph{Two-population} A DTD in which $\sim50\%$ of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the remainder form an exponential tail at large $t$:
-\begin{equation}
-    f_{\rm Ia}^{\rm twopop}(t) = 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
-    \label{eq:prompt-dtd}
-\end{equation}
-To approximate the DTD from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in $\sim 50\%$ of SNe Ia exploding within $t<100$ Myr.
-As Figure \ref{fig:dtds} illustrates, the two-population DTD has a shorter median delay time than most other models (except the power-law with $\alpha=-1.4$, not shown).
-This formulation is slightly different than the approximation used in other GCE studies \citep[e.g.,][]{Matteucci2006-BimodalDTDConsequences,Poulhazan2018-PrecisionPollution}, where it has a more distinctly bimodal shape.
-We have compared the two approximations to this DTD in a one-zone model and found that they produce very similar abundance tracks and MDFs.
-This DTD is adopted by the Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations.
-
-\paragraph{Power-law} A single power law with slope $\alpha$:
-\begin{equation}
-    f_{\rm Ia}^{\rm plaw}(t) = (t/1\,\rm{Gyr})^\alpha
-    \label{eq:powerlaw-dtd}
-\end{equation}
-% where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
-A declining power-law with $\alpha\sim-1$ is expected to arise from typical assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral \citep[see Section 3.5 from][]{Maoz2014-Review}.
-It is therefore a commonly assumed DTD in GCE studies (e.g., \citealt{Rybizki2017-Chempy}; \citetalias{Johnson2021-Migration}; \citealt{Weinberg2023-CCSNYield}).
-Additionally, the observational evidence for a power-law DTD is strong.
-\citet{Maoz2017-CosmicDTD} obtain a DTD with $\alpha=-1.07\pm0.09$ based on volumetric rates and an assumed cosmic SFH for field galaxies in redshift range $0\leq z\leq 2.25$.
-\citet{Wiseman2021-DESRates} obtain a similar slope of $\alpha=-1.13\pm0.05$ for field galaxies in the redshift range $0.2<z<0.6$.
-For galaxy clusters, \citet{Maoz2017-CosmicDTD} find a steeper DTD slope of $\alpha=-1.39^{+0.32}_{-0.05}$.
-\citet{Heringer2019-FieldGalaxyDTD} use a SFH-independent method to constrain the DTD for field galaxies within $0.01<z<0.2$ and find a steeper slope of $\alpha=-1.34^{+0.19}_{-0.17}$.
-In this paper, we investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$.
-
-\paragraph{Exponential} An exponentially declining DTD with timescale $\tau$:
-\begin{equation}
-    f_{\rm Ia}^{\rm exp}(t) = e^{-t/\tau}
-    \label{eq:exponential-dtd}
-\end{equation}
-This model allows analytic solutions to the abundances as a function of time for some SFHs, making it a popular choice.
-\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assume an exponential DTD with a timescale $\tau=1.5$ Gyr.
-We show in Appendix \ref{app:analytical-dtds} that a $\tau=1.5$ Gyr exponential is an adequate approximation for the analytical SD DTD from \citet{Greggio2005-AnalyticalRates}.
-There is less observational support for an exponential DTD.
-\citet{Strolger2020-ExponentialDTD}, fitting to the cosmic SFH and SFHs from field galaxies, find a range of exponential-like solutions with timescales $\sim 1.5 - 6$ Gyr.
-In this paper, we investigate timescales $\tau=1.5$ and 3 Gyr.
-
-\paragraph{Plateau} A modification of the power-law in which the DTD ``plateaus'' for a duration $W$ before declining:
-\begin{equation}
-    f_{\rm Ia}^{\rm plat}(t) =
-    \begin{cases}
-        1, & t < W \\
-        (t/W)^\alpha, & t \ge W
-    \end{cases}
-    \label{eq:plateau-dtd}
-\end{equation}
-% where $B_W=[(W-t_{\rm min}) + \frac{t_{\rm max}^{\alpha+1} - W^{\alpha+1}}{(\alpha+1)W^\alpha}]^{-1}$ is the normalization coefficient.
-Our primary motivation is to consider a model which matches observations at delay times beyond a few Gyr, where the DTD is best constrained, but with a smaller fraction of prompt ($\lesssim 100$ Myr) SNe Ia than the single power law.
-To our knowledge, this form of the DTD has not been considered in previous GCE models.
-We show in Appendix \ref{app:analytical-dtds} that this form can approximate the more complicated analytical DD DTDs from \citet{Greggio2005-AnalyticalRates}.
-We investigate the cases $W=0.3$ Gyr and $W=1$ Gyr, taking $\alpha=-1.1$ for all plateau models.
-
-\paragraph{Triple-system} A DTD based on simulations of triple-system evolution by \citet{Rajamuthukumar2023-TripleEvolution}.
-We approximate their numerically-generated DTD as a special case of the plateau model (Equation \ref{eq:plateau-dtd}) where the initial rate is quite low until an instantaneous rise to the plateau value at time $t_{\rm rise}$:
-\begin{equation}
-    f_{\rm Ia}^{\rm triple}(t) =
-    \begin{cases}
-        \epsilon, & t < t_{\rm rise} \\
-        1, & t_{\rm rise} \leq t < W \\
-        (t / W) ^ \alpha, & t \geq W
-    \end{cases}
-    \label{eq:triple-dtd}
-\end{equation}
-with $t_{\rm rise}=0.5$ Gyr, $W=0.5$ Gyr, $\alpha=-1.1$, and $\epsilon=0.05$ (i.e., the initial rate is 5\% of the peak rate).
-As illustrated in Figure \ref{fig:dtds}, the triple-system DTD has the longest median delay time out of all the models we investigate.
-
-\subsubsection{The Minimum SN Ia Delay Time}
-
-In addition to the DTD shape, the minimum SN Ia delay time $t_D$ is another parameter that can have an effect on chemical evolution observables, such as the location of the high-$\alpha$ knee and the [O/Fe] distribution function \citep[DF;][]{Andrews2017-ChemicalEvolution}.
-The value of $t_D$ is set by the lifetime of the most massive SN Ia progenitor system.
-Previous GCE studies have adopted values ranging from $t_D\approx30$ Myr \citep[e.g.,][]{Poulhazan2018-PrecisionPollution} to $t_D=150$ Myr \citepalias[e.g.,][]{Johnson2021-Migration}.
-We take $t_D=40$ Myr as our fiducial value as it is the approximate lifetime of an $8\,{\rm M}_\odot$ star.
-In Section \ref{sec:onezone-results} we find that adopting a longer $t_D$ has only a minor effect on the chemical evolution for most DTDs except the power-law, but in that case the effect of a longer $t_D$ can be approximated by adding an initial plateau of width $W=0.3$ Gyr to the DTD (see Figure \ref{fig:onezone-twopanel}).
-
-\subsection{Star Formation Histories}
-\label{sec:sfh}
-
-We consider four models for the SFH, which we refer to as inside-out, late-burst, early-burst, and two-infall. 
-The former two models, which feature a smooth SFH, were investigated by \citetalias{Johnson2021-Migration} using a similar methodology to this paper.
-The inside-out model produced a better agreement to the age--[O/Fe] relation observed by \citet{Feuillet2019-MilkyWayAges}, while the late-burst model better matched their observed age--metallicity relation.
-% The latter two models (early-burst and two-infall) feature discontinuous or ``bursty'' SFHs, and were proposed by \citet{Conroy2022-ThickDisk} and \citet{Chiappini1997-TwoInfall}, respectively, to explain the distinct evolution of the high- and low-$\alpha$ sequences.
-The latter two models feature discontinuous or ``bursty'' SFHs.
-The early-burst model, proposed by \citet{Conroy2022-ThickDisk}, uses an efficiency-driven starburst to explain the break in the \aFe trend observed in the H3 survey \citep{Conroy2019-H3Survey}.
-% , and [cite] found that it can also produce a bimodal \aFe distribution.
-The two-infall model was proposed by \citet{Chiappini1997-TwoInfall} and features two distinct episodes of gas infall which produce the thick and thin disks.
-Together, these four models cover a range of behavior including a smooth SFH and SFR-, SFE-, and infall-driven starbursts.
-
-The inside-out and late-burst models
-% The first two models are taken from \citetalias{Johnson2021-Migration} and 
-are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_\star$ is prescribed along with the star formation efficiency (SFE) timescale $\uptau_\star\equiv \Sigma_g/\dot\Sigma_\star$.
-The remaining quantities, infall rate (IFR) surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
-The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\uptau_\star$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in SFR mode).
-The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified.
-% See Appendix B of \citetalias{Johnson2021-Migration} for details on the normalization of the SFH. 
-The SFH is normalized such that the model predicts an accurate total stellar mass and surface density gradient (see Appendix B of \citetalias{Johnson2021-Migration}).
-We present an overview of the four SFHs in Figure \ref{fig:sfhs}, and we discuss them individually here.
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=\linewidth]{figures/star_formation_histories.pdf}
-    \caption{The surface densities of star formation $\dot \Sigma_\star$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\uptau_\star$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
-In each panel, we plot curves for the model zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
-    \label{fig:sfhs}
-    \script{star_formation_histories.py}
-\end{figure*}
-
-\paragraph{Inside-out} As in \citetalias{Johnson2021-Migration}, this is our fiducial SFH. The dimensionless time-dependence of the SFR is given by
-\begin{equation}
-    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm sfh}},
-    \label{eq:insideout-sfh}
-\end{equation}
-where we assume $\tau_{\rm rise}=2$ Gyr for all radii.
-The SFH timescale $\tau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\tau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the solar annulus and longer timescales in the outer Galaxy.
-The $\tau_{\rm sfh} - R_{\rm gal}$ relation is based on the radial gradients in stellar age in Milky Way-like spirals measured by \citet[][see Section 2.5 of \citetalias{Johnson2021-Migration} for details]{Sanchez2020-StarFormationTimescales}.
-
-\paragraph{Late-burst} A variation on the inside-out SFH with a burst in the SFR at late times which is described by a Gaussian according to
-\begin{equation}
-    f_{\rm LB}(t|R_{\rm gal}) = f_{\rm IO}(t|R_{\rm gal}) \Big(1 + A_b e^{-(t-t_b)^2/2\sigma_b^2} \Big),
-    \label{eq:lateburst-sfh}
-\end{equation}
-where $A_b$ is the dimensionless amplitude of the starburst, $t_b$ is the time of the peak of the burst, and $\sigma_b$ is the width of the Gaussian. 
-Evidence for a recent star formation burst $\sim 2-3$ Gyr ago has been found in {\it Gaia} \citep{Mor2019-Starburst} and in massive WDs in the solar neighborhood \citep{Isern2019-Starburst}.
-Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr. The determination of $\tau_{\rm sfh}$ 
-% and the normalization of the SFR as a function of $R_{\rm gal}$ 
-is the same as in the inside-out case.
-
-\paragraph{Early-burst} An extension of the model proposed by \citet{Conroy2022-ThickDisk} to explain the non-monotonic behavior of the high-$\alpha$ sequence down to ${\rm [Fe/H]}\approx-2.5$.
-This model features an abrupt factor $\sim20$ rise in the SFE at early times, driving an increase in the [O/Fe] abundance at the transition between the epochs of halo and thick disk formation.
-\citet{Stahlholdt2022-StarFormationEpochs} find evidence for a burst $\sim10$ Gyr ago which marks the beginning of a second phase of star formation.
-[Something about $\alpha$-bimodality from another paper].
-We adopt the following formula for the time-dependence of the SFE timescale from \citet{Conroy2022-ThickDisk}:
-\begin{equation}
-    \frac{\uptau_{\rm EB}}{1\,\rm{Gyr}} =
-    \begin{cases}
-        50, & t < 2.5\,\rm{Gyr} \\
-        \frac{50}{[1+3(t-2.5)]^2}, & 2.5\leq t \leq 3.7\,\rm{Gyr} \\
-        2.36, & t > 3.7\,\rm{Gyr}.
-    \end{cases}
-    \label{eq:earlyburst-taustar}
-\end{equation}
-While \citet{Conroy2022-ThickDisk} use a constant infall rate in their one-zone model, we adopt a radially-dependent infall rate which declines exponentially with time:
-\begin{equation}
-    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}},
-    \label{eq:earlyburst-ifr}
-\end{equation}
-where $\tau_{\rm sfh}$ is the same as in the inside-out case.
-To calculate $\dot \Sigma_\star$ from the above quantities, we modify the fiducial star formation law adopted from \citetalias{Johnson2021-Migration}, substituting $\uptau_{\rm EB}$ for the SFE timescale of molecular gas:
-\begin{equation}
-    \dot \Sigma_\star = 
-    \begin{cases}
-        \Sigma_g \uptau_{\rm EB}^{-1}, & \Sigma_g \geq \Sigma_{g,2} \\
-        \Sigma_g \uptau_{\rm EB}^{-1} \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
-        \Sigma_g \uptau_{\rm EB}^{-1} \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1},
-    \end{cases}
-    \label{eq:earlyburst-sfr}
-\end{equation}
-with $\Sigma_{g,1}=5\times 10^6\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\Sigma_{g,2}=2\times 10^7\,{\rm M}_\odot\,{\rm kpc}^{-2}$.
-
-\paragraph{Two-infall} First proposed by \citet{Chiappini1997-TwoInfall}, this model parameterizes the infall rate as two successive, exponentially declining bursts to explain the origin of the high- and low-$\alpha$ disk populations:
-\begin{equation}
-    \label{eq:twoinfall-ifr}
-    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2},
-\end{equation}
-% In this model, the first infall produces the thick disk and the second infall produces the thin disk. 
-where $N_1$ and $N_2$ are the normalizations of the first and second infall, respectively, and $t_{\rm on}$ is the onset time of the second infall.
-The normalization ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
-\begin{equation}
-    f_\Sigma(R) = f_\Sigma(0) e^{R(1/R_2 - 1/R_1)}.
-\end{equation}
-Following \citet{BlandHawthornGerhard2016-MilkyWayReview}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
-We note that most previous studies which use the two-infall model \citep[e.g.,][]{Spitoni2021-TwoInfall} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance.
-We adopt radially-dependent outflows as in \citetalias{Johnson2021-Migration} (see their Section 2.4 for details) for all our SFHs, including two-infall.
-We discuss the implications of this difference in Section \ref{sec:two-infall-discussion}.
-
-\subsection{The Multi-Zone Disk Model}
-\label{sec:multizone-methods}
+Table \ref{tab:multizone-parameters} summarizes our model parameters and the sub-sections in which we discuss them in detail.
 
@@
         % Multi-zone model parameters
-        R_{\rm gal}     & [0, 20] kpc   & \ref{sec:multizone-methods} & Galactocentric radius \\
-        \delta R_{\rm gal}  & 100 pc    & \ref{sec:multizone-methods} & Width of each concentric ring \\
+        R_{\rm gal}     & [0, 20] kpc   & \ref{sec:multizone-results} & Galactocentric radius \\
+        \delta R_{\rm gal}  & 100 pc    & \ref{sec:multizone-results} & Width of each concentric ring \\
         \Delta R_{\rm gal}  & N/A       & \ref{app:migration} & Change in orbital radius due to stellar migration \\
@@
         p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
-        \Delta t        & 10 Myr    & \ref{sec:multizone-methods} & Time-step size \\
-        t_{\rm max}     & 13.2 Gyr  & \ref{sec:multizone-methods} & Maximum simulation time \\
-        n               & 8         & \ref{sec:multizone-methods} & Number of stellar populations formed per ring per time-step \\
-        R_{\rm SF}      & 15.5 kpc  & \ref{sec:multizone-methods} & Maximum radius of star formation \\
+        \Delta t        & 10 Myr    & \ref{sec:multizone-results} & Time-step size \\
+        t_{\rm max}     & 13.2 Gyr  & \ref{sec:multizone-results} & Maximum simulation time \\
+        n               & 8         & \ref{sec:multizone-results} & Number of stellar populations formed per ring per time-step \\
+        R_{\rm SF}      & 15.5 kpc  & \ref{sec:multizone-results} & Maximum radius of star formation \\
         M_{g,0}   & 0         & \ref{sec:sfh}     & Initial gas mass \\
-        \dot M_r    & continuous    & \ref{sec:multizone-methods} & Recycling rate \citep[][Equation 2]{JohnsonWeinberg2020-Starbursts} \\
+        \dot M_r    & continuous    & \ref{sec:multizone-results} & Recycling rate \citep[][Equation 2]{JohnsonWeinberg2020-Starbursts} \\
         \hline
@@
 
-We use the multi-zone GCE model tools in \vice developed by \citetalias{Johnson2021-Migration}.
-The basic setup of our models follows theirs.
-The disk is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
-Stellar populations migrate radially under the prescription we describe in Appendix \ref{app:migration}, but each ring is otherwise described by a conventional one-zone GCE model with instantaneous mixing (see discussion in Section \ref{sec:onezone-results}).
-Following \citetalias{Johnson2021-Migration}, we do not implement radial gas flows \citep[e.g.,][]{LaceyFall1985-RadialGasFlows,BilitewskiSchonrich2012-RadialFlows}.
-
-We run our models with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
-Following \citetalias{Johnson2021-Migration}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_\star=0$ for $R_{\rm gal}>R_{\rm SF}$.
-The model has a full radial extent of 20 kpc, allowing a purely migrated population to arise in the outer 4.5 kpc.
-We adopt continuous recycling, which accounts for the time-dependent return of mass from all previous generations of stars \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
-We summarize these parameters, as well as those discussed in previous sub-sections, in Table \ref{tab:multizone-parameters}.
+\subsection{Nucleosynthetic Yields}
+\label{sec:yields}
+
+For simplicity and easier comparison to the results of \citetalias{Johnson2021-Migration}, we focus our analysis on O and Fe, representing the $\alpha$ and Fe-peak elements, respectively.
+Both elements are produced by CCSNe.
+\vice adopts the instantaneous recycling approximation for CCSNe, so the equation which governs CCSN enrichment as a function of star formation for some element $x$ is simply
+\begin{equation}
+    \dot M_x^{\rm CC} = y_x^{\rm CC} \dot M_\star
+    \label{eq:ccsn-enrichment}
+\end{equation}
+where $y_x^{\rm CC}$ is the CCSN yield of element $x$ per unit mass of star formation, and $\dot M_\star$ is the SFR. 
+Following \citetalias{Johnson2021-Migration}, who in turn adopt their CCSN yields from \citet{ChieffiLimongi2004-CCSNYields} and \citet{LimongiChieffi2006-CCSNYields}, we adopt $y_{\rm O}^{\rm CC}=0.015$ and $y_{\rm Fe}^{\rm CC}=0.0012$.
+The primary effect of these yields is to set the low-[Fe/H] ``plateau'' in [O/Fe] which represents pure CCSN enrichment.
+The chosen yields for this paper produce a plateau at ${\rm [O/Fe]}=0.45$; see \citet{Weinberg2023-CCSNYield} for more discussion on the effect of the CCSN yields on chemical evolution.
+
+Following the formalism of \citet{Weinberg2017-ChemicalEquilibrium}, the rate of Fe contribution to the ISM from SNe Ia is 
+\begin{equation}
+    \dot M_{\rm Fe}^{\rm Ia} = y_{\rm Fe}^{\rm Ia} \langle \dot M_\star\rangle_{\rm Ia} \\
+\end{equation}
+where $\langle \dot M_\star\rangle_{\rm Ia}$ is the time-averaged SFR weighted by the DTD and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia.
+\citet{Weinberg2017-ChemicalEquilibrium} show in their Appendix A that
+\begin{equation}
+    \langle \dot M_\star\rangle_{\rm Ia} \equiv \frac{\int_0^t \dot M_\star(t')R_{\rm Ia}(t-t')dt'}{\int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt'}
+    \label{eq:weighted-sfr}
+\end{equation}
+where %$\dot M_\star(t)$ is the SFR at time $t$, 
+%$R_{\rm Ia}(t) dt$ is the number of SNe Ia which explode in the time interval $(t, t+dt)$ per unit mass of stars formed at $t=0$, 
+$R_{\rm Ia}$ is the DTD in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$,
+$t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the maximum simulation time.
+The denominator of Equation \ref{eq:weighted-sfr} is therefore the total number of SNe Ia per M$_{\odot}$ of stars formed $N_{\rm Ia}/M_\star$.
+
+The yield $y_{\rm Fe}^{\rm Ia}$ measures the mass of Fe produced by SNe Ia over the full duration of the DTD, which can be expressed as:
+\begin{equation}
+    y_{\rm Fe}^{\rm Ia} = m_{\rm Fe}^{\rm Ia} \int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt' = m_{\rm Fe}^{\rm Ia} \frac{N_{\rm Ia}}{M_\star},
+    \label{eq:dtd-integral}
+\end{equation}
+where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia, and $N_{\rm Ia}/M_\star=2.2\pm1\times10^{-3}\,{\rm M}_\odot^{-1}$ is the average number of SNe Ia per mass of stars formed \citep{MaozMannucci2012-SNeIaReview}.
+Adjusting the value of $y_{\rm Fe}^{\rm Ia}$ primarily affects the end point of chemical evolution tracks in [O/Fe]--[Fe/H] space. 
+Following \citetalias{Johnson2021-Migration}, we adopt $y_{\rm Fe}^{\rm Ia}=0.00214$.
+This yield is originally adapted from the W70 model of \citet{Iwamoto1999-SNIaYields}, but it is increased slightly so that the inside-out SFH produces stars with ${\rm [O/Fe]}\approx 0.0$ by the end of the model.
+\citet{Palla2021-SNIaYield} studied the effect of different SN Ia yields on GCE models in detail.
+
+\subsection{Delay Time Distributions}
+\label{sec:dtd-models}
+
+We explore five different functional forms for the DTD: a single power-law, a broken power-law with an initially flat plateau, a simple exponential, a two-population model, and a model based on triple-system dynamics.
+We also investigate one or two useful variations of the input parameters for each functional form.
+Figure \ref{fig:dtds} presents a selection of these DTDs, and Table \ref{tab:dtds} summarizes all of our DTDs and their parameters.
+We use simple forms rather than simulated physical or analytical models of SNe Ia for the sake of decreased computational time and easier interpretation of the model predictions.
+Physically-motivated models of the DTD must contend with many unknown or poorly-constrained parameters, so our simplified forms have the advantage of reducing the number of free parameters.
+In Appendix \ref{app:analytical-dtds}, we show that a few of our simple forms adequately approximate the more complete analytic models of \citet{Greggio2005-AnalyticalRates}.
+
+In this subsection we present functional forms $f_{\rm Ia}$ describing the shape of each DTD.
+$f_{\rm Ia}$ does not include the normalization, so it has units of Gyr$^{-1}$ as opposed to M$_\odot^{-1}$ Gyr$^{-1}$ and ist related to $R_{\rm Ia}$ according to
+% The relationship between $f_{\rm Ia}$, which has units of ${\rm Gyr}^{-1}$, and $R_{\rm Ia}$, which has units of ${\rm M}_\odot^{-1}\,{\rm Gyr}^{-1}$, is: 
+\begin{equation}
+    R_{\rm Ia}(t) = 
+    \begin{cases}
+        \frac{N_{\rm Ia}}{M_\star}
+        \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
+        0 & t < t_D.
+    \end{cases}
+    \label{eq:dtd-function}
+\end{equation}
+\vice automatically normalizes the provided function for the DTD according to this equation.
+In the remainder of this subsection, we discuss each form of $f_{\rm Ia}$ individually.
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/delay_time_distributions.pdf}
+    \caption{Selection of models for the SN Ia delay time distribution (DTD) used in this paper.
+All functions are normalized such that $f_{\rm Ia}(t=1\,{\rm Gyr})=1$.
+The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD} at the same scale as the DTDs.
+The horizontal and vertical error bars indicate the time range and 1$\sigma$ uncertainties, respectively, of each DTD measurement.
+The colored circles along the horizontal axis indicate the median delay time for each model.}
+    \label{fig:dtds}
+    \script{delay_time_distributions.py}
+\end{figure}
+
+% \begin{deluxetable*}{lcll}
+% \tablecaption{Summary of SN Ia DTDs explored in this paper.\label{tab:dtds}}
+% \tablehead{
+% \colhead{Model} & \colhead{Eq.} & \colhead{Parameters} & \colhead{Similar to}
+% }
+% \startdata
+\begin{table*}
+    \centering
+    \caption{Summary of SN Ia delay time distributions (DTDs) explored in this paper.}
+    \label{tab:dtds}
+    \begin{tabular}{lcll}
+        \hline\hline
+        \multicolumn{1}{c}{Model} & Eq. & \multicolumn{1}{c}{Parameters} & \multicolumn{1}{c}{Similar to} \\
+        \hline
+        Two-population  & \ref{eq:prompt-dtd}   & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
+                        &                       & $\tau=3.0$ Gyr & \\
+        Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
+                                                      \citet{Heringer2019-FieldGalaxyDTD}       \\
+        Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.1$                 & \citet[][field]{Maoz2017-CosmicDTD}; 
+                                                      \citet{Wiseman2021-DESRates}              \\
+        Exponential & \ref{eq:exponential-dtd}  & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
+                                                                      \citet{Schonrich2009-RadialMixing};       \\
+                    &                           &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
+        Exponential & \ref{eq:exponential-dtd}   & $\tau=3.0$ Gyr    & --- \\
+        Plateau     & \ref{eq:plateau-dtd}  & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
+        Plateau     & \ref{eq:plateau-dtd}  & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
+        Triple-system   & \ref{eq:triple-dtd}   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2023-TripleEvolution} \\
+                        &                       & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
+        \hline
+    \end{tabular}
+\end{table*}
+% \enddata
+% \end{deluxetable*}
+
+\paragraph{Two-population} A DTD in which $\sim50\%$ of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the remainder form an exponential tail at large $t$:
+\begin{equation}
+    f_{\rm Ia}^{\rm twopop}(t) = 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
+    \label{eq:prompt-dtd}
+\end{equation}
+To approximate the DTD from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in $\sim 50\%$ of SNe Ia exploding within $t<100$ Myr.
+As we illustrate in Figure \ref{fig:dtds}, the two-population DTD has a shorter median delay time than most other models (except the power-law with $\alpha=-1.4$, not shown).
+This formulation is slightly different than the approximation used in other GCE studies \citep[e.g.,][]{Matteucci2006-BimodalDTDConsequences,Poulhazan2018-PrecisionPollution}, where it has a more distinctly bimodal shape.
+We have compared the two approximations to this DTD in a one-zone model and found that they produce very similar abundance tracks and MDFs.
+This DTD is adopted by the Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations.
+
+\paragraph{Power-law} A single power law with slope $\alpha$:
+\begin{equation}
+    f_{\rm Ia}^{\rm plaw}(t) = (t/1\,\rm{Gyr})^\alpha
+    \label{eq:powerlaw-dtd}
+\end{equation}
+% where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
+A declining power-law with $\alpha\sim-1$ is expected to arise from typical assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral \citep[see Section 3.5 from][]{Maoz2014-Review}.
+It is therefore a commonly assumed DTD in GCE studies (e.g., \citealt{Rybizki2017-Chempy}; \citetalias{Johnson2021-Migration}; \citealt{Weinberg2023-CCSNYield}).
+Additionally, the observational evidence for a power-law DTD is strong.
+\citet{Maoz2017-CosmicDTD} obtain a DTD with $\alpha=-1.07\pm0.09$ based on volumetric rates and an assumed cosmic SFH for field galaxies in redshift range $0\leq z\leq 2.25$.
+\citet{Wiseman2021-DESRates} obtain a similar slope of $\alpha=-1.13\pm0.05$ for field galaxies in the redshift range $0.2<z<0.6$.
+For galaxy clusters, \citet{Maoz2017-CosmicDTD} find a steeper DTD slope of $\alpha=-1.39^{+0.32}_{-0.05}$.
+\citet{Heringer2019-FieldGalaxyDTD} use a SFH-independent method to constrain the DTD for field galaxies within $0.01<z<0.2$ and find a steeper slope of $\alpha=-1.34^{+0.19}_{-0.17}$.
+In this paper, we investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$.
+
+\paragraph{Exponential} An exponentially declining DTD with timescale $\tau$:
+\begin{equation}
+    f_{\rm Ia}^{\rm exp}(t) = e^{-t/\tau}
+    \label{eq:exponential-dtd}
+\end{equation}
+This model allows analytic solutions to the abundances as a function of time for some SFHs, making it a popular choice.
+\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assume an exponential DTD with a timescale $\tau=1.5$ Gyr.
+We show in Appendix \ref{app:analytical-dtds} that a $\tau=1.5$ Gyr exponential is an adequate approximation for the analytical SD DTD from \citet{Greggio2005-AnalyticalRates}.
+There is less observational support for an exponential DTD.
+\citet{Strolger2020-ExponentialDTD}, fitting to the cosmic SFH and SFHs from field galaxies, find a range of exponential-like solutions with timescales $\sim 1.5 - 6$ Gyr.
+In this paper, we investigate timescales $\tau=1.5$ and 3 Gyr.
+
+\paragraph{Plateau} A modification of the power-law in which the DTD ``plateaus'' for a duration $W$ before declining:
+\begin{equation}
+    f_{\rm Ia}^{\rm plat}(t) =
+    \begin{cases}
+        1, & t < W \\
+        (t/W)^\alpha, & t \ge W
+    \end{cases}
+    \label{eq:plateau-dtd}
+\end{equation}
+% where $B_W=[(W-t_{\rm min}) + \frac{t_{\rm max}^{\alpha+1} - W^{\alpha+1}}{(\alpha+1)W^\alpha}]^{-1}$ is the normalization coefficient.
+Our primary motivation is to consider a model which matches observations at delay times beyond a few Gyr, where the DTD is best constrained, but with a smaller fraction of prompt ($\lesssim 100$ Myr) SNe Ia than the single power law.
+To our knowledge, this form of the DTD has not been considered in previous GCE models.
+We show in Appendix \ref{app:analytical-dtds} that this form can approximate the more complicated analytical DD DTDs from \citet{Greggio2005-AnalyticalRates}.
+We investigate the cases $W=0.3$ Gyr and $W=1$ Gyr, taking $\alpha=-1.1$ for all plateau models.
+
+\paragraph{Triple-system} A DTD based on simulations of triple-system evolution by \citet{Rajamuthukumar2023-TripleEvolution}.
+We approximate their numerically-generated DTD as a special case of the plateau model (Equation \ref{eq:plateau-dtd}) where the initial rate is quite low until an instantaneous rise to the plateau value at time $t_{\rm rise}$:
+\begin{equation}
+    f_{\rm Ia}^{\rm triple}(t) =
+    \begin{cases}
+        \epsilon, & t < t_{\rm rise} \\
+        1, & t_{\rm rise} \leq t < W \\
+        (t / W) ^ \alpha, & t \geq W
+    \end{cases}
+    \label{eq:triple-dtd}
+\end{equation}
+with $t_{\rm rise}=0.5$ Gyr, $W=0.5$ Gyr, $\alpha=-1.1$, and $\epsilon=0.05$ (i.e., the initial rate is 5\% of the peak rate).
+As illustrated in Figure \ref{fig:dtds}, the triple-system DTD has the longest median delay time out of all the models we investigate.
+
+\subsubsection{The Minimum SN Ia Delay Time}
+
+In addition to the DTD shape, the minimum SN Ia delay time $t_D$ is another parameter that can have an effect on chemical evolution observables, such as the location of the high-$\alpha$ knee and the [O/Fe] distribution function \citep[DF;][]{Andrews2017-ChemicalEvolution}.
+The value of $t_D$ is set by the lifetime of the most massive SN Ia progenitor system.
+Previous GCE studies have adopted values ranging from $t_D\approx30$ Myr \citep[e.g.,][]{Poulhazan2018-PrecisionPollution} to $t_D=150$ Myr \citepalias[e.g.,][]{Johnson2021-Migration}.
+We take $t_D=40$ Myr as our fiducial value as it is the approximate lifetime of an $8\,{\rm M}_\odot$ star.
+In Section \ref{sec:onezone-results} we find that adopting a longer $t_D$ has only a minor effect on the chemical evolution for most DTDs except the power-law, but in that case the effect of a longer $t_D$ can be approximated by adding an initial plateau of width $W=0.3$ Gyr to the DTD (see Figure \ref{fig:onezone-twopanel}).
+
+\subsection{Star Formation Histories}
+\label{sec:sfh}
+
+We consider four models for the SFH, which we refer to as inside-out, late-burst, early-burst, and two-infall. 
+The former two models, which feature a smooth SFH, were investigated by \citetalias{Johnson2021-Migration} using a similar methodology to this paper.
+The inside-out model produced a better agreement to the age--[O/Fe] relation observed by \citet{Feuillet2019-MilkyWayAges}, while the late-burst model better matched their observed age--metallicity relation.
+% The latter two models (early-burst and two-infall) feature discontinuous or ``bursty'' SFHs, and were proposed by \citet{Conroy2022-ThickDisk} and \citet{Chiappini1997-TwoInfall}, respectively, to explain the distinct evolution of the high- and low-$\alpha$ sequences.
+The latter two models feature discontinuous or ``bursty'' SFHs.
+The early-burst model, proposed by \citet{Conroy2022-ThickDisk}, uses an efficiency-driven starburst to explain the break in the \aFe trend observed in the H3 survey \citep{Conroy2019-H3Survey}.
+% , and [cite] found that it can also produce a bimodal \aFe distribution.
+The two-infall model was proposed by \citet{Chiappini1997-TwoInfall} and features two distinct episodes of gas infall which produce the thick and thin disks.
+Together, these four models cover a range of behavior including a smooth SFH and SFR-, SFE-, and infall-driven starbursts.
+
+The inside-out and late-burst models
+% The first two models are taken from \citetalias{Johnson2021-Migration} and 
+are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_\star$ is prescribed along with the star formation efficiency (SFE) timescale $\uptau_\star\equiv \Sigma_g/\dot\Sigma_\star$.
+The remaining quantities, infall rate (IFR) surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
+The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\uptau_\star$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in SFR mode).
+The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified.
+% See Appendix B of \citetalias{Johnson2021-Migration} for details on the normalization of the SFH. 
+The SFH is normalized such that the model predicts an accurate total stellar mass and surface density gradient (see Appendix B of \citetalias{Johnson2021-Migration}).
+We present an overview of the four SFHs in Figure \ref{fig:sfhs}, and we discuss them individually here.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figures/star_formation_histories.pdf}
+    \caption{The surface densities of star formation $\dot \Sigma_\star$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\uptau_\star$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
+In each panel, we plot curves for the model zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
+    \label{fig:sfhs}
+    \script{star_formation_histories.py}
+\end{figure*}
+
+\paragraph{Inside-out} As in \citetalias{Johnson2021-Migration}, this is our fiducial SFH. The dimensionless time-dependence of the SFR is given by
+\begin{equation}
+    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm sfh}},
+    \label{eq:insideout-sfh}
+\end{equation}
+where we assume $\tau_{\rm rise}=2$ Gyr for all radii.
+The SFH timescale $\tau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\tau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the solar annulus and longer timescales in the outer Galaxy.
+The $\tau_{\rm sfh} - R_{\rm gal}$ relation is based on the radial gradients in stellar age in Milky Way-like spirals measured by \citet[][see Section 2.5 of \citetalias{Johnson2021-Migration} for details]{Sanchez2020-StarFormationTimescales}.
+
+\paragraph{Late-burst} A variation on the inside-out SFH with a burst in the SFR at late times which is described by a Gaussian according to
+\begin{equation}
+    f_{\rm LB}(t|R_{\rm gal}) = f_{\rm IO}(t|R_{\rm gal}) \Big(1 + A_b e^{-(t-t_b)^2/2\sigma_b^2} \Big),
+    \label{eq:lateburst-sfh}
+\end{equation}
+where $A_b$ is the dimensionless amplitude of the starburst, $t_b$ is the time of the peak of the burst, and $\sigma_b$ is the width of the Gaussian. 
+Evidence for a recent star formation burst $\sim 2-3$ Gyr ago has been found in {\it Gaia} \citep{Mor2019-Starburst} and in massive WDs in the solar neighborhood \citep{Isern2019-Starburst}.
+Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr. The determination of $\tau_{\rm sfh}$ 
+% and the normalization of the SFR as a function of $R_{\rm gal}$ 
+is the same as in the inside-out case.
+
+\paragraph{Early-burst} An extension of the model proposed by \citet{Conroy2022-ThickDisk} to explain the non-monotonic behavior of the high-$\alpha$ sequence down to ${\rm [Fe/H]}\approx-2.5$.
+This model features an abrupt factor $\sim20$ rise in the SFE at early times, driving an increase in the [O/Fe] abundance at the transition between the epochs of halo and thick disk formation.
+\citet{Stahlholdt2022-StarFormationEpochs} find evidence for a burst $\sim10$ Gyr ago which marks the beginning of a second phase of star formation.
+[Something about $\alpha$-bimodality from another paper].
+We adopt the following formula for the time-dependence of the SFE timescale from \citet{Conroy2022-ThickDisk}:
+\begin{equation}
+    \frac{\uptau_{\rm EB}}{1\,\rm{Gyr}} =
+    \begin{cases}
+        50, & t < 2.5\,\rm{Gyr} \\
+        \frac{50}{[1+3(t-2.5)]^2}, & 2.5\leq t \leq 3.7\,\rm{Gyr} \\
+        2.36, & t > 3.7\,\rm{Gyr}.
+    \end{cases}
+    \label{eq:earlyburst-taustar}
+\end{equation}
+While \citet{Conroy2022-ThickDisk} use a constant infall rate in their one-zone model, we adopt a radially-dependent infall rate which declines exponentially with time:
+\begin{equation}
+    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}},
+    \label{eq:earlyburst-ifr}
+\end{equation}
+where $\tau_{\rm sfh}$ is the same as in the inside-out case.
+To calculate $\dot \Sigma_\star$ from the above quantities, we modify the fiducial star formation law adopted from \citetalias{Johnson2021-Migration}, substituting $\uptau_{\rm EB}$ for the SFE timescale of molecular gas:
+\begin{equation}
+    \dot \Sigma_\star = 
+    \begin{cases}
+        \Sigma_g \uptau_{\rm EB}^{-1}, & \Sigma_g \geq \Sigma_{g,2} \\
+        \Sigma_g \uptau_{\rm EB}^{-1} \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
+        \Sigma_g \uptau_{\rm EB}^{-1} \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1},
+    \end{cases}
+    \label{eq:earlyburst-sfr}
+\end{equation}
+with $\Sigma_{g,1}=5\times 10^6\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\Sigma_{g,2}=2\times 10^7\,{\rm M}_\odot\,{\rm kpc}^{-2}$.
+
+\paragraph{Two-infall} First proposed by \citet{Chiappini1997-TwoInfall}, this model parameterizes the infall rate as two successive, exponentially declining bursts to explain the origin of the high- and low-$\alpha$ disk populations:
+\begin{equation}
+    \label{eq:twoinfall-ifr}
+    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2},
+\end{equation}
+% In this model, the first infall produces the thick disk and the second infall produces the thin disk. 
+where $N_1$ and $N_2$ are the normalizations of the first and second infall, respectively, and $t_{\rm on}$ is the onset time of the second infall.
+The normalization ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
+\begin{equation}
+    f_\Sigma(R) = f_\Sigma(0) e^{R(1/R_2 - 1/R_1)}.
+\end{equation}
+Following \citet{BlandHawthornGerhard2016-MilkyWayReview}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
+We note that most previous studies which use the two-infall model \citep[e.g.,][]{Spitoni2021-TwoInfall} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance.
+We adopt radially-dependent outflows as in \citetalias{Johnson2021-Migration} (see their Section 2.4 for details) for all our SFHs, including two-infall.
+We discuss the implications of this difference in Section \ref{sec:two-infall-discussion}.
 
@@
 
+We use the multi-zone GCE model tools in \vice developed by \citetalias{Johnson2021-Migration}.
+The basic setup of our models follows theirs.
+The disk is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
+Stellar populations migrate radially under the prescription we describe in Appendix \ref{app:migration}, but each ring is otherwise described by a conventional one-zone GCE model with instantaneous mixing (see discussion in Section \ref{sec:onezone-results}).
+Following \citetalias{Johnson2021-Migration}, we do not implement radial gas flows \citep[e.g.,][]{LaceyFall1985-RadialGasFlows,BilitewskiSchonrich2012-RadialFlows}.
+
+We run our models with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
+Following \citetalias{Johnson2021-Migration}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_\star=0$ for $R_{\rm gal}>R_{\rm SF}$.
+The model has a full radial extent of 20 kpc, allowing a purely migrated population to arise in the outer 4.5 kpc.
+We adopt continuous recycling, which accounts for the time-dependent return of mass from all previous generations of stars \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
+We summarize these parameters in Table \ref{tab:multizone-parameters}.
+
 \subsection{The distribution of [Fe/H]}
@@
 For models with the late-burst and two-infall SFHs, bimodality is variable depending on the DTD: those with longer median delay times (e.g., exponential, plateau, or triple-system) generally produce a bimodal distribution in the $-0.6\leq{\rm [Fe/H]}<-0.4$ bin, while the power-law DTDs do not.
-None of our SFH+DTD combinations can produce an [O/Fe] distribution which is bimodal in {\it both} bins of [Fe/H], as we observe in APOGEE (j).
+None of our SFH+DTD combinations can produce an [O/Fe] distribution which is bimodal in {\it both} bins of [Fe/H] shown in Figure \ref{fig:ofe-bimodality}, as observed in APOGEE (panel j).
 
@@
 In order to identify trends among our many models, it will be useful to have some semi-quantitative way to compare their outputs to APOGEE data across the disk.
-In this Section, we compare all our model outputs to APOGEE across five diagnostics: the MDF, [O/Fe] DF, [Fe/H]--[O/Fe] plane, age--[O/Fe] plane, and [O/Fe] bimodality.
+In this section, we compare all of our model outputs to APOGEE across five diagnostics: the MDF, [O/Fe] DF, [Fe/H]--[O/Fe] plane, age--[O/Fe] plane, and [O/Fe] bimodality.
 We perform statistical tests between APOGEE and the model outputs in each region of the Galaxy (as described in corresponding subsections of Section \ref{sec:multizone-results}), then compute the average weighted by the size of the APOGEE sample in each region to obtain a single numerical score.
@@
 The diagnostic scores for each model are presented in Table \ref{tab:results}.
-These scores are useful to indicate combinations of SFH and DTD which are favorable or disfavorable in certain regimes, but we emphasize that we do not use these scores to fit the models to the data.
+We use these scores to indicate combinations of SFH and DTD which are favorable or unfavorable in certain regimes, but we do {\it not} fit our models to the data.
 To avoid drawing strong conclusions from small numerical differences in scores, 

### 2024-03-20 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Stellar populations at the high-[Fe/H] end of the distribution have migrated from inner regions.
+[More discussion about Figure \ref{fig:ofe-feh-twoinfall}].
 
@@
 
-Table \ref{tab:results} indicates combinations of SFH and DTD which are more or less favorable in certain regimes.
+% Table \ref{tab:results} indicates combinations of SFH and DTD which are more or less favorable in certain regimes.
 However, we emphasize that we do not use these scores to fit the models to the data.
-Much of the variation between models can be explained by the choice of SFH: in general, the two-infall models rank the highest across all diagnostics, while the late-burst models generally compare poorly to the rest.
-This is different for the bimodality test, where the early-burst SFH is able to produce a bimodal [O/Fe] distribution for all DTDs, as discussed in Section \ref{sec:bimodality}.
+Much of the variation between models can be explained by the choice of SFH.
+In general, the two-infall models rank the highest across all diagnostics, while the late-burst models compare poorly to the rest.
+If we remove the two-infall models altogether due to their dominance in the scoring system, our results do not qualitatively change.
+The SFHs rank differently in the bimodality test, where the early-burst SFH is able to produce a bimodal [O/Fe] distribution for all DTDs, as discussed in Section \ref{sec:bimodality}.
+
 The choice of DTD has a clear effect on the model scores, and this effect is similar across the diagnostics.
 The models which perform the best (most \yes's and fewest \no's) are those with the exponential and plateau DTDs.
-It is interesting that the best-performing DTD overall in our scoring system, the exponential DTD with $\tau=1.5$ Gyr, is intermediate among all our DTDs in terms of the number of prompt SNe Ia and median delay time, but has the {\it lowest} rate at very long delay times ($\sim10$ Gyr).
+It is interesting that the best-scoring DTD overall, the exponential DTD with $\tau=1.5$ Gyr, is intermediate among all our DTDs in terms of the number of prompt SNe Ia and median delay time, but has the {\it lowest} rate at very long delay times ($\sim10$ Gyr).
 Models with a large fraction of prompt SNe Ia, such as the power-law and two-population DTDs, fare quite poorly, with the steepest power-law ($\alpha=-1.4$) ending up in the bottom tirtile across the board for most of our SFHs.
-If we remove the two-infall models altogether due to their dominance in the scoring system, our results do not qualitatively change.
 
 % The best DTDs for each SFH
-The main takeaway from Table \ref{tab:results} is that while certain DTDs tend to score better than others, there is no single DTD which always produces optimal agreement with the data across all diagnostics.
+% The main takeaway from Table \ref{tab:results} is that 
+While certain DTDs tend to score better than others, there is no single DTD which always produces optimal agreement with the data across all diagnostics.
 Depending on the choice of SFH, different DTDs will succeed at reproducing different observables.
 If an inside-out or late-burst SFH is chosen, the exponential DTDs with either timescale will produce optimal agreement with all observables.
-However, the picture gets less clear-cut when looking at the other SFHs.
+However, the picture becomes less clear when looking at the other SFHs.
 If the early-burst SFH is chosen, the DTDs with many prompt SNe Ia (power-law and two-population) produce the best agreement with the APOGEE MDFs but the {\it worst} agreement with the other observables.

### 2024-03-20 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         \Delta R_{\rm gal}  & N/A       & \ref{app:migration} & Change in orbital radius due to stellar migration \\
-        p(\Delta R_{\rm gal}|\tau,R_{\rm form}) & Equation \ref{eq:radial-migration}    & \ref{app:migration} & Probability density function of radial migration distance \\
+        p(\Delta R_{\rm gal}|\uptau,R_{\rm form}) & Equation \ref{eq:radial-migration}    & \ref{app:migration} & Probability density function of radial migration distance \\
         z                   & [-3, 3] kpc                & \ref{app:migration} & Distance from Galactic midplane at present day \\
-        p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
+        p(z|\uptau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
         \Delta t        & 10 Myr    & \ref{sec:multizone-results} & Time-step size \\
@@
         f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the late-burst SFR \\
-        \tau_{\rm rise}             & 2 Gyr     & \ref{sec:sfh} & SFR rise timescale for inside-out and early-burst models \\
+        \uptau_{\rm rise}             & 2 Gyr     & \ref{sec:sfh} & SFR rise timescale for inside-out and early-burst models \\
         \uptau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the early-burst SFE timescale \\
@@
         \eta(R_{\rm gal}=8\,{\rm kpc})  & 2.15  & \ref{sec:onezone-results} & Outflow mass-loading factor at the solar annulus \\
-        \tau_{\rm sfh}(R_{\rm gal}=8\,{\rm kpc})    & 15.1 Gyr  & \ref{sec:sfh} & SFH timescale at the solar annulus \\
+        \uptau_{\rm sfh}(R_{\rm gal}=8\,{\rm kpc})    & 15.1 Gyr  & \ref{sec:sfh} & SFH timescale at the solar annulus \\
     \enddata
@@
         Two-population  & \ref{eq:prompt-dtd}   & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
-                        &                       & $\tau=3.0$ Gyr & \\
+                        &                       & $\uptau_{\rm Ia}=3$ Gyr & \\
         Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
@@
                                                       \citet{Wiseman2021-DESRates}              \\
-        Exponential & \ref{eq:exponential-dtd}  & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
+        Exponential & \ref{eq:exponential-dtd}  & $\uptau_{\rm Ia}=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
                                                                       \citet{Schonrich2009-RadialMixing};       \\
                     &                           &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
-        Exponential & \ref{eq:exponential-dtd}   & $\tau=3.0$ Gyr    & --- \\
+        Exponential & \ref{eq:exponential-dtd}  & $\uptau_{\rm Ia}=3$ Gyr   & --- \\
         Plateau     & \ref{eq:plateau-dtd}  & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
-        Plateau     & \ref{eq:plateau-dtd}  & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
+        Plateau     & \ref{eq:plateau-dtd}  & $W=1$ Gyr, $\alpha=-1.1$      & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
         Triple-system   & \ref{eq:triple-dtd}   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2023-TripleEvolution} \\
@@
 \begin{equation}
-    f_{\rm Ia}^{\rm twopop}(t) = 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
+    f_{\rm Ia}^{\rm twopop}(t) = 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\uptau}\Big]
     \label{eq:prompt-dtd}
 \end{equation}
-To approximate the DTD from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in $\sim 50\%$ of SNe Ia exploding within $t<100$ Myr.
+To approximate the DTD from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\uptau_{\rm Ia}=3$ Gyr, which results in $\sim 50\%$ of SNe Ia exploding within $t<100$ Myr.
 As we illustrate in Figure \ref{fig:dtds}, the two-population DTD has a shorter median delay time than most other models (except the power-law with $\alpha=-1.4$, not shown).
@@
 
-\paragraph{Exponential} An exponentially declining DTD with timescale $\tau$:
-\begin{equation}
-    f_{\rm Ia}^{\rm exp}(t) = e^{-t/\tau}
+\paragraph{Exponential} An exponentially declining DTD with timescale $\uptau_{\rm Ia}$:
+\begin{equation}
+    f_{\rm Ia}^{\rm exp}(t) = e^{-t/\uptau_{\rm Ia}}
     \label{eq:exponential-dtd}
@@
 This model allows analytic solutions to the abundances as a function of time for some SFHs, making it a popular choice.
-\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assume an exponential DTD with a timescale $\tau=1.5$ Gyr.
-We show in Appendix \ref{app:analytical-dtds} that a $\tau=1.5$ Gyr exponential is an adequate approximation for the analytical SD DTD from \citet{Greggio2005-AnalyticalRates}.
+\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assume an exponential DTD with a timescale $\uptau_{\rm Ia}=1.5$ Gyr.
+We show in Appendix \ref{app:analytical-dtds} that a $\uptau_{\rm Ia}=1.5$ Gyr exponential is an adequate approximation for the analytical SD DTD from \citet{Greggio2005-AnalyticalRates}.
 There is less observational support for an exponential DTD.
 \citet{Strolger2020-ExponentialDTD}, fitting to the cosmic SFH and SFHs from field galaxies, find a range of exponential-like solutions with timescales $\sim 1.5 - 6$ Gyr.
-In this paper, we investigate timescales $\tau=1.5$ and 3 Gyr.
+In this paper, we investigate timescales $\uptau_{\rm Ia}=1.5$ and 3 Gyr.
 
@@
 \begin{equation}
-    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm sfh}},
+    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\uptau_{\rm rise}}) e^{-t/\uptau_{\rm sfh}},
     \label{eq:insideout-sfh}
 \end{equation}
-where we assume $\tau_{\rm rise}=2$ Gyr for all radii.
-The SFH timescale $\tau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\tau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the solar annulus and longer timescales in the outer Galaxy.
-The $\tau_{\rm sfh} - R_{\rm gal}$ relation is based on the radial gradients in stellar age in Milky Way-like spirals measured by \citet[][see Section 2.5 of \citetalias{Johnson2021-Migration} for details]{Sanchez2020-StarFormationTimescales}.
+where we assume $\uptau_{\rm rise}=2$ Gyr for all radii.
+The SFH timescale $\uptau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\uptau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the solar annulus and longer timescales in the outer Galaxy.
+The $\uptau_{\rm sfh} - R_{\rm gal}$ relation is based on the radial gradients in stellar age in Milky Way-like spirals measured by \citet[][see Section 2.5 of \citetalias{Johnson2021-Migration} for details]{Sanchez2020-StarFormationTimescales}.
 
@@
 Evidence for a recent star formation burst $\sim 2-3$ Gyr ago has been found in {\it Gaia} \citep{Mor2019-Starburst} and in massive WDs in the solar neighborhood \citep{Isern2019-Starburst}.
-Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr. The determination of $\tau_{\rm sfh}$ 
+Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr. The determination of $\uptau_{\rm sfh}$ 
 % and the normalization of the SFR as a function of $R_{\rm gal}$ 
@@
 \begin{equation}
-    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}},
+    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\uptau_{\rm sfh}},
     \label{eq:earlyburst-ifr}
 \end{equation}
-where $\tau_{\rm sfh}$ is the same as in the inside-out case.
+where $\uptau_{\rm sfh}$ is the same as in the inside-out case.
 To calculate $\dot \Sigma_\star$ from the above quantities, we modify the fiducial star formation law adopted from \citetalias{Johnson2021-Migration}, substituting $\uptau_{\rm EB}$ for the SFE timescale of molecular gas:
@@
     \label{eq:twoinfall-ifr}
-    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2},
+    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\uptau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\uptau_2},
 \end{equation}
@@
 %         % $\dot M_\star(t)$     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
-%         % $\tau_{\rm rise}$ & 2.0 Gyr     & SFR rise timescale \\
-%         % $\tau_{\rm sfh}$  & 15.1 Gyr  & SFR exponential \\
+%         % $\uptau_{\rm rise}$ & 2.0 Gyr     & SFR rise timescale \\
+%         % $\uptau_{\rm sfh}$  & 15.1 Gyr  & SFR exponential \\
 %         \hline
@@
 For consistency, we adopt most of the parameter values from Table \ref{tab:multizone-parameters} for our one-zone models.
-We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr) and an SFE timescale $\uptau_\star\equiv M_g/\dot M_\star=2$ Gyr.
+We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\uptau_{\rm rise}=2$ Gyr and $\uptau_{\rm sfh}=15.1$ Gyr) and an SFE timescale $\uptau_\star\equiv M_g/\dot M_\star=2$ Gyr.
 Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_\star=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time $t_D=40$ Myr.
@@
     % The dotted, dashed, and solid curves represent models with $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively. 
-    For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr. 
-    \textit{Center:} Three models which assume an exponential DTD with varying timescale $\tau$. 
-    % The solid, dashed, and dotted curves represent $\tau=6$, 3, and 1.5 Gyr, respectively.
+    For reference, the solid gray curve represents an exponential DTD with $\uptau_{\rm Ia}=3$ Gyr. 
+    \textit{Center:} Three models which assume an exponential DTD with varying timescale $\uptau_{\rm Ia}$. 
+    % The solid, dashed, and dotted curves represent $\uptau=6$, 3, and 1.5 Gyr, respectively.
     \textit{Right:} Three models which assume a plateau DTD with varying plateau width $W$. 
@@
     All assume a post-plateau slope of $\alpha=-1.1$.
-For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted purple curve represents a power-law DTD with $\alpha=-1.1$ and no plateau.}
+For reference, the solid gray curve represents an exponential DTD with $\uptau_{\rm Ia}=3$ Gyr, and the dotted purple curve represents a power-law DTD with $\alpha=-1.1$ and no plateau.}
     \label{fig:onezone-threepanel}
@@
 The effect on the [O/Fe] DF is similar to the previous two models: a longer plateau raises the median delay time, resulting in a smaller low-$\alpha$ peak and a more prominent high-$\alpha$ tail.
-The abundance tracks from several different plateau widths fill the space in between the exponential ($\tau=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
-The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\tau=3$ Gyr), although the [O/Fe] DFs are somewhat more distinct, with the plateau model producing a peak closer to the power-law case.
+The abundance tracks from several different plateau widths fill the space in between the exponential ($\uptau_{\rm Ia}=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
+The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\uptau_{\rm Ia}=3$ Gyr), although the [O/Fe] DFs are somewhat more distinct, with the plateau model producing a peak closer to the power-law case.
 
@@
     \caption{\textit{Left:} Comparison of one-zone models with different minimum delay times $t_D$ and DTDs.
-    % minimum SN Ia delay times $t_D=40$ Myr (solid) and 150 Myr (dashed curves) for three DTDs: power-law with $\alpha=-1.1$ (blue), plateau with $W=0.3$ Gyr (green), and exponential with $\tau=1.5$ Gyr (purple curves).
+    % minimum SN Ia delay times $t_D=40$ Myr (solid) and 150 Myr (dashed curves) for three DTDs: power-law with $\alpha=-1.1$ (blue), plateau with $W=0.3$ Gyr (green), and exponential with $\uptau_{\rm Ia}=1.5$ Gyr (purple curves).
     The layout is similar to Figure \ref{fig:onezone-threepanel}. For clarity, we assume a mass-loading factor $\eta=1$ for the exponential DTD curves, which places the end-point at higher [Fe/H].
     \textit{Right:} Comparison of one-zone models with five different forms for the DTD.
-    % : triple-system (yellow), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
+    % : triple-system (yellow), plateau with $W=1$ Gyr (cyan), exponential with $\uptau_{\rm Ia}=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
     }
@@
 In Figure \ref{fig:onezone-twopanel}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (dashed purple line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (solid green line), and their [O/Fe] DFs are virtually identical.
-The difference between the two values of $t_D$ for the exponential ($\tau=3$ Gyr) DTD in both the abundance tracks and distributions is nearly indistinguishable.
+The difference between the two values of $t_D$ for the exponential ($\uptau_{\rm Ia}=3$ Gyr) DTD in both the abundance tracks and distributions is nearly indistinguishable.
 We do not consider the effect on the other DTDs because a 150 Myr minimum delay time is incompatible with the two-population model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD due to its low SN Ia rate at short delay times.
@@
 The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is a result of the delayed exponential component.
-The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models occupy the intermediate space between these extremes.
+The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\uptau_{\rm Ia}=1.5$ Gyr) models occupy the intermediate space between these extremes.
 On the other hand, the [O/Fe] DF from the exponential model has the strongest peak, while the plateau ($W=1$ Gyr) and triple-system models produce nearly identical distributions in the low-$\alpha$ regime.
 The power-law ($\alpha=-1.1$) and two-population DTDs produce similar [O/Fe] DFs despite notably different abundance tracks.
-The exponential ($\tau=3$ Gyr) and plateau ($W=0.3$ Gyr) models, while not shown, produce similar abundance tracks to the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models, respectively.
+The exponential ($\uptau_{\rm Ia}=3$ Gyr) and plateau ($W=0.3$ Gyr) models, while not shown, produce similar abundance tracks to the plateau ($W=1$ Gyr) and exponential ($\uptau_{\rm Ia}=1.5$ Gyr) models, respectively.
 
@@
 Degeneracies between models in one regime can be resolved in the other.
-For example, the exponential ($\tau=3$ Gyr) and plateau ($W=1$ Gyr) DTDs are indistinguishable in [O/Fe]--[Fe/H] space but predict different [O/Fe] DFs.
+For example, the exponential ($\uptau_{\rm Ia}=3$ Gyr) and plateau ($W=1$ Gyr) DTDs are indistinguishable in [O/Fe]--[Fe/H] space but predict different [O/Fe] DFs.
 Of course, both of these observables are also greatly affected by the parameters of the SFH.
@@
 All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:sample}) and smoothed with a box-car width of 0.2 dex.
-    \textit{Left columns:} comparison between the inside-out and two-infall SFHs; both assume the exponential ($\tau=1.5$ Gyr) DTD. 
+    \textit{Left columns:} comparison between the inside-out and two-infall SFHs; both assume the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD. 
     \textit{Center column:} the distributions from APOGEE DR17 for reference, binned and smoothed similarly.
-    \textit{Right columns:} comparison between the power-law ($\alpha=-1.4$) and exponential ($\tau=3$ Gyr) DTDs with the inside-out SFH.}
+    \textit{Right columns:} comparison between the power-law ($\alpha=-1.4$) and exponential ($\uptau_{\rm Ia}=3$ Gyr) DTDs with the inside-out SFH.
+[Add: noticeable but subtle change in inner-galaxy peak and tail between DTDs]}
     \label{fig:feh-df-comparison}
@@
 Figure \ref{fig:feh-df-comparison} shows MDFs across the Galaxy for a selection of models and APOGEE data.
-The two left-hand columns show MDFs from our models which assume the same DTD (exponential with $\tau=1.5$ Gyr) but different SFHs.
+The two left-hand columns show MDFs from our models which assume the same DTD (exponential with $\uptau_{\rm Ia}=1.5$ Gyr) but different SFHs.
 For comparison, the APOGEE MDFs are binned similarly and presented in the center column of Figure \ref{fig:feh-df-comparison}.
@@
 Holding the SFH fixed, varying the DTD has minimal influence on these MDFs for fixed SFH.
-The two right-hand columns of Figure \ref{fig:feh-df-comparison} plot the MDFs for two multi-zone models, which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
+The two right-hand columns of Figure \ref{fig:feh-df-comparison} plot the MDFs for two multi-zone models, which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\uptau_{\rm Ia}=3$ Gyr.
 The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of explosions occurring within 1 Gyr in the former but only $\sim 30\%$ in the latter.
@@
 For all SFHs except two-infall, the outer Galaxy has a longer SFR timescale than the inner Galaxy, so the MDF in the outer Galaxy is relatively unaffected by the fraction of prompt SNe Ia.
-The inner Galaxy is more sensitive to the choice of DTD than the outer Galaxy.
+The inner Galaxy MDF is more sensitive to the choice of DTD than the outer Galaxy.
 The SFH peaks earlier and declines more sharply due to the inside-out formation of the disk.
@@
 
-The model combination with the best (lowest) score for the MDF is the two-infall SFH with the exponential ($\tau=3$ Gyr) DTD.
+The model combination with the best (lowest) score for the MDF is the two-infall SFH with the exponential ($\uptau_{\rm Ia}=3$ Gyr) DTD.
 The choice of SFH has a larger effect on the overall score than the DTD, and the best-performing SFH is the two-infall model, followed closely by the early-burst.
@@
     \caption{Distributions of [O/Fe] from multi-zone models with different SFHs.
-All assume the exponential ($\tau=1.5$ Gyr) DTD.
+All assume the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD.
 The format of each panel is the same as in Figure \ref{fig:feh-df-comparison}, except that all distributions are smoothed with a box-car width of 0.05 dex.
@@
 As such, its shape is greatly affected by both the SFH and DTD.
-Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs compared to the distributions measured by APOGEE, all assuming an exponential DTD with $\tau=1.5$ Gyr.
+Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs compared to the distributions measured by APOGEE, all assuming an exponential DTD with $\uptau_{\rm Ia}=1.5$ Gyr.
 We see similar trends with Galactic region across all four models.
@@
 The two-population DTD, which has the most prompt SNe Ia, places the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.2$ dex higher at ${\rm [O/Fe]}\approx0.4$.
-In general, models with fewer prompt SNe Ia also populate the high-$\alpha$ sequence with more stars because the chemical evolution track spends more time in the high-$\alpha$ regime.
+In general, models with fewer prompt SNe Ia populate the high-$\alpha$ sequence with more stars because the chemical evolution track spends more time in the high-$\alpha$ regime.
 The exception to this is the two-population DTD, which produces a very strong high-$\alpha$ peak at $|z|>0.5$ kpc, likely a result of its long exponential tail.
@@
     \textit{Top row:} results from five multi-zone models which assume the late-bust SFH but different DTDs.
-\textit{Bottom row}: the first four panels compare the four SFHs, all assuming an exponential DTD with $\tau=1.5$ Gyr.
+\textit{Bottom row}: the first four panels compare the four SFHs, all assuming an exponential DTD with $\uptau_{\rm Ia}=1.5$ Gyr.
 The bottom-right panel (highlighted) plots data from APOGEE DR17 for reference.}
@@
 We calculate the prominence, or vertical distance between a peak and its highest neighboring trough, and adopt an arbitrary threshold of 0.1.
-Five of the eight DTDs (four of the five shown, plus the exponential form with $\tau=3$ Gyr) exceed this prominence threshold, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
+Five of the eight DTDs (four of the five shown, plus the exponential form with $\uptau_{\rm Ia}=3$ Gyr) exceed this prominence threshold, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
 Panel (b) shows that the power-law ($\alpha=-1.1$) DTD produces a marginal high-$\alpha$ peak, although it doesn't meet the prominence threshold because it is too close to the low-$\alpha$ peak.
@@
 
-Panels (f)--(i) in the bottom row of Figure \ref{fig:ofe-bimodality} illustrate the effect of the SFH on the [O/Fe] bimodality with the exponential ($\tau=1.5$ Gyr) DTD.
+Panels (f)--(i) in the bottom row of Figure \ref{fig:ofe-bimodality} illustrate the effect of the SFH on the [O/Fe] bimodality with the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD.
 The inside-out SFH does not produce a bimodal distribution for any of our DTDs.
@@
     \caption{A comparison of the [O/Fe]--[Fe/H] plane between the four SFHs in our multi-zone models.
-All assume the exponential ($\tau=1.5$ Gyr) DTD.
+All assume the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD.
 Each panel plots a random mass-weighted sample of 10,000 star particles in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by $R_{\rm gal}$ at birth.
@@
 Figure \ref{fig:ofe-feh-sfh} compares the [O/Fe]--[Fe/H] plane in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) between our four model SFHs.
-All models presented in this figure assume an exponential DTD with $\tau=1.5$ Gyr, as it lies in the middle in terms of balance between prompt and delayed SNe Ia.
+All models presented in this figure assume an exponential DTD with $\uptau_{\rm Ia}=1.5$ Gyr, as it lies in the middle in terms of balance between prompt and delayed SNe Ia.
 The black curves represent the ISM abundance as a function of time in the central zone; in the absence of radial migration, all simulated stellar populations would lie along these lines.
@@
 For these models, the simulated stellar abundances are reasonably well-aligned with the APOGEE contours at low $|z|$ (bottom panels), but they entirely miss the observed high-$\alpha$ sequence at high $|z|$ (top panels).
-In the center column, the exponential ($\tau=1.5$ Gyr) DTD produces a distribution which aligns quite well with the APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to large [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
+In the center column, the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD produces a distribution which aligns quite well with the APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to large [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
 While it does better at populating the high-$\alpha$ sequence than the previous DTDs, the bulk of the simulated populations at large $|z|$ still fall below the APOGEE 30\% contour (top panel).
@@
     \caption{A comparison of the age--[O/Fe] relation between multi-zone models with different SFHs.
-All assume the exponential ($\tau=1.5$ Gyr) DTD.
+All assume the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD.
 Each panel plots a random mass-weighted sample of 10,000 star particles in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
@@
 Figure \ref{fig:age-ofe-sfh} compares the stellar age and [O/Fe] distributions in the solar neighborhood between our four SFHs.
-Similar to Figure \ref{fig:ofe-feh-sfh}, all four panels assume an exponential DTD with $\tau=1.5$ Gyr.
+Similar to Figure \ref{fig:ofe-feh-sfh}, all four panels assume an exponential DTD with $\uptau_{\rm Ia}=1.5$ Gyr.
 We include age data from \citetalias{Leung2023-Ages} for qualitative comparison, though we caution against drawing strong conclusions because we don't correct for selection effects or systematics in the neural net ages.
@@
 Moving to stars at low $|z|$, our plateau ($W=1$ Gyr) and triple-system DTDs over-produce stars at the old, high-$\alpha$ end of the distribution, while also diverging significantly from the observed sequence near solar [O/Fe].
-The exponential ($\tau=1.5$ Gyr) DTD comes closest to reproducing the observed range in [O/Fe], while the two DTDs with the shortest median delay time once again produce a smaller range of [O/Fe] than observed.
+The exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD comes closest to reproducing the observed range in [O/Fe], while the two DTDs with the shortest median delay time once again produce a smaller range of [O/Fe] than observed.
 We note that the break between the linear and flat parts of the relation is sharpest for the exponential DTD, and a more gradual transition is observed for the other four DTDs.
-This could be because the exponential DTD is most dominant at intermediate delay times ($\tau\sim 1-3$ Gyr) but falls off much faster than the other models at long delay times, so the evolution of [O/Fe] is quite slow for lookback times $\lesssim 5$ Gyr.
-Overall, the exponential ($\tau=1.5$ Gyr) DTD most closely matches the data for stars with $0\leq|z|<1$ kpc.
+This could be because the exponential DTD is most dominant at intermediate delay times ($t\sim 1-3$ Gyr) but falls off much faster than the other models at long delay times, so the evolution of [O/Fe] is quite slow for lookback times $\lesssim 5$ Gyr.
+Overall, the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD most closely matches the data for stars with $0\leq|z|<1$ kpc.
 
@@
 \begin{equation}
-    \Delta\tau_{\rm RMS} \equiv \sqrt{\frac{\sum_k \Delta\tau_k^2 n_{{\rm L23},k}}{n_{\rm L23,tot}}}
+    \Delta\uptau_{\rm RMS} \equiv \sqrt{\frac{\sum_k \Delta\uptau_k^2 n_{{\rm L23},k}}{n_{\rm L23,tot}}}
     \label{eq:age-ofe-score}
 \end{equation}
-where $\Delta\tau_k=\rm{med}(\tau_{\rm \vice})-\rm{med}(\tau_{\rm L23})$ is the difference between the mass-weighted median star particle age in \vice and the median stellar age from \citetalias{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citetalias{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
-As before, the score for the model as a whole is the average of $\Delta \tau_{\rm RMS}$ across all regions, weighted by the number of stars in the age sample in each region.
+where $\Delta\uptau_k=\rm{med}(\uptau_{\rm \vice})-\rm{med}(\uptau_{\rm L23})$ is the difference between the mass-weighted median star particle age in \vice and the median stellar age from \citetalias{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citetalias{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
+As before, the score for the model as a whole is the average of $\Delta \uptau_{\rm RMS}$ across all regions, weighted by the number of stars in the age sample in each region.
 
@@
 In general, the two-infall models rank the highest across all diagnostics, while the late-burst models compare poorly to the rest.
+We discuss our implementation of the two-infall SFH in Section \ref{sec:two-infall-discussion}.
 If we remove the two-infall models altogether due to their dominance in the scoring system, our results do not qualitatively change.
@@
 The models which perform the best (most \yes's and fewest \no's) are those with the exponential and plateau DTDs.
-It is interesting that the best-scoring DTD overall, the exponential DTD with $\tau=1.5$ Gyr, is intermediate among all our DTDs in terms of the number of prompt SNe Ia and median delay time, but has the {\it lowest} rate at very long delay times ($\sim10$ Gyr).
+It is interesting that the best-scoring DTD overall, the exponential DTD with $\uptau_{\rm Ia}=1.5$ Gyr, is intermediate among all our DTDs in terms of the number of prompt SNe Ia and median delay time, but has the {\it lowest} rate at very long delay times ($\sim10$ Gyr).
 Models with a large fraction of prompt SNe Ia, such as the power-law and two-population DTDs, fare quite poorly, with the steepest power-law ($\alpha=-1.4$) ending up in the bottom tirtile across the board for most of our SFHs.
@@
 % The main takeaway from Table \ref{tab:results} is that 
-While certain DTDs tend to score better than others, there is no single DTD which always produces optimal agreement with the data across all diagnostics.
-Depending on the choice of SFH, different DTDs will succeed at reproducing different observables.
-If an inside-out or late-burst SFH is chosen, the exponential DTDs with either timescale will produce optimal agreement with all observables.
+While certain DTDs tend to score better than others, there is no single DTD which always produces optimal agreement with the data across all observables and for all SFHs. 
+% Depending on the choice of SFH, different DTDs will succeed at reproducing different observables. 
+If an inside-out or late-burst SFH is chosen, the exponential DTDs score the highest across all observables.
 However, the picture becomes less clear when looking at the other SFHs.
-If the early-burst SFH is chosen, the DTDs with many prompt SNe Ia (power-law and two-population) produce the best agreement with the APOGEE MDFs but the {\it worst} agreement with the other observables.
+If the early-burst SFH is chosen, the DTDs with a large prompt fraction (power-law and two-population) produce the best agreement with the APOGEE MDFs but the {\it worst} agreement with the other observables.
 Finally, for the two-infall SFH, any DTD other than the power-law and two-population scores well, but the best-scoring DTD varies between diagnostics.
@@
 
-% [Discuss \citet{Palicio2024-CosmicSNIaRate}]
-\citet{Palicio2024-CosmicSNIaRate} predict the cosmic SN Ia rate from a variety of DTDs and cosmic star formation rates (CSFRs) and fit to observations.
-They find that, depending on the choice of CSFR, the DTDs of \citet{MatteucciRecchi2001-SNIaTimescale}, \citet{Mannucci2006-TwoPopulations}, \citet{Totani2008-DTD}, and the WIDE DD model of \citet{Greggio2005-AnalyticalRates} can all produce good fits to the observed cosmic SN Ia rate.
-This study provides a useful basis for comparison because the first and last of these DTDs are similar to our exponential ($\tau=1.5$ Gyr) and plateau ($W=1$ Gyr) DTDs, respectively (see Appendix \ref{app:analytical-dtds} for more discussion); the \citet{Mannucci2006-TwoPopulations} is our two-population DTD; and the \citet{Totani2008-DTD} is a $t^{-1}$ power-law with a minimum delay $t_D=100$ Myr.
-It is noteworthy that the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale} best fits the majority of CSFRs in \citet{Palicio2024-CosmicSNIaRate}, and our similar exponential ($\tau=1.5$ Gyr) DTD {\it also} performs best across all our SFHs.
-
-\citet{Poulhazan2018-PrecisionPollution} found that DTDs with a significant prompt component (power-law and two-population) produced the highest average stellar abundance of [O/Fe].
-They also found that these models produced the narrowest [O/Fe] distributions and suppressed the long tail to low [O/Fe] ratios.
-Conversely, their models with essentially 0 prompt SNe Ia produced a lower average stellar [O/Fe] ratio at late times and a broader distribution of [O/Fe].
-Their isolated galaxy simulations have an SFR which features an early ($<1$ Gyr) burst followed by a roughly exponential decline, qualitatively similar to our early-burst model but with the peak of star formation occuring $\sim3$ Gyr earlier.
-We note that their simulations were not designed to reproduce a Milky Way-like galaxy; as such, their [O/Fe] distributions peak around $\sim0.45$ which is higher than the APOGEE high-$\alpha$ sequence.
-Nevertheless, our study reproduces their finding that a DTD with more prompt SNe Ia will produce a narrower distribution of [O/Fe].
-One exception to this is the exponential DTD, which has a marginally narrower distribution than the power-law DTD close to the midplane [numbers here] but a more prominent hith-$\alpha$ tail.
-This is likely a consequence of the fact that the exponential DTD has a much lower SN Ia rate at late times ($\sim10$ Gyr) than other models [expand on this].
-
 Across most of the observables, the power-law ($\alpha=-1.1$) DTD, which has the strongest motivation from extra-galactic observations, poorly reproduces the observed Galactic chemical abundance distributions.
-This can be mitigated somewhat with a longer minimum delay time, which we show in Section \ref{sec:onezone-results} has a similar effect on chemical evolution tracks as the plateau DTD.
+This can be mitigated somewhat with a longer minimum delay time, which we show in Section \ref{sec:onezone-results} has a similar effect on chemical evolution tracks as the addition of an initial plateau in the DTD.
 Even so, it is clear that the high fraction of prompt SNe Ia in the DTD of, e.g., \citet{Maoz2017-CosmicDTD} is at odds with Galactic chemical abundance measurements.
@@
 
-[Metallicity dependent DTD] \citet{Gandhi2022-MetallicityDependentRates,Johnson2023-Binaries}
+% [Discuss \citet{Palicio2024-CosmicSNIaRate}]
+% \citet{Palicio2024-CosmicSNIaRate} predict the cosmic SN Ia rate from a variety of DTDs and cosmic star formation rates (CSFRs) and fit to observations.
+They find that, depending on the choice of CSFR, the DTDs of \citet{MatteucciRecchi2001-SNIaTimescale}, \citet{Mannucci2006-TwoPopulations}, \citet{Totani2008-DTD}, and the WIDE DD model of \citet{Greggio2005-AnalyticalRates} can all produce good fits to the observed cosmic SN Ia rate.
+This study provides a useful basis for comparison because the first and last of these DTDs are similar to our exponential ($\uptau_{\rm Ia}=1.5$ Gyr) and plateau ($W=1$ Gyr) DTDs, respectively (see Appendix \ref{app:analytical-dtds} for more discussion); the \citet{Mannucci2006-TwoPopulations} is our two-population DTD; and the \citet{Totani2008-DTD} is a $t^{-1}$ power-law with a minimum delay $t_D=100$ Myr.
+It is noteworthy that the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale} best fits the majority of CSFRs in \citet{Palicio2024-CosmicSNIaRate}, and our similar exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD {\it also} performs best across all our SFHs.
+[Intro sentence].
+\citet{Palicio2024-CosmicSNIaRate} fit combinations of cosmic star formation rates (CSFRs) and DTDs, many of which are similar to the forms in this paper, to the observed cosmic SN Ia rate.
+Notably, the DTD which best fit the majority of their CSFRs was the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale}, which is similar to the exponential form with $\tau_{\rm Ia}=1.5$ Gyr (see Appendix \ref{app:analytical-dtds} for more discussion).
+\citet{Palicio2024-CosmicSNIaRate} are able to exclude DTDs with a very high or very low fraction of prompt SNe Ia, but a number of their DTDs could produce a convincing fit to the observed rates with the right CSFR.
+[Connect back to this paper].
+
+% In both isolated and cosmological simulations, \citet{Poulhazan2018-PrecisionPollution} found that DTDs with a significant prompt component (power-law and two-population) produced the highest average [O/Fe] and the narrowest [O/Fe] distributions.
+Conversely, their models with essentially 0 prompt SNe Ia produced a lower average stellar [O/Fe] ratio at late times and a broader distribution of [O/Fe].
+Their simulations have an SFR which features an early ($<1$ Gyr) burst followed by a roughly exponential decline, qualitatively similar to our early-burst model but with the peak of star formation occuring $\sim3$ Gyr earlier.
+We note that their simulations were not designed to reproduce a Milky Way-like galaxy; as such, their [O/Fe] distributions peak around $\sim0.45$ which is higher than the APOGEE high-$\alpha$ sequence.
+Nevertheless, our study reproduces their finding that a DTD with more prompt SNe Ia will produce a narrower distribution of [O/Fe].
+One exception to this is the exponential DTD, which has a marginally narrower distribution than the power-law DTD close to the midplane [numbers here] but a more prominent high-$\alpha$ tail.
+This is likely a consequence of the fact that the exponential DTD has a much lower SN Ia rate at late times ($\sim10$ Gyr) than other models [expand on this].
+Our findings are also in qualitative agreement with the isolated and cosmological simulations of \citet{Poulhazan2018-PrecisionPollution}, namely that DTDs with a significant prompt component produce narrower [O/Fe] distributions and a higher average [O/Fe].
 
@@
 [Why does two-infall do so well across the board, even in the [Fe/H] and [O/Fe] DFs where it seems worse by eye?]
-Across every diagnostic in Table \ref{tab:results}, the two-infall models outperform every other SFH.
+Across every diagnostic (except [O/Fe] bimodality), in Table \ref{tab:results}, the two-infall models outperform every other SFH.
 It is somewhat surprising that the two-infall models score higher than the early-burst even for the [O/Fe] DFs, when the double-peaked distributions produced by the latter are qualitatively closer to the APOGEE data than the former's triple-peaked distributions.
@@
 
-[First exploration of two-infall with mass loading, radial migration. Further investigation coming in future paper.]
+To our knowledge, this paper is the first exploration of a two-infall SFH which incorporates both mass-loading and radial migration.
+A detailed examination of the two-infall SFH in our GCE models is beyond the scope of this paper, but will be the subject of future work.
 
@@
     \item Metallicity-dependent DTD normalization and/or shape.
+    \item [Evidence for metallicity-dependent rates of SNe Ia \citet{Gandhi2022-MetallicityDependentRates,Johnson2023-Binaries} and CC SNe \citep{Pessi2023-MetalDepCCSNe}].
 \end{itemize}
@@
 
-    [Ohio State \& Carnegie land acknowledgements]
     % From the Center for Belonging and Social Change, https://cbsc.osu.edu/about-us/land-acknowledgement
@@
 
-    [David and Jennifer NSF grant]
+    [Carnegie land acknowledgement]
+
+    LOD and JAJ acknowledge support from NSF grant 2307621. JAJ and JWJ acknowledge support from NSF grant 1909841.
+    JWJ acknowledges financial support from an Ohio State University Presidential Fellowship and a Carnegie Theoretical Astrophysics Center postdoctoral fellowship.
     % Software acknowledgements if not a AAS journal
@@
 \begin{equation}
-    \sigma_{\Delta R} = 1.35\,{\rm kpc} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61} \Big(\frac{\tau}{1\,{\rm Gyr}}\Big)^{0.33}
+    \sigma_{\Delta R} = 1.35\,{\rm kpc} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61} \Big(\frac{T}{1\,{\rm Gyr}}\Big)^{0.33}
     \label{eq:radial-migration}
 \end{equation}
-where $\tau$ is the age of the star particle.
+where $T$ is the age of the star particle.
 
@@
 \end{equation}
-We fit the above function to the distributions of $z$ in h277 in varying bins of $\tau$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
+We fit the above function to the distributions of $z$ in h277 in varying bins of $T$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
 \begin{equation}
     h_z = (0.25\,{\rm kpc}) 
-    e^{\frac{\tau-5\,{\rm Gyr}}{7.0\,{\rm Gyr}}}
+    e^{\frac{T-5\,{\rm Gyr}}{7.0\,{\rm Gyr}}}
     e^{\frac{R_{\rm final}-8\,{\rm kpc}}{6.0\,{\rm kpc}}}.

### 2024-03-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     Type Ia supernovae (SNe Ia) produce most of the Fe-peak elements in the Universe and therefore are a crucial ingredient in galactic chemical evolution models.
-SNe Ia do not explode immediately after star formation and the delay-time distribution (DTD) has not been definitively determined by supernova surveys or theoretical models.
+SNe Ia do not explode immediately after star formation, and the delay-time distribution (DTD) has not been definitively determined by supernova surveys or theoretical models.
 Because the DTD also affects the relationship among age, [Fe/H], and \aFe in chemical evolution models, comparison with observations of stars in the Milky Way is an important consistency check for any proposed DTD.
 We implement several popular forms of the DTD in combination with multiple star formation histories for the Milky Way in %one-zone and
-    multi-zone chemical evolution models including a prescription for radial stellar migration.
+    multi-zone chemical evolution models which include radial stellar migration.
     % using the Versatile Integrator for Chemical Evolution (\vice). \vice includes a prescription for radial stellar migration in multi-zone models. 
     We compare our predicted interstellar medium abundance tracks, stellar abundance distributions, and stellar age distributions to the final data release of the Apache Point Observatory Galactic Evolution Experiment (APOGEE).
-We find that the SN Ia DTD has the largest effect on the \aFe distribution: a DTD with more prompt SNe Ia produces a stellar abundance distribution that is skewed toward a lower \aFe ratio, whereas a DTD with more delayed SNe Ia produces a distribution that is skewed toward higher \aFe.
+We find that the DTD has the largest effect on the \aFe distribution: a DTD with more prompt SNe Ia produces a stellar abundance distribution that is skewed toward a lower \aFe ratio.
+    % whereas a DTD with more delayed SNe Ia produces a distribution that is skewed toward higher \aFe.
     While the DTD alone cannot explain the observed bimodality in the \aFe distribution, in combination with an appropriate star formation history it affects the goodness of fit between the simulated and observed high-$\alpha$ sequence.
-Our model results favor a DTD with longer delay times and fewer prompt SNe Ia than the fiducial $t^{-1}$ power law.
+Our model results favor an extended DTD with fewer prompt SNe Ia than the fiducial $t^{-1}$ power law.
 \end{abstract}
@@
 
-% [What is the delay time distribution]
-The {\it delay time distribution} (DTD) refers to the rate of SN Ia events per unit mass of star formation as a function of stellar population age
+% [What is the delay-time distribution]
+The {\it delay-time distribution} (DTD) refers to the rate of SN Ia events per unit mass of star formation as a function of stellar population age
 % The rate of SNe Ia which explode as a function of time after the formation of a hypothetical unit-mass single stellar population is known as the delay-time distribution 
@@
 % [Observational DTDs]
-Surveys of SNe Ia 
-% have provided the primary observational constraints on the DTD. This can be done 
-can constrain the DTD
-by comparing the observed rate of SNe Ia to their host galaxy parameters \citep[e.g.,][]{Mannucci2005-SNRate,Heringer2019-FieldGalaxyDTD} or inferred star formation histories \citep[SFHs; e.g.,][]{Maoz2012-SloanIIDTD}, measuring SN Ia rates in galaxy clusters \citep[e.g.,][]{Maoz2010-ClusterDTD}, or comparing the volumetric SN Ia rate to the cosmic SFH as a whole \citep[e.g.,][]{Graur2014-VolumetricSNIaRates,Strolger2020-ExponentialDTD}.
+Surveys of SNe Ia can constrain the DTD by comparing the observed rate of SNe Ia to their host galaxy parameters \citep[e.g.,][]{Mannucci2005-SNRate,Heringer2019-FieldGalaxyDTD} or inferred star formation histories \citep[SFHs; e.g.,][]{Maoz2012-SloanIIDTD}, measuring SN Ia rates in galaxy clusters \citep[e.g.,][]{Maoz2010-ClusterDTD}, or comparing the volumetric SN Ia rate to the cosmic SFH as a whole \citep[e.g.,][]{Graur2014-VolumetricSNIaRates,Strolger2020-ExponentialDTD}.
 Early studies, which had limited sample sizes, produced unimodal \citep{Strolger2004-SNIaProgenitors} or bimodal \citep{Mannucci2006-TwoPopulations} DTDs where the majority of SNe Ia explode within a relatively narrow range of delay times.
@@
 In principle, the observed chemical abundance patterns should therefore contain information about the SN Ia DTD, and by extension their progenitors.
+A striking feature of the [O/Fe] distribution in the Milky Way is the distinct separation into two components, the high- and low-$\alpha$ sequences [references].
+[Introduce other MW disk features].
+
 A few studies have compared different DTDs in one-zone chemical evolution models, but their comparisons to abundance data are limited to the local solar neighborhood \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
-[Talk about \citep{Matteucci2009-DTDModels} multi-zone models].
+[Talk about \citet{Matteucci2009-DTDModels} multi-zone models].
 \citet{Poulhazan2018-PrecisionPollution} compared six DTDs in a cosmological smoothed-particle hydrodynamics simulation.
@@
         % DTD
-        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & Delay time distribution of Type Ia supernovae \\
+        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & delay-time distribution of Type Ia supernovae \\
         t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
@@
 
-\subsection{Delay Time Distributions}
+\subsection{Delay-Time Distributions}
 \label{sec:dtd-models}
@@
     \includegraphics{figures/delay_time_distributions.pdf}
-    \caption{Selection of models for the SN Ia delay time distribution (DTD) used in this paper.
+    \caption{Selection of models for the SN Ia delay-time distribution (DTD) used in this paper.
 All functions are normalized such that $f_{\rm Ia}(t=1\,{\rm Gyr})=1$.
@@
     \centering
-    \caption{Summary of SN Ia delay time distributions (DTDs) explored in this paper.}
+    \caption{Summary of SN Ia delay-time distributions (DTDs) explored in this paper.}
     \label{tab:dtds}
@@
 In this section, we compare the results from one-zone models which examine various parameters of the DTD while keeping other parameters fixed.
+We use the outputs of our one-zone models to identify the regions in chemical abundance space which are most sensitive to the DTD.
 
@@
     \textit{Right columns:} comparison between the power-law ($\alpha=-1.4$) and exponential ($\uptau_{\rm Ia}=3$ Gyr) DTDs with the inside-out SFH.
-[Add: noticeable but subtle change in inner-galaxy peak and tail between DTDs]}
+The MDFs in the inner Galaxy show the greatest change between the DTDs.}
     \label{fig:feh-df-comparison}
@@
 This so-called ``gas-starved ISM'' effect drives a faster increase in metallicity \citep[see analytic demonstration in][]{Weinberg2017-ChemicalEquilibrium}, which ultimately lowers the number of low-metallicity stars.
-The more extended the DTD< the stronger the effect.
+The more extended the DTD, the stronger the effect.
 The outer disk is less affected by the choice of DTD, though, due to the more extended SFH.
-
-While there are some {\it quantitative} differences in how the shape of the MDF varies with Galactic region, the {\it qualitative} trends are unaffected by the choice of model SFH or DTD.
-These trends are primarily driven by chemical equilibrium, abundance gradients, and radial migration \citepalias[][see their Section 3.2 for further discussion]{Johnson2021-Migration}.
 
@@
 However, the difference between the best-scoring model and the worst (late-burst SFH with triple-evolution DTD) is fairly small.
-The quantitative agreement between the predicted and observed MDFs is primarily affected by the assumption of chemical equilibrium, the abundance gradient, and radial migration (see discussion in section 3.2 of \citetalias{Johnson2021-Migration}).
+While there are some {\it quantitative} differences in how the shape of the MDF varies with Galactic region, the {\it qualitative} trends are unaffected by the choice of model SFH or DTD.
+These trends are primarily driven by the assumption of chemical equilibrium, the abundance gradient, and radial migration (see discussion in section 3.2 of \citetalias{Johnson2021-Migration}).
 
@@
 
-A striking feature of the [O/Fe] distribution in the Milky Way is the distinct separation into two components, the high- and low-$\alpha$ sequences [references].
+[Intro, connect to previous paragraph].
 The relative prominence of the two peaks varies with $R_{\rm gal}$ and $|z|$, as shown by the right-hand panels of Figures \ref{fig:ofe-df-sfh} and \ref{fig:ofe-df-dtd}.
@@
 \begin{itemize}
-
     \item Our diagnostics consistently favor a DTD with a large fraction of delayed SNe Ia, such as the 3 Gyr exponential, 1 Gyr plateau, or triple system evolution models, over a DTD with a high number of prompt SNe Ia, such as the $t^{-1.4}$ power-law or two-population models.
@@
 
-    \item While the choice of DTD cannot produce a bimodal distribution of [O/Fe], it can affect the shape of the distribution, the ratio of high-$\alpha$ to low-$\alpha$ stars, and the location of the high-$\alpha$ sequence if it exists.
+    \item The SFH is the critical factor for producing a bimodal [O/Fe] distribution at fixed [Fe/H].
+On its own, the DTD cannot produce a bimodal [O/Fe] distribution that matches what is observed, but it does affect the location and strength of the high-$\alpha$ sequence, potentially enhancing the $\alpha$-bimodality resulting from the choice of SFH.
+    % While the choice of DTD cannot produce a bimodal distribution of [O/Fe], it can affect the shape of the distribution, the ratio of high-$\alpha$ to low-$\alpha$ stars, and the location of the high-$\alpha$ sequence if it exists.
 The SFH is the critical determining factor in bimodality.
@@
 
-    \item Something about how radial migration can't produce bimodality on its own.
-
+    \item Radial migration on its own cannot reproduce the $\alpha$-bimodality. [Should we include this? It's basically already stated in James' migration paper]
 \end{itemize}
 
-Future work
-\begin{itemize}
-    \item Metallicity-dependent DTD normalization and/or shape.
-    \item [Evidence for metallicity-dependent rates of SNe Ia \citet{Gandhi2022-MetallicityDependentRates,Johnson2023-Binaries} and CC SNe \citep{Pessi2023-MetalDepCCSNe}].
-\end{itemize}
-
-We need to constrain DTD or galactic SFH better. With SDSS-V, the latter seems much more achievable.
+% Future work
+Recent studies have shown that the high specific SN Ia rates observed in low-mass galaxies \citep[e.g.,][]{Brown2019-ASASSNrates,Wiseman2021-DESRates} can be explained by a metallicity-dependent rate of SNe Ia \citep{Gandhi2022-MetallicityDependentRates,Johnson2023-Binaries}.
+A similar metallicity dependence has also been observed in the rate of CC SNe \citep{Pessi2023-MetalDepCCSNe}.
+The consequences of a metallicity-dependent SN Ia rate in the context of a multi-zone GCE simulation with radial migration could be explored in a future paper.
+A metallicity dependence on the {\it shape} of the DTD could also be interesting to explore, for example if binary evolution leads to different progenitor systems at low and high metallicity.
+
+Our results indicate that the range of parameter space in the DTD is still too broad to be completely constrained by GCE models.
+Future constraints on the DTD may come from the Legacy Survey of Space and Time (LSST) at the Vera Rubin Observatory [cite], which is expected to observe 10 million [?] SNe during its X-year run.
+On the other hand, better constraints on the Galactic SFH provided by SDSS-V [cite] will enable future GCE studies to constrain the DTD at a higher confidence.
 
 \begin{acknowledgments}
-    LOD thanks Dr.\ David Weinberg and attendees of OSU's Galaxy Hour for many useful discussions over the course of this project.
+    We thank Prof.\ David H.\ Weinberg and attendees of OSU's Galaxy Hour for many useful discussions over the course of this project.
     [Personal acknowledgements]
+
+    LOD and JAJ acknowledge support from National Science Foundation grant no.\ AST-2307621. JAJ and JWJ acknowledge support from National Science Foundation grant no.\ AST-1909841.
+    LOD acknowledges financial support from an Ohio State University Fellowship.
+    JWJ acknowledges financial support from an Ohio State University Presidential Fellowship and a Carnegie Theoretical Astrophysics Center postdoctoral fellowship.
 
@@
     [Carnegie land acknowledgement]
-
-    LOD and JAJ acknowledge support from NSF grant 2307621. JAJ and JWJ acknowledge support from NSF grant 1909841.
-    JWJ acknowledges financial support from an Ohio State University Presidential Fellowship and a Carnegie Theoretical Astrophysics Center postdoctoral fellowship.
     % Software acknowledgements if not a AAS journal

### 2024-03-22 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{xcolor}
-\usepackage{upgreek}
+% \usepackage{upgreek}
 \let\tablenum\relax
@@
         \Delta R_{\rm gal}  & N/A       & \ref{app:migration} & Change in orbital radius due to stellar migration \\
-        p(\Delta R_{\rm gal}|\uptau,R_{\rm form}) & Equation \ref{eq:radial-migration}    & \ref{app:migration} & Probability density function of radial migration distance \\
+        p(\Delta R_{\rm gal}|\tau,R_{\rm form}) & Equation \ref{eq:radial-migration}    & \ref{app:migration} & Probability density function of radial migration distance \\
         z                   & [-3, 3] kpc                & \ref{app:migration} & Distance from Galactic midplane at present day \\
-        p(z|\uptau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
+        p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
         \Delta t        & 10 Myr    & \ref{sec:multizone-results} & Time-step size \\
@@
         f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the late-burst SFR \\
-        \uptau_{\rm rise}             & 2 Gyr     & \ref{sec:sfh} & SFR rise timescale for inside-out and early-burst models \\
-        \uptau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the early-burst SFE timescale \\
+        \tau_{\rm rise}             & 2 Gyr     & \ref{sec:sfh} & SFR rise timescale for inside-out and early-burst models \\
+        \tau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the early-burst SFE timescale \\
         f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the early-burst IFR \\
@@
         % One-zone parameters
-        \uptau_\star                    & 2 Gyr & \ref{sec:onezone-results} & SFE timescale in one-zone models \\
+        \tau_\star                    & 2 Gyr & \ref{sec:onezone-results} & SFE timescale in one-zone models \\
         \eta(R_{\rm gal}=8\,{\rm kpc})  & 2.15  & \ref{sec:onezone-results} & Outflow mass-loading factor at the solar annulus \\
-        \uptau_{\rm sfh}(R_{\rm gal}=8\,{\rm kpc})    & 15.1 Gyr  & \ref{sec:sfh} & SFH timescale at the solar annulus \\
+        \tau_{\rm sfh}(R_{\rm gal}=8\,{\rm kpc})    & 15.1 Gyr  & \ref{sec:sfh} & SFH timescale at the solar annulus \\
     \enddata
@@
         Two-population  & \ref{eq:prompt-dtd}   & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
-                        &                       & $\uptau_{\rm Ia}=3$ Gyr & \\
+                        &                       & $\tau=3$ Gyr & \\
         Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
@@
                                                       \citet{Wiseman2021-DESRates}              \\
-        Exponential & \ref{eq:exponential-dtd}  & $\uptau_{\rm Ia}=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
+        Exponential & \ref{eq:exponential-dtd}  & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
                                                                       \citet{Schonrich2009-RadialMixing};       \\
                     &                           &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
-        Exponential & \ref{eq:exponential-dtd}  & $\uptau_{\rm Ia}=3$ Gyr   & --- \\
+        Exponential & \ref{eq:exponential-dtd}  & $\tau=3$ Gyr   & --- \\
         Plateau     & \ref{eq:plateau-dtd}  & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
@@
 \begin{equation}
-    f_{\rm Ia}^{\rm twopop}(t) = 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\uptau}\Big]
+    f_{\rm Ia}^{\rm twopop}(t) = 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
     \label{eq:prompt-dtd}
 \end{equation}
-To approximate the DTD from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\uptau_{\rm Ia}=3$ Gyr, which results in $\sim 50\%$ of SNe Ia exploding within $t<100$ Myr.
+To approximate the DTD from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in $\sim 50\%$ of SNe Ia exploding within $t<100$ Myr.
 As we illustrate in Figure \ref{fig:dtds}, the two-population DTD has a shorter median delay time than most other models (except the power-law with $\alpha=-1.4$, not shown).
@@
 
-\paragraph{Exponential} An exponentially declining DTD with timescale $\uptau_{\rm Ia}$:
-\begin{equation}
-    f_{\rm Ia}^{\rm exp}(t) = e^{-t/\uptau_{\rm Ia}}
+\paragraph{Exponential} An exponentially declining DTD with timescale $\tau$:
+\begin{equation}
+    f_{\rm Ia}^{\rm exp}(t) = e^{-t/\tau}
     \label{eq:exponential-dtd}
@@
 This model allows analytic solutions to the abundances as a function of time for some SFHs, making it a popular choice.
-\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assume an exponential DTD with a timescale $\uptau_{\rm Ia}=1.5$ Gyr.
-We show in Appendix \ref{app:analytical-dtds} that a $\uptau_{\rm Ia}=1.5$ Gyr exponential is an adequate approximation for the analytical SD DTD from \citet{Greggio2005-AnalyticalRates}.
+\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assume an exponential DTD with a timescale $\tau=1.5$ Gyr.
+We show in Appendix \ref{app:analytical-dtds} that a $\tau=1.5$ Gyr exponential is an adequate approximation for the analytical SD DTD from \citet{Greggio2005-AnalyticalRates}.
 There is less observational support for an exponential DTD.
 \citet{Strolger2020-ExponentialDTD}, fitting to the cosmic SFH and SFHs from field galaxies, find a range of exponential-like solutions with timescales $\sim 1.5 - 6$ Gyr.
-In this paper, we investigate timescales $\uptau_{\rm Ia}=1.5$ and 3 Gyr.
+In this paper, we investigate timescales $\tau=1.5$ and 3 Gyr.
 
@@
 % The first two models are taken from \citetalias{Johnson2021-Migration} and 
-are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_\star$ is prescribed along with the star formation efficiency (SFE) timescale $\uptau_\star\equiv \Sigma_g/\dot\Sigma_\star$.
+are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_\star$ is prescribed along with the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g/\dot\Sigma_\star$.
 The remaining quantities, infall rate (IFR) surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
-The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\uptau_\star$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in SFR mode).
+The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\tau_\star$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in SFR mode).
 The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified.
@@
     \includegraphics[width=\linewidth]{figures/star_formation_histories.pdf}
-    \caption{The surface densities of star formation $\dot \Sigma_\star$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\uptau_\star$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
+    \caption{The surface densities of star formation $\dot \Sigma_\star$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\tau_\star$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
 In each panel, we plot curves for the model zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
@@
 \begin{equation}
-    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\uptau_{\rm rise}}) e^{-t/\uptau_{\rm sfh}},
+    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm sfh}},
     \label{eq:insideout-sfh}
 \end{equation}
-where we assume $\uptau_{\rm rise}=2$ Gyr for all radii.
-The SFH timescale $\uptau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\uptau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the solar annulus and longer timescales in the outer Galaxy.
-The $\uptau_{\rm sfh} - R_{\rm gal}$ relation is based on the radial gradients in stellar age in Milky Way-like spirals measured by \citet[][see Section 2.5 of \citetalias{Johnson2021-Migration} for details]{Sanchez2020-StarFormationTimescales}.
+where we assume $\tau_{\rm rise}=2$ Gyr for all radii.
+The SFH timescale $\tau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\tau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the solar annulus and longer timescales in the outer Galaxy.
+The $\tau_{\rm sfh} - R_{\rm gal}$ relation is based on the radial gradients in stellar age in Milky Way-like spirals measured by \citet[][see Section 2.5 of \citetalias{Johnson2021-Migration} for details]{Sanchez2020-StarFormationTimescales}.
 
@@
 Evidence for a recent star formation burst $\sim 2-3$ Gyr ago has been found in {\it Gaia} \citep{Mor2019-Starburst} and in massive WDs in the solar neighborhood \citep{Isern2019-Starburst}.
-Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr. The determination of $\uptau_{\rm sfh}$ 
+Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr. The determination of $\tau_{\rm sfh}$ 
 % and the normalization of the SFR as a function of $R_{\rm gal}$ 
@@
 \begin{equation}
-    \frac{\uptau_{\rm EB}}{1\,\rm{Gyr}} =
+    \frac{\tau_{\rm EB}}{1\,\rm{Gyr}} =
     \begin{cases}
@@
 \begin{equation}
-    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\uptau_{\rm sfh}},
+    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}},
     \label{eq:earlyburst-ifr}
 \end{equation}
-where $\uptau_{\rm sfh}$ is the same as in the inside-out case.
-To calculate $\dot \Sigma_\star$ from the above quantities, we modify the fiducial star formation law adopted from \citetalias{Johnson2021-Migration}, substituting $\uptau_{\rm EB}$ for the SFE timescale of molecular gas:
+where $\tau_{\rm sfh}$ is the same as in the inside-out case.
+To calculate $\dot \Sigma_\star$ from the above quantities, we modify the fiducial star formation law adopted from \citetalias{Johnson2021-Migration}, substituting $\tau_{\rm EB}$ for the SFE timescale of molecular gas:
 \begin{equation}
@@
     \begin{cases}
-        \Sigma_g \uptau_{\rm EB}^{-1}, & \Sigma_g \geq \Sigma_{g,2} \\
-        \Sigma_g \uptau_{\rm EB}^{-1} \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
-        \Sigma_g \uptau_{\rm EB}^{-1} \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1},
+        \Sigma_g \tau_{\rm EB}^{-1}, & \Sigma_g \geq \Sigma_{g,2} \\
+        \Sigma_g \tau_{\rm EB}^{-1} \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
+        \Sigma_g \tau_{\rm EB}^{-1} \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1},
     \end{cases}
@@
     \label{eq:twoinfall-ifr}
-    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\uptau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\uptau_2},
+    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2},
 \end{equation}
@@
 %         % $\eta$            & 2.15      & Outflow mass-loading factor \\
-%         % $\uptau_\star$        & 2.0 Gyr   & SFE timescale \\
+%         % $\tau_\star$        & 2.0 Gyr   & SFE timescale \\
 %         $\dot M_r$        & continuous    & Recycling rate \\
@@
 %         % $\dot M_\star(t)$     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
-%         % $\uptau_{\rm rise}$ & 2.0 Gyr     & SFR rise timescale \\
-%         % $\uptau_{\rm sfh}$  & 15.1 Gyr  & SFR exponential \\
+%         % $\tau_{\rm rise}$ & 2.0 Gyr     & SFR rise timescale \\
+%         % $\tau_{\rm sfh}$  & 15.1 Gyr  & SFR exponential \\
 %         \hline
@@
 For consistency, we adopt most of the parameter values from Table \ref{tab:multizone-parameters} for our one-zone models.
-We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\uptau_{\rm rise}=2$ Gyr and $\uptau_{\rm sfh}=15.1$ Gyr) and an SFE timescale $\uptau_\star\equiv M_g/\dot M_\star=2$ Gyr.
+We adopt the inside-out SFR (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr) and an SFE timescale $\tau_\star\equiv M_g/\dot M_\star=2$ Gyr.
 Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_\star=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time $t_D=40$ Myr.
@@
     % The dotted, dashed, and solid curves represent models with $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively. 
-    For reference, the solid gray curve represents an exponential DTD with $\uptau_{\rm Ia}=3$ Gyr. 
-    \textit{Center:} Three models which assume an exponential DTD with varying timescale $\uptau_{\rm Ia}$. 
-    % The solid, dashed, and dotted curves represent $\uptau=6$, 3, and 1.5 Gyr, respectively.
+    For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr. 
+    \textit{Center:} Three models which assume an exponential DTD with varying timescale $\tau$. 
+    % The solid, dashed, and dotted curves represent $\tau=6$, 3, and 1.5 Gyr, respectively.
     \textit{Right:} Three models which assume a plateau DTD with varying plateau width $W$. 
@@
     All assume a post-plateau slope of $\alpha=-1.1$.
-For reference, the solid gray curve represents an exponential DTD with $\uptau_{\rm Ia}=3$ Gyr, and the dotted purple curve represents a power-law DTD with $\alpha=-1.1$ and no plateau.}
+For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted purple curve represents a power-law DTD with $\alpha=-1.1$ and no plateau.}
     \label{fig:onezone-threepanel}
@@
 The effect on the [O/Fe] DF is similar to the previous two models: a longer plateau raises the median delay time, resulting in a smaller low-$\alpha$ peak and a more prominent high-$\alpha$ tail.
-The abundance tracks from several different plateau widths fill the space in between the exponential ($\uptau_{\rm Ia}=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
-The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\uptau_{\rm Ia}=3$ Gyr), although the [O/Fe] DFs are somewhat more distinct, with the plateau model producing a peak closer to the power-law case.
+The abundance tracks from several different plateau widths fill the space in between the exponential ($\tau=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
+The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\tau=3$ Gyr), although the [O/Fe] DFs are somewhat more distinct, with the plateau model producing a peak closer to the power-law case.
 
@@
     \caption{\textit{Left:} Comparison of one-zone models with different minimum delay times $t_D$ and DTDs.
-    % minimum SN Ia delay times $t_D=40$ Myr (solid) and 150 Myr (dashed curves) for three DTDs: power-law with $\alpha=-1.1$ (blue), plateau with $W=0.3$ Gyr (green), and exponential with $\uptau_{\rm Ia}=1.5$ Gyr (purple curves).
+    % minimum SN Ia delay times $t_D=40$ Myr (solid) and 150 Myr (dashed curves) for three DTDs: power-law with $\alpha=-1.1$ (blue), plateau with $W=0.3$ Gyr (green), and exponential with $\tau=1.5$ Gyr (purple curves).
     The layout is similar to Figure \ref{fig:onezone-threepanel}. For clarity, we assume a mass-loading factor $\eta=1$ for the exponential DTD curves, which places the end-point at higher [Fe/H].
     \textit{Right:} Comparison of one-zone models with five different forms for the DTD.
-    % : triple-system (yellow), plateau with $W=1$ Gyr (cyan), exponential with $\uptau_{\rm Ia}=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
+    % : triple-system (yellow), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
     }
@@
 In Figure \ref{fig:onezone-twopanel}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (dashed purple line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (solid green line), and their [O/Fe] DFs are virtually identical.
-The difference between the two values of $t_D$ for the exponential ($\uptau_{\rm Ia}=3$ Gyr) DTD in both the abundance tracks and distributions is nearly indistinguishable.
+The difference between the two values of $t_D$ for the exponential ($\tau=3$ Gyr) DTD in both the abundance tracks and distributions is nearly indistinguishable.
 We do not consider the effect on the other DTDs because a 150 Myr minimum delay time is incompatible with the two-population model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD due to its low SN Ia rate at short delay times.
@@
 The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is a result of the delayed exponential component.
-The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\uptau_{\rm Ia}=1.5$ Gyr) models occupy the intermediate space between these extremes.
+The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models occupy the intermediate space between these extremes.
 On the other hand, the [O/Fe] DF from the exponential model has the strongest peak, while the plateau ($W=1$ Gyr) and triple-system models produce nearly identical distributions in the low-$\alpha$ regime.
 The power-law ($\alpha=-1.1$) and two-population DTDs produce similar [O/Fe] DFs despite notably different abundance tracks.
-The exponential ($\uptau_{\rm Ia}=3$ Gyr) and plateau ($W=0.3$ Gyr) models, while not shown, produce similar abundance tracks to the plateau ($W=1$ Gyr) and exponential ($\uptau_{\rm Ia}=1.5$ Gyr) models, respectively.
+The exponential ($\tau=3$ Gyr) and plateau ($W=0.3$ Gyr) models, while not shown, produce similar abundance tracks to the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models, respectively.
 
@@
 Degeneracies between models in one regime can be resolved in the other.
-For example, the exponential ($\uptau_{\rm Ia}=3$ Gyr) and plateau ($W=1$ Gyr) DTDs are indistinguishable in [O/Fe]--[Fe/H] space but predict different [O/Fe] DFs.
+For example, the exponential ($\tau=3$ Gyr) and plateau ($W=1$ Gyr) DTDs are indistinguishable in [O/Fe]--[Fe/H] space but predict different [O/Fe] DFs.
 Of course, both of these observables are also greatly affected by the parameters of the SFH.
@@
 All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:sample}) and smoothed with a box-car width of 0.2 dex.
-    \textit{Left columns:} comparison between the inside-out and two-infall SFHs; both assume the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD. 
+    \textit{Left columns:} comparison between the inside-out and two-infall SFHs; both assume the exponential ($\tau=1.5$ Gyr) DTD. 
     \textit{Center column:} the distributions from APOGEE DR17 for reference, binned and smoothed similarly.
-    \textit{Right columns:} comparison between the power-law ($\alpha=-1.4$) and exponential ($\uptau_{\rm Ia}=3$ Gyr) DTDs with the inside-out SFH.
+    \textit{Right columns:} comparison between the power-law ($\alpha=-1.4$) and exponential ($\tau=3$ Gyr) DTDs with the inside-out SFH.
 The MDFs in the inner Galaxy show the greatest change between the DTDs.}
@@
 Figure \ref{fig:feh-df-comparison} shows MDFs across the Galaxy for a selection of models and APOGEE data.
-The two left-hand columns show MDFs from our models which assume the same DTD (exponential with $\uptau_{\rm Ia}=1.5$ Gyr) but different SFHs.
+The two left-hand columns illustrate the effect of different SFHs on the model outputs.
+The effect of the SFH is most pronounced in the MDFs for the inner Galaxy.
+Near the midplane, the two-infall SFH produces a distinct bump $\sim0.4$ dex below the MDF peak, which is not seen for the inside-out SFH.
+Away from the midplane, the low-metallicity tail is slightly more pronounced for the two-infall than the inside-out model, and the two-infall MDFs extend to slightly higher metallicity.
+In the outer Galaxy, though, the MDFs produced by the two models are nearly identical.
+The shift in the peak metallicity from the inner to the outer Galaxy is unaffected by the choice of SFH, as is the shift in skewness of the MDFs.
+% The two left-hand columns show MDFs from models with different SFHs which assume the same DTD (exponential with $\tau=1.5$ Gyr).
 For comparison, the APOGEE MDFs are binned similarly and presented in the center column of Figure \ref{fig:feh-df-comparison}.
-The two right-hand columns
+The two right-hand columns show MDFs from models with
 
 Holding the SFH fixed, varying the DTD has minimal influence on these MDFs for fixed SFH.
-The two right-hand columns of Figure \ref{fig:feh-df-comparison} plot the MDFs for two multi-zone models, which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\uptau_{\rm Ia}=3$ Gyr.
+The two right-hand columns of Figure \ref{fig:feh-df-comparison} plot the MDFs for two multi-zone models, which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
 The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of explosions occurring within 1 Gyr in the former but only $\sim 30\%$ in the latter.
 % Nevertheless, while the former DTD produces a slightly narrower MDF in the inner Galaxy than the latter, the magnitude of this difference is much smaller than other factors.
-However, the effect on the MDF is interestingly small given this difference. The steep power-law leads to an MDF at small radii that is only slightly narrower than the extended exponential.
+However, the effect on the MDF is interestingly small given this difference.
+The steep power-law leads to an MDF at small $R_{\rm gal}$ that is only slightly narrower than the extended exponential (made apparent by the higher peak of the normalized MDF).
+This tracks with our findings from one-zone models in Section \ref{sec:onezone-results} that the DTD has a smaller effect on the MDF than other observables.
 
@@
 
-The model combination with the best (lowest) score for the MDF is the two-infall SFH with the exponential ($\uptau_{\rm Ia}=3$ Gyr) DTD.
+The model combination with the best (lowest) score for the MDF is the two-infall SFH with the exponential ($\tau=3$ Gyr) DTD.
 The choice of SFH has a larger effect on the overall score than the DTD, and the best-performing SFH is the two-infall model, followed closely by the early-burst.
@@
     \caption{Distributions of [O/Fe] from multi-zone models with different SFHs.
-All assume the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD.
+All assume the exponential ($\tau=1.5$ Gyr) DTD.
 The format of each panel is the same as in Figure \ref{fig:feh-df-comparison}, except that all distributions are smoothed with a box-car width of 0.05 dex.
@@
 As such, its shape is greatly affected by both the SFH and DTD.
-Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs compared to the distributions measured by APOGEE, all assuming an exponential DTD with $\uptau_{\rm Ia}=1.5$ Gyr.
+Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs compared to the distributions measured by APOGEE, all assuming an exponential DTD with $\tau=1.5$ Gyr.
 We see similar trends with Galactic region across all four models.
@@
     \textit{Top row:} results from five multi-zone models which assume the late-bust SFH but different DTDs.
-\textit{Bottom row}: the first four panels compare the four SFHs, all assuming an exponential DTD with $\uptau_{\rm Ia}=1.5$ Gyr.
+\textit{Bottom row}: the first four panels compare the four SFHs, all assuming an exponential DTD with $\tau=1.5$ Gyr.
 The bottom-right panel (highlighted) plots data from APOGEE DR17 for reference.}
@@
 We calculate the prominence, or vertical distance between a peak and its highest neighboring trough, and adopt an arbitrary threshold of 0.1.
-Five of the eight DTDs (four of the five shown, plus the exponential form with $\uptau_{\rm Ia}=3$ Gyr) exceed this prominence threshold, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
+Five of the eight DTDs (four of the five shown, plus the exponential form with $\tau=3$ Gyr) exceed this prominence threshold, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
 Panel (b) shows that the power-law ($\alpha=-1.1$) DTD produces a marginal high-$\alpha$ peak, although it doesn't meet the prominence threshold because it is too close to the low-$\alpha$ peak.
@@
 
-Panels (f)--(i) in the bottom row of Figure \ref{fig:ofe-bimodality} illustrate the effect of the SFH on the [O/Fe] bimodality with the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD.
+Panels (f)--(i) in the bottom row of Figure \ref{fig:ofe-bimodality} illustrate the effect of the SFH on the [O/Fe] bimodality with the exponential ($\tau=1.5$ Gyr) DTD.
 The inside-out SFH does not produce a bimodal distribution for any of our DTDs.
@@
     \caption{A comparison of the [O/Fe]--[Fe/H] plane between the four SFHs in our multi-zone models.
-All assume the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD.
+All assume the exponential ($\tau=1.5$ Gyr) DTD.
 Each panel plots a random mass-weighted sample of 10,000 star particles in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by $R_{\rm gal}$ at birth.
@@
 Figure \ref{fig:ofe-feh-sfh} compares the [O/Fe]--[Fe/H] plane in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) between our four model SFHs.
-All models presented in this figure assume an exponential DTD with $\uptau_{\rm Ia}=1.5$ Gyr, as it lies in the middle in terms of balance between prompt and delayed SNe Ia.
+All models presented in this figure assume an exponential DTD with $\tau=1.5$ Gyr, as it lies in the middle in terms of balance between prompt and delayed SNe Ia.
 The black curves represent the ISM abundance as a function of time in the central zone; in the absence of radial migration, all simulated stellar populations would lie along these lines.
@@
 For these models, the simulated stellar abundances are reasonably well-aligned with the APOGEE contours at low $|z|$ (bottom panels), but they entirely miss the observed high-$\alpha$ sequence at high $|z|$ (top panels).
-In the center column, the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD produces a distribution which aligns quite well with the APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to large [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
+In the center column, the exponential ($\tau=1.5$ Gyr) DTD produces a distribution which aligns quite well with the APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to large [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
 While it does better at populating the high-$\alpha$ sequence than the previous DTDs, the bulk of the simulated populations at large $|z|$ still fall below the APOGEE 30\% contour (top panel).
@@
     \caption{A comparison of the age--[O/Fe] relation between multi-zone models with different SFHs.
-All assume the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD.
+All assume the exponential ($\tau=1.5$ Gyr) DTD.
 Each panel plots a random mass-weighted sample of 10,000 star particles in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
@@
 Figure \ref{fig:age-ofe-sfh} compares the stellar age and [O/Fe] distributions in the solar neighborhood between our four SFHs.
-Similar to Figure \ref{fig:ofe-feh-sfh}, all four panels assume an exponential DTD with $\uptau_{\rm Ia}=1.5$ Gyr.
+Similar to Figure \ref{fig:ofe-feh-sfh}, all four panels assume an exponential DTD with $\tau=1.5$ Gyr.
 We include age data from \citetalias{Leung2023-Ages} for qualitative comparison, though we caution against drawing strong conclusions because we don't correct for selection effects or systematics in the neural net ages.
@@
 Moving to stars at low $|z|$, our plateau ($W=1$ Gyr) and triple-system DTDs over-produce stars at the old, high-$\alpha$ end of the distribution, while also diverging significantly from the observed sequence near solar [O/Fe].
-The exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD comes closest to reproducing the observed range in [O/Fe], while the two DTDs with the shortest median delay time once again produce a smaller range of [O/Fe] than observed.
+The exponential ($\tau=1.5$ Gyr) DTD comes closest to reproducing the observed range in [O/Fe], while the two DTDs with the shortest median delay time once again produce a smaller range of [O/Fe] than observed.
 We note that the break between the linear and flat parts of the relation is sharpest for the exponential DTD, and a more gradual transition is observed for the other four DTDs.
 This could be because the exponential DTD is most dominant at intermediate delay times ($t\sim 1-3$ Gyr) but falls off much faster than the other models at long delay times, so the evolution of [O/Fe] is quite slow for lookback times $\lesssim 5$ Gyr.
-Overall, the exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD most closely matches the data for stars with $0\leq|z|<1$ kpc.
+Overall, the exponential ($\tau=1.5$ Gyr) DTD most closely matches the data for stars with $0\leq|z|<1$ kpc.
 
@@
 \begin{equation}
-    \Delta\uptau_{\rm RMS} \equiv \sqrt{\frac{\sum_k \Delta\uptau_k^2 n_{{\rm L23},k}}{n_{\rm L23,tot}}}
+    \Delta\tau_{\rm RMS} \equiv \sqrt{\frac{\sum_k \Delta\tau_k^2 n_{{\rm L23},k}}{n_{\rm L23,tot}}}
     \label{eq:age-ofe-score}
 \end{equation}
-where $\Delta\uptau_k=\rm{med}(\uptau_{\rm \vice})-\rm{med}(\uptau_{\rm L23})$ is the difference between the mass-weighted median star particle age in \vice and the median stellar age from \citetalias{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citetalias{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
-As before, the score for the model as a whole is the average of $\Delta \uptau_{\rm RMS}$ across all regions, weighted by the number of stars in the age sample in each region.
+where $\Delta\tau_k=\rm{med}(\tau_{\rm \vice})-\rm{med}(\tau_{\rm L23})$ is the difference between the mass-weighted median star particle age in \vice and the median stellar age from \citetalias{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citetalias{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
+As before, the score for the model as a whole is the average of $\Delta \tau_{\rm RMS}$ across all regions, weighted by the number of stars in the age sample in each region.
 
@@
 The models which perform the best (most \yes's and fewest \no's) are those with the exponential and plateau DTDs.
-It is interesting that the best-scoring DTD overall, the exponential DTD with $\uptau_{\rm Ia}=1.5$ Gyr, is intermediate among all our DTDs in terms of the number of prompt SNe Ia and median delay time, but has the {\it lowest} rate at very long delay times ($\sim10$ Gyr).
+It is interesting that the best-scoring DTD overall, the exponential DTD with $\tau=1.5$ Gyr, is intermediate among all our DTDs in terms of the number of prompt SNe Ia and median delay time, but has the {\it lowest} rate at very long delay times ($\sim10$ Gyr).
 Models with a large fraction of prompt SNe Ia, such as the power-law and two-population DTDs, fare quite poorly, with the steepest power-law ($\alpha=-1.4$) ending up in the bottom tirtile across the board for most of our SFHs.
@@
 They find that, depending on the choice of CSFR, the DTDs of \citet{MatteucciRecchi2001-SNIaTimescale}, \citet{Mannucci2006-TwoPopulations}, \citet{Totani2008-DTD}, and the WIDE DD model of \citet{Greggio2005-AnalyticalRates} can all produce good fits to the observed cosmic SN Ia rate.
-This study provides a useful basis for comparison because the first and last of these DTDs are similar to our exponential ($\uptau_{\rm Ia}=1.5$ Gyr) and plateau ($W=1$ Gyr) DTDs, respectively (see Appendix \ref{app:analytical-dtds} for more discussion); the \citet{Mannucci2006-TwoPopulations} is our two-population DTD; and the \citet{Totani2008-DTD} is a $t^{-1}$ power-law with a minimum delay $t_D=100$ Myr.
-It is noteworthy that the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale} best fits the majority of CSFRs in \citet{Palicio2024-CosmicSNIaRate}, and our similar exponential ($\uptau_{\rm Ia}=1.5$ Gyr) DTD {\it also} performs best across all our SFHs.
+This study provides a useful basis for comparison because the first and last of these DTDs are similar to our exponential ($\tau=1.5$ Gyr) and plateau ($W=1$ Gyr) DTDs, respectively (see Appendix \ref{app:analytical-dtds} for more discussion); the \citet{Mannucci2006-TwoPopulations} is our two-population DTD; and the \citet{Totani2008-DTD} is a $t^{-1}$ power-law with a minimum delay $t_D=100$ Myr.
+It is noteworthy that the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale} best fits the majority of CSFRs in \citet{Palicio2024-CosmicSNIaRate}, and our similar exponential ($\tau=1.5$ Gyr) DTD {\it also} performs best across all our SFHs.
 [Intro sentence].
 \citet{Palicio2024-CosmicSNIaRate} fit combinations of cosmic star formation rates (CSFRs) and DTDs, many of which are similar to the forms in this paper, to the observed cosmic SN Ia rate.
-Notably, the DTD which best fit the majority of their CSFRs was the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale}, which is similar to the exponential form with $\tau_{\rm Ia}=1.5$ Gyr (see Appendix \ref{app:analytical-dtds} for more discussion).
+Notably, the DTD which best fit the majority of their CSFRs was the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale}, which is similar to the exponential form with $\tau=1.5$ Gyr (see Appendix \ref{app:analytical-dtds} for more discussion).
 \citet{Palicio2024-CosmicSNIaRate} are able to exclude DTDs with a very high or very low fraction of prompt SNe Ia, but a number of their DTDs could produce a convincing fit to the observed rates with the right CSFR.
@@
 The right-hand panel of Figure \ref{fig:analytical-dtd} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs.
-We assume $\eta=2.5$, $\uptau_\star=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
+We assume $\eta=2.5$, $\tau_\star=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
 We compare the SD, DD WIDE, and DD CLOSE schemes to standard power-law, broken power-law, and exponential DTDs.

### 2024-03-26 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % \documentclass[modern,linenumbers]{aastex631}
-\documentclass[twocolumn,twocolappendix,linenumbers,trackchanges]{aastex631}
+% \documentclass[twocolumn,twocolappendix,linenumbers,trackchanges]{aastex631}
+\documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
 
@@
 % \author[0000-0001-7775-7261]{David H. Weinberg}
+
+\correspondingauthor{Liam O. Dubay}
+\email{dubay.11@osu.edu}
 
@@
 The uncertainties in the SN Ia DTD propagate into GCE models.
-In principle, the observed chemical abundance patterns should therefore contain information about the SN Ia DTD, and by extension their progenitors.
-A striking feature of the [O/Fe] distribution in the Milky Way is the distinct separation into two components, the high- and low-$\alpha$ sequences [references].
-[Introduce other MW disk features].
+In principle, the observed chemical abundance patterns should therefore contain information about the DTD, and by extension the progenitors of SNe Ia.
+The metallicity distribution function (MDF) and distribution of [O/Fe] record the history of SN Ia enrichment as a function of stellar age and location in the Galaxy.
+A striking feature of the \aFe distribution in the Milky Way disk is the distinct separation into two components, the high- and low-$\alpha$ sequences, at similar metallicity \citep[e.g.,][]{Bensby2014-solarNeighborhoodAbundances}.
+Since the \aFe abundance reflects the ratio of CC SN to SN Ia enrichment, the DTD should have an effect on the \aFe bimodality.
+% [Introduce other MW disk features?]
 
 A few studies have compared different DTDs in one-zone chemical evolution models, but their comparisons to abundance data are limited to the local solar neighborhood \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
-[Talk about \citet{Matteucci2009-DTDModels} multi-zone models].
+=
 \citet{Poulhazan2018-PrecisionPollution} compared six DTDs in a cosmological smoothed-particle hydrodynamics simulation.
-They found that models with a prompt SN Ia component produced the highest abundance ratios and the narrowest \aFe distributions at late times, although their simulation was not tuned to reproduce the parameters of the Milky Way, and they did not compare to observed chemical abundances.
+They found that models with a prompt SN Ia component produced the highest abundance ratios and the narrowest \aFe distributions at late times, although their simulation was not tuned to reproduce the parameters of the Milky Way.%, and they did not compare to observed chemical abundances.
+\citet{Matteucci2009-DTDModels} compared multiple DTDs in a multi-zone GCE model with a two-infall SFH, but were limited by the available data for the solar neighborhood.
 The current era of large spectroscopic surveys such as the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE} and the forthcoming Milky Way Mapper \citep{Kollmeier2017-SDSS-V} has made abundances across the Milky Way disk available for comparison to more sophisticated GCE models.
@@
     \includegraphics[width=\linewidth]{figures/ofe_bimodality_summary.pdf}
-    \caption{The distributions of [O/Fe] along two different slices of [Fe/H]. 
-    % $-0.6\leq$[Fe/H]$<-0.4$ (blue dashed) and $-0.4\leq$[Fe/H]$<-0.2$ (red solid). 
+    \caption{The distributions of [O/Fe] along two different slices of [Fe/H]: $-0.6\leq$[Fe/H]$<-0.4$ (blue dashed) and $-0.4\leq$[Fe/H]$<-0.2$ (red solid). 
     All panels contain stars within the Galactic region defined by $7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc.
@@
 
-[Intro, connect to previous paragraph].
-The relative prominence of the two peaks varies with $R_{\rm gal}$ and $|z|$, as shown by the right-hand panels of Figures \ref{fig:ofe-df-sfh} and \ref{fig:ofe-df-dtd}.
-A crucial feature of this bimodality, which is not apparent in the previous figures, is the presence of both sequences at the same [Fe/H].
-Figure \ref{fig:ofe-bimodality} compares the [O/Fe] distributions in the solar annulus ($7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc) in two bins of [Fe/H] for select model outputs and APOGEE data.
+% [Intro, connect to previous section]. 
+The [O/Fe] distributions from APOGEE in Section \ref{sec:ofe-df}
+% (right-hand panels of Figures \ref{fig:ofe-df-sfh} and \ref{fig:ofe-df-dtd}) 
+show two distinct peaks whose relative prominence varies with $R_{\rm gal}$ and $|z|$.
+A crucial feature of this bimodality, which is not apparent in the analysis of the previous section, is the presence of both sequences {\it at the same [Fe/H]}.
+\citet{Vincenzo2021-AlphaDistribution} demonstrate that, although the APOGEE sample over-represents stars with $|z|\ge1$ which are more likely to be high-$\alpha$, the $\alpha$-bimodality is a real feature of the solar neighborhood population.
+A successful model for the evolution of the Milky Way must be able to reproduce this bimodality.
+
+Figure \ref{fig:ofe-bimodality} compares the [O/Fe] distributions in the solar annulus ($7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc) in two bins of [Fe/H] ($-0.6<{\rm [Fe/H]}<-0.4$ and $-0.4<{\rm [Fe/H]}<-0.2$) for select model outputs and APOGEE data.
 The APOGEE distributions in the bottom-right panel (j) show that the high-$\alpha$ mode is more prominent at lower [Fe/H] and vice versa, but the distributions in both bins are clearly bimodal.
@@
 
-[Reference \citet{Vincenzo2021-AlphaDistribution} for how the bimodality is made stronger by the selection function, but it's not just due to selection effects.
-Describe the re-sampling we do to correct for this.]
-% \citet{Vincenzo2021-AlphaDistribution} demonstrate that the APOGEE selection function makes the observed $\alpha$ bimodality {\it weaker} in that the high-$\alpha$ sequence is undersampled relative to low-$\alpha$ stars.
-For most of our models, the low-$\alpha$ peak is the more prominent of the two, so by performing this resampling we enhance strength of the bimodality.
+To quantify the strength of the $\alpha$-bimodality, we use the peak-finding algorithm {\tt scipy.signal.find\_peaks} \citep{2020SciPy-NMeth}.
+For each peak, we calculate the prominence, or the vertical distance between a peak and its highest neighboring trough.
+We consider a distribution bimodal if both peaks exceed an arbitrary threshold of 0.1.
+The APOGEE distributions exceed this threshold in both [Fe/H] bins.
+
+The top row of panels (a--e) in Figure \ref{fig:ofe-bimodality} shows the [O/Fe] bimodality (or lack thereof) across five different DTDs, all of which assume the late-burst SFH.
+To better approximate the APOGEE selection function, we re-sample our model stellar populations so the $|z|$ distribution closely matches that of APOGEE in the solar neighborhood.
+% For most of our models, the low-$\alpha$ peak is the more prominent of the two, so by performing this resampling we enhance strength of the bimodality.
 However, for some models the high-$\alpha$ peak is the strongest, and the re-sampling process de-emphasizes the low-$\alpha$ peak below the prominence threshold (e.g., panel f of Figure \ref{fig:ofe-bimodality}).
 [Explain why this is ok]
-
-The top row of panels (a--e) in Figure \ref{fig:ofe-bimodality} shows the [O/Fe] bimodality (or lack thereof) across five different DTDs, all of which assume the late-burst SFH.
-To quantify the bimodality, we use the peak-finding algorithm {\tt scipy.signal.find\_peaks} \citep{2020SciPy-NMeth}.
-We calculate the prominence, or vertical distance between a peak and its highest neighboring trough, and adopt an arbitrary threshold of 0.1.
-Five of the eight DTDs (four of the five shown, plus the exponential form with $\tau=3$ Gyr) exceed this prominence threshold, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
+Five of the eight DTDs (four of the five shown, plus the exponential form with $\tau=3$ Gyr) exceed our prominence threshold in the low-[Fe/H] bin, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
 Panel (b) shows that the power-law ($\alpha=-1.1$) DTD produces a marginal high-$\alpha$ peak, although it doesn't meet the prominence threshold because it is too close to the low-$\alpha$ peak.
-
 In general, DTDs with fewer prompt SNe Ia produce a high-$\alpha$ peak which is more prominent and at a higher [O/Fe], as was the case with the [O/Fe] distributions in Section \ref{sec:ofe-df}.
-One major discrepancy is that the APOGEE data show bimodality in both bins of [Fe/H], while the models run with the late-burst SFH only show a clear high-$\alpha$ peak at the low-metallicity ($-0.6<{\rm [Fe/H]}<-0.4$) bin.
-[Talk about why / if this matters]
-
-Panels (f)--(i) in the bottom row of Figure \ref{fig:ofe-bimodality} illustrate the effect of the SFH on the [O/Fe] bimodality with the exponential ($\tau=1.5$ Gyr) DTD.
+
+Panels (f)--(i) in the bottom row of Figure \ref{fig:ofe-bimodality} illustrate the effect of the SFH on the [O/Fe] bimodality.
 The inside-out SFH does not produce a bimodal distribution for any of our DTDs.
-On the other hand, the early-burst SFH {\it always} produces a bimodal distribution in the $-0.4\leq{\rm [Fe/H]}<-0.2$ bin regardless of the assumed DTD, although the lower-metallicity bin does not (the lower peak falls short of our prominence threshold of 0.1).
-
-For models with the late-burst and two-infall SFHs, bimodality is variable depending on the DTD: those with longer median delay times (e.g., exponential, plateau, or triple-system) generally produce a bimodal distribution in the $-0.6\leq{\rm [Fe/H]}<-0.4$ bin, while the power-law DTDs do not.
-None of our SFH+DTD combinations can produce an [O/Fe] distribution which is bimodal in {\it both} bins of [Fe/H] shown in Figure \ref{fig:ofe-bimodality}, as observed in APOGEE (panel j).
+On the other hand, the early-burst SFH {\it always} produces a bimodal distribution in the high-[Fe/H] bin regardless of the assumed DTD, but not in the low-[Fe/H] bin (the small low-$\alpha$ peak falls below our prominence threshold).
+For models with the late-burst and two-infall SFHs, the bimodality is variable depending on the DTD: those with longer median delay times (e.g., exponential, plateau, or triple-system) generally produce a bimodal distribution in the low-[Fe/H] bin, while the power-law DTDs do not.
+
+One major discrepancy in all of our models the breadth of the $\alpha$-bimodality across [Fe/H] space. 
+% In APOGEE, both bins in [Fe/H] show a clearly bimodal distribution of [O/Fe]. 
+Even our most successful models can produce a bimodal [O/Fe] distribution in only one bin: the high-[Fe/H] bin for the early-burst SFH, and the low-[Fe/H] bin for the late-burst and two-infall SFHs.
+In APOGEE, the two sequences are co-extant between ${\rm [Fe/H]}\approx-0.6$, below which the high-$\alpha$ sequence dominates, and ${\rm [Fe/H]}\approx+0.2$, at which point they join.
+The failure of our models to fully reproduce the bimodality across the whole range of [Fe/H] indicates that our picture of the formation of the $\alpha$-bimodality is still incomplete.
 
@@
 
+[Age at the knee, given our age uncertainties, is not a great diagnostic]
+
 % The best, lowest-scoring model in the age--[O/Fe] plane
@@
 
-[Is the MW DTD the same as elsewhere?]
-\citet{Walcher2016-SelfSimilarity} argue that the similarity of the age--[$\alpha$/Fe] relation between solar neighborhood stars and nearby elliptical galaxies is evidence for a universal DTD; between a bimodal, narrow Gaussian, and power-law DTD, they find the latter best explains their data.
+% [Is the MW DTD the same as elsewhere?]
+Our finding that the $t^{-1}$ power-law DTD poorly reproduces observed abundances could signal that the Milky Way and other galaxies obey different DTDs.
+This would not be too far beyond the findings of \citet{Maoz2017-CosmicDTD} that field galaxies and galaxy clusters have a different DTD slope.
+On the other hand, \citet{Walcher2016-SelfSimilarity} argue that the similarity of the age--\aFe relation between solar neighborhood stars and nearby elliptical galaxies is evidence for a universal DTD.
+A physical mechanism would be needed to produce different DTDs in different environments, such as a metallicity dependence in the fraction of close binaries \citep[e.g.,][]{Moe2019-CloseBinaryFraction}.
+
+[Discuss yield effects]
 
@@
 
+[More discussion of \citet{Matteucci2009-DTDModels}, which is multi-zone but only compares to the solar neighborhood, and no radial migration.]
+
 To our knowledge, this paper is the first exploration of a two-infall SFH which incorporates both mass-loading and radial migration.
@@
 
-One curious chemical feature of the Milky Way disk is the existence of two populations separated by their \aFe abundance ratios at similar metallicity \citep[e.g.,][]{Bensby2014-solarNeighborhoodAbundances}.
+% One curious chemical feature of the Milky Way disk is the existence of two populations separated by their \aFe abundance ratios at similar metallicity \citep[e.g.,][]{Bensby2014-solarNeighborhoodAbundances}.
 
@@
 
-\begin{acknowledgments}
+% \begin{acknowledgments}
+\section*{Acknowledgements}
+
 We thank Prof.\ David H.\ Weinberg and attendees of OSU's Galaxy Hour for many useful discussions over the course of this project.
@@
 % This work made use of Astropy:\footnote{http://www.astropy.org} a community-developed core Python package and an ecosystem of tools and resources for astronomy \citep{astropy:2013, astropy:2018, astropy:2022}.
-\end{acknowledgments}
+% \end{acknowledgments}
 
@@
 
-Discuss \citet{Greggio2005-AnalyticalRates} vs our simple function approximations here?
-
-\citet{Greggio2005-AnalyticalRates} derives analytical DTDs for SD and DD progenitor systems from assumptions about binary stellar evolution and outcomes of mass exchange.
-They find that the parameters which have a large effect on the shape of the DTD are the distribution and range of stellar masses in progenitor systems; the efficiency of accretion in the SD scenario; and the distribution of separations at birth in the DD scenario.
-The left-hand panel of Figure \ref{fig:analytical-dtd} shows the analytical DTDs for SD progenitors and two different prescriptions for DD progenitors (``WIDE'' and ``CLOSE'').
-In the ``WIDE'' scheme, it is assumed that there is a wide distribution of ratios $A/A_0$ of the separation of the DD system to the initial separation of the binary, and that the distributions of $A$ and total mass of the system $m_{\rm DD}$ are independent, so one cannot necessarily predict the total merge time of a system based on its initial parameters.
-In the ``CLOSE'' scheme, there is assumed to be a narrow distribution of $A/A_0$ and a correlation between $A$ and $m_{\rm DD}$, so the most massive binaries tend to merge quickly and the least massive merge last.
-
-The right-hand panel of Figure \ref{fig:analytical-dtd} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs.
-We assume $\eta=2.5$, $\tau_\star=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
-We compare the SD, DD WIDE, and DD CLOSE schemes to standard power-law, broken power-law, and exponential DTDs.
-The SD and DD CLOSE DTDs follow nearly identical tracks in [O/Fe] vs [Fe/H]; however, their distributions on [O/Fe] differ at the low end.
-The SD DTD follows an exponential with a 1.5 Gyr timescale, whereas the DD CLOSE DTD is well-approximated by a broken power-law with an initial plateau of 300 Myr and a subsequent declining slope of -1.1.
-The WIDE prescription is likewise best approximated by a broken power-law, but with a longer plateau width of 1 Gyr.
-In all cases, the difference between the analytical DTD and the nearest broken power-law or exponential is likely too small to be observationally detectable, so in our multi-zone models we implement the more generic functions in lieu of the analytical DTDs.
-
-A multi-zone with the \citet{Greggio2005-AnalyticalRates} SD DTD produced nearly identical results to an exponential DTD with a 1.5 Gyr timescale.
-
 \begin{figure*}
@@
 
+Discuss \citet{Greggio2005-AnalyticalRates} vs our simple function approximations here?
+
+\citet{Greggio2005-AnalyticalRates} derives analytical DTDs for SD and DD progenitor systems from assumptions about binary stellar evolution and outcomes of mass exchange.
+They find that the parameters which have a large effect on the shape of the DTD are the distribution and range of stellar masses in progenitor systems; the efficiency of accretion in the SD scenario; and the distribution of separations at birth in the DD scenario.
+The left-hand panel of Figure \ref{fig:analytical-dtd} shows the analytical DTDs for SD progenitors and two different prescriptions for DD progenitors (``WIDE'' and ``CLOSE'').
+In the ``WIDE'' scheme, it is assumed that there is a wide distribution of ratios $A/A_0$ of the separation of the DD system to the initial separation of the binary, and that the distributions of $A$ and total mass of the system $m_{\rm DD}$ are independent, so one cannot necessarily predict the total merge time of a system based on its initial parameters.
+In the ``CLOSE'' scheme, there is assumed to be a narrow distribution of $A/A_0$ and a correlation between $A$ and $m_{\rm DD}$, so the most massive binaries tend to merge quickly and the least massive merge last.
+
+The right-hand panel of Figure \ref{fig:analytical-dtd} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs.
+We assume $\eta=2.5$, $\tau_\star=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
+We compare the SD, DD WIDE, and DD CLOSE schemes to standard power-law, broken power-law, and exponential DTDs.
+The SD and DD CLOSE DTDs follow nearly identical tracks in [O/Fe] vs [Fe/H]; however, their distributions on [O/Fe] differ at the low end.
+The SD DTD follows an exponential with a 1.5 Gyr timescale, whereas the DD CLOSE DTD is well-approximated by a broken power-law with an initial plateau of 300 Myr and a subsequent declining slope of -1.1.
+The WIDE prescription is likewise best approximated by a broken power-law, but with a longer plateau width of 1 Gyr.
+In all cases, the difference between the analytical DTD and the nearest broken power-law or exponential is likely too small to be observationally detectable, so in our multi-zone models we implement the more generic functions in lieu of the analytical DTDs.
+
+A multi-zone with the \citet{Greggio2005-AnalyticalRates} SD DTD produced nearly identical results to an exponential DTD with a 1.5 Gyr timescale.
+
 \section{Stellar Migration}
 \label{app:migration}
-
-For each star particle in \vice, \citetalias{Johnson2021-Migration} randomly assign an analogue star particle from \texttt{h277} and adopt its radial migration distance $\Delta R$ and final midplane distance $z$.
-This allows \vice to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
-However, in regions where the number of h277 star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single h277 star particle can be assigned as an analogue to multiple \vice stellar populations.
-These populations will have similar formation and migration histories and consequently similar abundances, which produces unphysical ``clumps'' of stars in the abundance distributions at high latitudes and large radii.
-
-We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm initial}$ from the \texttt{h277} output in bins of $R_{\rm initial}$ and age.
-Each Gaussian is centered at 0 and we find that the scale $\sigma_{\Delta R}$ is best described by the function
-\begin{equation}
-    \sigma_{\Delta R} = 1.35\,{\rm kpc} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61} \Big(\frac{T}{1\,{\rm Gyr}}\Big)^{0.33}
-    \label{eq:radial-migration}
-\end{equation}
-where $T$ is the age of the star particle.
-
-We fit a sech$^2$ function \citep{Spitzer1942} to the distribution of midplane distances $z$.
-Vertical migration away from the midplane does not affect the chemical evolution model, but we do use $z$ in our analysis.
-The probability density function (PDF) of $z$ given some scale height $h_z$ is
-\begin{equation}
-    {\rm PDF}(z) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z}{2 h_z}\Big)
-    \label{eq:sech-pdf}
-\end{equation}
-and the corresponding cumulative distribution function (CDF) is
-\begin{equation}
-    {\rm CDF}(z) = \frac{1}{1 + e^{-z / h_z}}.
-    \label{eq:sech-cdf}
-\end{equation}
-We fit the above function to the distributions of $z$ in h277 in varying bins of $T$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
-\begin{equation}
-    h_z = (0.25\,{\rm kpc}) 
-    e^{\frac{T-5\,{\rm Gyr}}{7.0\,{\rm Gyr}}}
-    e^{\frac{R_{\rm final}-8\,{\rm kpc}}{6.0\,{\rm kpc}}}.
-    \label{eq:scale-height}
-\end{equation}
-
-When a star particle is created by \vice at initial radius $R_{\rm form}$, we sample its total radial migration distance $\Delta R$ from a Gaussian with a width described by Equation \ref{eq:radial-migration}, and we sample its final midplane distance $z_{\rm final}$ from the distribution described by Equation \ref{eq:sech-pdf} with a width given by Equation \ref{eq:scale-height}.
-The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citetalias{Johnson2021-Migration}, but with a time dependence $\propto \Delta t^{1/3}$.
-This produces distributions of $R_{\rm final}$ and $z_{\rm final}$ which are similar to the analogue migration case for all but the oldest stars.
-
-\citet{Okalidis2022-AurigaMigration} studied the stellar migration in the Auriga simulations and found that the migration strength had both a dependence on age and formation radius.
-They also found that in strongly-barred galaxies, the migration is stronger overall but has a slower timestep evolution than diffusion ($\Delta t^{0.5}$).
-
-Figure \ref{fig:radial-migration} compares the distributions of $R_{\rm final}$ in bins of $R_{\rm form}$ and age between the analogue and Gaussian migration schema.
 
@@
 
+For each star particle in \vice, \citetalias{Johnson2021-Migration} randomly assign an analogue star particle from \texttt{h277} and adopt its radial migration distance $\Delta R$ and final midplane distance $z$.
+This allows \vice to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
+However, in regions where the number of h277 star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single h277 star particle can be assigned as an analogue to multiple \vice stellar populations.
+These populations will have similar formation and migration histories and consequently similar abundances, which produces unphysical ``clumps'' of stars in the abundance distributions at high latitudes and large radii.
+
+We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm initial}$ from the \texttt{h277} output in bins of $R_{\rm initial}$ and age.
+Each Gaussian is centered at 0 and we find that the scale $\sigma_{\Delta R}$ is best described by the function
+\begin{equation}
+    \sigma_{\Delta R} = 1.35\,{\rm kpc} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61} \Big(\frac{T}{1\,{\rm Gyr}}\Big)^{0.33}
+    \label{eq:radial-migration}
+\end{equation}
+where $T$ is the age of the star particle.
+
+We fit a sech$^2$ function \citep{Spitzer1942} to the distribution of midplane distances $z$.
+Vertical migration away from the midplane does not affect the chemical evolution model, but we do use $z$ in our analysis.
+The probability density function (PDF) of $z$ given some scale height $h_z$ is
+\begin{equation}
+    {\rm PDF}(z) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z}{2 h_z}\Big)
+    \label{eq:sech-pdf}
+\end{equation}
+and the corresponding cumulative distribution function (CDF) is
+\begin{equation}
+    {\rm CDF}(z) = \frac{1}{1 + e^{-z / h_z}}.
+    \label{eq:sech-cdf}
+\end{equation}
+We fit the above function to the distributions of $z$ in h277 in varying bins of $T$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
+\begin{equation}
+    h_z = (0.25\,{\rm kpc}) 
+    e^{\frac{T-5\,{\rm Gyr}}{7.0\,{\rm Gyr}}}
+    e^{\frac{R_{\rm final}-8\,{\rm kpc}}{6.0\,{\rm kpc}}}.
+    \label{eq:scale-height}
+\end{equation}
+
+When a star particle is created by \vice at initial radius $R_{\rm form}$, we sample its total radial migration distance $\Delta R$ from a Gaussian with a width described by Equation \ref{eq:radial-migration}, and we sample its final midplane distance $z_{\rm final}$ from the distribution described by Equation \ref{eq:sech-pdf} with a width given by Equation \ref{eq:scale-height}.
+The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citetalias{Johnson2021-Migration}, but with a time dependence $\propto \Delta t^{1/3}$.
+This produces distributions of $R_{\rm final}$ and $z_{\rm final}$ which are similar to the analogue migration case for all but the oldest stars.
+
+\citet{Okalidis2022-AurigaMigration} studied the stellar migration in the Auriga simulations and found that the migration strength had both a dependence on age and formation radius.
+They also found that in strongly-barred galaxies, the migration is stronger overall but has a slower timestep evolution than diffusion ($\Delta t^{0.5}$).
+
+Figure \ref{fig:radial-migration} compares the distributions of $R_{\rm final}$ in bins of $R_{\rm form}$ and age between the analogue and Gaussian migration schema.
+
 \bibliography{bib}

### 2024-03-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \citet{Stahlholdt2022-StarFormationEpochs} find evidence for a burst $\sim10$ Gyr ago which marks the beginning of a second phase of star formation.
-[Something about $\alpha$-bimodality from another paper].
+An early infall-driven burst of star formation has been found to lead to MW-like $\alpha$-bimodality in simulations \citep{Mackereth2018-AlphaBimodality}.
 We adopt the following formula for the time-dependence of the SFE timescale from \citet{Conroy2022-ThickDisk}:
@@
 APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
-We use estimated ages from \citet[][hereafter \citetalias{Leung2023-Ages}]{Leung2023-Ages}, who use a variational encoder-decoder network to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
+We use estimated ages from \citet[][hereafter \citetalias{Leung2023-Ages}]{Leung2023-Ages}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
 Importantly, the \citetalias{Leung2023-Ages} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{Mackereth2019-astroNN-Ages}.
@@
 
-[Subsection introduction]
+% [Subsection introduction]
+As illustrated by the one-zone models in Section \ref{sec:onezone-results}, models which produce similar tracks in abundance space can be distinguished by the rate of their abundance evolution.
+We demonstrated in Section \ref{sec:ofe-df} that the DTD affects the final [O/Fe] distribution, so naturally it should have an effect on the evolution of [O/Fe] with age as well.
+We compare our model stellar age--[O/Fe] relations with age estimates for APOGEE stars from the variational encoder-decoder network of \citetalias{Leung2023-Ages}.
 
@@
 If we remove the two-infall models altogether due to their dominance in the scoring system, our results do not qualitatively change.
+In the age--[O/Fe] plane, the two bursty or discontinuous SFHs, early-burst and two-infall, score much better than the two smooth SFHs.
 The SFHs rank differently in the bimodality test, where the early-burst SFH is able to produce a bimodal [O/Fe] distribution for all DTDs, as discussed in Section \ref{sec:bimodality}.
@@
 
-[Why does two-infall do so well across the board, even in the [Fe/H] and [O/Fe] DFs where it seems worse by eye?]
-Across every diagnostic (except [O/Fe] bimodality), in Table \ref{tab:results}, the two-infall models outperform every other SFH.
+% [Why does two-infall do so well across the board, even in the [Fe/H] and [O/Fe] DFs where it seems worse by eye?]
+Across nearly every observable in Table \ref{tab:results}, the two-infall models outperform every other SFH.
+In some cases this does indicate that the two-infall SFH is more successful at reproducing the observed distributions, as is the case in the age--[O/Fe] plane (Figure \ref{fig:age-ofe-sfh}).
 It is somewhat surprising that the two-infall models score higher than the early-burst even for the [O/Fe] DFs, when the double-peaked distributions produced by the latter are qualitatively closer to the APOGEE data than the former's triple-peaked distributions.
@@
 The first GCE model to incorporate radial mixing was developed by \citet{Schonrich2009-RadialMixing}, and subsequent studies have incorporated more comprehensive numerical treatments of radial migration and the effect of a central bar \citep[e.g.,][]{Minchev2013-ChemodynamicalEvolution}.
-In this paper, we follow the treatment by \citetalias{Johnson2021-Migration}, who [describe treatment].
+%In this paper, we follow the treatment by \citetalias{Johnson2021-Migration}, who [describe treatment].
 
@@
 
+\citet{Mackereth2018-AlphaBimodality} find the appearance of a MW-like bimodality in the EAGLE simulations is rare, occuring in only $\sim5\%$ of their sample.
+
 \section{Conclusions}
@@
 
+We have explored the consequences of eight different DTDs for SNe Ia in combination with four different SFHs in multi-zone GCE models with radial migration.
+We compared our model outputs to abundances from APOGEE and ages from \citetalias{Leung2023-Ages} for stars across the Milky Way disk.
+For each model, we computed a numerical score which reflects the agreement between the model output and the data across the entire disk for five observables.
+Our main conclusions are as follows:
+
 \begin{itemize}
-    \item Our diagnostics consistently favor a DTD with a large fraction of delayed SNe Ia, such as the 3 Gyr exponential, 1 Gyr plateau, or triple system evolution models, over a DTD with a high number of prompt SNe Ia, such as the $t^{-1.4}$ power-law or two-population models.
+    \item The exponential DTD with a timescale of $\tau=1.5$ Gyr is best able to reproduce the observed abundance patterns for all four SFHs.
+
+    \item In general, we favor a DTD with a small fraction of prompt SNe Ia.
+The models with exponential, plateau, and triple-system DTDs perform significantly better than the models with two-population and power-law DTDs across all four SFHs.
+
+    \item The observationally-derived $t^{-1.1}$ power-law DTD produces too few high-$\alpha$ stars.
+This could be mitigated with a longer minimum delay time or the addition of an initial plateau in the DTD at short delay times.
+    % \item Our diagnostics consistently favor a DTD with a large fraction of delayed SNe Ia, such as the 3 Gyr exponential, 1 Gyr plateau, or triple system evolution models, over a DTD with a high number of prompt SNe Ia, such as the $t^{-1.4}$ power-law or two-population models.
 [Discuss the disconnect and/or complement with \citet{Maoz2017-CosmicDTD}, etc.; something about different timescales probed by volumetric surveys vs.
@@
 On its own, the DTD cannot produce a bimodal [O/Fe] distribution that matches what is observed, but it does affect the location and strength of the high-$\alpha$ sequence, potentially enhancing the $\alpha$-bimodality resulting from the choice of SFH.
-    % While the choice of DTD cannot produce a bimodal distribution of [O/Fe], it can affect the shape of the distribution, the ratio of high-$\alpha$ to low-$\alpha$ stars, and the location of the high-$\alpha$ sequence if it exists.
-The SFH is the critical determining factor in bimodality.
-
-    \item The distribution of [Fe/H] depends strongly on the chosen SFH, but there is only a weak effect from the DTD.
-
-    \item The early-burst SFH is the only one which produced a bimodal distribution of [O/Fe] across the disk resembling APOGEE, from the models we investigate.
+Radial migration also cannot reproduce the $\alpha$-bimodality on its own.
+
+    \item The MDF is more sensitive to the choice of SFH than the DTD.
+Overall trends across the Galaxy are primarily driven by the assumed radial abundance gradient and stellar migration prescription, although the MDF in the inner Galaxy is more sensitive to the DTD than elsewhere.
+
+    % \item The early-burst SFH is the only one which produced a bimodal distribution of [O/Fe] across the disk resembling APOGEE, from the models we investigate.
 [Add: summary of why everything else fails.]
-
-    \item Radial migration on its own cannot reproduce the $\alpha$-bimodality. [Should we include this? It's basically already stated in James' migration paper]
 \end{itemize}

### 2024-04-01 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \newcommand{\vice}{{\tt VICE}\xspace}
+\newcommand{\todo}[1]{{\color{red}#1}}
 
@@
 % Author list
-\author[0000-0003-3781-0747]{Liam O. Dubay}
+\author[0000-0003-3781-0747]{Liam O.\ Dubay}
 \affiliation{\osuaffil}
 \affiliation{\ccappaffil}
-\author[0000-0001-7258-1834]{Jennifer A. Johnson}
+\author[0000-0001-7258-1834]{Jennifer A.\ Johnson}
 \affiliation{\osuaffil}
 \affiliation{\ccappaffil}
-\author[0000-0002-6534-8783]{James W. Johnson}
+\author[0000-0002-6534-8783]{James W.\ Johnson}
 \affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
@@
 
-\correspondingauthor{Liam O. Dubay}
+\correspondingauthor{Liam O.\ Dubay}
 \email{dubay.11@osu.edu}
@@
     In standard bracket notation, $[X/Y]\equiv \log_{10}(X/Y) - \log_{10}(X/Y)_{\odot}$.
-In this work we will use \aFe and [O/Fe] interchangeably, although observational studies will often use a combination of $\alpha$-elements to calculate \aFe.
+In this paper we will use \aFe and [O/Fe] interchangeably, although observational studies will often use a combination of $\alpha$-elements to calculate \aFe.
 } ratios seen by, e.g., \citet{Wallerstein1962-GDwarfAbundances} were caused by different stellar lifetimes for the contributors of the Fe-peak elements than the $\alpha$-elements. 
@@
 % By formulating analytical DTDs for several progenitor models, \citet{Greggio2005-AnalyticalRates} found that the SD channel tends to produce a steeper DTD function than the DD channel, and the median delay time (by which 50\% of SNe Ia have exploded) can vary by a factor of 10 depending on the chosen progenitor scenario and its particular parameters.
-Theoretical models have yet to converge on a single prediction for the DTD.
-For the DD channel, assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral suggest a broad $\sim t^{-1}$ DTD at long delay times ($\gtrsim 1$ Gyr), but at short delays ($\lesssim 1$ Gyr) the rate is limited by the need to produce two WDs \citep[see Section 3.5 from][]{Maoz2014-Review}.
-Higher-order progenitor systems could also produce a $t^{-1}$ DTD \citep{Fang2018-QuadrupleSystems,Rajamuthukumar2023-TripleEvolution}.
+As a result of the uncertainty regarding SN Ia progenitors, theoretical models have yet to converge on a single prediction for the DTD.
+For the DD channel, assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral suggest a broad $\sim t^{-1}$ DTD at long delay times ($\gtrsim 1$ Gyr), but at short delays ($\lesssim 1$ Gyr) the rate is limited by the need to produce two WDs \citep[see][]{Maoz2014-Review}.
+Triple or higher-order progenitor systems could also produce a $t^{-1}$ DTD \citep{Fang2018-QuadrupleSystems,Rajamuthukumar2023-TripleEvolution}.
 The DTD which would result from the SD channel depends greatly on the assumptions of binary population synthesis, but in general is expected to cover a narrower range of delay times and may feature a steep exponential cutoff at the long end \citep[e.g.,][]{Greggio2005-AnalyticalRates}.
@@
 In principle, the observed chemical abundance patterns should therefore contain information about the DTD, and by extension the progenitors of SNe Ia.
-The metallicity distribution function (MDF) and distribution of [O/Fe] record the history of SN Ia enrichment as a function of stellar age and location in the Galaxy.
+The metallicity distribution function (MDF)\footnote{In this paper, we refer to the MDF and the distribution of [Fe/H] interchangeably.} and distribution of [O/Fe] record the history of SN Ia enrichment as a function of stellar age and location in the Galaxy.
 A striking feature of the \aFe distribution in the Milky Way disk is the distinct separation into two components, the high- and low-$\alpha$ sequences, at similar metallicity \citep[e.g.,][]{Bensby2014-solarNeighborhoodAbundances}.
-Since the \aFe abundance reflects the ratio of CC SN to SN Ia enrichment, the DTD should have an effect on the \aFe bimodality.
+Since the \aFe abundance reflects the ratio of CCSN to SN Ia enrichment, the DTD should influence the \aFe bimodality.
 % [Introduce other MW disk features?]
 
-A few studies have compared different DTDs in one-zone chemical evolution models, but their comparisons to abundance data are limited to the local solar neighborhood \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
-=
-\citet{Poulhazan2018-PrecisionPollution} compared six DTDs in a cosmological smoothed-particle hydrodynamics simulation.
-They found that models with a prompt SN Ia component produced the highest abundance ratios and the narrowest \aFe distributions at late times, although their simulation was not tuned to reproduce the parameters of the Milky Way.%, and they did not compare to observed chemical abundances.
-\citet{Matteucci2009-DTDModels} compared multiple DTDs in a multi-zone GCE model with a two-infall SFH, but were limited by the available data for the solar neighborhood.
+A few studies have investigated different DTDs in one-zone chemical evolution models, but comparisons to abundance data have been limited to the solar neighborhood \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
+\citet{Matteucci2009-DTDModels} compared five DTDs in a multi-zone GCE model and found that the agreement with observations worsens if the fraction of prompt SNe Ia is either too high or too low, but they were similarly limited by the the available data for the solar neighborhood.
+\citet{Poulhazan2018-PrecisionPollution} found that the prompt component of the DTD affects the peak and width of the \aFe distribution in a cosmological smoothed-particle hydrodynamics simulation, but their simulation was not designed to reproduce the parameters of the Milky Way.
 The current era of large spectroscopic surveys such as the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE} and the forthcoming Milky Way Mapper \citep{Kollmeier2017-SDSS-V} has made abundances across the Milky Way disk available for comparison to more sophisticated GCE models.
@@
 
-This paper presents the first comprehensive look at the DTD in a multi-zone GCE model that can qualitatively reproduce the observed abundance structure of the Milky Way disk.
+This paper presents the first\todo{(?)} comprehensive look at the DTD in a multi-zone GCE model that can qualitatively reproduce the observed abundance structure of the Milky Way disk.
 A multi-zone approach allows for a radially-dependent parameterization of the SFH, outflows, stellar migration, and abundance gradient which can better match observations across the Galactic disk.
 We evaluate a selection of DTDs from the literature with multiple SFHs and a prescription for radial stellar migration in the Versatile Integrator for Chemical Evolution \citep[\vice;][]{JohnsonWeinberg2020-Starbursts}.
-In Section \ref{sec:methods}, we present our models for the DTD and SFH.
+In Section \ref{sec:methods}, we present our models for the DTD and SFH and describe our observational sample.
 In Section \ref{sec:onezone-results}, we detail our one-zone chemical evolution models and present results.
@@
 Similar to \citetalias{Johnson2021-Migration}, we adopt a prescription for radial migration based on the {\tt h277} hydrodynamical simulation \citep{Christensen2012-h277}.
-Appendix \ref{app:migration} describes our method for determining the migration distance $\Delta R_{\rm gal}$ for each model stellar population, which produces smoother distributions in chemical abundance space than the simulation-based approach.
+In Appendix \ref{app:migration}, we describe our method for determining the migration distance $\Delta R_{\rm gal}$ and midplane distance $|z|$ for each model stellar population.
+Our method produces smoother distributions in chemical abundance space than the simulation-based approach, but the abundance distributions are otherwise unaffected by this change.
 Table \ref{tab:multizone-parameters} summarizes our model parameters and the sub-sections in which we discuss them in detail.
@@
         \tau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the early-burst SFE timescale \\
-        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the early-burst IFR \\
-        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the two-infall IFR \\
+        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the early-burst infall rate \\
+        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the two-infall infall rate \\
         \hline
@@
 $t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the maximum simulation time.
-The denominator of Equation \ref{eq:weighted-sfr} is therefore the total number of SNe Ia per M$_{\odot}$ of stars formed $N_{\rm Ia}/M_\star$.
+The denominator of Equation \ref{eq:weighted-sfr} is therefore equal to $N_{\rm Ia}/M_\star$, the total number of SNe Ia per M$_{\odot}$ of stars formed.
 
@@
 
-We explore five different functional forms for the DTD: a single power-law, a broken power-law with an initially flat plateau, a simple exponential, a two-population model, and a model based on triple-system dynamics.
+We explore five different functional forms for the DTD: a two-population model, a single power-law, an exponential, a broken power-law with an initially flat plateau, and a model computed from triple-system dynamics.
 We also investigate one or two useful variations of the input parameters for each functional form.
@@
 In this subsection we present functional forms $f_{\rm Ia}$ describing the shape of each DTD.
-$f_{\rm Ia}$ does not include the normalization, so it has units of Gyr$^{-1}$ as opposed to M$_\odot^{-1}$ Gyr$^{-1}$ and ist related to $R_{\rm Ia}$ according to
+$f_{\rm Ia}$ does not include the normalization, so it has units of Gyr$^{-1}$ as opposed to M$_\odot^{-1}$ Gyr$^{-1}$ and is related to $R_{\rm Ia}$ according to
 % The relationship between $f_{\rm Ia}$, which has units of ${\rm Gyr}^{-1}$, and $R_{\rm Ia}$, which has units of ${\rm M}_\odot^{-1}\,{\rm Gyr}^{-1}$, is: 
@@
 \begin{equation}
-    f_{\rm Ia}^{\rm twopop}(t) = 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
+    f_{\rm Ia}^{\rm twopop}(t) = 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big].
     \label{eq:prompt-dtd}
 \end{equation}
-To approximate the DTD from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in $\sim 50\%$ of SNe Ia exploding within $t<100$ Myr.
+To approximate the DTD from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in $\sim 40\%$ of SNe Ia exploding within $t<100$ Myr.
 As we illustrate in Figure \ref{fig:dtds}, the two-population DTD has a shorter median delay time than most other models (except the power-law with $\alpha=-1.4$, not shown).
 This formulation is slightly different than the approximation used in other GCE studies \citep[e.g.,][]{Matteucci2006-BimodalDTDConsequences,Poulhazan2018-PrecisionPollution}, where it has a more distinctly bimodal shape.
-We have compared the two approximations to this DTD in a one-zone model and found that they produce very similar abundance tracks and MDFs.
-This DTD is adopted by the Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations.
+We have compared the two approximations to this DTD in a one-zone model and found that they produce very similar abundance distributions.
+This DTD was adopted by the Feedback In Realistic Environments \citep[FIRE;][]{Hopkins2014-FIRE-1} and FIRE-2 \citep{Hopkins2018-FIRE-2} simulations.
 
@@
 % where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
-A declining power-law with $\alpha\sim-1$ is expected to arise from typical assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral \citep[see Section 3.5 from][]{Maoz2014-Review}.
+A declining power-law with $\alpha\sim-1$ arises from typical assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral \citep[see Section 3.5 from][]{Maoz2014-Review}.
 It is therefore a commonly assumed DTD in GCE studies (e.g., \citealt{Rybizki2017-Chempy}; \citetalias{Johnson2021-Migration}; \citealt{Weinberg2023-CCSNYield}).
 Additionally, the observational evidence for a power-law DTD is strong.
-\citet{Maoz2017-CosmicDTD} obtain a DTD with $\alpha=-1.07\pm0.09$ based on volumetric rates and an assumed cosmic SFH for field galaxies in redshift range $0\leq z\leq 2.25$.
-\citet{Wiseman2021-DESRates} obtain a similar slope of $\alpha=-1.13\pm0.05$ for field galaxies in the redshift range $0.2<z<0.6$.
-For galaxy clusters, \citet{Maoz2017-CosmicDTD} find a steeper DTD slope of $\alpha=-1.39^{+0.32}_{-0.05}$.
-\citet{Heringer2019-FieldGalaxyDTD} use a SFH-independent method to constrain the DTD for field galaxies within $0.01<z<0.2$ and find a steeper slope of $\alpha=-1.34^{+0.19}_{-0.17}$.
+\citet{Maoz2017-CosmicDTD} obtained a DTD with $\alpha=-1.07\pm0.09$ based on volumetric rates and an assumed cosmic SFH for field galaxies in redshift range $0\leq z\leq 2.25$.
+\citet{Wiseman2021-DESRates} obtained a similar slope of $\alpha=-1.13\pm0.05$ for field galaxies in the redshift range $0.2<z<0.6$.
+For galaxy clusters, \citet{Maoz2017-CosmicDTD} found a steeper DTD slope of $\alpha=-1.39^{+0.32}_{-0.05}$.
+\citet{Heringer2019-FieldGalaxyDTD} used a SFH-independent method to constrain the DTD for field galaxies within $0.01<z<0.2$ and found a similar slope of $\alpha=-1.34^{+0.19}_{-0.17}$.
 In this paper, we investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$.
@@
 \begin{equation}
-    f_{\rm Ia}^{\rm exp}(t) = e^{-t/\tau}
+    f_{\rm Ia}^{\rm exp}(t) = e^{-t/\tau}.
     \label{eq:exponential-dtd}
@@
 This model allows analytic solutions to the abundances as a function of time for some SFHs, making it a popular choice.
-\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assume an exponential DTD with a timescale $\tau=1.5$ Gyr.
-We show in Appendix \ref{app:analytical-dtds} that a $\tau=1.5$ Gyr exponential is an adequate approximation for the analytical SD DTD from \citet{Greggio2005-AnalyticalRates}.
-There is less observational support for an exponential DTD.
-\citet{Strolger2020-ExponentialDTD}, fitting to the cosmic SFH and SFHs from field galaxies, find a range of exponential-like solutions with timescales $\sim 1.5 - 6$ Gyr.
+\citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assumed an exponential DTD with a timescale $\tau=1.5$ Gyr.
+We show in Appendix \ref{app:analytical-dtds} that this is an adequate approximation for the analytical SD DTD from \citet{Greggio2005-AnalyticalRates}.
+However, there is less observational support for an exponential DTD.
+\citet{Strolger2020-ExponentialDTD}, fitting to the cosmic SFH and SFHs from field galaxies, found a range of exponential-like solutions with timescales $\sim 1.5 - 6$ Gyr.
 In this paper, we investigate timescales $\tau=1.5$ and 3 Gyr.
@@
         1, & t < W \\
-        (t/W)^\alpha, & t \ge W
+        (t/W)^\alpha, & t \ge W.
     \end{cases}
@@
         1, & t_{\rm rise} \leq t < W \\
-        (t / W) ^ \alpha, & t \geq W
+        (t / W) ^ \alpha, & t \geq W,
     \end{cases}
@@
 \subsubsection{The Minimum SN Ia Delay Time}
+\label{sec:minimum-delay}
 
@@
 The former two models, which feature a smooth SFH, were investigated by \citetalias{Johnson2021-Migration} using a similar methodology to this paper.
-The inside-out model produced a better agreement to the age--[O/Fe] relation observed by \citet{Feuillet2019-MilkyWayAges}, while the late-burst model better matched their observed age--metallicity relation.
+The inside-out model produced a good agreement to the age--[O/Fe] relation observed by \citet{Feuillet2019-MilkyWayAges}, while the late-burst model better matched their observed age--metallicity relation.
 % The latter two models (early-burst and two-infall) feature discontinuous or ``bursty'' SFHs, and were proposed by \citet{Conroy2022-ThickDisk} and \citet{Chiappini1997-TwoInfall}, respectively, to explain the distinct evolution of the high- and low-$\alpha$ sequences.
@@
 The two-infall model was proposed by \citet{Chiappini1997-TwoInfall} and features two distinct episodes of gas infall which produce the thick and thin disks.
-Together, these four models cover a range of behavior including a smooth SFH and SFR-, SFE-, and infall-driven starbursts.
+Together, these four models cover a range of behavior, including a smooth SFH, and SFR-, SFE-, and infall-driven starbursts.
 
@@
 are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_\star$ is prescribed along with the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g/\dot\Sigma_\star$.
-The remaining quantities, infall rate (IFR) surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
+The remaining quantities, infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
 The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\tau_\star$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in SFR mode).
@@
 This model features an abrupt factor $\sim20$ rise in the SFE at early times, driving an increase in the [O/Fe] abundance at the transition between the epochs of halo and thick disk formation.
-\citet{Stahlholdt2022-StarFormationEpochs} find evidence for a burst $\sim10$ Gyr ago which marks the beginning of a second phase of star formation.
+\citet{Stahlholdt2022-StarFormationEpochs} found evidence for a burst $\sim10$ Gyr ago which marks the beginning of a second phase of star formation.
 An early infall-driven burst of star formation has been found to lead to MW-like $\alpha$-bimodality in simulations \citep{Mackereth2018-AlphaBimodality}.
@@
 \end{equation}
-While \citet{Conroy2022-ThickDisk} use a constant infall rate in their one-zone model, we adopt a radially-dependent infall rate which declines exponentially with time:
+While \citet{Conroy2022-ThickDisk} used a constant infall rate in their one-zone model, we adopt a radially-dependent infall rate which declines exponentially with time:
 \begin{equation}
@@
 Following \citet{BlandHawthornGerhard2016-MilkyWayReview}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
-We note that most previous studies which use the two-infall model \citep[e.g.,][]{Spitoni2021-TwoInfall} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance.
+We note that most previous studies which use the two-infall model \citep[e.g.,][]{Chiappini1997-TwoInfall,Matteucci2006-BimodalDTDConsequences,Matteucci2009-DTDModels,Spitoni2021-TwoInfall} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance.
 We adopt radially-dependent outflows as in \citetalias{Johnson2021-Migration} (see their Section 2.4 for details) for all our SFHs, including two-infall.
@@
     \includegraphics[width=\linewidth]{figures/onezone_threepanel.pdf}
-    \caption{{\it Each panel:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone chemical evolution models which assume the same DTD.
+    \caption{{\it Each panel:} Abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume the same DTD form.
 The open symbols along each curve mark logarithmic steps in time.
@@
 The left-hand panel of Figure \ref{fig:onezone-threepanel} compares the results of three one-zone models that are identical except for the slope of the power-law DTD.
-A steeper slope produces a sharper ``knee'' and a faster decline in [O/Fe], resulting in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
-Conversely, a shallower slope produces a gentler knee and slower decline in [O/Fe], resulting in a broader [O/Fe] DF and a greater number of high-$\alpha$ stars.
-In all cases the [O/Fe] DF is distinctly unimodal.
-The MDF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
+A steeper slope produces a sharper ``knee'' and a faster decline in [O/Fe] with increasing [Fe/H], resulting in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
+% Conversely, a shallower slope produces a gentler knee and slower decline in [O/Fe], resulting in a broader [O/Fe] DF and a greater number of high-$\alpha$ stars. 
+In all cases the [O/Fe] DF is distinctly unimodal. The MDF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
 
@@
 Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around a simulation time of 1 Gyr.
-A short exponential timescale shifts this knee down to lower [O/Fe] values, while a longer timescale raises it.
-The effect on the [O/Fe] DF is similar to the power-law slope: a short timescale produces more low-$\alpha$ stars, while a long timescale produces more high-$\alpha$ stars (but still a unimodal distribution).
-The effect on the MDF is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values.
-A doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
-For all exponential models, the low-$\alpha$ peak sits approximately 0.02 dex lower than for the power-law models.
-
-Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of varying the width of the plateau DTD on abundance tracks and distributions.
-The effect on the [O/Fe] DF is similar to the previous two models: a longer plateau raises the median delay time, resulting in a smaller low-$\alpha$ peak and a more prominent high-$\alpha$ tail.
+Doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
+A longer exponential timescale also produces a broader [O/Fe] DF with more high-$\alpha$ stars, but the distribution is still unimodal.
+The effect on the MDF is slightly more pronounced than the power-law case, with longer timescales skewing to lower [Fe/H] values.
+
+Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of varying the width $W$ of the plateau DTD 
+% on abundance tracks and distributions. 
 The abundance tracks from several different plateau widths fill the space in between the exponential ($\tau=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
-The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\tau=3$ Gyr), although the [O/Fe] DFs are somewhat more distinct, with the plateau model producing a peak closer to the power-law case.
+% The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\tau=3$ Gyr), although the [O/Fe] DFs are somewhat more distinct, with the plateau model producing a peak closer to the power-law case.
+The plateau ($W=1$ Gyr) and exponential ($\tau=3$ Gyr) DTDs produce nearly identical abundance tracks but their [O/Fe] DFs are more distinct, illustrating the need for both observables to discriminate between DTDs.
+The effect on the [O/Fe] DF is similar to the previous two models: a longer plateau raises the median delay time, producing a broader [O/Fe] DF and a more prominent high-$\alpha$ tail.
+On the other hand, all of the plateau DTDs produce very similar MDFs.
 
@@
     % minimum SN Ia delay times $t_D=40$ Myr (solid) and 150 Myr (dashed curves) for three DTDs: power-law with $\alpha=-1.1$ (blue), plateau with $W=0.3$ Gyr (green), and exponential with $\tau=1.5$ Gyr (purple curves).
-    The layout is similar to Figure \ref{fig:onezone-threepanel}. For clarity, we assume a mass-loading factor $\eta=1$ for the exponential DTD curves, which places the end-point at higher [Fe/H].
+    The layout is similar to Figure \ref{fig:onezone-threepanel}.
+For clarity, we assume a mass-loading factor $\eta=1$ for the exponential DTD curves, which places the end-point of the abundance tracks at higher [Fe/H].
     \textit{Right:} Comparison of one-zone models with five different forms for the DTD.
@@
 
-One parameter of the DTD which we hold fixed in the multi-zone models is the minimum SN Ia delay time $t_D$.
+% One parameter of the DTD which we hold fixed in the multi-zone models is the minimum SN Ia delay time $t_D$.
 Typical choices for $t_D$ in the literature range from $\sim 30$ Myr \citep[e.g.,][]{Poulhazan2018-PrecisionPollution} to 150 Myr \citepalias[e.g.,][]{Johnson2021-Migration}.
-The left-hand panel of Figure \ref{fig:onezone-twopanel} shows that $t_D$ has a much stronger effect on the abundance tracks and distributions of models which assume a power-law DTD than models which assume a plateau or exponential DTD.
-This is a consequence of the much higher number of prompt SNe Ia in the power-law models compared to the others (see Figure \ref{fig:dtds}).
+We also explore the effect of varying the minimum SN Ia delay time $t_D$ (Section \ref{sec:minimum-delay}).
+The left-hand panel of Figure \ref{fig:onezone-twopanel} shows that $t_D$ has a much stronger effect in models which assume a power-law DTD than others.
+This is a consequence of the high number of prompt SNe Ia (see Figure \ref{fig:dtds}).
 Moreover, a power-law DTD with a long $t_D$ may be observationally hard to distinguish from a plateau model.
 In Figure \ref{fig:onezone-twopanel}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (dashed purple line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (solid green line), and their [O/Fe] DFs are virtually identical.
-The difference between the two values of $t_D$ for the exponential ($\tau=3$ Gyr) DTD in both the abundance tracks and distributions is nearly indistinguishable.
+For the exponential ($\tau=3$ Gyr) DTD, the the two values of $t_D$ produce nearly indistinguishable outputs.
 We do not consider the effect on the other DTDs because a 150 Myr minimum delay time is incompatible with the two-population model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD due to its low SN Ia rate at short delay times.
-
-The right-hand panel of Figure \ref{fig:onezone-twopanel} compares the one-zone model outputs from the full range of DTDs we investigate in this work.
-As with the individual DTD parameters, the choice of DTD primarily affects the location of the high-$\alpha$ ``knee'' in the [Fe/H]--[O/Fe] abundance tracks.
-At one extreme is the triple-system model, which sees the CC SN plateau extend up to ${\rm [Fe/H]}\approx-0.8$ followed by a sharp downward turn as the SN Ia rate suddenly increases at a delay time of 500 Myr.
-Star formation proceeds for such a long time before the knee that the [O/Fe] DF shows a slight second peak around the CC SN yield ratio.
-Out of all our one-zone models, this small bump is the only degree of bimodality in the [O/Fe] DF that arises.
-
-At the other extreme are the two-population and power-law ($\alpha=-1.1$) models which peak immediately after the minimum delay time of 40 Myr, placing the knee at ${\rm [Fe/H]}\approx-1.8$.
-The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is a result of the delayed exponential component.
+In the multi-zone models, we will hold $t_D$ fixed at 40 Myr.
+
+The right-hand panel of Figure \ref{fig:onezone-twopanel} compares the one-zone model outputs from the full range of DTDs we investigate in this paper.
+As with the individual DTD parameters, the form of the DTD primarily affects the location of the high-$\alpha$ knee in the [O/Fe]--[Fe/H] abundance tracks.
+At one extreme is the triple-system model, which sees the CCSN plateau extend up to ${\rm [Fe/H]}\approx-0.8$ followed by a sharp downward turn as the SN Ia rate suddenly increases at a delay time of 500 Myr.
+At the other extreme are the two-population and power-law ($\alpha=-1.1$) DTDs, for which the SN Ia rate peaks immediately after the minimum delay time of 40 Myr, placing the high-$\alpha$ knee at ${\rm [Fe/H]}\approx-1.8$.
+The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is produced by the delayed exponential component.
 The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models occupy the intermediate space between these extremes.
-On the other hand, the [O/Fe] DF from the exponential model has the strongest peak, while the plateau ($W=1$ Gyr) and triple-system models produce nearly identical distributions in the low-$\alpha$ regime.
+
+The [O/Fe] DFs also show significant differences between the DTDs.
+In the triple-system model, star formation proceeds for such a long time before the knee that the [O/Fe] DF shows a slight second peak around the CCSN yield ratio.
+Out of all our one-zone models, this small bump is the only degree of bimodality that arises in the [O/Fe] DF.
+Below ${\rm [O/Fe]}\approx0.4$, the plateau ($W=1$ Gyr) and triple-system DTDs produce nearly identical distributions, while the exponential DTD produces the narrowest distribution.
 The power-law ($\alpha=-1.1$) and two-population DTDs produce similar [O/Fe] DFs despite notably different abundance tracks.
 The exponential ($\tau=3$ Gyr) and plateau ($W=0.3$ Gyr) models, while not shown, produce similar abundance tracks to the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models, respectively.
+The DTD also slightly shifts the peak of the [O/Fe] DF, with the exponential DTD placing it $\sim 0.02$ dex lower than the power-law DTD. We see similar trends in the MDF, but to a lesser degree.
 
 % [Summary and conclusions from one-zone models]
-The results presented in this section indicate that the observables most sensitive to the choice of DTD are the [O/Fe]--[Fe/H] abundance tracks and the [O/Fe] DF.
+The results presented in this section indicate that the [O/Fe]--[Fe/H] abundance tracks and the [O/Fe] DF are most sensitive to the parameters of the DTD, while the MDF is a less sensitive diagnostic.
 Degeneracies between models in one regime can be resolved in the other.
@@
 Of course, both of these observables are also greatly affected by the parameters of the SFH.
-In this section we focused on the fiducial inside-out SFH; for a similar comparison of DTDs with a two-infall SFH, we direct the reader to \citet{Palicio2023-AnalyticDTD}.
+In this section we focused on the fiducial inside-out SFH.
+\citet{Palicio2023-AnalyticDTD} compared similar DTDs in one-zone models with a two-infall SFH (see \ref{sec:two-infall-discussion}).
+% for a similar comparison of DTDs with a two-infall SFH, we direct the reader to \citet{Palicio2023-AnalyticDTD}.
 
@@
 Following \citetalias{Johnson2021-Migration}, we do not implement radial gas flows \citep[e.g.,][]{LaceyFall1985-RadialGasFlows,BilitewskiSchonrich2012-RadialFlows}.
+Stellar populations are also assigned a distance from the midplane according to their age and final radius as described in Appendix \ref{app:migration}.
 
@@
 
+We run a total of multi-zone models with all combinations of our eight DTDs and four SFHs, for a total of 32.
+In the following subsections, we present the stellar abundance and age distributions from the multi-zone models and compare to APOGEE data from across the Galactic disk.
+
 \subsection{The distribution of [Fe/H]}
@@
     \includegraphics[width=\linewidth]{figures/feh_df_comparison.pdf}
-    \caption{Distributions of [Fe/H] from multi-zone models with various models for the SFH and DTD.
+    \caption{Metallicity distribution functions (MDFs) from multi-zone models with various models for the SFH and DTD.
 Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}).
@@
 Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row.
-All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:sample}) and smoothed with a box-car width of 0.2 dex.
+Each MDF is convolved with a Gaussian with a width equal to the median observational uncertainty in APOGEE DR17 (see Table \ref{tab:sample}) and smoothed with a box-car width of 0.2 dex.
     \textit{Left columns:} comparison between the inside-out and two-infall SFHs; both assume the exponential ($\tau=1.5$ Gyr) DTD. 
@@
 Figure \ref{fig:feh-df-comparison} shows MDFs across the Galaxy for a selection of models and APOGEE data.
-The two left-hand columns illustrate the effect of different SFHs on the model outputs.
-The effect of the SFH is most pronounced in the MDFs for the inner Galaxy.
+The two left-hand columns illustrate the effect of different SFHs on the model outputs, which is most pronounced in the inner Galaxy.
 Near the midplane, the two-infall SFH produces a distinct bump $\sim0.4$ dex below the MDF peak, which is not seen for the inside-out SFH.
-Away from the midplane, the low-metallicity tail is slightly more pronounced for the two-infall than the inside-out model, and the two-infall MDFs extend to slightly higher metallicity.
+Away from the midplane, the low-metallicity tail is slightly more prominent for the two-infall than the inside-out model, and the two-infall MDFs extend to slightly higher metallicity.
 In the outer Galaxy, though, the MDFs produced by the two models are nearly identical.
-The shift in the peak metallicity from the inner to the outer Galaxy is unaffected by the choice of SFH, as is the shift in skewness of the MDFs.
+The shift in the skewness and peak of the MDF from the inner to the outer Galaxy is unaffected by the choice of SFH.
 % The two left-hand columns show MDFs from models with different SFHs which assume the same DTD (exponential with $\tau=1.5$ Gyr).
@@
 
-Holding the SFH fixed, varying the DTD has minimal influence on these MDFs for fixed SFH.
+Holding the SFH fixed, varying the DTD has a minimal effect on the MDFs.
 The two right-hand columns of Figure \ref{fig:feh-df-comparison} plot the MDFs for two multi-zone models, which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr.
@@
 The inner Galaxy MDF is more sensitive to the choice of DTD than the outer Galaxy.
-The SFH peaks earlier and declines more sharply due to the inside-out formation of the disk.
+Here, the SFH peaks earlier and declines more sharply due to the inside-out formation of the disk.
 Consequently, SNe Ia often explode when the gas supply is significantly lower than when the progenitors formed.
@@
 As such, its shape is greatly affected by both the SFH and DTD.
-Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs compared to the distributions measured by APOGEE, all assuming an exponential DTD with $\tau=1.5$ Gyr.
+Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs compared to the distributions measured by APOGEE.
+All four models assume an exponential DTD with $\tau=1.5$ Gyr, which has an intermediate median delay time among all our DTDs.
 We see similar trends with Galactic region across all four models.
@@
 
-While trends with $R_{\rm gal}$ and $|z|$ are similar between DTD models, the shape of the distribution varies greatly with the chosen SFH.
-The inside-out and late-burst models produce similar distributions because of the similarity of their underlying SFHs \textemdash the burst is imposed upon the inside-out SFH (see Equation \ref{eq:lateburst-sfh}).
+While trends with $R_{\rm gal}$ and $|z|$ are similar across the different models, the shape of the distribution varies greatly with the chosen SFH.
+The inside-out and late-burst models produce similar distributions because of the similarity of their underlying SFHs, as the burst is imposed upon the inside-out SFH (see Equation \ref{eq:lateburst-sfh}).
 Both skew heavily toward near-solar [O/Fe], although the late-burst model produces a slightly broader peak and a less-prominent high-[O/Fe] tail.
@@
 
-On the other hand, the early-burst model produces a bimodal distribution in [O/Fe] at most radii and close to the midplane, whereas the APOGEE distribution does not show a prominent high-$\alpha$ peak beyond $R_{\rm gal}\sim11$ kpc ($\sim7$ kpc in the midplane).
-Although agreement is not perfect, the early-burst SFH produces the closest match to the data by far: the low-$\alpha$ sequence away from the midplane is dominated by stars in the solar annulus and outer disk.
-However, the high-$\alpha$ sequence has considerably more outer disk stars than the data.
+On the other hand, the early-burst model produces a bimodal [O/Fe] distribution in most regions.
+Although agreement is not perfect, the early-burst SFH produces the closest match to the data by far.
+In particular, the low-$\alpha$ sequence away from the midplane is dominated by stars in the solar annulus and outer disk, a trend which is also seen in APOGEE.
+However, the early-burst high-$\alpha$ sequence contains many stars in the outer disk and close to the midplane, whereas the APOGEE distribution does not show a prominent high-$\alpha$ peak beyond $R_{\rm gal}\sim11$ kpc ($\sim7$ kpc in the midplane).
 
 The two-infall SFH produces \textit{three} distinct modes at ${\rm [O/Fe]}\approx 0.0$, $0.2$, and $0.4$.
-At small $R_{\rm gal}$ and with increasing $|z|$, the low-$\alpha$ peak decreases in prominence as the high-$\alpha$ peak increases, but the intermediate peak is a striking feature at all latitudes that is not observed.
-In the APOGEE data, the high-$\alpha$ peak is at ${\rm [O/Fe]}\approx+0.3$, roughly halfway between the intermediate and high-$\alpha$ peaks this model predicts.
+At small $R_{\rm gal}$ and with increasing $|z|$, the low-$\alpha$ peak decreases in prominence as the high-$\alpha$ peak increases, but the intermediate peak is a striking feature at all latitudes that does not align with observations.
+In the APOGEE data, the high-$\alpha$ peak is at ${\rm [O/Fe]}\approx+0.3$, roughly halfway between the intermediate and high-$\alpha$ peaks produced by the two-infall model.
+However, the model high-$\alpha$ sequence does match the observed trends with $R_{\rm gal}$ and $|z|$ much better than the early-burst models.
 
@@
 Figure \ref{fig:ofe-df-dtd} shows [O/Fe] distributions produced by models with the same SFH but a range of different DTDs.
-We show the early-burst SFH because it produces distinct low- and high-$\alpha$ sequences.
+We show models with the early-burst SFH because it produces distinct low- and high-$\alpha$ sequences.
 The most obvious effect of the DTD is to shift the mode of the high-$\alpha$ sequence.
@@
 In general, models with fewer prompt SNe Ia populate the high-$\alpha$ sequence with more stars because the chemical evolution track spends more time in the high-$\alpha$ regime.
-The exception to this is the two-population DTD, which produces a very strong high-$\alpha$ peak at $|z|>0.5$ kpc, likely a result of its long exponential tail.
+The exception to this is the two-population DTD, which produces a very strong high-$\alpha$ peak at $|z|>0.5$ kpc.
+This might result from the second knee in the abundance track (Figure \ref{fig:onezone-twopanel}) which is produced by its long exponential tail.
 
@@
 The late-burst SFH generally produces [O/Fe] DFs that score poorly compared to other models.
+[Elaborate a bit more].
 
@@
     \includegraphics[width=\linewidth]{figures/ofe_bimodality_summary.pdf}
-    \caption{The distributions of [O/Fe] along two different slices of [Fe/H]: $-0.6\leq$[Fe/H]$<-0.4$ (blue dashed) and $-0.4\leq$[Fe/H]$<-0.2$ (red solid). 
-    All panels contain stars within the Galactic region defined by $7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc.
-The $|z|$-distributions of the model stellar populations are re-sampled to match the vertical distribution of the APOGEE sample, and \num{20000} stellar populations are drawn from the adjusted distribution in each panel.
+    \caption{The distributions of [O/Fe] along two different slices of [Fe/H]: $-0.6\leq$[Fe/H]$<-0.4$ (red solid) and $-0.4\leq$[Fe/H]$<-0.2$ (blue dashed). 
+    Each panel contains stars within the Galactic region defined by $7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc. 
+    % The $|z|$-distributions of the model stellar populations are re-sampled to match the vertical distribution of the APOGEE sample, and \num{20000} stellar populations are drawn from the adjusted distribution in each panel.
 The maximum of each distribution is normalized to 1 and the vertical scale is consistent across all panels.
+    For each distribution, \num{20000} stellar populations are re-sampled from the model output to match the $|z|$ distribution of the APOGEE sample.
     \textit{Top row:} results from five multi-zone models which assume the late-bust SFH but different DTDs.
@@
 All assume the exponential ($\tau=1.5$ Gyr) DTD.
-Each panel plots a random mass-weighted sample of 10,000 star particles in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by $R_{\rm gal}$ at birth.
+Each panel plots a random mass-weighted sample of \num{10000} star particles in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by $R_{\rm gal}$ at birth.
 A Gaussian scatter has been applied to all points based on the median abundance errors in APOGEE DR17 (see Table \ref{tab:sample}).
@@
 
-[Subsection introduction]
-Section \ref{sec:onezone-results} and specifically Figures \ref{fig:onezone-threepanel} and \ref{fig:onezone-twopanel} illustrated the effect of the DTDs and parameters on [O/Fe]--[Fe/H] tracks in idealized one-zone models.
+In Section \ref{sec:onezone-results}, and specifically Figures \ref{fig:onezone-threepanel} and \ref{fig:onezone-twopanel}, we illustrated that the form and parameters of the DTD have an important effect on the ISM abundance tracks in idealized one-zone models.
+However, comparisons to data are limited because the tracks do not record the number of stars which are formed with those abundances, nor do they incorporate the effect of stellar migration.
+Here, we present the distribution of stellar abundances in the [O/Fe]--[Fe/H] plane alongside the ISM abundance tracks from our multi-zone models.
+We compare our model outputs to the observed distributions from APOGEE across the Milky Way disk.
+% \todo{Subsection introduction.}
+% Section \ref{sec:onezone-results} and specifically Figures \ref{fig:onezone-threepanel} and \ref{fig:onezone-twopanel} illustrated the effect of the DTDs and parameters on [O/Fe]--[Fe/H] tracks in idealized one-zone models.
 
 Figure \ref{fig:ofe-feh-sfh} compares the [O/Fe]--[Fe/H] plane in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) between our four model SFHs.
-All models presented in this figure assume an exponential DTD with $\tau=1.5$ Gyr, as it lies in the middle in terms of balance between prompt and delayed SNe Ia.
-The black curves represent the ISM abundance as a function of time in the central zone; in the absence of radial migration, all simulated stellar populations would lie along these lines.
-Stars to the left of the abundance tracks were born in the outer disk, while stars to the right of the tracks were born in the inner disk, as evidenced by the color-coding in the figure.
-
-The inside-out and late-burst models produce similar results, the main difference being a slightly broader core of the abundance distribution around ${\rm [O/Fe]}\approx0.05$ dex.
-The Gaussian burst in SFH in the late-burst model introduces a loop in the ISM abundance track, where an uptick in star formation at $t\approx11$ Gyr raises the CCSN rate, leading to a slight increase in [O/Fe] before the subsequent increase in the SN Ia rate brings it back down.
-This same pattern is seen much more strongly in the abundance tracks for the two-infall model: here, the significant infall of pristine gas at $t=4$ Gyr leads to rapid dilution of the ISM, followed by a large burst in the SFR which raises [O/Fe] by $\sim 0.2$ dex.
-In this case the second infall produces a ``ridge line'' in the abundance distribution at ${\rm [O/Fe]}\approx 0.2$.
-Finally, the early-burst model shows the clearest separation between a high-[O/Fe] track which follows the ISM abundance from low metallicities, and a low-[O/Fe] sequence composed of stars with a wide range of birth radii.
-The early-burst model sees a higher density of points which closely follow the ISM track at ${\rm [Fe/H]}\lesssim 0.5$ which is likely the result of an increased SFR at early times relative to the other models.
+The black curves represent the ISM abundance as a function of time in the $R_{\rm gal}=8.0-8.1$ kpc zone; in the absence of radial migration, all simulated stellar populations would lie close to these lines.
+Stellar populations to the left of the abundance tracks were born in the outer disk, while those to the right were born in the inner disk, as evidenced by the color-coding in the figure.
+This illustrates how radial migration can explain much of the spread in [Fe/H] which is observed in a given Galactocentric region.
+% \todo{Discuss the effect of radial migration on the [O/Fe]--[Fe/H] distributions.}
+
+The abundance tracks of all four model SFHs initially follow a similar path of decreasing [O/Fe] with increasing [Fe/H].
+The ISM abundance ratios of the inside-out model change monotonically over the entire simulation time.
+The stellar abundance distribution at both low- and high-[O/Fe] is composed of stars with a wide range of birth $R_{\rm gal}$.
+In particular, we observe a high-[O/Fe] ``ridge'' on the high-metallicity side of the ISM track, which is composed of stellar populations from the inner Galaxy.
+
+The late-burst model produces similar results to the inside-out model up to ${\rm [Fe/H]}\approx-0.2$, again because of their similar SFHs.
+The Gaussian burst in SFH in the late-burst model introduces a loop in the ISM abundance track, as an uptick in star formation at $t\approx11$ Gyr raises the CCSN rate, leading to a slight increase in [O/Fe] before the subsequent increase in the SN Ia rate lowers the [O/Fe] once again.
+This loop slightly broadens the low-[O/Fe] stellar distribution as we observed in Section \ref{sec:ofe-df}.
+
+This same pattern is seen much more strongly in the abundance tracks for the two-infall model.
+Here, the significant infall of pristine gas at $t=4$ Gyr leads to rapid dilution of the metallicity of the ISM, followed by a large burst in the SFR which raises [O/Fe] by $\sim 0.2$ dex.
+The track begins to ``turn over'' back to lower [O/Fe] due to the delayed response of SNe Ia.
+We observe a ridge in the stellar abundance distribution at this turn-over point (${\rm [O/Fe]}\approx0.2$), which roughly coincides with the upper limit of the APOGEE distribution near the midplane.
+The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx0.0$ near the end of the simulation.
+
+The early-burst track is the most distinct from the other models at low metallicity.
+The portion which is shown in Figure \ref{fig:ofe-feh-sfh} represents the evolution {\it after} the early SFE burst.
+At low metallicity, there is a ``simmering phase'' where [O/Fe] slowly decreases to a local minimum at ${\rm [Fe/H]}\approx-1.3$, at which point the rapid increase in the SFE causes the [O/Fe] to rebound \citep[a more thorough examination of this behavior can be seen in][]{Conroy2022-ThickDisk}.
+The early-burst SFH produces the clearest separation in the stellar abundances between a high-[O/Fe] sequence which follows the ISM abundance track down to low [Fe/H], and a low-[O/Fe] sequence composed of stars with a wide range of birth radii.
+The stellar population density of the high-[O/Fe] sequence is relatively high, likely as a result of a higher SFR at early times compared to the other models.
 
@@
 
-Figure \ref{fig:ofe-feh-dtd} compares [O/Fe]--[Fe/H] distributions for five models with the same SFH (inside-out) but different DTDs.
+Figure \ref{fig:ofe-feh-dtd} compares the [O/Fe]--[Fe/H] ISM tracks and stellar distributions for five models with the same SFH but different DTDs.
 We choose the inside-out SFH for this figure because it produces a monotonically-decreasing abundance track, making comparisons between the different DTDs relatively straightforward.
-We note that in this model, both the low- and high-$\alpha$ sequences are composed of stars with a wide range of birth $R_{\rm gal}$.
-The model results are arranged by increasing median delay time from left to right.
-Results for the two-population and power-law ($\alpha=-1.1$) DTDs, with a large fraction of prompt SNe Ia, are presented in the first and second columns, respectively.
-For these models, the simulated stellar abundances are reasonably well-aligned with the APOGEE contours at low $|z|$ (bottom panels), but they entirely miss the observed high-$\alpha$ sequence at high $|z|$ (top panels).
-In the center column, the exponential ($\tau=1.5$ Gyr) DTD produces a distribution which aligns quite well with the APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to large [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
+% We note that in this model, both the low- and high-$\alpha$ sequences are composed of stars with a wide range of birth $R_{\rm gal}$. 
+The models are arranged according to the median delay time of the DTD, increasing across the panels from left to right.
+
+% Results for the two-population and power-law ($\alpha=-1.1$) DTDs, with a large fraction of prompt SNe Ia, are presented in the first and second columns, respectively. 
+The two-population and power-law ($\alpha=-1.1$) DTDs, which have a large fraction of prompt SNe Ia, produce stellar abundance distributions that are reasonably well-aligned with the APOGEE contours at low $|z|$, but they entirely miss the observed high-$\alpha$ sequence at large $|z|$.
+The ISM abundance tracks for the 8 kpc zone do not pass through the APOGEE 30\% contour.
+For both DTDs, the high-[O/Fe] knee is located below the left-most bound of the plot, but we observe a second knee at ${\rm [O/Fe]}\approx0.2$ where the abundance track turns further downward.
+% For these models, the simulated stellar abundances are reasonably well-aligned with the APOGEE contours at low $|z|$ (bottom panels), but they entirely miss the observed high-$\alpha$ sequence at high $|z|$ (top panels).
+
+The exponential ($\tau=1.5$ Gyr) DTD produces a distribution in Figure \ref{fig:ofe-feh-dtd} which aligns quite well with the outer APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to high [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
 While it does better at populating the high-$\alpha$ sequence than the previous DTDs, the bulk of the simulated populations at large $|z|$ still fall below the APOGEE 30\% contour (top panel).
+
 The two right-hand columns present model results for the plateau ($W=1$ Gyr) and triple-system DTDs, which have the longest median delay times.
@@
 
-[Discuss effect of radial migration]
-
-\citet{PerezCruz2008-KLTest2D} present a method for estimating the KL divergence between two continuous, multivariate samples using a $k$-nearest neighbor estimate.
-We implement this method to calculate the divergence between the multi-zone models and APOGEE data in [Fe/H]--[O/Fe] space.
+To quantify the agreement between the multi-zone model outputs and data in [O/Fe]--[Fe/H] space, we implement the method of \citet{PerezCruz2008-KLTest2D} for computing the KL divergence between two continuous, multivariate samples using a $k$-nearest neighbor estimate.
+% \citet{PerezCruz2008-KLTest2D} present a method for estimating the KL divergence between two continuous, multivariate samples using a $k$-nearest neighbor estimate.
+We implement this method to calculate the divergence between the multi-zone models and APOGEE data in [O/Fe]--[Fe/H] space.
+\todo{More detail on the scoring calculations.}
 % \footnote{We got the implementation from \url{https://mail.python.org/pipermail/scipy-user/2011-May/029521.html}.}
@@
 Stellar populations at the high-[Fe/H] end of the distribution have migrated from inner regions.
-[More discussion about Figure \ref{fig:ofe-feh-twoinfall}].
+\todo{More discussion about Figure \ref{fig:ofe-feh-twoinfall}.}
 
@@
 
-[Age at the knee, given our age uncertainties, is not a great diagnostic]
+\todo{Discuss how the age at the knee, given our age uncertainties, is not a great diagnostic.}
 
@@
 In order to identify trends among our many models, it will be useful to have some semi-quantitative way to compare their outputs to APOGEE data across the disk.
-In this section, we compare all of our model outputs to APOGEE across five diagnostics: the MDF, [O/Fe] DF, [Fe/H]--[O/Fe] plane, age--[O/Fe] plane, and [O/Fe] bimodality.
+In this section, we compare all of our model outputs to APOGEE across five diagnostics: the MDF, [O/Fe] DF, [O/Fe]--[Fe/H] plane, age--[O/Fe] plane, and [O/Fe] bimodality.
 We perform statistical tests between APOGEE and the model outputs in each region of the Galaxy (as described in corresponding subsections of Section \ref{sec:multizone-results}), then compute the average weighted by the size of the APOGEE sample in each region to obtain a single numerical score.
@@
 
-[Discuss yield effects]
+\todo{Discuss yield effects.}
 
@@
 
-\citet{Mackereth2018-AlphaBimodality} find the appearance of a MW-like bimodality in the EAGLE simulations is rare, occuring in only $\sim5\%$ of their sample.
+\citet{Mackereth2018-AlphaBimodality} find the appearance of a MW-like bimodality in the EAGLE simulations is rare, occurring in only $\sim5\%$ of their sample.
 
@@
 Recent studies have shown that the high specific SN Ia rates observed in low-mass galaxies \citep[e.g.,][]{Brown2019-ASASSNrates,Wiseman2021-DESRates} can be explained by a metallicity-dependent rate of SNe Ia \citep{Gandhi2022-MetallicityDependentRates,Johnson2023-Binaries}.
-A similar metallicity dependence has also been observed in the rate of CC SNe \citep{Pessi2023-MetalDepCCSNe}.
+A similar metallicity dependence has also been observed in the rate of CCSNe \citep{Pessi2023-MetalDepCCSNe}.
 The consequences of a metallicity-dependent SN Ia rate in the context of a multi-zone GCE simulation with radial migration could be explored in a future paper.
@@
 Our results indicate that the range of parameter space in the DTD is still too broad to be completely constrained by GCE models.
-Future constraints on the DTD may come from the Legacy Survey of Space and Time (LSST) at the Vera Rubin Observatory [cite], which is expected to observe 10 million [?] SNe during its X-year run.
-On the other hand, better constraints on the Galactic SFH provided by SDSS-V [cite] will enable future GCE studies to constrain the DTD at a higher confidence.
+Future constraints on the DTD may come from the Legacy Survey of Space and Time (LSST) at the Vera Rubin Observatory \todo{[cite]}, which is expected to observe 10 million \todo{(?)} SNe during its X-year run.
+On the other hand, better constraints on the Galactic SFH provided by SDSS-V \citep{Kollmeier2017-SDSS-V} will enable future GCE studies to constrain the DTD at a higher confidence.
 
@@
 We thank Prof.\ David H.\ Weinberg and attendees of OSU's Galaxy Hour for many useful discussions over the course of this project.
-[Personal acknowledgements]
+\todo{Other personal acknowledgements.}
 
@@
 
-[Carnegie land acknowledgement]
+\todo{Carnegie land acknowledgement.}
 % Software acknowledgements if not a AAS journal
@@
 repository associated to this study is publicly available at
-\url{\GitHubURL}, and the release v.X.X allows anyone to re-build the entire 
-manuscript. The datasets are stored at [URL].
+\url{\GitHubURL}, and the release \todo{v.X.X} allows anyone to re-build the entire 
+manuscript. The datasets are stored at \todo{URL}.
 
@@
 
-\section{Stellar Migration}
+\section{Stellar Migration \& Midplane Distances}
 \label{app:migration}

### 2024-04-02 src/scripts/feh_df_comparison.py
update plot bounds

@@ -25,7 +25,7 @@ DTD_LABELS = ['Power-law DTD\n($\\alpha=-1.4$)',
 SFH_MODEL = 'insideout' # hold constant while varying DTD
 # Plot settings
 NBINS = 100
-FEH_LIM = (-1.2, 0.6)
+FEH_LIM = (-1.2, 0.7)
 SMOOTH_WIDTH = 0.2
 CMAP = 'plasma_r'
 

### 2024-04-02 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \newcommand{\vice}{{\tt VICE}\xspace}
+\newcommand{\hydro}{{\tt h277}\xspace}
 \newcommand{\todo}[1]{{\color{red}#1}}
@@
 SNe Ia do not explode immediately after star formation, and the delay-time distribution (DTD) has not been definitively determined by supernova surveys or theoretical models.
-Because the DTD also affects the relationship among age, [Fe/H], and \aFe in chemical evolution models, comparison with observations of stars in the Milky Way is an important consistency check for any proposed DTD.
+Because the DTD also affects the relationship among age, [Fe/H], and \aFe \todo{([O/Fe]?)} in chemical evolution models, comparison with observations of stars in the Milky Way is an important consistency check for any proposed DTD.
 We implement several popular forms of the DTD in combination with multiple star formation histories for the Milky Way in %one-zone and
@@
 We refer the interested reader to the former for details about the \vice package and to the latter for details about the model Milky Way disk, including the star formation law, radial density gradient, and outflows.
-Similar to \citetalias{Johnson2021-Migration}, we adopt a prescription for radial migration based on the {\tt h277} hydrodynamical simulation \citep{Christensen2012-h277}.
+Similar to \citetalias{Johnson2021-Migration}, we adopt a prescription for radial migration based on the \hydro hydrodynamical simulation \citep{Christensen2012-h277}.
 In Appendix \ref{app:migration}, we describe our method for determining the migration distance $\Delta R_{\rm gal}$ and midplane distance $|z|$ for each model stellar population.
@@
 \citet{Stahlholdt2022-StarFormationEpochs} found evidence for a burst $\sim10$ Gyr ago which marks the beginning of a second phase of star formation.
-An early infall-driven burst of star formation has been found to lead to MW-like $\alpha$-bimodality in simulations \citep{Mackereth2018-AlphaBimodality}.
+An early infall-driven burst of star formation has been found to lead to MW-like $\alpha$-bimodality in the EAGLE simulations \citep{Mackereth2018-AlphaBimodality} \todo{(cite EAGLE?)}.
 We adopt the following formula for the time-dependence of the SFE timescale from \citet{Conroy2022-ThickDisk}:
@@
 APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
+
 We use estimated ages from \citet[][hereafter \citetalias{Leung2023-Ages}]{Leung2023-Ages}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
@@
 \begin{equation}
-    D_{\rm{KL}}(P,Q) \equiv \int_{-\infty}^{\infty} p(x) \log\Big(\frac{p(x)}{q(x)}\Big) dx
+    D_{\rm{KL}}(P||Q) \equiv \int_{-\infty}^{\infty} p(x) \log\Big(\frac{p(x)}{q(x)}\Big) dx
     \label{eq:kl-divergence}
 \end{equation}
-for distributions $P$ and $Q$ with probability density functions $p(x)$ and $q(x)$.
+for distributions $P$ and $Q$ with probability density functions (PDFs) $p(x)$ and $q(x)$.
 If $D_{\rm KL}=0$, the two distributions contain equal information.
@@
 \begin{equation}
-    S = \frac{\sum_R D_{\rm KL}(P,Q|R) N_\star(R)}{\sum_R N_\star(R)}.
+    S = \frac{\sum_R D_{\rm KL}(P||Q|R) N_\star(R)}{\sum_R N_\star(R)}.
     \label{eq:feh-df-score}
@@
 The late-burst SFH generally produces [O/Fe] DFs that score poorly compared to other models.
-[Elaborate a bit more].
+\todo{Elaborate on the model scores a bit more}.
 
@@
 For both DTDs, the high-[O/Fe] knee is located below the left-most bound of the plot, but we observe a second knee at ${\rm [O/Fe]}\approx0.2$ where the abundance track turns further downward.
+As discussed in Section \ref{sec:onezone-results}, the second knee is most prominent in the model with the two-population DTD because of its long exponential tail.
 % For these models, the simulated stellar abundances are reasonably well-aligned with the APOGEE contours at low $|z|$ (bottom panels), but they entirely miss the observed high-$\alpha$ sequence at high $|z|$ (top panels).
 
+The DTDs with an intermediate median delay time do well at reproducing the observed abundance distributions.
 The exponential ($\tau=1.5$ Gyr) DTD produces a distribution in Figure \ref{fig:ofe-feh-dtd} which aligns quite well with the outer APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to high [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
-While it does better at populating the high-$\alpha$ sequence than the previous DTDs, the bulk of the simulated populations at large $|z|$ still fall below the APOGEE 30\% contour (top panel).
+While it does better at populating the high-$\alpha$ sequence than the previous DTDs, the bulk of the simulated populations at large $|z|$ still fall below the APOGEE 30\% contour.
 
 The two right-hand columns present model results for the plateau ($W=1$ Gyr) and triple-system DTDs, which have the longest median delay times.
-The high-$\alpha$ ``knee'' occurs at a much higher metallicity in these models and is visible in the gas abundance tracks in the upper-left corner of the panels.
-At high $|z|$, the simulated abundance align quite well with the APOGEE high-$\alpha$ sequence (top panels), but there is a significant ridge of high-$\alpha$ stars from the inner Galaxy at low $|z|$ (bottom panels).
-
-To quantify the agreement between the multi-zone model outputs and data in [O/Fe]--[Fe/H] space, we implement the method of \citet{PerezCruz2008-KLTest2D} for computing the KL divergence between two continuous, multivariate samples using a $k$-nearest neighbor estimate.
-% \citet{PerezCruz2008-KLTest2D} present a method for estimating the KL divergence between two continuous, multivariate samples using a $k$-nearest neighbor estimate.
-We implement this method to calculate the divergence between the multi-zone models and APOGEE data in [O/Fe]--[Fe/H] space.
+The high-[O/Fe] knee occurs at a much higher metallicity in these models and is visible in the gas abundance tracks in the upper-left corner of the panels.
+At large $|z|$, the simulated abundance distributions align quite well with the APOGEE high-$\alpha$ sequence, but there is a significant ridge of high-$\alpha$ stars from the inner Galaxy at low $|z|$.
+
+To quantify the agreement between the multi-zone model outputs and data in [O/Fe]--[Fe/H] space, we implement the method of \citet{PerezCruz2008-KLTest2D} for estimating the KL divergence between two continuous, multivariate samples using a $k$-nearest neighbor estimate.
+For $n$ samples from a multivariate PDF $p(\mathbf{x})$ and $m$ samples from $q(\mathbf{x})$, we can estimate $D_{\rm KL}(P||Q)$ according to the following:
+\begin{equation}
+    \hat D_k(P||Q) = \frac dn \sum_{i=1}^n\log\frac{r_k(\mathbf{x}_i)}{s_k(\mathbf{x}_i)} + \log\frac{m}{n-1},
+\end{equation}
+where $r_k(\mathbf{x}_i)$ and $s_k(\mathbf{x}_i)$ are the distance to the $k$th nearest neighbor of $\mathbf{x}_i$ in the samples of $P$ and $Q$, respectively.
+We take $k=2$ to find the nearest neighbor other than the sample itself.
+As before, $P$ is the APOGEE distribution and $Q$ is the model distribution, and in this case $\mathbf{x}=({\rm [Fe/H]}, {\rm [O/Fe]})$.
+As in Sections \ref{sec:feh-df} and \ref{sec:ofe-df}, we bin the model outputs and data by $R_{\rm gal}$ and $|z|$, calculate $\hat D_k(P||Q)$ in each region, and then take the weighted mean of each region as in Equation \ref{eq:feh-df-score} to arrive at a single score for each model.
 \todo{More detail on the scoring calculations.}
@@
 \vspace{-24pt}
+
+\todo{I just noticed that I was using slightly wrong yields in all of the multi-zone models (JW20 instead of J+21).
+I re-ran all the models and this corrected the end-point of the inside-out tracks, which are now at (0,0).
+However, this also shifted the end-point of the two-infall tracks down to (+0.1, -0.1), so now two-infall is no longer the clear winner like it used to be.
+The best DTDs are now the 1-Gyr power-law and the triple-system, rather than the 1.5-Gyr exponential like before.
+The general trend of more prompt SNe = worse does still hold.
+At a minimum, I think this indicates that these scores are highly sensitive to the yields.
+At worst, maybe we need to consider adjusting the yields for the two-infall models so that the [O/Fe] distributions are not significantly lower than every other SFH.}
 
@@
     \includegraphics[width=\linewidth]{figures/radial_migration.pdf}
-    \caption{The distribution of final radius $R_{\rm final}$ as a function of formation radius $R_{\rm form}$ and age for the h277 analogue (top row) and Gaussian sampling scheme (bottom row).
+    \caption{The distribution of final radius $R_{\rm final}$ as a function of formation radius $R_{\rm form}$ and age for the \hydro analogue (top row) and Gaussian sampling scheme (bottom row).
 From left to right, star particles are binned by formation annulus, from the inner disk (far left column) to the solar annulus (center column) to the outer disk (far right column).
@@
 
-For each star particle in \vice, \citetalias{Johnson2021-Migration} randomly assign an analogue star particle from \texttt{h277} and adopt its radial migration distance $\Delta R$ and final midplane distance $z$.
+For each star particle in \vice, \citetalias{Johnson2021-Migration} randomly assign an analogue star particle from \hydro and adopt its radial migration distance $\Delta R$ and final midplane distance $z$.
 This allows \vice to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
-However, in regions where the number of h277 star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single h277 star particle can be assigned as an analogue to multiple \vice stellar populations.
+However, in regions where the number of \hydro star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single \hydro star particle can be assigned as an analogue to multiple \vice stellar populations.
 These populations will have similar formation and migration histories and consequently similar abundances, which produces unphysical ``clumps'' of stars in the abundance distributions at high latitudes and large radii.
 
-We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm initial}$ from the \texttt{h277} output in bins of $R_{\rm initial}$ and age.
+We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm initial}$ from the \hydro output in bins of $R_{\rm initial}$ and age.
 Each Gaussian is centered at 0 and we find that the scale $\sigma_{\Delta R}$ is best described by the function
@@
 \end{equation}
-We fit the above function to the distributions of $z$ in h277 in varying bins of $T$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
+We fit the above function to the distributions of $z$ in \hydro in varying bins of $T$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
 \begin{equation}
@@
 They also found that in strongly-barred galaxies, the migration is stronger overall but has a slower timestep evolution than diffusion ($\Delta t^{0.5}$).
+\todo{They argue that the bar has a minimal effect.}
+On the other hand, \citet{Brunetti2011-BarredSpiralDiffusion} argue that the bar has a strong effect on the strength of radial migration and that its effect is not constant with time.
 
@@
 
+\citet{Lu2023-LMCStars} examined radial migration strengths in galaxies from the NIHAO simulations.
+They found that it predicts galaxies to follow a relatively universal relation of $\sigma_{\rm RM}\propto \tau^{0.32}$, which is slower than the diffusion process of, e.g., \citet{Frankel2019-InsideOutGrowth}, but quite similar to our own age dependence.
+
 \bibliography{bib}

### 2024-04-03 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 SNe Ia do not explode immediately after star formation, and the delay-time distribution (DTD) has not been definitively determined by supernova surveys or theoretical models.
-Because the DTD also affects the relationship among age, [Fe/H], and \aFe \todo{([O/Fe]?)} in chemical evolution models, comparison with observations of stars in the Milky Way is an important consistency check for any proposed DTD.
+Because the DTD also affects the relationship among age, [Fe/H], and \aFe in chemical evolution models, comparison with observations of stars in the Milky Way is an important consistency check for any proposed DTD.
 We implement several popular forms of the DTD in combination with multiple star formation histories for the Milky Way in %one-zone and
@@
 % Uncertainties in the progenitor channels of SNe Ia translate into uncertainties in the shape of the DTD. 
-% By formulating analytical DTDs for several progenitor models, \citet{Greggio2005-AnalyticalRates} found that the SD channel tends to produce a steeper DTD function than the DD channel, and the median delay time (by which 50\% of SNe Ia have exploded) can vary by a factor of 10 depending on the chosen progenitor scenario and its particular parameters.
+% By formulating analytic DTDs for several progenitor models, \citet{Greggio2005-AnalyticalRates} found that the SD channel tends to produce a steeper DTD function than the DD channel, and the median delay time (by which 50\% of SNe Ia have exploded) can vary by a factor of 10 depending on the chosen progenitor scenario and its particular parameters.
 As a result of the uncertainty regarding SN Ia progenitors, theoretical models have yet to converge on a single prediction for the DTD.
@@
 
-This paper presents the first\todo{(?)} comprehensive look at the DTD in a multi-zone GCE model that can qualitatively reproduce the observed abundance structure of the Milky Way disk.
+This paper presents a comprehensive look at the DTD in a multi-zone GCE model that can qualitatively reproduce the observed abundance structure of the Milky Way disk.
 A multi-zone approach allows for a radially-dependent parameterization of the SFH, outflows, stellar migration, and abundance gradient which can better match observations across the Galactic disk.
@@
         \Delta t        & 10 Myr    & \ref{sec:multizone-results} & Time-step size \\
-        t_{\rm max}     & 13.2 Gyr  & \ref{sec:multizone-results} & Maximum simulation time \\
+        t_{\rm max}     & 13.2 Gyr  & \ref{sec:multizone-results} & Disk lifetime \\
         n               & 8         & \ref{sec:multizone-results} & Number of stellar populations formed per ring per time-step \\
@@
 $R_{\rm Ia}$ is the DTD in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$,
-$t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the maximum simulation time.
+$t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the lifetime of the disk.
 The denominator of Equation \ref{eq:weighted-sfr} is therefore equal to $N_{\rm Ia}/M_\star$, the total number of SNe Ia per M$_{\odot}$ of stars formed.
@@
 Figure \ref{fig:dtds} presents a selection of these DTDs, and Table \ref{tab:dtds} summarizes all of our DTDs and their parameters.
-We use simple forms rather than simulated physical or analytical models of SNe Ia for the sake of decreased computational time and easier interpretation of the model predictions.
+We use simple forms rather than simulated physical or analytic models of SNe Ia for the sake of decreased computational time and easier interpretation of the model predictions.
 Physically-motivated models of the DTD must contend with many unknown or poorly-constrained parameters, so our simplified forms have the advantage of reducing the number of free parameters.
-In Appendix \ref{app:analytical-dtds}, we show that a few of our simple forms adequately approximate the more complete analytic models of \citet{Greggio2005-AnalyticalRates}.
+In Appendix \ref{app:analytic-dtds}, we show that a few of our simple forms adequately approximate the more complete analytic models of \citet{Greggio2005-AnalyticalRates}.
 
@@
 \citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assumed an exponential DTD with a timescale $\tau=1.5$ Gyr.
-We show in Appendix \ref{app:analytical-dtds} that this is an adequate approximation for the analytical SD DTD from \citet{Greggio2005-AnalyticalRates}.
+We show in Appendix \ref{app:analytic-dtds} that this is an adequate approximation for the analytic SD DTD from \citet{Greggio2005-AnalyticalRates}.
 However, there is less observational support for an exponential DTD.
@@
 To our knowledge, this form of the DTD has not been considered in previous GCE models.
-We show in Appendix \ref{app:analytical-dtds} that this form can approximate the more complicated analytical DD DTDs from \citet{Greggio2005-AnalyticalRates}.
+We show in Appendix \ref{app:analytic-dtds} that this form can approximate the more complicated analytic DD DTDs from \citet{Greggio2005-AnalyticalRates}.
 We investigate the cases $W=0.3$ Gyr and $W=1$ Gyr, taking $\alpha=-1.1$ for all plateau models.
@@
     \includegraphics[width=\linewidth]{figures/star_formation_histories.pdf}
-    \caption{The surface densities of star formation $\dot \Sigma_\star$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\tau_\star$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
+    \caption{The surface densities of star formation $\dot \Sigma_\star$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\tau_\star$ (fourth row) as functions of time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
 In each panel, we plot curves for the model zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
@@
 % In this model, the first infall produces the thick disk and the second infall produces the thin disk. 
-where $N_1$ and $N_2$ are the normalizations of the first and second infall, respectively, and $t_{\rm on}$ is the onset time of the second infall.
+where $N_1$ and $N_2$ are the normalizations of the first and second infall, respectively, and $t_{\rm on}$\todo{=4 Gyr? (citations)} is the onset time of the second infall.
 The normalization ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
@@
 Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in the middle panel of Figure \ref{fig:onezone-threepanel}.
-Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around a simulation time of 1 Gyr.
+Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around $t=1$ Gyr.
 Doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
@@
 In the following subsections, we present the stellar abundance and age distributions from the multi-zone models and compare to APOGEE data from across the Galactic disk.
+\todo{Need to update plot descriptions and scores for runs with updated yields.}
 
@@
 The abundance tracks of all four model SFHs initially follow a similar path of decreasing [O/Fe] with increasing [Fe/H].
-The ISM abundance ratios of the inside-out model change monotonically over the entire simulation time.
+The ISM abundance ratios of the inside-out model change monotonically over time.
 The stellar abundance distribution at both low- and high-[O/Fe] is composed of stars with a wide range of birth $R_{\rm gal}$.
@@
 We observe a ridge in the stellar abundance distribution at this turn-over point (${\rm [O/Fe]}\approx0.2$), which roughly coincides with the upper limit of the APOGEE distribution near the midplane.
-The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx0.0$ near the end of the simulation.
+The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx0.0$ near the end of the model.
 
@@
     \includegraphics{figures/ofe_feh_twoinfall.pdf}
-    \caption{The [O/Fe]--[Fe/H] plane for multiple Galactocentric regions from the model with the inside-out SFH and plateau ($W=0.3$ Gyr) DTD.
+    \caption{The [O/Fe]--[Fe/H] plane for multiple Galactocentric regions from the model with the inside-out SFH and plateau ($W=1$ Gyr) DTD.
 The two columns of panels contain stars in different bins of $R_{\rm gal}$, and each row contains stars from a different bin of $|z|$.
@@
 
-The best-scoring model uses the two-infall SFH with the plateau ($W=0.3$ Gyr) DTD.
-Figure \ref{fig:ofe-feh-twoinfall} plots the stellar [O/Fe]--[Fe/H] abundances from this model in the inner and outer Galaxy.
+Figure \ref{fig:ofe-feh-twoinfall} plots the stellar [O/Fe]--[Fe/H] abundances from the model with the two-infall SFH and plateau ($W=1$ Gyr) DTD in the inner and outer Galaxy.
 The model distributions in the outer Galaxy closely match the APOGEE distributions.
@@
 
-\todo{I just noticed that I was using slightly wrong yields in all of the multi-zone models (JW20 instead of J+21).
+% \todo{I just noticed that I was using slightly wrong yields in all of the multi-zone models (JW20 instead of J+21).
 I re-ran all the models and this corrected the end-point of the inside-out tracks, which are now at (0,0).
@@
 At worst, maybe we need to consider adjusting the yields for the two-infall models so that the [O/Fe] distributions are not significantly lower than every other SFH.}
+\todo{Needs to be updated for the new yields.}
 
@@
 The SFHs rank differently in the bimodality test, where the early-burst SFH is able to produce a bimodal [O/Fe] distribution for all DTDs, as discussed in Section \ref{sec:bimodality}.
+
+It is somewhat surprising that the early-burst models score poorly against the APOGEE [O/Fe] DFs, given that they produce the clearest bimodal distributions.
+This is because the KL divergence test heavily penalizes models with a high density in a region where the observations have little, as is the case for the high-$\alpha$ sequence in the outer Galaxy and close to the midplane.
+An iteration of this SFH where the early burst predominantly affects the inner galaxy might have more success at reproducing the [O/Fe] DF across the disk.
+
+The two-infall models are penalized by the KL divergence tests for producing abundance distributions which are not well aligned with the data (see the bottom-right panel of Figure \ref{fig:ofe-feh-sfh}).
+With a slightly lower $y_{\rm Fe}^{\rm Ia}$, the abundance tracks do not dip so far below ${\rm [O/Fe]}=0$, and the two-infall models out-perform every other SFH.
 
@@
 They find that, depending on the choice of CSFR, the DTDs of \citet{MatteucciRecchi2001-SNIaTimescale}, \citet{Mannucci2006-TwoPopulations}, \citet{Totani2008-DTD}, and the WIDE DD model of \citet{Greggio2005-AnalyticalRates} can all produce good fits to the observed cosmic SN Ia rate.
-This study provides a useful basis for comparison because the first and last of these DTDs are similar to our exponential ($\tau=1.5$ Gyr) and plateau ($W=1$ Gyr) DTDs, respectively (see Appendix \ref{app:analytical-dtds} for more discussion); the \citet{Mannucci2006-TwoPopulations} is our two-population DTD; and the \citet{Totani2008-DTD} is a $t^{-1}$ power-law with a minimum delay $t_D=100$ Myr.
+This study provides a useful basis for comparison because the first and last of these DTDs are similar to our exponential ($\tau=1.5$ Gyr) and plateau ($W=1$ Gyr) DTDs, respectively (see Appendix \ref{app:analytic-dtds} for more discussion); the \citet{Mannucci2006-TwoPopulations} is our two-population DTD; and the \citet{Totani2008-DTD} is a $t^{-1}$ power-law with a minimum delay $t_D=100$ Myr.
 It is noteworthy that the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale} best fits the majority of CSFRs in \citet{Palicio2024-CosmicSNIaRate}, and our similar exponential ($\tau=1.5$ Gyr) DTD {\it also} performs best across all our SFHs.
@@
 \citet{Palicio2024-CosmicSNIaRate} fit combinations of cosmic star formation rates (CSFRs) and DTDs, many of which are similar to the forms in this paper, to the observed cosmic SN Ia rate.
-Notably, the DTD which best fit the majority of their CSFRs was the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale}, which is similar to the exponential form with $\tau=1.5$ Gyr (see Appendix \ref{app:analytical-dtds} for more discussion).
+Notably, the DTD which best fit the majority of their CSFRs was the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale}, which is similar to the exponential form with $\tau=1.5$ Gyr (see Appendix \ref{app:analytic-dtds} for more discussion).
 \citet{Palicio2024-CosmicSNIaRate} are able to exclude DTDs with a very high or very low fraction of prompt SNe Ia, but a number of their DTDs could produce a convincing fit to the observed rates with the right CSFR.
@@
 
-% [Is the MW DTD the same as elsewhere?]
+% Is the MW DTD the same as elsewhere?
 Our finding that the $t^{-1}$ power-law DTD poorly reproduces observed abundances could signal that the Milky Way and other galaxies obey different DTDs.
@@
 
-\todo{Discuss yield effects.}
+Our model scores are highly sensitive to small changes in the nucleosynthetic yields.
+A decrease in the SN Ia yield of Fe to $y_{\rm Fe}^{\rm Ia}=0.0017$, which only shifts the end-point of the gas abundance tracks up by $\sim+0.05$ dex in [O/Fe], produces dramatically different scores for many of the models.
+\todo{More discussion of yield effects.}
+
+\todo{Briefly discuss radial migration trends, refer back to J21. Future work on implications of radial migration on the disk abundance structure.}
 
@@
 
-% [Why does two-infall do so well across the board, even in the [Fe/H] and [O/Fe] DFs where it seems worse by eye?]
-Across nearly every observable in Table \ref{tab:results}, the two-infall models outperform every other SFH.
-In some cases this does indicate that the two-infall SFH is more successful at reproducing the observed distributions, as is the case in the age--[O/Fe] plane (Figure \ref{fig:age-ofe-sfh}).
-It is somewhat surprising that the two-infall models score higher than the early-burst even for the [O/Fe] DFs, when the double-peaked distributions produced by the latter are qualitatively closer to the APOGEE data than the former's triple-peaked distributions.
-This is because the KL divergence test heavily penalizes models with a high density in a region where the observations have little, as is the case for the high-$\alpha$ sequence in the outer Galaxy and close to the midplane.
-
-[Compare to previous studies]
-Discuss \citet{Matteucci2006-BimodalDTDConsequences} findings of the \citet{Mannucci2006-TwoPopulations} DTD in the two-infall model.
-
-\citet{Palicio2023-AnalyticDTD} compare seven different DTDs, including the analytical SD, DD-WIDE, and DD-CLOSE, as well as the empirical two-population and $t^{-1}$ power-law DTDs, in a one-zone model with a two-infall SFH.
-[Note that they use some different parameters for the analytical models than we do).
-Critically for our purposes, and in contrast to previous studies of the two-infall model \citep[e.g.,][others]{Chiappini1997-TwoInfall,Spitoni2021-TwoInfall}, the authors include the effects of outflows, although they explore mass-loading values of $\eta=0.2-0.8$ which is significantly lower than in our models.
-
-[More discussion of \citet{Matteucci2009-DTDModels}, which is multi-zone but only compares to the solar neighborhood, and no radial migration.]
-
-To our knowledge, this paper is the first exploration of a two-infall SFH which incorporates both mass-loading and radial migration.
-A detailed examination of the two-infall SFH in our GCE models is beyond the scope of this paper, but will be the subject of future work.
+There have been many comparative GCE studies of the DTD with the two-infall model, providing an important point of comparison with our models.
+For example, \citet{Matteucci2006-BimodalDTDConsequences} explored the consequences of the two-population DTD \citep{Mannucci2006-TwoPopulations}, finding that its very high prompt SN Ia rate began to pollute the ISM during the halo phase and led to a faster decline in [O/Fe] with [Fe/H].
+\citet{Matteucci2009-DTDModels} compared several DTDs, including the analytic forms of \citet{Greggio2005-AnalyticalRates} and the two-population DTD, in a multi-zone GCE model of the disk.
+Their comparisons to data were limited to the solar neighborhood, and unlike our models, they did not factor in radial migration or gas outflows.
+Nevertheless, their conclusions align fairly well with ours: that a relatively low fraction of prompt SNe Ia is needed to produce good agreement with observations, and that a higher prompt fraction worsens that agreement.
+
+More recently, \citet{Palicio2023-AnalyticDTD} compared a similar suite of DTDs in one-zone models with a two-infall SFH.
+In contrast to previous studies of the two-infall model \citep[e.g.,][]{Chiappini1997-TwoInfall,Matteucci2009-DTDModels,Spitoni2021-TwoInfall}, they do incorporate gas outflows, making their models especially well-suited to compare to ours.
+\citet{Palicio2023-AnalyticDTD} achieve a good fit with solar neighborhood data for analytic DTDs for both SD and DD progenitors, which are approximated by our exponential ($\tau=1.5$ Gyr) and plateau ($W=1$ Gyr) models, respectively.
+
+To our knowledge, this paper is the first exploration of the two-infall SFH in a multi-zone GCE model which incorporates both mass-loading and radial migration.
+A detailed examination of the parameters of the two-infall model is beyond the scope of this paper, but will be the subject of future work.
 
@@
 
+\citet{Mackereth2018-AlphaBimodality} find the appearance of a MW-like bimodality in the EAGLE simulations is rare, occurring in only $\sim5\%$ of their sample.
+
 % Taken from introduction
-A complicating factor in observing and modeling the effects of the DTD is the migration of stars throughout the disk.
+% A complicating factor in observing and modeling the effects of the DTD is the migration of stars throughout the disk.
 \citet{SellwoodBinney2002-RadialMixing} first demonstrated that a transient spiral perturbation (or other potential feature; see [citations]) can cause resonant interactions which adjust stars' guiding center radii without leading to kinematic heating of the disk.
@@
 The first GCE model to incorporate radial mixing was developed by \citet{Schonrich2009-RadialMixing}, and subsequent studies have incorporated more comprehensive numerical treatments of radial migration and the effect of a central bar \citep[e.g.,][]{Minchev2013-ChemodynamicalEvolution}.
-%In this paper, we follow the treatment by \citetalias{Johnson2021-Migration}, who [describe treatment].
-
-\citet{Karapetyan2022-SNIaDistances} find a correlation between the SN Ia light curve decline rate, $\Delta m_{15}$, and the distance between the SN and the star-forming shock front of spiral arms.
+% %In this paper, we follow the treatment by \citetalias{Johnson2021-Migration}, who [describe treatment].
+
+% \citet{Karapetyan2022-SNIaDistances} find a correlation between the SN Ia light curve decline rate, $\Delta m_{15}$, and the distance between the SN and the star-forming shock front of spiral arms.
 As this distance is expected to be an indicator of the age of the SN progenitor, such a correlation would suggest that the less-luminous, faster-declining SNe Ia come from an older progenitor population, which would be expected from progenitor models with sub-Chandrasekhar mass explosions.
@@
 It could be interesting to incorporate a SN Ia yield which varies with progenitor age into a GCE model.
-[Are there analytic DTDs for a DD progenitor with sub-Chandra explosions?]
-
-Something about \citetalias{Johnson2021-Migration} and \citet{Schonrich2009-RadialMixing}.
-
-\citet{Mackereth2018-AlphaBimodality} find the appearance of a MW-like bimodality in the EAGLE simulations is rare, occurring in only $\sim5\%$ of their sample.
+% [Are there analytic DTDs for a DD progenitor with sub-Chandra explosions?]
+
+% Something about \citetalias{Johnson2021-Migration} and \citet{Schonrich2009-RadialMixing}.
 
@@
 
-We have explored the consequences of eight different DTDs for SNe Ia in combination with four different SFHs in multi-zone GCE models with radial migration.
+We have explored the consequences of eight different forms for the SN Ia DTD in multi-zone GCE models with radial migration.
+For each DTD, we explored combinations with four different popular SFHs from the literature, which represent a broad range of behavior over the lifetime of the disk.
+% in combination with four different SFHs in multi-zone GCE models with radial migration. 
 We compared our model outputs to abundances from APOGEE and ages from \citetalias{Leung2023-Ages} for stars across the Milky Way disk.
@@
 
+% \todo{We don't have a good combination of SFH+DTD+yields+etc that can explain everything we observe about the Milky Way.
+Emphasize how comprehensive this was.
+We focus on the comparisons that are most interesting, but this is a very broad look at}
+
 \begin{itemize}
-    \item The exponential DTD with a timescale of $\tau=1.5$ Gyr is best able to reproduce the observed abundance patterns for all four SFHs.
+    \item While some combinations of SFH and DTD perform better than others, none of our models are able to reproduce every observed feature of the Milky Way disk.
+
+    \item The plateau DTD with a width $W=1$ Gyr is best able to reproduce the observed abundance patterns for three of the four SFHs.
+For the inside-out SFH, it is narrowly surpassed by the (similar) triple-system DTD.
+    % \item The exponential DTD with a timescale of $\tau=1.5$ Gyr is best able to reproduce the observed abundance patterns for all four SFHs.
 
@@
     \item The SFH is the critical factor for producing a bimodal [O/Fe] distribution at fixed [Fe/H].
-On its own, the DTD cannot produce a bimodal [O/Fe] distribution that matches what is observed, but it does affect the location and strength of the high-$\alpha$ sequence, potentially enhancing the $\alpha$-bimodality resulting from the choice of SFH.
-Radial migration also cannot reproduce the $\alpha$-bimodality on its own.
+On its own, the DTD cannot produce a bimodal [O/Fe] distribution that matches what is observed, but it does affect the location and strength of the high-$\alpha$ sequence, potentially enhancing the \aFe bimodality resulting from the choice of SFH.
+Radial migration also cannot reproduce the \aFe bimodality on its own.
 
     \item The MDF is more sensitive to the choice of SFH than the DTD.
-Overall trends across the Galaxy are primarily driven by the assumed radial abundance gradient and stellar migration prescription, although the MDF in the inner Galaxy is more sensitive to the DTD than elsewhere.
+Overall trends in the MDF across the Galaxy are primarily driven by the assumed radial abundance gradient and stellar migration prescription, although it is more sensitive to the DTD in the inner Galaxy than elsewhere.
 
@@
 A similar metallicity dependence has also been observed in the rate of CCSNe \citep{Pessi2023-MetalDepCCSNe}.
-The consequences of a metallicity-dependent SN Ia rate in the context of a multi-zone GCE simulation with radial migration could be explored in a future paper.
+The consequences of a metallicity-dependent SN Ia rate in the context of a multi-zone GCE model with radial migration could be explored in a future paper.
 A metallicity dependence on the {\it shape} of the DTD could also be interesting to explore, for example if binary evolution leads to different progenitor systems at low and high metallicity.
@@
 
-\section{Analytical DTDs}
-\label{app:analytical-dtds}
+\section{Analytic DTDs}
+\label{app:analytic-dtds}
 
@@
     \includegraphics[width=0.49\linewidth]{figures/onezone_analytical_dtd.pdf}
-    \caption{\textit{Left:} Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and simple DTD functions (dashed curves).
+    \caption{\textit{Left:} Analytic DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and simple DTD functions (dashed curves).
 Some functions are presented with a constant multiplicative factor for visual clarity.
-\textit{Right:} Abundance tracks and distributions from one-zone models with the analytical and simple DTDs (same color scheme).
+\textit{Right:} Abundance tracks and distributions from one-zone models with the analytic and simple DTDs (same color scheme).
 For clarity, we vary the mass-loading factor to be $\eta=4$, $\eta=2$, and $\eta=1$ for the red, green, and blue curves, respectively.
-All model parameters between the similarly-colored solid and dashed curves are identical.}
-    \label{fig:analytical-dtd}
+All other model parameters are identical.}
+    \label{fig:analytic-dtds}
     \script{analytical_dtd_twopanel.py}
@@
 
-Discuss \citet{Greggio2005-AnalyticalRates} vs our simple function approximations here?
-
-\citet{Greggio2005-AnalyticalRates} derives analytical DTDs for SD and DD progenitor systems from assumptions about binary stellar evolution and outcomes of mass exchange.
-They find that the parameters which have a large effect on the shape of the DTD are the distribution and range of stellar masses in progenitor systems; the efficiency of accretion in the SD scenario; and the distribution of separations at birth in the DD scenario.
-The left-hand panel of Figure \ref{fig:analytical-dtd} shows the analytical DTDs for SD progenitors and two different prescriptions for DD progenitors (``WIDE'' and ``CLOSE'').
-In the ``WIDE'' scheme, it is assumed that there is a wide distribution of ratios $A/A_0$ of the separation of the DD system to the initial separation of the binary, and that the distributions of $A$ and total mass of the system $m_{\rm DD}$ are independent, so one cannot necessarily predict the total merge time of a system based on its initial parameters.
+\citet{Greggio2005-AnalyticalRates} derived analytic DTDs for SD and DD progenitor systems from assumptions about binary stellar evolution and mass exchange.
+Significant parameters for the shape of the DTD are the distribution and range of stellar masses in progenitor systems, the efficiency of accretion in the SD scenario, and the distribution of separations at birth in the DD scenario.
+The left-hand panel of Figure \ref{fig:analytic-dtds} shows several of the \citet{Greggio2005-AnalyticalRates} analytic DTDs: one for SD progenitors, and two different prescriptions for DD progenitors (``WIDE'' and ``CLOSE'').
+The difference between the DD prescriptions relates to the ratio between the separation of the DD system and the initial separation of the binary, $A/A_0$.
+In the ``WIDE'' scheme, it is assumed that $A/A_0$ spans a wide distribution, and that the distributions of $A$ and total mass of the system $m_{\rm DD}$ are independent, so one cannot necessarily predict the total merge time of a system based on its initial parameters.
 In the ``CLOSE'' scheme, there is assumed to be a narrow distribution of $A/A_0$ and a correlation between $A$ and $m_{\rm DD}$, so the most massive binaries tend to merge quickly and the least massive merge last.
 
-The right-hand panel of Figure \ref{fig:analytical-dtd} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs.
-We assume $\eta=2.5$, $\tau_\star=2$ Gyr, an inside-out SFH evaluated at a radius of 8 kpc, a continuous recycling approximation, and a minimum SN Ia delay of 40 Myr.
-We compare the SD, DD WIDE, and DD CLOSE schemes to standard power-law, broken power-law, and exponential DTDs.
-The SD and DD CLOSE DTDs follow nearly identical tracks in [O/Fe] vs [Fe/H]; however, their distributions on [O/Fe] differ at the low end.
-The SD DTD follows an exponential with a 1.5 Gyr timescale, whereas the DD CLOSE DTD is well-approximated by a broken power-law with an initial plateau of 300 Myr and a subsequent declining slope of -1.1.
-The WIDE prescription is likewise best approximated by a broken power-law, but with a longer plateau width of 1 Gyr.
-In all cases, the difference between the analytical DTD and the nearest broken power-law or exponential is likely too small to be observationally detectable, so in our multi-zone models we implement the more generic functions in lieu of the analytical DTDs.
-
-A multi-zone with the \citet{Greggio2005-AnalyticalRates} SD DTD produced nearly identical results to an exponential DTD with a 1.5 Gyr timescale.
-
-\section{Stellar Migration \& Midplane Distances}
+In the left-hand panel of Figure \ref{fig:analytic-dtds}, we also include simple functions which approximate the analytic DTDs of \citet{Greggio2005-AnalyticalRates}.
+Chemical abundance distributions are sensitive to the broad shape of the DTD but are agnostic to the underlying physics of the progenitor systems.
+These simplified forms reduce the number of free parameters for the DTD and make the GCE model predictions easier to interpret.
+
+The right-hand panel of Figure \ref{fig:analytic-dtds} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs and our simplified forms.
+We use the same model parameters as in Section \ref{sec:onezone-results}.
+The model with the SD DTD follows a nearly identical track to the exponential ($\tau=1.5$ Gyr) DTD, and they produce very similar distributions of [O/Fe].
+Likewise, the DD CLOSE DTD is well approximated by the plateau DTD with $W=0.3$ Gyr and a power-law slope $\alpha=-1.1$.
+The WIDE prescription is also best approximated by a plateau DTD, but with a longer plateau width of $W=1$ Gyr.
+In all cases, the difference between the analytic DTD and its simple approximation is too small to be observed.
+We also ran a multi-zone model with the inside-out SFH and the \citet{Greggio2005-AnalyticalRates} SD DTD and found it produced nearly identical results to the model with the exponential ($\tau=1.5$ Gyr) DTD.
+
+\section{Stellar Migration}
 \label{app:migration}
@@
 
+In their multi-zone models, \citetalias{Johnson2021-Migration} randomly assign an analogue star particle from \hydro, adopting its radial migration distance $\Delta R$ and final midplane distance $z$, for each stellar population generated by \vice.
+This allows \vice to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
+However, in regions where the number of \hydro star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single \hydro star particle can be assigned as an analogue to multiple \vice stellar populations.
+These populations will have similar formation and migration histories and consequently similar abundances, which produces unphysical ``clumps'' of stars in the abundance distributions at large $|z|$ and $R_{\rm gal}$.
+
+We adopt a prescription for radial migration which produces smoother abundance distributions while still following the behavior of \hydro.
+We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm form}$ from the \hydro output, binned by both formation radius $R_{\rm form}$ and age.
+We are motivated by the findings of \citet{Okalidis2022-AurigaMigration} that the strength of stellar migration in the Auriga simulations \todo{(cite?)} varies with both $R_{\rm form}$ and age.
+Each Gaussian is centered at 0, and we find that the scale $\sigma_{\rm RM}$ is best described by the function
+% \begin{equation}
+%     \sigma_{\rm RM} = 1.35\,{\rm kpc} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61} \Big(\frac{\tau}{1\,{\rm Gyr}}\Big)^{0.33}
+%     \label{eq:radial-migration}
+% \end{equation}
+\begin{equation}
+    \sigma_{\rm RM} = \sigma_{\rm RM8} \Big(\frac{\tau}{8\,{\rm Gyr}}\Big)^{0.33} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61}
+    \label{eq:radial-migration}
+\end{equation}
+where $\tau$ is the stellar age and $\sigma_{\rm RM8}=2.68$ kpc describes the migration strength for an 8 Gyr old population with $R_{\rm form}=8$ kpc. 
+For comparison, \citet{Frankel2018-RadialMigration} found a steeper $\tau$-dependence of $\sigma_{\rm RM}\propto \tau^{1/2}$ and a higher scaling of $\sigma_{\rm RM8}=3.6$ kpc for a sample of APOGEE red clump stars.
+Our age scaling is in good agreement with \citet{Lu2023-LMCStars}, who find that radial migration in galaxies from the NIHAO simulations \todo{(cite?)} follow a relatively universal relation of $\sigma_{\rm RM}\propto\tau^{0.32}$.
+% This value is $\sim30\%$ smaller than that found by \citet{Frankel2019-InsideOutGrowth}.
+
+When \vice forms a stellar population at initial radius $R_{\rm form}$, we assign a value of $\Delta R$ by randomly sampling from a Gaussian with a width given by Equation \ref{eq:radial-migration}.
+The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citetalias{Johnson2021-Migration}, but with a time dependence $\propto \Delta t^{1/3}$.
+This is motivated by the age-scaling of $\sigma_{\rm RM}$ and is slower than the diffusion process of, e.g., \citet{Frankel2018-RadialMigration}.
+
+We note that the \hydro galaxy has a weak and transient bar, in contrast to the Milky Way.
+The presence of a strong bar has been found to affect the strength of radial migration throughout the disk \citep[e.g.,][]{Brunetti2011-BarredSpiralDiffusion,Okalidis2022-AurigaMigration} and lead to a flattening of the metallicity gradient for old populations \citet{Okalidis2022-AurigaMigration}.
+% also a slower timestep evolution than diffusion
+% \citet{Okalidis2022-AurigaMigration} studied the stellar migration in the Auriga simulations and found that the migration strength had both a dependence on age and formation radius.
+They also found that in strongly-barred galaxies, the migration is stronger overall but has a slower timestep evolution than diffusion ($\Delta t^{0.5}$).
+\todo{They argue that the bar has a minimal effect.}
+% On the other hand, \citet{Brunetti2011-BarredSpiralDiffusion} argue that the bar has a strong effect on the strength of radial migration and that its effect is not constant with time.
+
+Figure \ref{fig:radial-migration} compares the distributions of $R_{\rm final}$ in bins of $R_{\rm form}$ and stellar age between the \hydro analogue method and our new prescription.
+There is good agreement across the Galaxy in the youngest age bins, but the ``clumpiness'' of the \hydro analogue populations becomes evident for old stars formed in the outer Galaxy.
+The distribution of \hydro star particles in the $10\leq\tau<12$ Gyr and $11\leq R_{\rm form}<13$ kpc bin indicates significant inward migration due to a merging satellite.
+Our Gaussian sampling scheme eliminates both the clumpiness and the impact of mergers and other external events on radial migration.
+
 \begin{figure*}
@@
 
-For each star particle in \vice, \citetalias{Johnson2021-Migration} randomly assign an analogue star particle from \hydro and adopt its radial migration distance $\Delta R$ and final midplane distance $z$.
-This allows \vice to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
-However, in regions where the number of \hydro star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single \hydro star particle can be assigned as an analogue to multiple \vice stellar populations.
-These populations will have similar formation and migration histories and consequently similar abundances, which produces unphysical ``clumps'' of stars in the abundance distributions at high latitudes and large radii.
-
-We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm initial}$ from the \hydro output in bins of $R_{\rm initial}$ and age.
-Each Gaussian is centered at 0 and we find that the scale $\sigma_{\Delta R}$ is best described by the function
-\begin{equation}
-    \sigma_{\Delta R} = 1.35\,{\rm kpc} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61} \Big(\frac{T}{1\,{\rm Gyr}}\Big)^{0.33}
-    \label{eq:radial-migration}
-\end{equation}
-where $T$ is the age of the star particle.
-
-We fit a sech$^2$ function \citep{Spitzer1942} to the distribution of midplane distances $z$.
-Vertical migration away from the midplane does not affect the chemical evolution model, but we do use $z$ in our analysis.
-The probability density function (PDF) of $z$ given some scale height $h_z$ is
-\begin{equation}
-    {\rm PDF}(z) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z}{2 h_z}\Big)
+Like \citetalias{Johnson2021-Migration}, we assume all stellar populations form in the midplane ($z=0$).
+\citetalias{Johnson2021-Migration} take the final midplane distance $z_{\rm final}$ from the \hydro analogue particle.
+To produce smoother abundance distributions, we fit a sech$^2$ function \citep{Spitzer1942} to the distribution of $z$ in \hydro.
+% Vertical migration away from the midplane does not affect the chemical evolution model, but we do use $z$ in our analysis. 
+The PDF of $z_{\rm final}$ given some scale height $h_z$ is
+\begin{equation}
+    {\rm PDF}(z_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z_{\rm final}}{2 h_z}\Big)
     \label{eq:sech-pdf}
@@
 \begin{equation}
-    {\rm CDF}(z) = \frac{1}{1 + e^{-z / h_z}}.
+    {\rm CDF}(z_{\rm final}) = \frac{1}{1 + e^{-z_{\rm final} / h_z}}.
     \label{eq:sech-cdf}
 \end{equation}
-We fit the above function to the distributions of $z$ in \hydro in varying bins of $T$ and $R_{\rm final}$ and found that $h_z$ is best described by the function
-\begin{equation}
-    h_z = (0.25\,{\rm kpc}) 
-    e^{\frac{T-5\,{\rm Gyr}}{7.0\,{\rm Gyr}}}
-    e^{\frac{R_{\rm final}-8\,{\rm kpc}}{6.0\,{\rm kpc}}}.
+We fit Equation \ref{eq:sech-pdf} to the distributions of $z$ in \hydro in varying bins of $T$ and $R_{\rm final}$. We find that $h_z$ is best described by the function
+\begin{equation}
+    h_z = h_{z,8} \exp(\tau/\tau_s + R_{\rm final}/R_s)
     \label{eq:scale-height}
 \end{equation}
-
-When a star particle is created by \vice at initial radius $R_{\rm form}$, we sample its total radial migration distance $\Delta R$ from a Gaussian with a width described by Equation \ref{eq:radial-migration}, and we sample its final midplane distance $z_{\rm final}$ from the distribution described by Equation \ref{eq:sech-pdf} with a width given by Equation \ref{eq:scale-height}.
-The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citetalias{Johnson2021-Migration}, but with a time dependence $\propto \Delta t^{1/3}$.
-This produces distributions of $R_{\rm final}$ and $z_{\rm final}$ which are similar to the analogue migration case for all but the oldest stars.
-
-\citet{Okalidis2022-AurigaMigration} studied the stellar migration in the Auriga simulations and found that the migration strength had both a dependence on age and formation radius.
-They also found that in strongly-barred galaxies, the migration is stronger overall but has a slower timestep evolution than diffusion ($\Delta t^{0.5}$).
-\todo{They argue that the bar has a minimal effect.}
-On the other hand, \citet{Brunetti2011-BarredSpiralDiffusion} argue that the bar has a strong effect on the strength of radial migration and that its effect is not constant with time.
-
-Figure \ref{fig:radial-migration} compares the distributions of $R_{\rm final}$ in bins of $R_{\rm form}$ and age between the analogue and Gaussian migration schema.
-
-\citet{Lu2023-LMCStars} examined radial migration strengths in galaxies from the NIHAO simulations.
-They found that it predicts galaxies to follow a relatively universal relation of $\sigma_{\rm RM}\propto \tau^{0.32}$, which is slower than the diffusion process of, e.g., \citet{Frankel2019-InsideOutGrowth}, but quite similar to our own age dependence.
+where $h_{z,8}=0.032$ kpc, $\tau_s=7$ Gyr, and $R_s=6$ kpc.
+For each star particle in \vice, we sample $z_{\rm final}$ from the distribution described by Equation \ref{eq:sech-pdf} with a width given by Equation \ref{eq:scale-height}.
+Figure \ref{fig:midplane-distance} shows the resulting distributions of $z_{rm final}$ are similar to the \hydro analogue scheme for all but the oldest stellar populations.
 

### 2024-04-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
+% For TeXworks
+\makeatletter
+\declare@file@substitution{revtex4-1.cls}{revtex4-2.cls}
+\makeatother
+
 % Define document class
@@
     % whereas a DTD with more delayed SNe Ia produces a distribution that is skewed toward higher \aFe.
-    While the DTD alone cannot explain the observed bimodality in the \aFe distribution, in combination with an appropriate star formation history it affects the goodness of fit between the simulated and observed high-$\alpha$ sequence.
+    While the DTD alone cannot explain the observed bimodality in the \aFe distribution, in combination with an appropriate star formation history it affects the goodness of fit between the predicted and observed high-$\alpha$ sequence.
 Our model results favor an extended DTD with fewer prompt SNe Ia than the fiducial $t^{-1}$ power law.
@@
 Type Ia supernovae (SNe Ia), the thermonuclear explosions of carbon-oxygen white dwarfs (WDs), are responsible for a majority of the Fe produced in the Galaxy \citep{Matteucci1986-SupernovaEnrichment}; meanwhile, core collapse supernovae (CCSNe), the explosions of massive stars, produce the $\alpha$-elements (e.g., O and Mg) in addition to a smaller fraction of Fe.
-SNe Ia are delayed by $\sim0.1-10$ Gyr after star formation events, as evidenced by observations at large distances from star forming regions and in elliptical galaxies \citep[e.g.,][]{Maza1976-SNStatistics}.
+SNe Ia are delayed by $\sim0.1-10$ Gyr after star formation events, as evidenced by observations at large distances from star-forming regions and in elliptical galaxies \citep[e.g.,][]{Maza1976-SNStatistics}.
 This delayed enrichment leads to a decrease in \aFe with increasing [Fe/H] \citep{Matteucci1986-SupernovaEnrichment}.
@@
 A few studies have investigated different DTDs in one-zone chemical evolution models, but comparisons to abundance data have been limited to the solar neighborhood \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
-\citet{Matteucci2009-DTDModels} compared five DTDs in a multi-zone GCE model and found that the agreement with observations worsens if the fraction of prompt SNe Ia is either too high or too low, but they were similarly limited by the the available data for the solar neighborhood.
+\citet{Matteucci2009-DTDModels} compared five DTDs in a multi-zone GCE model and found that the agreement with observations worsens if the fraction of prompt SNe Ia is either too high or too low, but they were similarly limited by the available data for the solar neighborhood.
 \citet{Poulhazan2018-PrecisionPollution} found that the prompt component of the DTD affects the peak and width of the \aFe distribution in a cosmological smoothed-particle hydrodynamics simulation, but their simulation was not designed to reproduce the parameters of the Milky Way.
-The current era of large spectroscopic surveys such as the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE} and the forthcoming Milky Way Mapper \citep{Kollmeier2017-SDSS-V} has made abundances across the Milky Way disk available for comparison to more sophisticated GCE models.
+The current era of large spectroscopic surveys such as the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE} and the ongoing Milky Way Mapper \citep{Kollmeier2017-SDSS-V} has made abundances across the Milky Way disk available for comparison to more sophisticated GCE models.
 
@@
 \begin{deluxetable*}{Cccl}
-    \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models.
+    \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}).
 We omit some parameters that are unchanged from \citetalias{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
@@
     \includegraphics{figures/delay_time_distributions.pdf}
-    \caption{Selection of models for the SN Ia delay-time distribution (DTD) used in this paper.
+    \caption{Selection of models for the SN Ia DTD used in this paper.
 All functions are normalized such that $f_{\rm Ia}(t=1\,{\rm Gyr})=1$.
-The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD} at the same scale as the DTDs.
-The horizontal and vertical error bars indicate the time range and 1$\sigma$ uncertainties, respectively, of each DTD measurement.
+The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD} at the same scale as the model DTDs.
+The horizontal and vertical error bars indicate the time range and 1$\sigma$ uncertainties of each DTD measurement, respectively.
 The colored circles along the horizontal axis indicate the median delay time for each model.}
@@
     \centering
-    \caption{Summary of SN Ia delay-time distributions (DTDs) explored in this paper.}
+    \caption{Summary of SN Ia DTDs explored in this paper (see discussion in Section \ref{sec:dtd-models}).}
     \label{tab:dtds}
@@
     \includegraphics[width=\linewidth]{figures/star_formation_histories.pdf}
-    \caption{The surface densities of star formation $\dot \Sigma_\star$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\tau_\star$ (fourth row) as functions of time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
+    \caption{The surface densities of star formation $\dot \Sigma_\star$ (first row from the top), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\tau_\star$ (fourth row) as functions of time for our four model SFHs (see discussion in Section \ref{sec:sfh}): inside-out (first column from the left; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-taustar} and \ref{eq:earlyburst-ifr}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}).
 In each panel, we plot curves for the model zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
@@
 \citet{Stahlholdt2022-StarFormationEpochs} found evidence for a burst $\sim10$ Gyr ago which marks the beginning of a second phase of star formation.
-An early infall-driven burst of star formation has been found to lead to MW-like $\alpha$-bimodality in the EAGLE simulations \citep{Mackereth2018-AlphaBimodality} \todo{(cite EAGLE?)}.
+\citet{Mackereth2018-AlphaBimodality} found that an early infall-driven burst of star formation can lead to a MW-like $\alpha$-bimodality in the EAGLE simulations \citep{Crain2015-EAGLE,Schaye2015-EAGLE}.
 We adopt the following formula for the time-dependence of the SFE timescale from \citet{Conroy2022-ThickDisk}:
@@
 % In this model, the first infall produces the thick disk and the second infall produces the thin disk. 
-where $N_1$ and $N_2$ are the normalizations of the first and second infall, respectively, and $t_{\rm on}$\todo{=4 Gyr? (citations)} is the onset time of the second infall.
-The normalization ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
+where $\tau_1=1$ Gyr and $\tau_2=4$ Gyr are the exponential timescales of the first and second infall, respectively, and $t_{\rm on}=4$ Gyr is the onset time of the second infall \citep[based on typical values in, e.g.,][]{Chiappini1997-TwoInfall,Spitoni2020-TwoInfall,Spitoni2021-TwoInfall}.
+$N_1$ and $N_2$ are the normalizations of the first and second infall, respectively, and their ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
 \begin{equation}
@@
 Following \citet{BlandHawthornGerhard2016-MilkyWayReview}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
-We note that most previous studies which use the two-infall model \citep[e.g.,][]{Chiappini1997-TwoInfall,Matteucci2006-BimodalDTDConsequences,Matteucci2009-DTDModels,Spitoni2021-TwoInfall} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance.
+We note that most previous studies which use the two-infall model \citep[e.g.,][]{Chiappini1997-TwoInfall,Matteucci2006-BimodalDTDConsequences,Matteucci2009-DTDModels,Spitoni2019-TwoInfall} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance.
 We adopt radially-dependent outflows as in \citetalias{Johnson2021-Migration} (see their Section 2.4 for details) for all our SFHs, including two-infall.
@@
     \centering
-    \caption{Sample selection parameters and median uncertainties from APOGEE DR17.}
+    \caption{Sample selection parameters and median uncertainties from APOGEE DR17 (see Section \ref{sec:observational-sample}).}
     \label{tab:sample}
@@
     \includegraphics[width=\linewidth]{figures/onezone_threepanel.pdf}
-    \caption{{\it Each panel:} Abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume the same DTD form.
+    \caption{Abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models (see discussion in Section \ref{sec:onezone-results}) which assume the various DTD shapes (see Figure \ref{fig:dtds}).
 The open symbols along each curve mark logarithmic steps in time.
@@
 For display purposes, these distributions are convolved with a Gaussian kernel with a standard deviation of 0.02 dex.
-    \textit{Left:} Three models which assume a power-law DTD with varying slope $\alpha$. 
+    \textit{Left:} A power-law DTD with varying slope $\alpha$. 
     % The dotted, dashed, and solid curves represent models with $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively. 
     For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr. 
-    \textit{Center:} Three models which assume an exponential DTD with varying timescale $\tau$. 
+    \textit{Center:} An exponential DTD with varying timescale $\tau$. 
     % The solid, dashed, and dotted curves represent $\tau=6$, 3, and 1.5 Gyr, respectively.
-    \textit{Right:} Three models which assume a plateau DTD with varying plateau width $W$. 
+    \textit{Right:} A plateau DTD with varying width $W$. 
     % The solid, dashed, and dotted green curves represent $W=1$, 0.3, and 0.1 Gyr, respectively. 
@@
     \includegraphics[width=\linewidth]{figures/onezone_twopanel.pdf}
-    \caption{\textit{Left:} Comparison of one-zone models with different minimum delay times $t_D$ and DTDs.
+    \caption{\textit{Left:} Comparison of one-zone models with different combinations of minimum delay time $t_D$ and DTD shape.
     % minimum SN Ia delay times $t_D=40$ Myr (solid) and 150 Myr (dashed curves) for three DTDs: power-law with $\alpha=-1.1$ (blue), plateau with $W=0.3$ Gyr (green), and exponential with $\tau=1.5$ Gyr (purple curves).
     The layout is similar to Figure \ref{fig:onezone-threepanel}.
-For clarity, we assume a mass-loading factor $\eta=1$ for the exponential DTD curves, which places the end-point of the abundance tracks at higher [Fe/H].
-    \textit{Right:} Comparison of one-zone models with five different forms for the DTD.
+For visual clarity, we assume a mass-loading factor $\eta=1$ for the exponential DTD curves, which places the end-point of the abundance tracks at higher [Fe/H].
+    \textit{Right:} Comparison of one-zone models with five different DTD models (see Figure \ref{fig:dtds}).
     % : triple-system (yellow), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
@@
 In Figure \ref{fig:onezone-twopanel}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (dashed purple line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (solid green line), and their [O/Fe] DFs are virtually identical.
-For the exponential ($\tau=3$ Gyr) DTD, the the two values of $t_D$ produce nearly indistinguishable outputs.
+For the exponential ($\tau=3$ Gyr) DTD, the two values of $t_D$ produce nearly indistinguishable outputs.
 We do not consider the effect on the other DTDs because a 150 Myr minimum delay time is incompatible with the two-population model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD due to its low SN Ia rate at short delay times.
@@
     \includegraphics[width=\linewidth]{figures/feh_df_comparison.pdf}
-    \caption{Metallicity distribution functions (MDFs) from multi-zone models with various models for the SFH and DTD.
-Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}).
+    \caption{MDFs from multi-zone models with various SFHs and DTDs.
+Each row presents distributions of stars within a range of midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}).
 Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue).
@@
     \textit{Right columns:} comparison between the power-law ($\alpha=-1.4$) and exponential ($\tau=3$ Gyr) DTDs with the inside-out SFH.
-The MDFs in the inner Galaxy show the greatest change between the DTDs.}
+The MDFs in the inner Galaxy show the greatest change between the DTDs (see discussion in Section \ref{sec:feh-df}).}
     \label{fig:feh-df-comparison}
@@
 
-The model combination with the best (lowest) score for the MDF is the two-infall SFH with the exponential ($\tau=3$ Gyr) DTD.
-The choice of SFH has a larger effect on the overall score than the DTD, and the best-performing SFH is the two-infall model, followed closely by the early-burst.
-However, the difference between the best-scoring model and the worst (late-burst SFH with triple-evolution DTD) is fairly small.
+The model combination with the best (lowest) score for the MDF is the two-infall SFH with the triple-system DTD.
+The choice of SFH has a larger effect on the overall score than the DTD, and the best-performing SFH is the two-infall model.
+However, the difference between the best-scoring model and the worst (inside-out SFH with the $\alpha=-1.4$ power-law DTD) is fairly small.
 While there are some {\it quantitative} differences in how the shape of the MDF varies with Galactic region, the {\it qualitative} trends are unaffected by the choice of model SFH or DTD.
@@
     \includegraphics[width=\linewidth]{figures/ofe_df_dtd.pdf}
-    \caption{Distributions of [O/Fe] from multi-zone models with different DTDs. In all cases an early-burst SFH is assumed. The plot format is similar to Figure \ref{fig:ofe-df-sfh}.}
+    \caption{The same as Figure \ref{fig:ofe-df-sfh} but for different DTDs. In all cases an early-burst SFH is assumed.}
     \label{fig:ofe-df-dtd}
@@
 The two-population DTD, which has the most prompt SNe Ia, places the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.2$ dex higher at ${\rm [O/Fe]}\approx0.4$.
+The plateau ($W=1$ Gyr) DTD places the higher peak at ${\rm [O/Fe]}\approx0.35$, close to where it appears in the APOGEE distributions.
+However, the distance {\it between} the peaks of the APOGEE distributions is only $\approx0.2$ dex, since the observed low-$\alpha$ sequence sits at ${\rm [O/Fe]}\approx0.1$.
+This spacing is best replicated by the power-law ($\alpha=-1.1$) DTD, even though both peaks sit $\sim0.1$ dex too low and the distributions are narrower than observed.
 In general, models with fewer prompt SNe Ia populate the high-$\alpha$ sequence with more stars because the chemical evolution track spends more time in the high-$\alpha$ regime.
-The exception to this is the two-population DTD, which produces a very strong high-$\alpha$ peak at $|z|>0.5$ kpc.
-This might result from the second knee in the abundance track (Figure \ref{fig:onezone-twopanel}) which is produced by its long exponential tail.
 
@@
 We calculate a score for each model as described in Section \ref{sec:feh-df}.
-The best-scoring model uses the two-infall SFH with the plateau ($W=0.3$ Gyr) DTD, although both plateau and exponential DTDs as well as the triple-system DTD score well when combined with certain SFHs.
+% The best-scoring model uses the two-infall SFH with the plateau ($W=0.3$ Gyr) DTD, although both plateau and exponential DTDs as well as the triple-system DTD score well when combined with certain SFHs.
 The late-burst SFH generally produces [O/Fe] DFs that score poorly compared to other models.
 \todo{Elaborate on the model scores a bit more}.
+The best-scoring model combines the inside-out SFH with the triple-system DTD, and the plateau ($W=1$ Gyr) and exponential ($\tau=3$ Gyr) DTDs score well when combined with either the inside-out or late-burst SFHs.
+Both plateau DTDs also score relatively well with the two-infall SFH.
+Surprisingly, the early-burst SFH scores quite poorly for all DTD models, despite the fact that it produces the most distinct high- and low-$\alpha$ sequences.
+We discuss this further in Section \ref{sec:discussion}.
 
@@
     \textit{Top row:} results from five multi-zone models which assume the late-bust SFH but different DTDs.
-\textit{Bottom row}: the first four panels compare the four SFHs, all assuming an exponential DTD with $\tau=1.5$ Gyr.
+\textit{Bottom row}: the first four panels compare the four SFHs (see Figure \ref{fig:sfhs}), all assuming an exponential DTD with $\tau=1.5$ Gyr.
 The bottom-right panel (highlighted) plots data from APOGEE DR17 for reference.}
@@
 % (right-hand panels of Figures \ref{fig:ofe-df-sfh} and \ref{fig:ofe-df-dtd}) 
-show two distinct peaks whose relative prominence varies with $R_{\rm gal}$ and $|z|$.
-A crucial feature of this bimodality, which is not apparent in the analysis of the previous section, is the presence of both sequences {\it at the same [Fe/H]}.
-\citet{Vincenzo2021-AlphaDistribution} demonstrate that, although the APOGEE sample over-represents stars with $|z|\ge1$ which are more likely to be high-$\alpha$, the $\alpha$-bimodality is a real feature of the solar neighborhood population.
-A successful model for the evolution of the Milky Way must be able to reproduce this bimodality.
+show two distinct peaks whose relative prominence varies with $R_{\rm gal}$ and $|z|$ \citep[see also Figure 4 of][]{Hayden2015-ChemicalCartography}.
+A crucial feature of this bimodality, which is not apparent in the analysis of the previous section, is the presence of both sequences at fixed [Fe/H].
+The separation between the two sequences appears to be a real feature and not an artifact of the APOGEE selection function \citep{Vincenzo2021-AlphaDistribution}.
+A successful model for the evolution of the Milky Way therefore must reproduce this bimodality.
 
 Figure \ref{fig:ofe-bimodality} compares the [O/Fe] distributions in the solar annulus ($7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc) in two bins of [Fe/H] ($-0.6<{\rm [Fe/H]}<-0.4$ and $-0.4<{\rm [Fe/H]}<-0.2$) for select model outputs and APOGEE data.
-The APOGEE distributions in the bottom-right panel (j) show that the high-$\alpha$ mode is more prominent at lower [Fe/H] and vice versa, but the distributions in both bins are clearly bimodal.
-Moreover, the ``trough'' at ${\rm [O/Fe]}\approx0.2$ is consistent in each bin.
+The APOGEE distributions in the bottom-right panel (j) show that the high-$\alpha$ mode is more prominent at lower [Fe/H], but the distributions in both bins are clearly bimodal.
+The ``trough'' occurs near ${\rm [O/Fe]}\approx0.2$ in each bin.
 
@@
 [Explain why this is ok]
-Five of the eight DTDs (four of the five shown, plus the exponential form with $\tau=3$ Gyr) exceed our prominence threshold in the low-[Fe/H] bin, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
-Panel (b) shows that the power-law ($\alpha=-1.1$) DTD produces a marginal high-$\alpha$ peak, although it doesn't meet the prominence threshold because it is too close to the low-$\alpha$ peak.
+Five of these eight DTDs (four of the five shown, plus the exponential form with $\tau=3$ Gyr) exceed our prominence threshold in the low-[Fe/H] bin, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
+Panel (b) shows that the power-law ($\alpha=-1.1$) DTD produces a marginal high-$\alpha$ peak, although it does not meet the prominence threshold because it is too close to the low-$\alpha$ peak.
 In general, DTDs with fewer prompt SNe Ia produce a high-$\alpha$ peak which is more prominent and at a higher [O/Fe], as was the case with the [O/Fe] distributions in Section \ref{sec:ofe-df}.
@@
 
-One major discrepancy in all of our models the breadth of the $\alpha$-bimodality across [Fe/H] space. 
+One major problem in all of our models is the presence of the \aFe bimodality across only a narrow range of [Fe/H].
+% in all of our models the breadth of the $\alpha$-bimodality across [Fe/H] space. 
 % In APOGEE, both bins in [Fe/H] show a clearly bimodal distribution of [O/Fe]. 
@@
 In APOGEE, the two sequences are co-extant between ${\rm [Fe/H]}\approx-0.6$, below which the high-$\alpha$ sequence dominates, and ${\rm [Fe/H]}\approx+0.2$, at which point they join.
-The failure of our models to fully reproduce the bimodality across the whole range of [Fe/H] indicates that our picture of the formation of the $\alpha$-bimodality is still incomplete.
+The failure of these models to fully reproduce the bimodality across the whole range of [Fe/H] was noted by \citetalias{Johnson2021-Migration}, and the problem persists for each model we consider here.
+% indicates that our picture of the formation of the $\alpha$-bimodality is still incomplete.
 
@@
 The black curves represent the ISM abundance tracks in the 8 kpc zone.
-The red contours represent a 2-D kernel density estimate with a bandwidth of 0.03 of the APOGEE abundance distribution in that Galactic region, with the solid and dashed contours enclosing 30\% and 80\% of stars in the sample, respectively.}
+The red contours represent a 2-D kernel density estimate of the APOGEE abundance distribution in that Galactic region with a bandwidth of 0.03.
+The solid and dashed contours enclose 30\% and 80\% of stars in the sample, respectively.}
     \label{fig:ofe-feh-sfh}
@@
 
-In Section \ref{sec:onezone-results}, and specifically Figures \ref{fig:onezone-threepanel} and \ref{fig:onezone-twopanel}, we illustrated that the form and parameters of the DTD have an important effect on the ISM abundance tracks in idealized one-zone models.
-However, comparisons to data are limited because the tracks do not record the number of stars which are formed with those abundances, nor do they incorporate the effect of stellar migration.
+In Section \ref{sec:onezone-results}, we illustrated that the form and parameters of the DTD have an important effect on the ISM abundance tracks in idealized one-zone models (see Figures \ref{fig:onezone-threepanel} and \ref{fig:onezone-twopanel}).
+However, comparisons to data are limited because the tracks neither record the number of stars that formed at each abundance, nor incorporate the effect of stellar migration.
 Here, we present the distribution of stellar abundances in the [O/Fe]--[Fe/H] plane alongside the ISM abundance tracks from our multi-zone models.
@@
 Figure \ref{fig:ofe-feh-sfh} compares the [O/Fe]--[Fe/H] plane in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) between our four model SFHs.
-The black curves represent the ISM abundance as a function of time in the $R_{\rm gal}=8.0-8.1$ kpc zone; in the absence of radial migration, all simulated stellar populations would lie close to these lines.
-Stellar populations to the left of the abundance tracks were born in the outer disk, while those to the right were born in the inner disk, as evidenced by the color-coding in the figure.
-This illustrates how radial migration can explain much of the spread in [Fe/H] which is observed in a given Galactocentric region.
-% \todo{Discuss the effect of radial migration on the [O/Fe]--[Fe/H] distributions.}
-
-The abundance tracks of all four model SFHs initially follow a similar path of decreasing [O/Fe] with increasing [Fe/H].
-The ISM abundance ratios of the inside-out model change monotonically over time.
+The black curves represent the ISM abundance as a function of time in the $R_{\rm gal}=8.0-8.1$ kpc zone; in the absence of radial migration, all model stellar populations would lie close to these lines.
+Stellar populations to the left of the abundance tracks were born in the outer disk, while those to the right were born in the inner disk, as illustrated by the color-coding in the figure.
+Much of the scatter in [Fe/H] in a given Galactic region can be attributed to radial migration \citep{Edvardsson1993-ChemicalEvolution}.
+% This illustrates how radial migration can explain much of the spread in [Fe/H] which is observed in a given Galactocentric region.
+
+The tracks predicted by all four SFHs initially follow a similar path of decreasing [O/Fe] with increasing [Fe/H].
+The ISM abundance ratios of the inside-out model change monotonically over the entire disk lifetime.
 The stellar abundance distribution at both low- and high-[O/Fe] is composed of stars with a wide range of birth $R_{\rm gal}$.
-In particular, we observe a high-[O/Fe] ``ridge'' on the high-metallicity side of the ISM track, which is composed of stellar populations from the inner Galaxy.
-
-The late-burst model produces similar results to the inside-out model up to ${\rm [Fe/H]}\approx-0.2$, again because of their similar SFHs.
-The Gaussian burst in SFH in the late-burst model introduces a loop in the ISM abundance track, as an uptick in star formation at $t\approx11$ Gyr raises the CCSN rate, leading to a slight increase in [O/Fe] before the subsequent increase in the SN Ia rate lowers the [O/Fe] once again.
+% In particular, we observe a high-[O/Fe] ``ridge'' on the high-metallicity side of the ISM track, which is composed of stellar populations from the inner Galaxy.
+
+The late-burst model produces similar results to the inside-out model up to ${\rm [Fe/H]}\approx-0.2$ due to their similar SFHs.
+The Gaussian burst in its SFH introduces a loop in the ISM abundance track, as an uptick in star formation at $t\approx11$ Gyr raises the CCSN rate, leading to a slight increase in [O/Fe] before the subsequent increase in the SN Ia rate lowers the [O/Fe] once again \citep[see e.g.
+Figure 1 of][]{JohnsonWeinberg2020-Starbursts}.
 This loop slightly broadens the low-[O/Fe] stellar distribution as we observed in Section \ref{sec:ofe-df}.
@@
 This same pattern is seen much more strongly in the abundance tracks for the two-infall model.
-Here, the significant infall of pristine gas at $t=4$ Gyr leads to rapid dilution of the metallicity of the ISM, followed by a large burst in the SFR which raises [O/Fe] by $\sim 0.2$ dex.
-The track begins to ``turn over'' back to lower [O/Fe] due to the delayed response of SNe Ia.
-We observe a ridge in the stellar abundance distribution at this turn-over point (${\rm [O/Fe]}\approx0.2$), which roughly coincides with the upper limit of the APOGEE distribution near the midplane.
-The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx0.0$ near the end of the model.
+Here, the significant infall of pristine gas at $t=4$ Gyr leads to rapid dilution of the metallicity of the ISM, followed by a large burst in the SFR, which raises [O/Fe] by $\sim 0.2$ dex.
+% The track begins to ``turn over'' back to lower [O/Fe] due to the delayed response of SNe Ia. 
+We observe a ridge in the stellar abundance distribution at the turn-over point (${\rm [O/Fe]}\approx0.15$) associated with SNe Ia whose progenitors formed during the burst.
+This ridge roughly coincides with the upper limit of the APOGEE distribution near the midplane.
+The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx-0.05$, which reflects the population-averaged yield ratio of [O/Fe].
 
 The early-burst track is the most distinct from the other models at low metallicity.
-The portion which is shown in Figure \ref{fig:ofe-feh-sfh} represents the evolution {\it after} the early SFE burst.
-At low metallicity, there is a ``simmering phase'' where [O/Fe] slowly decreases to a local minimum at ${\rm [Fe/H]}\approx-1.3$, at which point the rapid increase in the SFE causes the [O/Fe] to rebound \citep[a more thorough examination of this behavior can be seen in][]{Conroy2022-ThickDisk}.
-The early-burst SFH produces the clearest separation in the stellar abundances between a high-[O/Fe] sequence which follows the ISM abundance track down to low [Fe/H], and a low-[O/Fe] sequence composed of stars with a wide range of birth radii.
-The stellar population density of the high-[O/Fe] sequence is relatively high, likely as a result of a higher SFR at early times compared to the other models.
+The portion shown in Figure \ref{fig:ofe-feh-sfh} represents the evolution {\it after} the early SFE burst.
+At low metallicity, there is a ``simmering phase'' where [O/Fe] slowly decreases to a local minimum at ${\rm [Fe/H]}\approx-1.3$, at which point the rapid increase in the SFE causes the [O/Fe] to rebound \citep[a more thorough examination of this behavior can be found in][]{Conroy2022-ThickDisk}.
+The early-burst SFH produces the clearest separation between a high- and low-[O/Fe] sequences.
+The number of stars on the high-[O/Fe] sequence is relatively high, likely as a result of its higher SFR at early times compared to the other models.
 
@@
     \includegraphics[width=\linewidth]{figures/ofe_feh_dtd.pdf}
-    \caption{The [O/Fe]--[Fe/H] plane from multi-zone models with different DTDs.
+    \caption{The [O/Fe]--[Fe/H] plane from multi-zone models with different DTDs (see Figure \ref{fig:dtds}).
 All assume the inside-out SFH.
-Each panel is similar to those in Figure \ref{fig:ofe-feh-sfh}, except each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
+Each panel is similar to those in Figure \ref{fig:ofe-feh-sfh}, except each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row as labeled in the middle column.
 All panels contain stars within the solar annulus ($7\leq R_{\rm gal}<9$ kpc).}
@@
 Figure \ref{fig:ofe-feh-dtd} compares the [O/Fe]--[Fe/H] ISM tracks and stellar distributions for five models with the same SFH but different DTDs.
-We choose the inside-out SFH for this figure because it produces a monotonically-decreasing abundance track, making comparisons between the different DTDs relatively straightforward.
+We choose the inside-out SFH for this figure because it predicts monotonically-decreasing abundance ratios, making comparisons between the different DTDs relatively straightforward.
 % We note that in this model, both the low- and high-$\alpha$ sequences are composed of stars with a wide range of birth $R_{\rm gal}$. 
-The models are arranged according to the median delay time of the DTD, increasing across the panels from left to right.
+The models are arranged according to the median delay time of the DTD, increasing across the panel columns from left to right.
 
@@
 The two-population and power-law ($\alpha=-1.1$) DTDs, which have a large fraction of prompt SNe Ia, produce stellar abundance distributions that are reasonably well-aligned with the APOGEE contours at low $|z|$, but they entirely miss the observed high-$\alpha$ sequence at large $|z|$.
-The ISM abundance tracks for the 8 kpc zone do not pass through the APOGEE 30\% contour.
-For both DTDs, the high-[O/Fe] knee is located below the left-most bound of the plot, but we observe a second knee at ${\rm [O/Fe]}\approx0.2$ where the abundance track turns further downward.
+The ISM abundance tracks for the 8 kpc zone do not pass through the APOGEE 30\% contour at $|z|=1-2$ kpc.
+For both DTDs, the high-[O/Fe] knee is located below the left-most bound of the plot, but we observe a second knee at ${\rm [O/Fe]}\approx0.2$ where the abundance tracks turn downward once more.
 As discussed in Section \ref{sec:onezone-results}, the second knee is most prominent in the model with the two-population DTD because of its long exponential tail.
@@
 The DTDs with an intermediate median delay time do well at reproducing the observed abundance distributions.
-The exponential ($\tau=1.5$ Gyr) DTD produces a distribution in Figure \ref{fig:ofe-feh-dtd} which aligns quite well with the outer APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to high [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
-While it does better at populating the high-$\alpha$ sequence than the previous DTDs, the bulk of the simulated populations at large $|z|$ still fall below the APOGEE 30\% contour.
+The exponential ($\tau=1.5$ Gyr) DTD produces a distribution in Figure \ref{fig:ofe-feh-dtd} which aligns quite well with the 80\% APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to high [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
+While it does better at populating the high-$\alpha$ sequence than the previous DTDs, the bulk of the model stellar populations at large $|z|$ still fall below the APOGEE 30\% contour.
 
@@
 The high-[O/Fe] knee occurs at a much higher metallicity in these models and is visible in the gas abundance tracks in the upper-left corner of the panels.
-At large $|z|$, the simulated abundance distributions align quite well with the APOGEE high-$\alpha$ sequence, but there is a significant ridge of high-$\alpha$ stars from the inner Galaxy at low $|z|$.
+At large $|z|$, the predicted abundance distributions align quite well with the APOGEE high-$\alpha$ sequence, but there is a significant ridge of high-$\alpha$ stars from the inner Galaxy at low $|z|$.
 
@@
 As in Sections \ref{sec:feh-df} and \ref{sec:ofe-df}, we bin the model outputs and data by $R_{\rm gal}$ and $|z|$, calculate $\hat D_k(P||Q)$ in each region, and then take the weighted mean of each region as in Equation \ref{eq:feh-df-score} to arrive at a single score for each model.
-\todo{More detail on the scoring calculations.}
-% \footnote{We got the implementation from \url{https://mail.python.org/pipermail/scipy-user/2011-May/029521.html}.}
+
+\todo{Which models score best.}
 
@@
     \includegraphics{figures/ofe_feh_twoinfall.pdf}
-    \caption{The [O/Fe]--[Fe/H] plane for multiple Galactocentric regions from the model with the inside-out SFH and plateau ($W=1$ Gyr) DTD.
+    \caption{The [O/Fe]--[Fe/H] plane for multiple Galactocentric regions from the model with the two-infall SFH and plateau ($W=1$ Gyr) DTD.
 The two columns of panels contain stars in different bins of $R_{\rm gal}$, and each row contains stars from a different bin of $|z|$.
-The contents of each panel is as described in Figure \ref{fig:ofe-feh-sfh}.}
+The contents of each panel are as described in Figure \ref{fig:ofe-feh-sfh}.}
     \label{fig:ofe-feh-twoinfall}
@@
 
-Figure \ref{fig:ofe-feh-twoinfall} plots the stellar [O/Fe]--[Fe/H] abundances from the model with the two-infall SFH and plateau ($W=1$ Gyr) DTD in the inner and outer Galaxy.
-The model distributions in the outer Galaxy closely match the APOGEE distributions.
-Stellar populations at the high-[Fe/H] end of the distribution have migrated from inner regions.
-\todo{More discussion about Figure \ref{fig:ofe-feh-twoinfall}.}
+Figure \ref{fig:ofe-feh-twoinfall} plots the stellar [O/Fe]--[Fe/H] abundances from the model with the two-infall SFH and plateau ($W=1$ Gyr) DTD.
+In the inner Galaxy, the model distribution at large $|z|$ lies at higher [O/Fe] and is more extended than the APOGEE distribution.
+Agreement between the model and data is worst at mid-latitudes: the model distribution is sparsest in the area of the peak of the APOGEE distribution.
+Near the midplane, however, the model output is well-aligned with the data.
+In the outer Galaxy, the distributions are well-aligned at all $|z|$, though the model distributions are more extended along the [O/Fe] axis than in the data.
+Adjustments to the yields or the relative infall strengths could improve the agreement between the two-infall model output and the observed distributions.
 
@@
 All assume the exponential ($\tau=1.5$ Gyr) DTD.
-Each panel plots a random mass-weighted sample of 10,000 star particles in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth.
+Each panel plots a random mass-weighted sample of 10,000 star particles in the solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by [Fe/H].
 A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citetalias{Leung2023-Ages} (see Table \ref{tab:sample}).
@@
 % [Subsection introduction]
-As illustrated by the one-zone models in Section \ref{sec:onezone-results}, models which produce similar tracks in abundance space can be distinguished by the rate of their abundance evolution.
-We demonstrated in Section \ref{sec:ofe-df} that the DTD affects the final [O/Fe] distribution, so naturally it should have an effect on the evolution of [O/Fe] with age as well.
+As demonstrated by our one-zone models in Section \ref{sec:onezone-results}, models that produce similar tracks in abundance space can be distinguished by the rate of their abundance evolution.
+We therefore expect the age--[O/Fe] relation to be a useful diagnostic.
+% We demonstrated in Section \ref{sec:ofe-df} that the DTD affects the final [O/Fe] distribution, so naturally it should have an effect on the evolution of [O/Fe] with age as well.
 We compare our model stellar age--[O/Fe] relations with age estimates for APOGEE stars from the variational encoder-decoder network of \citetalias{Leung2023-Ages}.
-
-Figure \ref{fig:age-ofe-sfh} compares the stellar age and [O/Fe] distributions in the solar neighborhood between our four SFHs.
-Similar to Figure \ref{fig:ofe-feh-sfh}, all four panels assume an exponential DTD with $\tau=1.5$ Gyr.
-We include age data from \citetalias{Leung2023-Ages} for qualitative comparison, though we caution against drawing strong conclusions because we don't correct for selection effects or systematics in the neural net ages.
-The inside-out and late-burst models show fair agreement with the data at high [O/Fe], although both show a $\sim2$ Gyr offset to older ages.
+Figure \ref{fig:age-ofe-sfh} shows the stellar age and [O/Fe] distributions in the solar neighborhood for each of our four SFHs.
+As in Figure \ref{fig:ofe-feh-sfh}, all four panels assume an exponential DTD with $\tau=1.5$ Gyr.
+We compare these predictions against ages estimated with \citetalias{Leung2023-Ages}'s variational encoder-decoder algorithm.
+% We include age data from \citetalias{Leung2023-Ages} for qualitative comparison, though 
+We caution against drawing strong conclusions from this comparison, because we do not correct for selection effects or systematic errors in the age determination.
+
+The inside-out and late-burst models show fair agreement with the data at high [O/Fe], although both show a $\sim2$ Gyr offset at older ages.
 One could shift the ramp-up in star formation to slightly later times or simply run the model for a shorter amount of time to close this gap.
-Like the data, the trend in the median age with decreasing [O/Fe] decreases monotonically in the inside-out model.
-The late-burst model, however, shows a bump in the distribution around a lookback time of $\sim2$ Gyr driven by the Gaussian SFR burst, which is not seen in the data, as noted by \citetalias{Johnson2021-Migration}.
-Neither model produces a significant amount of stars below solar [O/Fe], in contrast to the data.
-
-For the early-burst SFH, the simulated stellar ages are almost perfectly aligned with the data for ${\rm [O/Fe]}\gtrsim 0.2$.
+As in the data, the trend in the median age with decreasing [O/Fe] decreases monotonically in the inside-out model.
+The late-burst model, however, shows a bump in the relation at a lookback time of $\sim2$ Gyr which is not seen in the data, as noted by \citetalias{Johnson2021-Migration}.
+% Neither model produces a significant amount of stars below solar [O/Fe], in contrast to the data.
+
+For the early-burst SFH, the predicted stellar ages are almost perfectly aligned with the data for ${\rm [O/Fe]}\gtrsim 0.2$.
 The rapid rise in the SFE at early times delays the descent to lower [O/Fe] values and produces a clump of low-metallicity, high-[O/Fe] stars at an age of $\sim10$ Gyr.
-The early-burst model produces a sharp transition between a linear relationship between [O/Fe] and age for stars older than $\sim5$ Gyr and a flat relationship for the younger stars, and it too misses the lowest [O/Fe] bin in the data.
-Finally, the two-infall SFH produces the closest overall agreement between the simulated and observed median ages.
+% The early-burst model produces a sharp transition between a linear relationship between [O/Fe] and age for stars older than $\sim5$ Gyr and a flat relationship for the younger stars, and it too misses the lowest [O/Fe] bin in the data.
+Lastly, the two-infall SFH produces the closest overall match to the data.
 Stars with ${\rm [O/Fe]}\gtrsim 0.25$ were produced in the first infall, while the second infall produces a clump of stars with similar metallicity, ages of $\sim8$ Gyr, and ${\rm [O/Fe]}\approx0.2$.
-There is an interesting small population of very old, low-$\alpha$ stars which is not seen in any of the other models.
+There is a population of old, low-$\alpha$ stars that arise due to the initial descent in [O/Fe] prior to the second accretion epoch.
+The subsequent increase in [O/Fe] does not produce as strong of a bump as the late-burst SFH, because it occurs much earlier and is therefore narrower in log(age).
+% which is not seen in any of the other models.
 The two-infall model is the only one which plateaus at sub-solar [O/Fe] for the youngest stars, leading to a very good match to the observed data at low [O/Fe].
@@
 All assume the early-burst SFH.
-Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row.
-In all panels stars are limited to the solar annulus ($7\leq R_{\rm gal}<9$ kpc), and the layout of each panel is as in Figure \ref{fig:age-ofe-sfh}.}
+Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row as labeled in the middle column.
+In all panels stars are limited to the solar annulus ($7\leq R_{\rm gal}<9$ kpc), and the layout of each panel is the same as in Figure \ref{fig:age-ofe-sfh}.}
     \label{fig:age-ofe-dtd}
@@
 
-Figure \ref{fig:age-ofe-dtd} similarly plots the simulated distributions in age--[O/Fe] space for five of our DTDs.
-All models were run with the early-burst SFH because the high-$\alpha$ sequence was distinct in metallicity space in Figure \ref{fig:age-ofe-sfh}.
+Figure \ref{fig:age-ofe-dtd} shows the predicted age--[O/Fe] relation for five of our DTDs.
+All models were run with the early-burst SFH, because it predicts the clearest separation between the high- and low-$\alpha$ sequences (see Figure \ref{fig:age-ofe-sfh}).
 Similar to Figure \ref{fig:ofe-feh-dtd}, models are arranged from left to right by increasing median SN Ia delay time.
-Moving from left to right, the high-$\alpha$ sequence moves to higher [O/Fe] with increasing median delay time, from $\sim0.4$ for the two-population model to $\sim0.4$ for the triple-system DTD.
-As we have seen in previous figures, the range in [O/Fe] produced by the models on the left is much smaller than for the models on the right.
-At high $|z|$ (top row), the observed range of [O/Fe] is larger than produced by any of our models, although the plateau ($W=1$ Gyr) and triple-system models come close.
-While the other three fall short of the observed range in [O/Fe], they more closely match the median age--[O/Fe] relation.
-There is a slight reversal in the observed trend for the stars with the highest [O/Fe]: the $0.45\leq{\rm [O/Fe]}<0.5$ bin has a slightly \textit{lower} median age than the $0.3\leq{\rm [O/Fe]}<0.35$ bin at high $|z|$ in the \citetalias{Leung2023-Ages} sample, a small effect but one which is not observed in any of our model results.
-
-Moving to stars at low $|z|$, our plateau ($W=1$ Gyr) and triple-system DTDs over-produce stars at the old, high-$\alpha$ end of the distribution, while also diverging significantly from the observed sequence near solar [O/Fe].
+The high-$\alpha$ sequence moves to higher [O/Fe] with increasing median delay time, from $\sim0.2$ for the two-population model to $\sim0.4$ for the triple-system DTD.
+As we have seen in previous figures, the range in [O/Fe] produced by DTD models with many prompt SNe Ia is much smaller than the extended DTDs.
+At high $|z|$ (top row), the observed range of [O/Fe] is larger all of our models.
+While the plateau ($W=1$ Gyr) and triple-system models come close, the other three fall short of the observed range in [O/Fe], but closely match the median age--[O/Fe] relation.
+There is a slight reversal in the observed trend for the stars with the highest [O/Fe]: the $0.45\leq{\rm [O/Fe]}<0.5$ bin has a slightly \textit{lower} median age than the $0.3\leq{\rm [O/Fe]}<0.35$ bin at high $|z|$ in the \citetalias{Leung2023-Ages} sample, a small effect but one which is not predicted by any of our models.
+
+Moving to stars at low $|z|$, the plateau ($W=1$ Gyr) and triple-system DTDs over-produce stars at the old, high-$\alpha$ end of the distribution, while also diverging significantly from the observed sequence near solar [O/Fe].
 The exponential ($\tau=1.5$ Gyr) DTD comes closest to reproducing the observed range in [O/Fe], while the two DTDs with the shortest median delay time once again produce a smaller range of [O/Fe] than observed.
 We note that the break between the linear and flat parts of the relation is sharpest for the exponential DTD, and a more gradual transition is observed for the other four DTDs.
-This could be because the exponential DTD is most dominant at intermediate delay times ($t\sim 1-3$ Gyr) but falls off much faster than the other models at long delay times, so the evolution of [O/Fe] is quite slow for lookback times $\lesssim 5$ Gyr.
+This difference arises because the exponential DTD is most dominant at intermediate delay times ($t\sim 1-3$ Gyr) but falls off much faster than the other models at long delay times, so [O/Fe] is close to constant for lookback times $\lesssim 5$ Gyr.
 Overall, the exponential ($\tau=1.5$ Gyr) DTD most closely matches the data for stars with $0\leq|z|<1$ kpc.
@@
 We use a different scoring system from previous sub-sections due to the much larger uncertainties in age than [O/Fe].
-As shown in Figures \ref{fig:age-ofe-sfh} and \ref{fig:age-ofe-dtd}, in each Galactic region we bin the model outputs and data into bins of [O/Fe] with a width of 0.05 dex.
+As shown in Figures \ref{fig:age-ofe-sfh} and \ref{fig:age-ofe-dtd}, in each Galactic region we sort the model outputs and data into bins of [O/Fe] with a width of 0.05 dex.
 We define the RMS median age difference for the region as
@@
 \end{equation}
-where $\Delta\tau_k=\rm{med}(\tau_{\rm \vice})-\rm{med}(\tau_{\rm L23})$ is the difference between the mass-weighted median star particle age in \vice and the median stellar age from \citetalias{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citetalias{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
-As before, the score for the model as a whole is the average of $\Delta \tau_{\rm RMS}$ across all regions, weighted by the number of stars in the age sample in each region.
-
-\todo{Discuss how the age at the knee, given our age uncertainties, is not a great diagnostic.}
+where $\Delta\tau_k=\rm{med}(\tau_{\rm \vice})-\rm{med}(\tau_{\rm L23})$ is the difference between the mass-weighted median age in \vice and the median stellar age from \citetalias{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citetalias{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
+As before, the score for the model as a whole is the average of $\Delta \tau_{\rm RMS}$ across all regions, weighted by the number of stars with age measurements in each region.
+We discuss the quantitative scores in Section \ref{sec:discussion} below.
 
@@
 
-% \todo{I just noticed that I was using slightly wrong yields in all of the multi-zone models (JW20 instead of J+21).
-I re-ran all the models and this corrected the end-point of the inside-out tracks, which are now at (0,0).
-However, this also shifted the end-point of the two-infall tracks down to (+0.1, -0.1), so now two-infall is no longer the clear winner like it used to be.
-The best DTDs are now the 1-Gyr power-law and the triple-system, rather than the 1.5-Gyr exponential like before.
-The general trend of more prompt SNe = worse does still hold.
-At a minimum, I think this indicates that these scores are highly sensitive to the yields.
-At worst, maybe we need to consider adjusting the yields for the two-infall models so that the [O/Fe] distributions are not significantly lower than every other SFH.}
-\todo{Needs to be updated for the new yields.}
-
-The results presented in Section \ref{sec:multizone-results} represent a fraction of the 32 total multi-zone model outputs (four SFHs and eight DTDs) and focus on the even smaller fraction of outputs which lie in the solar annulus.
+In Section \ref{sec:multizone-results}, we focused on a representative subset of our 32 multi-zone models (four SFHs and eight DTDs). 
 % While we focused our attention on results in the solar annulus (for which we still have the best data), we have model outputs which span the entire disk out to 20 kpc.
 In order to identify trends among our many models, it will be useful to have some semi-quantitative way to compare their outputs to APOGEE data across the disk.
-In this section, we compare all of our model outputs to APOGEE across five diagnostics: the MDF, [O/Fe] DF, [O/Fe]--[Fe/H] plane, age--[O/Fe] plane, and [O/Fe] bimodality.
-We perform statistical tests between APOGEE and the model outputs in each region of the Galaxy (as described in corresponding subsections of Section \ref{sec:multizone-results}), then compute the average weighted by the size of the APOGEE sample in each region to obtain a single numerical score.
+Here, we compare all of our model outputs to APOGEE across five observables: the MDF, [O/Fe] DF, [O/Fe]--[Fe/H] plane, age--[O/Fe] plane, and [O/Fe] bimodality.
+We perform statistical tests between APOGEE and the model outputs in each region of the Galaxy as described in corresponding subsections of Section \ref{sec:multizone-results}, then compute the average weighted by the size of the APOGEE sample in each region to obtain a single numerical score.
 
 The diagnostic scores for each model are presented in Table \ref{tab:results}.
-We use these scores to indicate combinations of SFH and DTD which are favorable or unfavorable in certain regimes, but we do {\it not} fit our models to the data.
+We use these scores to indicate combinations of SFH and DTD that are favorable or unfavorable in certain regimes, but we do {\it not} fit our models to the data due to computational expense.
 To avoid drawing strong conclusions from small numerical differences in scores, 
-% Instead of reporting the numerical scores for each model output, 
-in the column corresponding to a particular diagnostic we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom tirtile out of all of our models, respectively.
-A \yes indicates that particular combination of model SFH and DTD performed better than most when compared to the APOGEE sample for that diagnostic.
-
-% Table \ref{tab:results} indicates combinations of SFH and DTD which are more or less favorable in certain regimes.
-However, we emphasize that we do not use these scores to fit the models to the data.
-Much of the variation between models can be explained by the choice of SFH.
-In general, the two-infall models rank the highest across all diagnostics, while the late-burst models compare poorly to the rest.
-We discuss our implementation of the two-infall SFH in Section \ref{sec:two-infall-discussion}.
+% in the column corresponding to a particular diagnostic 
+we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom third out of all models, respectively.
+
+%Much of the variation between models can be explained by the choice of SFH.
+In general, the two-infall models rank the highest across all diagnostics, while the late-burst models score poorly to the rest.
 If we remove the two-infall models altogether due to their dominance in the scoring system, our results do not qualitatively change.
-In the age--[O/Fe] plane, the two bursty or discontinuous SFHs, early-burst and two-infall, score much better than the two smooth SFHs.
-The SFHs rank differently in the bimodality test, where the early-burst SFH is able to produce a bimodal [O/Fe] distribution for all DTDs, as discussed in Section \ref{sec:bimodality}.
+In the age--[O/Fe] plane, the early-burst and two-infall models, score much better than the others.
+The SFHs rank differently in the bimodality test, where the early-burst SFH is able to produce a bimodal [O/Fe] distribution for all DTDs (see discussion in Section \ref{sec:bimodality}).
+Some of the variation between models can be explained by the choice of SFH.
+The two-infall models tend to out-perform the others for the MDFs, while the late-burst models score poorly, especially with the prompt DTDs.
+The early-burst models consistently have the lowest scores for the [O/Fe] DF and [O/Fe]--[Fe/H] distribution, but are able to produce a bimodal [O/Fe] distribution with every \todo{(check 3 Gyr exponential)} DTD.
+The late-burst and two-infall SFHs also produce a bimodal [O/Fe] disbtribution with all DTDs but those with the highest prompt fraction, while the inside-out models never produce bimodality \todo{(check 1.5 Gyr exponential)}.
+The inside-out models also tend score poorly in the age--[O/Fe] plane.
+\todo{Visually the late-burst SFH should score the lowest here, need to double-check.}
 
 It is somewhat surprising that the early-burst models score poorly against the APOGEE [O/Fe] DFs, given that they produce the clearest bimodal distributions.
-This is because the KL divergence test heavily penalizes models with a high density in a region where the observations have little, as is the case for the high-$\alpha$ sequence in the outer Galaxy and close to the midplane.
-An iteration of this SFH where the early burst predominantly affects the inner galaxy might have more success at reproducing the [O/Fe] DF across the disk.
-
-The two-infall models are penalized by the KL divergence tests for producing abundance distributions which are not well aligned with the data (see the bottom-right panel of Figure \ref{fig:ofe-feh-sfh}).
+The KL divergence test heavily penalizes models with a high density in a region where the observations have little, as is the case for the high-$\alpha$ sequence in the outer Galaxy and close to the midplane (see Figure \ref{fig:ofe-df-sfh}).
+An iteration of this SFH where the early burst predominantly affects the inner galaxy is probably more accurate and might have more success at reproducing the [O/Fe] DF across the disk.
+
+% The two-infall models are penalized by the KL divergence tests for producing abundance distributions which are not well aligned with the data (see the bottom-right panel of Figure \ref{fig:ofe-feh-sfh}).
 With a slightly lower $y_{\rm Fe}^{\rm Ia}$, the abundance tracks do not dip so far below ${\rm [O/Fe]}=0$, and the two-infall models out-perform every other SFH.
 
-The choice of DTD has a clear effect on the model scores, and this effect is similar across the diagnostics.
+%The choice of DTD has a clear effect on the model scores, and this effect is similar across the observables.
 The models which perform the best (most \yes's and fewest \no's) are those with the exponential and plateau DTDs.
-It is interesting that the best-scoring DTD overall, the exponential DTD with $\tau=1.5$ Gyr, is intermediate among all our DTDs in terms of the number of prompt SNe Ia and median delay time, but has the {\it lowest} rate at very long delay times ($\sim10$ Gyr).
-Models with a large fraction of prompt SNe Ia, such as the power-law and two-population DTDs, fare quite poorly, with the steepest power-law ($\alpha=-1.4$) ending up in the bottom tirtile across the board for most of our SFHs.
-
-% The best DTDs for each SFH
-% The main takeaway from Table \ref{tab:results} is that 
-While certain DTDs tend to score better than others, there is no single DTD which always produces optimal agreement with the data across all observables and for all SFHs. 
-% Depending on the choice of SFH, different DTDs will succeed at reproducing different observables. 
+It is interesting that the best-scoring DTD overall, the exponential DTD with $\tau=1.5$ Gyr, is intermediate among all our DTDs in terms of the number of prompt SNe Ia and median delay time but has the {\it lowest} rate at very long delay times ($\sim10$ Gyr).
+Models with a large fraction of prompt SNe Ia, such as the power-law and two-population DTDs, fare quite poorly, with the steepest power-law ($\alpha=-1.4$) ending up in the bottom third across the board for most of our SFHs.
+The choice of DTD has a clear effect on the model scores, and this effect is similar for every observable.
+The models which perform the best (most \yes's and fewest \no's) are the most extended DTDs with the fewest prompt SNe Ia: both power-law DTDs, the exponential DTD with $\tau=3$ Gyr, and the triple-system DTD.
+The latter actually produces the highest scores for each observable, but the plateau DTD with $W=1$ Gyr is the most successful across all SFHs; both models have some of the longest median delay times.
+Models with a large fraction of prompt SNe Ia, such as the power-law and two-population DTDs, fare quite poorly, with the steepest power-law ($\alpha=-1.4$) and two-population DTDs ending up in the bottom third across the board for most of our SFHs.
+The fiducial power-law ($\alpha-1.1$) does slightly better, but still compares poorly to the more extended DTDs.
+
+Each DTD tends to score similarly across the board, but there are some combinations of SFH and DTD that buck the general trend.
+For example, the two-population DTD with the early-burst SFH produces an MDF which scores quite well.
+\todo{Explain why.} The shorter exponential DTD with $\tau=1.5$ Gyr has generally middling performance, but does a notably poorer job when combined with the early-burst SFH.
+\todo{Explain why.}
+
+\todo{Discuss how the age at the knee, given our age uncertainties, is not a great diagnostic.}
+
+%[Old text] While certain DTDs tend to score better than others overall, there is no single DTD which always produces optimal agreement with the data across all observables and for all SFHs.
 If an inside-out or late-burst SFH is chosen, the exponential DTDs score the highest across all observables.
@@
 If the early-burst SFH is chosen, the DTDs with a large prompt fraction (power-law and two-population) produce the best agreement with the APOGEE MDFs but the {\it worst} agreement with the other observables.
-Finally, for the two-infall SFH, any DTD other than the power-law and two-population scores well, but the best-scoring DTD varies between diagnostics.
+For the two-infall SFH, any DTD other than the power-law and two-population scores well, but the best-scoring DTD varies between observables.
 In general, too many prompt SNe Ia worsens agreement with observations across all our SFHs, while too few prompt SNe Ia can also worsen agreement for some SFHs and observables.
 
-Across most of the observables, the power-law ($\alpha=-1.1$) DTD, which has the strongest motivation from extra-galactic observations, poorly reproduces the observed Galactic chemical abundance distributions.
-This can be mitigated somewhat with a longer minimum delay time, which we show in Section \ref{sec:onezone-results} has a similar effect on chemical evolution tracks as the addition of an initial plateau in the DTD.
-Even so, it is clear that the high fraction of prompt SNe Ia in the DTD of, e.g., \citet{Maoz2017-CosmicDTD} is at odds with Galactic chemical abundance measurements.
-Measurements of the cosmic SN Ia rate become much more uncertain above $z\approx1$, and it is difficult to constrain the SFH of individual galaxies below [number] [cite], so constraints on the DTD from external galaxies should be more sensitive to the rates at long delay times.
+The power-law ($\alpha=-1.1$) DTD has the strongest observational motivation but poorly reproduces the disk abundance distributions.
+This can be mitigated somewhat with a longer minimum delay time, which has a similar effect on chemical evolution tracks as the addition of an initial plateau in the DTD (see discussion in Section \ref{sec:onezone-results}).
+Even so, it is clear that the high fraction of prompt SNe Ia in the DTD of, e.g., \citet{MaozMannucci2012-SNeIaReview} is at odds with Galactic chemical abundance measurements.
+Measurements of the cosmic SN Ia rate become considerably uncertain at $z\gtrsim1$ \citep[see, e.g.,][]{Palicio2024-CosmicSNIaRate}.
+Additionally, measurements of galactic or cosmic SFHs typically provide constraints for the DTD in coarse age bins, with especially large uncertainties in the youngest bins \citep[e.g.,][]{MaozMannucci2012-SNeIaReview},
+%, and it is difficult to constrain the SFH of individual galaxies below [number] [cite],
+so constraints on the DTD from external galaxies should be more sensitive to the rates at long delay times.
 On the other hand, our results demonstrate that the high-$\alpha$ sequence in GCE models is highly sensitive to the DTD at short delay times.
@@
 It is noteworthy that the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale} best fits the majority of CSFRs in \citet{Palicio2024-CosmicSNIaRate}, and our similar exponential ($\tau=1.5$ Gyr) DTD {\it also} performs best across all our SFHs.
-[Intro sentence].
+\todo{Intro sentence}.
 \citet{Palicio2024-CosmicSNIaRate} fit combinations of cosmic star formation rates (CSFRs) and DTDs, many of which are similar to the forms in this paper, to the observed cosmic SN Ia rate.
-Notably, the DTD which best fit the majority of their CSFRs was the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale}, which is similar to the exponential form with $\tau=1.5$ Gyr (see Appendix \ref{app:analytic-dtds} for more discussion).
+Notably, the DTD that best fit the majority of their CSFRs was the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale}, which is similar to the exponential form with $\tau=1.5$ Gyr (see Appendix \ref{app:analytic-dtds} for more discussion).
 \citet{Palicio2024-CosmicSNIaRate} are able to exclude DTDs with a very high or very low fraction of prompt SNe Ia, but a number of their DTDs could produce a convincing fit to the observed rates with the right CSFR.
-[Connect back to this paper].
-
+Despite a very different methodology, their results mirror ours: that many forms for the DTD can produce a reasonable fit to the data when combined with the right SFH.
+Our findings are also in qualitative agreement with the isolated and cosmological simulations of \citet{Poulhazan2018-PrecisionPollution}, namely that DTDs with a significant prompt component produce narrower [O/Fe] distributions and a higher average [O/Fe].
 % In both isolated and cosmological simulations, \citet{Poulhazan2018-PrecisionPollution} found that DTDs with a significant prompt component (power-law and two-population) produced the highest average [O/Fe] and the narrowest [O/Fe] distributions.
@@
 This is likely a consequence of the fact that the exponential DTD has a much lower SN Ia rate at late times ($\sim10$ Gyr) than other models [expand on this].
-Our findings are also in qualitative agreement with the isolated and cosmological simulations of \citet{Poulhazan2018-PrecisionPollution}, namely that DTDs with a significant prompt component produce narrower [O/Fe] distributions and a higher average [O/Fe].
 
 % Is the MW DTD the same as elsewhere?
-Our finding that the $t^{-1}$ power-law DTD poorly reproduces observed abundances could signal that the Milky Way and other galaxies obey different DTDs.
-This would not be too far beyond the findings of \citet{Maoz2017-CosmicDTD} that field galaxies and galaxy clusters have a different DTD slope.
+Our finding that the $t^{-1}$ power-law DTD poorly reproduces observed abundances is a signal that the Milky Way could obey a different DTD than other galaxies.
+This would not be too far beyond \citet{Maoz2017-CosmicDTD}'s finding that field galaxies and galaxy clusters have a different DTD slope.
 On the other hand, \citet{Walcher2016-SelfSimilarity} argue that the similarity of the age--\aFe relation between solar neighborhood stars and nearby elliptical galaxies is evidence for a universal DTD.
-A physical mechanism would be needed to produce different DTDs in different environments, such as a metallicity dependence in the fraction of close binaries \citep[e.g.,][]{Moe2019-CloseBinaryFraction}.
+A physical mechanism would be needed to produce a different slope or form for the DTD in different environments, such as a metallicity dependence in the fraction of close binaries \citep[e.g.,][]{Moe2019-CloseBinaryFraction}.
 
 Our model scores are highly sensitive to small changes in the nucleosynthetic yields.
-A decrease in the SN Ia yield of Fe to $y_{\rm Fe}^{\rm Ia}=0.0017$, which only shifts the end-point of the gas abundance tracks up by $\sim+0.05$ dex in [O/Fe], produces dramatically different scores for many of the models.
-\todo{More discussion of yield effects.}
+A decrease in the SN Ia yield of Fe to $y_{\rm Fe}^{\rm Ia}=0.0017$, which shifts the end-point of the gas abundance tracks up by $\sim+0.05$ dex in [O/Fe], produces dramatically different scores for many of the models.
+This is because the KL divergence tests penalize distributions which are not well aligned with the data, even if the general trends and shape of the distribution are reproduced.
+For example, if the two-infall models are run with $y_{\rm Fe}^{\rm Ia}=0.0017$, the abundance tracks do not dip below solar [O/Fe] (see the bottom-right panel of Figure \ref{fig:ofe-feh-sfh}) and consequently they out-score every other SFH.
+Small adjustments in the yields can affect the quality of the fit between our models and the data, so we caution against over-interpreting the model scores in Table \ref{tab:results}.
 
@@
 Their comparisons to data were limited to the solar neighborhood, and unlike our models, they did not factor in radial migration or gas outflows.
-Nevertheless, their conclusions align fairly well with ours: that a relatively low fraction of prompt SNe Ia is needed to produce good agreement with observations, and that a higher prompt fraction worsens that agreement.
+Nevertheless, their conclusions align fairly well with ours: a relatively low fraction of prompt SNe Ia is needed to produce good agreement with observations.
 
@@
 
-To our knowledge, this paper is the first exploration of the two-infall SFH in a multi-zone GCE model which incorporates both mass-loading and radial migration.
-A detailed examination of the parameters of the two-infall model is beyond the scope of this paper, but will be the subject of future work.
+To our knowledge, this paper is the first exploration of the two-infall SFH in a multi-zone GCE model which incorporates both mass-loaded outflows and radial migration.
+A detailed examination of the parameters of the two-infall model is beyond the scope of this paper but will be the subject of future work.
 
@@
 % Taken from introduction
-The bimodal distribution of \aFe in stars with similar metallicities was first noted in the solar neighborhood \citep[e.g.,][]{Furhmann1998-NearbyStars}, later extended to the whole of the Milky Way disk \citep{Nidever2014-ChemicalEvolutionAPOGEE,Hayden2015-ChemicalCartography}.
+The bimodal distribution of \aFe in stars with similar metallicities was first noted in the solar neighborhood \citep[e.g.,][]{Furhmann1998-NearbyStars} and later extended to the rest of the Milky Way disk \citep{Nidever2014-ChemicalEvolutionAPOGEE,Hayden2015-ChemicalCartography}.
 The ``high-$\alpha$'' population contains stars with low enrichment from SNe Ia, so their abundance ratios reflect that of almost pure CCSN enrichment; it is associated with the kinematically hot thick disk \citep{Bensby2003-AbundanceTrends}.
@@
 We have explored the consequences of eight different forms for the SN Ia DTD in multi-zone GCE models with radial migration.
-For each DTD, we explored combinations with four different popular SFHs from the literature, which represent a broad range of behavior over the lifetime of the disk.
+For each DTD, we explored combinations with four different popular SFHs from the literature, which represent a broad range of behavior over the lifetime of the disk seen in many prior GCE models.
 % in combination with four different SFHs in multi-zone GCE models with radial migration. 
 We compared our model outputs to abundances from APOGEE and ages from \citetalias{Leung2023-Ages} for stars across the Milky Way disk.
-For each model, we computed a numerical score which reflects the agreement between the model output and the data across the entire disk for five observables.
+For each model, we computed a numerical score that reflects the agreement between the predictions and data across the entire disk for five observables.
 Our main conclusions are as follows:
@@
     \item The SFH is the critical factor for producing a bimodal [O/Fe] distribution at fixed [Fe/H].
-On its own, the DTD cannot produce a bimodal [O/Fe] distribution that matches what is observed, but it does affect the location and strength of the high-$\alpha$ sequence, potentially enhancing the \aFe bimodality resulting from the choice of SFH.
-Radial migration also cannot reproduce the \aFe bimodality on its own.
+On its own, the DTD cannot produce a bimodal [O/Fe] distribution that matches what is observed.
+However, it does affect the location and strength of the high-$\alpha$ sequence, potentially enhancing the \aFe bimodality resulting from the choice of SFH.
+Radial migration also does not predict the \aFe bimodality on its own, in agreement with \citetalias{Johnson2021-Migration} but in tension with \citep{Sharma2021-RadialMigration} and \citep{Chen2023-RadialMixingRedux}.
 
     \item The MDF is more sensitive to the choice of SFH than the DTD.
-Overall trends in the MDF across the Galaxy are primarily driven by the assumed radial abundance gradient and stellar migration prescription, although it is more sensitive to the DTD in the inner Galaxy than elsewhere.
+Overall trends in the MDF across the Galaxy are primarily driven by the assumed radial abundance gradient and stellar migration prescription, but it is more sensitive to the DTD in the inner Galaxy due to the more sharply declining SFH (see discussion in Section \ref{sec:feh-df}).
 
@@
 A similar metallicity dependence has also been observed in the rate of CCSNe \citep{Pessi2023-MetalDepCCSNe}.
-The consequences of a metallicity-dependent SN Ia rate in the context of a multi-zone GCE model with radial migration could be explored in a future paper.
+% The consequences of a metallicity-dependent SN Ia rate in the context of a multi-zone GCE model with radial migration could be explored in a future paper.
 A metallicity dependence on the {\it shape} of the DTD could also be interesting to explore, for example if binary evolution leads to different progenitor systems at low and high metallicity.
-
-Our results indicate that the range of parameter space in the DTD is still too broad to be completely constrained by GCE models.
-Future constraints on the DTD may come from the Legacy Survey of Space and Time (LSST) at the Vera Rubin Observatory \todo{[cite]}, which is expected to observe 10 million \todo{(?)} SNe during its X-year run.
+These previous investigations varied only the normalization in the DTD.
+\citet{Gandhi2022-MetallicityDependentRates} take into account radial migration by construction through their use of the FIRE-2 simulations.
+An exploration in the context of multi-zone models would be an interesting direction for future work, as would variations in the DTD shape.
+
+Our results indicate that the allowed range of parameter space in GCE models is still too broad to precisely constrain the DTD.
+Future constraints may come from the Legacy Survey of Space and Time (LSST) at the Vera Rubin Observatory \citep{Ivezic2019-LSST}, which is expected to observe several million SNe during its X-year run.
 On the other hand, better constraints on the Galactic SFH provided by SDSS-V \citep{Kollmeier2017-SDSS-V} will enable future GCE studies to constrain the DTD at a higher confidence.
@@
 
-\todo{Carnegie land acknowledgement.}
 % Software acknowledgements if not a AAS journal
@@
     \includegraphics[width=0.49\linewidth]{figures/onezone_analytical_dtd.pdf}
-    \caption{\textit{Left:} Analytic DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and simple DTD functions (dashed curves).
+    \caption{\textit{Left:} Analytic DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and simplified approximations thereof (dashed curves; see Section \ref{sec:dtd-models}).
 Some functions are presented with a constant multiplicative factor for visual clarity.
 \textit{Right:} Abundance tracks and distributions from one-zone models with the analytic and simple DTDs (same color scheme).
-For clarity, we vary the mass-loading factor to be $\eta=4$, $\eta=2$, and $\eta=1$ for the red, green, and blue curves, respectively.
+For visual clarity, we vary the mass-loading factor to be $\eta=4$, $\eta=2$, and $\eta=1$ for the red, green, and blue curves, respectively.
 All other model parameters are identical.}
@@
 The right-hand panel of Figure \ref{fig:analytic-dtds} shows the results of one-zone chemical evolution models with the \citet{Greggio2005-AnalyticalRates} DTDs and our simplified forms.
-We use the same model parameters as in Section \ref{sec:onezone-results}.
+We use the same model parameters as in Section \ref{sec:onezone-results} but with different values of $\eta$ to spread the tracks out visually in [Fe/H].
 The model with the SD DTD follows a nearly identical track to the exponential ($\tau=1.5$ Gyr) DTD, and they produce very similar distributions of [O/Fe].
@@
     \includegraphics[width=\linewidth]{figures/radial_migration.pdf}
-    \caption{The distribution of final radius $R_{\rm final}$ as a function of formation radius $R_{\rm form}$ and age for the \hydro analogue (top row) and Gaussian sampling scheme (bottom row).
-From left to right, star particles are binned by formation annulus, from the inner disk (far left column) to the solar annulus (center column) to the outer disk (far right column).
+    \caption{The distribution of final radius $R_{\rm final}$ as a function of formation radius $R_{\rm form}$ and age for the \hydro analogue (top row) and Gaussian sampling scheme (bottom row; see discussion in Appendix \ref{app:migration}).
+From left to right, star particles are binned by formation annulus, as noted at the top of each column of panels.
 Within each panel, colored curves represent the different age bins, ranging from the youngest stars (dark blue) to the oldest (dark red).
-In the top row, we exclude age bins with fewer than 100 unique analogue IDs for clarity.
-All distributions are normalized so that the area under the curve is 1, and have been smoothed by a boxcar function with a width of 0.5 kpc.
-The vertical dotted black lines indicate the bounds of each bin in $R_{\rm form}$; stars within that region of the distribution have not migrated outside their birth annulus over their lifetime.}
+In the top row, we exclude age bins with fewer than 100 unique analogue IDs for visual clarity.
+All distributions are normalized so that the area under the curve is 1, and have been boxcar-smoothed with a window width of 0.5 kpc.
+The vertical dotted black lines indicate the bounds of each bin in $R_{\rm form}$; stars within that region of the distribution have not migrated significantly far from their birth radius.}
     \label{fig:radial-migration}
@@
 
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figures/midplane_distance.pdf}
+    \caption{Similar to Figure \ref{fig:radial-migration} but for the distribution of present-day midplane distance $z_{\rm final}$ as a function of radius and age.
+From left to right, star particles are binned by \textit{final} annulus.
+In the top row, we exclude age bins with fewer than 500 unique analogue IDs for clarity.
+All distributions have been boxcar-smoothed with a window width of 0.1 kpc.}
+    \label{fig:midplane-distance}
+    \script{midplane_distance.py}
+\end{figure*}
+
 In their multi-zone models, \citetalias{Johnson2021-Migration} randomly assign an analogue star particle from \hydro, adopting its radial migration distance $\Delta R$ and final midplane distance $z$, for each stellar population generated by \vice.
-This allows \vice to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
+The analogues are chosen such that the star particle was born at a similar radius and time as the stellar population in the GCE model.
+This prescription allows \vice to adopt a realistic pattern of radial migration without needing to implement its own hydrodynamical simulation.
 However, in regions where the number of \hydro star particles is relatively low, such as at large $R_{\rm gal}$ and small $t$, a single \hydro star particle can be assigned as an analogue to multiple \vice stellar populations.
@@
 We fit a Gaussian to the distribution of $\Delta R = R_{\rm final} - R_{\rm form}$ from the \hydro output, binned by both formation radius $R_{\rm form}$ and age.
-We are motivated by the findings of \citet{Okalidis2022-AurigaMigration} that the strength of stellar migration in the Auriga simulations \todo{(cite?)} varies with both $R_{\rm form}$ and age.
+We are motivated by the findings of \citet{Okalidis2022-AurigaMigration} that the strength of stellar migration in the Auriga simulations \citep{Grand2017-AurigaSims} varies with both $R_{\rm form}$ and age.
 Each Gaussian is centered at 0, and we find that the scale $\sigma_{\rm RM}$ is best described by the function
@@
 For comparison, \citet{Frankel2018-RadialMigration} found a steeper $\tau$-dependence of $\sigma_{\rm RM}\propto \tau^{1/2}$ and a higher scaling of $\sigma_{\rm RM8}=3.6$ kpc for a sample of APOGEE red clump stars.
-Our age scaling is in good agreement with \citet{Lu2023-LMCStars}, who find that radial migration in galaxies from the NIHAO simulations \todo{(cite?)} follow a relatively universal relation of $\sigma_{\rm RM}\propto\tau^{0.32}$.
-% This value is $\sim30\%$ smaller than that found by \citet{Frankel2019-InsideOutGrowth}.
+Our age scaling is in good agreement with \citet{Lu2023-LMCStars}, who find that radial migration in galaxies from the NIHAO simulations \citep{Wang2015-NIHAOSims} follow a relatively universal relation of $\sigma_{\rm RM}\propto\tau^{0.32}$, but with a slightly higher $\sigma_{\rm RM8}\approx3$ kpc.
+We use the lower value here as it reproduces the trends in \hydro, and by extension \citetalias{Johnson2021-Migration}, but the $\sim25\%$ difference may affect the predictions.
 
 When \vice forms a stellar population at initial radius $R_{\rm form}$, we assign a value of $\Delta R$ by randomly sampling from a Gaussian with a width given by Equation \ref{eq:radial-migration}.
-The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citetalias{Johnson2021-Migration}, but with a time dependence $\propto \Delta t^{1/3}$.
-This is motivated by the age-scaling of $\sigma_{\rm RM}$ and is slower than the diffusion process of, e.g., \citet{Frankel2018-RadialMigration}.
+The star particle migrates to its final radius $R_{\rm final}$ in a similar manner to the ``diffusion'' case from \citetalias{Johnson2021-Migration}, but with a time dependence $\propto \Delta t^{1/3}$, motivated by the age-scaling of $\sigma_{\rm RM}$.
 
 We note that the \hydro galaxy has a weak and transient bar, in contrast to the Milky Way.
-The presence of a strong bar has been found to affect the strength of radial migration throughout the disk \citep[e.g.,][]{Brunetti2011-BarredSpiralDiffusion,Okalidis2022-AurigaMigration} and lead to a flattening of the metallicity gradient for old populations \citet{Okalidis2022-AurigaMigration}.
+The presence of a strong bar has been found to affect the strength of radial migration throughout the disk \citep[e.g.,][]{Brunetti2011-BarredSpiralDiffusion} and lead to a flattening of the metallicity gradient for old populations \citep{Okalidis2022-AurigaMigration}.
 % also a slower timestep evolution than diffusion
@@
 Figure \ref{fig:radial-migration} compares the distributions of $R_{\rm final}$ in bins of $R_{\rm form}$ and stellar age between the \hydro analogue method and our new prescription.
-There is good agreement across the Galaxy in the youngest age bins, but the ``clumpiness'' of the \hydro analogue populations becomes evident for old stars formed in the outer Galaxy.
+There is good agreement across the Galaxy in the youngest age bins, but the ``clumpiness'' of the \hydro analogue populations, a consequence of sampling noise, becomes evident for old stars formed in the outer Galaxy.
 The distribution of \hydro star particles in the $10\leq\tau<12$ Gyr and $11\leq R_{\rm form}<13$ kpc bin indicates significant inward migration due to a merging satellite.
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=\linewidth]{figures/midplane_distance.pdf}
-    \caption{Similar to Figure \ref{fig:radial-migration} but for the distribution of final midplane distance $z_{\rm final}$ as a function of final radius and age.
-From left to right, star particles are binned by \textit{final} annulus.
-In the top row, we exclude age bins with fewer than 500 unique analogue IDs for clarity.
-All distributions have been smoothed by a boxcar function with a width of 0.1 kpc.}
-    \label{fig:midplane-distance}
-    \script{midplane_distance.py}
-\end{figure*}
-
 Like \citetalias{Johnson2021-Migration}, we assume all stellar populations form in the midplane ($z=0$).
-\citetalias{Johnson2021-Migration} take the final midplane distance $z_{\rm final}$ from the \hydro analogue particle.
+\citetalias{Johnson2021-Migration} take the present-day midplane distance $z_{\rm final}$ directly from the \hydro analogue particle.
 To produce smoother abundance distributions, we fit a sech$^2$ function \citep{Spitzer1942} to the distribution of $z$ in \hydro.
@@
 \begin{equation}
-    {\rm PDF}(z_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z_{\rm final}}{2 h_z}\Big)
+    {\rm PDF}(z_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z_{\rm final}}{2 h_z}\Big).
     \label{eq:sech-pdf}
 \end{equation}
-and the corresponding cumulative distribution function (CDF) is
-\begin{equation}
-    {\rm CDF}(z_{\rm final}) = \frac{1}{1 + e^{-z_{\rm final} / h_z}}.
-    \label{eq:sech-cdf}
-\end{equation}
+% and the corresponding cumulative distribution function (CDF) is
+% \begin{equation}
+%     {\rm CDF}(z_{\rm final}) = \frac{1}{1 + e^{-z_{\rm final} / h_z}}.
+%     \label{eq:sech-cdf}
+% \end{equation}
 We fit Equation \ref{eq:sech-pdf} to the distributions of $z$ in \hydro in varying bins of $T$ and $R_{\rm final}$. We find that $h_z$ is best described by the function
 \begin{equation}
-    h_z = h_{z,8} \exp(\tau/\tau_s + R_{\rm final}/R_s)
+    h_z = (h_{z,s}/e^2) \exp(\tau/\tau_s + R_{\rm final}/R_s)
     \label{eq:scale-height}
 \end{equation}
-where $h_{z,8}=0.032$ kpc, $\tau_s=7$ Gyr, and $R_s=6$ kpc.
+where $h_{z,s}=0.24$ kpc is the scale height at $\tau_s=7$ Gyr and $R_s=6$ kpc.
 For each star particle in \vice, we sample $z_{\rm final}$ from the distribution described by Equation \ref{eq:sech-pdf} with a width given by Equation \ref{eq:scale-height}.
-Figure \ref{fig:midplane-distance} shows the resulting distributions of $z_{rm final}$ are similar to the \hydro analogue scheme for all but the oldest stellar populations.
+Figure \ref{fig:midplane-distance} shows the resulting distributions of $z_{\rm final}$ are similar to the \hydro analogue scheme for all but the oldest stellar populations.
 

### 2024-04-09 src/scripts/extract_multizone_output.py
Update extract_multizone_output.py

@@ -6,5 +6,5 @@ to src/data/multizone/.
 import tarfile
 import paths
 
-with tarfile.open(paths.data / 'multizone.tar.gz') as f:
-    f.extractall(paths.data / 'multizone')
+with tarfile.open(paths.data / 'multizone.tar.gz', mode='r:gz') as f:
+    f.extractall(paths.data)

### 2024-04-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Even so, it is clear that the high fraction of prompt SNe Ia in the DTD of, e.g., \citet{MaozMannucci2012-SNeIaReview} is at odds with Galactic chemical abundance measurements.
+
 Measurements of the cosmic SN Ia rate become considerably uncertain at $z\gtrsim1$ \citep[see, e.g.,][]{Palicio2024-CosmicSNIaRate}.
@@
 % Is the MW DTD the same as elsewhere?
-Our finding that the $t^{-1}$ power-law DTD poorly reproduces observed abundances is a signal that the Milky Way could obey a different DTD than other galaxies.
+Our finding that the $t^{-1}$ power-law DTD poorly reproduces observed abundances could suggest that the Milky Way obeys a different DTD than other galaxies.
 This would not be too far beyond \citet{Maoz2017-CosmicDTD}'s finding that field galaxies and galaxy clusters have a different DTD slope.

### 2024-05-16 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % For TeXworks
-\makeatletter
-\declare@file@substitution{revtex4-1.cls}{revtex4-2.cls}
-\makeatother
-
-% Define document class
-% \documentclass[modern,linenumbers]{aastex631}
-% \documentclass[twocolumn,twocolappendix,linenumbers,trackchanges]{aastex631}
+% \makeatletter
+% \declare@file@substitution{revtex4-1.cls}{revtex4-2.cls}
+% \makeatother
+
 \documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
@@
 \usepackage{graphicx}
-% \usepackage{layouts}
 \usepackage{xcolor}
-% \usepackage{upgreek}
 \let\tablenum\relax
@@
 \newcommand{\todo}[1]{{\color{red}#1}}
+\newcommand{\samplesize}{\num{192990}\xspace}
+\newcommand{\agesamplesize}{\num{58987}\xspace}
 
@@
 
-% Title
-% \title{The Galactic Delay-Time Distribution of Type Ia Supernovae:\\
-%        A Chemical Evolution Perspective}
 \title{Galactic Chemical Evolution Models Favor an Extended Type Ia Supernova Delay-Time Distribution}
 
-% Author list
 \author[0000-0003-3781-0747]{Liam O.\ Dubay}
@@
 \affiliation{\ccappaffil}
-% \author[0000-0001-7775-7261]{David H. Weinberg}
 
@@
 
-% Abstract from AAS 241
 \begin{abstract}
@@
 SNe Ia do not explode immediately after star formation, and the delay-time distribution (DTD) has not been definitively determined by supernova surveys or theoretical models.
-Because the DTD also affects the relationship among age, [Fe/H], and \aFe in chemical evolution models, comparison with observations of stars in the Milky Way is an important consistency check for any proposed DTD.
-We implement several popular forms of the DTD in combination with multiple star formation histories for the Milky Way in %one-zone and
-    multi-zone chemical evolution models which include radial stellar migration.
-    % using the Versatile Integrator for Chemical Evolution (\vice). \vice includes a prescription for radial stellar migration in multi-zone models. 
+Because the DTD also affects the relationship among age, [Fe/H], and [$\alpha$/Fe] in chemical evolution models, comparison with observations of stars in the Milky Way is an important consistency check for any proposed DTD.
+We implement several popular forms of the DTD in combination with multiple star formation histories for the Milky Way in multi-zone chemical evolution models which include radial stellar migration.
 We compare our predicted interstellar medium abundance tracks, stellar abundance distributions, and stellar age distributions to the final data release of the Apache Point Observatory Galactic Evolution Experiment (APOGEE).
-We find that the DTD has the largest effect on the \aFe distribution: a DTD with more prompt SNe Ia produces a stellar abundance distribution that is skewed toward a lower \aFe ratio.
-    % whereas a DTD with more delayed SNe Ia produces a distribution that is skewed toward higher \aFe.
-    While the DTD alone cannot explain the observed bimodality in the \aFe distribution, in combination with an appropriate star formation history it affects the goodness of fit between the predicted and observed high-$\alpha$ sequence.
+We find that the DTD has the largest effect on the [$\alpha$/Fe] distribution: a DTD with more prompt SNe Ia produces a stellar abundance distribution that is skewed toward a lower [$\alpha$/Fe] ratio.
+While the DTD alone cannot explain the observed bimodality in the [$\alpha$/Fe] distribution, in combination with an appropriate star formation history it affects the goodness of fit between the predicted and observed high-$\alpha$ sequence.
 Our model results favor an extended DTD with fewer prompt SNe Ia than the fiducial $t^{-1}$ power law.
@@
 
-% [Hook and intro paragraph]
 Galactic chemical evolution (GCE) studies seek to explain the observed distribution of metals throughout the Milky Way Galaxy.
@@
 This delayed enrichment leads to a decrease in \aFe with increasing [Fe/H] \citep{Matteucci1986-SupernovaEnrichment}.
-% The decrease in \aFe with [Fe/H] has long been understood to be a consequence of the delayed nature of SNe Ia, which do not contribute substantially to chemical enrichment for $\sim 10^8$ years after the commencement of star formation \citep{Tinsley1979-StellarLifetimes,Matteucci1986-SupernovaEnrichment}.
-% As SNe Ia are a product of intermediate-mass stars which undergo binary evolution, they do not contribute substantially to chemical enrichment for $\sim 10^8$ years after the commencement of star formation \citep{Matteucci1986-SupernovaEnrichment}.
-% The timescale for Fe enrichment in the Galaxy, a key component of chemical evolution models, is directly linked to the progenitor lifetimes of SNe Ia. 
 Therefore, the relative abundances of the $\alpha$-elements and Fe as a function of stellar age trace the balance of SN rates over time.
 
-% [What is the delay-time distribution]
-The {\it delay-time distribution} (DTD) refers to the rate of SN Ia events per unit mass of star formation as a function of stellar population age
-% The rate of SNe Ia which explode as a function of time after the formation of a hypothetical unit-mass single stellar population is known as the delay-time distribution 
-\citep[for a review, see Section 3.5 of][]{Maoz2014-Review}.
+The {\it delay-time distribution} (DTD) refers to the rate of SN Ia events per unit mass of star formation as a function of stellar population age \citep[for a review, see Section 3.5 of][]{Maoz2014-Review}.
 When the DTD is convolved with the Galactic star formation rate (SFR), it yields the overall SN Ia rate.
@@
 Searches for signs of interaction between the SN ejecta and a non-degenerate companion \citep[e.g.,][]{Panagia2006-RadioEmission,Chomiuk2016-RadioEmission,Fausnaugh2019-EarlyIaLightCurves,Tucker2020-SNeIaSpectra,Dubay2022-SNeIaCSM} or for a surviving companion \citep[e.g.,][]{Schaefer2012-ExCompanionSNR,Do2021-Progenitor1972E,Tucker2023-SN2011fe} have placed tight constraints on the SD channel, heavily disfavoring it as the main pathway for producing ``normal'' SNe Ia.
-The DD channel, now the preferred model, faces issues of its own with matching observed SN Ia rates because not all WD mergers may lead to a thermonuclear explosion \citep[e.g.,][]{NomotoIben1985-DDMergers,SaioNomoto1998-DDMergers,Shen2012-DDMergers}, and the progenitor systems are difficult to detect even within our own Galaxy \citep{RebassaMansergas2019-WhereAreDDProgenitors}.
-
-% [Theoretical DTDs]
-% Uncertainties in the progenitor channels of SNe Ia translate into uncertainties in the shape of the DTD. 
-% By formulating analytic DTDs for several progenitor models, \citet{Greggio2005-AnalyticalRates} found that the SD channel tends to produce a steeper DTD function than the DD channel, and the median delay time (by which 50\% of SNe Ia have exploded) can vary by a factor of 10 depending on the chosen progenitor scenario and its particular parameters.
+The DD channel is now the preferred model, but it faces issues with matching observed SN Ia rates because not all WD mergers necessarily lead to a thermonuclear explosion \citep[e.g.,][]{NomotoIben1985-DDMergers,SaioNomoto1998-DDMergers,Shen2012-DDMergers}, and the progenitor systems are difficult to detect even within our own Galaxy \citep{RebassaMansergas2019-WhereAreDDProgenitors}.
+
 As a result of the uncertainty regarding SN Ia progenitors, theoretical models have yet to converge on a single prediction for the DTD.
@@
 The DTD which would result from the SD channel depends greatly on the assumptions of binary population synthesis, but in general is expected to cover a narrower range of delay times and may feature a steep exponential cutoff at the long end \citep[e.g.,][]{Greggio2005-AnalyticalRates}.
-% More recently, \citet{Rajamuthukumar2023-TripleEvolution} computed a DTD from the evolution of triple system progenitors.
-[Expand, connect binary evolution to delay times, look for other theory papers]
-
-% [Observational DTDs]
+
 Surveys of SNe Ia can constrain the DTD by comparing the observed rate of SNe Ia to their host galaxy parameters \citep[e.g.,][]{Mannucci2005-SNRate,Heringer2019-FieldGalaxyDTD} or inferred star formation histories \citep[SFHs; e.g.,][]{Maoz2012-SloanIIDTD}, measuring SN Ia rates in galaxy clusters \citep[e.g.,][]{Maoz2010-ClusterDTD}, or comparing the volumetric SN Ia rate to the cosmic SFH as a whole \citep[e.g.,][]{Graur2014-VolumetricSNIaRates,Strolger2020-ExponentialDTD}.
@@
 It is especially difficult to constrain the DTD for short delay times \citep{MaozMannucci2012-SNeIaReview} because of the need for SN Ia rates at long lookback times and uncertainties in the age estimates of stellar populations.
-
-% Notes on observational DTDs:
-% \citet{Strolger2004-SNIaProgenitors} analyzed 42 SNe Ia with redshifts $0.2<z<1.6$ and favored a delayed ($\gtrsim2$ Gyr) narrow Gaussian DTD while disfavoring exponentially declining models with a large fraction of prompt SNe Ia.
-% \citet{Mannucci2005-SNRate} found that the SN Ia rate per unit mass has a strong dependence on host galaxy morphology and color.
-Using these results, \citet{Mannucci2006-TwoPopulations} obtained a best-fit model for the DTD which consists of both a prompt component ($<100$ Myr) and a long exponential tail.
-% The Maoz studies all assume a particular form for the DTD and fit for the specific parameters. They do not quantitatively favor one form over another (e.g., power-law over exponential). 
-% \citet{Castrillo2021-DTD} find a best fit power law slope of $\alpha\approx-1.1$ with a minimum delay time of $\sim50$ Myr, they also find a fairly high correlation between SN Ia rate and H$\alpha$ (a proxy for young stars) which is surprising.
-% \citet{Stolger2020-ExponentialDTD} perform maximum likelihood estimations based on the cosmic star formation history and the star formation histories of individual galaxies.
-In both cases their best fit functions were approximately exponential, though they started with a skew-normal function so could not have ended up with a power law even if they wanted to.
-They don't actually report the timescale of this exponential, but based on the plots I'd say it's about 1.5 - 2 (1.7?) Gyr.
-Their best fit parameters make no sense to me as they don't report their units.
 
@@
 Since the \aFe abundance reflects the ratio of CCSN to SN Ia enrichment, the DTD should influence the \aFe bimodality.
-% [Introduce other MW disk features?]
 
@@
 The current era of large spectroscopic surveys such as the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE} and the ongoing Milky Way Mapper \citep{Kollmeier2017-SDSS-V} has made abundances across the Milky Way disk available for comparison to more sophisticated GCE models.
-
-% Notes on GCE studies
-% \citet{Andrews2017-ChemicalEvolution} predict abundance tracks and distributions using one-zone models for four different DTDs; they find that most are consistent with their abundance data.
-% \citet{Palicio2023-AnalyticDTD} derive analytic solutions to one-zone chemical evolution equations for seven DTDs, but their comparisons to data are limited to the solar neighborhood. 
-% \citet{Poulhazan2018-PrecisionPollution} investigate six different DTDs in a smoothed-particle hydrodynamics simulation, but they only present global results for the entire galaxy, they don't compare abundances throughout the disk, and they don't compare to observations.
 
@@
 \end{equation}
-where %$\dot M_\star(t)$ is the SFR at time $t$, 
-%$R_{\rm Ia}(t) dt$ is the number of SNe Ia which explode in the time interval $(t, t+dt)$ per unit mass of stars formed at $t=0$, 
-$R_{\rm Ia}$ is the DTD in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$,
-$t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the lifetime of the disk.
+where $R_{\rm Ia}$ is the DTD in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$, $t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the lifetime of the disk.
 The denominator of Equation \ref{eq:weighted-sfr} is therefore equal to $N_{\rm Ia}/M_\star$, the total number of SNe Ia per M$_{\odot}$ of stars formed.
@@
 $f_{\rm Ia}$ does not include the normalization, so it has units of Gyr$^{-1}$ as opposed to M$_\odot^{-1}$ Gyr$^{-1}$ and is related to $R_{\rm Ia}$ according to
-% The relationship between $f_{\rm Ia}$, which has units of ${\rm Gyr}^{-1}$, and $R_{\rm Ia}$, which has units of ${\rm M}_\odot^{-1}\,{\rm Gyr}^{-1}$, is: 
 \begin{equation}
@@
 
-% \begin{deluxetable*}{lcll}
-% \tablecaption{Summary of SN Ia DTDs explored in this paper.\label{tab:dtds}}
-% \tablehead{
-% \colhead{Model} & \colhead{Eq.} & \colhead{Parameters} & \colhead{Similar to}
-% }
-% \startdata
 \begin{table*}
@@
 \end{table*}
-% \enddata
-% \end{deluxetable*}
 
@@
 \end{equation}
-% where $A_\alpha = (\alpha+1)(t_{\rm max}^{\alpha+1} - t_{\rm min}^{\alpha+1})^{-1}$ is the normalization coefficient.
 A declining power-law with $\alpha\sim-1$ arises from typical assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral \citep[see Section 3.5 from][]{Maoz2014-Review}.
@@
 \end{equation}
-% where $B_W=[(W-t_{\rm min}) + \frac{t_{\rm max}^{\alpha+1} - W^{\alpha+1}}{(\alpha+1)W^\alpha}]^{-1}$ is the normalization coefficient.
 Our primary motivation is to consider a model which matches observations at delay times beyond a few Gyr, where the DTD is best constrained, but with a smaller fraction of prompt ($\lesssim 100$ Myr) SNe Ia than the single power law.
@@
 The inside-out model produced a good agreement to the age--[O/Fe] relation observed by \citet{Feuillet2019-MilkyWayAges}, while the late-burst model better matched their observed age--metallicity relation.
-% The latter two models (early-burst and two-infall) feature discontinuous or ``bursty'' SFHs, and were proposed by \citet{Conroy2022-ThickDisk} and \citet{Chiappini1997-TwoInfall}, respectively, to explain the distinct evolution of the high- and low-$\alpha$ sequences.
 The latter two models feature discontinuous or ``bursty'' SFHs.
 The early-burst model, proposed by \citet{Conroy2022-ThickDisk}, uses an efficiency-driven starburst to explain the break in the \aFe trend observed in the H3 survey \citep{Conroy2019-H3Survey}.
-% , and [cite] found that it can also produce a bimodal \aFe distribution.
 The two-infall model was proposed by \citet{Chiappini1997-TwoInfall} and features two distinct episodes of gas infall which produce the thick and thin disks.
@@
 
-The inside-out and late-burst models
-% The first two models are taken from \citetalias{Johnson2021-Migration} and 
-are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_\star$ is prescribed along with the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g/\dot\Sigma_\star$.
+The inside-out and late-burst models are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_\star$ is prescribed along with the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g/\dot\Sigma_\star$.
 The remaining quantities, infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
@@
 The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified.
-% See Appendix B of \citetalias{Johnson2021-Migration} for details on the normalization of the SFH. 
 The SFH is normalized such that the model predicts an accurate total stellar mass and surface density gradient (see Appendix B of \citetalias{Johnson2021-Migration}).
@@
 Evidence for a recent star formation burst $\sim 2-3$ Gyr ago has been found in {\it Gaia} \citep{Mor2019-Starburst} and in massive WDs in the solar neighborhood \citep{Isern2019-Starburst}.
-Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr. The determination of $\tau_{\rm sfh}$ 
-% and the normalization of the SFR as a function of $R_{\rm gal}$ 
-is the same as in the inside-out case.
+Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr. The determination of $\tau_{\rm sfh}$ is the same as in the inside-out case.
 
@@
 \end{equation}
-% In this model, the first infall produces the thick disk and the second infall produces the thin disk. 
 where $\tau_1=1$ Gyr and $\tau_2=4$ Gyr are the exponential timescales of the first and second infall, respectively, and $t_{\rm on}=4$ Gyr is the onset time of the second infall \citep[based on typical values in, e.g.,][]{Chiappini1997-TwoInfall,Spitoni2020-TwoInfall,Spitoni2021-TwoInfall}.
@@
 
-% \begin{table}
-%     \centering
-%     \caption{Median parameter uncertainties}
-%     \label{tab:sample}
-%     \begin{tabular}{ccc}
-%         \hline\hline
-%         Parameter & Median Uncertainty & Source \\
-%         \hline
-%         ${\rm [Fe/H]}$ & $9.2\times10^{-3}$ & APOGEE DR17 \\
-%         ${\rm [O/Fe]}$ & $1.8\times10^{-2}$ & APOGEE DR17 \\
-%         log(Age/Gyr) & $0.10$ & \citetalias{Leung2023-Ages} \\
-%         \hline
-%     \end{tabular}
-% \end{table}
-
 We compare our model results to abundance measurements from the final data release \citep[DR17;][]{Abdurro'uf2022-SDSSIV-DR17} of the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE}.
@@
 Table \ref{tab:sample} lists our selection criteria, which largely follow from \citet{Hayden2015-ChemicalCartography}.
-This produces a final sample of \variable{output/sample_size.txt}stars with [O/Fe] and [Fe/H] abundance measurements.
+This produces a final sample of \samplesize stars with [O/Fe] and [Fe/H] abundance measurements.
 APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
@@
 Importantly, the \citetalias{Leung2023-Ages} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{Mackereth2019-astroNN-Ages}.
-We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt}APOGEE stars with age estimates.
-We note that we use the full sample of \variable{output/sample_size.txt}APOGEE stars unless we explicitly compare to age estimates.
+We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \agesamplesize APOGEE stars with age estimates.
+We note that we use the full sample of \samplesize APOGEE stars unless we explicitly compare to age estimates.
 Table \ref{tab:sample} also presents the median uncertainties in the data for [Fe/H], [O/Fe], and age.
@@
 
-% \begin{table}
-%     \centering
-%     \caption{A summary of parameters and their fiducial values for our one-zone chemical evolution models.\label{tab:onezone-parameters}}
-%     \begin{tabular}{ccl}
-%         \hline\hline
-%         Quantity & Value & \multicolumn{1}{c}{Description} \\
-%         \hline
-%         % $\Delta t$        & 10 Myr    & Time-step size \\
-%         % $t_{\rm max}$     & 13.2 Gyr  & Maximum simulation time \\
-%         % $\eta$            & 2.15      & Outflow mass-loading factor \\
-%         % $\tau_\star$        & 2.0 Gyr   & SFE timescale \\
-%         $\dot M_r$        & continuous    & Recycling rate \\
-%         % $t_D$             & 40 Myr    & Minimum SN Ia delay time \\
-%         % $M_{g,0}$         & 0         & Initial gas mass \\
-%         % $\dot M_\star(t)$     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
-%         % $\tau_{\rm rise}$ & 2.0 Gyr     & SFR rise timescale \\
-%         % $\tau_{\rm sfh}$  & 15.1 Gyr  & SFR exponential \\
-%         \hline
-%     \end{tabular}
-% \end{table}
-
-% [Intro paragraph, motivation for running one-zone models]
 Before running the full multi-zone models, it is useful to understand the effects of the DTD in more idealized conditions.
@@
 
-% All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=10$ Myr. 
 For consistency, we adopt most of the parameter values from Table \ref{tab:multizone-parameters} for our one-zone models.
@@
 Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_\star=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time $t_D=40$ Myr.
-% A summary of these fiducial parameters is presented in Table \ref{tab:onezone-parameters}.
 
@@
 For display purposes, these distributions are convolved with a Gaussian kernel with a standard deviation of 0.02 dex.
-    \textit{Left:} A power-law DTD with varying slope $\alpha$. 
-    % The dotted, dashed, and solid curves represent models with $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively. 
-    For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr. 
+    \textit{Left:} A power-law DTD with varying slope $\alpha$. For reference, the solid gray curve represents an exponential DTD with $\tau=3$ Gyr. 
     \textit{Center:} An exponential DTD with varying timescale $\tau$. 
-    % The solid, dashed, and dotted curves represent $\tau=6$, 3, and 1.5 Gyr, respectively.
     \textit{Right:} A plateau DTD with varying width $W$.
-    % The solid, dashed, and dotted green curves represent $W=1$, 0.3, and 0.1 Gyr, respectively. 
 All assume a post-plateau slope of $\alpha=-1.1$.
@@
 A steeper slope produces a sharper ``knee'' and a faster decline in [O/Fe] with increasing [Fe/H], resulting in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
-% Conversely, a shallower slope produces a gentler knee and slower decline in [O/Fe], resulting in a broader [O/Fe] DF and a greater number of high-$\alpha$ stars. 
-In all cases the [O/Fe] DF is distinctly unimodal. The MDF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
+In all cases the [O/Fe] DF is distinctly unimodal.
+The MDF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
 
@@
 
-Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of varying the width $W$ of the plateau DTD 
-% on abundance tracks and distributions. 
+Finally, the right-hand panel of Figure \ref{fig:onezone-threepanel} shows the effect of varying the width $W$ of the plateau DTD.
 The abundance tracks from several different plateau widths fill the space in between the exponential ($\tau=3$ Gyr) and power-law ($\alpha=-1.1$ with no plateau) models, which are both included in the panel for reference.
-% The abundance track from the plateau ($W=1$ Gyr) model is nearly identical to the exponential ($\tau=3$ Gyr), although the [O/Fe] DFs are somewhat more distinct, with the plateau model producing a peak closer to the power-law case.
 The plateau ($W=1$ Gyr) and exponential ($\tau=3$ Gyr) DTDs produce nearly identical abundance tracks but their [O/Fe] DFs are more distinct, illustrating the need for both observables to discriminate between DTDs.
@@
     \caption{\textit{Left:} Comparison of one-zone models with different combinations of minimum delay time $t_D$ and DTD shape.
-    % minimum SN Ia delay times $t_D=40$ Myr (solid) and 150 Myr (dashed curves) for three DTDs: power-law with $\alpha=-1.1$ (blue), plateau with $W=0.3$ Gyr (green), and exponential with $\tau=1.5$ Gyr (purple curves).
     The layout is similar to Figure \ref{fig:onezone-threepanel}.
@@
     \textit{Right:} Comparison of one-zone models with five different DTD models (see Figure \ref{fig:dtds}).
-    % : triple-system (yellow), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink).
     }
@@
 
-% One parameter of the DTD which we hold fixed in the multi-zone models is the minimum SN Ia delay time $t_D$.
-Typical choices for $t_D$ in the literature range from $\sim 30$ Myr \citep[e.g.,][]{Poulhazan2018-PrecisionPollution} to 150 Myr \citepalias[e.g.,][]{Johnson2021-Migration}.
 We also explore the effect of varying the minimum SN Ia delay time $t_D$ (Section \ref{sec:minimum-delay}).
@@
 
-% [Summary and conclusions from one-zone models]
 The results presented in this section indicate that the [O/Fe]--[Fe/H] abundance tracks and the [O/Fe] DF are most sensitive to the parameters of the DTD, while the MDF is a less sensitive diagnostic.
@@
 \citet{Palicio2023-AnalyticDTD} compared similar DTDs in one-zone models with a two-infall SFH (see \ref{sec:two-infall-discussion}).
-% for a similar comparison of DTDs with a two-infall SFH, we direct the reader to \citet{Palicio2023-AnalyticDTD}.
 
@@
 In the following subsections, we present the stellar abundance and age distributions from the multi-zone models and compare to APOGEE data from across the Galactic disk.
-\todo{Need to update plot descriptions and scores for runs with updated yields.}
 
@@
 The shift in the skewness and peak of the MDF from the inner to the outer Galaxy is unaffected by the choice of SFH.
-% The two left-hand columns show MDFs from models with different SFHs which assume the same DTD (exponential with $\tau=1.5$ Gyr).
-For comparison, the APOGEE MDFs are binned similarly and presented in the center column of Figure \ref{fig:feh-df-comparison}.
-The two right-hand columns show MDFs from models with
 
@@
 The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of explosions occurring within 1 Gyr in the former but only $\sim 30\%$ in the latter.
-% Nevertheless, while the former DTD produces a slightly narrower MDF in the inner Galaxy than the latter, the magnitude of this difference is much smaller than other factors.
 However, the effect on the MDF is interestingly small given this difference.
@@
 
-% The choice of DTD and SFH has a larger effect on the inner regions of the Galaxy than the outer.
-Inner regions have a higher SFR and more stars are formed at early times than late, so differences in the SN Ia rate have a more pronounced effect on the MDF.
-For all SFHs except two-infall, the outer Galaxy has a longer SFR timescale than the inner Galaxy, so the MDF in the outer Galaxy is relatively unaffected by the fraction of prompt SNe Ia.
 The inner Galaxy MDF is more sensitive to the choice of DTD than the outer Galaxy.
@@
 The distribution of [O/Fe] serves as a record of the relative rates of SNe Ia and CCSNe.
-As such, its shape is greatly affected by both the SFH and DTD.
+As such, its shape is affected by both the SFH and DTD.
 Figure \ref{fig:ofe-df-sfh} shows the distribution of [O/Fe] across the disk for the four model SFHs compared to the distributions measured by APOGEE.
@@
 
-The two-infall SFH produces \textit{three} distinct modes at ${\rm [O/Fe]}\approx 0.0$, $0.2$, and $0.4$.
+The two-infall SFH produces \textit{three} distinct modes at ${\rm [O/Fe]}\approx -0.05$, $0.15$, and $0.4$.
 At small $R_{\rm gal}$ and with increasing $|z|$, the low-$\alpha$ peak decreases in prominence as the high-$\alpha$ peak increases, but the intermediate peak is a striking feature at all latitudes that does not align with observations.
-In the APOGEE data, the high-$\alpha$ peak is at ${\rm [O/Fe]}\approx+0.3$, roughly halfway between the intermediate and high-$\alpha$ peaks produced by the two-infall model.
+In the APOGEE data, the high-$\alpha$ peak is at ${\rm [O/Fe]}\approx0.3$, roughly halfway between the intermediate and high-$\alpha$ peaks produced by the two-infall model.
 However, the model high-$\alpha$ sequence does match the observed trends with $R_{\rm gal}$ and $|z|$ much better than the early-burst models.
@@
 The most obvious effect of the DTD is to shift the mode of the high-$\alpha$ sequence.
-The two-population DTD, which has the most prompt SNe Ia, places the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx 0.2$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.2$ dex higher at ${\rm [O/Fe]}\approx0.4$.
+The two-population DTD, which has the most prompt SNe Ia, places the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx 0.15$, while the triple-system DTD, which has the fewest prompt SNe Ia, places it $\sim0.25$ dex higher at ${\rm [O/Fe]}\approx0.4$.
 The plateau ($W=1$ Gyr) DTD places the higher peak at ${\rm [O/Fe]}\approx0.35$, close to where it appears in the APOGEE distributions.
-However, the distance {\it between} the peaks of the APOGEE distributions is only $\approx0.2$ dex, since the observed low-$\alpha$ sequence sits at ${\rm [O/Fe]}\approx0.1$.
+However, the distance {\it between} the peaks of the APOGEE distributions is only $\sim0.2$ dex, since the observed low-$\alpha$ sequence sits at ${\rm [O/Fe]}\approx0.1$.
 This spacing is best replicated by the power-law ($\alpha=-1.1$) DTD, even though both peaks sit $\sim0.1$ dex too low and the distributions are narrower than observed.
+
 In general, models with fewer prompt SNe Ia populate the high-$\alpha$ sequence with more stars because the chemical evolution track spends more time in the high-$\alpha$ regime.
-
-% [Talk about scores]
+This qualitatively agrees with the isolated and cosmological simulations of \citet{Poulhazan2018-PrecisionPollution}, who find that DTDs with a significant prompt component produce narrower [O/Fe] distributions and a higher average [O/Fe].
+
 We again compute the KL divergence (Equation \ref{eq:kl-divergence}) to quantify the agreement between the [O/Fe] DFs of our models and APOGEE.
 We calculate a score for each model as described in Section \ref{sec:feh-df}.
-% The best-scoring model uses the two-infall SFH with the plateau ($W=0.3$ Gyr) DTD, although both plateau and exponential DTDs as well as the triple-system DTD score well when combined with certain SFHs.
-The late-burst SFH generally produces [O/Fe] DFs that score poorly compared to other models.
-\todo{Elaborate on the model scores a bit more}.
 The best-scoring model combines the inside-out SFH with the triple-system DTD, and the plateau ($W=1$ Gyr) and exponential ($\tau=3$ Gyr) DTDs score well when combined with either the inside-out or late-burst SFHs.
@@
 Surprisingly, the early-burst SFH scores quite poorly for all DTD models, despite the fact that it produces the most distinct high- and low-$\alpha$ sequences.
-We discuss this further in Section \ref{sec:discussion}.
+We discuss this further in Section \ref{sec:discussion-scores}.
 
@@
 Each panel contains stars within the Galactic region defined by $7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc.
-    % The $|z|$-distributions of the model stellar populations are re-sampled to match the vertical distribution of the APOGEE sample, and \num{20000} stellar populations are drawn from the adjusted distribution in each panel.
-The maximum of each distribution is normalized to 1 and the vertical scale is consistent across all panels.
-    For each distribution, \num{20000} stellar populations are re-sampled from the model output to match the $|z|$ distribution of the APOGEE sample.
+For each distribution, \num{100000} stellar populations are re-sampled from the model output to match the $|z|$ distribution of the APOGEE sample.
     \textit{Top row:} results from five multi-zone models which assume the late-bust SFH but different DTDs.
@@
 
-% [Intro, connect to previous section]. 
-The [O/Fe] distributions from APOGEE in Section \ref{sec:ofe-df}
-% (right-hand panels of Figures \ref{fig:ofe-df-sfh} and \ref{fig:ofe-df-dtd}) 
-show two distinct peaks whose relative prominence varies with $R_{\rm gal}$ and $|z|$ \citep[see also Figure 4 of][]{Hayden2015-ChemicalCartography}.
+The [O/Fe] distributions from APOGEE in Section \ref{sec:ofe-df} show two distinct peaks whose relative prominence varies with $R_{\rm gal}$ and $|z|$ \citep[see also Figure 4 of][]{Hayden2015-ChemicalCartography}.
 A crucial feature of this bimodality, which is not apparent in the analysis of the previous section, is the presence of both sequences at fixed [Fe/H].
@@
 To better approximate the APOGEE selection function, we re-sample our model stellar populations so the $|z|$ distribution closely matches that of APOGEE in the solar neighborhood.
-% For most of our models, the low-$\alpha$ peak is the more prominent of the two, so by performing this resampling we enhance strength of the bimodality.
-However, for some models the high-$\alpha$ peak is the strongest, and the re-sampling process de-emphasizes the low-$\alpha$ peak below the prominence threshold (e.g., panel f of Figure \ref{fig:ofe-bimodality}).
-[Explain why this is ok]
-Five of these eight DTDs (four of the five shown, plus the exponential form with $\tau=3$ Gyr) exceed our prominence threshold in the low-[Fe/H] bin, while both power-law DTDs and the plateau ($W=0.3$ Gyr) model do not.
-Panel (b) shows that the power-law ($\alpha=-1.1$) DTD produces a marginal high-$\alpha$ peak, although it does not meet the prominence threshold because it is too close to the low-$\alpha$ peak.
+Six of the eight DTDs (all except the two-infall and $\alpha=-1.4$ power-law DTDs) exceed our prominence threshold in the low-[Fe/H] bin.
+Panel (a) shows that the two-infall DTD produces a marginal low-$\alpha$ peak, although it does not meet the prominence threshold.
 In general, DTDs with fewer prompt SNe Ia produce a high-$\alpha$ peak which is more prominent and at a higher [O/Fe], as was the case with the [O/Fe] distributions in Section \ref{sec:ofe-df}.
@@
 Panels (f)--(i) in the bottom row of Figure \ref{fig:ofe-bimodality} illustrate the effect of the SFH on the [O/Fe] bimodality.
-The inside-out SFH does not produce a bimodal distribution for any of our DTDs.
+The inside-out SFH does not produce a bimodal distribution for most of our DTDs (the exception is the $W=1$ Gyr plateau DTD, which produces a much smaller trough than observed).
 On the other hand, the early-burst SFH {\it always} produces a bimodal distribution in the high-[Fe/H] bin regardless of the assumed DTD, but not in the low-[Fe/H] bin (the small low-$\alpha$ peak falls below our prominence threshold).
-For models with the late-burst and two-infall SFHs, the bimodality is variable depending on the DTD: those with longer median delay times (e.g., exponential, plateau, or triple-system) generally produce a bimodal distribution in the low-[Fe/H] bin, while the power-law DTDs do not.
+For models with the late-burst and two-infall SFHs, the bimodality is variable depending on the DTD: those with longer median delay times (e.g., exponential, plateau, or triple-system) generally produce a bimodal distribution in the low-[Fe/H] bin, while the two DTDs with the most prompt SNe Ia do not.
 
 One major problem in all of our models is the presence of the \aFe bimodality across only a narrow range of [Fe/H].
-% in all of our models the breadth of the $\alpha$-bimodality across [Fe/H] space. 
-% In APOGEE, both bins in [Fe/H] show a clearly bimodal distribution of [O/Fe]. 
 Even our most successful models can produce a bimodal [O/Fe] distribution in only one bin: the high-[Fe/H] bin for the early-burst SFH, and the low-[Fe/H] bin for the late-burst and two-infall SFHs.
@@
 The failure of these models to fully reproduce the bimodality across the whole range of [Fe/H] was noted by \citetalias{Johnson2021-Migration}, and the problem persists for each model we consider here.
-% indicates that our picture of the formation of the $\alpha$-bimodality is still incomplete.
 
@@
 We compare our model outputs to the observed distributions from APOGEE across the Milky Way disk.
-% \todo{Subsection introduction.}
-% Section \ref{sec:onezone-results} and specifically Figures \ref{fig:onezone-threepanel} and \ref{fig:onezone-twopanel} illustrated the effect of the DTDs and parameters on [O/Fe]--[Fe/H] tracks in idealized one-zone models.
 
@@
 Much of the scatter in [Fe/H] in a given Galactic region can be attributed to radial migration \citep{Edvardsson1993-ChemicalEvolution}.
-% This illustrates how radial migration can explain much of the spread in [Fe/H] which is observed in a given Galactocentric region.
 
@@
 The stellar abundance distribution at both low- and high-[O/Fe] is composed of stars with a wide range of birth $R_{\rm gal}$.
-% In particular, we observe a high-[O/Fe] ``ridge'' on the high-metallicity side of the ISM track, which is composed of stellar populations from the inner Galaxy.
 
@@
 Here, the significant infall of pristine gas at $t=4$ Gyr leads to rapid dilution of the metallicity of the ISM, followed by a large burst in the SFR, which raises [O/Fe] by $\sim 0.2$ dex.
-% The track begins to ``turn over'' back to lower [O/Fe] due to the delayed response of SNe Ia. 
 We observe a ridge in the stellar abundance distribution at the turn-over point (${\rm [O/Fe]}\approx0.15$) associated with SNe Ia whose progenitors formed during the burst.
 This ridge roughly coincides with the upper limit of the APOGEE distribution near the midplane.
-The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx-0.05$, which reflects the population-averaged yield ratio of [O/Fe].
+The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx-0.1$, which reflects the population-averaged yield ratio of [O/Fe].
 
@@
 We choose the inside-out SFH for this figure because it predicts monotonically-decreasing abundance ratios, making comparisons between the different DTDs relatively straightforward.
-% We note that in this model, both the low- and high-$\alpha$ sequences are composed of stars with a wide range of birth $R_{\rm gal}$. 
 The models are arranged according to the median delay time of the DTD, increasing across the panel columns from left to right.
 
-% Results for the two-population and power-law ($\alpha=-1.1$) DTDs, with a large fraction of prompt SNe Ia, are presented in the first and second columns, respectively. 
 The two-population and power-law ($\alpha=-1.1$) DTDs, which have a large fraction of prompt SNe Ia, produce stellar abundance distributions that are reasonably well-aligned with the APOGEE contours at low $|z|$, but they entirely miss the observed high-$\alpha$ sequence at large $|z|$.
 The ISM abundance tracks for the 8 kpc zone do not pass through the APOGEE 30\% contour at $|z|=1-2$ kpc.
-For both DTDs, the high-[O/Fe] knee is located below the left-most bound of the plot, but we observe a second knee at ${\rm [O/Fe]}\approx0.2$ where the abundance tracks turn downward once more.
+For both DTDs, the high-[O/Fe] knee is located below the left-most bound of the plot, but we observe a second knee at ${\rm [O/Fe]}\approx0.15$ where the abundance tracks turn downward once more.
 As discussed in Section \ref{sec:onezone-results}, the second knee is most prominent in the model with the two-population DTD because of its long exponential tail.
-% For these models, the simulated stellar abundances are reasonably well-aligned with the APOGEE contours at low $|z|$ (bottom panels), but they entirely miss the observed high-$\alpha$ sequence at high $|z|$ (top panels).
 
@@
 
-\todo{Which models score best.}
+The best-scoring model combines the triple-system DTD with the inside-out SFH.
+The two other DTDs with the longest median delay times, plateau ($W=1$ Gyr) and exponential ($\tau=3$ Gyr), also score quite well.
+As with the [O/Fe] DFs, the inside-out and late-burst SFH models score similarly across all DTDs in the [O/Fe]--[Fe/H] plane.
+The early-burst SFH models score the worst out of all the SFHs, likely due to the long ``tail'' in the distribution down to low [Fe/H] which is not seen in the APOGEE data.
 
@@
 
-% [Subsection introduction]
 As demonstrated by our one-zone models in Section \ref{sec:onezone-results}, models that produce similar tracks in abundance space can be distinguished by the rate of their abundance evolution.
 We therefore expect the age--[O/Fe] relation to be a useful diagnostic.
-% We demonstrated in Section \ref{sec:ofe-df} that the DTD affects the final [O/Fe] distribution, so naturally it should have an effect on the evolution of [O/Fe] with age as well.
-We compare our model stellar age--[O/Fe] relations with age estimates for APOGEE stars from the variational encoder-decoder network of \citetalias{Leung2023-Ages}.
 Figure \ref{fig:age-ofe-sfh} shows the stellar age and [O/Fe] distributions in the solar neighborhood for each of our four SFHs.
@@
 We compare these predictions against ages estimated with \citetalias{Leung2023-Ages}'s variational encoder-decoder algorithm.
-% We include age data from \citetalias{Leung2023-Ages} for qualitative comparison, though 
 We caution against drawing strong conclusions from this comparison, because we do not correct for selection effects or systematic errors in the age determination.
 
-The inside-out and late-burst models show fair agreement with the data at high [O/Fe], although both show a $\sim2$ Gyr offset at older ages.
+The inside-out and late-burst models show fair agreement with the data at high [O/Fe], although both show a $\sim2$ Gyr offset.
 One could shift the ramp-up in star formation to slightly later times or simply run the model for a shorter amount of time to close this gap.
+Although it is a visually striking difference, the age at the high-[O/Fe] knee is not a good diagnostic for the SFH after factoring in the age uncertainties.
 As in the data, the trend in the median age with decreasing [O/Fe] decreases monotonically in the inside-out model.
 The late-burst model, however, shows a bump in the relation at a lookback time of $\sim2$ Gyr which is not seen in the data, as noted by \citetalias{Johnson2021-Migration}.
-% Neither model produces a significant amount of stars below solar [O/Fe], in contrast to the data.
 
@@
 The rapid rise in the SFE at early times delays the descent to lower [O/Fe] values and produces a clump of low-metallicity, high-[O/Fe] stars at an age of $\sim10$ Gyr.
-% The early-burst model produces a sharp transition between a linear relationship between [O/Fe] and age for stars older than $\sim5$ Gyr and a flat relationship for the younger stars, and it too misses the lowest [O/Fe] bin in the data.
-Lastly, the two-infall SFH produces the closest overall match to the data.
+Lastly, the two-infall SFH produces a fair match to the data.
 Stars with ${\rm [O/Fe]}\gtrsim 0.25$ were produced in the first infall, while the second infall produces a clump of stars with similar metallicity, ages of $\sim8$ Gyr, and ${\rm [O/Fe]}\approx0.2$.
@@
 The subsequent increase in [O/Fe] does not produce as strong of a bump as the late-burst SFH, because it occurs much earlier and is therefore narrower in log(age).
-% which is not seen in any of the other models.
-The two-infall model is the only one which plateaus at sub-solar [O/Fe] for the youngest stars, leading to a very good match to the observed data at low [O/Fe].
+However, the two-infall SFH produces [O/Fe] abundances for the youngest stars which are roughly 0.1 dex lower than the other models.
+
+In contrast to \citetalias{Johnson2021-Migration}, none of our models predict a population of young, $\alpha$-enhanced stars in the solar neighborhood.
+These stars have been observed in APOGEE \citep[e.g.,][]{Martig2016-CNAbundances,SilvaAguirre2018-YoungAlphaEnhanced} and many are likely old systems masquerading as young stars due to mass transfer or a merger \citep[e.g.,][]{Yong2016-YoungAlphaRich}, but it is not known whether some fraction are truly intrinsically young \citep{HekkerJohnson2019-YoungAlphaRich}.
+In \citetalias{Johnson2021-Migration}, these young, $\alpha$-enhanced stars are the result of a highly variable SN Ia rate in the outer Galaxy.
+The SN Ia progenitors migrate before they are able to enrich their birth annulus, so the subsequent stellar populations are depleted in Fe.
+Two differences in the migration scheme explain the lack of these stars in our own models: first, we adopt a time-dependence for radial migration of $\Delta t^{1/3}$, which is slower than the diffusion scheme ($\Delta t^{1/2}$) of \citetalias{Johnson2021-Migration}.
+Second, our migration method is designed to produce smooth abundance distributions, whereas the method of \citetalias{Johnson2021-Migration} can assign identical migration patterns to many stellar populations in sparsely-populated regions of the Galaxy, potentially removing many SN Ia progenitors from a given zone simultaneously (for more discussion, see Appendix \ref{app:migration}).
+This update to the model is consistent with \citeauthor{Grisoni2024-YoungAlphaRich}'s \citeyearpar{Grisoni2024-YoungAlphaRich} finding that young $\alpha$-rich stars have similar occurrence rates across the disk, which supports a stellar, as opposed to Galactic, origin.
 
@@
 Figure \ref{fig:age-ofe-dtd} shows the predicted age--[O/Fe] relation for five of our DTDs.
-All models were run with the early-burst SFH, because it predicts the clearest separation between the high- and low-$\alpha$ sequences (see Figure \ref{fig:age-ofe-sfh}).
+All models were run with the early-burst SFH because it predicts the clearest separation between the high- and low-$\alpha$ sequences (see Figure \ref{fig:age-ofe-sfh}).
 Similar to Figure \ref{fig:ofe-feh-dtd}, models are arranged from left to right by increasing median SN Ia delay time.
@@
 As we have seen in previous figures, the range in [O/Fe] produced by DTD models with many prompt SNe Ia is much smaller than the extended DTDs.
-At high $|z|$ (top row), the observed range of [O/Fe] is larger all of our models.
-While the plateau ($W=1$ Gyr) and triple-system models come close, the other three fall short of the observed range in [O/Fe], but closely match the median age--[O/Fe] relation.
+At high $|z|$ (top row), the observed range of [O/Fe] is larger than what is produced by most of our models.
+While the plateau ($W=1$ Gyr) and triple-system models come close, the other three fall short of the observed range in [O/Fe], but still closely match the median age--[O/Fe] relation.
 There is a slight reversal in the observed trend for the stars with the highest [O/Fe]: the $0.45\leq{\rm [O/Fe]}<0.5$ bin has a slightly \textit{lower} median age than the $0.3\leq{\rm [O/Fe]}<0.35$ bin at high $|z|$ in the \citetalias{Leung2023-Ages} sample, a small effect but one which is not predicted by any of our models.
 
-Moving to stars at low $|z|$, the plateau ($W=1$ Gyr) and triple-system DTDs over-produce stars at the old, high-$\alpha$ end of the distribution, while also diverging significantly from the observed sequence near solar [O/Fe].
+Moving to stars at low $|z|$, the plateau ($W=1$ Gyr) and triple-system DTDs over-produce stars at the old, high-$\alpha$ end of the distribution, while also diverging somewhat from the observed sequence near solar [O/Fe].
 The exponential ($\tau=1.5$ Gyr) DTD comes closest to reproducing the observed range in [O/Fe], while the two DTDs with the shortest median delay time once again produce a smaller range of [O/Fe] than observed.
@@
 This difference arises because the exponential DTD is most dominant at intermediate delay times ($t\sim 1-3$ Gyr) but falls off much faster than the other models at long delay times, so [O/Fe] is close to constant for lookback times $\lesssim 5$ Gyr.
-Overall, the exponential ($\tau=1.5$ Gyr) DTD most closely matches the data for stars with $0\leq|z|<1$ kpc.
+Overall, the exponential ($\tau=1.5$ Gyr) DTD most closely matches the data for stars with $0\leq|z|<0.5$ kpc.
 
@@
 As shown in Figures \ref{fig:age-ofe-sfh} and \ref{fig:age-ofe-dtd}, in each Galactic region we sort the model outputs and data into bins of [O/Fe] with a width of 0.05 dex.
-We define the RMS median age difference for the region as
+We define the root mean square (RMS) median age difference for the region as
 \begin{equation}
@@
 where $\Delta\tau_k=\rm{med}(\tau_{\rm \vice})-\rm{med}(\tau_{\rm L23})$ is the difference between the mass-weighted median age in \vice and the median stellar age from \citetalias{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citetalias{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
+If a bin has no modeled or observed stars, we do not calculate $\Delta \tau_k$ for that bin.
 As before, the score for the model as a whole is the average of $\Delta \tau_{\rm RMS}$ across all regions, weighted by the number of stars with age measurements in each region.
-We discuss the quantitative scores in Section \ref{sec:discussion} below.
-
-% The best, lowest-scoring model in the age--[O/Fe] plane
+
+The best (lowest-scoring) model in the age--[O/Fe] plane is the triple-system DTD with the two-infall SFH.
+Models which score almost as well are the plateau ($W=1$ Gyr) and triple-system DTDs with either the early-burst or two-infall SFH.
+Visually, the non-monotonic bump in the age--[O/Fe] relation produced by the late-burst SFH does not match the observed distribution, but it actually {\it improves} $\Delta \tau_{\rm RMS}$ by lowering the median age of stars in the low-[O/Fe] bins.
+If the shape of the distribution is taken into account, the late-burst SFH produces the worst match to the data.
+We discuss the quantitative scores in further Section \ref{sec:discussion-scores} below.
 
@@
 
+\subsection{Quantitative Comparisons}
+\label{sec:discussion-scores}
+
 \variable{output/summary_table.tex}
@@
 In Section \ref{sec:multizone-results}, we focused on a representative subset of our 32 multi-zone models (four SFHs and eight DTDs).
-% While we focused our attention on results in the solar annulus (for which we still have the best data), we have model outputs which span the entire disk out to 20 kpc.
-In order to identify trends among our many models, it will be useful to have some semi-quantitative way to compare their outputs to APOGEE data across the disk.
 Here, we compare all of our model outputs to APOGEE across five observables: the MDF, [O/Fe] DF, [O/Fe]--[Fe/H] plane, age--[O/Fe] plane, and [O/Fe] bimodality.
@@
 We use these scores to indicate combinations of SFH and DTD that are favorable or unfavorable in certain regimes, but we do {\it not} fit our models to the data due to computational expense.
-To avoid drawing strong conclusions from small numerical differences in scores, 
-% in the column corresponding to a particular diagnostic 
-we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom third out of all models, respectively.
-
-%Much of the variation between models can be explained by the choice of SFH.
-In general, the two-infall models rank the highest across all diagnostics, while the late-burst models score poorly to the rest.
-If we remove the two-infall models altogether due to their dominance in the scoring system, our results do not qualitatively change.
-In the age--[O/Fe] plane, the early-burst and two-infall models, score much better than the others.
-The SFHs rank differently in the bimodality test, where the early-burst SFH is able to produce a bimodal [O/Fe] distribution for all DTDs (see discussion in Section \ref{sec:bimodality}).
+To avoid drawing strong conclusions from small numerical differences in scores, we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom third out of all models, respectively.
+
 Some of the variation between models can be explained by the choice of SFH.
 The two-infall models tend to out-perform the others for the MDFs, while the late-burst models score poorly, especially with the prompt DTDs.
-The early-burst models consistently have the lowest scores for the [O/Fe] DF and [O/Fe]--[Fe/H] distribution, but are able to produce a bimodal [O/Fe] distribution with every \todo{(check 3 Gyr exponential)} DTD.
-The late-burst and two-infall SFHs also produce a bimodal [O/Fe] disbtribution with all DTDs but those with the highest prompt fraction, while the inside-out models never produce bimodality \todo{(check 1.5 Gyr exponential)}.
-The inside-out models also tend score poorly in the age--[O/Fe] plane.
-\todo{Visually the late-burst SFH should score the lowest here, need to double-check.}
+The early-burst models consistently have the lowest scores for the [O/Fe] DF and [O/Fe]--[Fe/H] distribution, but are able to produce a bimodal [O/Fe] distribution with every DTD (see discussion in Section \ref{sec:bimodality}).
+The late-burst and two-infall SFHs also produce a bimodal [O/Fe] distribution with all DTDs except those with the highest prompt fraction, while the inside-out models never produce bimodality.
+The inside-out models also tend score poorly in the age--[O/Fe] plane, while the early-burst models tend to score well, although as discussed in Section \ref{sec:age-ofe}, adjusting the time of the peak SFR or running the models for a shorter period of time would affect the level of agreement in the high-[O/Fe] bins.
 
@@
 The KL divergence test heavily penalizes models with a high density in a region where the observations have little, as is the case for the high-$\alpha$ sequence in the outer Galaxy and close to the midplane (see Figure \ref{fig:ofe-df-sfh}).
+This similarly explains the early-burst models' poor performance in the [O/Fe]--[Fe/H] plane.
 An iteration of this SFH where the early burst predominantly affects the inner galaxy is probably more accurate and might have more success at reproducing the [O/Fe] DF across the disk.
 
-% The two-infall models are penalized by the KL divergence tests for producing abundance distributions which are not well aligned with the data (see the bottom-right panel of Figure \ref{fig:ofe-feh-sfh}).
-With a slightly lower $y_{\rm Fe}^{\rm Ia}$, the abundance tracks do not dip so far below ${\rm [O/Fe]}=0$, and the two-infall models out-perform every other SFH.
-
-%The choice of DTD has a clear effect on the model scores, and this effect is similar across the observables.
-The models which perform the best (most \yes's and fewest \no's) are those with the exponential and plateau DTDs.
-It is interesting that the best-scoring DTD overall, the exponential DTD with $\tau=1.5$ Gyr, is intermediate among all our DTDs in terms of the number of prompt SNe Ia and median delay time but has the {\it lowest} rate at very long delay times ($\sim10$ Gyr).
-Models with a large fraction of prompt SNe Ia, such as the power-law and two-population DTDs, fare quite poorly, with the steepest power-law ($\alpha=-1.4$) ending up in the bottom third across the board for most of our SFHs.
-The choice of DTD has a clear effect on the model scores, and this effect is similar for every observable.
-The models which perform the best (most \yes's and fewest \no's) are the most extended DTDs with the fewest prompt SNe Ia: both power-law DTDs, the exponential DTD with $\tau=3$ Gyr, and the triple-system DTD.
+The choice of DTD has a clear effect on the model scores, and this effect is similar for most of the observables.
+The models which perform the best (most \yes's and fewest \no's) are the most extended DTDs with the fewest prompt SNe Ia: both plateau DTDs, the exponential DTD with $\tau=3$ Gyr, and the triple-system DTD.
 The latter actually produces the highest scores for each observable, but the plateau DTD with $W=1$ Gyr is the most successful across all SFHs; both models have some of the longest median delay times.
 Models with a large fraction of prompt SNe Ia, such as the power-law and two-population DTDs, fare quite poorly, with the steepest power-law ($\alpha=-1.4$) and two-population DTDs ending up in the bottom third across the board for most of our SFHs.
-The fiducial power-law ($\alpha-1.1$) does slightly better, but still compares poorly to the more extended DTDs.
+The fiducial power-law ($\alpha=-1.1$) does slightly better, but still compares poorly to the more extended DTDs.
 
 Each DTD tends to score similarly across the board, but there are some combinations of SFH and DTD that buck the general trend.
-For example, the two-population DTD with the early-burst SFH produces an MDF which scores quite well.
-\todo{Explain why.} The shorter exponential DTD with $\tau=1.5$ Gyr has generally middling performance, but does a notably poorer job when combined with the early-burst SFH.
-\todo{Explain why.}
-
-\todo{Discuss how the age at the knee, given our age uncertainties, is not a great diagnostic.}
-
-%[Old text] While certain DTDs tend to score better than others overall, there is no single DTD which always produces optimal agreement with the data across all observables and for all SFHs.
-If an inside-out or late-burst SFH is chosen, the exponential DTDs score the highest across all observables.
-However, the picture becomes less clear when looking at the other SFHs.
-If the early-burst SFH is chosen, the DTDs with a large prompt fraction (power-law and two-population) produce the best agreement with the APOGEE MDFs but the {\it worst} agreement with the other observables.
-For the two-infall SFH, any DTD other than the power-law and two-population scores well, but the best-scoring DTD varies between observables.
-In general, too many prompt SNe Ia worsens agreement with observations across all our SFHs, while too few prompt SNe Ia can also worsen agreement for some SFHs and observables.
-
-The power-law ($\alpha=-1.1$) DTD has the strongest observational motivation but poorly reproduces the disk abundance distributions.
-This can be mitigated somewhat with a longer minimum delay time, which has a similar effect on chemical evolution tracks as the addition of an initial plateau in the DTD (see discussion in Section \ref{sec:onezone-results}).
-Even so, it is clear that the high fraction of prompt SNe Ia in the DTD of, e.g., \citet{MaozMannucci2012-SNeIaReview} is at odds with Galactic chemical abundance measurements.
-
-Measurements of the cosmic SN Ia rate become considerably uncertain at $z\gtrsim1$ \citep[see, e.g.,][]{Palicio2024-CosmicSNIaRate}.
-Additionally, measurements of galactic or cosmic SFHs typically provide constraints for the DTD in coarse age bins, with especially large uncertainties in the youngest bins \citep[e.g.,][]{MaozMannucci2012-SNeIaReview},
-%, and it is difficult to constrain the SFH of individual galaxies below [number] [cite],
-so constraints on the DTD from external galaxies should be more sensitive to the rates at long delay times.
-On the other hand, our results demonstrate that the high-$\alpha$ sequence in GCE models is highly sensitive to the DTD at short delay times.
-
-% [Discuss \citet{Palicio2024-CosmicSNIaRate}]
-% \citet{Palicio2024-CosmicSNIaRate} predict the cosmic SN Ia rate from a variety of DTDs and cosmic star formation rates (CSFRs) and fit to observations.
-They find that, depending on the choice of CSFR, the DTDs of \citet{MatteucciRecchi2001-SNIaTimescale}, \citet{Mannucci2006-TwoPopulations}, \citet{Totani2008-DTD}, and the WIDE DD model of \citet{Greggio2005-AnalyticalRates} can all produce good fits to the observed cosmic SN Ia rate.
-This study provides a useful basis for comparison because the first and last of these DTDs are similar to our exponential ($\tau=1.5$ Gyr) and plateau ($W=1$ Gyr) DTDs, respectively (see Appendix \ref{app:analytic-dtds} for more discussion); the \citet{Mannucci2006-TwoPopulations} is our two-population DTD; and the \citet{Totani2008-DTD} is a $t^{-1}$ power-law with a minimum delay $t_D=100$ Myr.
-It is noteworthy that the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale} best fits the majority of CSFRs in \citet{Palicio2024-CosmicSNIaRate}, and our similar exponential ($\tau=1.5$ Gyr) DTD {\it also} performs best across all our SFHs.
-\todo{Intro sentence}.
-\citet{Palicio2024-CosmicSNIaRate} fit combinations of cosmic star formation rates (CSFRs) and DTDs, many of which are similar to the forms in this paper, to the observed cosmic SN Ia rate.
-Notably, the DTD that best fit the majority of their CSFRs was the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale}, which is similar to the exponential form with $\tau=1.5$ Gyr (see Appendix \ref{app:analytic-dtds} for more discussion).
-\citet{Palicio2024-CosmicSNIaRate} are able to exclude DTDs with a very high or very low fraction of prompt SNe Ia, but a number of their DTDs could produce a convincing fit to the observed rates with the right CSFR.
-Despite a very different methodology, their results mirror ours: that many forms for the DTD can produce a reasonable fit to the data when combined with the right SFH.
-Our findings are also in qualitative agreement with the isolated and cosmological simulations of \citet{Poulhazan2018-PrecisionPollution}, namely that DTDs with a significant prompt component produce narrower [O/Fe] distributions and a higher average [O/Fe].
-% In both isolated and cosmological simulations, \citet{Poulhazan2018-PrecisionPollution} found that DTDs with a significant prompt component (power-law and two-population) produced the highest average [O/Fe] and the narrowest [O/Fe] distributions.
-Conversely, their models with essentially 0 prompt SNe Ia produced a lower average stellar [O/Fe] ratio at late times and a broader distribution of [O/Fe].
-Their simulations have an SFR which features an early ($<1$ Gyr) burst followed by a roughly exponential decline, qualitatively similar to our early-burst model but with the peak of star formation occuring $\sim3$ Gyr earlier.
-We note that their simulations were not designed to reproduce a Milky Way-like galaxy; as such, their [O/Fe] distributions peak around $\sim0.45$ which is higher than the APOGEE high-$\alpha$ sequence.
-Nevertheless, our study reproduces their finding that a DTD with more prompt SNe Ia will produce a narrower distribution of [O/Fe].
-One exception to this is the exponential DTD, which has a marginally narrower distribution than the power-law DTD close to the midplane [numbers here] but a more prominent high-$\alpha$ tail.
-This is likely a consequence of the fact that the exponential DTD has a much lower SN Ia rate at late times ($\sim10$ Gyr) than other models [expand on this].
-
-% Is the MW DTD the same as elsewhere?
-Our finding that the $t^{-1}$ power-law DTD poorly reproduces observed abundances could suggest that the Milky Way obeys a different DTD than other galaxies.
-This would not be too far beyond \citet{Maoz2017-CosmicDTD}'s finding that field galaxies and galaxy clusters have a different DTD slope.
-On the other hand, \citet{Walcher2016-SelfSimilarity} argue that the similarity of the age--\aFe relation between solar neighborhood stars and nearby elliptical galaxies is evidence for a universal DTD.
-A physical mechanism would be needed to produce a different slope or form for the DTD in different environments, such as a metallicity dependence in the fraction of close binaries \citep[e.g.,][]{Moe2019-CloseBinaryFraction}.
+For example, the two-population DTD with the early-burst SFH produces an MDF which scores relatively well.
+The early-burst models generally produce MDFs in the \meh category, so a small increase in the numerical score bumps it up to \yes; this indicates the insensitivity of the MDF to the DTD in general.
+The exponential DTD with $\tau=1.5$ Gyr has generally middling performance, but does a notably poorer job when combined with the early-burst SFH, a result of the generally poor performance of that SFH.
+
+The plateau DTD with $W=1$ Gyr, our most successful model overall, poorly reproduces the MDF with the late-burst SFH, while the exponential DTD with $\tau=3$ Gyr produces better agreement with the data for that SFH.
+Finally, the inside-out SFH generally does not reproduce the APOGEE age--[O/Fe] relation well, but it scores better than average when combined with the triple-system DTD.
 
@@
 
-\todo{Briefly discuss radial migration trends, refer back to J21. Future work on implications of radial migration on the disk abundance structure.}
-
 \subsection{The Two-Infall SFH}
@@
 In contrast to previous studies of the two-infall model \citep[e.g.,][]{Chiappini1997-TwoInfall,Matteucci2009-DTDModels,Spitoni2021-TwoInfall}, they do incorporate gas outflows, making their models especially well-suited to compare to ours.
-\citet{Palicio2023-AnalyticDTD} achieve a good fit with solar neighborhood data for analytic DTDs for both SD and DD progenitors, which are approximated by our exponential ($\tau=1.5$ Gyr) and plateau ($W=1$ Gyr) models, respectively.
+By modifying their yields, outflow mass-loading factor, and some of the parameters of their SFH, \citet{Palicio2023-AnalyticDTD} were able to achieve a good fit to solar neighborhood abundance data for both the SD and DD analytic DTDs, which are approximated by our exponential ($\tau=1.5$ Gyr) and plateau ($W=1$ Gyr) models, respectively.
+Our results and theirs highlight the need for independent constraints on the SFH to resolve degeneracies with the DTD.
 
@@
 
-\subsection{Radial Migration \& Bimodality}
-
-% One curious chemical feature of the Milky Way disk is the existence of two populations separated by their \aFe abundance ratios at similar metallicity \citep[e.g.,][]{Bensby2014-solarNeighborhoodAbundances}.
-
-% Taken from introduction
-The bimodal distribution of \aFe in stars with similar metallicities was first noted in the solar neighborhood \citep[e.g.,][]{Furhmann1998-NearbyStars} and later extended to the rest of the Milky Way disk \citep{Nidever2014-ChemicalEvolutionAPOGEE,Hayden2015-ChemicalCartography}.
-The ``high-$\alpha$'' population contains stars with low enrichment from SNe Ia, so their abundance ratios reflect that of almost pure CCSN enrichment; it is associated with the kinematically hot thick disk \citep{Bensby2003-AbundanceTrends}.
-The ``low-$\alpha$'' population is associated with the thin disk and contains stars with roughly solar $\alpha$-abundances.
-Various explanations of the \aFe bimodality have been proposed, including radial stellar mixing \citep{Schonrich2009-RadialMixing} and a bursty gas infall history \citep[e.g.,][]{Spitoni2021-TwoInfall}.
-% The origin of the \aFe bimodality is debated.
-\citet{Schonrich2009-RadialMixing} argue that it arises due to radial migration (churning) even with a smooth SFR.
-\citetalias{Johnson2021-Migration} use a smooth SFR and a prescription for radial migration but are unable to reproduce the bimodality.
-\citet{Spitoni2021-TwoInfall} (definitely earlier papers too) argue that two distinct infall episodes can explain the bimodality.
-What separates the two sequences is the ratio of CCSN to SN Ia enrichment, so the DTD ought to have some impact on the \aFe bimodality, perhaps even determining whether or not it exists.
-
-\citet{Mackereth2018-AlphaBimodality} find the appearance of a MW-like bimodality in the EAGLE simulations is rare, occurring in only $\sim5\%$ of their sample.
-
-% Taken from introduction
-% A complicating factor in observing and modeling the effects of the DTD is the migration of stars throughout the disk.
-\citet{SellwoodBinney2002-RadialMixing} first demonstrated that a transient spiral perturbation (or other potential feature; see [citations]) can cause resonant interactions which adjust stars' guiding center radii without leading to kinematic heating of the disk.
-Core-collapse SNe explode on timescales of a few Myr, before the progenitor has a chance to migrate far from its birth location.
-On the other hand, SNe Ia have a broad distribution of delay times and their progenitors can migrate great distances between birth and explosion.
-The consequence is that SNe Ia can enrich regions of the Galaxy far removed from regions which have experienced a high rate of star formation.
-Talk about \citet{Scannapieco2005-ChemicalEnrichment}.
-The first GCE model to incorporate radial mixing was developed by \citet{Schonrich2009-RadialMixing}, and subsequent studies have incorporated more comprehensive numerical treatments of radial migration and the effect of a central bar \citep[e.g.,][]{Minchev2013-ChemodynamicalEvolution}.
-% %In this paper, we follow the treatment by \citetalias{Johnson2021-Migration}, who [describe treatment].
-
-% \citet{Karapetyan2022-SNIaDistances} find a correlation between the SN Ia light curve decline rate, $\Delta m_{15}$, and the distance between the SN and the star-forming shock front of spiral arms.
-As this distance is expected to be an indicator of the age of the SN progenitor, such a correlation would suggest that the less-luminous, faster-declining SNe Ia come from an older progenitor population, which would be expected from progenitor models with sub-Chandrasekhar mass explosions.
-A similar study on the {\it radial} migration distance is probably impossible due to the challenges in estimating birth radii even in the Milky Way.
-It could be interesting to incorporate a SN Ia yield which varies with progenitor age into a GCE model.
-% [Are there analytic DTDs for a DD progenitor with sub-Chandra explosions?]
-
-% Something about \citetalias{Johnson2021-Migration} and \citet{Schonrich2009-RadialMixing}.
+\subsection{Extragalactic Constraints}
+
+The power-law ($\alpha=-1.1$) DTD has the strongest observational motivation but poorly reproduces the disk abundance distributions.
+This can be mitigated somewhat with a longer minimum delay time, which has a similar effect on chemical evolution tracks as the addition of an initial plateau in the DTD (see discussion in Section \ref{sec:onezone-results}).
+Even so, it is clear that the high fraction of prompt SNe Ia in extragalactic constraints on the DTD by, e.g., \citet{Maoz2017-CosmicDTD} is at odds with Galactic chemical abundance measurements.
+
+This tension could suggest that the Milky Way obeys a different DTD than other galaxies.
+This would not be too far beyond \citeauthor{Maoz2017-CosmicDTD}'s \citeyearpar{Maoz2017-CosmicDTD} finding that field galaxies and galaxy clusters have a different DTD slope.
+However, \citet{Walcher2016-SelfSimilarity} argue that the similarity of the age--\aFe relation between solar neighborhood stars and nearby elliptical galaxies is evidence for a universal DTD.
+A physical mechanism would be needed to produce a different slope or form for the DTD in different environments, such as a metallicity dependence in the fraction of close binaries \citep[e.g.,][]{Moe2019-CloseBinaryFraction}.
+
+On the other hand, the difference between constraints from GCE models and extragalactic surveys indicates that these types of studies are most sensitive to different regimes of the DTD.
+Our results demonstrate that the high-$\alpha$ sequence in GCE models is highly sensitive to the DTD at short delay times.
+Measurements of galactic or cosmic SFHs typically provide constraints for the DTD in coarse age bins, with especially large uncertainties in the youngest bins \citep[e.g.,][]{MaozMannucci2012-SNeIaReview}, and it is difficult to constrain the SFH of individual galaxies at long lookback times \citep{Conroy2013-PanchromaticSED}.
+Additionally, measurements of the cosmic SN Ia rate become considerably uncertain at $z\gtrsim1$ \citep[see, e.g.,][]{Palicio2024-CosmicSNIaRate}.
+As a result, constraints from external galaxies should be more sensitive to the DTD at long delay times.
+
+\citet{Palicio2024-CosmicSNIaRate} fit combinations of cosmic star formation rates (CSFRs) and DTDs, many of which are similar to the forms in this paper, to the observed cosmic SN Ia rate.
+Notably, the DTD that best fit the majority of their CSFRs was the single-degenerate DTD of \citet{MatteucciRecchi2001-SNIaTimescale}, which is similar to the exponential form with $\tau=1.5$ Gyr (see Appendix \ref{app:analytic-dtds} for more discussion).
+They were able to exclude DTDs with a very high or very low fraction of prompt SNe Ia, but a number of their DTDs could produce a convincing fit to the observed rates with the right CSFR.
+Despite a very different methodology, their results mirror ours: that many forms for the DTD can produce a reasonable fit to the data when combined with the right SFH.
 
@@
 For each DTD, we explored combinations with four different popular SFHs from the literature, which represent a broad range of behavior over the lifetime of the disk seen in many prior GCE models.
-% in combination with four different SFHs in multi-zone GCE models with radial migration. 
 We compared our model outputs to abundances from APOGEE and ages from \citetalias{Leung2023-Ages} for stars across the Milky Way disk.
@@
 
-% \todo{We don't have a good combination of SFH+DTD+yields+etc that can explain everything we observe about the Milky Way.
-Emphasize how comprehensive this was.
-We focus on the comparisons that are most interesting, but this is a very broad look at}
-
 \begin{itemize}
@@
 For the inside-out SFH, it is narrowly surpassed by the (similar) triple-system DTD.
-    % \item The exponential DTD with a timescale of $\tau=1.5$ Gyr is best able to reproduce the observed abundance patterns for all four SFHs.
 
@@
 This could be mitigated with a longer minimum delay time or the addition of an initial plateau in the DTD at short delay times.
-    % \item Our diagnostics consistently favor a DTD with a large fraction of delayed SNe Ia, such as the 3 Gyr exponential, 1 Gyr plateau, or triple system evolution models, over a DTD with a high number of prompt SNe Ia, such as the $t^{-1.4}$ power-law or two-population models.
-[Discuss the disconnect and/or complement with \citet{Maoz2017-CosmicDTD}, etc.; something about different timescales probed by volumetric surveys vs.
-us]
-
-    \item The SFH is the critical factor for producing a bimodal [O/Fe] distribution at fixed [Fe/H].
-On its own, the DTD cannot produce a bimodal [O/Fe] distribution that matches what is observed.
+
+    \item The SFH is the critical factor for producing a bimodal \aFe distribution at fixed [Fe/H].
+On its own, the DTD cannot produce a bimodal \aFe distribution that matches what is observed.
 However, it does affect the location and strength of the high-$\alpha$ sequence, potentially enhancing the \aFe bimodality resulting from the choice of SFH.
-Radial migration also does not predict the \aFe bimodality on its own, in agreement with \citetalias{Johnson2021-Migration} but in tension with \citep{Sharma2021-RadialMigration} and \citep{Chen2023-RadialMixingRedux}.
-
-    \item The MDF is more sensitive to the choice of SFH than the DTD.
-Overall trends in the MDF across the Galaxy are primarily driven by the assumed radial abundance gradient and stellar migration prescription, but it is more sensitive to the DTD in the inner Galaxy due to the more sharply declining SFH (see discussion in Section \ref{sec:feh-df}).
-
-    % \item The early-burst SFH is the only one which produced a bimodal distribution of [O/Fe] across the disk resembling APOGEE, from the models we investigate.
-[Add: summary of why everything else fails.]
+Radial migration also does not predict the \aFe bimodality on its own, in agreement with \citetalias{Johnson2021-Migration} but in tension with \citet{Sharma2021-RadialMigration} and \citet{Chen2023-RadialMixingRedux}.
 \end{itemize}
@@
 % Future work
+We found that the MDF is least able to provide constraints on the DTD.
+The MDF is more sensitive to the SFH, but overall trends across the Galaxy are primarily driven by the assumed radial abundance gradient and stellar migration prescription.
+However, the MDF is more sensitive to the DTD in the inner Galaxy due to the more sharply declining SFH (see discussion in Section \ref{sec:feh-df}), so improved measurements of the MDF in the inner disk by, e.g., SDSS-V \citep{Kollmeier2017-SDSS-V} could help constrain the DTD.
+
+We implemented a stellar migration scheme which reproduces the abundance trends seen in the models of \citetalias{Johnson2021-Migration}, but produces smoother abundance distributions.
+Our method is flexible and is not tied to the output of a single hydrodynamical simulation.
+In future work, we will explore the effect of the strength and speed of radial migration on GCE models.
+
 Recent studies have shown that the high specific SN Ia rates observed in low-mass galaxies \citep[e.g.,][]{Brown2019-ASASSNrates,Wiseman2021-DESRates} can be explained by a metallicity-dependent rate of SNe Ia \citep{Gandhi2022-MetallicityDependentRates,Johnson2023-Binaries}.
 A similar metallicity dependence has also been observed in the rate of CCSNe \citep{Pessi2023-MetalDepCCSNe}.
-% The consequences of a metallicity-dependent SN Ia rate in the context of a multi-zone GCE model with radial migration could be explored in a future paper.
-A metallicity dependence on the {\it shape} of the DTD could also be interesting to explore, for example if binary evolution leads to different progenitor systems at low and high metallicity.
 These previous investigations varied only the normalization in the DTD.
@@
 
-% \begin{acknowledgments}
 \section*{Acknowledgements}
@@
 We thank Prof.\ David H.\ Weinberg and attendees of OSU's Galaxy Hour for many useful discussions over the course of this project.
-\todo{Other personal acknowledgements.}
 
@@
 % This work made use of Astropy:\footnote{http://www.astropy.org} a community-developed core Python package and an ecosystem of tools and resources for astronomy \citep{astropy:2013, astropy:2018, astropy:2022}.
-% \end{acknowledgments}
 
@@
 repository associated to this study is publicly available at
-\url{\GitHubURL}, and the release \todo{v.X.X} allows anyone to re-build the entire 
-manuscript. The datasets are stored at \todo{URL}.
+\url{\GitHubURL}, and the release v1.0.0 allows anyone to re-build the entire 
+manuscript. The multi-zone model outputs and APOGEE sample dataset are stored at \url{https://doi.org/10.5281/zenodo.10961091}.
 
@@
 Each Gaussian is centered at 0, and we find that the scale $\sigma_{\rm RM}$ is best described by the function
-% \begin{equation}
-%     \sigma_{\rm RM} = 1.35\,{\rm kpc} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61} \Big(\frac{\tau}{1\,{\rm Gyr}}\Big)^{0.33}
-%     \label{eq:radial-migration}
-% \end{equation}
 \begin{equation}
@@
 The presence of a strong bar has been found to affect the strength of radial migration throughout the disk \citep[e.g.,][]{Brunetti2011-BarredSpiralDiffusion} and lead to a flattening of the metallicity gradient for old populations \citep{Okalidis2022-AurigaMigration}.
-% also a slower timestep evolution than diffusion
-% \citet{Okalidis2022-AurigaMigration} studied the stellar migration in the Auriga simulations and found that the migration strength had both a dependence on age and formation radius.
-They also found that in strongly-barred galaxies, the migration is stronger overall but has a slower timestep evolution than diffusion ($\Delta t^{0.5}$).
-\todo{They argue that the bar has a minimal effect.}
-% On the other hand, \citet{Brunetti2011-BarredSpiralDiffusion} argue that the bar has a strong effect on the strength of radial migration and that its effect is not constant with time.
 
@@
 To produce smoother abundance distributions, we fit a sech$^2$ function \citep{Spitzer1942} to the distribution of $z$ in \hydro.
-% Vertical migration away from the midplane does not affect the chemical evolution model, but we do use $z$ in our analysis. 
 The PDF of $z_{\rm final}$ given some scale height $h_z$ is
@@
 \end{equation}
-% and the corresponding cumulative distribution function (CDF) is
-% \begin{equation}
-%     {\rm CDF}(z_{\rm final}) = \frac{1}{1 + e^{-z_{\rm final} / h_z}}.
-%     \label{eq:sech-cdf}
-% \end{equation}
 We fit Equation \ref{eq:sech-pdf} to the distributions of $z$ in \hydro in varying bins of $T$ and $R_{\rm final}$. We find that $h_z$ is best described by the function

### 2024-06-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Type Ia supernovae (SNe Ia), the thermonuclear explosions of carbon-oxygen white dwarfs (WDs), are responsible for a majority of the Fe produced in the Galaxy \citep{Matteucci1986-SupernovaEnrichment}; meanwhile, core collapse supernovae (CCSNe), the explosions of massive stars, produce the $\alpha$-elements (e.g., O and Mg) in addition to a smaller fraction of Fe.
-SNe Ia are delayed by $\sim0.1-10$ Gyr after star formation events, as evidenced by observations at large distances from star-forming regions and in elliptical galaxies \citep[e.g.,][]{Maza1976-SNStatistics}.
+SNe Ia are delayed by $\sim{\bf 0.04}-10$ Gyr after star formation events, as evidenced by observations at large distances from star-forming regions and in elliptical galaxies \citep[e.g.,][]{Maza1976-SNStatistics}.
 This delayed enrichment leads to a decrease in \aFe with increasing [Fe/H] \citep{Matteucci1986-SupernovaEnrichment}.
@@
 As a result of the uncertainty regarding SN Ia progenitors, theoretical models have yet to converge on a single prediction for the DTD.
-For the DD channel, assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral suggest a broad $\sim t^{-1}$ DTD at long delay times ($\gtrsim 1$ Gyr), but at short delays ($\lesssim 1$ Gyr) the rate is limited by the need to produce two WDs \citep[see][]{Maoz2014-Review}.
+For the DD channel, assumptions about the distribution of {\bf WD} separations and the rate of gravitational wave inspiral suggest a broad $\sim t^{-1}$ DTD at long delay times ($\gtrsim 1$ Gyr), but at short delays ($\lesssim 1$ Gyr) the rate is limited by the need to produce two WDs {\bf \citep[see][]{Greggio2005-AnalyticalRates,Maoz2014-Review}}.
 Triple or higher-order progenitor systems could also produce a $t^{-1}$ DTD \citep{Fang2018-QuadrupleSystems,Rajamuthukumar2023-TripleEvolution}.
@@
 A few studies have investigated different DTDs in one-zone chemical evolution models, but comparisons to abundance data have been limited to the solar neighborhood \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
-\citet{Matteucci2009-DTDModels} compared five DTDs in a multi-zone GCE model and found that the agreement with observations worsens if the fraction of prompt SNe Ia is either too high or too low, but they were similarly limited by the available data for the solar neighborhood.
+\citet{Matteucci2009-DTDModels} compared five DTDs in a multi-zone GCE model and found that the agreement with observations worsens if the fraction of prompt {\bf ($\bf t\lesssim 100$ Myr)} SNe Ia is either too high or too low, but they were similarly limited by the available data for the solar neighborhood.
 \citet{Poulhazan2018-PrecisionPollution} found that the prompt component of the DTD affects the peak and width of the \aFe distribution in a cosmological smoothed-particle hydrodynamics simulation, but their simulation was not designed to reproduce the parameters of the Milky Way.
@@
 \begin{equation}
-    \dot M_x^{\rm CC} = y_x^{\rm CC} \dot M_\star
+    \dot M_x^{\rm CC}{\bf (t)} = y_x^{\rm CC} \dot M_\star{\bf (t)}
     \label{eq:ccsn-enrichment}
@@
 \begin{equation}
-    \dot M_{\rm Fe}^{\rm Ia} = y_{\rm Fe}^{\rm Ia} \langle \dot M_\star\rangle_{\rm Ia} \\
-\end{equation}
-where $\langle \dot M_\star\rangle_{\rm Ia}$ is the time-averaged SFR weighted by the DTD and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia.
+    \dot M_{\rm Fe}^{\rm Ia}{\bf (t)} = y_{\rm Fe}^{\rm Ia} \langle \dot M_\star{\bf (t)}\rangle_{\rm Ia} \\
+\end{equation}
+where $\langle \dot M_\star\rangle_{\rm Ia}$ is the time-averaged SFR weighted by the DTD {\bf at time $t$} and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia.
 \citet{Weinberg2017-ChemicalEquilibrium} show in their Appendix A that
@@
 We also investigate one or two useful variations of the input parameters for each functional form.
-Figure \ref{fig:dtds} presents a selection of these DTDs, and Table \ref{tab:dtds} summarizes all of our DTDs and their parameters.
+Figure \ref{fig:dtds} presents a selection of these DTDs, and Table \ref{tab:dtds} summarizes {\bf the parameters and median delay times ($t_{\rm med}$) for all of our DTDs}.
 We use simple forms rather than simulated physical or analytic models of SNe Ia for the sake of decreased computational time and easier interpretation of the model predictions.
@@
 
-In this subsection we present functional forms $f_{\rm Ia}$ describing the shape of each DTD.
-$f_{\rm Ia}$ does not include the normalization, so it has units of Gyr$^{-1}$ as opposed to M$_\odot^{-1}$ Gyr$^{-1}$ and is related to $R_{\rm Ia}$ according to
+{\bf In this subsection, we present functional forms of each DTD in terms of a function $f_{\rm Ia}$ that has units of ${\rm Gyr}^{-1}$ and defines the shape of the DTD for $t\ge t_D$ as}
+% describing the shape of each DTD. $f_{\rm Ia}$ does not include the normalization, so it has units of Gyr$^{-1}$ as opposed to M$_\odot^{-1}$ Gyr$^{-1}$ and is related to $R_{\rm Ia}$ according to
 \begin{equation}
@@
 \end{equation}
-\vice automatically normalizes the provided function for the DTD according to this equation.
-In the remainder of this subsection, we discuss each form of $f_{\rm Ia}$ individually.
+{\bf Note that the denominator in Equation \ref{eq:dtd-function} normalizes the DTD.}
+% \vice automatically normalizes the provided function for the DTD according to this equation.
+% In the remainder of this subsection, we discuss each form of $f_{\rm Ia}$ individually.
 
@@
     \label{tab:dtds}
-    \begin{tabular}{lcll}
+    \begin{tabular}{lclcl}
         \hline\hline
-        \multicolumn{1}{c}{Model} & Eq. & \multicolumn{1}{c}{Parameters} & \multicolumn{1}{c}{Similar to} \\
+        \multicolumn{1}{c}{Model} & Eq. & \multicolumn{1}{c}{Parameters} & $t_{\rm med}$ [Gyr] & \multicolumn{1}{c}{Similar to} \\
         \hline
-        Two-population  & \ref{eq:prompt-dtd}   & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
-                        &                       & $\tau=3$ Gyr & \\
-        Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
+        Two-population  & \ref{eq:prompt-dtd}   & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr,   & 0.39  & \citet{Mannucci2006-TwoPopulations} \\
+                        &                       & $\tau=3$ Gyr & & \\
+        Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.4$                 & 0.18  & \citet[][cluster]{Maoz2017-CosmicDTD}; 
                                                       \citet{Heringer2019-FieldGalaxyDTD}       \\
-        Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.1$                 & \citet[][field]{Maoz2017-CosmicDTD}; 
+        Power-law   & \ref{eq:powerlaw-dtd} & $\alpha=-1.1$                 & 0.48  & \citet[][field]{Maoz2017-CosmicDTD}; 
                                                       \citet{Wiseman2021-DESRates}              \\
-        Exponential & \ref{eq:exponential-dtd}  & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
+        Exponential & \ref{eq:exponential-dtd}  & $\tau=1.5$ Gyr    & 1.08  & \citet[][SD]{Greggio2005-AnalyticalRates};
                                                                       \citet{Schonrich2009-RadialMixing};       \\
-                    &                           &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
-        Exponential & \ref{eq:exponential-dtd}  & $\tau=3$ Gyr   & --- \\
-        Plateau     & \ref{eq:plateau-dtd}  & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
-        Plateau     & \ref{eq:plateau-dtd}  & $W=1$ Gyr, $\alpha=-1.1$      & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
-        Triple-system   & \ref{eq:triple-dtd}   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2023-TripleEvolution} \\
-                        &                       & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
+                    &                           &                   &       & \citet{Weinberg2017-ChemicalEquilibrium}  \\
+        Exponential & \ref{eq:exponential-dtd}  & $\tau=3$ Gyr   & 2.08 & --- \\
+        Plateau     & \ref{eq:plateau-dtd}  & $W=0.3$ Gyr, $\alpha=-1.1$    & 1.08  &\citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
+        Plateau     & \ref{eq:plateau-dtd}  & $W=1$ Gyr, $\alpha=-1.1$      & 2.02  & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
+        Triple-system   & \ref{eq:triple-dtd}   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & 2.50   & \citet{Rajamuthukumar2023-TripleEvolution} \\
+                        &                       & $W=0.5$ Gyr, $\alpha=-1.1$ & &  \\
         \hline
@@
 \begin{equation}
-    f_{\rm Ia}^{\rm twopop}(t) = 0.5\Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big].
+    f_{\rm Ia}^{\rm twopop}(t) = \frac{1}{\sigma\sqrt{2\pi}} e^{-\frac{(t-t_p)^2}{2\sigma^2}} + \frac{1}{\tau} e^{-t/\tau}.
     \label{eq:prompt-dtd}
@@
 \end{equation}
-A declining power-law with $\alpha\sim-1$ arises from typical assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral \citep[see Section 3.5 from][]{Maoz2014-Review}.
+A declining power-law with $\alpha\sim-1$ {\bf \citep{Totani2008-DTD}} arises from typical assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral \citep[see Section 3.5 from][]{Maoz2014-Review}.
 It is therefore a commonly assumed DTD in GCE studies (e.g., \citealt{Rybizki2017-Chempy}; \citetalias{Johnson2021-Migration}; \citealt{Weinberg2023-CCSNYield}).
@@
 \end{equation}
-This model allows analytic solutions to the abundances as a function of time for some SFHs, making it a popular choice.
+This model allows analytic solutions to the abundances as a function of time for some SFHs, making it a popular choice {\bf \citep[e.g.,][]{Weinberg2017-ChemicalEquilibrium,Pantoni2019-AnalyticSolutions,Palicio2023-AnalyticDTD}}.
 \citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assumed an exponential DTD with a timescale $\tau=1.5$ Gyr.
@@
 Our primary motivation is to consider a model which matches observations at delay times beyond a few Gyr, where the DTD is best constrained, but with a smaller fraction of prompt ($\lesssim 100$ Myr) SNe Ia than the single power law.
-To our knowledge, this form of the DTD has not been considered in previous GCE models.
+{\bf This form has been used for the DTD of neutron star mergers \citep{Simonetti2019-NeutronStarDTD}, but to our knowledge it has not been considered for SNe Ia in previous GCE models.}
+% To our knowledge, this form of the DTD has not been considered in previous GCE models. 
 We show in Appendix \ref{app:analytic-dtds} that this form can approximate the more complicated analytic DD DTDs from \citet{Greggio2005-AnalyticalRates}.
@@
 The inside-out and late-burst models are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_\star$ is prescribed along with the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g/\dot\Sigma_\star$.
-The remaining quantities, infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities.
-The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\tau_\star$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in SFR mode).
+The remaining quantities, infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities {\bf assuming the star formation law adopted by \citetalias{Johnson2021-Migration} (see their Equation 14)}.
+The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\tau_\star$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in {\bf star formation mode}).
 The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified.
-The SFH is normalized such that the model predicts an accurate total stellar mass and surface density gradient (see Appendix B of \citetalias{Johnson2021-Migration}).
+The SFH is normalized such that the model predicts %an accurate
+{\bf a total stellar mass of $(5.17\pm1.11)\times10^{10} M_\odot$ \citep{LicquiaNewman2015-StellarMass} and the stellar surface density gradient reported by \citet[][see Appendix B of \citetalias{Johnson2021-Migration}]{BlandHawthornGerhard2016-MilkyWayReview}}.
 We present an overview of the four SFHs in Figure \ref{fig:sfhs}, and we discuss them individually here.
@@
 \begin{equation}
-    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm sfh}},
+    f_{\rm IO}(t|R_{\rm gal}) = \Big[1 - \exp\Big(\frac{-t}{\tau_{\rm rise}}\Big)\Big] \exp\Big(\frac{-t}{\tau_{\rm sfh}(R_{\rm gal})}\Big),
     \label{eq:insideout-sfh}
@@
 Evidence for a recent star formation burst $\sim 2-3$ Gyr ago has been found in {\it Gaia} \citep{Mor2019-Starburst} and in massive WDs in the solar neighborhood \citep{Isern2019-Starburst}.
-Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr. The determination of $\tau_{\rm sfh}$ is the same as in the inside-out case.
+Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr.
+{\bf The values of $\tau_{\rm rise}$ and $\tau_{\rm sfh}(R_{\rm gal})$ are the same as in the inside-out case.}
+% The determination of $\tau_{\rm sfh}$ is the same as in the inside-out case.
 
@@
 \begin{equation}
-    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}},
+    f_{\rm EB}(t|R_{\rm gal}) = \exp\Big(\frac{-t}{\tau_{\rm sfh}(R_{\rm gal})}\Big),
     \label{eq:earlyburst-ifr}
@@
         Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{Leung2023-Ages} \\
+        % {\bf
+        \bf $R_{\rm gal}$   & $3 < R_{\rm gal} < 15$ kpc    & Eliminate bulge \& extreme outer-disk stars \\
+        $|z|$               & $|z| < 2$ kpc                 & Eliminate halo stars \\
+        % }
         \hline
-        $\sigma({\rm [Fe/H]})$ & $9.2\times10^{-3}$ & Median uncertainty in [Fe/H] \\
-        $\sigma({\rm [O/Fe]})$ & $1.8\times10^{-2}$ & Median uncertainty in [O/Fe] \\
-        $\sigma($log(Age/Gyr)) & $0.10$ & Median age uncertainty \citepalias{Leung2023-Ages} \\
+        % $\sigma({\rm [Fe/H]})$ & $9.2\times10^{-3}$ & Median uncertainty in [Fe/H] \\
+        % $\sigma({\rm [O/Fe]})$ & $1.8\times10^{-2}$ & Median uncertainty in [O/Fe] \\
+        % $\sigma($log(Age/Gyr)) & $0.10$ & Median age uncertainty \citepalias{Leung2023-Ages} \\
+        % \hline
+    \end{tabular}
+\end{table*}
+
+\begin{table*}
+    \centering
+    \caption{Median and dispersion in APOGEE parameter uncertainties.}
+    \label{tab:uncertainties}
+    \begin{tabular}{lcc}
+        \hline\hline
+        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Median Uncertainty} & \multicolumn{1}{c}{Uncertainty Dispersion ($95\%-5\%$)} \\
+        \hline
+        [Fe/H]          & $8.9\times10^{-3}$    & $6.0\times10^{-3}$ \\
+        ${\rm [O/Fe]}$        & $1.9\times10^{-2}$    & $3.1\times10^{-2}$ \\
+        log(Age/Gyr)    & $0.10$                & $0.16$ \\
         \hline
@@
 Table \ref{tab:sample} lists our selection criteria, which largely follow from \citet{Hayden2015-ChemicalCartography}.
-This produces a final sample of \samplesize stars with [O/Fe] and [Fe/H] abundance measurements.
-APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
+This produces a final sample of \samplesize stars with {\bf calibrated} [O/Fe] and [Fe/H] abundance measurements.
+{\bf APOGEE stars were cross-matched with the {\it Gaia} Early Data Release 3 catalog \citep{Gaia2016-Mission,Gaia2021-EDR3} by the APOGEE team, and we use the \citet{Bailer-Jones2021-GaiaDistances} photo-geometric distance estimates}
+% APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use 
+to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$, {\bf assuming a Sun--Galactic center distance $R_\odot=8.122$ kpc and height of the Sun above the midplane $z_\odot=20.8$ pc.
+Table \ref{tab:apogee-regions} lists the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$.
+The median distance error exceeds 1 kpc for Galactic regions with $R_{\rm gal}<5$ kpc or $R_{\rm gal}>13$ kpc, but the vast majority of stars have much smaller uncertainties.}
 
@@
 We note that we use the full sample of \samplesize APOGEE stars unless we explicitly compare to age estimates.
-Table \ref{tab:sample} also presents the median uncertainties in the data for [Fe/H], [O/Fe], and age.
+{\bf Table \ref{tab:uncertainties} presents the median and dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the uncertainty in [Fe/H], [O/Fe], and log(age).}
+
+\begin{table*}
+\centering
+\caption{Number of APOGEE stars in each Galactic region.}
+\label{tab:apogee-regions}
+\variable{output/apogee_regions_table.tex}
+\end{table*}
 
@@
 A one-zone model assumes the entire gas reservoir is instantaneously mixed, removing all spatial dependence.
-This limits the ability to compare to observations across the disk, but it eliminates the complicating factor of stellar migration and better isolates the effects of the nucleosynthesis prescription.
+This limits the ability to compare to observations across the disk, but it {\bf obviates} the complicating factor of stellar migration and better isolates the effects of the nucleosynthesis prescription.
 In this section, we compare the results from one-zone models which examine various parameters of the DTD while keeping other parameters fixed.
@@
 Unless otherwise specified, we adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_\star=2.15$ \citepalias[see Equation 8 from][]{Johnson2021-Migration} and a minimum SN Ia delay time $t_D=40$ Myr.
+
+\subsection{\bf DTD Parameters: Slope, Timescale, and Plateau Width}
+\label{sec:onezone-dtd-params}
 
@@
 The left-hand panel of Figure \ref{fig:onezone-threepanel} compares the results of three one-zone models that are identical except for the slope of the power-law DTD.
-A steeper slope produces a sharper ``knee'' and a faster decline in [O/Fe] with increasing [Fe/H], resulting in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
+A steeper slope {\bf implies a greater number of prompt SNe Ia which rapidly enrich the ISM with Fe, producing a faster decline in [O/Fe] with increasing [Fe/H] and hence a sharper ``knee'' after the minimum delay time.
+This results} in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
 In all cases the [O/Fe] DF is distinctly unimodal.
 The MDF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
+{\bf The abundance tracks converge to the same values which reflect the yield ratio of CCSNe to SNe Ia and the asymptotic evolution with nearly quenched star formation at the end of the model.}
 
@@
 Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around $t=1$ Gyr.
-Doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.
+Doubling the timescale from 1.5 Gyr to 3 Gyr {\bf implies a longer median delay time, which} raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex.
+% but the equilibrium abundance reached at $t=10$ Gyr remains unchanged. 
 A longer exponential timescale also produces a broader [O/Fe] DF with more high-$\alpha$ stars, but the distribution is still unimodal.
@@
 On the other hand, all of the plateau DTDs produce very similar MDFs.
+
+\subsection{\bf The Minimum SN Ia Delay Time}
+\label{sec:onezone-minimum-delay}
 
@@
 The left-hand panel of Figure \ref{fig:onezone-twopanel} shows that $t_D$ has a much stronger effect in models which assume a power-law DTD than others.
-This is a consequence of the high number of prompt SNe Ia (see Figure \ref{fig:dtds}).
+This is a consequence of the high number of prompt SNe Ia ({\bf $\bf t\lesssim100$ Myr;} see Figure \ref{fig:dtds}).
 Moreover, a power-law DTD with a long $t_D$ may be observationally hard to distinguish from a plateau model.
@@
 
+\subsection{\bf The Form of the DTD}
+\label{sec:onezone-dtd-form}
+
 The right-hand panel of Figure \ref{fig:onezone-twopanel} compares the one-zone model outputs from the full range of DTDs we investigate in this paper.
@@
 At the other extreme are the two-population and power-law ($\alpha=-1.1$) DTDs, for which the SN Ia rate peaks immediately after the minimum delay time of 40 Myr, placing the high-$\alpha$ knee at ${\rm [Fe/H]}\approx-1.8$.
-The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is produced by the delayed exponential component.
+The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is produced by the delayed exponential component, {\bf as observed by \citet{Vincenzo2017-ChemicalEvolution}}.
 The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models occupy the intermediate space between these extremes.
@@
 The [O/Fe] DFs also show significant differences between the DTDs.
-In the triple-system model, star formation proceeds for such a long time before the knee that the [O/Fe] DF shows a slight second peak around the CCSN yield ratio.
+In the triple-system model, star formation proceeds for such a long time before the knee that the [O/Fe] DF shows a slight second peak around the CCSN yield ratio {\bf ($\bf \sim0.45$ dex)}.
 Out of all our one-zone models, this small bump is the only degree of bimodality that arises in the [O/Fe] DF.
@@
 In this section we focused on the fiducial inside-out SFH.
-\citet{Palicio2023-AnalyticDTD} compared similar DTDs in one-zone models with a two-infall SFH (see \ref{sec:two-infall-discussion}).
+\citet{Palicio2023-AnalyticDTD} compared similar DTDs in one-zone models with a two-infall SFH (see {\bf Section} \ref{sec:two-infall-discussion}).
 
@@
 Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row.
-Each MDF is convolved with a Gaussian with a width equal to the median observational uncertainty in APOGEE DR17 (see Table \ref{tab:sample}) and smoothed with a box-car width of 0.2 dex.
+{\bf A Gaussian scatter with a width equal to the median observational uncertainty in APOGEE DR17 (see Table \ref{tab:sample}) is applied to the abundance of each model stellar population.
+For visual clarity,} each MDF is smoothed with a box-car width of 0.2 dex.
     \textit{Left columns:} comparison between the inside-out and two-infall SFHs; both assume the exponential ($\tau=1.5$ Gyr) DTD. 
@@
 The two left-hand columns illustrate the effect of different SFHs on the model outputs, which is most pronounced in the inner Galaxy.
-Near the midplane, the two-infall SFH produces a distinct bump $\sim0.4$ dex below the MDF peak, which is not seen for the inside-out SFH.
+Near the midplane {\bf and in the inner Galaxy}, the two-infall SFH produces a distinct bump $\sim0.4$ dex below the MDF peak, which is not seen for the inside-out SFH.
 Away from the midplane, the low-metallicity tail is slightly more prominent for the two-infall than the inside-out model, and the two-infall MDFs extend to slightly higher metallicity.
@@
 In this case, $P$ is the APOGEE MDF, $Q$ is the model MDF, and $x={\rm [Fe/H]}$.
-We bin the distributions with a width of 0.01 dex and apply observational uncertainties to our modeled MDFs according to Table \ref{tab:sample}.
-For each SFH and DTD, we compute $D_{\rm{KL}}$ in the 18 different Galactocentric regions shown in Figure \ref{fig:feh-df-comparison}.
+{\bf We forward-model the observational uncertainties given in Table \ref{tab:sample} by applying a random Gaussian scatter to the abundance of each model stellar population, and we numerically evaluate Equation \ref{eq:kl-divergence} with integration step size $d{\rm [Fe/H]}=0.01$ dex.}
+% We bin the distributions with a width of 0.01 dex and apply observational uncertainties to our modeled MDFs according to Table \ref{tab:sample}. 
+For each SFH and DTD, we compute $D_{\rm{KL}}$ in the 18 different {\bf Galactic} regions shown in Figure \ref{fig:feh-df-comparison}.
 We use bins in $R_{\rm gal}$ with a width of 2 kpc between 3 and 15 kpc, and bins in midplane distance of $|z|=0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
-The score $S$ for the entire model is taken to be the average of $D_{\rm{KL}}$ for each region $R$ weighted by the number of APOGEE stars in that region $N_{\star,R}$:
-\begin{equation}
-    S = \frac{\sum_R D_{\rm KL}(P||Q|R) N_\star(R)}{\sum_R N_\star(R)}.
+The score $S$ for the entire model is taken to be the average of $D_{\rm{KL}}$ for each region $\bf (R_{\rm gal}, |z|)$
+% $R,z\equiv(R_{\rm gal}\in(R_{\rm min}, R_{\rm max}),|z|\in(z_{\rm min}, z_{\rm max}))$
+weighted by the number of APOGEE stars in that region $\bf N_\star(R_{\rm gal}, |z|)$ {\bf (see Table \ref{tab:apogee-regions})}:
+\begin{equation}
+    S = \frac{\sum_{R_{\rm gal}, |z|} D_{\rm KL}(P||Q|R_{\rm gal}, |z|) N_\star(R_{\rm gal}, |z|)}{\sum_{R_{\rm gal}, |z|} N_\star(R_{\rm gal}, |z|)}.
     \label{eq:feh-df-score}
 \end{equation}
+{\bf We also run a two-sample Kolmogorov-Smirnov (KS) test for each region to estimate the significance of the agreement with the observed distributions.
+However, for the best-performing model, we reject the null hypothesis that the model and observed abundances are drawn from the same distribution at very high significance ($p<<0.05$) in each region.}
 
@@
 Figure \ref{fig:ofe-bimodality} compares the [O/Fe] distributions in the solar annulus ($7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc) in two bins of [Fe/H] ($-0.6<{\rm [Fe/H]}<-0.4$ and $-0.4<{\rm [Fe/H]}<-0.2$) for select model outputs and APOGEE data.
-The APOGEE distributions in the bottom-right panel (j) show that the high-$\alpha$ mode is more prominent at lower [Fe/H], but the distributions in both bins are clearly bimodal.
+{\bf The purpose of the narrow [Fe/H] bins is to isolate the bimodality of the [O/Fe] distribution with minimal variation in [Fe/H].} The APOGEE distributions in the bottom-right panel (j) show that the high-$\alpha$ mode is more prominent at lower [Fe/H], but the distributions in both bins are clearly bimodal.
 The ``trough'' occurs near ${\rm [O/Fe]}\approx0.2$ in each bin.
@@
 On the other hand, the early-burst SFH {\it always} produces a bimodal distribution in the high-[Fe/H] bin regardless of the assumed DTD, but not in the low-[Fe/H] bin (the small low-$\alpha$ peak falls below our prominence threshold).
-For models with the late-burst and two-infall SFHs, the bimodality is variable depending on the DTD: those with longer median delay times (e.g., exponential, plateau, or triple-system) generally produce a bimodal distribution in the low-[Fe/H] bin, while the two DTDs with the most prompt SNe Ia do not.
+For models with the late-burst and two-infall SFHs, the bimodality {\bf in the low-[Fe/H] bin} is variable depending on the DTD: those with longer median delay times (e.g., exponential, plateau, or triple-system) generally produce a bimodal distribution, while the two DTDs with the most prompt SNe Ia do not.
 
@@
 The black curves represent the ISM abundance tracks in the 8 kpc zone.
-The red contours represent a 2-D kernel density estimate of the APOGEE abundance distribution in that Galactic region with a bandwidth of 0.03.
+The red contours represent a 2-D {\bf Gaussian} kernel density estimate of the APOGEE abundance distribution in that Galactic region with a bandwidth of 0.03.
 The solid and dashed contours enclose 30\% and 80\% of stars in the sample, respectively.}
@@
 This ridge roughly coincides with the upper limit of the APOGEE distribution near the midplane.
-The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx-0.1$, which reflects the population-averaged yield ratio of [O/Fe].
+The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx-0.1$ %which reflects the population-averaged yield ratio of [O/Fe].
+{\bf which reflects the equilibrium [O/Fe] abundance ratio of the second infall.}
 
@@
 
-The two-population and power-law ($\alpha=-1.1$) DTDs, which have a large fraction of prompt SNe Ia, produce stellar abundance distributions that are reasonably well-aligned with the APOGEE contours at low $|z|$, but they entirely miss the observed high-$\alpha$ sequence at large $|z|$.
+The two-population and power-law ($\alpha=-1.1$) DTDs, which have a large fraction of prompt {\bf ($\bf t\lesssim100$ Myr)} SNe Ia, produce stellar abundance distributions that are reasonably well-aligned with the APOGEE contours at low $|z|$, but they entirely miss the observed high-$\alpha$ sequence at large $|z|$.
 The ISM abundance tracks for the 8 kpc zone do not pass through the APOGEE 30\% contour at $|z|=1-2$ kpc.
@@
 
-The DTDs with an intermediate median delay time do well at reproducing the observed abundance distributions.
-The exponential ($\tau=1.5$ Gyr) DTD produces a distribution in Figure \ref{fig:ofe-feh-dtd} which aligns quite well with the 80\% APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to high [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
+% The DTDs with an intermediate median delay time do well at reproducing the observed abundance distributions.
+The exponential ($\tau=1.5$ Gyr) DTD, {\bf which has an intermediate median delay time,} produces a distribution in Figure \ref{fig:ofe-feh-dtd} which aligns quite well with the 80\% APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to high [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
 While it does better at populating the high-$\alpha$ sequence than the previous DTDs, the bulk of the model stellar populations at large $|z|$ still fall below the APOGEE 30\% contour.
@@
 \begin{equation}
+    \label{eq:2d-kl-divergence}
     \hat D_k(P||Q) = \frac dn \sum_{i=1}^n\log\frac{r_k(\mathbf{x}_i)}{s_k(\mathbf{x}_i)} + \log\frac{m}{n-1},
 \end{equation}
-where $r_k(\mathbf{x}_i)$ and $s_k(\mathbf{x}_i)$ are the distance to the $k$th nearest neighbor of $\mathbf{x}_i$ in the samples of $P$ and $Q$, respectively.
+where {\bf $d=2$ is the dimension of the sample space and} $r_k(\mathbf{x}_i)$ and $s_k(\mathbf{x}_i)$ are the distance to the $k$th nearest neighbor of $\mathbf{x}_i$ in the samples of $P$ and $Q$, respectively.
 We take $k=2$ to find the nearest neighbor other than the sample itself.
@@
 
-Figure \ref{fig:ofe-feh-twoinfall} plots the stellar [O/Fe]--[Fe/H] abundances from the model with the two-infall SFH and plateau ($W=1$ Gyr) DTD.
+Figure \ref{fig:ofe-feh-twoinfall} plots the stellar [O/Fe]--[Fe/H] abundances from the model with the two-infall SFH and plateau ($W=1$ Gyr) DTD {\bf in two different bins of $R_{\rm gal}$}.
 In the inner Galaxy, the model distribution at large $|z|$ lies at higher [O/Fe] and is more extended than the APOGEE distribution.
@@
 where $\Delta\tau_k=\rm{med}(\tau_{\rm \vice})-\rm{med}(\tau_{\rm L23})$ is the difference between the mass-weighted median age in \vice and the median stellar age from \citetalias{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citetalias{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
-If a bin has no modeled or observed stars, we do not calculate $\Delta \tau_k$ for that bin.
+{\bf This is similar to a reduced $\chi^2$ estimator except that the difference in medians is not weighted by the variance in the observed sample.} If a bin has no modeled or observed stars, we do not calculate $\Delta \tau_k$ for that bin.
 As before, the score for the model as a whole is the average of $\Delta \tau_{\rm RMS}$ across all regions, weighted by the number of stars with age measurements in each region.
@@
 
-\subsection{Quantitative Comparisons}
+\subsection{\bf Qualitative Comparisons}
 \label{sec:discussion-scores}
@@
 
-The diagnostic scores for each model are presented in Table \ref{tab:results}.
-We use these scores to indicate combinations of SFH and DTD that are favorable or unfavorable in certain regimes, but we do {\it not} fit our models to the data due to computational expense.
+% The diagnostic scores for each model are presented in Table \ref{tab:results}. 
+{\bf The relative performance of each model is summarized in Table \ref{tab:results}.} We use these scores to indicate combinations of SFH and DTD that are favorable or unfavorable in certain regimes, but we do {\it not} fit our models to the data due to computational expense.
 To avoid drawing strong conclusions from small numerical differences in scores, we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom third out of all models, respectively.
+{\bf The exact numerical scores are presented in Appendix \ref{app:quantitative-scores}.}
 
@@
 For example, if the two-infall models are run with $y_{\rm Fe}^{\rm Ia}=0.0017$, the abundance tracks do not dip below solar [O/Fe] (see the bottom-right panel of Figure \ref{fig:ofe-feh-sfh}) and consequently they out-score every other SFH.
-Small adjustments in the yields can affect the quality of the fit between our models and the data, so we caution against over-interpreting the model scores in Table \ref{tab:results}.
+Small adjustments in the yields can affect the quality of the fit between our models and the data, so we caution against over-interpreting the {\bf qualitative comparisons} in Table \ref{tab:results}.
 
@@
 The MDF is more sensitive to the SFH, but overall trends across the Galaxy are primarily driven by the assumed radial abundance gradient and stellar migration prescription.
-However, the MDF is more sensitive to the DTD in the inner Galaxy due to the more sharply declining SFH (see discussion in Section \ref{sec:feh-df}), so improved measurements of the MDF in the inner disk by, e.g., SDSS-V \citep{Kollmeier2017-SDSS-V} could help constrain the DTD.
+However, the MDF is more sensitive to the DTD in the inner Galaxy due to the more sharply declining SFH (see discussion in Section \ref{sec:feh-df}).
+%, so improved measurements of the MDF in the inner disk by, e.g., SDSS-V \citep{Kollmeier2017-SDSS-V} could help constrain the DTD.
+{\bf Under the model of inside-out formation, the MDF in the inner Galaxy traces older populations which are more sensitive to the enrichment of prompt SNe Ia.}
 
@@
 Our results indicate that the allowed range of parameter space in GCE models is still too broad to precisely constrain the DTD.
-Future constraints may come from the Legacy Survey of Space and Time (LSST) at the Vera Rubin Observatory \citep{Ivezic2019-LSST}, which is expected to observe several million SNe during its X-year run.
-On the other hand, better constraints on the Galactic SFH provided by SDSS-V \citep{Kollmeier2017-SDSS-V} will enable future GCE studies to constrain the DTD at a higher confidence.
+Future constraints may come from the Legacy Survey of Space and Time (LSST) at the Vera Rubin Observatory \citep{Ivezic2019-LSST}, which is expected to observe several million SNe during its {\bf 10}-year run.
+On the other hand, %better constraints on the Galactic SFH provided by
+{\bf the improved sample size of} SDSS-V \citep{Kollmeier2017-SDSS-V} will enable future GCE studies to constrain {\bf both the Galactic SFH and} the DTD at a higher confidence.
 
@@
 The WIDE prescription is also best approximated by a plateau DTD, but with a longer plateau width of $W=1$ Gyr.
-In all cases, the difference between the analytic DTD and its simple approximation is too small to be observed.
+In all cases, the {\bf effect of the} difference between the analytic DTD and its simple approximation is too small to be observed.
 We also ran a multi-zone model with the inside-out SFH and the \citet{Greggio2005-AnalyticalRates} SD DTD and found it produced nearly identical results to the model with the exponential ($\tau=1.5$ Gyr) DTD.
@@
 
+\section{\bf Quantitative Comparison Scores}
+\label{app:quantitative-scores}
+
+\variable{output/scores_table.tex}
+\vspace{-24pt}
+
+{\bf Table \ref{tab:scores} presents the quantitative scores which measure the difference between the multi-zone outputs and APOGEE data for four observables.
+Details of the calculations for each observable are presented in the corresponding subsections of Section \ref{sec:multizone-results}, but in summary, divergence statistics between the multi-zone output and APOGEE data (Equation \ref{eq:kl-divergence} for the [Fe/H] and [O/Fe] DFs, Equation \ref{eq:2d-kl-divergence} for the [O/Fe]--[Fe/H] plane, and Equation \ref{eq:age-ofe-score} for the age--[O/Fe] plane) are computed within each Galactic region.
+The overall score for the model is the average of the divergence statistics across all regions, weighted by the number of APOGEE targets in each region.
+The scores can be strongly affected by zero-point offsets between the model and observed abundance distributions, so we caution against using these scores as an absolute metric of model performance.}
+
 \bibliography{bib}

### 2024-06-18 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % [Introduction to SNe Ia]
-The explosion mechanism(s) of SNe Ia are not fully understood \citep[for reviews, see][]{Maoz2014-Review,Livio2018-ProgenitorReview,Ruiter2020-ProgenitorReview}.
+The explosion mechanism(s) of SNe Ia are not fully understood \citep[for reviews, see][]{Maoz2014-Review,Livio2018-ProgenitorReview,Ruiter2020-ProgenitorReview,Liu2023-SNIaBinaryReview}.
 Two general production channels have been proposed.
@@
 Early studies, which had limited sample sizes, produced unimodal \citep{Strolger2004-SNIaProgenitors} or bimodal \citep{Mannucci2006-TwoPopulations} DTDs where the majority of SNe Ia explode within a relatively narrow range of delay times.
-More recent studies have recovered broader DTD functions, with many converging on a declining power-law of $\sim t^{-1}$ \citep[e.g.,][]{Maoz2017-CosmicDTD,Castrillo2021-DTD,Wiseman2021-DESRates}, though there is some evidence for a steeper slope in galaxy clusters \citep{Maoz2017-CosmicDTD,FriedmannMaoz2018-ClusterDTD}.
-It is especially difficult to constrain the DTD for short delay times \citep{MaozMannucci2012-SNeIaReview} because of the need for SN Ia rates at long lookback times and uncertainties in the age estimates of stellar populations.
+More recent studies have recovered broader DTD functions, with many converging on a declining power-law of $\sim t^{-1}$ {\bf \citep[e.g.,][]{Graur2013-IaRateVsMass,Graur2015-UnifiedExplanation,Maoz2017-CosmicDTD,Castrillo2021-DTD,Wiseman2021-DESRates}}, though there is some evidence for a steeper slope in galaxy clusters \citep{Maoz2017-CosmicDTD,FriedmannMaoz2018-ClusterDTD}.
+It is especially difficult to constrain the DTD for short delay times {\bf \citep{MaozMannucci2012-SNeIaReview,Rodney2014-PromptSNeIa}} because of the need for SN Ia rates at long lookback times and uncertainties in the age estimates of stellar populations.
 
@@
 \begin{equation}
-    \dot M_{\rm Fe}^{\rm Ia}{\bf (t)} = y_{\rm Fe}^{\rm Ia} \langle \dot M_\star{\bf (t)}\rangle_{\rm Ia} \\
-\end{equation}
-where $\langle \dot M_\star\rangle_{\rm Ia}$ is the time-averaged SFR weighted by the DTD {\bf at time $t$} and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia.
+    \dot M_{\rm Fe}^{\rm Ia}{\bf (t)} = y_{\rm Fe}^{\rm Ia} \langle \dot M_\star\rangle_{\rm Ia} {\bf (t)}\\
+\end{equation}
+where $\langle \dot M_\star\rangle_{\rm Ia}{\bf (t)}$ is the time-averaged SFR weighted by the DTD {\bf at time $t$} and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia.
 \citet{Weinberg2017-ChemicalEquilibrium} show in their Appendix A that
@@
 This yield is originally adapted from the W70 model of \citet{Iwamoto1999-SNIaYields}, but it is increased slightly so that the inside-out SFH produces stars with ${\rm [O/Fe]}\approx 0.0$ by the end of the model.
-\citet{Palla2021-SNIaYield} studied the effect of different SN Ia yields on GCE models in detail.
+{\bf The overall scale of the yields is inconsequential: a lower value of $y_{\rm Fe}^{\rm Ia}$ would produce similar results if compensated with a lower outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_\star$ (this is the yield-outflow degeneracy; see \citealt{Weinberg2023-CCSNYield}, \citealt{Sandford2024-StrongOutflows}, and appendix B of \citealt{Johnson2023-DwarfGalaxyArchaeology}).} \citet{Palla2021-SNIaYield} studied the effect of different SN Ia yields on GCE models in detail.
 
@@
 \citet{Wiseman2021-DESRates} obtained a similar slope of $\alpha=-1.13\pm0.05$ for field galaxies in the redshift range $0.2<z<0.6$.
-For galaxy clusters, \citet{Maoz2017-CosmicDTD} found a steeper DTD slope of $\alpha=-1.39^{+0.32}_{-0.05}$.
-\citet{Heringer2019-FieldGalaxyDTD} used a SFH-independent method to constrain the DTD for field galaxies within $0.01<z<0.2$ and found a similar slope of $\alpha=-1.34^{+0.19}_{-0.17}$.
+{\bf \citet{Heringer2019-FieldGalaxyDTD} used a SFH-independent method to constrain the DTD for field galaxies within $0.01<z<0.2$ and found a larger value of $\alpha=-1.34^{+0.19}_{-0.17}$.} For galaxy clusters, \citet{Maoz2017-CosmicDTD} found a steeper DTD slope of $\alpha=-1.39^{+0.32}_{-0.05}$, {\bf and \citet{FriedmannMaoz2018-ClusterDTD} found a similar slope of $\alpha=-1.3^{+0.23}_{-0.16}$; however, a re-analysis by \citet{FreundlichMaoz2021-ClusterDTD} revealed no significant difference between the cluster and field galaxy DTDs}.
 In this paper, we investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$.
@@
 
+{\bf There are many models for the DTD which have been proposed in the literature, and an exhaustive test of every one is infeasible.
+In particular, we do not consider a Gaussian DTD \citep[e.g.,][]{Strolger2004-SNIaProgenitors}, in which most SNe Ia explode with delay times close to $\sim 3$ Gyr.
+Evidence for this form came from SN Ia rate measurements for $z>1$, but re-analysis of the data revealed large errors due to the small sample size, extinction corrections, and uncertainties in the SFHs \citep[e.g.,][]{Forster2006-SNIaConstraints,Greggio2008-CosmicMix}.
+Additionally, \citet{Mannucci2006-TwoPopulations} found that such a DTD fails to reproduce the observed dependence of the SN Ia rate on galaxy color and radio power.
+Previous GCE studies have found that a Gaussian DTD over-produces high-[O/Fe] and low-[Fe/H] stars \citep{Matteucci2009-DTDModels,Palicio2023-AnalyticDTD}.}
+
 \subsubsection{The Minimum SN Ia Delay Time}
@@
 The inside-out and late-burst models are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_\star$ is prescribed along with the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g/\dot\Sigma_\star$.
-The remaining quantities, infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities {\bf assuming the star formation law adopted by \citetalias{Johnson2021-Migration} (see their Equation 14)}.
+The remaining quantities, infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities {\bf assuming the star formation law adopted by \citetalias{Johnson2021-Migration} (see their Equation 14).
+More specifically, at each timestep the infall rate is calculated to fulfill the quantity of gas required to produce the specified SFR by the star formation law}.
 The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\tau_\star$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in {\bf star formation mode}).
 The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified.
+
 The SFH is normalized such that the model predicts %an accurate 
@@
 \centering
+\caption{Number of APOGEE stars in each Galactic region.}
+\label{tab:apogee-regions}
+\variable{output/apogee_regions_table.tex}
+\end{table*}
+
+\begin{table*}
+    \centering
     \caption{Median and dispersion in APOGEE parameter uncertainties.}
@@
         \hline
-        [Fe/H]          & $8.9\times10^{-3}$    & $6.0\times10^{-3}$ \\
-        ${\rm [O/Fe]}$        & $1.9\times10^{-2}$    & $3.1\times10^{-2}$ \\
+        [Fe/H]          & $0.0089$   & $0.0060$ \\
+        ${\rm [O/Fe]}$  & $0.019$    & $0.031$ \\
         log(Age/Gyr)    & $0.10$     & $0.16$ \\
@@
 This produces a final sample of \samplesize stars with {\bf calibrated} [O/Fe] and [Fe/H] abundance measurements.
-{\bf APOGEE stars were cross-matched with the {\it Gaia} Early Data Release 3 catalog \citep{Gaia2016-Mission,Gaia2021-EDR3} by the APOGEE team, and we use the \citet{Bailer-Jones2021-GaiaDistances} photo-geometric distance estimates}
+{\bf APOGEE stars were cross-matched with the {\it Gaia} Early Data Release 3 (EDR3) catalog \citep{Gaia2016-Mission,Gaia2021-EDR3} by the APOGEE team using Two Micron All Sky Survey \citep[2MASS;][]{Skrutskie2006-2MASS} identifiers, which were cross-matched with EDR3 by the {\it Gaia} collaboration.
+We use the \citet{Bailer-Jones2021-GaiaDistances} photo-geometric distance estimates}
 % APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use 
@@
 Table \ref{tab:apogee-regions} lists the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$.
-The median distance error exceeds 1 kpc for Galactic regions with $R_{\rm gal}<5$ kpc or $R_{\rm gal}>13$ kpc, but the vast majority of stars have much smaller uncertainties.}
+For Galactic regions with $R_{\rm gal}<5$ kpc or $R_{\rm gal}>13$ kpc, the median distance error exceeds 1 kpc but remains within our bin width of 2 kpc, and the vast majority of stars have much smaller distance uncertainties.}
 
@@
 {\bf Table \ref{tab:uncertainties} presents the median and dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the uncertainty in [Fe/H], [O/Fe], and log(age).}
-
-\begin{table*}
-\centering
-\caption{Number of APOGEE stars in each Galactic region.}
-\label{tab:apogee-regions}
-\variable{output/apogee_regions_table.tex}
-\end{table*}
 
@@
 The MDF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
-{\bf The abundance tracks converge to the same values which reflect the yield ratio of CCSNe to SNe Ia and the asymptotic evolution with nearly quenched star formation at the end of the model.}
+{\bf The abundance tracks converge to the equilibrium value, reflecting the yield ratio of CCSNe to SNe Ia which is the same in all models.}
 
@@
 On the other hand, all of the plateau DTDs produce very similar MDFs.
+
+{\bf The two-population and triple-system models have fixed parameters which are tuned to reproduce specific DTDs from the literature.
+A variant of the two-population DTD with a later, broader Gaussian component ($t_{\rm max}=0.1$ Gyr, $\sigma=0.03$ Gyr) produced similar abundance tracks and a nearly identical [O/Fe] distribution to the fiducial parametrization in a one-zone model.
+The effect of different parameters for the triple-system DTD would be very similar to the plateau DTD described above, of which the triple-system DTD is a special case.}
 
@@
 Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row.
-{\bf A Gaussian scatter with a width equal to the median observational uncertainty in APOGEE DR17 (see Table \ref{tab:sample}) is applied to the abundance of each model stellar population.
+{\bf A Gaussian scatter with a width equal to the median observational uncertainty in APOGEE DR17 (see Table \ref{tab:uncertainties}) is applied to the abundance of each model stellar population.
 For visual clarity,} each MDF is smoothed with a box-car width of 0.2 dex.
@@
 In this case, $P$ is the APOGEE MDF, $Q$ is the model MDF, and $x={\rm [Fe/H]}$.
-{\bf We forward-model the observational uncertainties given in Table \ref{tab:sample} by applying a random Gaussian scatter to the abundance of each model stellar population, and we numerically evaluate Equation \ref{eq:kl-divergence} with integration step size $d{\rm [Fe/H]}=0.01$ dex.}
+{\bf We forward-model the observational uncertainties given in Table \ref{tab:uncertainties} by applying a random Gaussian scatter to the abundance of each model stellar population, and we numerically evaluate Equation \ref{eq:kl-divergence} with integration step size $d{\rm [Fe/H]}=0.01$ dex.}
 % We bin the distributions with a width of 0.01 dex and apply observational uncertainties to our modeled MDFs according to Table \ref{tab:sample}. 
@@
 \end{equation}
-{\bf We also run a two-sample Kolmogorov-Smirnov (KS) test for each region to estimate the significance of the agreement with the observed distributions.
-However, for the best-performing model, we reject the null hypothesis that the model and observed abundances are drawn from the same distribution at very high significance ($p<<0.05$) in each region.}
 
@@
 The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx-0.1$ %which reflects the population-averaged yield ratio of [O/Fe].
-{\bf which reflects the equilibrium [O/Fe] abundance ratio of the second infall.}
+{\bf which reflects the equilibrium abundance ratio of the second infall.}
 
@@
 As before, $P$ is the APOGEE distribution and $Q$ is the model distribution, and in this case $\mathbf{x}=({\rm [Fe/H]}, {\rm [O/Fe]})$.
+{\bf A difference of 1 dex in [Fe/H] contributes the same as 1 dex in [O/Fe]; this metric is acceptable because the range of [Fe/H] is relatively limited for most stars ($-1.5\lesssim {\rm [Fe/H]} \lesssim +0.5$).}
 As in Sections \ref{sec:feh-df} and \ref{sec:ofe-df}, we bin the model outputs and data by $R_{\rm gal}$ and $|z|$, calculate $\hat D_k(P||Q)$ in each region, and then take the weighted mean of each region as in Equation \ref{eq:feh-df-score} to arrive at a single score for each model.
@@
 Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row as labeled in the middle column.
-In all panels stars are limited to the solar annulus ($7\leq R_{\rm gal}<9$ kpc), and the layout of each panel is the same as in Figure \ref{fig:age-ofe-sfh}.}
+In all panels stars are limited to the solar annulus ($7\leq R_{\rm gal}<9$ kpc), and the layout of each panel is the same as in Figure \ref{fig:age-ofe-sfh}.
+{\bf The red numbers in the left-most panels indicate the number of APOGEE stars with \citetalias{Leung2023-Ages} ages in each bin of $|z|$.}}
     \label{fig:age-ofe-dtd}
@@
 
+{\bf We also run a two-sample Kolmogorov-Smirnov (KS) test on the model [Fe/H] and [O/Fe] DFs to estimate the significance of the agreement with the observed distributions.
+However, we consistently reject the null hypothesis that the model and observed abundances are drawn from the same distribution at very high significance ($p<<0.05$) in each Galactic region.
+The large sample size means that even small deviations from the APOGEE distribution result in a very small $p$-value, making the KS test a poor diagnostic for model comparison.
+Overall, this reinforces the conclusion that even our best-performing models cannot reproduce all observations.}
+
 \subsection{The Two-Infall SFH}
@@
 More recently, \citet{Palicio2023-AnalyticDTD} compared a similar suite of DTDs in one-zone models with a two-infall SFH.
-In contrast to previous studies of the two-infall model \citep[e.g.,][]{Chiappini1997-TwoInfall,Matteucci2009-DTDModels,Spitoni2021-TwoInfall}, they do incorporate gas outflows, making their models especially well-suited to compare to ours.
+In contrast to previous studies of the two-infall model \citep[e.g.,][]{Chiappini1997-TwoInfall,Matteucci2009-DTDModels,Spitoni2021-TwoInfall}, they {\bf did} incorporate gas outflows, making their models especially well-suited to compare to ours.
 By modifying their yields, outflow mass-loading factor, and some of the parameters of their SFH, \citet{Palicio2023-AnalyticDTD} were able to achieve a good fit to solar neighborhood abundance data for both the SD and DD analytic DTDs, which are approximated by our exponential ($\tau=1.5$ Gyr) and plateau ($W=1$ Gyr) models, respectively.
@@
 This would not be too far beyond \citeauthor{Maoz2017-CosmicDTD}'s \citeyearpar{Maoz2017-CosmicDTD} finding that field galaxies and galaxy clusters have a different DTD slope.
-However, \citet{Walcher2016-SelfSimilarity} argue that the similarity of the age--\aFe relation between solar neighborhood stars and nearby elliptical galaxies is evidence for a universal DTD.
+However, \citet{Walcher2016-SelfSimilarity} {\bf argued} that the similarity of the age--\aFe relation between solar neighborhood stars and nearby elliptical galaxies is evidence for a universal DTD.
 A physical mechanism would be needed to produce a different slope or form for the DTD in different environments, such as a metallicity dependence in the fraction of close binaries \citep[e.g.,][]{Moe2019-CloseBinaryFraction}.
@@
 However, it does affect the location and strength of the high-$\alpha$ sequence, potentially enhancing the \aFe bimodality resulting from the choice of SFH.
-Radial migration also does not predict the \aFe bimodality on its own, in agreement with \citetalias{Johnson2021-Migration} but in tension with \citet{Sharma2021-RadialMigration} and \citet{Chen2023-RadialMixingRedux}.
+    % Radial migration also does not predict the \aFe bimodality on its own, in agreement with \citetalias{Johnson2021-Migration} but in tension with \citet{Sharma2021-RadialMigration} and \citet{Chen2023-RadialMixingRedux}.
 \end{itemize}
+
+{\bf The origin of the Milky Way's \aFe bimodality is not currently understood.
+\citet{Sharma2021-RadialMigration} and \citet{Chen2023-RadialMixingRedux} showed that a GCE model with a continuous star formation history and radial migration can reproduce the observed abundance distributions.
+Similarly, \citet{Kubryk2015-RadialMigrationEvolution} and \citet{Prantzos2023-ThinThickDisks} argued that radial migration, combined with different SFHs for the inner and outer disk, can explain the \aFe bimodality.
+On the other hand, many studies have argued that the bimodality is instead driven by multiple bursts of gas infall \citep[e.g.,][]{Chiappini1997-TwoInfall,Mackereth2018-AlphaBimodality,Spitoni2019-TwoInfall,Spitoni2020-TwoInfall,Spitoni2021-TwoInfall}.
+We found that radial migration does not predict the \aFe bimodality on its own, in agreement with \citetalias{Johnson2021-Migration}.}
 
@@
 We thank Prof.\ David H.\ Weinberg and attendees of OSU's Galaxy Hour for many useful discussions over the course of this project.
+{\bf We also thank the anonymous reviewer for their thoughtful and constructive comments on the manuscript.}
 
@@
 
+{\bf Here we state our assumptions for the hyper-parameters which can affect the shape of the \citet{Greggio2005-AnalyticalRates} DTDs.
+For the SD case, we assume a power law slope of the mass ratio distribution with $\gamma=1$, an efficiency of mass transfer $\epsilon=1$, and maximum initial primary mass of $8~{\rm M}_\odot$.
+For the DD channel, we additionally assume a nuclear timescale for the least massive secondary $\tau_{\rm n,x}=1$ Gyr, a minimum gravitational insprial delay $\tau_{\rm gw,i}=1$ Myr, an exponent of the power law distribution of final separations $\beta_{\rm a}=0$ (for the WIDE scheme), and an exponent of the power law distribution of gravitational delays $\beta_{\rm g}=-0.75$ (for the CLOSE scheme).}
+
 In the left-hand panel of Figure \ref{fig:analytic-dtds}, we also include simple functions which approximate the analytic DTDs of \citet{Greggio2005-AnalyticalRates}.

### 2024-06-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Table \ref{tab:apogee-regions} lists the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$.
-For Galactic regions with $R_{\rm gal}<5$ kpc or $R_{\rm gal}>13$ kpc, the median distance error exceeds 1 kpc but remains within our bin width of 2 kpc, and the vast majority of stars have much smaller distance uncertainties.}
+For some Galactic regions with $R_{\rm gal}<5$ kpc or $R_{\rm gal}>13$ kpc, the median distance error exceeds 1 kpc but remains within our bin width of 2 kpc, and the vast majority of stars have much smaller distance uncertainties.}
 
@@
 
-{\bf The origin of the Milky Way's \aFe bimodality is not currently understood.
-\citet{Sharma2021-RadialMigration} and \citet{Chen2023-RadialMixingRedux} showed that a GCE model with a continuous star formation history and radial migration can reproduce the observed abundance distributions.
+{\bf The origin of the Milky Way's \aFe bimodality remains disputed.
+Some authors have argued that the combination of inside-out growth and radial migration sufficiently explains the observed distribution \citep[e.g.,][]{Kubryk2015-RadialMigrationEvolution,Sharma2021-RadialMigration,Chen2023-RadialMixingRedux,Prantzos2023-ThinThickDisks}, while others have argued that multiple episodes of gas infall at early times are required \citep[e.g.,][]{Chiappini1997-TwoInfall,Mackereth2018-AlphaBimodality,Spitoni2019-TwoInfall,Spitoni2020-TwoInfall,Spitoni2021-TwoInfall}.
+In agreement with \citetalias{Johnson2021-Migration}, we find that a smooth SFH combined with radial migration does not suffice.
+We find that these parameter choices predict too many stars between the high- and low-$\alpha$ sequences, resulting in a broad but unimodal \aFe distribution at fixed [Fe/H].
+% \citet{Sharma2021-RadialMigration} and \citet{Chen2023-RadialMixingRedux} showed that a GCE model with a continuous star formation history and radial migration can reproduce the observed abundance distributions.
 Similarly, \citet{Kubryk2015-RadialMigrationEvolution} and \citet{Prantzos2023-ThinThickDisks} argued that radial migration, combined with different SFHs for the inner and outer disk, can explain the \aFe bimodality.
 On the other hand, many studies have argued that the bimodality is instead driven by multiple bursts of gas infall \citep[e.g.,][]{Chiappini1997-TwoInfall,Mackereth2018-AlphaBimodality,Spitoni2019-TwoInfall,Spitoni2020-TwoInfall,Spitoni2021-TwoInfall}.
-We found that radial migration does not predict the \aFe bimodality on its own, in agreement with \citetalias{Johnson2021-Migration}.}
+We found that radial migration does not predict the \aFe bimodality on its own, in agreement with \citetalias{Johnson2021-Migration}.
+}
 
@@
 
-% Software acknowledgements if not a AAS journal
-% This work made use of Astropy:\footnote{http://www.astropy.org} a community-developed core Python package and an ecosystem of tools and resources for astronomy \citep{astropy:2013, astropy:2018, astropy:2022}.
-
 \software{\vice \citep{JohnsonWeinberg2020-Starbursts}, Astropy \citep{astropy2013,astropy2018,astropy2022}, scikit-learn \citep{Pedregosa2011-ScikitLearn}, SciPy \citep{2020SciPy-NMeth}, Matplotlib \citep{Hunter2007-Matplotlib}}

### 2024-07-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
+% \documentclass[twocolumn,twocolappendix]{aastex631}
 
@@
 \newcommand{\todo}[1]{{\color{red}#1}}
-\newcommand{\samplesize}{\num{192990}\xspace}
-\newcommand{\agesamplesize}{\num{58987}\xspace}
+% \newcommand{\samplesize}{\num{171635}\xspace}
+% \newcommand{\agesamplesize}{\num{57607}\xspace}
 
@@
 Type Ia supernovae (SNe Ia), the thermonuclear explosions of carbon-oxygen white dwarfs (WDs), are responsible for a majority of the Fe produced in the Galaxy \citep{Matteucci1986-SupernovaEnrichment}; meanwhile, core collapse supernovae (CCSNe), the explosions of massive stars, produce the $\alpha$-elements (e.g., O and Mg) in addition to a smaller fraction of Fe.
-SNe Ia are delayed by $\sim{\bf 0.04}-10$ Gyr after star formation events, as evidenced by observations at large distances from star-forming regions and in elliptical galaxies \citep[e.g.,][]{Maza1976-SNStatistics}.
+SNe Ia are delayed by $\sim{\bf 0.04}-10$ Gyr after star formation events, as evidenced by observations {\bf in both star-forming and} elliptical galaxies \citep[e.g.,][]{Maza1976-SNStatistics}.
 This delayed enrichment leads to a decrease in \aFe with increasing [Fe/H] \citep{Matteucci1986-SupernovaEnrichment}.
@@
 
-% [Introduction to SNe Ia]
 The explosion mechanism(s) of SNe Ia are not fully understood \citep[for reviews, see][]{Maoz2014-Review,Livio2018-ProgenitorReview,Ruiter2020-ProgenitorReview,Liu2023-SNIaBinaryReview}.
@@
 {\bf In this subsection, we present functional forms of each DTD in terms of a function $f_{\rm Ia}$ that has units of ${\rm Gyr}^{-1}$ and defines the shape of the DTD for $t\ge t_D$ as}
-% describing the shape of each DTD. $f_{\rm Ia}$ does not include the normalization, so it has units of Gyr$^{-1}$ as opposed to M$_\odot^{-1}$ Gyr$^{-1}$ and is related to $R_{\rm Ia}$ according to
 \begin{equation}
@@
 {\bf Note that the denominator in Equation \ref{eq:dtd-function} normalizes the DTD.}
-% \vice automatically normalizes the provided function for the DTD according to this equation.
-% In the remainder of this subsection, we discuss each form of $f_{\rm Ia}$ individually.
 
@@
 \citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assumed an exponential DTD with a timescale $\tau=1.5$ Gyr.
-We show in Appendix \ref{app:analytic-dtds} that this is an adequate approximation for the analytic SD DTD from \citet{Greggio2005-AnalyticalRates}.
-However, there is less observational support for an exponential DTD.
+However, observational support for an exponential DTD {\bf is scarce}.
 \citet{Strolger2020-ExponentialDTD}, fitting to the cosmic SFH and SFHs from field galaxies, found a range of exponential-like solutions with timescales $\sim 1.5 - 6$ Gyr.
 In this paper, we investigate timescales $\tau=1.5$ and 3 Gyr.
+{\bf We show in Appendix \ref{app:analytic-dtds} that an exponential DTD with $\tau=1.5$ Gyr is an adequate approximation for the analytic SD DTD from \citet{Greggio2005-AnalyticalRates}.}
 
@@
 Our primary motivation is to consider a model which matches observations at delay times beyond a few Gyr, where the DTD is best constrained, but with a smaller fraction of prompt ($\lesssim 100$ Myr) SNe Ia than the single power law.
-{\bf This form has been used for the DTD of neutron star mergers \citep{Simonetti2019-NeutronStarDTD}, but to our knowledge it has not been considered for SNe Ia in previous GCE models.}
-% To our knowledge, this form of the DTD has not been considered in previous GCE models. 
-We show in Appendix \ref{app:analytic-dtds} that this form can approximate the more complicated analytic DD DTDs from \citet{Greggio2005-AnalyticalRates}.
+{\bf This form has been used for the DTD of neutron star mergers \citep{Simonetti2019-NeutronStarDTD}, but to our knowledge it has not been considered for SNe Ia in previous GCE models.} We show in Appendix \ref{app:analytic-dtds} that this form can approximate the more complicated analytic DD DTDs from \citet{Greggio2005-AnalyticalRates}.
 We investigate the cases $W=0.3$ Gyr and $W=1$ Gyr, taking $\alpha=-1.1$ for all plateau models.
@@
 {\bf There are many models for the DTD which have been proposed in the literature, and an exhaustive test of every one is infeasible.
-In particular, we do not consider a Gaussian DTD \citep[e.g.,][]{Strolger2004-SNIaProgenitors}, in which most SNe Ia explode with delay times close to $\sim 3$ Gyr.
+In particular, we do not consider a Gaussian DTD \citep[e.g.,][]{Strolger2004-SNIaProgenitors}, in which most SNe Ia explode with delay times close to $\sim 3$ Gyr and there are very few prompt events.
 Evidence for this form came from SN Ia rate measurements for $z>1$, but re-analysis of the data revealed large errors due to the small sample size, extinction corrections, and uncertainties in the SFHs \citep[e.g.,][]{Forster2006-SNIaConstraints,Greggio2008-CosmicMix}.
-Additionally, \citet{Mannucci2006-TwoPopulations} found that such a DTD fails to reproduce the observed dependence of the SN Ia rate on galaxy color and radio power.
-Previous GCE studies have found that a Gaussian DTD over-produces high-[O/Fe] and low-[Fe/H] stars \citep{Matteucci2009-DTDModels,Palicio2023-AnalyticDTD}.}
+Additionally, \citet{Mannucci2006-TwoPopulations} found that such a DTD fails to reproduce the observed dependence of the SN Ia rate on galaxy color, and there is evidence that at least some SNe Ia must be prompt in order to explain observed rates in spiral galaxies \citep[e.g.,][]{Mannucci2005-SNRate,ScannapiecoBildsten2005-SNIaRate}.
+GCE studies have found that a Gaussian DTD over-produces high-[O/Fe] and low-[Fe/H] stars \citep{Matteucci2009-DTDModels,Palicio2023-AnalyticDTD}.}
 
@@
 More specifically, at each timestep the infall rate is calculated to fulfill the quantity of gas required to produce the specified SFR by the star formation law}.
-The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\tau_\star$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in {\bf star formation mode}).
-The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified.
-
-The SFH is normalized such that the model predicts %an accurate 
-{\bf a total stellar mass of $(5.17\pm1.11)\times10^{10} M_\odot$ \citep{LicquiaNewman2015-StellarMass} and the stellar surface density gradient reported by \citet[][see Appendix B of \citetalias{Johnson2021-Migration}]{BlandHawthornGerhard2016-MilkyWayReview}}.
+The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$ {\bf and} $\tau_\star$.
+{\bf The initial gas mass is zero for all models (including those run in star formation mode).} The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified.
+
+The SFH is normalized such that the model predicts {\bf a total stellar mass of $(5.17\pm1.11)\times10^{10} M_\odot$ \citep{LicquiaNewman2015-StellarMass} and the stellar surface density gradient reported by \citet[][see Appendix B of \citetalias{Johnson2021-Migration}]{BlandHawthornGerhard2016-MilkyWayReview}}.
 We present an overview of the four SFHs in Figure \ref{fig:sfhs}, and we discuss them individually here.
@@
 {\bf The values of $\tau_{\rm rise}$ and $\tau_{\rm sfh}(R_{\rm gal})$ are the same as in the inside-out case.}
-% The determination of $\tau_{\rm sfh}$ is the same as in the inside-out case.
 
@@
         Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{Leung2023-Ages} \\
-        % {\bf
-        \bf $R_{\rm gal}$   & $3 < R_{\rm gal} < 15$ kpc    & Eliminate bulge \& extreme outer-disk stars \\
+        $R_{\rm gal}$     & $3 < R_{\rm gal} < 15$ kpc    & Eliminate bulge \& extreme outer-disk stars \\
         $|z|$               & $|z| < 2$ kpc                 & Eliminate halo stars \\
-        % }
         \hline
-        % $\sigma({\rm [Fe/H]})$ & $9.2\times10^{-3}$ & Median uncertainty in [Fe/H] \\
-        % $\sigma({\rm [O/Fe]})$ & $1.8\times10^{-2}$ & Median uncertainty in [O/Fe] \\
-        % $\sigma($log(Age/Gyr)) & $0.10$ & Median age uncertainty \citepalias{Leung2023-Ages} \\
-        % \hline
     \end{tabular}
@@
 Table \ref{tab:sample} lists our selection criteria, which largely follow from \citet{Hayden2015-ChemicalCartography}.
-This produces a final sample of \samplesize stars with {\bf calibrated} [O/Fe] and [Fe/H] abundance measurements.
-{\bf APOGEE stars were cross-matched with the {\it Gaia} Early Data Release 3 (EDR3) catalog \citep{Gaia2016-Mission,Gaia2021-EDR3} by the APOGEE team using Two Micron All Sky Survey \citep[2MASS;][]{Skrutskie2006-2MASS} identifiers, which were cross-matched with EDR3 by the {\it Gaia} collaboration.
-We use the \citet{Bailer-Jones2021-GaiaDistances} photo-geometric distance estimates}
-% APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use 
-to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$, {\bf assuming a Sun--Galactic center distance $R_\odot=8.122$ kpc and height of the Sun above the midplane $z_\odot=20.8$ pc.
+This produces a final sample of \variable{output/sample_size.txt} stars with {\bf calibrated} [O/Fe] and [Fe/H] abundance measurements.
+{\bf We make use of the {\it Gaia} Early Data Release 3 (EDR3) data \citep{Gaia2016-Mission,Gaia2021-EDR3} included in the catalog by the APOGEE team.
+Specifically, we use the \citet{Bailer-Jones2021-GaiaDistances} photo-geometric distance estimates} to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$, {\bf assuming a Sun--Galactic center distance $R_\odot=8.122$ kpc \citep{GRAVITY2018-GalactocentricDistance} and height of the Sun above the midplane $z_\odot=20.8$ pc \citep{BennetBovy2019-SunZHeight}.
 Table \ref{tab:apogee-regions} lists the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$.
@@
 Importantly, the \citetalias{Leung2023-Ages} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{Mackereth2019-astroNN-Ages}.
-We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \agesamplesize APOGEE stars with age estimates.
-We note that we use the full sample of \samplesize APOGEE stars unless we explicitly compare to age estimates.
+We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt} APOGEE stars with age estimates.
+We note that we use the full sample of \variable{output/sample_size.txt} APOGEE stars unless we explicitly compare to age estimates.
 {\bf Table \ref{tab:uncertainties} presents the median and dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the uncertainty in [Fe/H], [O/Fe], and log(age).}
@@
 Doubling the timescale from 1.5 Gyr to 3 Gyr {\bf implies a longer median delay time, which} raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex.
-% but the equilibrium abundance reached at $t=10$ Gyr remains unchanged. 
 A longer exponential timescale also produces a broader [O/Fe] DF with more high-$\alpha$ stars, but the distribution is still unimodal.
@@
 
-{\bf The two-population and triple-system models have fixed parameters which are tuned to reproduce specific DTDs from the literature.
-A variant of the two-population DTD with a later, broader Gaussian component ($t_{\rm max}=0.1$ Gyr, $\sigma=0.03$ Gyr) produced similar abundance tracks and a nearly identical [O/Fe] distribution to the fiducial parametrization in a one-zone model.
+{\bf Unlike the previous three DTDs, we fix the hyper-parameters of the two-population and triple-system models to reproduce specific DTDs from the literature.
+A variant of the two-population DTD with a broader Gaussian component ($t_{\rm max}=0.1$ Gyr, $\sigma=0.03$ Gyr) produced similar abundance tracks and a nearly identical [O/Fe] distribution to the fiducial parametrization in a one-zone model.
 The effect of different parameters for the triple-system DTD would be very similar to the plateau DTD described above, of which the triple-system DTD is a special case.}
@@
 At the other extreme are the two-population and power-law ($\alpha=-1.1$) DTDs, for which the SN Ia rate peaks immediately after the minimum delay time of 40 Myr, placing the high-$\alpha$ knee at ${\rm [Fe/H]}\approx-1.8$.
-The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is produced by the delayed exponential component, {\bf as observed by \citet{Vincenzo2017-ChemicalEvolution}}.
+The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is produced by the delayed exponential component, {\bf as noted by \citet{Vincenzo2017-ChemicalEvolution}}.
 The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models occupy the intermediate space between these extremes.
@@
 {\bf We forward-model the observational uncertainties given in Table \ref{tab:uncertainties} by applying a random Gaussian scatter to the abundance of each model stellar population, and we numerically evaluate Equation \ref{eq:kl-divergence} with integration step size $d{\rm [Fe/H]}=0.01$ dex.}
-% We bin the distributions with a width of 0.01 dex and apply observational uncertainties to our modeled MDFs according to Table \ref{tab:sample}. 
 For each SFH and DTD, we compute $D_{\rm{KL}}$ in the 18 different {\bf Galactic} regions shown in Figure \ref{fig:feh-df-comparison}.
 We use bins in $R_{\rm gal}$ with a width of 2 kpc between 3 and 15 kpc, and bins in midplane distance of $|z|=0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
-The score $S$ for the entire model is taken to be the average of $D_{\rm{KL}}$ for each region $\bf (R_{\rm gal}, |z|)$
-% $R,z\equiv(R_{\rm gal}\in(R_{\rm min}, R_{\rm max}),|z|\in(z_{\rm min}, z_{\rm max}))$
-weighted by the number of APOGEE stars in that region $\bf N_\star(R_{\rm gal}, |z|)$ {\bf (see Table \ref{tab:apogee-regions})}:
+The score $S$ for the entire model is taken to be the average of $D_{\rm{KL}}$ for each region $\bf (R_{\rm gal}, |z|)$ weighted by the number of APOGEE stars in that region $\bf N_\star(R_{\rm gal}, |z|)$ {\bf (see Table \ref{tab:apogee-regions})}:
 \begin{equation}
@@
 This ridge roughly coincides with the upper limit of the APOGEE distribution near the midplane.
-The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx-0.1$ %which reflects the population-averaged yield ratio of [O/Fe].
-{\bf which reflects the equilibrium abundance ratio of the second infall.}
+The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx-0.1${\bf which reflects the equilibrium abundance ratio of the second infall.}
 
@@
 
-% The DTDs with an intermediate median delay time do well at reproducing the observed abundance distributions.
 The exponential ($\tau=1.5$ Gyr) DTD, {\bf which has an intermediate median delay time,} produces a distribution in Figure \ref{fig:ofe-feh-dtd} which aligns quite well with the 80\% APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to high [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
@@
 We take $k=2$ to find the nearest neighbor other than the sample itself.
-As before, $P$ is the APOGEE distribution and $Q$ is the model distribution, and in this case $\mathbf{x}=({\rm [Fe/H]}, {\rm [O/Fe]})$.
-{\bf A difference of 1 dex in [Fe/H] contributes the same as 1 dex in [O/Fe]; this metric is acceptable because the range of [Fe/H] is relatively limited for most stars ($-1.5\lesssim {\rm [Fe/H]} \lesssim +0.5$).}
+As before, $P$ is the APOGEE distribution and $Q$ is the model distribution, and in this case $\mathbf{x}=({\rm [Fe/H]}, {\rm [O/Fe]})$, {\bf without applying any scaling factor to each dimension.}
 As in Sections \ref{sec:feh-df} and \ref{sec:ofe-df}, we bin the model outputs and data by $R_{\rm gal}$ and $|z|$, calculate $\hat D_k(P||Q)$ in each region, and then take the weighted mean of each region as in Equation \ref{eq:feh-df-score} to arrive at a single score for each model.
@@
 
+\begin{table*}
+\centering
+\caption{Qualitative summary of comparisons between the model output,
+APOGEE DR17 abundances, and \citetalias{Leung2023-Ages} ages for each multi-zone
+model. See discussion in Section \ref{sec:feh-df} for the [Fe/H] DF, 
+Section \ref{sec:ofe-df} for the [O/Fe] DF, Section \ref{sec:bimodality} for
+the [O/Fe] bimodality, Section \ref{sec:ofe-feh} for the [O/Fe]--[Fe/H] plane,
+and Section \ref{sec:age-ofe} for the age--[O/Fe] plane. Table \ref{tab:scores}
+presents the quantitative scores used to make these comparisons.}
+\label{tab:results}
 \variable{output/summary_table.tex}
-\vspace{-24pt}
+\end{table*}
 
@@
 
-% The diagnostic scores for each model are presented in Table \ref{tab:results}. 
 {\bf The relative performance of each model is summarized in Table \ref{tab:results}.} We use these scores to indicate combinations of SFH and DTD that are favorable or unfavorable in certain regimes, but we do {\it not} fit our models to the data due to computational expense.
@@
 However, it does affect the location and strength of the high-$\alpha$ sequence, potentially enhancing the \aFe bimodality resulting from the choice of SFH.
-    % Radial migration also does not predict the \aFe bimodality on its own, in agreement with \citetalias{Johnson2021-Migration} but in tension with \citet{Sharma2021-RadialMigration} and \citet{Chen2023-RadialMixingRedux}.
 \end{itemize}
@@
 In agreement with \citetalias{Johnson2021-Migration}, we find that a smooth SFH combined with radial migration does not suffice.
-We find that these parameter choices predict too many stars between the high- and low-$\alpha$ sequences, resulting in a broad but unimodal \aFe distribution at fixed [Fe/H].
-% \citet{Sharma2021-RadialMigration} and \citet{Chen2023-RadialMixingRedux} showed that a GCE model with a continuous star formation history and radial migration can reproduce the observed abundance distributions.
-Similarly, \citet{Kubryk2015-RadialMigrationEvolution} and \citet{Prantzos2023-ThinThickDisks} argued that radial migration, combined with different SFHs for the inner and outer disk, can explain the \aFe bimodality.
-On the other hand, many studies have argued that the bimodality is instead driven by multiple bursts of gas infall \citep[e.g.,][]{Chiappini1997-TwoInfall,Mackereth2018-AlphaBimodality,Spitoni2019-TwoInfall,Spitoni2020-TwoInfall,Spitoni2021-TwoInfall}.
-We found that radial migration does not predict the \aFe bimodality on its own, in agreement with \citetalias{Johnson2021-Migration}.
-}
-
-% Future work
+We find that these parameter choices predict too many stars between the high- and low-$\alpha$ sequences, resulting in a broad but unimodal \aFe distribution at fixed [Fe/H].}
+
 We found that the MDF is least able to provide constraints on the DTD.
@@
 However, the MDF is more sensitive to the DTD in the inner Galaxy due to the more sharply declining SFH (see discussion in Section \ref{sec:feh-df}).
-%, so improved measurements of the MDF in the inner disk by, e.g., SDSS-V \citep{Kollmeier2017-SDSS-V} could help constrain the DTD.
 {\bf Under the model of inside-out formation, the MDF in the inner Galaxy traces older populations which are more sensitive to the enrichment of prompt SNe Ia.}
@@
 repository associated to this study is publicly available at
-\url{\GitHubURL}, and the release v1.0.0 allows anyone to re-build the entire 
-manuscript. The multi-zone model outputs and APOGEE sample dataset are stored at \url{https://doi.org/10.5281/zenodo.10961091}.
+\url{\GitHubURL}, and the release v1.1.1 allows anyone to re-build the entire 
+manuscript.
+The multi-zone model outputs and APOGEE sample dataset are stored at \url{https://zenodo.org/doi/10.5281/zenodo.10961090}, {\bf and the source code for this manuscript is stored at \url{https://zenodo.org/doi/10.5281/zenodo.12521399}}.
 
@@
 
+\begin{table*}
+\centering
+\caption{Quantitative scores comparing the model output,
+APOGEE DR17 abundances, and \citetalias{Leung2023-Ages} ages for each multi-zone
+model. See discussion in Section \ref{sec:feh-df} for the [Fe/H] DF, 
+Section \ref{sec:ofe-df} for the [O/Fe] DF, Section \ref{sec:ofe-feh} for the 
+[O/Fe]--[Fe/H] plane, and Section \ref{sec:age-ofe} for the age--[O/Fe] 
+plane. Table \ref{tab:results} summarizes the relative performance
+of each model based on the scores presented here.}
+\label{tab:scores}
 \variable{output/scores_table.tex}
-\vspace{-24pt}
+\end{table*}
 

### 2024-07-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
-% \documentclass[twocolumn,twocolappendix]{aastex631}
+\documentclass[twocolumn,twocolappendix]{aastex631}
 
@@
 Type Ia supernovae (SNe Ia), the thermonuclear explosions of carbon-oxygen white dwarfs (WDs), are responsible for a majority of the Fe produced in the Galaxy \citep{Matteucci1986-SupernovaEnrichment}; meanwhile, core collapse supernovae (CCSNe), the explosions of massive stars, produce the $\alpha$-elements (e.g., O and Mg) in addition to a smaller fraction of Fe.
-SNe Ia are delayed by $\sim{\bf 0.04}-10$ Gyr after star formation events, as evidenced by observations {\bf in both star-forming and} elliptical galaxies \citep[e.g.,][]{Maza1976-SNStatistics}.
+SNe Ia are delayed by $\sim 0.04-10$ Gyr after star formation events, as evidenced by observations in both star-forming and elliptical galaxies \citep[e.g.,][]{Maza1976-SNStatistics}.
 This delayed enrichment leads to a decrease in \aFe with increasing [Fe/H] \citep{Matteucci1986-SupernovaEnrichment}.
@@
 As a result of the uncertainty regarding SN Ia progenitors, theoretical models have yet to converge on a single prediction for the DTD.
-For the DD channel, assumptions about the distribution of {\bf WD} separations and the rate of gravitational wave inspiral suggest a broad $\sim t^{-1}$ DTD at long delay times ($\gtrsim 1$ Gyr), but at short delays ($\lesssim 1$ Gyr) the rate is limited by the need to produce two WDs {\bf \citep[see][]{Greggio2005-AnalyticalRates,Maoz2014-Review}}.
+For the DD channel, assumptions about the distribution of WD separations and the rate of gravitational wave inspiral suggest a broad $\sim t^{-1}$ DTD at long delay times ($\gtrsim 1$ Gyr), but at short delays ($\lesssim 1$ Gyr) the rate is limited by the need to produce two WDs \citep[see][]{Greggio2005-AnalyticalRates,Maoz2014-Review}.
 Triple or higher-order progenitor systems could also produce a $t^{-1}$ DTD \citep{Fang2018-QuadrupleSystems,Rajamuthukumar2023-TripleEvolution}.
@@
 Early studies, which had limited sample sizes, produced unimodal \citep{Strolger2004-SNIaProgenitors} or bimodal \citep{Mannucci2006-TwoPopulations} DTDs where the majority of SNe Ia explode within a relatively narrow range of delay times.
-More recent studies have recovered broader DTD functions, with many converging on a declining power-law of $\sim t^{-1}$ {\bf \citep[e.g.,][]{Graur2013-IaRateVsMass,Graur2015-UnifiedExplanation,Maoz2017-CosmicDTD,Castrillo2021-DTD,Wiseman2021-DESRates}}, though there is some evidence for a steeper slope in galaxy clusters \citep{Maoz2017-CosmicDTD,FriedmannMaoz2018-ClusterDTD}.
-It is especially difficult to constrain the DTD for short delay times {\bf \citep{MaozMannucci2012-SNeIaReview,Rodney2014-PromptSNeIa}} because of the need for SN Ia rates at long lookback times and uncertainties in the age estimates of stellar populations.
+More recent studies have recovered broader DTD functions, with many converging on a declining power-law of $\sim t^{-1}$ \citep[e.g.,][]{Graur2013-IaRateVsMass,Graur2015-UnifiedExplanation,Maoz2017-CosmicDTD,Castrillo2021-DTD,Wiseman2021-DESRates}, though there is some evidence for a steeper slope in galaxy clusters \citep{Maoz2017-CosmicDTD,FriedmannMaoz2018-ClusterDTD}.
+It is especially difficult to constrain the DTD for short delay times \citep{MaozMannucci2012-SNeIaReview,Rodney2014-PromptSNeIa} because of the need for SN Ia rates at long lookback times and uncertainties in the age estimates of stellar populations.
 
@@
 A few studies have investigated different DTDs in one-zone chemical evolution models, but comparisons to abundance data have been limited to the solar neighborhood \citep[e.g.,][]{Andrews2017-ChemicalEvolution,Palicio2023-AnalyticDTD}.
-\citet{Matteucci2009-DTDModels} compared five DTDs in a multi-zone GCE model and found that the agreement with observations worsens if the fraction of prompt {\bf ($\bf t\lesssim 100$ Myr)} SNe Ia is either too high or too low, but they were similarly limited by the available data for the solar neighborhood.
+\citet{Matteucci2009-DTDModels} compared five DTDs in a multi-zone GCE model and found that the agreement with observations worsens if the fraction of prompt ($t\lesssim 100$ Myr) SNe Ia is either too high or too low, but they were similarly limited by the available data for the solar neighborhood.
 \citet{Poulhazan2018-PrecisionPollution} found that the prompt component of the DTD affects the peak and width of the \aFe distribution in a cosmological smoothed-particle hydrodynamics simulation, but their simulation was not designed to reproduce the parameters of the Milky Way.
@@
 \begin{equation}
-    \dot M_x^{\rm CC}{\bf (t)} = y_x^{\rm CC} \dot M_\star{\bf (t)}
+    \dot M_x^{\rm CC}(t) = y_x^{\rm CC} \dot M_\star(t)
     \label{eq:ccsn-enrichment}
@@
 \begin{equation}
-    \dot M_{\rm Fe}^{\rm Ia}{\bf (t)} = y_{\rm Fe}^{\rm Ia} \langle \dot M_\star\rangle_{\rm Ia} {\bf (t)}\\
-\end{equation}
-where $\langle \dot M_\star\rangle_{\rm Ia}{\bf (t)}$ is the time-averaged SFR weighted by the DTD {\bf at time $t$} and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia.
+    \dot M_{\rm Fe}^{\rm Ia}(t) = y_{\rm Fe}^{\rm Ia} \langle \dot M_\star\rangle_{\rm Ia}(t)\\
+\end{equation}
+where $\langle \dot M_\star\rangle_{\rm Ia}(t)$ is the time-averaged SFR weighted by the DTD at time $t$ and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia.
 \citet{Weinberg2017-ChemicalEquilibrium} show in their Appendix A that
@@
 This yield is originally adapted from the W70 model of \citet{Iwamoto1999-SNIaYields}, but it is increased slightly so that the inside-out SFH produces stars with ${\rm [O/Fe]}\approx 0.0$ by the end of the model.
-{\bf The overall scale of the yields is inconsequential: a lower value of $y_{\rm Fe}^{\rm Ia}$ would produce similar results if compensated with a lower outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_\star$ (this is the yield-outflow degeneracy; see \citealt{Weinberg2023-CCSNYield}, \citealt{Sandford2024-StrongOutflows}, and appendix B of \citealt{Johnson2023-DwarfGalaxyArchaeology}).} \citet{Palla2021-SNIaYield} studied the effect of different SN Ia yields on GCE models in detail.
+The overall scale of the yields is inconsequential: a lower value of $y_{\rm Fe}^{\rm Ia}$ would produce similar results if compensated with a lower outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_\star$ (this is the yield-outflow degeneracy; see \citealt{Weinberg2023-CCSNYield}, \citealt{Sandford2024-StrongOutflows}, and appendix B of \citealt{Johnson2023-DwarfGalaxyArchaeology}).
+\citet{Palla2021-SNIaYield} studied the effect of different SN Ia yields on GCE models in detail.
 
@@
 We also investigate one or two useful variations of the input parameters for each functional form.
-Figure \ref{fig:dtds} presents a selection of these DTDs, and Table \ref{tab:dtds} summarizes {\bf the parameters and median delay times ($t_{\rm med}$) for all of our DTDs}.
+Figure \ref{fig:dtds} presents a selection of these DTDs, and Table \ref{tab:dtds} summarizes the parameters and median delay times ($t_{\rm med}$) for all of our DTDs.
 We use simple forms rather than simulated physical or analytic models of SNe Ia for the sake of decreased computational time and easier interpretation of the model predictions.
@@
 
-{\bf In this subsection, we present functional forms of each DTD in terms of a function $f_{\rm Ia}$ that has units of ${\rm Gyr}^{-1}$ and defines the shape of the DTD for $t\ge t_D$ as}
+In this subsection, we present functional forms of each DTD in terms of a function $f_{\rm Ia}$ that has units of ${\rm Gyr}^{-1}$ and defines the shape of the DTD for $t\ge t_D$ as
 \begin{equation}
@@
 \end{equation}
-{\bf Note that the denominator in Equation \ref{eq:dtd-function} normalizes the DTD.}
+Note that the denominator in Equation \ref{eq:dtd-function} normalizes the DTD.
 
@@
 \end{equation}
-A declining power-law with $\alpha\sim-1$ {\bf \citep{Totani2008-DTD}} arises from typical assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral \citep[see Section 3.5 from][]{Maoz2014-Review}.
+A declining power-law with $\alpha\sim-1$ \citep{Totani2008-DTD} arises from typical assumptions about the distribution of post-common envelope separations and the rate of gravitational wave inspiral \citep[see Section 3.5 from][]{Maoz2014-Review}.
 It is therefore a commonly assumed DTD in GCE studies (e.g., \citealt{Rybizki2017-Chempy}; \citetalias{Johnson2021-Migration}; \citealt{Weinberg2023-CCSNYield}).
@@
 \citet{Wiseman2021-DESRates} obtained a similar slope of $\alpha=-1.13\pm0.05$ for field galaxies in the redshift range $0.2<z<0.6$.
-{\bf \citet{Heringer2019-FieldGalaxyDTD} used a SFH-independent method to constrain the DTD for field galaxies within $0.01<z<0.2$ and found a larger value of $\alpha=-1.34^{+0.19}_{-0.17}$.} For galaxy clusters, \citet{Maoz2017-CosmicDTD} found a steeper DTD slope of $\alpha=-1.39^{+0.32}_{-0.05}$, {\bf and \citet{FriedmannMaoz2018-ClusterDTD} found a similar slope of $\alpha=-1.3^{+0.23}_{-0.16}$; however, a re-analysis by \citet{FreundlichMaoz2021-ClusterDTD} revealed no significant difference between the cluster and field galaxy DTDs}.
+\citet{Heringer2019-FieldGalaxyDTD} used a SFH-independent method to constrain the DTD for field galaxies within $0.01<z<0.2$ and found a larger value of $\alpha=-1.34^{+0.19}_{-0.17}$.
+For galaxy clusters, \citet{Maoz2017-CosmicDTD} found a steeper DTD slope of $\alpha=-1.39^{+0.32}_{-0.05}$, and \citet{FriedmannMaoz2018-ClusterDTD} found a similar slope of $\alpha=-1.3^{+0.23}_{-0.16}$; however, a re-analysis by \citet{FreundlichMaoz2021-ClusterDTD} revealed no significant difference between the cluster and field galaxy DTDs.
 In this paper, we investigate the cases $\alpha=-1.1$ and $\alpha=-1.4$.
@@
 \end{equation}
-This model allows analytic solutions to the abundances as a function of time for some SFHs, making it a popular choice {\bf \citep[e.g.,][]{Weinberg2017-ChemicalEquilibrium,Pantoni2019-AnalyticSolutions,Palicio2023-AnalyticDTD}}.
+This model allows analytic solutions to the abundances as a function of time for some SFHs, making it a popular choice \citep[e.g.,][]{Weinberg2017-ChemicalEquilibrium,Pantoni2019-AnalyticSolutions,Palicio2023-AnalyticDTD}.
 \citet{Schonrich2009-RadialMixing} and \citet{Weinberg2017-ChemicalEquilibrium} both assumed an exponential DTD with a timescale $\tau=1.5$ Gyr.
-However, observational support for an exponential DTD {\bf is scarce}.
+However, observational support for an exponential DTD is scarce.
 \citet{Strolger2020-ExponentialDTD}, fitting to the cosmic SFH and SFHs from field galaxies, found a range of exponential-like solutions with timescales $\sim 1.5 - 6$ Gyr.
 In this paper, we investigate timescales $\tau=1.5$ and 3 Gyr.
-{\bf We show in Appendix \ref{app:analytic-dtds} that an exponential DTD with $\tau=1.5$ Gyr is an adequate approximation for the analytic SD DTD from \citet{Greggio2005-AnalyticalRates}.}
+We show in Appendix \ref{app:analytic-dtds} that an exponential DTD with $\tau=1.5$ Gyr is an adequate approximation for the analytic SD DTD from \citet{Greggio2005-AnalyticalRates}.
 
@@
 Our primary motivation is to consider a model which matches observations at delay times beyond a few Gyr, where the DTD is best constrained, but with a smaller fraction of prompt ($\lesssim 100$ Myr) SNe Ia than the single power law.
-{\bf This form has been used for the DTD of neutron star mergers \citep{Simonetti2019-NeutronStarDTD}, but to our knowledge it has not been considered for SNe Ia in previous GCE models.} We show in Appendix \ref{app:analytic-dtds} that this form can approximate the more complicated analytic DD DTDs from \citet{Greggio2005-AnalyticalRates}.
+This form has been used for the DTD of neutron star mergers \citep{Simonetti2019-NeutronStarDTD}, but to our knowledge it has not been considered for SNe Ia in previous GCE models.
+We show in Appendix \ref{app:analytic-dtds} that this form can approximate the more complicated analytic DD DTDs from \citet{Greggio2005-AnalyticalRates}.
 We investigate the cases $W=0.3$ Gyr and $W=1$ Gyr, taking $\alpha=-1.1$ for all plateau models.
@@
 
-{\bf There are many models for the DTD which have been proposed in the literature, and an exhaustive test of every one is infeasible.
+There are many models for the DTD which have been proposed in the literature, and an exhaustive test of every one is infeasible.
 In particular, we do not consider a Gaussian DTD \citep[e.g.,][]{Strolger2004-SNIaProgenitors}, in which most SNe Ia explode with delay times close to $\sim 3$ Gyr and there are very few prompt events.
@@
 Additionally, \citet{Mannucci2006-TwoPopulations} found that such a DTD fails to reproduce the observed dependence of the SN Ia rate on galaxy color, and there is evidence that at least some SNe Ia must be prompt in order to explain observed rates in spiral galaxies \citep[e.g.,][]{Mannucci2005-SNRate,ScannapiecoBildsten2005-SNIaRate}.
-GCE studies have found that a Gaussian DTD over-produces high-[O/Fe] and low-[Fe/H] stars \citep{Matteucci2009-DTDModels,Palicio2023-AnalyticDTD}.}
+GCE studies have found that a Gaussian DTD over-produces high-[O/Fe] and low-[Fe/H] stars \citep{Matteucci2009-DTDModels,Palicio2023-AnalyticDTD}.
 
@@
 The inside-out and late-burst models are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_\star$ is prescribed along with the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g/\dot\Sigma_\star$.
-The remaining quantities, infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities {\bf assuming the star formation law adopted by \citetalias{Johnson2021-Migration} (see their Equation 14).
-More specifically, at each timestep the infall rate is calculated to fulfill the quantity of gas required to produce the specified SFR by the star formation law}.
-The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$ {\bf and} $\tau_\star$.
-{\bf The initial gas mass is zero for all models (including those run in star formation mode).} The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified.
-
-The SFH is normalized such that the model predicts {\bf a total stellar mass of $(5.17\pm1.11)\times10^{10} M_\odot$ \citep{LicquiaNewman2015-StellarMass} and the stellar surface density gradient reported by \citet[][see Appendix B of \citetalias{Johnson2021-Migration}]{BlandHawthornGerhard2016-MilkyWayReview}}.
+The remaining quantities, infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities assuming the star formation law adopted by \citetalias{Johnson2021-Migration} (see their Equation 14).
+More specifically, at each timestep the infall rate is calculated to fulfill the quantity of gas required to produce the specified SFR by the star formation law.
+The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$ and $\tau_\star$.
+The initial gas mass is zero for all models (including those run in star formation mode).
+The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified.
+
+The SFH is normalized such that the model predicts a total stellar mass of $(5.17\pm1.11)\times10^{10} M_\odot$ \citep{LicquiaNewman2015-StellarMass} and the stellar surface density gradient reported by \citet[][see Appendix B of \citetalias{Johnson2021-Migration}]{BlandHawthornGerhard2016-MilkyWayReview}.
 We present an overview of the four SFHs in Figure \ref{fig:sfhs}, and we discuss them individually here.
@@
 Following \citetalias{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr.
-{\bf The values of $\tau_{\rm rise}$ and $\tau_{\rm sfh}(R_{\rm gal})$ are the same as in the inside-out case.}
+The values of $\tau_{\rm rise}$ and $\tau_{\rm sfh}(R_{\rm gal})$ are the same as in the inside-out case.
 
@@
 Table \ref{tab:sample} lists our selection criteria, which largely follow from \citet{Hayden2015-ChemicalCartography}.
-This produces a final sample of \variable{output/sample_size.txt} stars with {\bf calibrated} [O/Fe] and [Fe/H] abundance measurements.
-{\bf We make use of the {\it Gaia} Early Data Release 3 (EDR3) data \citep{Gaia2016-Mission,Gaia2021-EDR3} included in the catalog by the APOGEE team.
-Specifically, we use the \citet{Bailer-Jones2021-GaiaDistances} photo-geometric distance estimates} to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$, {\bf assuming a Sun--Galactic center distance $R_\odot=8.122$ kpc \citep{GRAVITY2018-GalactocentricDistance} and height of the Sun above the midplane $z_\odot=20.8$ pc \citep{BennetBovy2019-SunZHeight}.
+This produces a final sample of \variable{output/sample_size.txt} stars with calibrated [O/Fe] and [Fe/H] abundance measurements.
+We make use of the {\it Gaia} Early Data Release 3 (EDR3) data \citep{Gaia2016-Mission,Gaia2021-EDR3} included in the catalog by the APOGEE team.
+Specifically, we use the \citet{Bailer-Jones2021-GaiaDistances} photo-geometric distance estimates to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$, assuming a Sun--Galactic center distance $R_\odot=8.122$ kpc \citep{GRAVITY2018-GalactocentricDistance} and height of the Sun above the midplane $z_\odot=20.8$ pc \citep{BennetBovy2019-SunZHeight}.
 Table \ref{tab:apogee-regions} lists the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$.
-For some Galactic regions with $R_{\rm gal}<5$ kpc or $R_{\rm gal}>13$ kpc, the median distance error exceeds 1 kpc but remains within our bin width of 2 kpc, and the vast majority of stars have much smaller distance uncertainties.}
+For some Galactic regions with $R_{\rm gal}<5$ kpc or $R_{\rm gal}>13$ kpc, the median distance error exceeds 1 kpc but remains within our bin width of 2 kpc, and the vast majority of stars have much smaller distance uncertainties.
 
@@
 We note that we use the full sample of \variable{output/sample_size.txt} APOGEE stars unless we explicitly compare to age estimates.
-{\bf Table \ref{tab:uncertainties} presents the median and dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the uncertainty in [Fe/H], [O/Fe], and log(age).}
+Table \ref{tab:uncertainties} presents the median and dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the uncertainty in [Fe/H], [O/Fe], and log(age).
 
@@
 A one-zone model assumes the entire gas reservoir is instantaneously mixed, removing all spatial dependence.
-This limits the ability to compare to observations across the disk, but it {\bf obviates} the complicating factor of stellar migration and better isolates the effects of the nucleosynthesis prescription.
+This limits the ability to compare to observations across the disk, but it obviates the complicating factor of stellar migration and better isolates the effects of the nucleosynthesis prescription.
 In this section, we compare the results from one-zone models which examine various parameters of the DTD while keeping other parameters fixed.
@@
 
-\subsection{\bf DTD Parameters: Slope, Timescale, and Plateau Width}
+\subsection{DTD Parameters: Slope, Timescale, and Plateau Width}
 \label{sec:onezone-dtd-params}
@@
 The left-hand panel of Figure \ref{fig:onezone-threepanel} compares the results of three one-zone models that are identical except for the slope of the power-law DTD.
-A steeper slope {\bf implies a greater number of prompt SNe Ia which rapidly enrich the ISM with Fe, producing a faster decline in [O/Fe] with increasing [Fe/H] and hence a sharper ``knee'' after the minimum delay time.
-This results} in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
+A steeper slope implies a greater number of prompt SNe Ia which rapidly enrich the ISM with Fe, producing a faster decline in [O/Fe] with increasing [Fe/H] and hence a sharper ``knee'' after the minimum delay time.
+This results in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars.
 In all cases the [O/Fe] DF is distinctly unimodal.
 The MDF is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.
-{\bf The abundance tracks converge to the equilibrium value, reflecting the yield ratio of CCSNe to SNe Ia which is the same in all models.}
+The abundance tracks converge to the equilibrium value, reflecting the yield ratio of CCSNe to SNe Ia which is the same in all models.
 
@@
 Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around $t=1$ Gyr.
-Doubling the timescale from 1.5 Gyr to 3 Gyr {\bf implies a longer median delay time, which} raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex.
+Doubling the timescale from 1.5 Gyr to 3 Gyr implies a longer median delay time, which raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex.
 A longer exponential timescale also produces a broader [O/Fe] DF with more high-$\alpha$ stars, but the distribution is still unimodal.
@@
 
-{\bf Unlike the previous three DTDs, we fix the hyper-parameters of the two-population and triple-system models to reproduce specific DTDs from the literature.
+Unlike the previous three DTDs, we fix the hyper-parameters of the two-population and triple-system models to reproduce specific DTDs from the literature.
 A variant of the two-population DTD with a broader Gaussian component ($t_{\rm max}=0.1$ Gyr, $\sigma=0.03$ Gyr) produced similar abundance tracks and a nearly identical [O/Fe] distribution to the fiducial parametrization in a one-zone model.
-The effect of different parameters for the triple-system DTD would be very similar to the plateau DTD described above, of which the triple-system DTD is a special case.}
-
-\subsection{\bf The Minimum SN Ia Delay Time}
+The effect of different parameters for the triple-system DTD would be very similar to the plateau DTD described above, of which the triple-system DTD is a special case.
+
+\subsection{The Minimum SN Ia Delay Time}
 \label{sec:onezone-minimum-delay}
@@
 The left-hand panel of Figure \ref{fig:onezone-twopanel} shows that $t_D$ has a much stronger effect in models which assume a power-law DTD than others.
-This is a consequence of the high number of prompt SNe Ia ({\bf $\bf t\lesssim100$ Myr;} see Figure \ref{fig:dtds}).
+This is a consequence of the high number of prompt SNe Ia ($t\lesssim100$ Myr; see Figure \ref{fig:dtds}).
 Moreover, a power-law DTD with a long $t_D$ may be observationally hard to distinguish from a plateau model.
@@
 
-\subsection{\bf The Form of the DTD}
+\subsection{The Form of the DTD}
 \label{sec:onezone-dtd-form}
@@
 At the other extreme are the two-population and power-law ($\alpha=-1.1$) DTDs, for which the SN Ia rate peaks immediately after the minimum delay time of 40 Myr, placing the high-$\alpha$ knee at ${\rm [Fe/H]}\approx-1.8$.
-The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is produced by the delayed exponential component, {\bf as noted by \citet{Vincenzo2017-ChemicalEvolution}}.
+The two-population model has a unique second knee at ${\rm [Fe/H]}\approx-0.2$ and ${\rm [O/Fe]}\approx0.1$, which is produced by the delayed exponential component, as noted by \citet{Vincenzo2017-ChemicalEvolution}.
 The abundance tracks from the plateau ($W=1$ Gyr) and exponential ($\tau=1.5$ Gyr) models occupy the intermediate space between these extremes.
@@
 The [O/Fe] DFs also show significant differences between the DTDs.
-In the triple-system model, star formation proceeds for such a long time before the knee that the [O/Fe] DF shows a slight second peak around the CCSN yield ratio {\bf ($\bf \sim0.45$ dex)}.
+In the triple-system model, star formation proceeds for such a long time before the knee that the [O/Fe] DF shows a slight second peak around the CCSN yield ratio ($\sim0.45$ dex).
 Out of all our one-zone models, this small bump is the only degree of bimodality that arises in the [O/Fe] DF.
@@
 In this section we focused on the fiducial inside-out SFH.
-\citet{Palicio2023-AnalyticDTD} compared similar DTDs in one-zone models with a two-infall SFH (see {\bf Section} \ref{sec:two-infall-discussion}).
+\citet{Palicio2023-AnalyticDTD} compared similar DTDs in one-zone models with a two-infall SFH (see Section \ref{sec:two-infall-discussion}).
 
@@
 Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row.
-{\bf A Gaussian scatter with a width equal to the median observational uncertainty in APOGEE DR17 (see Table \ref{tab:uncertainties}) is applied to the abundance of each model stellar population.
-For visual clarity,} each MDF is smoothed with a box-car width of 0.2 dex.
+A Gaussian scatter with a width equal to the median observational uncertainty in APOGEE DR17 (see Table \ref{tab:uncertainties}) is applied to the abundance of each model stellar population.
+For visual clarity, each MDF is smoothed with a box-car width of 0.2 dex.
     \textit{Left columns:} comparison between the inside-out and two-infall SFHs; both assume the exponential ($\tau=1.5$ Gyr) DTD. 
@@
 The two left-hand columns illustrate the effect of different SFHs on the model outputs, which is most pronounced in the inner Galaxy.
-Near the midplane {\bf and in the inner Galaxy}, the two-infall SFH produces a distinct bump $\sim0.4$ dex below the MDF peak, which is not seen for the inside-out SFH.
+Near the midplane and in the inner Galaxy, the two-infall SFH produces a distinct bump $\sim0.4$ dex below the MDF peak, which is not seen for the inside-out SFH.
 Away from the midplane, the low-metallicity tail is slightly more prominent for the two-infall than the inside-out model, and the two-infall MDFs extend to slightly higher metallicity.
@@
 In this case, $P$ is the APOGEE MDF, $Q$ is the model MDF, and $x={\rm [Fe/H]}$.
-{\bf We forward-model the observational uncertainties given in Table \ref{tab:uncertainties} by applying a random Gaussian scatter to the abundance of each model stellar population, and we numerically evaluate Equation \ref{eq:kl-divergence} with integration step size $d{\rm [Fe/H]}=0.01$ dex.}
-For each SFH and DTD, we compute $D_{\rm{KL}}$ in the 18 different {\bf Galactic} regions shown in Figure \ref{fig:feh-df-comparison}.
+We forward-model the observational uncertainties given in Table \ref{tab:uncertainties} by applying a random Gaussian scatter to the abundance of each model stellar population, and we numerically evaluate Equation \ref{eq:kl-divergence} with integration step size $d{\rm [Fe/H]}=0.01$ dex.
+For each SFH and DTD, we compute $D_{\rm{KL}}$ in the 18 different Galactic regions shown in Figure \ref{fig:feh-df-comparison}.
 We use bins in $R_{\rm gal}$ with a width of 2 kpc between 3 and 15 kpc, and bins in midplane distance of $|z|=0-0.5$ kpc, $0.5-1$ kpc, and $1-2$ kpc.
-The score $S$ for the entire model is taken to be the average of $D_{\rm{KL}}$ for each region $\bf (R_{\rm gal}, |z|)$ weighted by the number of APOGEE stars in that region $\bf N_\star(R_{\rm gal}, |z|)$ {\bf (see Table \ref{tab:apogee-regions})}:
+The score $S$ for the entire model is taken to be the average of $D_{\rm{KL}}$ for each region $(R_{\rm gal}, |z|)$ weighted by the number of APOGEE stars in that region $N_\star(R_{\rm gal}, |z|)$ (see Table \ref{tab:apogee-regions}):
 \begin{equation}
@@
 Figure \ref{fig:ofe-bimodality} compares the [O/Fe] distributions in the solar annulus ($7\leq R_{\rm gal}<9$ kpc and $0\leq|z|<2$ kpc) in two bins of [Fe/H] ($-0.6<{\rm [Fe/H]}<-0.4$ and $-0.4<{\rm [Fe/H]}<-0.2$) for select model outputs and APOGEE data.
-{\bf The purpose of the narrow [Fe/H] bins is to isolate the bimodality of the [O/Fe] distribution with minimal variation in [Fe/H].} The APOGEE distributions in the bottom-right panel (j) show that the high-$\alpha$ mode is more prominent at lower [Fe/H], but the distributions in both bins are clearly bimodal.
+The purpose of the narrow [Fe/H] bins is to isolate the bimodality of the [O/Fe] distribution with minimal variation in [Fe/H].
+The APOGEE distributions in the bottom-right panel (j) show that the high-$\alpha$ mode is more prominent at lower [Fe/H], but the distributions in both bins are clearly bimodal.
 The ``trough'' occurs near ${\rm [O/Fe]}\approx0.2$ in each bin.
@@
 On the other hand, the early-burst SFH {\it always} produces a bimodal distribution in the high-[Fe/H] bin regardless of the assumed DTD, but not in the low-[Fe/H] bin (the small low-$\alpha$ peak falls below our prominence threshold).
-For models with the late-burst and two-infall SFHs, the bimodality {\bf in the low-[Fe/H] bin} is variable depending on the DTD: those with longer median delay times (e.g., exponential, plateau, or triple-system) generally produce a bimodal distribution, while the two DTDs with the most prompt SNe Ia do not.
+For models with the late-burst and two-infall SFHs, the bimodality in the low-[Fe/H] bin is variable depending on the DTD: those with longer median delay times (e.g., exponential, plateau, or triple-system) generally produce a bimodal distribution, while the two DTDs with the most prompt SNe Ia do not.
 
@@
 The black curves represent the ISM abundance tracks in the 8 kpc zone.
-The red contours represent a 2-D {\bf Gaussian} kernel density estimate of the APOGEE abundance distribution in that Galactic region with a bandwidth of 0.03.
+The red contours represent a 2-D Gaussian kernel density estimate of the APOGEE abundance distribution in that Galactic region with a bandwidth of 0.03.
 The solid and dashed contours enclose 30\% and 80\% of stars in the sample, respectively.}
@@
 This ridge roughly coincides with the upper limit of the APOGEE distribution near the midplane.
-The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx-0.1${\bf which reflects the equilibrium abundance ratio of the second infall.}
+The three-peaked structure of the [O/Fe] distributions in Section \ref{sec:ofe-df} is explained by the abundance tracks here: a small population of stellar populations at ${\rm [O/Fe]}\approx0.4$ is produced initially, followed by the middle peak when the abundance track turns over, and finally the peak at ${\rm [O/Fe]}\approx-0.1$ which reflects the equilibrium abundance ratio of the second infall.
 
@@
 
-The two-population and power-law ($\alpha=-1.1$) DTDs, which have a large fraction of prompt {\bf ($\bf t\lesssim100$ Myr)} SNe Ia, produce stellar abundance distributions that are reasonably well-aligned with the APOGEE contours at low $|z|$, but they entirely miss the observed high-$\alpha$ sequence at large $|z|$.
+The two-population and power-law ($\alpha=-1.1$) DTDs, which have a large fraction of prompt ($t\lesssim100$ Myr) SNe Ia, produce stellar abundance distributions that are reasonably well-aligned with the APOGEE contours at low $|z|$, but they entirely miss the observed high-$\alpha$ sequence at large $|z|$.
 The ISM abundance tracks for the 8 kpc zone do not pass through the APOGEE 30\% contour at $|z|=1-2$ kpc.
@@
 
-The exponential ($\tau=1.5$ Gyr) DTD, {\bf which has an intermediate median delay time,} produces a distribution in Figure \ref{fig:ofe-feh-dtd} which aligns quite well with the 80\% APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to high [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
+The exponential ($\tau=1.5$ Gyr) DTD, which has an intermediate median delay time, produces a distribution in Figure \ref{fig:ofe-feh-dtd} which aligns quite well with the 80\% APOGEE contours in all $|z|$-bins, and even produces a ``ridge'' which extends to high [O/Fe] at low- and mid-latitudes (bottom and center panels, respectively).
 While it does better at populating the high-$\alpha$ sequence than the previous DTDs, the bulk of the model stellar populations at large $|z|$ still fall below the APOGEE 30\% contour.
@@
 \end{equation}
-where {\bf $d=2$ is the dimension of the sample space and} $r_k(\mathbf{x}_i)$ and $s_k(\mathbf{x}_i)$ are the distance to the $k$th nearest neighbor of $\mathbf{x}_i$ in the samples of $P$ and $Q$, respectively.
+where $d=2$ is the dimension of the sample space and $r_k(\mathbf{x}_i)$ and $s_k(\mathbf{x}_i)$ are the distance to the $k$th nearest neighbor of $\mathbf{x}_i$ in the samples of $P$ and $Q$, respectively.
 We take $k=2$ to find the nearest neighbor other than the sample itself.
-As before, $P$ is the APOGEE distribution and $Q$ is the model distribution, and in this case $\mathbf{x}=({\rm [Fe/H]}, {\rm [O/Fe]})$, {\bf without applying any scaling factor to each dimension.}
+As before, $P$ is the APOGEE distribution and $Q$ is the model distribution, and in this case $\mathbf{x}=({\rm [Fe/H]}, {\rm [O/Fe]})$, without applying any scaling factor to each dimension.
 As in Sections \ref{sec:feh-df} and \ref{sec:ofe-df}, we bin the model outputs and data by $R_{\rm gal}$ and $|z|$, calculate $\hat D_k(P||Q)$ in each region, and then take the weighted mean of each region as in Equation \ref{eq:feh-df-score} to arrive at a single score for each model.
@@
 
-Figure \ref{fig:ofe-feh-twoinfall} plots the stellar [O/Fe]--[Fe/H] abundances from the model with the two-infall SFH and plateau ($W=1$ Gyr) DTD {\bf in two different bins of $R_{\rm gal}$}.
+Figure \ref{fig:ofe-feh-twoinfall} plots the stellar [O/Fe]--[Fe/H] abundances from the model with the two-infall SFH and plateau ($W=1$ Gyr) DTD in two different bins of $R_{\rm gal}$.
 In the inner Galaxy, the model distribution at large $|z|$ lies at higher [O/Fe] and is more extended than the APOGEE distribution.
@@
 In all panels stars are limited to the solar annulus ($7\leq R_{\rm gal}<9$ kpc), and the layout of each panel is the same as in Figure \ref{fig:age-ofe-sfh}.
-{\bf The red numbers in the left-most panels indicate the number of APOGEE stars with \citetalias{Leung2023-Ages} ages in each bin of $|z|$.}}
+The red numbers in the left-most panels indicate the number of APOGEE stars with \citetalias{Leung2023-Ages} ages in each bin of $|z|$.}
     \label{fig:age-ofe-dtd}
@@
 where $\Delta\tau_k=\rm{med}(\tau_{\rm \vice})-\rm{med}(\tau_{\rm L23})$ is the difference between the mass-weighted median age in \vice and the median stellar age from \citetalias{Leung2023-Ages} in bin $k$, $n_{{\rm L23},k}$ is the number of stars from the \citetalias{Leung2023-Ages} age sample in bin $k$, and $n_{\rm L23,tot}$ is the total number of stars in the sample in that Galactic region.
-{\bf This is similar to a reduced $\chi^2$ estimator except that the difference in medians is not weighted by the variance in the observed sample.} If a bin has no modeled or observed stars, we do not calculate $\Delta \tau_k$ for that bin.
+This is similar to a reduced $\chi^2$ estimator except that the difference in medians is not weighted by the variance in the observed sample.
+If a bin has no modeled or observed stars, we do not calculate $\Delta \tau_k$ for that bin.
 As before, the score for the model as a whole is the average of $\Delta \tau_{\rm RMS}$ across all regions, weighted by the number of stars with age measurements in each region.
@@
 
-\subsection{\bf Qualitative Comparisons}
+\subsection{Qualitative Comparisons}
 \label{sec:discussion-scores}
@@
 
-{\bf The relative performance of each model is summarized in Table \ref{tab:results}.} We use these scores to indicate combinations of SFH and DTD that are favorable or unfavorable in certain regimes, but we do {\it not} fit our models to the data due to computational expense.
+The relative performance of each model is summarized in Table \ref{tab:results}.
+We use these scores to indicate combinations of SFH and DTD that are favorable or unfavorable in certain regimes, but we do {\it not} fit our models to the data due to computational expense.
 To avoid drawing strong conclusions from small numerical differences in scores, we simply write \yes, \meh, or \no, which corresponds to a score in the top, middle, or bottom third out of all models, respectively.
-{\bf The exact numerical scores are presented in Appendix \ref{app:quantitative-scores}.}
+The exact numerical scores are presented in Appendix \ref{app:quantitative-scores}.
 
@@
 For example, if the two-infall models are run with $y_{\rm Fe}^{\rm Ia}=0.0017$, the abundance tracks do not dip below solar [O/Fe] (see the bottom-right panel of Figure \ref{fig:ofe-feh-sfh}) and consequently they out-score every other SFH.
-Small adjustments in the yields can affect the quality of the fit between our models and the data, so we caution against over-interpreting the {\bf qualitative comparisons} in Table \ref{tab:results}.
-
-{\bf We also run a two-sample Kolmogorov-Smirnov (KS) test on the model [Fe/H] and [O/Fe] DFs to estimate the significance of the agreement with the observed distributions.
+Small adjustments in the yields can affect the quality of the fit between our models and the data, so we caution against over-interpreting the qualitative comparisons in Table \ref{tab:results}.
+
+We also run a two-sample Kolmogorov-Smirnov (KS) test on the model [Fe/H] and [O/Fe] DFs to estimate the significance of the agreement with the observed distributions.
 However, we consistently reject the null hypothesis that the model and observed abundances are drawn from the same distribution at very high significance ($p<<0.05$) in each Galactic region.
 The large sample size means that even small deviations from the APOGEE distribution result in a very small $p$-value, making the KS test a poor diagnostic for model comparison.
-Overall, this reinforces the conclusion that even our best-performing models cannot reproduce all observations.}
+Overall, this reinforces the conclusion that even our best-performing models cannot reproduce all observations.
 
@@
 More recently, \citet{Palicio2023-AnalyticDTD} compared a similar suite of DTDs in one-zone models with a two-infall SFH.
-In contrast to previous studies of the two-infall model \citep[e.g.,][]{Chiappini1997-TwoInfall,Matteucci2009-DTDModels,Spitoni2021-TwoInfall}, they {\bf did} incorporate gas outflows, making their models especially well-suited to compare to ours.
+In contrast to previous studies of the two-infall model \citep[e.g.,][]{Chiappini1997-TwoInfall,Matteucci2009-DTDModels,Spitoni2021-TwoInfall}, they did incorporate gas outflows, making their models especially well-suited to compare to ours.
 By modifying their yields, outflow mass-loading factor, and some of the parameters of their SFH, \citet{Palicio2023-AnalyticDTD} were able to achieve a good fit to solar neighborhood abundance data for both the SD and DD analytic DTDs, which are approximated by our exponential ($\tau=1.5$ Gyr) and plateau ($W=1$ Gyr) models, respectively.
@@
 This would not be too far beyond \citeauthor{Maoz2017-CosmicDTD}'s \citeyearpar{Maoz2017-CosmicDTD} finding that field galaxies and galaxy clusters have a different DTD slope.
-However, \citet{Walcher2016-SelfSimilarity} {\bf argued} that the similarity of the age--\aFe relation between solar neighborhood stars and nearby elliptical galaxies is evidence for a universal DTD.
+However, \citet{Walcher2016-SelfSimilarity} argued that the similarity of the age--\aFe relation between solar neighborhood stars and nearby elliptical galaxies is evidence for a universal DTD.
 A physical mechanism would be needed to produce a different slope or form for the DTD in different environments, such as a metallicity dependence in the fraction of close binaries \citep[e.g.,][]{Moe2019-CloseBinaryFraction}.
@@
 
-{\bf The origin of the Milky Way's \aFe bimodality remains disputed.
+The origin of the Milky Way's \aFe bimodality remains disputed.
 Some authors have argued that the combination of inside-out growth and radial migration sufficiently explains the observed distribution \citep[e.g.,][]{Kubryk2015-RadialMigrationEvolution,Sharma2021-RadialMigration,Chen2023-RadialMixingRedux,Prantzos2023-ThinThickDisks}, while others have argued that multiple episodes of gas infall at early times are required \citep[e.g.,][]{Chiappini1997-TwoInfall,Mackereth2018-AlphaBimodality,Spitoni2019-TwoInfall,Spitoni2020-TwoInfall,Spitoni2021-TwoInfall}.
 In agreement with \citetalias{Johnson2021-Migration}, we find that a smooth SFH combined with radial migration does not suffice.
-We find that these parameter choices predict too many stars between the high- and low-$\alpha$ sequences, resulting in a broad but unimodal \aFe distribution at fixed [Fe/H].}
+We find that these parameter choices predict too many stars between the high- and low-$\alpha$ sequences, resulting in a broad but unimodal \aFe distribution at fixed [Fe/H].
 
@@
 However, the MDF is more sensitive to the DTD in the inner Galaxy due to the more sharply declining SFH (see discussion in Section \ref{sec:feh-df}).
-{\bf Under the model of inside-out formation, the MDF in the inner Galaxy traces older populations which are more sensitive to the enrichment of prompt SNe Ia.}
+Under the model of inside-out formation, the MDF in the inner Galaxy traces older populations which are more sensitive to the enrichment of prompt SNe Ia.
 
@@
 Our results indicate that the allowed range of parameter space in GCE models is still too broad to precisely constrain the DTD.
-Future constraints may come from the Legacy Survey of Space and Time (LSST) at the Vera Rubin Observatory \citep{Ivezic2019-LSST}, which is expected to observe several million SNe during its {\bf 10}-year run.
-On the other hand, %better constraints on the Galactic SFH provided by
-{\bf the improved sample size of} SDSS-V \citep{Kollmeier2017-SDSS-V} will enable future GCE studies to constrain {\bf both the Galactic SFH and} the DTD at a higher confidence.
+Future constraints may come from the Legacy Survey of Space and Time (LSST) at the Vera Rubin Observatory \citep{Ivezic2019-LSST}, which is expected to observe several million SNe during its 10-year run.
+On the other hand,
+the improved sample size of SDSS-V \citep{Kollmeier2017-SDSS-V} will enable future GCE studies to constrain both the Galactic SFH and the DTD at a higher confidence.
 
@@
 We thank Prof.\ David H.\ Weinberg and attendees of OSU's Galaxy Hour for many useful discussions over the course of this project.
-{\bf We also thank the anonymous reviewer for their thoughtful and constructive comments on the manuscript.}
+We also thank the anonymous reviewer for their thoughtful and constructive comments on the manuscript.
 
@@
 manuscript.
-The multi-zone model outputs and APOGEE sample dataset are stored at \url{https://zenodo.org/doi/10.5281/zenodo.10961090}, {\bf and the source code for this manuscript is stored at \url{https://zenodo.org/doi/10.5281/zenodo.12521399}}.
+The multi-zone model outputs and APOGEE sample dataset are stored at \url{https://zenodo.org/doi/10.5281/zenodo.10961090}, and the source code for this manuscript is stored at \url{https://zenodo.org/doi/10.5281/zenodo.12521399}.
 
@@
 
-{\bf Here we state our assumptions for the hyper-parameters which can affect the shape of the \citet{Greggio2005-AnalyticalRates} DTDs.
+Here we state our assumptions for the hyper-parameters which can affect the shape of the \citet{Greggio2005-AnalyticalRates} DTDs.
 For the SD case, we assume a power law slope of the mass ratio distribution with $\gamma=1$, an efficiency of mass transfer $\epsilon=1$, and maximum initial primary mass of $8~{\rm M}_\odot$.
-For the DD channel, we additionally assume a nuclear timescale for the least massive secondary $\tau_{\rm n,x}=1$ Gyr, a minimum gravitational insprial delay $\tau_{\rm gw,i}=1$ Myr, an exponent of the power law distribution of final separations $\beta_{\rm a}=0$ (for the WIDE scheme), and an exponent of the power law distribution of gravitational delays $\beta_{\rm g}=-0.75$ (for the CLOSE scheme).}
+For the DD channel, we additionally assume a nuclear timescale for the least massive secondary $\tau_{\rm n,x}=1$ Gyr, a minimum gravitational insprial delay $\tau_{\rm gw,i}=1$ Myr, an exponent of the power law distribution of final separations $\beta_{\rm a}=0$ (for the WIDE scheme), and an exponent of the power law distribution of gravitational delays $\beta_{\rm g}=-0.75$ (for the CLOSE scheme).
 
@@
 The WIDE prescription is also best approximated by a plateau DTD, but with a longer plateau width of $W=1$ Gyr.
-In all cases, the {\bf effect of the} difference between the analytic DTD and its simple approximation is too small to be observed.
+In all cases, the effect of the difference between the analytic DTD and its simple approximation is too small to be observed.
 We also ran a multi-zone model with the inside-out SFH and the \citet{Greggio2005-AnalyticalRates} SD DTD and found it produced nearly identical results to the model with the exponential ($\tau=1.5$ Gyr) DTD.
@@
 
-\section{\bf Quantitative Comparison Scores}
+\section{Quantitative Comparison Scores}
 \label{app:quantitative-scores}
@@
 
-{\bf Table \ref{tab:scores} presents the quantitative scores which measure the difference between the multi-zone outputs and APOGEE data for four observables.
+Table \ref{tab:scores} presents the quantitative scores which measure the difference between the multi-zone outputs and APOGEE data for four observables.
 Details of the calculations for each observable are presented in the corresponding subsections of Section \ref{sec:multizone-results}, but in summary, divergence statistics between the multi-zone output and APOGEE data (Equation \ref{eq:kl-divergence} for the [Fe/H] and [O/Fe] DFs, Equation \ref{eq:2d-kl-divergence} for the [O/Fe]--[Fe/H] plane, and Equation \ref{eq:age-ofe-score} for the age--[O/Fe] plane) are computed within each Galactic region.
 The overall score for the model is the average of the divergence statistics across all regions, weighted by the number of APOGEE targets in each region.
-The scores can be strongly affected by zero-point offsets between the model and observed abundance distributions, so we caution against using these scores as an absolute metric of model performance.}
+The scores can be strongly affected by zero-point offsets between the model and observed abundance distributions, so we caution against using these scores as an absolute metric of model performance.
 
